### 2023-08-14 appendix.Rmd
first commit

\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}
\renewcommand{\thefigure}{\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}

# **Supplementary Information**

\setcounter{page}{1}
\centering
\noindent \hspace*{5mm} \small Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare \newline
\hspace*{1cm} \small Amalia P. M. Bastos\textsuperscript{1,2}, Scott Claessens\textsuperscript{2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, \newline
\hspace*{25mm} Quentin D. Atkinson\textsuperscript{2}, Alex H. Taylor\textsuperscript{2,3,5,6} \newline
\raggedright
\noindent \footnotesize \textsuperscript{1} Department of Psychological & Brain Sciences, Johns Hopkins University, Baltimore, MD, United States \newline
\noindent \footnotesize \textsuperscript{2} School of Psychology, University of Auckland, Auckland, New Zealand \newline
\noindent \footnotesize \textsuperscript{3} School of Biological Sciences, University of Canterbury, Christchurch, New Zealand \newline
\noindent \footnotesize \textsuperscript{4} School of Computer Science, University of Auckland, Auckland, New Zealand \newline
\noindent \footnotesize \textsuperscript{5} ICREA, Pg. Lluís Companys 23, Barcelona, Spain \newline
\noindent \footnotesize \textsuperscript{6} Institute of Neuroscience, Universitat Autònoma de Barcelona, Barcelona, Spain \newline
\normalsize
\newpage

## Supplementary Figures

(ref:plotSurvCure3Caption) _Median posterior probabilities of undetected tool use for each parrot species without observed evidence of tool use from reduced model._ This reduced version of the phylogenetic survival cure model does not contain relative brain size or feeding strategy as predictors, nor does it contain any phylogenetic covariance. The only information included in the model is the number of papers published and the number of YouTube search hits for each species. Each point is a parrot species without observed evidence of tool use, and the colour of the points scales with the probability of undetected tool use. All else being equal, those species with fewer published papers and fewer YouTube search hits have a higher probability of being undetected tool users.

```{r plotSurvCure3, echo=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.cap="(ref:plotSurvCure3Caption)"}
tar_read(plotSurvCure3)
```

\newpage

(ref:plotSurvCure9Caption) _Receiver operating characteristic (ROC) curve for the phylogenetic survival cure model._ The area-under-the-curve in this plot is `r printnum(tar_read(auc), digits = 2)`, suggesting that the model is able to adequately classify observed tool users and non-tool users.

```{r plotSurvCure9, echo=FALSE, warning=FALSE, fig.width=4, fig.height=4, fig.cap="(ref:plotSurvCure9Caption)"}
tar_read(plotSurvCure9)
```

\newpage

(ref:plotSurvCure5Caption) _Prior and posterior phylogenetic covariance functions from the Bayesian survival cure model fitted to the full dataset._ Lines are median posterior functions and shaded areas are 50% and 95% credible intervals.

```{r plotSurvCure5, echo=FALSE, warning=FALSE, fig.width=7, fig.height=4, fig.cap="(ref:plotSurvCure5Caption)"}
tar_read(plotSurvCure5)
```

\newpage

(ref:plotSurvCure6Caption) _Between-species correlation matrix implied by the posterior phylogenetic covariance function from the Bayesian survival cure model._ Correlations are median posterior estimates. Individual species names omitted for space reasons.

```{r plotSurvCure6, echo=FALSE, warning=FALSE, fig.width=6.5, fig.height=6, fig.cap="(ref:plotSurvCure6Caption)"}
tar_read(plotSurvCure6)
```

\newpage

(ref:plotComparisonCaption) _Comparing results between the survival cure model and models fitted to the pre-survey and post-survey data without any survival cure component._ Densities are full posterior distributions from three separate models iterated over 100 posterior parrot phylogenies. Points represent posterior medians, and lines represent 50% and 95% credible intervals.

```{r plotComparison, echo=FALSE, warning=FALSE, fig.width=8, fig.height=4, fig.cap="(ref:plotComparisonCaption)"}
tar_read(plotComparison)
```

\newpage

(ref:plotASR1Caption) _Results of exploratory ancestral state reconstruction analysis fitted to pre-video-survey data, represented on a maximum clade credibility tree._ Tip nodes represent the presence (red) or absence (grey) of observed tool use in the scientific literature. Pie charts represent the posterior probability of tool use presence at each ancestral node.

```{r plotASR1, echo=FALSE, warning=FALSE, fig.width=10, fig.height=13, fig.cap="(ref:plotASR1Caption)"}
tar_read(plotASR1)
```

\newpage

(ref:plotASR2Caption) _Results of exploratory ancestral state reconstruction analysis fitted to post-video-survey data, represented on a maximum clade credibility tree._ Tip nodes represent the presence (red) or absence (grey) of observed tool use in the scientific literature and the video survey. Pie charts represent the posterior probability of tool use presence at each ancestral node.

```{r plotASR2, echo=FALSE, warning=FALSE, fig.width=10, fig.height=13, fig.cap="(ref:plotASR2Caption)"}
tar_read(plotASR2)
```

\newpage

(ref:plotASR3Caption) _Results of exploratory ancestral state reconstruction analysis fitted to predicted probabilities from the phylogenetic survival cure model, represented on a maximum clade credibility tree._ Tip nodes represent the median posterior predicted probabilities of tool use from the phylogenetic survival cure model, with more red indicating an increasing probability of tool use presence and more grey indicating a decreasing probability of tool use presence. Pie charts represent the posterior probability of tool use presence at each ancestral node.

```{r plotASR3, echo=FALSE, warning=FALSE, fig.width=10, fig.height=13, fig.cap="(ref:plotASR3Caption)"}
tar_read(plotASR3)
```

\newpage

(ref:plotPhylo2Caption) _Data on encephalisation quotient and feeding strategy for all parrots, presented on a maximum clade credibility tree._ Tip points are coloured according to feeding generalism (orange) and specialism (blue), and scaled according to encephalisation quotient (EQ).

```{r plotPhylo2, echo=FALSE, warning=FALSE, fig.width=17, fig.height=15, fig.cap="(ref:plotPhylo2Caption)"}
tar_read(plotPhylo2)
```

\newpage

(ref:plotPhylo3Caption) _Data on number of scientific publications until tool use discovery for all parrots, presented on a maximum clade credibility tree._ Tip points are scaled according to the number of published papers up until tool use discovery (or, if tool use has not been observed, the current number of published papers).

```{r plotPhylo3, echo=FALSE, warning=FALSE, fig.width=17, fig.height=15, fig.cap="(ref:plotPhylo3Caption)"}
tar_read(plotPhylo3)
```

\newpage

(ref:plotPhylo4Caption) _Data on number of video search hits until tool use discovery for all parrots, presented on a maximum clade credibility tree._ Tip points are scaled according to the estimated number of video search hits up until tool use discovery (or, if tool use has not been observed, the current number of video search hits).

```{r plotPhylo4, echo=FALSE, warning=FALSE, fig.width=17, fig.height=15, fig.cap="(ref:plotPhylo4Caption)"}
tar_read(plotPhylo4)
```

\newpage

(ref:plotSurvCure7Caption) _Prior predicted probabilities of tool use for each species from our phylogenetic survival cure model._ Points are prior medians and lines are 50% and 95% credible intervals.

```{r plotSurvCure7, echo=F, fig.width=7, fig.height=10, fig.cap="(ref:plotSurvCure7Caption)"}
tar_read(plotSurvCure7)
```

\newpage

(ref:plotSurvCure8Caption) _Results of sensitivity analysis._ The phylogenetic survival cure model was fitted with either a standard Normal(0, 1) prior on the intercept or an alternative Normal(1.78507, 2) prior on the intercept. This latter prior is wider on the logit scale and roughly converts to a 0.86 prior probability of non-tool-use (or a 0.14 prior probability of tool-use, which is the proportion of tool users in the dataset). The sensitivity analysis showed that changing this intercept prior did not have a marked impact on (a) the posterior rankings of parrot species from 1st to 174th or (b) the median posterior probabilities of tool use for parrot species.

```{r plotSurvCure8, echo=F, fig.width=4.5, fig.height=7.5, fig.cap="(ref:plotSurvCure8Caption)"}
tar_read(plotSurvCure8)
```

\newpage

(ref:plotTraceCaption) _Trace plots for the Bayesian phylogenetic survival cure model._ Only four chains are shown for ease of presentation.

```{r plotTrace, echo=FALSE, warning=FALSE, fig.width=6, fig.height=6, fig.cap="(ref:plotTraceCaption)"}
tar_read(plotTrace)
```

\newpage

(ref:plotSurvCureSimCaption) _Posterior estimates from Bayesian survival cure models fitted to 100 datasets simulated with known parameters._ Each dataset consisted of 100 species. Known parameters are presented as solid vertical lines, whereas points and horizontal lines represent posterior medians and 95% credible intervals. The models were successfully able to recapture the parameters from the simulated datasets.

```{r plotSurvCureSim, echo=FALSE, warning=FALSE, fig.width=8.5, fig.height=8.5, fig.cap="(ref:plotSurvCureSimCaption)"}
tar_read(plotSurvCureSim)
```

### 2023-08-14 manuscript.Rmd
first commit

---
title             : "Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare"
shorttitle        : "Parrot tool use"

author: 
  - name          : "Amalia P. M. Bastos"
    affiliation   : "†,1,2"
  - name          : "Scott Claessens"
    affiliation   : "*†,2"
  - name          : "Ximena J. Nelson"
    affiliation   : "3"
  - name          : "David Welch"
    affiliation   : "4"
  - name          : "Quentin D. Atkinson"
    affiliation   : "‡,2"
  - name          : "Alex H. Taylor"
    affiliation   : "‡,2,3,5,6"

affiliation:
  - id            : "1"
    institution   : "\\footnotesize Department of Psychological & Brain Sciences, Johns Hopkins University, Baltimore, MD, United States"
  - id            : "2"
    institution   : "\\footnotesize School of Psychology, University of Auckland, Auckland, New Zealand"
  - id            : "3"
    institution   : "\\footnotesize School of Biological Sciences, University of Canterbury, Christchurch, New Zealand"
  - id            : "4"
    institution   : "\\footnotesize School of Computer Science, University of Auckland, Auckland, New Zealand"
  - id            : "5"
    institution   : "\\footnotesize ICREA, Pg. Lluís Companys 23, Barcelona, Spain"
  - id            : "6"
    institution   : "\\footnotesize Institute of Neuroscience, Universitat Autònoma de Barcelona, Barcelona, Spain"

abstract: |
 Studying the prevalence of putatively rare behaviours, such as tool use, is challenging because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort. Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to approximate actual rates of a rarely observed behaviour based on limited data, targeting tool use in parrots. Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%). Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11% and 17% of extant parrot species may be tool users. These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait. Overall, our findings challenge the assumption that current sampling effort captures the full distribution of putatively rare animal behaviours. Combining our sampling and analysis methods offers a fruitful approach for investigating the distribution, drivers, and origins of other rare behaviours.

keywords          : "tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling"
wordcount         : "4273 words excluding Methods (Methods: 1792 words)"
bibliography      : ["r-references.bib"]
floatsintext      : yes
figurelist        : no
figsintext        : yes
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
numbersections    : false
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes: 
  - \usepackage{array}
  - \usepackage{caption}
  - \usepackage{graphicx}
  - \usepackage{siunitx}
  - \usepackage[normalem]{ulem}
  - \usepackage{colortbl}
  - \usepackage{multirow}
  - \usepackage{hhline}
  - \usepackage{calc}
  - \usepackage{tabularx}
  - \usepackage{threeparttable}
  - \usepackage{wrapfig}
  - \usepackage{adjustbox}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \raggedbottom
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1,small}}
  - \captionsetup[figure]{font={stretch=1,small}}
  - \nolinenumbers
  - \note{\raggedright † indicates shared first authorship, ‡ indicates shared senior authorship \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand. \text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}} \par This working paper has not yet been peer-reviewed.}
appendix          : "appendix.Rmd"
csl               : nature.csl
---

\linenumbers

Our understanding of the evolution of animal behaviour is built on the assumption that we have access to sufficient data[@MacLean2012; @Lefebvre2011; @Logan2018]. However, this is not always the case. Data on behaviours that are rare, fleeting, or otherwise difficult to observe are likely to be patchy and incomplete[@Healy2007; @Powell2017]. Among species for which such behaviours have not been observed, it can be difficult to differentiate between cases in which the species is truly incapable of producing the behaviour and cases in which the species is capable of producing the behaviour but the behaviour has not yet been observed. Such a distinction can be critical for drawing conclusions about the rarity and evolution of the behaviour in question.

Comparative work on the evolution of tool use is a paradigmatic example of this issue. The initial discoveries of tool use in chimpanzees[@Goodall1964], birds[@Hunt1996], dolphins[@Smolker1997], and octopuses[@Finn2009] occurred decades after significant advances on other more easily measurable aspects of their biology. Since these initial discoveries, scholars have used the distribution of reported tool use across species to make various claims about the evolutionary drivers of tool use behaviours. For example, based on the observation that bird species with reported tool use tended to have larger brains, researchers have identified higher relative brain size as a likely precondition for tool using capabilities[@Lefebvre2002;@Lefebvre1997;@Lefebvre2004]. These researchers argue that larger brains are better able to integrate visual and somatosensory information when innovating novel behaviours, such as tool use, in changing environments[@Sol2005;@Sol2009]. Similarly, researchers have used existing reports of tool use in birds to debate the roles of generalist versus specialist feeding strategies in driving the evolution of tool use, with some arguing that feeding generalists require technical innovations to expand their dietary niche[@Ducatez2015;@Overington2011;@Sol2005] and others arguing that feeding specialists require technical innovations for extractive foraging of specific foods[@HenkeVonDerMalsburg2020;@MettkeHofmann2014].

However, before we can make claims of this kind, we need to know whether current research effort in the literature is sufficient for robust conclusions to be drawn about the evolution of tool use. In fact, evidence suggests that research effort is often systematically biased towards particular taxonomic groups, parts of the world that are easy to access, and species with life history traits that make them easier to study, such as larger distribution ranges and population sizes[@Ducatez2014]. This is a crucial limitation because insufficient observation may lead researchers to miss true instances of tool behaviours and thus draw premature conclusions about the evolutionary drivers and origins of tool use. While researchers have attempted to deal with this problem by controlling for the number of scientific papers published on different species, previous work has not yet attempted to quantify and explicitly model the relationship between actual tool-using behaviour and what is reported in the scientific literature. If more tool-using species exist than previously thought, this could have important implications for theories of the evolutionary drivers and origins of tool use and, more generally, for our understanding of how rare this behaviour actually is.

One potentially powerful method for quantifying actual rates of rare animal behaviours is crowdsourcing[@Nelson2013]. In a crowdsourcing study, researchers collect reports from the general public and/or collate and analyse videos posted on social media platforms. This citizen science approach has been widely used in ecology to monitor the distributional patterns of species[@Dickinson2010], but has also recently been used to uncover a variety of rare animal behaviours, including interspecies play in dogs[@Nelson2013], novel problem-solving behaviours in horses[@Krueger2019], and socially-learned foraging innovations in cockatoos[@Klump2021;@Klump2022]. By casting the net wider than the scientific literature, the crowdsourcing method can provide an indication of the tool-using species that the literature might be missing.

Even after using this crowdsourcing approach, some tool-users could _still_ remain unobserved. An additional approach to identify these unobserved species is to specify a causal model of the process that generates the observed data. We propose one such causal model in Figure \@ref(fig:plotDAG). In this model, we assume that the presence of tool use in the scientific literature (or in crowdsourced reports) is caused by both unobserved tool use capabilities and the number of published studies (or the number of crowdsourced reports) for any given species. Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected. Furthermore, based on existing theories of the evolution of tool use[@Ducatez2015;@HenkeVonDerMalsburg2020;@Lefebvre1997;@Lefebvre2002;@Lefebvre2004;@MettkeHofmann2014;@Overington2011;@Sol2005;@Sol2009], we propose that the unobserved presence or absence of tool use is additionally caused by relative brain size, feeding strategy, and shared phylogenetic ancestry. Expressing this causal model as a statistical model can suggest further species which are likely to be unobserved tool-users and, simultaneously, test existing theories of the evolutionary drivers of tool use without incorrectly assuming that absence of evidence is evidence of absence.

(ref:plotDAGCaption) _Causal model of observed tool use._ Directed acyclic graph of the causal relationships between observed tool use and other variables. Available scientific data on tool use is caused both by unobserved tool use presence and scientific research effort (i.e., number of publications). Available crowdsourced data on tool use is caused both by unobserved tool use presence and crowdsourcing effort (i.e., number of crowdsourced reports). According to theory, unobserved tool use presence should be caused by relative brain size (encephalisation quotient) and feeding strategy (generalist vs. specialist). These variables all share unobserved confounds generated by shared phylogenetic history. Grey circles indicate unobserved variables.

```{r plotDAG, echo=F, fig.width=6, fig.height=3.6, fig.cap="(ref:plotDAGCaption)"}
tar_read(plotDAG)
```

Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool use in the parrot order. We focus on tool use in parrots for a number of reasons. First, the scientific literature suggests that only a small proportion of extant parrot species (11 out of 398[@Burgio2019]; 3%) use tools[@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;@Auersperg2012;@Bastos2021;@BentleyCondit2010;@Borsari2005;@Goodman2018;@Heinsohn2017;@Janzen1976;@Lambert2015;@Lefebvre2002;@OHara2021] (note that we do not include in this count species that have been previously shown to use touchscreen devices as these behaviours were explicitly trained[@Kleinberger2023]). Parrot tool use thus provides an ideal test case for examining how robust sampling is in the scientific literature. Second, parrots are highly popular as pets. Over 70% of all extant parrot species are bred in the aviculture industry and kept as pets worldwide[@Anderson2003;@Carrete2008;@Drews2001;@Kelly2014;@Li2014;@Su2015;@Young2012], enabling us to leverage the power of crowdsourcing on a social media platform to search for evidence of tool use[@Nelson2013]. Third, detailed data on relative brain sizes[@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;@Schuck2008;@Silva2017], feeding strategies[@Wilman2016], and shared ancestry[@Jetz2012] exist for parrots, allowing us to fit the statistical model implied by Figure \@ref(fig:plotDAG) to the entire parrot order.

We first present the results from our crowdsourcing survey, in which we collated videos of tool use in parrots from an online video platform. This survey reveals a number of previously unidentified tool-using parrot species, which we map onto the phylogeny of the parrot order. We then describe our statistical model in more detail, and use it to (_i_) rank further parrot species that are likely unobserved tool users and (_ii_) re-examine key hypotheses regarding the evolutionary drivers and origins of tool use in parrots.

# Results

## Crowdsourcing video survey

We surveyed the social media platform YouTube for video evidence of tool use in parrots (see Methods for detailed search criteria). In our search, we defined "true" tool use behaviour as the manipulation of an unattached object to achieve a goal[@Shumaker2011], while "borderline" tool use involved the use of an object that was still attached to a substrate[@Seed2010].

```{r echo=F}
tar_load(crowdData)
trueCrowdData <- filter(crowdData, ToolUse == "Y")
bordCrowdData <- filter(crowdData, ToolUse == "B")
```

In total, we found `r nrow(crowdData)` videos of `r crowdData %>% pull(IndividualID) %>% unique() %>% length()` individuals from `r crowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` parrot species performing either true tool use (`r nrow(trueCrowdData)` videos of `r trueCrowdData %>% pull(IndividualID) %>% unique() %>% length()` individuals from `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` species) or borderline tool use (`r nrow(bordCrowdData)` videos of `r bordCrowdData %>% pull(IndividualID) %>% unique() %>% length()` individuals from `r bordCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` species). All videos featured pet parrots in captive settings. In `r crowdData %>% pull(HumanInfluence) %>% str_starts("No") %>% sum()` of these videos, owners did not appear to interfere with the subjects' actions. In `r crowdData %>% pull(HumanInfluence) %>% str_starts("Yes") %>% sum()` videos, there was potential interference, either from the owners being in close physical contact with the bird (e.g., bird perching on hand), talking to the bird, or handing it the tool (which occurred in only two videos). We could not establish the degree of interference in the remaining `r crowdData %>% pull(HumanInfluence) %>% str_starts("Unknown") %>% sum()` videos, as sound had been removed or was substituted by music. None of the videos featured owners directly rewarding tool use behaviours with food. All borderline tool use cases were excluded from further analyses.

Of the `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` parrot species performing true tool use, `r trueCrowdData %>% filter(Species != "Unknown") %>% group_by(Species, IndividualID) %>% summarise(n = n(), .groups = "drop") %>% group_by(Species) %>% summarise(check = n() > 1, .groups = "drop") %>% pull(check) %>% sum()` were represented in our video survey by two or more individuals over multiple independent observations. True tool use always involved the subject using an object for self-scratching (`r trueCrowdData %>% mutate(BodyPartScratched = str_detect(BodyPartScratched, "Head/Neck")) %>% pull(BodyPartScratched) %>% sum()` videos involved scratching the head and/or neck). The most common tool (`r sum(pull(trueCrowdData, EvaluatedTool) == "Feather")` videos) was a moulted feather. Human-made objects (e.g., pens, spoons, pieces of wood, cardboard) were also common.

According to YouTube video descriptions and owner comments, `r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Male"))` of the individuals performing true tool use were males and `r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Female"))` were females. No sex information was provided for the remaining `r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Unknown"))` individuals. As owners provided no information on whether sex had been established through genetic testing, and sexual dimorphism in parrots is rare[@Bercovitz1987;@Hoyo2011], we could not typically ascertain if descriptions were accurate. It is unclear if the disproportionately large number of males in the sample is a consequence of owners more readily assuming their parrots are male when they have not been genetically tested, owners being more likely to own or film male parrots, or male parrots exhibiting more true tool use behaviours than female parrots.

Figure \@ref(fig:plotPhylo1) maps the findings from the video survey onto a maximum clade credibility phylogeny for the parrot order, plotted alongside species previously identified in the scientific literature. Before the video survey, 11 parrot species (3%) had been identified as tool users in the scientific literature. Across our video survey, we observed true tool use in `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` species, 5 of which overlapped with the scientific literature and `r (trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()) - 5` of which were novel species. All of the species identified in the video survey were cockatoos (Cacatuidae), Old World parrots (Psittacinae), or neotropical parrots (Arinae). The most common species in our survey, accounting for `r crowdData %>% filter(Species == "Pyrrhura molinae") %>% nrow()` videos from `r crowdData %>% filter(Species == "Pyrrhura molinae") %>% pull(IndividualID) %>% unique() %>% length()` individuals, was the green-cheeked conure (_Pyrrhura molinae_). In accordance with the scientific literature, the video survey found no evidence of tool use in any species of Psittaculidae, despite this family containing some of the most commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet species. Combining both the video survey and the scientific literature, we can thus identify 28 tool-using parrot species overall (7%), compared to the 11 previously reported.

(ref:plotPhylo1Caption) _Results of crowdsourcing video survey and phylogenetic survival cure modelling mapped onto a maximum clade credibility phylogeny of the parrot order._ Purple tips indicate species observed in the scientific literature and in the video survey. Blue tips indicate species observed only in the scientific literature. Orange tips indicate species observed only in the video survey (note that three species observed only in the video survey are not present in the phylogeny due to a lack of genomic data: _Psittacara erythrogenys_, _Psittacus timneh_, and _Aratinga nenday_). Yellow tips indicate the top ten most likely tool-using species from our phylogenetic survival cure model which were not observed in the scientific literature or the video survey. All other tips are labelled as absent (grey).

```{r plotPhylo1, echo=F, fig.width=17, fig.height=15, fig.cap="(ref:plotPhylo1Caption)"}
tar_read(plotPhylo1)
```

The identification of new tool-using species in our video survey increases the extent to which phylogeny can explain the distribution of tool use in the parrot order. We estimated phylogenetic signal (Pagel's $\lambda$) of tool use using both the pre-video-survey and post-video-survey data. Pagel's $\lambda$ varies between 0 and 1, where 0 implies that the distribution of a trait across species is unexplained by phylogenetic relatedness and 1 implies that the distribution of a trait across species is fully explained by phylogeny. Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's $\lambda$ of `r printnum(mean(tar_read(phySignal1)))` (95% credible interval [`r printnum(quantile(tar_read(phySignal1), 0.025))` `r printnum(quantile(tar_read(phySignal1), 0.975))`]). This estimate was moderate-to-strong, but highly uncertain. In comparison, combining the evidence from both the literature and the video survey (post-video-survey data; 28 tool-using species) resulted in a stronger and more certain estimate of phylogenetic signal. With these data, we estimated Pagel's $\lambda$ = `r printnum(mean(tar_read(phySignal2)))` (95% CI [`r printnum(quantile(tar_read(phySignal2), 0.025))` `r printnum(quantile(tar_read(phySignal2), 0.975))`]). Thus, the results of our video survey increase the extent to which the distribution of tool use across parrot species can be explained by shared phylogenetic ancestry. This suggests that we can potentially use phylogenetic information, along with other variables, to identify further tool-using parrot species that may remain undetected.

## Phylogenetic survival cure model

In addition to the 28 tool-using species identified in the literature and our video survey, we fitted a Bayesian phylogenetic survival cure model to rank further species that are likely to be undetected tool-users (i.e., tool-using species with no tool use reported in the literature or in crowdsourced videos).

Survival cure models are often used in the medical sciences to analyse the time to some event, such as cancer relapse, with censored patient data[@Amico2018]. The data are right-censored because some patients have relapsed when they are measured, and some have not yet relapsed when they are measured (i.e., they are censored). The cure aspect of these models comes from an additional assumption that a certain proportion of the population is "cured" and can never relapse, no matter how long we measure them for.

Our tool use problem has the same features. We are modelling a time-to-event; specifically, the amount of "time" (i.e., observation opportunities measured as the number of published papers or crowdsourced videos) until tool use is identified. This is right-censored data, because many species will not have had tool use identified when we measure them. Moreover, we can assume that a certain proportion of the population is "cured" -- that is, they are not tool users, and so we will never identify tool use for them, no matter how long we measure them for.

In our model, we infer the tool-using status of each species by allowing each species to have their own probability of being "cured" (i.e., not a tool user). Following our causal model (Figure \@ref(fig:plotDAG)), we predict these probabilities based on feeding strategy, encephalisation quotient, and phylogenetic history (see Methods for full model). The model additionally takes research effort into account by allowing that, among species for which tool use is unobserved, all else being equal those with fewer published papers and fewer video search hits have a higher probability of being undetected tool users (Supplementary Figure \@ref(fig:plotSurvCure3)).

```{r echo=FALSE}
tar_load(plotSurvCure1)
```

We found that this phylogenetic survival cure model was able to adequately distinguish between species with and without evidence for tool use, with an area-under-the-curve classification statistic of `r printnum(tar_read(auc), digits = 2)` (Supplementary Figure \@ref(fig:plotSurvCure9)). To further estimate the accuracy of the model's predictions, we also used a leave-one-species-out approach with known tool users. For each of the 25 tool-using species that were represented on the phylogeny and for which we had brain size and genomic data (we lacked data for three tool-using species), we fitted the model to a modified dataset which set tool use to be absent for the target species in both the scientific literature and the video survey. Across `r length(tar_read(cv))` cross-validation models, `r sum(tar_read(cv))` models (`r printnum(mean(tar_read(cv))*100, digits = 0)`%) continued to predict the target species as having a median posterior probability of tool use that was within the range of all other tool users. This classification rate was greater than the baseline classification rate of `r printnum(mean(plotSurvCure1$data %>% filter(ToolUse == "Absent") %>% pull(med) > 0.16478274) * 100, digits = 0)`% for species without evidence of tool use in the full model (`r sum(plotSurvCure1$data %>% filter(ToolUse == "Absent") %>% pull(med) > 0.16478274)` of `r nrow(plotSurvCure1$data %>% filter(ToolUse == "Absent"))` species without evidence of tool use had a median posterior probability of tool use that was within the range of the tool-using species). Together, the area-under-the-curve statistic and the leave-one-species-out approach suggest that the model is able to adequately classify known tool users, with some error.

Figure \@ref(fig:plotSurvCure1) visualises the ranked posterior probabilities of tool use from the phylogenetic survival cure model for all parrot species. As expected, the known tool users are ranked towards the top of this list. However, several "tool use absent" species also rank highly on the list, despite not being identified as tool users in the scientific literature or in our video survey. In fact, according to the model, the most likely tool user is a species for which tool use is unobserved in our data: the blue-eyed cockatoo (_Cacatua opthalmica_). This species is endemic to Papua New Guinea and is relatively understudied, with only `r tar_read(d)$EX.Pre.Tool.Papers[165]` published papers and `r tar_read(d)$SearchHits[165]` video search hits, which is fewer than the model expects are necessary to discover tool use when it is present (Figure \@ref(fig:plotSurvCure2)). This species is also found in the _Cacatua_ genus, a clade containing several known tool users. This prediction makes sense given the high phylogenetic signal for tool use reported by the model (Supplementary Figures \@ref(fig:plotSurvCure5) and \@ref(fig:plotSurvCure6)). Beyond the blue-eyed cockatoo, other highly ranked species without observed evidence of tool use are the Meyer's parrot (_Poicephalus meyeri_), the golden parakeet (_Guaruba guarouba_), the long-billed corella (_Cacatua tenuirostris_), the Solomons cockatoo (_Cacatua ducorpsii_), the red-fronted parrot (_Poicephalus gulielmi_), the Cape parrot (_Poicephalus robustus_), the yellow-eared parrot (_Ognorhynchus icterotis_), the red-vented cockatoo (_Cacatua haematuropygia_), and the gang-gang cockatoo (_Callocephalon fimbriatum_). Figure \@ref(fig:plotPhylo1) plots these species on the parrot phylogeny, using the top ten highest ranked species without observed evidence of tool use as an abitrary cutoff for visualisation purposes.

(ref:plotSurvCure1Caption) _Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model._ Points are posterior medians and lines are 50% and 95% credible intervals.

```{r plotSurvCure1, echo=F, fig.width=7, fig.height=10, fig.cap="(ref:plotSurvCure1Caption)"}
tar_read(plotSurvCure1)
```

(ref:plotSurvCure2Caption) _Expected number of published papers and videos until tool use discovery, according to the survival component of the phylogenetic survival cure model._ Densities are full posterior distributions, points are posterior medians, and lines are 50% and 95% credible intervals.

```{r plotSurvCure2, echo=F, fig.width=7, fig.height=3, fig.cap="(ref:plotSurvCure2Caption)"}
tar_read(plotSurvCure2)
```

```{r echo=F}
tar_load(sumProbs)
```

The posterior probabilities shown in Figure \@ref(fig:plotSurvCure1) are estimated with uncertainty, so it is difficult to "identify" any particular species as an undetected tool user. Nevertheless, taking the sum of all the posterior probabilities for the `r nrow(plotSurvCure1$data %>% filter(ToolUse == "Absent"))` species without observed evidence of tool use, we can estimate that around `r printnum(median(sumProbs), digits = 0)` of those species are likely to be undetected tool users (median sum of probabilities = `r printnum(median(sumProbs), digits = 2)`, 95% CI [`r printnum(quantile(sumProbs, 0.025), digits = 2)` `r printnum(quantile(sumProbs, 0.975), digits = 2)`]). When combined with the species known to use tools, this implies that between 11% and 17% of extant parrot species may be tool users.

## Implications for the evolutionary drivers and origins of tool use

```{r echo=FALSE}
tar_load(postFull)
diff <- postFull$aP[,2] - postFull$aP[,1]
```

The predicted probabilities from our phylogenetic survival cure model have implications for inferences about the evolutionary drivers and origins of tool use in the parrot order. Regarding the drivers of tool use hypothesised in Figure \@ref(fig:plotDAG), the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = `r printnum(median(-postFull$bEQ))`, 95% CI [`r printnum(quantile(-postFull$bEQ, 0.025))` `r printnum(quantile(-postFull$bEQ, 0.975))`]; Figure \@ref(fig:plotSurvCure4)). This helps explain the ranking in Figure \@ref(fig:plotSurvCure1): the blue-eyed cockatoo has the largest relative brain size in the dataset. We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = `r printnum(median(diff))`, 95% CI [`r printnum(quantile(diff, 0.025))` `r printnum(quantile(diff, 0.975))`]). These results from the survival cure model differed from the results of models fitted to pre-video-survey and post-video-survey data without the survival cure component, which found no effect of relative brain size and no difference between feeding strategies, respectively (Supplementary Figure \@ref(fig:plotComparison)).

(ref:plotSurvCure4Caption) _Posterior predictions for the effects of feeding strategy and encephalisation quotient on the probability of tool use from the phylogenetic survival cure model._ In the left plot, points and lines represent posterior medians and 50% and 95% credible intervals, with densities representing full posterior distributions. In the right plot, the line and shaded area represents the posterior median regression line with 95% credible intervals. In both plots, individual species are coloured according to the presence / absence of tool use in the video survey and the scientific literature.

```{r plotSurvCure4, echo=F, fig.width=8, fig.height=4, fig.cap="(ref:plotSurvCure4Caption)"}
tar_read(plotSurvCure4)
```

Regarding the origins of tool use, we fitted exploratory ancestral state reconstruction models to the pre-video-survey data, the post-video-survey data, and the predicted probabilities from the phylogenetic survival cure model. The discoveries from our video survey and from our phylogenetic modelling increased the likelihood that tool use was present in the most recent common ancestor for several parrot genera. These include the amazon parrots native to the Americas (_Amazona_), the true white cockatoos and corellas found in South East Asia and Australasia (_Cacatua_), the kea and the kākā from New Zealand (_Nestor_), and the _Poicephalus_ genus native to Africa (Table \@ref(tab:tableASR); Supplementary Figures \@ref(fig:plotASR1) - \@ref(fig:plotASR3)). These findings suggest that species from each of these genera share their tool use capabilities via common descent from their respective common ancestors, rather than via independent evolution within each genus.

(ref:tableASRCaption) Estimated probabilities of tool use for most recent common ancestors of several parrot genera. _Probabilities estimated using exploratory ancestral state reconstruction models fitted to the pre-video-survey data, post-video-survey data, and predicted probabilities from the phylogenetic survival cure model._

```{r tableASR, echo=F, warning=F, message=F}
apa_table(
  tar_read(tableASR),
  caption = "(ref:tableASRCaption)",
  escape = FALSE
)
```

# Discussion

Since the earliest anecdotal reports of parrots using tools in the 1970s[@Goodall1971], only 11 parrot species (3% of all extant parrot species) have been documented as tool users in the scientific literature. Our study used crowdsourcing to identify 17 additional tool-using parrot species that are new to science, more than doubling the overall count to 28 species (7%). These species consisted of cockatoos (Cacatuidae), Old World parrots (Psittacinae), and neotropical parrots (Arinae).

We found strong phylogenetic signal in our extended dataset, demonstrating that the distribution of tool use across parrot species is affected by shared phylogenetic ancestry. This allowed us to use phylogenetic information, along with other variables, to infer the unobserved probabilities of tool use across the parrot order. Our phylogenetic survival cure model incorporated information on phylogenetic history, research effort, relative brain size, and feeding specialisation to rank parrot species that were most likely to be undetected tool users. The sum of probabilities from this model implied that between 15 and 41 of the species without observed evidence of tool use are likely to be undetected tool users, suggesting that the true proportion of tool users may be as high as 17%.

These findings have a number of important implications. First, our findings show that current research effort in the scientific literature is insufficient to capture the real world occurrence of parrot tool use. If the scientific literature had sampled the natural world sufficiently, we would expect to see close correspondence between those species reported as tool users in the literature and those species the public have filmed performing tool use. Instead, we discovered a large discrepancy between these two data sources, both in the prevalence of tool use and the species identified. This raises the possibility that insufficient research effort is a general issue across the scientific literature, both for tool use in other groups and for other rare behaviours.

Second, in terms of the evolution of tool use in parrots, our study challenges a key assumption made in the literature to date: that only a minority of parrots are tool users[@Auersperg2012;@Bastos2021;@Goodman2018;@Lambert2015;@OHara2021]. The paucity of evidence for tool use across parrots in the literature initially implied that tool use may have evolved independently in different parrot species. Our discovery of the widespread distribution of tool use across the parrot phylogeny, along with the strong phylogenetic signal in this expanded dataset, challenges this and suggests that, at least for some parrot clades, the capacity for tool use might be a homologous trait that has been evolutionarily conserved. Our exploratory ancestral state reconstruction analysis provides preliminary support for this hypothesis, revealing an increased probability of tool use among the most recent common ancestors for the _Amazona_, _Cacatua_, _Nestor_, and _Poicephalus_ genera. Even at this preliminary stage, our analysis therefore raises an alternative hypothesis for the observed tool use in _Cacatua_[@Auersperg2012;@OHara2021] and _Nestor_[@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;@Bastos2021;@Goodman2018], namely that tool behaviours have arisen due to the common ancestor being a tool user, rather than from behavioural innovation within a species.

Third, our results support existing theories of the drivers of tool use. We found that encephalisation was strongly positively related to the probability of tool use in our phylogenetic model, supporting previous theories linking relative brain size to increased tool innovation in birds[@Lefebvre1997;@Lefebvre2002;@Lefebvre2004] and primates[@Reader2002]. Nevertheless, we recognise that cross-species correlations between brain size and behaviour are challenging to interpret causally[@Healy2007;@Logan2018], and thus encourage further work on the specific neural correlates of technical intelligence in parrots (see e.g.[@Alvarez2020]). In our phylogenetic model, we also found that tool use was somewhat more likely among feeding generalists compared to feeding specialists, although this difference was uncertain. This trend supports previous suggestions that increased cognitive abilities and technical innovation rates are required to expand a generalist species' dietary niche[@HenkeVonDerMalsburg2020;@HenkeVonDerMalsburg2021;@Ducatez2015]. However, the trend contradicts theories linking tool use to dietary specialisation, whereby species eating specific foods that require extractive foraging have higher cognitive ability and are especially prone to using tools (reviewed in ref[@HenkeVonDerMalsburg2020]).

We believe that the observations of tool use in our video survey reflect intentional tool use, rather than accidental object manipulations or trained behaviours. In the crowdsourcing video survey, individual parrots often used tools slowly and repetitively over long periods of time, even across multiple different videos, suggesting that their behaviour was not accidental[@Sandor2020]. Moreover, for 60% of the species we report on, we found two or more videos of repetitive and sustained scratching by different individuals in separate households. Following the assumption that accidental tool use (e.g., briefly holding an object and attempting to scratch oneself simultaneously) is rare[@Auersperg2020], the repeated observation of the same tool use behaviours for scratching by multiple animals of the same species across multiple households suggests that these manipulations are intentional and recurring events rather than rare "accidents" and likely do not represent unusual stereotypies of a single individual. We also found little evidence to suggest that the tool use behaviours were trained or unintentionally cued by the birds' owners. Over half of the videos coded contained no evidence of human interference with the parrots' tool use aside from filming the behaviour. Humans only handed parrots their tools in two of the videos, and none of the videos featured owners directly rewarding tool use behaviours with food. Finally, and perhaps most importantly, the high levels of phylogenetic signal in our data provides strong evidence that the observations from our video survey reflect biologically-endowed capacities for tool use rather than accidents or trained behaviours, which would likely appear uniformly across the phylogeny.

While missing data imputation is becoming more common in phylogenetic analyses[@Debastiani2021], the important distinction between absence of evidence and evidence of absence has not been given as much attention. Our phylogenetic analysis provides one approach to this problem by distinguishing between true absences of tool use and absences of tool use due to a lack of research effort in the scientific literature or in crowdsourced videos. To achieve this, we explicitly modelled the measurement of the outcome variable along a research effort time series, such that species with lower research effort in the literature or in videos were likely to be censored. In line with our causal model, we also included relative brain size, feeding strategy, and phylogenetic history as predictors of unobserved tool use. We encourage researchers to test this model by directing future study efforts towards the parrot species with the highest probabilities of being undetected tool-users. Future work should also refine the causal model in Figure \@ref(fig:plotDAG) to provide more certain estimates of tool use probabilities, either by including additional predictor variables or modelling further causes of measurement error in the taxonomic record, such as species abundance and geographic accessibility[@Ducatez2014].

In conclusion, we have shown that the scientific literature has insufficiently captured the full distribution of tool use in the parrot order. Our crowdsourcing survey has more than doubled the number of known tool using parrot species from 11 to 28, and our phylogenetic inference suggested that the true proportion of parrot tool users could be as high as 17%. These discoveries have implications for theories of the evolutionary drivers and origins of tool use in parrots. Beyond parrot tool use, the crowdsourcing and phylogenetic methods used in this study have the potential to be applied to other rarely observed behaviours, including tool use in other taxa[@Hunt2013], rhythmic entrainment in birds[@Benichov2016;@Patel2009;@tenCate2016;@Wilson2016], teasing behaviours in primates[@Eckert2020], and tactical deception across the animal kingdom[@BroJorgensen2010;@Byrne1988;@Byrne1991]. We hope that these methods will continue to uncover a diverse array of ephemeral behaviours that have as yet gone undetected in the scientific literature.

# Methods

## Video searches and coding

Our video search was conducted on YouTube in July 2020. Search terms included "parrot using tool" and variants (e.g., "macaw using tool", "lorikeet using tool", "parakeet using tool"), "tool use in parrot", "parrot tool use", "parrot scratching itself" (included after we found several videos demonstrating self-care tool use in previous searches) and equivalent terms (e.g., "parrot preening itself", "parrot grooming itself", "parrot scratching"). For all species that did not display results including object manipulation or scratching behaviours, we also searched the species’ common name(s) + "tool use", as well as the species’ common name(s) + "scratching". We also searched for translations of the terms "parrot tool use" and "parrot scratching" in languages for all countries where bird ownership was reported as >5%[@GlobalGfkSurvey], namely, Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, Portuguese, and Mandarin.

When we found a relevant video, we also searched for similar content uploaded by the same person/channel. For each YouTube search conducted, we watched all relevant videos until we reached five consecutive videos that did not feature any parrots. At this point, we ended that search and initiated the next search. In line with previous recommendations[@Nelson2013], we planned to exclude any videos that consisted of four or more shots edited together so as to ensure the behaviours being observed were not edited or manipulated, but none of the videos obtained qualified for exclusion.

All videos featuring parrots manipulating objects were investigated for potential tool use or borderline tool use. We defined tool use as the manipulation of an unattached object as an extension of the beak or foot to achieve a goal towards another object, individual, or oneself[@Shumaker2011]. Borderline tool use was similarly defined, except that it involved the use of an object that was still attached to a substrate[@Seed2010]. For example, if individuals used a fallen feather or stick for self-scratching this was defined as tool use, but using one’s currently attached tail feathers or cage furnishings for the same purpose was defined as borderline tool use. Self-scratching had to involve slow and repeated movements of touching an object to one’s body (or, in the case of borderline tool use, rubbing repetitively against an attached object[@Sandor2020]).

All relevant videos were coded for video length, species, tool use presence (yes/borderline), tool use type (e.g., scratching, feeding), the object being used (e.g., feather, stick), tool use target, human interference with the action (talking or handing object to parrot, holding parrot), and the number of shots within each video. Our complete dataset also includes the name for each video, link, subject name, sex (as declared by owner, as most parrot species are not sexually dimorphic), publishing date, and dates found and coded.

## Data for parrot species

We collected data for 194 parrot species (Supplementary Figures \@ref(fig:plotPhylo2) - \@ref(fig:plotPhylo4)). We gathered feeding strategy data as a dichotomous variable ("generalist" or "specialist") from the EltonTraits ecological database[@Wilman2016]. As per the database, specialists were defined as species whose diet comprised at least 70% of a single food source. To calculate relative brain size, we collated data from the literature for all known body mass (g) and brain mass (g) values across parrots[@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;@Schuck2008;@Silva2017]. For all species for which we obtained body and brain mass data, we calculated the encephalisation quotient (EQ) using the following formula[@Jerison1973]: $BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))$. We found body mass and brain mass data for a total of 194 parrot species. This included all tool-using species in our video dataset, with the exception of three species: _Diopsittaca nobilis_, _Psittacara erythrogenys_, and _Coracopsis vasa_. For the latter, we used values for the closely related _Coracopsis nigra_. The other two species were excluded from the final dataset.

For modelling purposes, we coded research effort in both the scientific literature and the crowdsourced videos. For the scientific literature, we operationalised research effort as the number of papers published for each species' Latin name up to and including the first paper containing tool use for that species. If no tool use had been identified in the scientific literature for a species, then we coded the total number of papers published to date. We used the scientific database Scopus for coding the number of published papers. For the crowdsourced videos, we coded research effort as the number of search hits for each species on YouTube. If tool use had been identified on YouTube, we estimated the number of search hits when the first video of tool use was published on YouTube, assuming linear growth of search hits since the inception of YouTube. If tool use had not been identified, we used the current number of search hits.

For phylogenetic data, we used the phylogenetic tool at www.birdtree.org[@Jetz2012] to compile 1000 posterior draws of phylogenetic trees for 174 of the 194 parrot species for which both EQ and genomic data exist. A single maximum clade credibility tree was generated from these posterior draws for visualisation purposes. In our analyses, we iterated over posterior draws of the phylogeny to account for phylogenetic uncertainty.

## Phylogenetic signal

We used the _fitDiscrete_ function in the _ape_ R package[@Paradis2019] to calculate phylogenetic signal, for both the pre-survey and post-survey tool use data. We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.

## Causal model of tool use

To infer unobserved probabilities of tool use across parrots, we proposed a causal model of observed tool use (Figure \@ref(fig:plotDAG)). We assumed that observed tool use in the scientific literature and in the crowdsourced videos is caused by both the unobserved presence or absence of tool use and research effort, proxied by the number of papers published on a species and the number of videos published on a species. Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected. In addition, based on theory, we also assumed that unobserved tool use is caused by feeding strategy and relative brain size[@Lefebvre2004;@Lefebvre1997;@Lefebvre2002;@Ducatez2015;@Sol2005;@Overington2011;@HenkeVonDerMalsburg2020]. Finally, we assumed that shared phylogenetic history causes unobserved confounding and non-independence in unobserved tool use, feeding strategy, and relative brain size across the parrot phylogeny.

## Bayesian phylogenetic survival cure model

Given our proposed causal model, we constructed a statistical model to impute unobserved probabilities of tool use and test existing theories of the evolution of tool use in parrots. To understand the model, suppose that we have the following observed variables for parrot species $i$. For the scientific literature, we declare $\text{N}_{\text{Lit},i}$ as the number of papers published before and up to tool use identification for species $i$ (or, if tool use has not been identified, the total number of papers published for species $i$) and $\text{T}_{\text{Lit},i}$ as a binary variable stating whether (1) or not (0) tool use has yet been observed in the scientific literature for species $i$. For the crowdsourced videos, we declare $\text{N}_{\text{Vid},i}$ as the number of videos published before and up to tool use identification for species $i$ (or, if tool use has not been identified, the total number of videos published for species $i$) and $\text{T}_{\text{Vid},i}$ as a binary variable stating whether (1) or not (0) tool use has yet been observed in the crowdsourced videos for species $i$. Additionally, $\text{F}_i$ and $\text{EQ}_i$ are feeding strategy and encephalisation quotient values for species $i$ and we have a phylogenetic distance matrix $D$ that describes the patristic distances between all parrot species.

We assume that species $i$ is a non-tool-user (i.e. "cured") with some probability $p_i$. We also assume that tool use is identified in the scientific literature and the crowdsourced videos at constant rates $\lambda_{\text{Lit}}$ and $\lambda_{\text{Vid}}$ following exponential survival functions. Given these assumptions, we can then describe the different ways in which variables $\text{N}_\text{Lit}$ and $\text{N}_\text{Vid}$ can be distributed. Focusing on the scientific literature, if tool use has been observed ($\text{T}_{\text{Lit},i} = 1$), then the likelihood for $\text{N}_{\text{Lit},i}$ is:

\begin{align}
\text{Pr}(\text{N}_{\text{Lit},i}|\text{T}_{\text{Lit},i} = 1,p_i,\lambda_\text{Lit}) = (1-p_i)\cdot\text{Exponential}(\text{N}_{\text{Lit},i}|\lambda_\text{Lit})
\end{align}

On the other hand, if tool use has not yet been observed ($\text{T}_{\text{Lit},i} = 0$), there are two ways that the outcome variable could have been realised. First, the species could be a non-tool-user with probability $p_i$. Second, the species could be a tool-user with probability ($1 - p_i$) that has been censored and has not had its tool use measured yet. Together, then, the likelihood for $\text{N}_{\text{Lit},i}$ is:

\begin{align}
\text{Pr}(\text{N}_{\text{Lit},i}|\text{T}_{\text{Lit},i} = 0,p_i,\lambda_\text{Lit}) = p_i + ((1-p_i)\cdot\text{Exponential-CCDF}(\text{N}_{\text{Lit},i}|\lambda_\text{Lit}))
\end{align}

The Exponential-CCDF function allows for the censored nature of the data. The same data generating process is assumed to underlie the crowdsourced videos.

We define the mixture likelihood $\text{SurvivalCure}$ as the distribution above, with parameters $p$ (the probability of being a "cured" non-tool-user) and $\lambda$ (the rate of the exponential distribution). We use an Ornstein-Uhlenbeck Gaussian process[@McElreath2020] to model phylogenetic covariance. Below, we specify the full model with priors:

\begin{align}
N_{\text{Lit},i} &\sim \text{SurvivalCure}(\lambda_{\text{Lit},i}, p_{i}) \\
N_{\text{Vid},i} &\sim \text{SurvivalCure}(\lambda_{\text{Vid},i}, p_{i}) \nonumber \\
\lambda_{\text{Lit},i} &= 1 / \text{exp}(\gamma_\text{Lit}) \nonumber \\
\lambda_{\text{Vid},i} &= 1 / \text{exp}(\gamma_\text{Vid}) \nonumber \\
\text{logit}(p_{i}) &= \alpha_{\text{FEEDING}[i]} + \beta\text{EQ}_{i} +  k_{\text{SPECIES}[i]} \nonumber \\
\begin{pmatrix}k_{1}\\k_{2}\\...\\k_{n}\\\end{pmatrix}
&\sim \text{MVNormal}
\begin{pmatrix}\begin{pmatrix}0\\0\\...\\0\\\end{pmatrix},\bf{K}\end{pmatrix} \nonumber \\
\bf{K}_{ij} &= \eta^2\text{exp}(-\rho^2D_{ij}) \nonumber \\
\gamma_\text{Lit}, \gamma_\text{Vid}, \alpha_{1,2}, \beta &\sim \text{Normal(0, 1)} \nonumber \\
\eta^2, \rho^2 &\sim \text{Exponential(0.5)} \nonumber
\end{align}

The priors for this model produce reasonable prior predictions of the probabilities of tool use for each parrot species (Supplementary Figure \@ref(fig:plotSurvCure7)), but a sensitivity analysis revealed that the ranking and posterior probabilities reported in the main text were robust to modifying these priors (Supplementary Figure \@ref(fig:plotSurvCure8)). We estimated the posterior distribution of this model using Hamiltonian Monte Carlo as implemented in Stan version 2.26.1[@Stan2020]. We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty. R-hat values and effective sample sizes suggested that the model converged normally. Trace plots are reported in Supplementary Figure \@ref(fig:plotTrace).

To validate our method, we fitted the model to 100 simulated datasets with known parameters. The model was able to successfully recover those parameters (Supplementary Figure \@ref(fig:plotSurvCureSim)). We also ran a leave-one-species-out exercise to ensure that we could accurately predict known tool users. We repeated this approach for each known tool user by setting observed tool use to zero. Cross-validation results are reported in the main text.

## Ancestral state reconstruction

To determine whether the identification of novel tool-using species has implications for our understanding of the evolutionary origins of tool use in parrots, we fitted three exploratory ancestral state reconstruction models. We used the _ancThresh_ function from the _phytools_ R package[@phytools], iterating the function over 100 posterior parrot phylogenies. This function estimates discrete ancestral states by assuming the evolution of a latent continuous variable following an Ornstein-Uhlenbeck process. We fitted this model to three different outcome variables: (_i_) presence vs. absence of tool use in scientific literature only, (_ii_) presence vs. absence of tool use in literature and/or videos, and (_iii_) the median predicted probabilities of tool use from the phylogenetic survival cure model.

## Reproducibility

All analyses were conducted in R v4.2.1.[@RCoreTeam]. Visualisations were produced using the _ggplot2_[@Wickham2016] and _cowplot_[@Wilke2020] packages. The manuscript was reproducibly generated using the _targets_[@Landau2021] and _papaja_[@Aust2022] packages. Code to reproduce all analyses and figures can be found here: https://github.com/ScottClaessens/phyloParrot

\newpage
\nolinenumbers

# Acknowledgements

This project was made possible through the support of a grant from the Templeton World Charity Foundation (A.H.T., X.J.N.) and a Prime Minister’s McDiarmid Emerging Scientist Prize (A.H.T.). The authors would like to thank Daniel Sol for providing feedback on a previous version of the manuscript.

# Author Contributions

All authors contributed to the conceptualisation of the paper. A.P.M.B., X.J.N., and A.H.T. developed the video search methodology. S.C., D.W., and Q.A.D. developed the statistical models and analysed the data. All the authors wrote the manuscript and approved the final version for submission.

# Competing Interests

The authors declare no competing interests.

# Data Availability

All data used in this study are publicly available on GitHub: https://github.com/ScottClaessens/phyloParrot

# Code Availability

All code to reproduce the analyses in this study are publicly available on GitHub: https://github.com/ScottClaessens/phyloParrot

\newpage

# References

\begingroup

<div id="refs" custom-style="Bibliography"></div>
\endgroup

\newpage
\vspace*{60mm}

```{r child = "appendix.Rmd"}
```

### 2023-08-14 manuscript.tex
first commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling\newline\indent Word count: 4273 words excluding Methods (Methods: 1792 words)}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[normalem]{ulem}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{hyperref}
\usepackage{setspace}
\raggedbottom
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\AtBeginEnvironment{tablenotes}{\doublespacing}
\captionsetup[table]{font={stretch=1,small}}
\captionsetup[figure]{font={stretch=1,small}}
\nolinenumbers
\note{\raggedright † indicates shared first authorship, ‡ indicates shared senior authorship \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand. \text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}} \par This working paper has not yet been peer-reviewed.}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare},
  pdfauthor={Amalia P. M. Bastos†,1,2, Scott Claessens*†,2, Ximena J. Nelson3, David Welch4, Quentin D. Atkinson‡,2, \& Alex H. Taylor‡,2,3,5,6},
  pdflang={en-EN},
  pdfkeywords={tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare}
\author{Amalia P. M. Bastos\textsuperscript{†,1,2}, Scott Claessens\textsuperscript{*†,2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, Quentin D. Atkinson\textsuperscript{‡,2}, \& Alex H. Taylor\textsuperscript{‡,2,3,5,6}}
\date{}

\shorttitle{Parrot tool use}

\affiliation{\vspace{0.5cm}\textsuperscript{1} \footnotesize Department of Psychological \& Brain Sciences, Johns Hopkins University, Baltimore, MD, United States\\\textsuperscript{2} \footnotesize School of Psychology, University of Auckland, Auckland, New Zealand\\\textsuperscript{3} \footnotesize School of Biological Sciences, University of Canterbury, Christchurch, New Zealand\\\textsuperscript{4} \footnotesize School of Computer Science, University of Auckland, Auckland, New Zealand\\\textsuperscript{5} \footnotesize ICREA, Pg. Lluís Companys 23, Barcelona, Spain\\\textsuperscript{6} \footnotesize Institute of Neuroscience, Universitat Autònoma de Barcelona, Barcelona, Spain}

\abstract{%
Studying the prevalence of putatively rare behaviours, such as tool use, is challenging because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort. Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to approximate actual rates of a rarely observed behaviour based on limited data, targeting tool use in parrots. Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%). Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11\% and 17\% of extant parrot species may be tool users. These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait. Overall, our findings challenge the assumption that current sampling effort captures the full distribution of putatively rare animal behaviours. Combining our sampling and analysis methods offers a fruitful approach for investigating the distribution, drivers, and origins of other rare behaviours.
}

\begin{document}
\maketitle

\linenumbers

Our understanding of the evolution of animal behaviour is built on the assumption that we have access to sufficient data\textsuperscript{1--3}. However, this is not always the case. Data on behaviours that are rare, fleeting, or otherwise difficult to observe are likely to be patchy and incomplete\textsuperscript{4,5}. Among species for which such behaviours have not been observed, it can be difficult to differentiate between cases in which the species is truly incapable of producing the behaviour and cases in which the species is capable of producing the behaviour but the behaviour has not yet been observed. Such a distinction can be critical for drawing conclusions about the rarity and evolution of the behaviour in question.

Comparative work on the evolution of tool use is a paradigmatic example of this issue. The initial discoveries of tool use in chimpanzees\textsuperscript{6}, birds\textsuperscript{7}, dolphins\textsuperscript{8}, and octopuses\textsuperscript{9} occurred decades after significant advances on other more easily measurable aspects of their biology. Since these initial discoveries, scholars have used the distribution of reported tool use across species to make various claims about the evolutionary drivers of tool use behaviours. For example, based on the observation that bird species with reported tool use tended to have larger brains, researchers have identified higher relative brain size as a likely precondition for tool using capabilities\textsuperscript{10--12}. These researchers argue that larger brains are better able to integrate visual and somatosensory information when innovating novel behaviours, such as tool use, in changing environments\textsuperscript{13,14}. Similarly, researchers have used existing reports of tool use in birds to debate the roles of generalist versus specialist feeding strategies in driving the evolution of tool use, with some arguing that feeding generalists require technical innovations to expand their dietary niche\textsuperscript{13,15,16} and others arguing that feeding specialists require technical innovations for extractive foraging of specific foods\textsuperscript{17,18}.

However, before we can make claims of this kind, we need to know whether current research effort in the literature is sufficient for robust conclusions to be drawn about the evolution of tool use. In fact, evidence suggests that research effort is often systematically biased towards particular taxonomic groups, parts of the world that are easy to access, and species with life history traits that make them easier to study, such as larger distribution ranges and population sizes\textsuperscript{19}. This is a crucial limitation because insufficient observation may lead researchers to miss true instances of tool behaviours and thus draw premature conclusions about the evolutionary drivers and origins of tool use. While researchers have attempted to deal with this problem by controlling for the number of scientific papers published on different species, previous work has not yet attempted to quantify and explicitly model the relationship between actual tool-using behaviour and what is reported in the scientific literature. If more tool-using species exist than previously thought, this could have important implications for theories of the evolutionary drivers and origins of tool use and, more generally, for our understanding of how rare this behaviour actually is.

One potentially powerful method for quantifying actual rates of rare animal behaviours is crowdsourcing\textsuperscript{20}. In a crowdsourcing study, researchers collect reports from the general public and/or collate and analyse videos posted on social media platforms. This citizen science approach has been widely used in ecology to monitor the distributional patterns of species\textsuperscript{21}, but has also recently been used to uncover a variety of rare animal behaviours, including interspecies play in dogs\textsuperscript{20}, novel problem-solving behaviours in horses\textsuperscript{22}, and socially-learned foraging innovations in cockatoos\textsuperscript{23,24}. By casting the net wider than the scientific literature, the crowdsourcing method can provide an indication of the tool-using species that the literature might be missing.

Even after using this crowdsourcing approach, some tool-users could \emph{still} remain unobserved. An additional approach to identify these unobserved species is to specify a causal model of the process that generates the observed data. We propose one such causal model in Figure \ref{fig:plotDAG}. In this model, we assume that the presence of tool use in the scientific literature (or in crowdsourced reports) is caused by both unobserved tool use capabilities and the number of published studies (or the number of crowdsourced reports) for any given species. Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected. Furthermore, based on existing theories of the evolution of tool use\textsuperscript{10--18}, we propose that the unobserved presence or absence of tool use is additionally caused by relative brain size, feeding strategy, and shared phylogenetic ancestry. Expressing this causal model as a statistical model can suggest further species which are likely to be unobserved tool-users and, simultaneously, test existing theories of the evolutionary drivers of tool use without incorrectly assuming that absence of evidence is evidence of absence.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotDAG-1.pdf}
\caption{\label{fig:plotDAG}\emph{Causal model of observed tool use.} Directed acyclic graph of the causal relationships between observed tool use and other variables. Available scientific data on tool use is caused both by unobserved tool use presence and scientific research effort (i.e., number of publications). Available crowdsourced data on tool use is caused both by unobserved tool use presence and crowdsourcing effort (i.e., number of crowdsourced reports). According to theory, unobserved tool use presence should be caused by relative brain size (encephalisation quotient) and feeding strategy (generalist vs.~specialist). These variables all share unobserved confounds generated by shared phylogenetic history. Grey circles indicate unobserved variables.}
\end{figure}

Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool use in the parrot order. We focus on tool use in parrots for a number of reasons. First, the scientific literature suggests that only a small proportion of extant parrot species (11 out of 398\textsuperscript{25}; 3\%) use tools\textsuperscript{10,26--38} (note that we do not include in this count species that have been previously shown to use touchscreen devices as these behaviours were explicitly trained\textsuperscript{39}). Parrot tool use thus provides an ideal test case for examining how robust sampling is in the scientific literature. Second, parrots are highly popular as pets. Over 70\% of all extant parrot species are bred in the aviculture industry and kept as pets worldwide\textsuperscript{40--46}, enabling us to leverage the power of crowdsourcing on a social media platform to search for evidence of tool use\textsuperscript{20}. Third, detailed data on relative brain sizes\textsuperscript{47--52}, feeding strategies\textsuperscript{53}, and shared ancestry\textsuperscript{54} exist for parrots, allowing us to fit the statistical model implied by Figure \ref{fig:plotDAG} to the entire parrot order.

We first present the results from our crowdsourcing survey, in which we collated videos of tool use in parrots from an online video platform. This survey reveals a number of previously unidentified tool-using parrot species, which we map onto the phylogeny of the parrot order. We then describe our statistical model in more detail, and use it to (\emph{i}) rank further parrot species that are likely unobserved tool users and (\emph{ii}) re-examine key hypotheses regarding the evolutionary drivers and origins of tool use in parrots.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{crowdsourcing-video-survey}{%
\subsection{Crowdsourcing video survey}\label{crowdsourcing-video-survey}}

We surveyed the social media platform YouTube for video evidence of tool use in parrots (see Methods for detailed search criteria). In our search, we defined ``true'' tool use behaviour as the manipulation of an unattached object to achieve a goal\textsuperscript{55}, while ``borderline'' tool use involved the use of an object that was still attached to a substrate\textsuperscript{56}.

In total, we found 116 videos of 104 individuals from 25 parrot species performing either true tool use (100 videos of 89 individuals from 22 species) or borderline tool use (16 videos of 16 individuals from 7 species). All videos featured pet parrots in captive settings. In 68 of these videos, owners did not appear to interfere with the subjects' actions. In 43 videos, there was potential interference, either from the owners being in close physical contact with the bird (e.g., bird perching on hand), talking to the bird, or handing it the tool (which occurred in only two videos). We could not establish the degree of interference in the remaining 5 videos, as sound had been removed or was substituted by music. None of the videos featured owners directly rewarding tool use behaviours with food. All borderline tool use cases were excluded from further analyses.

Of the 22 parrot species performing true tool use, 13 were represented in our video survey by two or more individuals over multiple independent observations. True tool use always involved the subject using an object for self-scratching (95 videos involved scratching the head and/or neck). The most common tool (53 videos) was a moulted feather. Human-made objects (e.g., pens, spoons, pieces of wood, cardboard) were also common.

According to YouTube video descriptions and owner comments, 45 of the individuals performing true tool use were males and 18 were females. No sex information was provided for the remaining 26 individuals. As owners provided no information on whether sex had been established through genetic testing, and sexual dimorphism in parrots is rare\textsuperscript{57,58}, we could not typically ascertain if descriptions were accurate. It is unclear if the disproportionately large number of males in the sample is a consequence of owners more readily assuming their parrots are male when they have not been genetically tested, owners being more likely to own or film male parrots, or male parrots exhibiting more true tool use behaviours than female parrots.

Figure \ref{fig:plotPhylo1} maps the findings from the video survey onto a maximum clade credibility phylogeny for the parrot order, plotted alongside species previously identified in the scientific literature. Before the video survey, 11 parrot species (3\%) had been identified as tool users in the scientific literature. Across our video survey, we observed true tool use in 22 species, 5 of which overlapped with the scientific literature and 17 of which were novel species. All of the species identified in the video survey were cockatoos (Cacatuidae), Old World parrots (Psittacinae), or neotropical parrots (Arinae). The most common species in our survey, accounting for 41 videos from 37 individuals, was the green-cheeked conure (\emph{Pyrrhura molinae}). In accordance with the scientific literature, the video survey found no evidence of tool use in any species of Psittaculidae, despite this family containing some of the most commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet species. Combining both the video survey and the scientific literature, we can thus identify 28 tool-using parrot species overall (7\%), compared to the 11 previously reported.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotPhylo1-1.pdf}
\caption{\label{fig:plotPhylo1}\emph{Results of crowdsourcing video survey and phylogenetic survival cure modelling mapped onto a maximum clade credibility phylogeny of the parrot order.} Purple tips indicate species observed in the scientific literature and in the video survey. Blue tips indicate species observed only in the scientific literature. Orange tips indicate species observed only in the video survey (note that three species observed only in the video survey are not present in the phylogeny due to a lack of genomic data: \emph{Psittacara erythrogenys}, \emph{Psittacus timneh}, and \emph{Aratinga nenday}). Yellow tips indicate the top ten most likely tool-using species from our phylogenetic survival cure model which were not observed in the scientific literature or the video survey. All other tips are labelled as absent (grey).}
\end{figure}

The identification of new tool-using species in our video survey increases the extent to which phylogeny can explain the distribution of tool use in the parrot order. We estimated phylogenetic signal (Pagel's \(\lambda\)) of tool use using both the pre-video-survey and post-video-survey data. Pagel's \(\lambda\) varies between 0 and 1, where 0 implies that the distribution of a trait across species is unexplained by phylogenetic relatedness and 1 implies that the distribution of a trait across species is fully explained by phylogeny. Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's \(\lambda\) of 0.60 (95\% credible interval {[}0.00 0.90{]}). This estimate was moderate-to-strong, but highly uncertain. In comparison, combining the evidence from both the literature and the video survey (post-video-survey data; 28 tool-using species) resulted in a stronger and more certain estimate of phylogenetic signal. With these data, we estimated Pagel's \(\lambda\) = 0.65 (95\% CI {[}0.50 0.77{]}). Thus, the results of our video survey increase the extent to which the distribution of tool use across parrot species can be explained by shared phylogenetic ancestry. This suggests that we can potentially use phylogenetic information, along with other variables, to identify further tool-using parrot species that may remain undetected.

\hypertarget{phylogenetic-survival-cure-model}{%
\subsection{Phylogenetic survival cure model}\label{phylogenetic-survival-cure-model}}

In addition to the 28 tool-using species identified in the literature and our video survey, we fitted a Bayesian phylogenetic survival cure model to rank further species that are likely to be undetected tool-users (i.e., tool-using species with no tool use reported in the literature or in crowdsourced videos).

Survival cure models are often used in the medical sciences to analyse the time to some event, such as cancer relapse, with censored patient data\textsuperscript{59}. The data are right-censored because some patients have relapsed when they are measured, and some have not yet relapsed when they are measured (i.e., they are censored). The cure aspect of these models comes from an additional assumption that a certain proportion of the population is ``cured'' and can never relapse, no matter how long we measure them for.

Our tool use problem has the same features. We are modelling a time-to-event; specifically, the amount of ``time'' (i.e., observation opportunities measured as the number of published papers or crowdsourced videos) until tool use is identified. This is right-censored data, because many species will not have had tool use identified when we measure them. Moreover, we can assume that a certain proportion of the population is ``cured'' -- that is, they are not tool users, and so we will never identify tool use for them, no matter how long we measure them for.

In our model, we infer the tool-using status of each species by allowing each species to have their own probability of being ``cured'' (i.e., not a tool user). Following our causal model (Figure \ref{fig:plotDAG}), we predict these probabilities based on feeding strategy, encephalisation quotient, and phylogenetic history (see Methods for full model). The model additionally takes research effort into account by allowing that, among species for which tool use is unobserved, all else being equal those with fewer published papers and fewer video search hits have a higher probability of being undetected tool users (Supplementary Figure \ref{fig:plotSurvCure3}).

We found that this phylogenetic survival cure model was able to adequately distinguish between species with and without evidence for tool use, with an area-under-the-curve classification statistic of 0.95 (Supplementary Figure \ref{fig:plotSurvCure9}). To further estimate the accuracy of the model's predictions, we also used a leave-one-species-out approach with known tool users. For each of the 25 tool-using species that were represented on the phylogeny and for which we had brain size and genomic data (we lacked data for three tool-using species), we fitted the model to a modified dataset which set tool use to be absent for the target species in both the scientific literature and the video survey. Across 25 cross-validation models, 18 models (72\%) continued to predict the target species as having a median posterior probability of tool use that was within the range of all other tool users. This classification rate was greater than the baseline classification rate of 26\% for species without evidence of tool use in the full model (38 of 149 species without evidence of tool use had a median posterior probability of tool use that was within the range of the tool-using species). Together, the area-under-the-curve statistic and the leave-one-species-out approach suggest that the model is able to adequately classify known tool users, with some error.

Figure \ref{fig:plotSurvCure1} visualises the ranked posterior probabilities of tool use from the phylogenetic survival cure model for all parrot species. As expected, the known tool users are ranked towards the top of this list. However, several ``tool use absent'' species also rank highly on the list, despite not being identified as tool users in the scientific literature or in our video survey. In fact, according to the model, the most likely tool user is a species for which tool use is unobserved in our data: the blue-eyed cockatoo (\emph{Cacatua opthalmica}). This species is endemic to Papua New Guinea and is relatively understudied, with only 6 published papers and 596 video search hits, which is fewer than the model expects are necessary to discover tool use when it is present (Figure \ref{fig:plotSurvCure2}). This species is also found in the \emph{Cacatua} genus, a clade containing several known tool users. This prediction makes sense given the high phylogenetic signal for tool use reported by the model (Supplementary Figures \ref{fig:plotSurvCure5} and \ref{fig:plotSurvCure6}). Beyond the blue-eyed cockatoo, other highly ranked species without observed evidence of tool use are the Meyer's parrot (\emph{Poicephalus meyeri}), the golden parakeet (\emph{Guaruba guarouba}), the long-billed corella (\emph{Cacatua tenuirostris}), the Solomons cockatoo (\emph{Cacatua ducorpsii}), the red-fronted parrot (\emph{Poicephalus gulielmi}), the Cape parrot (\emph{Poicephalus robustus}), the yellow-eared parrot (\emph{Ognorhynchus icterotis}), the red-vented cockatoo (\emph{Cacatua haematuropygia}), and the gang-gang cockatoo (\emph{Callocephalon fimbriatum}). Figure \ref{fig:plotPhylo1} plots these species on the parrot phylogeny, using the top ten highest ranked species without observed evidence of tool use as an abitrary cutoff for visualisation purposes.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure1-1.pdf}
\caption{\label{fig:plotSurvCure1}\emph{Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model.} Points are posterior medians and lines are 50\% and 95\% credible intervals.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure2-1.pdf}
\caption{\label{fig:plotSurvCure2}\emph{Expected number of published papers and videos until tool use discovery, according to the survival component of the phylogenetic survival cure model.} Densities are full posterior distributions, points are posterior medians, and lines are 50\% and 95\% credible intervals.}
\end{figure}

The posterior probabilities shown in Figure \ref{fig:plotSurvCure1} are estimated with uncertainty, so it is difficult to ``identify'' any particular species as an undetected tool user. Nevertheless, taking the sum of all the posterior probabilities for the 149 species without observed evidence of tool use, we can estimate that around 26 of those species are likely to be undetected tool users (median sum of probabilities = 25.68, 95\% CI {[}15.15 41.33{]}). When combined with the species known to use tools, this implies that between 11\% and 17\% of extant parrot species may be tool users.

\hypertarget{implications-for-the-evolutionary-drivers-and-origins-of-tool-use}{%
\subsection{Implications for the evolutionary drivers and origins of tool use}\label{implications-for-the-evolutionary-drivers-and-origins-of-tool-use}}

The predicted probabilities from our phylogenetic survival cure model have implications for inferences about the evolutionary drivers and origins of tool use in the parrot order. Regarding the drivers of tool use hypothesised in Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = 1.12, 95\% CI {[}0.39 2.00{]}; Figure \ref{fig:plotSurvCure4}). This helps explain the ranking in Figure \ref{fig:plotSurvCure1}: the blue-eyed cockatoo has the largest relative brain size in the dataset. We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = 0.33, 95\% CI {[}-1.13 1.76{]}). These results from the survival cure model differed from the results of models fitted to pre-video-survey and post-video-survey data without the survival cure component, which found no effect of relative brain size and no difference between feeding strategies, respectively (Supplementary Figure \ref{fig:plotComparison}).

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure4-1.pdf}
\caption{\label{fig:plotSurvCure4}\emph{Posterior predictions for the effects of feeding strategy and encephalisation quotient on the probability of tool use from the phylogenetic survival cure model.} In the left plot, points and lines represent posterior medians and 50\% and 95\% credible intervals, with densities representing full posterior distributions. In the right plot, the line and shaded area represents the posterior median regression line with 95\% credible intervals. In both plots, individual species are coloured according to the presence / absence of tool use in the video survey and the scientific literature.}
\end{figure}

Regarding the origins of tool use, we fitted exploratory ancestral state reconstruction models to the pre-video-survey data, the post-video-survey data, and the predicted probabilities from the phylogenetic survival cure model. The discoveries from our video survey and from our phylogenetic modelling increased the likelihood that tool use was present in the most recent common ancestor for several parrot genera. These include the amazon parrots native to the Americas (\emph{Amazona}), the true white cockatoos and corellas found in South East Asia and Australasia (\emph{Cacatua}), the kea and the kākā from New Zealand (\emph{Nestor}), and the \emph{Poicephalus} genus native to Africa (Table \ref{tab:tableASR}; Supplementary Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}). These findings suggest that species from each of these genera share their tool use capabilities via common descent from their respective common ancestors, rather than via independent evolution within each genus.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tableASR}Estimated probabilities of tool use for most recent common ancestors of several parrot genera. \emph{Probabilities estimated using exploratory ancestral state reconstruction models fitted to the pre-video-survey data, post-video-survey data, and predicted probabilities from the phylogenetic survival cure model.}}

\begin{tabular}{llll}
\toprule
Genus & \multicolumn{1}{c}{Pre-video-survey} & \multicolumn{1}{c}{Post-video-survey} & \multicolumn{1}{c}{Survival cure probabilities}\\
\midrule
\textit{Amazona} & 0.06, 95\% CI [0.01 0.17] & 0.21, 95\% CI [0.04 0.66] & 0.48, 95\% CI [0.05 0.84]\\
\textit{Cacatua} & 0.08, 95\% CI [0.03 0.20] & 0.17, 95\% CI [0.03 0.45] & 0.81, 95\% CI [0.23 0.99]\\
\textit{Nestor} & 0.11, 95\% CI [0.05 0.29] & 0.21, 95\% CI [0.12 0.37] & 0.53, 95\% CI [0.29 0.66]\\
\textit{Poicephalus} & 0.06, 95\% CI [0.02 0.11] & 0.19, 95\% CI [0.12 0.41] & 0.72, 95\% CI [0.16 0.90]\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Since the earliest anecdotal reports of parrots using tools in the 1970s\textsuperscript{60}, only 11 parrot species (3\% of all extant parrot species) have been documented as tool users in the scientific literature. Our study used crowdsourcing to identify 17 additional tool-using parrot species that are new to science, more than doubling the overall count to 28 species (7\%). These species consisted of cockatoos (Cacatuidae), Old World parrots (Psittacinae), and neotropical parrots (Arinae).

We found strong phylogenetic signal in our extended dataset, demonstrating that the distribution of tool use across parrot species is affected by shared phylogenetic ancestry. This allowed us to use phylogenetic information, along with other variables, to infer the unobserved probabilities of tool use across the parrot order. Our phylogenetic survival cure model incorporated information on phylogenetic history, research effort, relative brain size, and feeding specialisation to rank parrot species that were most likely to be undetected tool users. The sum of probabilities from this model implied that between 15 and 41 of the species without observed evidence of tool use are likely to be undetected tool users, suggesting that the true proportion of tool users may be as high as 17\%.

These findings have a number of important implications. First, our findings show that current research effort in the scientific literature is insufficient to capture the real world occurrence of parrot tool use. If the scientific literature had sampled the natural world sufficiently, we would expect to see close correspondence between those species reported as tool users in the literature and those species the public have filmed performing tool use. Instead, we discovered a large discrepancy between these two data sources, both in the prevalence of tool use and the species identified. This raises the possibility that insufficient research effort is a general issue across the scientific literature, both for tool use in other groups and for other rare behaviours.

Second, in terms of the evolution of tool use in parrots, our study challenges a key assumption made in the literature to date: that only a minority of parrots are tool users\textsuperscript{30,31,34,37,38}. The paucity of evidence for tool use across parrots in the literature initially implied that tool use may have evolved independently in different parrot species. Our discovery of the widespread distribution of tool use across the parrot phylogeny, along with the strong phylogenetic signal in this expanded dataset, challenges this and suggests that, at least for some parrot clades, the capacity for tool use might be a homologous trait that has been evolutionarily conserved. Our exploratory ancestral state reconstruction analysis provides preliminary support for this hypothesis, revealing an increased probability of tool use among the most recent common ancestors for the \emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera. Even at this preliminary stage, our analysis therefore raises an alternative hypothesis for the observed tool use in \emph{Cacatua}\textsuperscript{30,38} and \emph{Nestor}\textsuperscript{26--29,31,34}, namely that tool behaviours have arisen due to the common ancestor being a tool user, rather than from behavioural innovation within a species.

Third, our results support existing theories of the drivers of tool use. We found that encephalisation was strongly positively related to the probability of tool use in our phylogenetic model, supporting previous theories linking relative brain size to increased tool innovation in birds\textsuperscript{10--12} and primates\textsuperscript{61}. Nevertheless, we recognise that cross-species correlations between brain size and behaviour are challenging to interpret causally\textsuperscript{3,4}, and thus encourage further work on the specific neural correlates of technical intelligence in parrots (see e.g.\textsuperscript{62}). In our phylogenetic model, we also found that tool use was somewhat more likely among feeding generalists compared to feeding specialists, although this difference was uncertain. This trend supports previous suggestions that increased cognitive abilities and technical innovation rates are required to expand a generalist species' dietary niche\textsuperscript{15,17,63}. However, the trend contradicts theories linking tool use to dietary specialisation, whereby species eating specific foods that require extractive foraging have higher cognitive ability and are especially prone to using tools (reviewed in ref\textsuperscript{17}).

We believe that the observations of tool use in our video survey reflect intentional tool use, rather than accidental object manipulations or trained behaviours. In the crowdsourcing video survey, individual parrots often used tools slowly and repetitively over long periods of time, even across multiple different videos, suggesting that their behaviour was not accidental\textsuperscript{64}. Moreover, for 60\% of the species we report on, we found two or more videos of repetitive and sustained scratching by different individuals in separate households. Following the assumption that accidental tool use (e.g., briefly holding an object and attempting to scratch oneself simultaneously) is rare\textsuperscript{65}, the repeated observation of the same tool use behaviours for scratching by multiple animals of the same species across multiple households suggests that these manipulations are intentional and recurring events rather than rare ``accidents'' and likely do not represent unusual stereotypies of a single individual. We also found little evidence to suggest that the tool use behaviours were trained or unintentionally cued by the birds' owners. Over half of the videos coded contained no evidence of human interference with the parrots' tool use aside from filming the behaviour. Humans only handed parrots their tools in two of the videos, and none of the videos featured owners directly rewarding tool use behaviours with food. Finally, and perhaps most importantly, the high levels of phylogenetic signal in our data provides strong evidence that the observations from our video survey reflect biologically-endowed capacities for tool use rather than accidents or trained behaviours, which would likely appear uniformly across the phylogeny.

While missing data imputation is becoming more common in phylogenetic analyses\textsuperscript{66}, the important distinction between absence of evidence and evidence of absence has not been given as much attention. Our phylogenetic analysis provides one approach to this problem by distinguishing between true absences of tool use and absences of tool use due to a lack of research effort in the scientific literature or in crowdsourced videos. To achieve this, we explicitly modelled the measurement of the outcome variable along a research effort time series, such that species with lower research effort in the literature or in videos were likely to be censored. In line with our causal model, we also included relative brain size, feeding strategy, and phylogenetic history as predictors of unobserved tool use. We encourage researchers to test this model by directing future study efforts towards the parrot species with the highest probabilities of being undetected tool-users. Future work should also refine the causal model in Figure \ref{fig:plotDAG} to provide more certain estimates of tool use probabilities, either by including additional predictor variables or modelling further causes of measurement error in the taxonomic record, such as species abundance and geographic accessibility\textsuperscript{19}.

In conclusion, we have shown that the scientific literature has insufficiently captured the full distribution of tool use in the parrot order. Our crowdsourcing survey has more than doubled the number of known tool using parrot species from 11 to 28, and our phylogenetic inference suggested that the true proportion of parrot tool users could be as high as 17\%. These discoveries have implications for theories of the evolutionary drivers and origins of tool use in parrots. Beyond parrot tool use, the crowdsourcing and phylogenetic methods used in this study have the potential to be applied to other rarely observed behaviours, including tool use in other taxa\textsuperscript{67}, rhythmic entrainment in birds\textsuperscript{68--71}, teasing behaviours in primates\textsuperscript{72}, and tactical deception across the animal kingdom\textsuperscript{73--75}. We hope that these methods will continue to uncover a diverse array of ephemeral behaviours that have as yet gone undetected in the scientific literature.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{video-searches-and-coding}{%
\subsection{Video searches and coding}\label{video-searches-and-coding}}

Our video search was conducted on YouTube in July 2020. Search terms included ``parrot using tool'' and variants (e.g., ``macaw using tool'', ``lorikeet using tool'', ``parakeet using tool''), ``tool use in parrot'', ``parrot tool use'', ``parrot scratching itself'' (included after we found several videos demonstrating self-care tool use in previous searches) and equivalent terms (e.g., ``parrot preening itself'', ``parrot grooming itself'', ``parrot scratching''). For all species that did not display results including object manipulation or scratching behaviours, we also searched the species' common name(s) + ``tool use'', as well as the species' common name(s) + ``scratching''. We also searched for translations of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all countries where bird ownership was reported as \textgreater5\%\textsuperscript{76}, namely, Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, Portuguese, and Mandarin.

When we found a relevant video, we also searched for similar content uploaded by the same person/channel. For each YouTube search conducted, we watched all relevant videos until we reached five consecutive videos that did not feature any parrots. At this point, we ended that search and initiated the next search. In line with previous recommendations\textsuperscript{20}, we planned to exclude any videos that consisted of four or more shots edited together so as to ensure the behaviours being observed were not edited or manipulated, but none of the videos obtained qualified for exclusion.

All videos featuring parrots manipulating objects were investigated for potential tool use or borderline tool use. We defined tool use as the manipulation of an unattached object as an extension of the beak or foot to achieve a goal towards another object, individual, or oneself\textsuperscript{55}. Borderline tool use was similarly defined, except that it involved the use of an object that was still attached to a substrate\textsuperscript{56}. For example, if individuals used a fallen feather or stick for self-scratching this was defined as tool use, but using one's currently attached tail feathers or cage furnishings for the same purpose was defined as borderline tool use. Self-scratching had to involve slow and repeated movements of touching an object to one's body (or, in the case of borderline tool use, rubbing repetitively against an attached object\textsuperscript{64}).

All relevant videos were coded for video length, species, tool use presence (yes/borderline), tool use type (e.g., scratching, feeding), the object being used (e.g., feather, stick), tool use target, human interference with the action (talking or handing object to parrot, holding parrot), and the number of shots within each video. Our complete dataset also includes the name for each video, link, subject name, sex (as declared by owner, as most parrot species are not sexually dimorphic), publishing date, and dates found and coded.

\hypertarget{data-for-parrot-species}{%
\subsection{Data for parrot species}\label{data-for-parrot-species}}

We collected data for 194 parrot species (Supplementary Figures \ref{fig:plotPhylo2} - \ref{fig:plotPhylo4}). We gathered feeding strategy data as a dichotomous variable (``generalist'' or ``specialist'') from the EltonTraits ecological database\textsuperscript{53}. As per the database, specialists were defined as species whose diet comprised at least 70\% of a single food source. To calculate relative brain size, we collated data from the literature for all known body mass (g) and brain mass (g) values across parrots\textsuperscript{47--52}. For all species for which we obtained body and brain mass data, we calculated the encephalisation quotient (EQ) using the following formula\textsuperscript{77}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We found body mass and brain mass data for a total of 194 parrot species. This included all tool-using species in our video dataset, with the exception of three species: \emph{Diopsittaca nobilis}, \emph{Psittacara erythrogenys}, and \emph{Coracopsis vasa}. For the latter, we used values for the closely related \emph{Coracopsis nigra}. The other two species were excluded from the final dataset.

For modelling purposes, we coded research effort in both the scientific literature and the crowdsourced videos. For the scientific literature, we operationalised research effort as the number of papers published for each species' Latin name up to and including the first paper containing tool use for that species. If no tool use had been identified in the scientific literature for a species, then we coded the total number of papers published to date. We used the scientific database Scopus for coding the number of published papers. For the crowdsourced videos, we coded research effort as the number of search hits for each species on YouTube. If tool use had been identified on YouTube, we estimated the number of search hits when the first video of tool use was published on YouTube, assuming linear growth of search hits since the inception of YouTube. If tool use had not been identified, we used the current number of search hits.

For phylogenetic data, we used the phylogenetic tool at www.birdtree.org\textsuperscript{54} to compile 1000 posterior draws of phylogenetic trees for 174 of the 194 parrot species for which both EQ and genomic data exist. A single maximum clade credibility tree was generated from these posterior draws for visualisation purposes. In our analyses, we iterated over posterior draws of the phylogeny to account for phylogenetic uncertainty.

\hypertarget{phylogenetic-signal}{%
\subsection{Phylogenetic signal}\label{phylogenetic-signal}}

We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{78} to calculate phylogenetic signal, for both the pre-survey and post-survey tool use data. We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.

\hypertarget{causal-model-of-tool-use}{%
\subsection{Causal model of tool use}\label{causal-model-of-tool-use}}

To infer unobserved probabilities of tool use across parrots, we proposed a causal model of observed tool use (Figure \ref{fig:plotDAG}). We assumed that observed tool use in the scientific literature and in the crowdsourced videos is caused by both the unobserved presence or absence of tool use and research effort, proxied by the number of papers published on a species and the number of videos published on a species. Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected. In addition, based on theory, we also assumed that unobserved tool use is caused by feeding strategy and relative brain size\textsuperscript{10--13,15--17}. Finally, we assumed that shared phylogenetic history causes unobserved confounding and non-independence in unobserved tool use, feeding strategy, and relative brain size across the parrot phylogeny.

\hypertarget{bayesian-phylogenetic-survival-cure-model}{%
\subsection{Bayesian phylogenetic survival cure model}\label{bayesian-phylogenetic-survival-cure-model}}

Given our proposed causal model, we constructed a statistical model to impute unobserved probabilities of tool use and test existing theories of the evolution of tool use in parrots. To understand the model, suppose that we have the following observed variables for parrot species \(i\). For the scientific literature, we declare \(\text{N}_{\text{Lit},i}\) as the number of papers published before and up to tool use identification for species \(i\) (or, if tool use has not been identified, the total number of papers published for species \(i\)) and \(\text{T}_{\text{Lit},i}\) as a binary variable stating whether (1) or not (0) tool use has yet been observed in the scientific literature for species \(i\). For the crowdsourced videos, we declare \(\text{N}_{\text{Vid},i}\) as the number of videos published before and up to tool use identification for species \(i\) (or, if tool use has not been identified, the total number of videos published for species \(i\)) and \(\text{T}_{\text{Vid},i}\) as a binary variable stating whether (1) or not (0) tool use has yet been observed in the crowdsourced videos for species \(i\). Additionally, \(\text{F}_i\) and \(\text{EQ}_i\) are feeding strategy and encephalisation quotient values for species \(i\) and we have a phylogenetic distance matrix \(D\) that describes the patristic distances between all parrot species.

We assume that species \(i\) is a non-tool-user (i.e.~``cured'') with some probability \(p_i\). We also assume that tool use is identified in the scientific literature and the crowdsourced videos at constant rates \(\lambda_{\text{Lit}}\) and \(\lambda_{\text{Vid}}\) following exponential survival functions. Given these assumptions, we can then describe the different ways in which variables \(\text{N}_\text{Lit}\) and \(\text{N}_\text{Vid}\) can be distributed. Focusing on the scientific literature, if tool use has been observed (\(\text{T}_{\text{Lit},i} = 1\)), then the likelihood for \(\text{N}_{\text{Lit},i}\) is:

\begin{align}
\text{Pr}(\text{N}_{\text{Lit},i}|\text{T}_{\text{Lit},i} = 1,p_i,\lambda_\text{Lit}) = (1-p_i)\cdot\text{Exponential}(\text{N}_{\text{Lit},i}|\lambda_\text{Lit})
\end{align}

On the other hand, if tool use has not yet been observed (\(\text{T}_{\text{Lit},i} = 0\)), there are two ways that the outcome variable could have been realised. First, the species could be a non-tool-user with probability \(p_i\). Second, the species could be a tool-user with probability (\(1 - p_i\)) that has been censored and has not had its tool use measured yet. Together, then, the likelihood for \(\text{N}_{\text{Lit},i}\) is:

\begin{align}
\text{Pr}(\text{N}_{\text{Lit},i}|\text{T}_{\text{Lit},i} = 0,p_i,\lambda_\text{Lit}) = p_i + ((1-p_i)\cdot\text{Exponential-CCDF}(\text{N}_{\text{Lit},i}|\lambda_\text{Lit}))
\end{align}

The Exponential-CCDF function allows for the censored nature of the data. The same data generating process is assumed to underlie the crowdsourced videos.

We define the mixture likelihood \(\text{SurvivalCure}\) as the distribution above, with parameters \(p\) (the probability of being a ``cured'' non-tool-user) and \(\lambda\) (the rate of the exponential distribution). We use an Ornstein-Uhlenbeck Gaussian process\textsuperscript{79} to model phylogenetic covariance. Below, we specify the full model with priors:

\begin{align}
N_{\text{Lit},i} &\sim \text{SurvivalCure}(\lambda_{\text{Lit},i}, p_{i}) \\
N_{\text{Vid},i} &\sim \text{SurvivalCure}(\lambda_{\text{Vid},i}, p_{i}) \nonumber \\
\lambda_{\text{Lit},i} &= 1 / \text{exp}(\gamma_\text{Lit}) \nonumber \\
\lambda_{\text{Vid},i} &= 1 / \text{exp}(\gamma_\text{Vid}) \nonumber \\
\text{logit}(p_{i}) &= \alpha_{\text{FEEDING}[i]} + \beta\text{EQ}_{i} +  k_{\text{SPECIES}[i]} \nonumber \\
\begin{pmatrix}k_{1}\\k_{2}\\...\\k_{n}\\\end{pmatrix}
&\sim \text{MVNormal}
\begin{pmatrix}\begin{pmatrix}0\\0\\...\\0\\\end{pmatrix},\bf{K}\end{pmatrix} \nonumber \\
\bf{K}_{ij} &= \eta^2\text{exp}(-\rho^2D_{ij}) \nonumber \\
\gamma_\text{Lit}, \gamma_\text{Vid}, \alpha_{1,2}, \beta &\sim \text{Normal(0, 1)} \nonumber \\
\eta^2, \rho^2 &\sim \text{Exponential(0.5)} \nonumber
\end{align}

The priors for this model produce reasonable prior predictions of the probabilities of tool use for each parrot species (Supplementary Figure \ref{fig:plotSurvCure7}), but a sensitivity analysis revealed that the ranking and posterior probabilities reported in the main text were robust to modifying these priors (Supplementary Figure \ref{fig:plotSurvCure8}). We estimated the posterior distribution of this model using Hamiltonian Monte Carlo as implemented in Stan version 2.26.1\textsuperscript{80}. We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty. R-hat values and effective sample sizes suggested that the model converged normally. Trace plots are reported in Supplementary Figure \ref{fig:plotTrace}.

To validate our method, we fitted the model to 100 simulated datasets with known parameters. The model was able to successfully recover those parameters (Supplementary Figure \ref{fig:plotSurvCureSim}). We also ran a leave-one-species-out exercise to ensure that we could accurately predict known tool users. We repeated this approach for each known tool user by setting observed tool use to zero. Cross-validation results are reported in the main text.

\hypertarget{ancestral-state-reconstruction}{%
\subsection{Ancestral state reconstruction}\label{ancestral-state-reconstruction}}

To determine whether the identification of novel tool-using species has implications for our understanding of the evolutionary origins of tool use in parrots, we fitted three exploratory ancestral state reconstruction models. We used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{81}, iterating the function over 100 posterior parrot phylogenies. This function estimates discrete ancestral states by assuming the evolution of a latent continuous variable following an Ornstein-Uhlenbeck process. We fitted this model to three different outcome variables: (\emph{i}) presence vs.~absence of tool use in scientific literature only, (\emph{ii}) presence vs.~absence of tool use in literature and/or videos, and (\emph{iii}) the median predicted probabilities of tool use from the phylogenetic survival cure model.

\hypertarget{reproducibility}{%
\subsection{Reproducibility}\label{reproducibility}}

All analyses were conducted in R v4.2.1.\textsuperscript{82}. Visualisations were produced using the \emph{ggplot2}\textsuperscript{83} and \emph{cowplot}\textsuperscript{84} packages. The manuscript was reproducibly generated using the \emph{targets}\textsuperscript{85} and \emph{papaja}\textsuperscript{86} packages. Code to reproduce all analyses and figures can be found here: \url{https://github.com/ScottClaessens/phyloParrot}

\newpage
\nolinenumbers

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This project was made possible through the support of a grant from the Templeton World Charity Foundation (A.H.T., X.J.N.) and a Prime Minister's McDiarmid Emerging Scientist Prize (A.H.T.). The authors would like to thank Daniel Sol for providing feedback on a previous version of the manuscript.

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

All authors contributed to the conceptualisation of the paper. A.P.M.B., X.J.N., and A.H.T. developed the video search methodology. S.C., D.W., and Q.A.D. developed the statistical models and analysed the data. All the authors wrote the manuscript and approved the final version for submission.

\hypertarget{competing-interests}{%
\section{Competing Interests}\label{competing-interests}}

The authors declare no competing interests.

\hypertarget{data-availability}{%
\section{Data Availability}\label{data-availability}}

All data used in this study are publicly available on GitHub: \url{https://github.com/ScottClaessens/phyloParrot}

\hypertarget{code-availability}{%
\section{Code Availability}\label{code-availability}}

All code to reproduce the analyses in this study are publicly available on GitHub: \url{https://github.com/ScottClaessens/phyloParrot}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-MacLean2012}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{MacLean, E. L. \emph{et al.} \href{https://doi.org/10.1007/s10071-011-0448-8}{How does cognition evolve? Phylogenetic comparative psychology}. \emph{Animal Cognition} \textbf{15}, 223--238 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2011}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Lefebvre, L. \href{https://doi.org/10.1098/rsbl.2010.0556}{Taxonomic counts of cognition in the wild}. \emph{Biology Letters} \textbf{7}, 631--633 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-Logan2018}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Logan, C. J. \emph{et al.} \href{https://doi.org/10.3819/CCBR.2018.130008}{Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization}. \emph{Comparative Cognition \& Behavior Reviews} \textbf{13}, 55--89 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Healy2007}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Healy, S. D. \& Rowe, C. \href{https://doi.org/10.1098/rspb.2006.3748}{A critique of comparative studies of brain size}. \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{274}, 453--464 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-Powell2017}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Powell, L. E., Isler, K. \& Barton, R. A. \href{https://doi.org/10.1098/rspb.2017.1765}{Re-evaluating the link between brain size and behavioural ecology in primates}. \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{284}, 20171765 (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-Goodall1964}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Goodall, J. Tool-using and aimed throwing in a community of free-living chimpanzees. \emph{Nature} \textbf{201}, 1264--1266 (1964).}

\leavevmode\vadjust pre{\hypertarget{ref-Hunt1996}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Hunt, G. R. \href{https://doi.org/10.1038/379249a0}{Manufacture and use of hook-tools by {N}ew {C}aledonian crows}. \emph{Nature} \textbf{379}, 249--251 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-Smolker1997}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Smolker, R., Richards, A., Connor, R., Mann, J. \& Berggren, P. \href{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}{Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?} \emph{Ethology} \textbf{103}, 454--465 (1997).}

\leavevmode\vadjust pre{\hypertarget{ref-Finn2009}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Finn, J. K., Tregenza, T. \& Norman, M. D. \href{https://doi.org/10.1016/j.cub.2009.10.052}{Defensive tool use in a coconut-carrying octopus}. \emph{Current Biology} \textbf{19}, R1069--R1070 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2002}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Lefebvre, L., Nicolakakis, N. \& Boire, D. \href{https://doi.org/10.1163/156853902320387918}{Tools and brains in birds}. \emph{Behaviour} \textbf{139}, 939--973 (2002).}

\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre1997}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E. \& Finkelstein, A. \href{https://doi.org/10.1006/anbe.1996.0330}{Feeding innovations and forebrain size in birds}. \emph{Animal Behaviour} \textbf{53}, 549--560 (1997).}

\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2004}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Lefebvre, L., Reader, S. M. \& Sol, D. \href{https://doi.org/10.1159/000076784}{Brains, innovations and evolution in birds and primates}. \emph{Brain, Behavior and Evolution} \textbf{63}, 233--246 (2004).}

\leavevmode\vadjust pre{\hypertarget{ref-Sol2005}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Sol, D., Duncan, R. P., Blackburn, T. M., Cassey, P. \& Lefebvre, L. \href{https://doi.org/10.1073/pnas.0408145102}{Big brains, enhanced cognition, and response of birds to novel environments}. \emph{Proceedings of the National Academy of Sciences} \textbf{102}, 5460--5465 (2005).}

\leavevmode\vadjust pre{\hypertarget{ref-Sol2009}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Sol, D. \href{https://doi.org/10.1098/rsbl.2008.0621}{Revisiting the cognitive buffer hypothesis for the evolution of large brains}. \emph{Biology Letters} \textbf{5}, 130--133 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2015}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Ducatez, S., Clavel, J. \& Lefebvre, L. \href{https://doi.org/10.1111/1365-2656.12255}{Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?} \emph{Journal of Animal Ecology} \textbf{84}, 79--89 (2015).}

\leavevmode\vadjust pre{\hypertarget{ref-Overington2011}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{Overington, S. E., Griffin, A. S., Sol, D. \& Lefebvre, L. \href{https://doi.org/10.1093/beheco/arr130}{Are innovative species ecological generalists? A test in {N}orth {A}merican birds}. \emph{Behavioral Ecology} \textbf{22}, 1286--1293 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2020}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P. M. \& Fichtel, C. Linking ecology and cognition: Does ecological specialisation predict cognitive test performance? \emph{Behavioral Ecology and Sociobiology} \textbf{74}, 154 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-MettkeHofmann2014}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{Mettke-Hofmann, C. \href{https://doi.org/10.1002/wcs.1289}{Cognitive ecology: Ecological factors, life-styles, and cognition}. \emph{WIREs Cognitive Science} \textbf{5}, 345--360 (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2014}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{Ducatez, S. \& Lefebvre, L. \href{https://doi.org/10.1371/journal.pone.0089955}{Patterns of research effort in birds}. \emph{PLOS ONE} \textbf{9}, e89955 (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-Nelson2013}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{Nelson, X. J. \& Fijn, N. \href{https://doi.org/10.1016/j.anbehav.2012.12.009}{The use of visual media as a tool for investigating animal behaviour}. \emph{Animal Behaviour} \textbf{85}, 525--536 (2013).}

\leavevmode\vadjust pre{\hypertarget{ref-Dickinson2010}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{Dickinson, J. L., Zuckerberg, B. \& Bonter, D. N. \href{https://doi.org/10.1146/annurev-ecolsys-102209-144636}{Citizen science as an ecological research tool: Challenges and benefits}. \emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{41}, 149--172 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{Krueger, K., Esch, L. \& Byrne, R. \href{https://doi.org/10.1371/journal.pone.0218954}{Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms}. \emph{PLOS ONE} \textbf{14}, 1--20 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-Klump2021}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Klump, B. C. \emph{et al.} \href{https://doi.org/10.1126/science.abe7808}{Innovation and geographic spread of a complex foraging culture in an urban parrot}. \emph{Science} \textbf{373}, 456--460 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Klump2022}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{Klump, B. C., Major, R. E., Farine, D. R., Martin, J. M. \& Aplin, L. M. Is bin-opening in cockatoos leading to an innovation arms race with humans? \emph{Current Biology} \textbf{32}, R910--R911 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-Burgio2019}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{Burgio, K. R. \emph{et al.} \href{https://doi.org/10.1016/j.dib.2019.103882}{Phylogenetic supertree and functional trait database for all extant parrots}. \emph{Data in Brief} \textbf{24}, 103882 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2009}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Auersperg, A. M. I., Gajdon, G. K. \& Huber, L. \href{https://doi.org/10.1098/rsbl.2009.0114}{Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem}. \emph{Biology Letters} \textbf{5}, 455--458 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2010}{}}%
\CSLLeftMargin{27. }%
\CSLRightInline{Auersperg, A. M. I., Gajdon, G. K. \& Huber, L. \href{https://doi.org/10.1016/j.anbehav.2010.08.007}{Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task}. \emph{Animal Behaviour} \textbf{80}, 783--789 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011a}{}}%
\CSLLeftMargin{28. }%
\CSLRightInline{Auersperg, A. M. I., Huber, L. \& Gajdon, G. K. \href{https://doi.org/10.1098/rsbl.2011.0388}{Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis})}. \emph{Biology Letters} \textbf{7}, 825--828 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011b}{}}%
\CSLLeftMargin{29. }%
\CSLRightInline{Auersperg, A. M. I., Bayern, A. M. P. von, Gajdon, G. K., Huber, L. \& Kacelnik, A. \href{https://doi.org/10.1371/journal.pone.0020231}{Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm}. \emph{PLOS ONE} \textbf{6}, 1--8 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2012}{}}%
\CSLLeftMargin{30. }%
\CSLRightInline{Auersperg, A. M. I., Szabo, B., von Bayern, A. M. P. \& Kacelnik, A. \href{https://doi.org/10.1016/j.cub.2012.09.002}{Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo}. \emph{Current Biology} \textbf{22}, R903--R904 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Bastos2021}{}}%
\CSLLeftMargin{31. }%
\CSLRightInline{Bastos, A. P., Horváth, K., Webb, J. L., Wood, P. M. \& Taylor, A. H. Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}). \emph{Scientific Reports} \textbf{11}, 18035 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-BentleyCondit2010}{}}%
\CSLLeftMargin{32. }%
\CSLRightInline{Bentley-Condit, V. \& Smith, E. O. \href{https://doi.org/10.1163/000579509X12512865686555}{Animal tool use: Current definitions and an updated comprehensive catalog}. \emph{Behaviour} \textbf{147}, 185--32A (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Borsari2005}{}}%
\CSLLeftMargin{33. }%
\CSLRightInline{Borsari, A. \& Ottoni, E. B. \href{https://doi.org/10.1007/s10071-004-0221-3}{Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus})}. \emph{Animal Cognition} \textbf{8}, 48--52 (2005).}

\leavevmode\vadjust pre{\hypertarget{ref-Goodman2018}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{Goodman, M., Hayward, T. \& Hunt, G. R. \href{https://doi.org/10.1038/s41598-018-32363-9}{Habitual tool use innovated by free-living {N}ew {Z}ealand kea}. \emph{Scientific Reports} \textbf{8}, 13935 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Heinsohn2017}{}}%
\CSLLeftMargin{35. }%
\CSLRightInline{Heinsohn, R., Zdenek, C. N., Cunningham, R. B., Endler, J. A. \& Langmore, N. E. \href{https://doi.org/10.1126/sciadv.1602399}{Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music}. \emph{Science Advances} \textbf{3}, e1602399 (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-Janzen1976}{}}%
\CSLLeftMargin{36. }%
\CSLRightInline{Janzen, M. J., Janzen, D. H. \& Pond, C. M. Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). \emph{Biotropica} \textbf{8}, 70 (1976).}

\leavevmode\vadjust pre{\hypertarget{ref-Lambert2015}{}}%
\CSLLeftMargin{37. }%
\CSLRightInline{Lambert, M. L., Seed, A. M. \& Slocombe, K. E. \href{https://doi.org/10.1098/rsbl.2015.0861}{A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa})}. \emph{Biology Letters} \textbf{11}, 20150861 (2015).}

\leavevmode\vadjust pre{\hypertarget{ref-OHara2021}{}}%
\CSLLeftMargin{38. }%
\CSLRightInline{O'Hara, M. \emph{et al.} \href{https://doi.org/10.1016/j.cub.2021.08.009}{Wild {G}offin's cockatoos flexibly manufacture and use tool sets}. \emph{Current Biology} \textbf{31}, 4512--4520.e6 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Kleinberger2023}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{Kleinberger, R., Cunha, J., Vemuri, M. M. \& Hirskyj-Douglas, I. Birds of a feather video-flock together: Design and evaluation of an agency-based parrot-to-parrot video-calling system for interspecies ethical enrichment. in \emph{Proceedings of the 2023 CHI conference on human factors in computing systems} (Association for Computing Machinery, 2023). doi:\href{https://doi.org/10.1145/3544548.3581166}{10.1145/3544548.3581166}.}

\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{Anderson, P. \href{https://doi.org/10.1163/156853003322796109}{A bird in the house: An anthropological perspective on companion parrots}. \emph{Society \& Animals} \textbf{11}, 393--418 (2003).}

\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{Carrete, M. \& Tella, J. \href{https://doi.org/10.1890/070075}{Wild-bird trade and exotic invasions: A new link of conservation concern?} \emph{Frontiers in Ecology and the Environment} \textbf{6}, 207--211 (2008).}

\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{Drews, C. \href{https://doi.org/10.1163/156853001753639233}{Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers}. \emph{Society \& Animals} \textbf{9}, 107--126 (2001).}

\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Kelly, D., McCarthy, E., Menzel, K. \& Engebretson, M. \href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?} (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Li, L. \& Jiang, Z. \href{https://doi.org/10.1371/journal.pone.0085012}{International trade of {CITES} listed bird species in {C}hina}. \emph{PLOS ONE} \textbf{9}, 1--8 (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{Su, S., Cassey, P., Vall-llosera, M. \& Blackburn, T. M. \href{https://doi.org/10.1371/journal.pone.0127482}{Going cheap: Determinants of bird price in the {T}aiwanese pet market}. \emph{PLOS ONE} \textbf{10}, 1--17 (2015).}

\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{Young, A. M., Hobson, E. A., Lackey, L. B. \& Wright, T. F. \href{https://doi.org/10.1111/j.1469-1795.2011.00477.x}{Survival on the ark: Life-history trends in captive parrots}. \emph{Animal Conservation} \textbf{15}, 28--43 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{Flammer, K., Whitt-Smith, D. \& Papich, M. \href{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}{Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection}. \emph{Journal of Avian Medicine and Surgery} \textbf{15}, 276--282 (2001).}

\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{Iwaniuk, A. N., Dean, K. M. \& Nelson, J. E. Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates. \emph{Brain, Behavior and Evolution} \textbf{65}, 40--59 (2005).}

\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P. R. \& Ihunwo, A. O. \href{https://doi.org/10.3389/fnana.2018.00007}{Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh})}. \emph{Frontiers in Neuroanatomy} \textbf{12}, 7 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
\CSLLeftMargin{50. }%
\CSLRightInline{Olkowicz, S. \emph{et al.} \href{https://doi.org/10.1073/pnas.1517131113}{Birds have primate-like numbers of neurons in the forebrain}. \emph{Proceedings of the National Academy of Sciences} \textbf{113}, 7255--7260 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
\CSLLeftMargin{51. }%
\CSLRightInline{Schuck-Paim, C., Alonso, W. J. \& Ottoni, E. B. \href{https://doi.org/10.1159/000119710}{Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots}. \emph{Brain, Behavior and Evolution} \textbf{71}, 200--215 (2008).}

\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
\CSLLeftMargin{52. }%
\CSLRightInline{Silva, T., Guzmán, A., Urantówka, A. D. \& Mackiewicz, P. \href{https://doi.org/10.7717/peerj.3475}{A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny}. \emph{PeerJ} \textbf{5}, e3475 (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
\CSLLeftMargin{53. }%
\CSLRightInline{Wilman, H. \emph{et al.} EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals. (2016) doi:\href{https://doi.org/10.6084/m9.figshare.c.3306933.v1}{10.6084/m9.figshare.c.3306933.v1}.}

\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
\CSLLeftMargin{54. }%
\CSLRightInline{Jetz, W., Thomas, G. H., Joy, J. B., Hartmann, K. \& Mooers, A. O. The global diversity of birds in space and time. \emph{Nature} \textbf{491}, 444--448 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
\CSLLeftMargin{55. }%
\CSLRightInline{Shumaker, R. W., Walkup, K. R., Beck, B. B. \& Burghardt, G. M. \emph{Animal tool behavior: The use and manufacture of tools by animals}. (Johns Hopkins University Press). doi:\href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}

\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
\CSLLeftMargin{56. }%
\CSLRightInline{Seed, A. \& Byrne, R. \href{https://doi.org/10.1016/j.cub.2010.09.042}{Animal tool-use}. \emph{Current Biology} \textbf{20}, R1032--R1039 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
\CSLLeftMargin{57. }%
\CSLRightInline{Bercovitz, A. B. Avian sex identification techniques. in \emph{Companion bird medicine} (ed. Burr, E. W.) (Iowa State University Press, 1987).}

\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
\CSLLeftMargin{58. }%
\CSLRightInline{Hoyo, J. D. \& Bierregaard, R. \emph{Handbook of the birds of the world}. (Lynx Edicions, 2011).}

\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
\CSLLeftMargin{59. }%
\CSLRightInline{Amico, M. \& Van Keilegom, I. \href{https://doi.org/10.1146/annurev-statistics-031017-100101}{Cure models in survival analysis}. \emph{Annual Review of Statistics and Its Application} \textbf{5}, 311--342 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Goodall1971}{}}%
\CSLLeftMargin{60. }%
\CSLRightInline{Goodall, J. \href{https://doi.org/10.1016/S0065-3454(08)60157-6}{Tool-using in primates and other vertebrates}. in (eds. Lehrman, D. S., Hinde, R. A. \& Shaw, E.) vol. 3 195--249 (Academic Press, 1971).}

\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
\CSLLeftMargin{61. }%
\CSLRightInline{Reader, S. M. \& Laland, K. N. \href{https://doi.org/10.1073/pnas.062041299}{Social intelligence, innovation, and enhanced brain size in primates}. \emph{Proceedings of the National Academy of Sciences} \textbf{99}, 4436--4441 (2002).}

\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
\CSLLeftMargin{62. }%
\CSLRightInline{Cabrera-Álvarez, M. J. \& Clayton, N. S. \href{https://doi.org/10.3389/fpsyg.2020.560669}{Neural processes underlying tool use in humans, macaques, and corvids}. \emph{Frontiers in Psychology} \textbf{11}, 560669 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
\CSLLeftMargin{63. }%
\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P. M. \& Fichtel, C. \href{https://doi.org/10.1098/rspb.2021.1728}{Linking cognition to ecology in wild sympatric mouse lemur species}. \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{288}, 20211728 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
\CSLLeftMargin{64. }%
\CSLRightInline{Sándor, K. \& Miklósi, Á. \href{https://doi.org/10.3389/fpsyg.2020.555487}{How to report anecdotal observations? A new approach based on a lesson from "puffin tool use"}. \emph{Frontiers in Psychology} \textbf{11}, 555487 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2020}{}}%
\CSLLeftMargin{65. }%
\CSLRightInline{Auersperg, A. M. I., Schwing, R., Mioduszewska, B., O'Hara, M. \& Huber, L. \href{https://doi.org/10.1073/pnas.2001988117}{Do puffins use tools?} \emph{Proceedings of the National Academy of Sciences} \textbf{117}, 11859--11859 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
\CSLLeftMargin{66. }%
\CSLRightInline{Debastiani, V. J., Bastazini, V. A. G. \& Pillar, V. D. \href{https://doi.org/10.1016/j.ecoinf.2021.101315}{Using phylogenetic information to impute missing functional trait values in ecological databases}. \emph{Ecological Informatics} \textbf{63}, 101315 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
\CSLLeftMargin{67. }%
\CSLRightInline{Hunt, G. R., Gray, R. D. \& Taylor, A. H. Why is tool use rare in animals? in \emph{Tool use in animals: Cognition and ecology} (eds. Sanz, C. M., Call, J. \& Boesch, C.) 89--118 (Cambridge University Press, 2013). doi:\href{https://doi.org/10.1017/CBO9780511894800.007}{10.1017/CBO9780511894800.007}.}

\leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
\CSLLeftMargin{68. }%
\CSLRightInline{Benichov, J. I., Globerson, E. \& Tchernichovski, O. \href{https://doi.org/10.3389/fnhum.2016.00255}{Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans}. \emph{Frontiers in Human Neuroscience} \textbf{10}, (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
\CSLLeftMargin{69. }%
\CSLRightInline{Patel, A. D., Iversen, J. R., Bregman, M. R. \& Schulz, I. \href{https://doi.org/10.1016/j.cub.2009.03.038}{Experimental evidence for synchronization to a musical beat in a nonhuman animal}. \emph{Current Biology} \textbf{19}, 827--830 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
\CSLLeftMargin{70. }%
\CSLRightInline{ten Cate, C., Spierings, M., Hubert, J. \& Honing, H. \href{https://doi.org/10.3389/fpsyg.2016.00730}{Can birds perceive rhythmic patterns? A review and experiments on a songbird and a parrot species}. \emph{Frontiers in Psychology} \textbf{7}, (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
\CSLLeftMargin{71. }%
\CSLRightInline{Wilson, M. \& Cook, P. F. \href{https://doi.org/10.3758/s13423-016-1013-x}{Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed}. \emph{Psychonomic Bulletin \& Review} \textbf{23}, 1647--1659 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
\CSLLeftMargin{72. }%
\CSLRightInline{Eckert, J., Winkler, S. L. \& Cartmill, E. A. \href{https://doi.org/10.1098/rsbl.2020.0370}{Just kidding: The evolutionary roots of playful teasing}. \emph{Biology Letters} \textbf{16}, 20200370 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
\CSLLeftMargin{73. }%
\CSLRightInline{Bro-Jørgensen, J. \& Pangle, W. M. \href{https://doi.org/10.1086/653078}{Male topi antelopes alarm snort deceptively to retain females for mating}. \emph{The American Naturalist} \textbf{176}, E33--E39 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
\CSLLeftMargin{74. }%
\CSLRightInline{Byrne, R. W. \& Whiten, A. \href{https://doi.org/10.1017/S0140525X00049955}{Toward the next generation in data quality: A new survey of primate tactical deception}. \emph{Behavioral and Brain Sciences} \textbf{11}, 267--273 (1988).}

\leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
\CSLLeftMargin{75. }%
\CSLRightInline{Byrne, R. W. \& Whiten, A. Computation and mindreading in primate tactical deception. in \emph{Natural theories of mind: Evolution, development and simulation of everyday mindreading} (ed. Whiten, A.) 127--141 (Basil Blackwell, 1991).}

\leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
\CSLLeftMargin{76. }%
\CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership}. (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
\CSLLeftMargin{77. }%
\CSLRightInline{Jerison, H. J. \emph{Evolution of the brain and intelligence}. (Academic Press, 1973).}

\leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
\CSLLeftMargin{78. }%
\CSLRightInline{Paradis, E. \& Schliep, K. \href{https://doi.org/10.1093/bioinformatics/bty633}{{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}}. \emph{Bioinformatics} \textbf{35}, 526--528 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
\CSLLeftMargin{79. }%
\CSLRightInline{McElreath, R. \emph{\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition}}. (CRC Press, 2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
\CSLLeftMargin{80. }%
\CSLRightInline{Stan Development Team. \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}. (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
\CSLLeftMargin{81. }%
\CSLRightInline{Revell, L. J. \href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{{phytools}: An {R} package for phylogenetic comparative biology (and other things)}. \emph{Methods in Ecology and Evolution} \textbf{3}, 217--223 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
\CSLLeftMargin{82. }%
\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2022).}

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
\CSLLeftMargin{83. }%
\CSLRightInline{Wickham, H. \emph{\href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis}}. (Springer-Verlag New York, 2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
\CSLLeftMargin{84. }%
\CSLRightInline{Wilke, C. O. \emph{\href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}}. (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
\CSLLeftMargin{85. }%
\CSLRightInline{Landau, W. M. \href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}. \emph{Journal of Open Source Software} \textbf{6}, 2959 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
\CSLLeftMargin{86. }%
\CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}}. (2022).}

\end{CSLReferences}

\endgroup

\newpage
\vspace*{60mm}

\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}
\renewcommand{\thefigure}{\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}

\hypertarget{supplementary-information}{%
\section{\texorpdfstring{\textbf{Supplementary Information}}{Supplementary Information}}\label{supplementary-information}}

\setcounter{page}{1}
\centering

\noindent \hspace*{5mm} \small Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare \newline
\hspace*{1cm} \small Amalia P. M. Bastos\textsuperscript{1,2}, Scott Claessens\textsuperscript{2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, \newline
\hspace*{25mm} Quentin D. Atkinson\textsuperscript{2}, Alex H. Taylor\textsuperscript{2,3,5,6} \newline

\raggedright

\noindent \footnotesize \textsuperscript{1} Department of Psychological \& Brain Sciences, Johns Hopkins University, Baltimore, MD, United States \newline
\noindent \footnotesize \textsuperscript{2} School of Psychology, University of Auckland, Auckland, New Zealand \newline
\noindent \footnotesize \textsuperscript{3} School of Biological Sciences, University of Canterbury, Christchurch, New Zealand \newline
\noindent \footnotesize \textsuperscript{4} School of Computer Science, University of Auckland, Auckland, New Zealand \newline
\noindent \footnotesize \textsuperscript{5} ICREA, Pg. Lluís Companys 23, Barcelona, Spain \newline
\noindent \footnotesize \textsuperscript{6} Institute of Neuroscience, Universitat Autònoma de Barcelona, Barcelona, Spain \newline
\normalsize
\newpage

\hypertarget{supplementary-figures}{%
\subsection{Supplementary Figures}\label{supplementary-figures}}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure3-1.pdf}
\caption{\label{fig:plotSurvCure3}\emph{Median posterior probabilities of undetected tool use for each parrot species without observed evidence of tool use from reduced model.} This reduced version of the phylogenetic survival cure model does not contain relative brain size or feeding strategy as predictors, nor does it contain any phylogenetic covariance. The only information included in the model is the number of papers published and the number of YouTube search hits for each species. Each point is a parrot species without observed evidence of tool use, and the colour of the points scales with the probability of undetected tool use. All else being equal, those species with fewer published papers and fewer YouTube search hits have a higher probability of being undetected tool users.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure9-1.pdf}
\caption{\label{fig:plotSurvCure9}\emph{Receiver operating characteristic (ROC) curve for the phylogenetic survival cure model.} The area-under-the-curve in this plot is 0.95, suggesting that the model is able to adequately classify observed tool users and non-tool users.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure5-1.pdf}
\caption{\label{fig:plotSurvCure5}\emph{Prior and posterior phylogenetic covariance functions from the Bayesian survival cure model fitted to the full dataset.} Lines are median posterior functions and shaded areas are 50\% and 95\% credible intervals.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure6-1.pdf}
\caption{\label{fig:plotSurvCure6}\emph{Between-species correlation matrix implied by the posterior phylogenetic covariance function from the Bayesian survival cure model.} Correlations are median posterior estimates. Individual species names omitted for space reasons.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotComparison-1.pdf}
\caption{\label{fig:plotComparison}\emph{Comparing results between the survival cure model and models fitted to the pre-survey and post-survey data without any survival cure component.} Densities are full posterior distributions from three separate models iterated over 100 posterior parrot phylogenies. Points represent posterior medians, and lines represent 50\% and 95\% credible intervals.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotASR1-1.pdf}
\caption{\label{fig:plotASR1}\emph{Results of exploratory ancestral state reconstruction analysis fitted to pre-video-survey data, represented on a maximum clade credibility tree.} Tip nodes represent the presence (red) or absence (grey) of observed tool use in the scientific literature. Pie charts represent the posterior probability of tool use presence at each ancestral node.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotASR2-1.pdf}
\caption{\label{fig:plotASR2}\emph{Results of exploratory ancestral state reconstruction analysis fitted to post-video-survey data, represented on a maximum clade credibility tree.} Tip nodes represent the presence (red) or absence (grey) of observed tool use in the scientific literature and the video survey. Pie charts represent the posterior probability of tool use presence at each ancestral node.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotASR3-1.pdf}
\caption{\label{fig:plotASR3}\emph{Results of exploratory ancestral state reconstruction analysis fitted to predicted probabilities from the phylogenetic survival cure model, represented on a maximum clade credibility tree.} Tip nodes represent the median posterior predicted probabilities of tool use from the phylogenetic survival cure model, with more red indicating an increasing probability of tool use presence and more grey indicating a decreasing probability of tool use presence. Pie charts represent the posterior probability of tool use presence at each ancestral node.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotPhylo2-1.pdf}
\caption{\label{fig:plotPhylo2}\emph{Data on encephalisation quotient and feeding strategy for all parrots, presented on a maximum clade credibility tree.} Tip points are coloured according to feeding generalism (orange) and specialism (blue), and scaled according to encephalisation quotient (EQ).}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotPhylo3-1.pdf}
\caption{\label{fig:plotPhylo3}\emph{Data on number of scientific publications until tool use discovery for all parrots, presented on a maximum clade credibility tree.} Tip points are scaled according to the number of published papers up until tool use discovery (or, if tool use has not been observed, the current number of published papers).}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotPhylo4-1.pdf}
\caption{\label{fig:plotPhylo4}\emph{Data on number of video search hits until tool use discovery for all parrots, presented on a maximum clade credibility tree.} Tip points are scaled according to the estimated number of video search hits up until tool use discovery (or, if tool use has not been observed, the current number of video search hits).}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure7-1.pdf}
\caption{\label{fig:plotSurvCure7}\emph{Prior predicted probabilities of tool use for each species from our phylogenetic survival cure model.} Points are prior medians and lines are 50\% and 95\% credible intervals.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCure8-1.pdf}
\caption{\label{fig:plotSurvCure8}\emph{Results of sensitivity analysis.} The phylogenetic survival cure model was fitted with either a standard Normal(0, 1) prior on the intercept or an alternative Normal(1.78507, 2) prior on the intercept. This latter prior is wider on the logit scale and roughly converts to a 0.86 prior probability of non-tool-use (or a 0.14 prior probability of tool-use, which is the proportion of tool users in the dataset). The sensitivity analysis showed that changing this intercept prior did not have a marked impact on (a) the posterior rankings of parrot species from 1st to 174th or (b) the median posterior probabilities of tool use for parrot species.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotTrace-1.pdf}
\caption{\label{fig:plotTrace}\emph{Trace plots for the Bayesian phylogenetic survival cure model.} Only four chains are shown for ease of presentation.}
\end{figure}

\newpage

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotSurvCureSim-1.pdf}
\caption{\label{fig:plotSurvCureSim}\emph{Posterior estimates from Bayesian survival cure models fitted to 100 datasets simulated with known parameters.} Each dataset consisted of 100 species. Known parameters are presented as solid vertical lines, whereas points and horizontal lines represent posterior medians and 95\% credible intervals. The models were successfully able to recapture the parameters from the simulated datasets.}
\end{figure}

\end{document}

### 2023-08-14 R/functionsAncestralState.R

@@ -1,0 +1,157 @@
+# custom functions - ancestral state reconstruction
+
+# plot ancestral probabilities of tool use on mcc tree
+plotASR <- function(d, postFull, MCCphylogeny, type, filename) {
+  # get post probs of tool use at tips
+  probs <-
+    tibble(
+      species = rep(1:nrow(d), each = length(postFull$aP[,1])),
+      aP1 = rep(postFull$aP[,1], times = nrow(d)),
+      aP2 = rep(postFull$aP[,2], times = nrow(d)),
+      bEQ = rep(postFull$bEQ, times = nrow(d)),
+      k = as.vector(postFull$k),
+      Feeding = rep(d$Feeding, each = length(postFull$aP[,1])),
+      EQ = rep(as.numeric(scale(d$EQ)), each = length(postFull$aP[,1]))
+    ) %>%
+    mutate(
+      aP = ifelse(Feeding == "Generalist", aP1, aP2),
+      p = inv_logit(-(aP + k + bEQ*EQ))
+    ) %>%
+    group_by(species) %>%
+    summarise(p = median(p)) %>%
+    ungroup()
+  # get input data for asr
+  if (type == 1) {
+    # literature only
+    X <- data.frame(Present = d$LiteratureExists_Binary)
+  } else if (type == 2) {
+    # literature and videos
+    X <- data.frame(Present = d$ToolUse)
+  } else if (type == 3) {
+    # literature, videos, and model probabilities
+    X <- data.frame(Present = ifelse(d$ToolUse == 1, 1, probs$p))
+  }
+  X$Absent <- 1 - X$Present
+  rownames(X) <- d$Name
+  # run ancestral state for mcc tree
+  set.seed(1000)
+  asr <- ancThresh(MCCphylogeny, X, ngen = 1e+06, model = "OU")
+  # abbreviated species names for labels
+  X <- rownames_to_column(X, var = "Name")
+  makeLabel <- function(x) paste0(substring(x, 1, 1), ". ", str_split(x, "_")[[1]][2])
+  for (i in 1:length(d$Name)) {
+    d$Name[i] <- makeLabel(d$Name[i])
+    X$Name[i] <- makeLabel(X$Name[i])
+    MCCphylogeny$tip.label[i] <- makeLabel(MCCphylogeny$tip.label[i])
+  }
+  # plot ancestral states
+  p <-
+    ggtree(MCCphylogeny) %<+% X +
+    geom_tiplab(size = 2) +
+    geom_tippoint(aes(colour = Present)) +
[…]

### 2023-08-14 R/functionsComparisonModels.R

@@ -1,0 +1,57 @@
+# logistic regression with phylogenetic control
+fitComparisonModel <- function(d, phylogeny, iter, var) {
+  # scaled distance matrix from one phylogeny
+  phylogeny <- phylogeny[[iter]]
+  distMat <- cophenetic.phylo(phylogeny)
+  distMat <- distMat / max(distMat)
+  # reorder data
+  d <- d[match(phylogeny$tip.label, d$Name),]
+  # data list for stan
+  dat_list <- list(
+    N = nrow(d),
+    Species = 1:nrow(d),
+    y = pull(d, var), 
+    Feeding = ifelse(d$Feeding == "Generalist", 1, 2),
+    EQ = as.numeric(scale(d$EQ)),
+    distMat = distMat
+  )
+  # fit model in rethinking
+  out <- ulam(
+    alist(
+      y ~ bernoulli(p),
+      logit(p) <- aP[Feeding] + bEQ*EQ + k[Species],
+      vector[N]:k ~ multi_normal(0, SIGMA),
+      matrix[N,N]:SIGMA <- cov_GPL1(distMat, etasq, rhosq, 0.01),
+      aP[Feeding] ~ normal(0, 1),
+      bEQ ~ normal(0, 1),
+      c(rhosq, etasq) ~ exponential(0.5)
+    ),
+    data = dat_list,
+    iter = 4000, chains = 1, cores = 1, seed = 2113, 
+    control = list(adapt_delta = 0.85)
+  )
+  return(out)
+}
+
+# plot comparing models
+plotComparisons <- function(postM1, postM2, postFull) {
+  out <-
+    tibble(
+      Model = rep(c("Pre-survey", "Post-survey", "Survival cure"), each = length(postFull$bEQ)),
+      `Effect of encephalisation quotient` = c(postM1$bEQ, postM2$bEQ, -postFull$bEQ),
+      `Difference between feeding strategies` = c(
+        postM1$aP[,1] - postM1$aP[,2],
+        postM2$aP[,1] - postM2$aP[,2],
+        postFull$aP[,2] - postFull$aP[,1]
+      )
+    ) %>%
+    pivot_longer(cols = !Model, names_to = "parameter", values_to = "Log-odds posterior value") %>%
+    mutate(Model = factor(Model, levels = c("Survival cure", "Post-survey", "Pre-survey"))) %>%
+    ggplot(aes(x = `Log-odds posterior value`, y = Model)) +
[…]

### 2023-08-14 R/functionsDAG.R

@@ -1,0 +1,52 @@
+# custom functions - dag
+
+# draw causal model
+drawDAG <- function() {
+  # coordinates for plot
+  dag_coords <- tibble(
+    name = c("TUu", "TUoLit", "TUoVid", "numLit", "numVid", "EQ", "U", "Phy", "F"),
+    x    = c(0, -1, 1, -2, 2, -1, 0, 1.5, 1),
+    y    = c(1, 2, 2, 1, 1, 0.25, -0.5, -0.5, 0.25)
+  )
+  out <-
+    dagify(TUoVid ~ TUu + numVid,
+           TUoLit ~ TUu + numLit,
+           TUu ~ EQ + F + U,
+           EQ ~ U,
+           F ~ U,
+           U ~ Phy,
+           latent = c("TUu", "U"),
+           coords = dag_coords
+           ) %>%
+    ggplot(aes(x = x, y = y, xend = xend, yend = yend))
+  # modify labels
+  labels <- c("TUu"    = "Tool use\n(unobserved)",
+              "TUoLit" = "Tool use\nobserved in\nliterature",
+              "TUoVid" = "Tool use\nobserved in\ncrowdsourcing",
+              "numLit" = "Number of\nscientific papers\npublished",
+              "numVid" = "Number of\ncrowdsourced\nreports",
+              "EQ"     = "Relative\nbrain size",
+              "F"      = "Feeding\nstrategy",
+              "U"      = "Unobserved\nconfounds",
+              "Phy"    = "Phylogeny")
+  out$data$name <- labels[out$data$name]
+  out$data$to <- labels[out$data$to]
+  # plot
+  out <-
+    out +
+    geom_dag_point(
+      data = function(x) filter(x, name %in% c("Tool use\n(unobserved)", "Unobserved\nconfounds")),
+      alpha = 0.5, size = 35, show.legend = FALSE, colour = "lightgrey"
+    ) +
+    geom_dag_text(colour = "black") +
+    geom_dag_edges(
+      start_cap = ggraph::circle(radius = 1.35, unit = "cm"),
+      end_cap = ggraph::circle(radius = 1.35, unit = "cm")
+    ) +
+    ylim(c(-1, 2.3)) +
+    xlim(c(-2.5, 2.5)) +
+    theme_void()
+  # save
+  ggsave(out, filename = "figures/dag.pdf", height = 4, width = 6)
+  return(out)
+}

### 2023-08-14 R/functionsData.R

@@ -1,0 +1,69 @@
+# custom functions - load data
+
+# convert search hits variable to "search hits before tool use discovered"
+convertSearchHits <- function(dateFirstVideoPublished, searchHits) {
+  # estimate how many search hits there were when the first video of tool use was published
+  # fit model, assuming 1 search hit at youtube inception and exponential growth
+  dateSearchHitsRecorded <- as.Date("2020-03-01")
+  dateYouTubeInception <- as.Date("2005-02-14")
+  d <- data.frame(
+    daysSinceYouTubeInception = c(0, as.numeric(dateSearchHitsRecorded - dateYouTubeInception)),
+    numSearchHits = c(1, searchHits)
+  )
+  m <- lm(numSearchHits ~ daysSinceYouTubeInception, data = d)
+  # make prediction for date video published
+  newdata <- data.frame(daysSinceYouTubeInception = as.numeric(dateFirstVideoPublished - dateYouTubeInception))
+  pred <- predict(m, newdata = newdata)[[1]]
+  out <- round(pred, 0)
+  return(out)
+}
+
+# load main data
+loadData <- function(data_file, litCount_file, crowdData, phylogeny) {
+  # load lit count data for matching
+  litCount <- read.csv(litCount_file)
+  # edit crowdsourcing data
+  crowdData <- 
+    crowdData %>%
+    # mutate species name for matching
+    mutate(Species = str_replace(crowdData$Species, " ", "_")) %>%
+    # for each species, keep earliest video of true tool use
+    group_by(Species) %>%
+    filter(ToolUse == "Y") %>%
+    filter(PublishingDate == min(PublishingDate)) %>%
+    dplyr::select(Species, PublishingDate)
+  # load main data
+  out <- 
+    read_csv(data_file, show_col_types = FALSE) %>% 
+    mutate(
+      # match names with phylogeny
+      Name = str_replace(Name, " ", "_"),
+      # tool use
+      ToolUse = ifelse(VideosFound == 0 & LiteratureExists_Binary == 0, 0, 1)
+      ) %>% 
+    # keep only species in phylogeny
+    filter(Name %in% phylogeny[[1]]$tip.label) %>%
+    # join lit count data
+    left_join(litCount, by = "Name") %>%
+    # join publishing date
+    left_join(crowdData, by = c("Name" = "Species")) %>%
+    # estimate search hits before tool use
+    mutate(
+      SearchHitsPreToolUse = ifelse(
[…]

### 2023-08-14 R/functionsPlotPhylo.R

@@ -1,0 +1,183 @@
+# custom functions - plot phylogeny
+
+# plot maximum clade credibility phylogeny with tool use data
+plotPhylogeny1 <- function(d, MCCphylogeny) {
+  # top ten candidate tool users from survival cure model
+  candidates <- c(
+    "Cacatua_ophthalmica","Poicephalus_meyeri","Guaruba_guarouba",
+    "Cacatua_tenuirostris","Cacatua_ducorpsii","Poicephalus_gulielmi",
+    "Poicephalus_robustus","Ognorhynchus_icterotis","Cacatua_haematuropygia",
+    "Callocephalon_fimbriatum"
+  )
+  # mutate and rename vars
+  d <-
+    d %>%
+    mutate(ToolUse = ifelse(d$ToolUse == 0, "Absent",
+                                   ifelse(d$LiteratureExists_Binary == 1 & d$VideosFound == 0, "Present (in literature only)",
+                                          ifelse(d$LiteratureExists_Binary == 0 & d$VideosFound > 0, "Present (in videos only)",
+                                                 "Present (in videos and lit.)")
+                                   ))) %>%
+    # add "candidate" tool users from survival cure model
+    mutate(ToolUse = ifelse(d$Name %in% candidates, "Top 10 candidate species", ToolUse),
+           ToolUse = factor(ToolUse, levels = c("Present (in videos and lit.)",
+                                                "Present (in literature only)",
+                                                "Present (in videos only)",
+                                                "Top 10 candidate species",
+                                                "Absent"))) %>%
+    # rename variables
+    rename(`Tool Use` = ToolUse, `Search Hits` = SearchHits)
+  # abbreviated species names for labels
+  makeLabel <- function(x) paste0(substring(x, 1, 1), ". ", str_split(x, "_")[[1]][2])
+  for (i in 1:length(d$Name)) {
+    d$Name[i] <- makeLabel(d$Name[i])
+    MCCphylogeny$tip.label[i] <- makeLabel(MCCphylogeny$tip.label[i])
+  }
+  # plot
+  out <- 
[…]

### 2023-08-14 R/functionsSignal.R

@@ -1,0 +1,13 @@
+# custom functions - phylogenetic signal
+
+# get phylogenetic signal
+fitPhySignal <- function(d, phylogeny, iter, dv) {
+  # get data
+  var <- factor(pull(d[,dv]))
+  names(var) <- d$Name
+  # fit model
+  model <- fitDiscrete(phylogeny[[iter]], var, transform = "lambda")
+  # extract lambda
+  out <- model$opt$lambda
+  return(out)
+}

### 2023-08-14 R/functionsSurvivalCure.R

@@ -1,0 +1,786 @@
+# custom functions - survival cure model
+
+# simulation
+simSurvCureModel <- function(model, seed) {
+  # set seed
+  set.seed(seed)
+  # number of species
+  n <- 100
+  # simulate tree
+  phylo <- rtree(n)
+  # scaled distance matrix from phylogeny
+  distMat <- cophenetic.phylo(phylo)
+  distMat <- distMat / max(distMat)
+  # generate standardised EQ
+  EQ <- rnorm(n)
+  # generate feeding type
+  f <- ifelse(rbinom(n, 1, prob = 0.5) == 1, "Generalist", "Specialist")
+  # set simulation parameters
+  etasq <- 2
+  rhosq <- 2
+  aP1 <- 1
+  aP2 <- -1
+  bEQ <- 1.5
+  # simulate tool use
+  # sigma from gaussian process
+  sigma <- etasq*exp(-rhosq*distMat)
+  k <- rmvnorm(1, sigma = sigma)[1,]
+  # log odds probability of tool use
+  p <- ifelse(f == "Generalist", aP1, aP2) + k + bEQ*EQ
+  # simulate tool use
+  t <- rbern(n, inv_logit(p))
+  # simulate time-to-event #1 (number of publications)
+  # https://inla.r-inla-download.org/r-inla.org/doc/likelihood/weibullcure.pdf
+  lambda1 <- 1
+  censorTime1 <- runif(n, 0, 5)
+  y1 <- round(rexp(n, rate = lambda1), 0)
+  # censoring if (1) not measured yet or (2) not a tool user
+  censoredEvent1 <- (y1 > censorTime1) | (t == 0)
+  # censored observations
+  yObs1 <- y1
+  yObs1[censoredEvent1] <- censorTime1[censoredEvent1]
+  event1 <- as.numeric(!censoredEvent1)
+  # simulate time-to-event #1 (number of videos)
+  lambda2 <- 0.01
+  censorTime2 <- runif(n, 0, 600)
+  y2 <- rexp(n, rate = lambda2)
+  # censoring if (1) not measured yet or (2) not a tool user
+  censoredEvent2 <- (y2 > censorTime2) | (t == 0)
+  # censored observations
+  yObs2 <- y2
+  yObs2[censoredEvent2] <- censorTime2[censoredEvent2]
+  event2 <- as.numeric(!censoredEvent2)
+  # data list for stan
+  dat_list <- list(
+    N        = n,
+    eventLit = as.integer(event1),
+    eventVid = as.integer(event2),
[…]

### 2023-08-14 _targets.R

@@ -1,0 +1,206 @@
+library(targets)
+library(tarchetypes)
+library(tidyverse)
+library(future)
+library(future.callr)
+source("R/functionsAncestralState.R")
+source("R/functionsComparisonModels.R")
+source("R/functionsDAG.R")
+source("R/functionsData.R")
+source("R/functionsPlotPhylo.R")
+source("R/functionsSignal.R")
+source("R/functionsSurvivalCure.R")
+options(tidyverse.quiet = TRUE)
+tar_option_set(packages = c("tidyverse", "ape", "brms", "cowplot", "dagitty", 
+                            "geiger", "ggdag", "ggridges", "ggstance", "ggtree", 
+                            "magick", "papaja", "phangorn", "phytools", 
+                            "readxl", "reshape2", "rethinking", "rstan",
+                            "scales", "sdamr", "tidybayes"))
+options(
+  clustermq.scheduler = "slurm", 
+  clustermq.template = "slurm_clustermq.tmpl"
+)
+plan(callr)
+
+# cross-validation static branching (see below)
+cvTargets <-
+  tar_map(
+    # data points to map over (25 data points with observed tool use)
+    values = tibble(cv = c(83, 85, 87, 89, 102, 109, 110, 111, 114,
+                           138, 140, 141, 142, 143, 144, 145, 147,
+                           154, 156, 158, 160, 161, 162, 164, 172)),
+    # fit cv model to data with data point edited, dynamic branching iterating over trees
+    tar_target(crossValSurvCureInd, crossValSurvCureModel(d, phylogeny, iter, survCureFullCompiled, cv), pattern = map(iter), iteration = "list"),
+    # combine models
+    tar_target(crossValSurvCure, rstan::sflist2stanfit(lapply(crossValSurvCureInd, function(x) x))),
+    # posterior samples
+    tar_target(crossValPost, extract.samples(crossValSurvCure)),
+    # did the cross-validation identify the tool-user?
+    tar_target(crossVal, getCrossVal(d, crossValPost, cv))
+  )
+
+# full workflow
+list(
+  
+  ######################
+  # Load and plot data #
+  ######################
+  
+  # load phylogeny
+  tar_target(phylogeny_file, "data/parrotTree.nex", format = "file"),
[…]

### 2023-08-14 run.R

@@ -1,0 +1,1 @@
+targets::tar_make_clustermq(workers = 250L)

### 2023-08-18 manuscript.Rmd
update manuscript for peer review

@@
 keywords          : "tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling"
-wordcount         : "4273 words excluding Methods (Methods: 1792 words)"
+wordcount         : "4289 words excluding Methods (Methods: 1821 words)"
 bibliography      : ["r-references.bib"]
@@
 All other tips are labelled as absent (grey).
+Total _n_ = `r nrow(tar_read(d))` species.
 
@@
 Pagel's $\lambda$ varies between 0 and 1, where 0 implies that the distribution of a trait across species is unexplained by phylogenetic relatedness and 1 implies that the distribution of a trait across species is fully explained by phylogeny.
-Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's $\lambda$ of `r printnum(mean(tar_read(phySignal1)))` (95% credible interval [`r printnum(quantile(tar_read(phySignal1), 0.025))` `r printnum(quantile(tar_read(phySignal1), 0.975))`]).
+Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's $\lambda$ of `r printnum(mean(tar_read(phySignal1)))` (95% credible interval [`r printnum(quantile(tar_read(phySignal1), 0.025))` `r printnum(quantile(tar_read(phySignal1), 0.975))`]; total _n_ = `r nrow(tar_read(d))` species).
 This estimate was moderate-to-strong, but highly uncertain.
 In comparison, combining the evidence from both the literature and the video survey (post-video-survey data; 28 tool-using species) resulted in a stronger and more certain estimate of phylogenetic signal.
-With these data, we estimated Pagel's $\lambda$ = `r printnum(mean(tar_read(phySignal2)))` (95% CI [`r printnum(quantile(tar_read(phySignal2), 0.025))` `r printnum(quantile(tar_read(phySignal2), 0.975))`]).
+With these data, we estimated Pagel's $\lambda$ = `r printnum(mean(tar_read(phySignal2)))` (95% CI [`r printnum(quantile(tar_read(phySignal2), 0.025))` `r printnum(quantile(tar_read(phySignal2), 0.975))`]; total _n_ = `r nrow(tar_read(d))` species).
 Thus, the results of our video survey increase the extent to which the distribution of tool use across parrot species can be explained by shared phylogenetic ancestry.
@@
 (ref:plotSurvCure1Caption) _Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model._ Points are posterior medians and lines are 50% and 95% credible intervals.
+Total _n_ = `r nrow(tar_read(d))` species.
 
@@
 The predicted probabilities from our phylogenetic survival cure model have implications for inferences about the evolutionary drivers and origins of tool use in the parrot order.
-Regarding the drivers of tool use hypothesised in Figure \@ref(fig:plotDAG), the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = `r printnum(median(-postFull$bEQ))`, 95% CI [`r printnum(quantile(-postFull$bEQ, 0.025))` `r printnum(quantile(-postFull$bEQ, 0.975))`]; Figure \@ref(fig:plotSurvCure4)).
+Regarding the drivers of tool use hypothesised in Figure \@ref(fig:plotDAG), the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = `r printnum(median(-postFull$bEQ))`, 95% CI [`r printnum(quantile(-postFull$bEQ, 0.025))` `r printnum(quantile(-postFull$bEQ, 0.975))`]; total _n_ = `r nrow(tar_read(d))` species; Figure \@ref(fig:plotSurvCure4)).
 This helps explain the ranking in Figure \@ref(fig:plotSurvCure1): the blue-eyed cockatoo has the largest relative brain size in the dataset.
-We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = `r printnum(median(diff))`, 95% CI [`r printnum(quantile(diff, 0.025))` `r printnum(quantile(diff, 0.975))`]).
+We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = `r printnum(median(diff))`, 95% CI [`r printnum(quantile(diff, 0.025))` `r printnum(quantile(diff, 0.975))`]; total _n_ = `r nrow(tar_read(d))` species).
 These results from the survival cure model differed from the results of models fitted to pre-video-survey and post-video-survey data without the survival cure component, which found no effect of relative brain size and no difference between feeding strategies, respectively (Supplementary Figure \@ref(fig:plotComparison)).
@@
 In both plots, individual species are coloured according to the presence / absence of tool use in the video survey and the scientific literature.
+Total _n_ = `r nrow(tar_read(d))` species, generalist _n_ = `r sum(tar_read(d)$Feeding == "Generalist")` species, specialist _n_ = `r sum(tar_read(d)$Feeding == "Specialist")` species.
 
@@
 (ref:tableASRCaption) Estimated probabilities of tool use for most recent common ancestors of several parrot genera.
-_Probabilities estimated using exploratory ancestral state reconstruction models fitted to the pre-video-survey data, post-video-survey data, and predicted probabilities from the phylogenetic survival cure model._
+_Probabilities estimated using exploratory ancestral state reconstruction models fitted to the pre-video-survey data, post-video-survey data, and predicted probabilities from the phylogenetic survival cure model.
+Total_ n _= `r nrow(tar_read(d))` species._
 
@@
 We estimated the posterior distribution of this model using Hamiltonian Monte Carlo as implemented in Stan version 2.26.1[@Stan2020].
-We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
+We ran the model for 4000 samples, with 2000 warmup samples, and iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
 R-hat values and effective sample sizes suggested that the model converged normally.
 Trace plots are reported in Supplementary Figure \@ref(fig:plotTrace).
+We report equal-tailed credible intervals to describe the posterior distribution of this model in the main text.
 

### 2023-08-18 manuscript.tex
update manuscript for peer review

@@
 {}{\PatchFailed}
-\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling\newline\indent Word count: 4273 words excluding Methods (Methods: 1792 words)}
+\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling\newline\indent Word count: 4289 words excluding Methods (Methods: 1821 words)}
 \usepackage{lineno}
@@
 Yellow tips indicate the top ten most likely tool-using species from our phylogenetic survival cure model which were not observed in the scientific literature or the video survey.
-All other tips are labelled as absent (grey).}
+All other tips are labelled as absent (grey).
+Total \emph{n} = 174 species.}
 \end{figure}
@@
 Pagel's \(\lambda\) varies between 0 and 1, where 0 implies that the distribution of a trait across species is unexplained by phylogenetic relatedness and 1 implies that the distribution of a trait across species is fully explained by phylogeny.
-Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's \(\lambda\) of 0.60 (95\% credible interval {[}0.00 0.90{]}).
+Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's \(\lambda\) of 0.60 (95\% credible interval {[}0.00 0.90{]}; total \emph{n} = 174 species).
 This estimate was moderate-to-strong, but highly uncertain.
 In comparison, combining the evidence from both the literature and the video survey (post-video-survey data; 28 tool-using species) resulted in a stronger and more certain estimate of phylogenetic signal.
-With these data, we estimated Pagel's \(\lambda\) = 0.65 (95\% CI {[}0.50 0.77{]}).
+With these data, we estimated Pagel's \(\lambda\) = 0.65 (95\% CI {[}0.50 0.77{]}; total \emph{n} = 174 species).
 Thus, the results of our video survey increase the extent to which the distribution of tool use across parrot species can be explained by shared phylogenetic ancestry.
@@
 \includegraphics{manuscript_files/figure-latex/plotSurvCure1-1.pdf}
-\caption{\label{fig:plotSurvCure1}\emph{Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model.} Points are posterior medians and lines are 50\% and 95\% credible intervals.}
+\caption{\label{fig:plotSurvCure1}\emph{Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model.} Points are posterior medians and lines are 50\% and 95\% credible intervals.
+Total \emph{n} = 174 species.}
 \end{figure}
@@
 The predicted probabilities from our phylogenetic survival cure model have implications for inferences about the evolutionary drivers and origins of tool use in the parrot order.
-Regarding the drivers of tool use hypothesised in Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = 1.12, 95\% CI {[}0.39 2.00{]}; Figure \ref{fig:plotSurvCure4}).
+Regarding the drivers of tool use hypothesised in Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = 1.12, 95\% CI {[}0.39 2.00{]}; total \emph{n} = 174 species; Figure \ref{fig:plotSurvCure4}).
 This helps explain the ranking in Figure \ref{fig:plotSurvCure1}: the blue-eyed cockatoo has the largest relative brain size in the dataset.
-We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = 0.33, 95\% CI {[}-1.13 1.76{]}).
+We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = 0.33, 95\% CI {[}-1.13 1.76{]}; total \emph{n} = 174 species).
 These results from the survival cure model differed from the results of models fitted to pre-video-survey and post-video-survey data without the survival cure component, which found no effect of relative brain size and no difference between feeding strategies, respectively (Supplementary Figure \ref{fig:plotComparison}).
@@
 In the right plot, the line and shaded area represents the posterior median regression line with 95\% credible intervals.
-In both plots, individual species are coloured according to the presence / absence of tool use in the video survey and the scientific literature.}
+In both plots, individual species are coloured according to the presence / absence of tool use in the video survey and the scientific literature.
+Total \emph{n} = 174 species, generalist \emph{n} = 121 species, specialist \emph{n} = 53 species.}
 \end{figure}
@@
 \caption{\label{tab:tableASR}Estimated probabilities of tool use for most recent common ancestors of several parrot genera.
-\emph{Probabilities estimated using exploratory ancestral state reconstruction models fitted to the pre-video-survey data, post-video-survey data, and predicted probabilities from the phylogenetic survival cure model.}}
+\emph{Probabilities estimated using exploratory ancestral state reconstruction models fitted to the pre-video-survey data, post-video-survey data, and predicted probabilities from the phylogenetic survival cure model.
+Total} n \emph{= 174 species.}}
 
@@
 We estimated the posterior distribution of this model using Hamiltonian Monte Carlo as implemented in Stan version 2.26.1\textsuperscript{80}.
-We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
+We ran the model for 4000 samples, with 2000 warmup samples, and iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
 R-hat values and effective sample sizes suggested that the model converged normally.
 Trace plots are reported in Supplementary Figure \ref{fig:plotTrace}.
+We report equal-tailed credible intervals to describe the posterior distribution of this model in the main text.
 

### 2023-11-20 manuscript.Rmd
prepare for submission

@@
 abstract: |
- Studying the prevalence of putatively rare behaviours, such as tool use, is challenging because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort.
-Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to approximate actual rates of a rarely observed behaviour based on limited data, targeting tool use in parrots.
-Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%).
-Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11% and 17% of extant parrot species may be tool users.
-These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait.
-Overall, our findings challenge the assumption that current sampling effort captures the full distribution of putatively rare animal behaviours.
-Combining our sampling and analysis methods offers a fruitful approach for investigating the distribution, drivers, and origins of other rare behaviours.
+ Putatively rare behaviours, such as tool use, are challenging to study because absence of evidence can arise either from a species’ inability to produce the behaviour or from insufficient research effort.
+Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to estimate actual rates of tool use in parrots.
+Crowdsourcing revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%).
+Phylogenetic models incorporating these data together with measures of research effort and hypothesised predictors of tool use suggest that between 11% and 17% of parrot species may be tool users.
+These findings challenge the assumption that current research effort captures the distribution of putatively rare animal behaviours.
 
 keywords          : "tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling"
-wordcount         : "4289 words excluding Methods (Methods: 1821 words)"
+wordcount         : "6548 words"
 bibliography      : ["r-references.bib"]
@@
   - \nolinenumbers
-  - \note{\raggedright † indicates shared first authorship, ‡ indicates shared senior authorship \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand.
+  - \note{\raggedright † These authors contributed equally to this work \par ‡ These authors contributed equally to this work \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand.
 \text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}} \par This working paper has not yet been peer-reviewed.}
 appendix          : "appendix.Rmd"
-csl               : nature.csl
+csl               : science.csl
 ---
 
-\linenumbers
+\nolinenumbers
 
-Our understanding of the evolution of animal behaviour is built on the assumption that we have access to sufficient data[@MacLean2012; @Lefebvre2011; @Logan2018].
-However, this is not always the case.
-Data on behaviours that are rare, fleeting, or otherwise difficult to observe are likely to be patchy and incomplete[@Healy2007; @Powell2017].
-Among species for which such behaviours have not been observed, it can be difficult to differentiate between cases in which the species is truly incapable of producing the behaviour and cases in which the species is capable of producing the behaviour but the behaviour has not yet been observed.
-Such a distinction can be critical for drawing conclusions about the rarity and evolution of the behaviour in question.
+Our understanding of the evolution of animal behaviour is built on the 
+assumption that we have access to sufficient data [@MacLean2012; @Lefebvre2011; 
+@Logan2018]. However, this is not always the case. Data on behaviours that are 
+rare, fleeting, or otherwise difficult to observe are likely to be patchy and 
+incomplete [@Healy2007; @Powell2017]. Among species for which such behaviours 
+have not been observed, it can be difficult to differentiate between cases in 
+which the species is truly incapable of producing the behaviour and cases in 
+which the species is capable of producing the behaviour but the behaviour has 
+not yet been observed. Such a distinction can be critical for drawing 
+conclusions about the rarity and evolution of the behaviour in question.
 
-Comparative work on the evolution of tool use is a paradigmatic example of this issue.
-The initial discoveries of tool use in chimpanzees[@Goodall1964], birds[@Hunt1996], dolphins[@Smolker1997], and octopuses[@Finn2009] occurred decades after significant advances on other more easily measurable aspects of their biology.
-Since these initial discoveries, scholars have used the distribution of reported tool use across species to make various claims about the evolutionary drivers of tool use behaviours.
-For example, based on the observation that bird species with reported tool use tended to have larger brains, researchers have identified higher relative brain size as a likely precondition for tool using capabilities[@Lefebvre2002;@Lefebvre1997;@Lefebvre2004].
-These researchers argue that larger brains are better able to integrate visual and somatosensory information when innovating novel behaviours, such as tool use, in changing environments[@Sol2005;@Sol2009].
-Similarly, researchers have used existing reports of tool use in birds to debate the roles of generalist versus specialist feeding strategies in driving the evolution of tool use, with some arguing that feeding generalists require technical innovations to expand their dietary niche[@Ducatez2015;@Overington2011;@Sol2005] and others arguing that feeding specialists require technical innovations for extractive foraging of specific foods[@HenkeVonDerMalsburg2020;@MettkeHofmann2014].
+Comparative work on the evolution of tool use is a paradigmatic example of this 
+issue. The initial discoveries of tool use in chimpanzees [@Goodall1964], 
+birds [@Hunt1996], dolphins [@Smolker1997], and octopuses [@Finn2009] occurred 
+decades after significant advances on other more easily measurable aspects of 
+their biology. Since then, scholars have proposed a clear operational 
+definition of tool use applicable to all species --- the manipulation of an 
+unattached object as an extension of the animal's body to achieve a 
+goal [@Shumaker2011] --- and have used the distribution of species meeting this 
+definition to make various claims about the evolutionary drivers of tool use 
+behaviours. For example, based on the observation that bird species with 
+reported tool use tended to have larger brains, researchers have identified 
+higher relative brain size as a likely precondition for tool using 
+capabilities [@Lefebvre2002;@Lefebvre1997;@Lefebvre2004]. These researchers 
+argue that larger brains are better able to integrate visual and somatosensory 
+information when innovating novel behaviours, such as tool use, in changing 
+environments [@Sol2005;@Sol2009]. Similarly, researchers have used existing 
+reports of tool use in birds to debate the roles of generalist versus 
+specialist feeding strategies in driving the evolution of tool use, with some 
+arguing that feeding generalists require technical innovations to expand their 
+dietary niche [@Ducatez2015;@Overington2011;@Sol2005] and others arguing that 
+feeding specialists require technical innovations for extractive foraging of 
+specific foods [@HenkeVonDerMalsburg2020;@MettkeHofmann2014].
 
-However, before we can make claims of this kind, we need to know whether current research effort in the literature is sufficient for robust conclusions to be drawn about the evolution of tool use.
-In fact, evidence suggests that research effort is often systematically biased towards particular taxonomic groups, parts of the world that are easy to access, and species with life history traits that make them easier to study, such as larger distribution ranges and population sizes[@Ducatez2014].
-This is a crucial limitation because insufficient observation may lead researchers to miss true instances of tool behaviours and thus draw premature conclusions about the evolutionary drivers and origins of tool use.
-While researchers have attempted to deal with this problem by controlling for the number of scientific papers published on different species, previous work has not yet attempted to quantify and explicitly model the relationship between actual tool-using behaviour and what is reported in the scientific literature.
-If more tool-using species exist than previously thought, this could have important implications for theories of the evolutionary drivers and origins of tool use and, more generally, for our understanding of how rare this behaviour actually is.
+However, before we can make claims of this kind, we need to know whether current 
+research effort in the literature is sufficient for robust conclusions to be 
+drawn about the evolution of tool use. In fact, evidence suggests that research 
+effort is often systematically biased towards particular taxonomic groups, parts 
+of the world that are easy to access, and species with life history traits that 
+make them easier to study, such as larger distribution ranges and population 
+sizes [@Ducatez2014]. This is a crucial limitation because insufficient 
+observation may lead researchers to miss true instances of tool behaviours and 
+thus draw premature conclusions about the evolutionary drivers and origins of 
+tool use. While researchers have attempted to deal with this problem by 
+controlling for the number of scientific papers published on different species, 
+previous work has not yet attempted to quantify and explicitly model the 
+relationship between actual tool-using behaviour and what is reported in the 
+scientific literature. If more tool-using species exist than previously thought, 
+this could have important implications for theories of the evolutionary drivers 
+and origins of tool use and for our understanding of how rare this behaviour 
+actually is.
 
-One potentially powerful method for quantifying actual rates of rare animal behaviours is crowdsourcing[@Nelson2013].
-In a crowdsourcing study, researchers collect reports from the general public and/or collate and analyse videos posted on social media platforms.
-This citizen science approach has been widely used in ecology to monitor the distributional patterns of species[@Dickinson2010], but has also recently been used to uncover a variety of rare animal behaviours, including interspecies play in dogs[@Nelson2013], novel problem-solving behaviours in horses[@Krueger2019], and socially-learned foraging innovations in cockatoos[@Klump2021;@Klump2022].
-By casting the net wider than the scientific literature, the crowdsourcing method can provide an indication of the tool-using species that the literature might be missing.
+One potentially powerful method for quantifying actual rates of rare animal 
+behaviours is crowdsourcing [@Nelson2013]. In a crowdsourcing study, researchers 
+collect reports from the general public and/or collate and analyse videos posted 
+on social media platforms. This citizen science approach has been widely used in 
+ecology to monitor the distributional patterns of species [@Dickinson2010], but 
+has also recently been used to uncover a variety of rare animal behaviours, 
+including interspecies play in dogs [@Nelson2013], novel problem-solving 
+behaviours in horses [@Krueger2019], and socially-learned foraging innovations 
+in cockatoos [@Klump2021;@Klump2022]. By casting the net wider than the 
+scientific literature, the crowdsourcing method can provide an indication of the 
+tool-using species that the literature might be missing.
 
-Even after using this crowdsourcing approach, some tool-users could _still_ remain unobserved.
-An additional approach to identify these unobserved species is to specify a causal model of the process that generates the observed data.
-We propose one such causal model in Figure \@ref(fig:plotDAG).
-In this model, we assume that the presence of tool use in the scientific literature (or in crowdsourced reports) is caused by both unobserved tool use capabilities and the number of published studies (or the number of crowdsourced reports) for any given species.
-Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected.
-Furthermore, based on existing theories of the evolution of tool use[@Ducatez2015;@HenkeVonDerMalsburg2020;@Lefebvre1997;@Lefebvre2002;@Lefebvre2004;@MettkeHofmann2014;@Overington2011;@Sol2005;@Sol2009], we propose that the unobserved presence or absence of tool use is additionally caused by relative brain size, feeding strategy, and shared phylogenetic ancestry.
-Expressing this causal model as a statistical model can suggest further species which are likely to be unobserved tool-users and, simultaneously, test existing theories of the evolutionary drivers of tool use without incorrectly assuming that absence of evidence is evidence of absence.
+Even after using this crowdsourcing approach, some tool-users could _still_ 
+remain unobserved. One principled framework for identifying these unobserved species 
+is to specify a causal model of the process that generates the observed data. We 
+propose one such causal model in Figure \@ref(fig:plotDAG). In this model, we 
+assume that the presence of tool use in the scientific literature (or in 
+crowdsourced reports) is caused by both unobserved tool use capabilities and the 
+number of published studies (or the number of crowdsourced reports) for any 
+given species. Tool users are more likely to be observed if they are well 
+studied, but understudied tool users may go undetected. Furthermore, based on 
+existing theories of the evolution of tool use [@Ducatez2015;
+@HenkeVonDerMalsburg2020;@Lefebvre1997;@Lefebvre2002;@Lefebvre2004;
+@MettkeHofmann2014;@Overington2011;@Sol2005;@Sol2009], we propose that the 
+unobserved tool use capabilities are additionally caused by relative brain size, 
+feeding strategy, and shared phylogenetic ancestry. Expressing this causal model 
+as a statistical model can suggest further species which are likely to be 
+unobserved tool-users and, simultaneously, test existing theories of the 
+evolutionary drivers of tool use without incorrectly assuming that absence of 
+evidence is evidence of absence.
 
-(ref:plotDAGCaption) _Causal model of observed tool use._ Directed acyclic graph of the causal relationships between observed tool use and other variables.
-Available scientific data on tool use is caused both by unobserved tool use presence and scientific research effort (i.e., number of publications).
-Available crowdsourced data on tool use is caused both by unobserved tool use presence and crowdsourcing effort (i.e., number of crowdsourced reports).
-According to theory, unobserved tool use presence should be caused by relative brain size (encephalisation quotient) and feeding strategy (generalist vs.
-specialist).
-These variables all share unobserved confounds generated by shared phylogenetic history.
-Grey circles indicate unobserved variables.
+(ref:plotDAGCaption) _Causal model of observed tool use._ Directed acyclic graph 
+of the causal relationships between observed tool use and other variables. 
+Available scientific data on tool use is caused both by unobserved tool use 
+presence and scientific research effort (i.e., number of publications). 
+Available crowdsourced data on tool use is caused both by unobserved tool use 
+presence and crowdsourcing effort (i.e., number of crowdsourced reports). 
+According to theory, unobserved tool use presence should be caused by relative 
+brain size (encephalisation quotient) and feeding strategy (generalist vs. 
+specialist). These variables all share unobserved confounds generated by shared 
+phylogenetic history. Grey circles indicate unobserved variables.
 
@@
 
-Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool use in the parrot order.
-We focus on tool use in parrots for a number of reasons.
-First, the scientific literature suggests that only a small proportion of extant parrot species (11 out of 398[@Burgio2019]; 3%) use tools[@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;@Auersperg2012;@Bastos2021;@BentleyCondit2010;@Borsari2005;@Goodman2018;@Heinsohn2017;@Janzen1976;@Lambert2015;@Lefebvre2002;@OHara2021] (note that we do not include in this count species that have been previously shown to use touchscreen devices as these behaviours were explicitly trained[@Kleinberger2023]).
-Parrot tool use thus provides an ideal test case for examining how robust sampling is in the scientific literature.
-Second, parrots are highly popular as pets.
-Over 70% of all extant parrot species are bred in the aviculture industry and kept as pets worldwide[@Anderson2003;@Carrete2008;@Drews2001;@Kelly2014;@Li2014;@Su2015;@Young2012], enabling us to leverage the power of crowdsourcing on a social media platform to search for evidence of tool use[@Nelson2013].
-Third, detailed data on relative brain sizes[@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;@Schuck2008;@Silva2017], feeding strategies[@Wilman2016], and shared ancestry[@Jetz2012] exist for parrots, allowing us to fit the statistical model implied by Figure \@ref(fig:plotDAG) to the entire parrot order.
+Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool 
+use in the parrot order. We focus on tool use in parrots for a number of 
+reasons. First, the scientific literature suggests that only a small proportion 
+of extant parrot species (11 out of 398; 3%) use tools 
+[@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;@Auersperg2012;
+@Bastos2021;@BentleyCondit2010;@Borsari2005;@Goodman2018;@Heinsohn2017;
+@Janzen1976;@Lambert2015;@Lefebvre2002;@OHara2021]. Parrot tool use 
+thus provides an ideal test case for examining how robust sampling is in the 
+scientific literature. Second, parrots are highly popular as pets. Over 70% of 
+all extant parrot species are bred in the aviculture industry and kept as pets 
+worldwide [@Anderson2003;@Carrete2008;@Drews2001;@Kelly2014;@Li2014;@Su2015;
+@Young2012], enabling us to leverage the power of crowdsourcing on a social 
+media platform to search for evidence of tool use [@Nelson2013]. Third, detailed 
+data on relative brain sizes [@Flammer2001;@Iwaniuk2005;@Mazengenya2018;
+@Olkowicz2016;@Schuck2008;@Silva2017], feeding strategies [@Wilman2016], and 
+shared ancestry [@Jetz2012] exist for parrots, allowing us to fit the 
+statistical model implied by Figure \@ref(fig:plotDAG) to the entire parrot 
+order.
 
-We first present the results from our crowdsourcing survey, in which we collated videos of tool use in parrots from an online video platform.
-This survey reveals a number of previously unidentified tool-using parrot species, which we map onto the phylogeny of the parrot order.
-We then describe our statistical model in more detail, and use it to (_i_) rank further parrot species that are likely unobserved tool users and (_ii_) re-examine key hypotheses regarding the evolutionary drivers and origins of tool use in parrots.
+We first present the results from our crowdsourcing survey, in which we collated 
+videos of tool use in parrots from an online video platform. This survey reveals 
+a number of previously unidentified tool-using parrot species, which we map onto 
+the phylogeny of the parrot order. We then describe our statistical model in 
+more detail, and use it to (_i_) rank further parrot species that are likely 
+unobserved tool users and (_ii_) re-examine key hypotheses regarding the 
+evolutionary drivers and origins of tool use in parrots.
 
@@
 
-## Crowdsourcing video survey
+## Crowdsourcing reveals tool use in additional parrot species
 
-We surveyed the social media platform YouTube for video evidence of tool use in parrots (see Methods for detailed search criteria).
-In our search, we defined "true" tool use behaviour as the manipulation of an unattached object to achieve a goal[@Shumaker2011], while "borderline" tool use involved the use of an object that was still attached to a substrate[@Seed2010].
+We surveyed the social media platform YouTube for video evidence of tool use in 
+parrots (see Methods for detailed search criteria). In our search, we used the 
+standard criteria for identifying tool use in the literature, defining "true" 
+tool use behaviour as the manipulation of an unattached object as an extension 
+of the animal's body to achieve a goal [@Shumaker2011], while "borderline" tool 
+use involved the use of an object that was still attached to a substrate
+[@Seed2010].
 
@@
 
-In total, we found `r nrow(crowdData)` videos of `r crowdData %>% pull(IndividualID) %>% unique() %>% length()` individuals from `r crowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` parrot species performing either true tool use (`r nrow(trueCrowdData)` videos of `r trueCrowdData %>% pull(IndividualID) %>% unique() %>% length()` individuals from `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` species) or borderline tool use (`r nrow(bordCrowdData)` videos of `r bordCrowdData %>% pull(IndividualID) %>% unique() %>% length()` individuals from `r bordCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` species).
-All videos featured pet parrots in captive settings.
-In `r crowdData %>% pull(HumanInfluence) %>% str_starts("No") %>% sum()` of these videos, owners did not appear to interfere with the subjects' actions.
-In `r crowdData %>% pull(HumanInfluence) %>% str_starts("Yes") %>% sum()` videos, there was potential interference, either from the owners being in close physical contact with the bird (e.g., bird perching on hand), talking to the bird, or handing it the tool (which occurred in only two videos).
-We could not establish the degree of interference in the remaining `r crowdData %>% pull(HumanInfluence) %>% str_starts("Unknown") %>% sum()` videos, as sound had been removed or was substituted by music.
-None of the videos featured owners directly rewarding tool use behaviours with food.
-All borderline tool use cases were excluded from further analyses.
+In total, we found `r nrow(crowdData)` videos of 
+`r crowdData %>% pull(IndividualID) %>% unique() %>% length()` individuals from 
+`r crowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` 
+parrot species performing behaviours that met the definition of either true tool 
+use (`r nrow(trueCrowdData)` videos of 
+`r trueCrowdData %>% pull(IndividualID) %>% unique() %>% length()` 
+individuals from 
+`r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` 
+species) or borderline tool use (`r nrow(bordCrowdData)` videos of 
+`r bordCrowdData %>% pull(IndividualID) %>% unique() %>% length()` 
+individuals from 
+`r bordCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` 
+species). All videos featured pet parrots in captive settings. In 
+`r crowdData %>% pull(HumanInfluence) %>% str_starts("No") %>% sum()` of these 
+videos, owners did not appear to interact with the subjects. In 
+`r crowdData %>% pull(HumanInfluence) %>% str_starts("Yes") %>% sum()` videos, 
+there was potential human interaction, either from the owners being in close physical 
+contact with the bird (e.g., bird perching on hand), talking to the bird, or 
+handing it the tool (which occurred in only two videos). We could not establish 
+the degree of human interaction in the remaining 
+`r crowdData %>% pull(HumanInfluence) %>% str_starts("Unknown") %>% sum()` 
+videos, as sound had been removed or was substituted by music. None of the 
+videos featured owners directly rewarding tool use behaviours with food. All 
+borderline tool use cases were excluded from further analyses.
 
-Of the `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` parrot species performing true tool use, `r trueCrowdData %>% filter(Species != "Unknown") %>% group_by(Species, IndividualID) %>% summarise(n = n(), .groups = "drop") %>% group_by(Species) %>% summarise(check = n() > 1, .groups = "drop") %>% pull(check) %>% sum()` were represented in our video survey by two or more individuals over multiple independent observations.
-True tool use always involved the subject using an object for self-scratching (`r trueCrowdData %>% mutate(BodyPartScratched = str_detect(BodyPartScratched, "Head/Neck")) %>% pull(BodyPartScratched) %>% sum()` videos involved scratching the head and/or neck).
-The most common tool (`r sum(pull(trueCrowdData, EvaluatedTool) == "Feather")` videos) was a moulted feather.
-Human-made objects (e.g., pens, spoons, pieces of wood, cardboard) were also common.
+Of the `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` 
+parrot species performing true tool use, 
+`r trueCrowdData %>% filter(Species != "Unknown") %>% group_by(Species, IndividualID) %>% summarise(n = n(), .groups = "drop") %>% group_by(Species) %>% summarise(check = n() > 1, .groups = "drop") %>% pull(check) %>% sum()`
+were represented in our video survey by two or more individuals over multiple 
+independent observations. True tool use always involved the subject using an 
+object for self-scratching (`r trueCrowdData %>% mutate(BodyPartScratched = str_detect(BodyPartScratched, "Head/Neck")) %>% pull(BodyPartScratched) %>% sum()` 
+videos involved scratching the head and/or neck). The most common tool (`r sum(pull(trueCrowdData, EvaluatedTool) == "Feather")`
+videos) was a moulted feather. Human-made objects (e.g., pens, spoons, pieces of 
+wood, cardboard) were also common.
 
-According to YouTube video descriptions and owner comments, `r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Male"))` of the individuals performing true tool use were males and `r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Female"))` were females.
-No sex information was provided for the remaining `r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Unknown"))` individuals.
-As owners provided no information on whether sex had been established through genetic testing, and sexual dimorphism in parrots is rare[@Bercovitz1987;@Hoyo2011], we could not typically ascertain if descriptions were accurate.
-It is unclear if the disproportionately large number of males in the sample is a consequence of owners more readily assuming their parrots are male when they have not been genetically tested, owners being more likely to own or film male parrots, or male parrots exhibiting more true tool use behaviours than female parrots.
+According to YouTube video descriptions and owner comments, 
+`r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Male"))` 
+of the individuals performing true tool use were males and 
+`r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Female"))` 
+were females. No sex information was provided for the remaining 
+`r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Unknown"))` 
+individuals. As owners provided no information on whether sex had been 
+established through genetic testing, and sexual dimorphism in parrots is 
+rare [@Bercovitz1987;@Hoyo2011], we could not typically ascertain if descriptions 
+were accurate. It is unclear if the disproportionately large number of males in 
+the sample is a consequence of owners more readily assuming their parrots are 
+male when they have not been genetically tested, owners being more likely to own 
+or film male parrots, or male parrots exhibiting more true tool use behaviours 
+than female parrots.
 
-Figure \@ref(fig:plotPhylo1) maps the findings from the video survey onto a maximum clade credibility phylogeny for the parrot order, plotted alongside species previously identified in the scientific literature.
-Before the video survey, 11 parrot species (3%) had been identified as tool users in the scientific literature.
-Across our video survey, we observed true tool use in `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` species, 5 of which overlapped with the scientific literature and `r (trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()) - 5` of which were novel species.
-All of the species identified in the video survey were cockatoos (Cacatuidae), Old World parrots (Psittacinae), or neotropical parrots (Arinae).
-The most common species in our survey, accounting for `r crowdData %>% filter(Species == "Pyrrhura molinae") %>% nrow()` videos from `r crowdData %>% filter(Species == "Pyrrhura molinae") %>% pull(IndividualID) %>% unique() %>% length()` individuals, was the green-cheeked conure (_Pyrrhura molinae_).
-In accordance with the scientific literature, the video survey found no evidence of tool use in any species of Psittaculidae, despite this family containing some of the most commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet species.
-Combining both the video survey and the scientific literature, we can thus identify 28 tool-using parrot species overall (7%), compared to the 11 previously reported.
+Figure \@ref(fig:plotPhylo1) maps the findings from the video survey onto a 
+maximum clade credibility phylogeny for the parrot order, plotted alongside 
+species previously identified in the scientific literature. Before the video 
+survey, 11 parrot species (3%) had been identified as tool users in the 
+scientific literature. Across our video survey, we observed true tool use in 
+`r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` 
+species, 5 of which overlapped with the scientific literature and 
+`r (trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()) - 5` 
+of which were novel species. All of the species identified in the video survey 
+were cockatoos (_Cacatuidae_), Old World parrots (_Psittacinae_), or neotropical 
+parrots (_Arinae_). The most common species in our survey, accounting for 
+`r crowdData %>% filter(Species == "Pyrrhura molinae") %>% nrow()` videos from 
+`r crowdData %>% filter(Species == "Pyrrhura molinae") %>% pull(IndividualID) %>% unique() %>% length()` 
+individuals, was the green-cheeked conure (_Pyrrhura molinae_). In accordance 
+with the scientific literature, the video survey found no evidence of tool use 
+in any species of Psittaculidae, despite this family containing some of the most 
+commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet 
+species. Combining both the video survey and the scientific literature, we can 
+thus identify 28 tool-using parrot species overall (7%), compared to the 11 
+previously reported.
 
-(ref:plotPhylo1Caption) _Results of crowdsourcing video survey and phylogenetic survival cure modelling mapped onto a maximum clade credibility phylogeny of the parrot order._ Purple tips indicate species observed in the scientific literature and in the video survey.
-Blue tips indicate species observed only in the scientific literature.
-Orange tips indicate species observed only in the video survey (note that three species observed only in the video survey are not present in the phylogeny due to a lack of genomic data: _Psittacara erythrogenys_, _Psittacus timneh_, and _Aratinga nenday_).
-Yellow tips indicate the top ten most likely tool-using species from our phylogenetic survival cure model which were not observed in the scientific literature or the video survey.
-All other tips are labelled as absent (grey).
+(ref:plotPhylo1Caption) _Results of crowdsourcing video survey and phylogenetic 
+survival cure modelling mapped onto a maximum clade credibility phylogeny of the 
+parrot order._ Orange points in the inner ring indicate species observed in the 
+video survey, with point size scaled by the number of videos for each species 
+(note that three species observed only in the video survey are not present in 
+the phylogeny due to a lack of genomic data: _Psittacara erythrogenys_, 
+_Psittacus timneh_, and _Aratinga nenday_). Blue points in the outer ring 
+indicate species observed in the scientific literature, with point size scaled 
+by the number of papers published on each species. Yellow species names indicate 
+the top ten most likely tool-using species from our phylogenetic survival cure 
+model which were not observed in the scientific literature or the video survey. 
 Total _n_ = `r nrow(tar_read(d))` species.
@@
 
-The identification of new tool-using species in our video survey increases the extent to which phylogeny can explain the distribution of tool use in the parrot order.
-We estimated phylogenetic signal (Pagel's $\lambda$) of tool use using both the pre-video-survey and post-video-survey data.
-Pagel's $\lambda$ varies between 0 and 1, where 0 implies that the distribution of a trait across species is unexplained by phylogenetic relatedness and 1 implies that the distribution of a trait across species is fully explained by phylogeny.
-Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's $\lambda$ of `r printnum(mean(tar_read(phySignal1)))` (95% credible interval [`r printnum(quantile(tar_read(phySignal1), 0.025))` `r printnum(quantile(tar_read(phySignal1), 0.975))`]; total _n_ = `r nrow(tar_read(d))` species).
-This estimate was moderate-to-strong, but highly uncertain.
-In comparison, combining the evidence from both the literature and the video survey (post-video-survey data; 28 tool-using species) resulted in a stronger and more certain estimate of phylogenetic signal.
-With these data, we estimated Pagel's $\lambda$ = `r printnum(mean(tar_read(phySignal2)))` (95% CI [`r printnum(quantile(tar_read(phySignal2), 0.025))` `r printnum(quantile(tar_read(phySignal2), 0.975))`]; total _n_ = `r nrow(tar_read(d))` species).
-Thus, the results of our video survey increase the extent to which the distribution of tool use across parrot species can be explained by shared phylogenetic ancestry.
-This suggests that we can potentially use phylogenetic information, along with other variables, to identify further tool-using parrot species that may remain undetected.
+The identification of new tool-using species in our video survey increases the 
+extent to which phylogeny can explain the distribution of tool use in the parrot 
+order. We estimated phylogenetic signal (Pagel's $\lambda$) of tool use using 
+both the pre-video-survey and post-video-survey data. Pagel's $\lambda$ varies 
+between 0 and 1, where 0 implies that the distribution of a trait across species 
+is unexplained by phylogenetic relatedness and 1 implies that the distribution 
+of a trait across species is fully explained by phylogeny. Using the evidence of 
+tool use from the scientific literature alone (pre-video-survey data; 11 
+tool-using species), we estimated an average posterior Pagel's $\lambda$ of 
+`r printnum(mean(tar_read(phySignal1)))` (95% credible interval [`r printnum(quantile(tar_read(phySignal1), 0.025))` 
+`r printnum(quantile(tar_read(phySignal1), 0.975))`]; total _n_ = 
+`r nrow(tar_read(d))` species). This estimate was moderate-to-strong, but highly 
+uncertain. In comparison, combining the evidence from both the literature and 
+the video survey (post-video-survey data; 28 tool-using species) resulted in a 
+stronger and more certain estimate of phylogenetic signal. With these data, we 
+estimated Pagel's $\lambda$ = `r printnum(mean(tar_read(phySignal2)))` (95% CI 
+[`r printnum(quantile(tar_read(phySignal2), 0.025))` 
+`r printnum(quantile(tar_read(phySignal2), 0.975))`]; total _n_ = 
+`r nrow(tar_read(d))` species). Thus, the results of our video survey increase 
+the extent to which the distribution of tool use across parrot species can be 
+explained by shared phylogenetic ancestry. This suggests that we can potentially 
+use phylogenetic information, along with other variables, to identify further 
+tool-using parrot species that may remain undetected.
 
-## Phylogenetic survival cure model
+## Phylogenetic survival cure modelling identifies further candidate tool users
 
-In addition to the 28 tool-using species identified in the literature and our video survey, we fitted a Bayesian phylogenetic survival cure model to rank further species that are likely to be undetected tool-users (i.e., tool-using species with no tool use reported in the literature or in crowdsourced videos).
+In addition to the 28 tool-using species identified in the literature and our 
+video survey, we fitted a Bayesian phylogenetic survival cure model to rank 
+further species that are likely to be undetected tool-users (i.e., tool-using 
+species with no tool use reported in the literature or in crowdsourced videos).
 
-Survival cure models are often used in the medical sciences to analyse the time to some event, such as cancer relapse, with censored patient data[@Amico2018].
-The data are right-censored because some patients have relapsed when they are measured, and some have not yet relapsed when they are measured (i.e., they are censored).
-The cure aspect of these models comes from an additional assumption that a certain proportion of the population is "cured" and can never relapse, no matter how long we measure them for.
+Survival cure models [@Amico2018], also known as split population 
+models [@Schmidt1989], are used to analyse the time to some event of interest 
+with the added assumption that a certain proportion of the population will never 
+experience the event, no matter how long they are measured for. These models 
+have been used to analyse a variety of right-censored outcomes, from cancer 
+relapse [@Amico2018] to criminal recidivism [@Schmidt1989]. The data are 
+right-censored because some individuals will have experienced the event when 
+they are measured (e.g., disease onset, return to prison) while others will have 
+not experienced the event. For those who have not experienced the event, this 
+may be because (_i_) the event has not happened to them yet or (_ii_) the event 
+will _never_ happen to them. Survival cure models treat these two processes 
+separately.
 
-Our tool use problem has the same features.
-We are modelling a time-to-event; specifically, the amount of "time" (i.e., observation opportunities measured as the number of published papers or crowdsourced videos) until tool use is identified.
-This is right-censored data, because many species will not have had tool use identified when we measure them.
-Moreover, we can assume that a certain proportion of the population is "cured" -- that is, they are not tool users, and so we will never identify tool use for them, no matter how long we measure them for.
+Our tool use problem has the same features. We are modelling a time-to-event; 
+specifically, the amount of "time" (i.e., observation opportunities measured as 
+the number of published papers or crowdsourced videos) until tool use is 
+identified. This is right-censored data because many species will not have had 
+tool use identified when we measure them. Moreover, we can assume that a certain 
+proportion of the population will never experience the event -- that is, they 
+are a non-tool-user and so we will never identify tool use no matter how long we 
+measure them for.
 
-In our model, we infer the tool-using status of each species by allowing each species to have their own probability of being "cured" (i.e., not a tool user).
-Following our causal model (Figure \@ref(fig:plotDAG)), we predict these probabilities based on feeding strategy, encephalisation quotient, and phylogenetic history (see Methods for full model).
-The model additionally takes research effort into account by allowing that, among species for which tool use is unobserved, all else being equal those with fewer published papers and fewer video search hits have a higher probability of being undetected tool users (Supplementary Figure \@ref(fig:plotSurvCure3)).
+In our model, we infer the tool-using status of each species by allowing each 
+species to have their own probability of being a non-tool-user. Following our 
+causal model (Figure \@ref(fig:plotDAG)), we predict these probabilities based 
+on feeding strategy, encephalisation quotient, and phylogenetic history (see 
+Methods for full model). The model additionally takes research effort into 
+account by allowing that, among species for which tool use is unobserved, all 
+else being equal those with fewer published papers and fewer video search hits 
+have a higher probability of being undetected tool users (fig. 
+\@ref(fig:plotSurvCure3)).
 
@@
 
-We found that this phylogenetic survival cure model was able to adequately distinguish between species with and without evidence for tool use, with an area-under-the-curve classification statistic of `r printnum(tar_read(auc), digits = 2)` (Supplementary Figure \@ref(fig:plotSurvCure9)).
-To further estimate the accuracy of the model's predictions, we also used a leave-one-species-out approach with known tool users.
-For each of the 25 tool-using species that were represented on the phylogeny and for which we had brain size and genomic data (we lacked data for three tool-using species), we fitted the model to a modified dataset which set tool use to be absent for the target species in both the scientific literature and the video survey.
-Across `r length(tar_read(cv))` cross-validation models, `r sum(tar_read(cv))` models (`r printnum(mean(tar_read(cv))*100, digits = 0)`%) continued to predict the target species as having a median posterior probability of tool use that was within the range of all other tool users.
-This classification rate was greater than the baseline classification rate of `r printnum(mean(plotSurvCure1$data %>% filter(ToolUse == "Absent") %>% pull(med) > 0.16478274) * 100, digits = 0)`% for species without evidence of tool use in the full model (`r sum(plotSurvCure1$data %>% filter(ToolUse == "Absent") %>% pull(med) > 0.16478274)` of `r nrow(plotSurvCure1$data %>% filter(ToolUse == "Absent"))` species without evidence of tool use had a median posterior probability of tool use that was within the range of the tool-using species).
-Together, the area-under-the-curve statistic and the leave-one-species-out approach suggest that the model is able to adequately classify known tool users, with some error.
+We found that this phylogenetic survival cure model was able to adequately 
+distinguish between species with and without evidence for tool use, with an 
+area-under-the-curve classification statistic of 
+`r printnum(tar_read(auc), digits = 2)` (fig.  
+\@ref(fig:plotSurvCure9)). To further estimate the accuracy of the model's 
+predictions, we also used a leave-one-species-out approach with known tool 
+users. For each of the 25 tool-using species that were represented on the 
+phylogeny and for which we had brain size and genomic data (we lacked data for 
+three tool-using species), we fitted the model to a modified dataset which set 
+tool use to be absent for the target species in both the scientific literature 
+and the video survey. Across `r length(tar_read(cv))` cross-validation models, 
+`r sum(tar_read(cv))` models (`r printnum(mean(tar_read(cv))*100, digits = 0)`%) 
+continued to predict the target species as having a median posterior probability 
+of tool use that was within the range of all other tool users. This 
+classification rate was greater than the baseline classification rate of 
+`r printnum(mean(plotSurvCure1$data %>% filter(ToolUse == "Absent") %>% pull(med) > 0.16478274) * 100, digits = 0)`% 
+for species without evidence of tool use in the full model
+(`r sum(plotSurvCure1$data %>% filter(ToolUse == "Absent") %>% pull(med) > 0.16478274)` 
+of `r nrow(plotSurvCure1$data %>% filter(ToolUse == "Absent"))` species without 
+evidence of tool use had a median posterior probability of tool use that was 
+within the range of the tool-using species). Together, the area-under-the-curve 
+statistic and the leave-one-species-out approach suggest that the model is able 
+to adequately classify known tool users, with some error.
 
-Figure \@ref(fig:plotSurvCure1) visualises the ranked posterior probabilities of tool use from the phylogenetic survival cure model for all parrot species.
-As expected, the known tool users are ranked towards the top of this list.
-However, several "tool use absent" species also rank highly on the list, despite not being identified as tool users in the scientific literature or in our video survey.
-In fact, according to the model, the most likely tool user is a species for which tool use is unobserved in our data: the blue-eyed cockatoo (_Cacatua opthalmica_).
-This species is endemic to Papua New Guinea and is relatively understudied, with only `r tar_read(d)$EX.Pre.Tool.Papers[165]` published papers and `r tar_read(d)$SearchHits[165]` video search hits, which is fewer than the model expects are necessary to discover tool use when it is present (Figure \@ref(fig:plotSurvCure2)).
-This species is also found in the _Cacatua_ genus, a clade containing several known tool users.
-This prediction makes sense given the high phylogenetic signal for tool use reported by the model (Supplementary Figures \@ref(fig:plotSurvCure5) and \@ref(fig:plotSurvCure6)).
-Beyond the blue-eyed cockatoo, other highly ranked species without observed evidence of tool use are the Meyer's parrot (_Poicephalus meyeri_), the golden parakeet (_Guaruba guarouba_), the long-billed corella (_Cacatua tenuirostris_), the Solomons cockatoo (_Cacatua ducorpsii_), the red-fronted parrot (_Poicephalus gulielmi_), the Cape parrot (_Poicephalus robustus_), the yellow-eared parrot (_Ognorhynchus icterotis_), the red-vented cockatoo (_Cacatua haematuropygia_), and the gang-gang cockatoo (_Callocephalon fimbriatum_).
-Figure \@ref(fig:plotPhylo1) plots these species on the parrot phylogeny, using the top ten highest ranked species without observed evidence of tool use as an abitrary cutoff for visualisation purposes.
+Figure \@ref(fig:plotSurvCure1) visualises the ranked posterior probabilities of 
+tool use from the phylogenetic survival cure model for all parrot species. As 
+expected, the known tool users are ranked towards the top of this list. However, 
+several "tool use absent" species also rank highly on the list, despite not 
+being identified as tool users in the scientific literature or in our video 
+survey. In fact, according to the model, the most likely tool user is a species 
+for which tool use is unobserved in our data: the blue-eyed cockatoo (_Cacatua 
+opthalmica_). This species is endemic to Papua New Guinea and is relatively 
+understudied, with only `r tar_read(d)$EX.Pre.Tool.Papers[165]` published papers 
+and `r tar_read(d)$SearchHits[165]` video search hits, which is fewer than the 
+model expects are necessary to discover tool use when it is present (Figure 
+\@ref(fig:plotSurvCure2)). This species is also found in the _Cacatua_ genus, a 
+clade containing several known tool users. This prediction makes sense given the 
+high phylogenetic signal for tool use reported by the model (Supplementary 
+Figures \@ref(fig:plotSurvCure5) and \@ref(fig:plotSurvCure6)). Beyond the 
+blue-eyed cockatoo, other highly ranked species without observed evidence of 
+tool use are the Meyer's parrot (_Poicephalus meyeri_), the golden parakeet 
+(_Guaruba guarouba_), the long-billed corella (_Cacatua tenuirostris_), the 
+Solomons cockatoo (_Cacatua ducorpsii_), the red-fronted parrot (_Poicephalus 
+gulielmi_), the Cape parrot (_Poicephalus robustus_), the yellow-eared parrot 
+(_Ognorhynchus icterotis_), the red-vented cockatoo (_Cacatua haematuropygia_), 
+and the gang-gang cockatoo (_Callocephalon fimbriatum_). Figure 
+\@ref(fig:plotPhylo1) plots these species on the parrot phylogeny, using the top 
+ten highest ranked species without observed evidence of tool use as an arbitrary 
+cutoff for visualisation purposes.
 
-(ref:plotSurvCure1Caption) _Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model._ Points are posterior medians and lines are 50% and 95% credible intervals.
-Total _n_ = `r nrow(tar_read(d))` species.
+(ref:plotSurvCure1Caption) _Posterior predicted probabilities of tool use for 
+each species from our phylogenetic survival cure model._ Points are posterior 
+medians and lines are 50% and 95% credible intervals. Total _n_ = 
+`r nrow(tar_read(d))` species.
 
@@
 
-(ref:plotSurvCure2Caption) _Expected number of published papers and videos until tool use discovery, according to the survival component of the phylogenetic survival cure model._ Densities are full posterior distributions, points are posterior medians, and lines are 50% and 95% credible intervals.
+(ref:plotSurvCure2Caption) _Expected number of published papers and videos until 
+tool use discovery, according to the survival component of the phylogenetic 
+survival cure model._ Densities are full posterior distributions, points are 
+posterior medians, and lines are 50% and 95% credible intervals.
 
@@
 
-The posterior probabilities shown in Figure \@ref(fig:plotSurvCure1) are estimated with uncertainty, so it is difficult to "identify" any particular species as an undetected tool user.
-Nevertheless, taking the sum of all the posterior probabilities for the `r nrow(plotSurvCure1$data %>% filter(ToolUse == "Absent"))` species without observed evidence of tool use, we can estimate that around `r printnum(median(sumProbs), digits = 0)` of those species are likely to be undetected tool users (median sum of probabilities = `r printnum(median(sumProbs), digits = 2)`, 95% CI [`r printnum(quantile(sumProbs, 0.025), digits = 2)` `r printnum(quantile(sumProbs, 0.975), digits = 2)`]).
-When combined with the species known to use tools, this implies that between 11% and 17% of extant parrot species may be tool users.
+The posterior probabilities shown in Figure \@ref(fig:plotSurvCure1) are 
+estimated with uncertainty, so it is difficult to "identify" any particular 
+species as an undetected tool user. Nevertheless, taking the sum of all the 
+posterior probabilities for the 
+`r nrow(plotSurvCure1$data %>% filter(ToolUse == "Absent"))` species without 
+observed evidence of tool use, we can estimate that around 
+`r printnum(median(sumProbs), digits = 0)` of those species are likely to be 
+undetected tool users (median sum of probabilities = 
+`r printnum(median(sumProbs), digits = 2)`, 95% CI
+[`r printnum(quantile(sumProbs, 0.025), digits = 2)` 
+`r printnum(quantile(sumProbs, 0.975), digits = 2)`]). When combined with the 
+species known to use tools, this implies that between 11% and 17% of extant 
+parrot species may be tool users.
 
@@
 
-The predicted probabilities from our phylogenetic survival cure model have implications for inferences about the evolutionary drivers and origins of tool use in the parrot order.
-Regarding the drivers of tool use hypothesised in Figure \@ref(fig:plotDAG), the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = `r printnum(median(-postFull$bEQ))`, 95% CI [`r printnum(quantile(-postFull$bEQ, 0.025))` `r printnum(quantile(-postFull$bEQ, 0.975))`]; total _n_ = `r nrow(tar_read(d))` species; Figure \@ref(fig:plotSurvCure4)).
-This helps explain the ranking in Figure \@ref(fig:plotSurvCure1): the blue-eyed cockatoo has the largest relative brain size in the dataset.
-We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = `r printnum(median(diff))`, 95% CI [`r printnum(quantile(diff, 0.025))` `r printnum(quantile(diff, 0.975))`]; total _n_ = `r nrow(tar_read(d))` species).
-These results from the survival cure model differed from the results of models fitted to pre-video-survey and post-video-survey data without the survival cure component, which found no effect of relative brain size and no difference between feeding strategies, respectively (Supplementary Figure \@ref(fig:plotComparison)).
+The predicted probabilities from our phylogenetic survival cure model have 
+implications for inferences about the evolutionary drivers and origins of tool 
+use in the parrot order. Regarding the drivers of tool use hypothesised in 
+Figure \@ref(fig:plotDAG), the phylogenetic survival cure model revealed that 
+encephalisation quotient strongly positively predicted the probability of tool 
+use (median posterior log odds slope = `r printnum(median(-postFull$bEQ))`, 95% 
+CI [`r printnum(quantile(-postFull$bEQ, 0.025))` 
+`r printnum(quantile(-postFull$bEQ, 0.975))`]; total _n_ = `r nrow(tar_read(d))` 
+species; Figure \@ref(fig:plotSurvCure4)). This helps explain the ranking in 
+Figure \@ref(fig:plotSurvCure1): the blue-eyed cockatoo has the largest relative 
+brain size in the dataset. We also found that feeding generalist species were 
+slightly more likely to be tool users, though the posterior difference between 
+generalists and specialists was quite uncertain (median posterior log odds 
+difference = `r printnum(median(diff))`, 95% CI [
+`r printnum(quantile(diff, 0.025))` `r printnum(quantile(diff, 0.975))`]; total 
+_n_ = `r nrow(tar_read(d))` species). These results from the survival cure model 
+differed from the results of models fitted to pre-video-survey and 
+post-video-survey data without the survival cure component, which found no 
+effect of relative brain size and no difference between feeding strategies, 
+respectively (fig. \@ref(fig:plotComparison)).
 
-(ref:plotSurvCure4Caption) _Posterior predictions for the effects of feeding strategy and encephalisation quotient on the probability of tool use from the phylogenetic survival cure model._ In the left plot, points and lines represent posterior medians and 50% and 95% credible intervals, with densities representing full posterior distributions.
-In the right plot, the line and shaded area represents the posterior median regression line with 95% credible intervals.
-In both plots, individual species are coloured according to the presence / absence of tool use in the video survey and the scientific literature.
-Total _n_ = `r nrow(tar_read(d))` species, generalist _n_ = `r sum(tar_read(d)$Feeding == "Generalist")` species, specialist _n_ = `r sum(tar_read(d)$Feeding == "Specialist")` species.
+(ref:plotSurvCure4Caption) _Posterior predictions for the effects of feeding 
+strategy and encephalisation quotient on the probability of tool use from the 
+phylogenetic survival cure model._ In the left plot, points and lines represent 
+posterior medians and 50% and 95% credible intervals, with densities 
+representing full posterior distributions. In the right plot, the line and 
+shaded areas represent the posterior median regression line with 50% and 95% 
+credible intervals. In both plots, individual species are coloured according to 
+the presence / absence of tool use in the video survey and the scientific 
+literature. Total _n_ = `r nrow(tar_read(d))` species, generalist _n_ = 
+`r sum(tar_read(d)$Feeding == "Generalist")` species, specialist _n_ = 
+`r sum(tar_read(d)$Feeding == "Specialist")` species.
 
@@
 
-Regarding the origins of tool use, we fitted exploratory ancestral state reconstruction models to the pre-video-survey data, the post-video-survey data, and the predicted probabilities from the phylogenetic survival cure model.
-The discoveries from our video survey and from our phylogenetic modelling increased the likelihood that tool use was present in the most recent common ancestor for several parrot genera.
-These include the amazon parrots native to the Americas (_Amazona_), the true white cockatoos and corellas found in South East Asia and Australasia (_Cacatua_), the kea and the kākā from New Zealand (_Nestor_), and the _Poicephalus_ genus native to Africa (Table \@ref(tab:tableASR); Supplementary Figures \@ref(fig:plotASR1) - \@ref(fig:plotASR3)).
-These findings suggest that species from each of these genera share their tool use capabilities via common descent from their respective common ancestors, rather than via independent evolution within each genus.
+Regarding the origins of tool use, we fitted exploratory ancestral state 
+reconstruction models to the pre-video-survey data, the post-video-survey data, 
+and the predicted probabilities from the phylogenetic survival cure model. The 
+discoveries from our video survey and from our phylogenetic modelling increased 
+the likelihood that tool use was present in the most recent common ancestor for 
+several parrot genera. These include the amazon parrots native to the Americas 
+(_Amazona_), the true white cockatoos and corellas found in South East Asia and 
+Australasia (_Cacatua_), the kea and the kākā from New Zealand (_Nestor_), and 
+the _Poicephalus_ genus native to Africa (Table \@ref(tab:tableASR); 
+fig. s \@ref(fig:plotASR1) - \@ref(fig:plotASR3)). These findings 
+suggest that species from each of these genera may share their tool use 
+capabilities via common descent from their respective common ancestors, rather 
+than via independent evolution within each genus or behavioural innovation
+within species.
 
-(ref:tableASRCaption) Estimated probabilities of tool use for most recent common ancestors of several parrot genera.
-_Probabilities estimated using exploratory ancestral state reconstruction models fitted to the pre-video-survey data, post-video-survey data, and predicted probabilities from the phylogenetic survival cure model.
-Total_ n _= `r nrow(tar_read(d))` species._
+(ref:tableASRCaption) Estimated probabilities of tool use for most recent common 
+ancestors of several parrot genera. _Probabilities estimated using exploratory 
+ancestral state reconstruction models fitted to the pre-video-survey data, 
+post-video-survey data, and predicted probabilities from the phylogenetic 
+survival cure model. Total_ n _= `r nrow(tar_read(d))` species._
 
@@
 
-Since the earliest anecdotal reports of parrots using tools in the 1970s[@Goodall1971], only 11 parrot species (3% of all extant parrot species) have been documented as tool users in the scientific literature.
-Our study used crowdsourcing to identify 17 additional tool-using parrot species that are new to science, more than doubling the overall count to 28 species (7%).
-These species consisted of cockatoos (Cacatuidae), Old World parrots (Psittacinae), and neotropical parrots (Arinae).
+Since the earliest anecdotes of parrots using tools by Wallace in the 1880s
+[@Wallace1869] and more systematic anecdotal reports in the 1970s [@Goodall1971], 
+only 11 parrot species (3% of all extant parrots) have been documented as tool 
+users in the scientific literature. Our study used crowdsourcing to identify 17 
+additional tool-using parrot species that are new to science, more than doubling 
+the overall count to 28 species (7%). These species consisted of cockatoos 
+(_Cacatuidae_), Old World parrots (_Psittacinae_), and neotropical parrots 
+(_Arinae_).
 
-We found strong phylogenetic signal in our extended dataset, demonstrating that the distribution of tool use across parrot species is affected by shared phylogenetic ancestry.
-This allowed us to use phylogenetic information, along with other variables, to infer the unobserved probabilities of tool use across the parrot order.
-Our phylogenetic survival cure model incorporated information on phylogenetic history, research effort, relative brain size, and feeding specialisation to rank parrot species that were most likely to be undetected tool users.
-The sum of probabilities from this model implied that between 15 and 41 of the species without observed evidence of tool use are likely to be undetected tool users, suggesting that the true proportion of tool users may be as high as 17%.
+While parrots in the wild use tools to achieve a variety of 
+goals [@Goodman2018;@OHara2021], the 17 additional species identified by our 
+video survey were exclusively observed using tools for self-scratching. This is 
+likely because preening is the only context in which captive parrots regularly 
+require tools, unlike wild parrots who may also require tools for extractive 
+foraging [@Goodman2018;@OHara2021]. Despite this difference in the type of tool 
+use observed, self-scratching is nonetheless a major category of animal tool 
+use and clearly meets the established criteria for tool use in the literature: 
+the manipulation of an unattached object as an extension of the animal's body to 
+achieve a goal [@Shumaker2011]. It also meets the definition for a more complex 
+type of embodied tool use known as 'tooling', the deliberate generation of a 
+mechanical interface by using an object to manipulate another target or 
+surface [@Fragaszy2018]. The fact that we found strong phylogenetic clustering 
+of self-scratching tool use from the video survey with other examples of tool 
+use from the literature supports a common underlying cognitive mechanism. In 
+line with this, some of the species of parrots that use tools for 
+self-scratching in captivity also use tools for other purposes in the wild
+[@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021].
 
-These findings have a number of important implications.
-First, our findings show that current research effort in the scientific literature is insufficient to capture the real world occurrence of parrot tool use.
-If the scientific literature had sampled the natural world sufficiently, we would expect to see close correspondence between those species reported as tool users in the literature and those species the public have filmed performing tool use.
-Instead, we discovered a large discrepancy between these two data sources, both in the prevalence of tool use and the species identified.
-This raises the possibility that insufficient research effort is a general issue across the scientific literature, both for tool use in other groups and for other rare behaviours.
+There was little evidence to suggest that the observations of self-scratching
+tool use in the video survey were merely unintentional accidents or explicitly 
+trained behaviours. Individual parrots often used tools slowly and repetitively 
+over long periods of time, even across multiple different videos, suggesting 
+that their behaviour was not random or accidental [@Sandor2020]. Parrots 
+preferentially employed self-scratching tools on areas of their body that were 
+otherwise inaccessible, with 96% of all instances involving scratching of the 
+head or neck, suggesting intentional tool use. For 60% of the species in the 
+video survey, we found two or more videos of repetitive and sustained scratching 
+by different individuals of the same species in separate households, suggesting 
+that the manipulations were intentional and recurring events that did not 
+represent unusual stereotypies of any single individual. Regarding the 
+possibility of training or cueing from owners, over half of the videos contained 
+no evidence of human interaction aside from filming the behaviour. Humans only 
+handed parrots their tools in two of the videos, and none of the videos featured 
+owners directly rewarding tool use behaviours with food. Finally, the high 
+levels of phylogenetic signal in our data provides strong evidence that the 
+observations from our video survey reflect biologically-endowed capacities for 
+tool use rather than accidental or trained behaviours, which would likely appear 
+uniformly across the phylogeny.
 
-Second, in terms of the evolution of tool use in parrots, our study challenges a key assumption made in the literature to date: that only a minority of parrots are tool users[@Auersperg2012;@Bastos2021;@Goodman2018;@Lambert2015;@OHara2021].
-The paucity of evidence for tool use across parrots in the literature initially implied that tool use may have evolved independently in different parrot species.
-Our discovery of the widespread distribution of tool use across the parrot phylogeny, along with the strong phylogenetic signal in this expanded dataset, challenges this and suggests that, at least for some parrot clades, the capacity for tool use might be a homologous trait that has been evolutionarily conserved.
-Our exploratory ancestral state reconstruction analysis provides preliminary support for this hypothesis, revealing an increased probability of tool use among the most recent common ancestors for the _Amazona_, _Cacatua_, _Nestor_, and _Poicephalus_ genera.
-Even at this preliminary stage, our analysis therefore raises an alternative hypothesis for the observed tool use in _Cacatua_[@Auersperg2012;@OHara2021] and _Nestor_[@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;@Bastos2021;@Goodman2018], namely that tool behaviours have arisen due to the common ancestor being a tool user, rather than from behavioural innovation within a species.
+Beyond the video survey, the strong phylogenetic signal in our dataset allowed 
+us to use phylogenetic information, along with other variables, to infer the 
+unobserved probabilities of tool use across the parrot order. Our phylogenetic 
+survival cure model incorporated information on phylogenetic history, research 
+effort, relative brain size, and feeding specialisation to rank parrot species 
+that were most likely to be undetected tool users. The sum of probabilities from 
+this model implied that between 15 and 41 of the species without observed 
+evidence of tool use are likely to be undetected tool users, suggesting that the 
+true proportion of tool users may be as high as 17%.
 
-Third, our results support existing theories of the drivers of tool use.
-We found that encephalisation was strongly positively related to the probability of tool use in our phylogenetic model, supporting previous theories linking relative brain size to increased tool innovation in birds[@Lefebvre1997;@Lefebvre2002;@Lefebvre2004] and primates[@Reader2002].
-Nevertheless, we recognise that cross-species correlations between brain size and behaviour are challenging to interpret causally[@Healy2007;@Logan2018], and thus encourage further work on the specific neural correlates of technical intelligence in parrots (see e.g.[@Alvarez2020]).
-In our phylogenetic model, we also found that tool use was somewhat more likely among feeding generalists compared to feeding specialists, although this difference was uncertain.
-This trend supports previous suggestions that increased cognitive abilities and technical innovation rates are required to expand a generalist species' dietary niche[@HenkeVonDerMalsburg2020;@HenkeVonDerMalsburg2021;@Ducatez2015].
-However, the trend contradicts theories linking tool use to dietary specialisation, whereby species eating specific foods that require extractive foraging have higher cognitive ability and are especially prone to using tools (reviewed in ref[@HenkeVonDerMalsburg2020]).
+These findings have a number of important implications. First, our findings show 
+that current research effort in the scientific literature is insufficient to 
+capture the real world occurrence of parrot tool use. If the scientific 
+literature had sampled the natural world sufficiently, we would expect to see 
+close correspondence between those species reported as tool users in the 
+literature and those species the public have filmed performing tool use. 
+Instead, we discovered a large discrepancy between these two data sources, both 
+in the prevalence of tool use and the species identified. This raises the 
+possibility that insufficient research effort is a general issue across the 
+scientific literature, both for tool use in other groups and for other rare 
+behaviours.
 
-We believe that the observations of tool use in our video survey reflect intentional tool use, rather than accidental object manipulations or trained behaviours.
-In the crowdsourcing video survey, individual parrots often used tools slowly and repetitively over long periods of time, even across multiple different videos, suggesting that their behaviour was not accidental[@Sandor2020].
-Moreover, for 60% of the species we report on, we found two or more videos of repetitive and sustained scratching by different individuals in separate households.
-Following the assumption that accidental tool use (e.g., briefly holding an object and attempting to scratch oneself simultaneously) is rare[@Auersperg2020], the repeated observation of the same tool use behaviours for scratching by multiple animals of the same species across multiple households suggests that these manipulations are intentional and recurring events rather than rare "accidents" and likely do not represent unusual stereotypies of a single individual.
-We also found little evidence to suggest that the tool use behaviours were trained or unintentionally cued by the birds' owners.
-Over half of the videos coded contained no evidence of human interference with the parrots' tool use aside from filming the behaviour.
-Humans only handed parrots their tools in two of the videos, and none of the videos featured owners directly rewarding tool use behaviours with food.
-Finally, and perhaps most importantly, the high levels of phylogenetic signal in our data provides strong evidence that the observations from our video survey reflect biologically-endowed capacities for tool use rather than accidents or trained behaviours, which would likely appear uniformly across the phylogeny.
+Second, in terms of the evolution of tool use in parrots, our study challenges a 
+key assumption made in the literature to date: that only a minority of parrots 
+are tool users [@Auersperg2012;@Bastos2021;@Goodman2018;@Lambert2015;@OHara2021]. 
+The paucity of evidence for tool use across parrots in the literature initially 
+implied that the capacity for tool use may have evolved independently in 
+different parrot species. Our discovery of the widespread distribution of tool 
+use across the parrot phylogeny, along with the strong phylogenetic signal in 
+this expanded dataset, challenges this and suggests that, at least for some 
+parrot clades, the capacity for tool use might be a homologous trait that has 
+been evolutionarily conserved. Our exploratory ancestral state reconstruction 
+analysis provides preliminary support for this hypothesis, revealing an 
+increased probability of tool use among the most recent common ancestors for the 
+_Amazona_, _Cacatua_, _Nestor_, and _Poicephalus_ genera. Even at this 
+preliminary stage, our analysis therefore raises an alternative hypothesis for 
+the observed tool use in _Cacatua_ [@Auersperg2012;@OHara2021] and 
+_Nestor_ [@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;
+@Bastos2021;@Goodman2018], namely that tool behaviours have arisen due to the 
+common ancestor having the capacity to use tools, rather than from independent 
+evolution or behavioural innovation within species.
 
-While missing data imputation is becoming more common in phylogenetic analyses[@Debastiani2021], the important distinction between absence of evidence and evidence of absence has not been given as much attention.
-Our phylogenetic analysis provides one approach to this problem by distinguishing between true absences of tool use and absences of tool use due to a lack of research effort in the scientific literature or in crowdsourced videos.
-To achieve this, we explicitly modelled the measurement of the outcome variable along a research effort time series, such that species with lower research effort in the literature or in videos were likely to be censored.
-In line with our causal model, we also included relative brain size, feeding strategy, and phylogenetic history as predictors of unobserved tool use.
-We encourage researchers to test this model by directing future study efforts towards the parrot species with the highest probabilities of being undetected tool-users.
-Future work should also refine the causal model in Figure \@ref(fig:plotDAG) to provide more certain estimates of tool use probabilities, either by including additional predictor variables or modelling further causes of measurement error in the taxonomic record, such as species abundance and geographic accessibility[@Ducatez2014].
+Third, our results support existing theories of the drivers of tool use. We 
+found that encephalisation was strongly positively related to the probability of 
+tool use in our phylogenetic model, supporting previous theories linking 
+relative brain size to increased tool innovation in birds [@Lefebvre1997;
+@Lefebvre2002;@Lefebvre2004] and primates [@Reader2002]. We acknowledge that
+encephalisation quotient is not a perfect measure due to measurement error and
+challenges with interpretation [@Healy2007;@Logan2018]. However, encephalisation
+quotient has much greater coverage across the parrot phylogeny than more 
+fine-grained measures like whole neuron count [@Sol2022] and there is no reason 
+to think that measurement error would produce the consistent patterns across our
+study and prior work. To understand the causal mechanisms responsible for these
+relationships, we encourage further work on the specific neural correlates of 
+technical intelligence in parrots, e.g., [@Alvarez2020]. In our phylogenetic 
+model, we also found that tool use was somewhat more likely among feeding 
+generalists compared to feeding specialists, although this difference was 
+uncertain. This trend supports previous suggestions that increased cognitive 
+abilities and technical innovation rates are required to expand a generalist 
+species' dietary niche [@HenkeVonDerMalsburg2020;@HenkeVonDerMalsburg2021;
+@Ducatez2015]. However, the trend contradicts theories linking tool use to 
+dietary specialisation, whereby species eating specific foods that require 
+extractive foraging have higher cognitive ability and are especially prone to 
+using tools [@HenkeVonDerMalsburg2020].
 
-In conclusion, we have shown that the scientific literature has insufficiently captured the full distribution of tool use in the parrot order.
-Our crowdsourcing survey has more than doubled the number of known tool using parrot species from 11 to 28, and our phylogenetic inference suggested that the true proportion of parrot tool users could be as high as 17%.
-These discoveries have implications for theories of the evolutionary drivers and origins of tool use in parrots.
-Beyond parrot tool use, the crowdsourcing and phylogenetic methods used in this study have the potential to be applied to other rarely observed behaviours, including tool use in other taxa[@Hunt2013], rhythmic entrainment in birds[@Benichov2016;@Patel2009;@tenCate2016;@Wilson2016], teasing behaviours in primates[@Eckert2020], and tactical deception across the animal kingdom[@BroJorgensen2010;@Byrne1988;@Byrne1991].
-We hope that these methods will continue to uncover a diverse array of ephemeral behaviours that have as yet gone undetected in the scientific literature.
+While missing data imputation is becoming more common in phylogenetic 
+analyses [@Debastiani2021], the important distinction between absence of 
+evidence and evidence of absence has not been given as much attention. Our 
+phylogenetic analysis provides one approach to this problem by distinguishing 
+between true absences of tool use and absences of tool use due to a lack of 
+research effort in the scientific literature or in crowdsourced videos. To 
+achieve this, we explicitly modelled the measurement of the outcome variable 
+along a research effort time series, such that species with lower research 
+effort in the literature or in videos were likely to be censored. In line with 
+our causal model, we also included relative brain size, feeding strategy, and 
+phylogenetic history as predictors of unobserved tool use. We encourage 
+researchers to test this model by directing future study efforts towards the 
+parrot species with the highest probabilities of being undetected tool-users. 
+Future work should also refine the causal model in Figure \@ref(fig:plotDAG) to 
+provide more certain estimates of tool use probabilities, either by including 
+additional predictor variables or modelling further causes of measurement error 
+in the taxonomic record, such as species abundance and geographic 
+accessibility [@Ducatez2014].
+
+In conclusion, we have shown that the scientific literature has insufficiently 
+captured the full distribution of tool use in the parrot order. Our 
+crowdsourcing survey more than doubled the number of known tool using parrot 
+species from 11 to 28, and our phylogenetic model suggested that the true 
+proportion of parrot tool users could be as high as 17% of all species in this 
+order. These discoveries have implications for theories of the evolutionary 
+drivers and origins of tool use in parrots. Beyond parrot tool use, the 
+crowdsourcing and phylogenetic methods used in this study have the potential to 
+be applied to other rarely observed behaviours, including tool use in other 
+taxa [@Hunt2013], rhythmic entrainment in birds [@Benichov2016;@Patel2009;
+@tenCate2016;@Wilson2016], teasing behaviours in primates [@Eckert2020], and 
+tactical deception across all animals [@BroJorgensen2010;@Byrne1988;@Byrne1991]. 
+We hope that these methods will continue to uncover a diverse array of ephemeral 
+behaviours that have as yet gone undetected in the scientific literature.
 
@@
 
-Our video search was conducted on YouTube in July 2020.
-Search terms included "parrot using tool" and variants (e.g., "macaw using tool", "lorikeet using tool", "parakeet using tool"), "tool use in parrot", "parrot tool use", "parrot scratching itself" (included after we found several videos demonstrating self-care tool use in previous searches) and equivalent terms (e.g., "parrot preening itself", "parrot grooming itself", "parrot scratching").
-For all species that did not display results including object manipulation or scratching behaviours, we also searched the species’ common name(s) + "tool use", as well as the species’ common name(s) + "scratching".
-We also searched for translations of the terms "parrot tool use" and "parrot scratching" in languages for all countries where bird ownership was reported as >5%[@GlobalGfkSurvey], namely, Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, Portuguese, and Mandarin.
+Our video search was conducted on YouTube in July 2020. Search terms included 
+"parrot using tool" and variants (e.g., "macaw using tool", "lorikeet using 
+tool", "parakeet using tool"), "tool use in parrot", "parrot tool use", "parrot 
+scratching itself" (included after we found several videos demonstrating 
+self-care tool use in previous searches) and equivalent terms (e.g., "parrot 
+preening itself", "parrot grooming itself", "parrot scratching"). For all 
+species that did not display results including object manipulation or scratching 
+behaviours, we also searched the species’ common name(s) + "tool use", as well 
+as the species’ common name(s) + "scratching". We also searched for translations 
+of the terms "parrot tool use" and "parrot scratching" in languages for all 
+countries where bird ownership was reported as >5% [@GlobalGfkSurvey], namely, 
+Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, 
+Portuguese, and Mandarin.
 
-When we found a relevant video, we also searched for similar content uploaded by the same person/channel.
-For each YouTube search conducted, we watched all relevant videos until we reached five consecutive videos that did not feature any parrots.
-At this point, we ended that search and initiated the next search.
-In line with previous recommendations[@Nelson2013], we planned to exclude any videos that consisted of four or more shots edited together so as to ensure the behaviours being observed were not edited or manipulated, but none of the videos obtained qualified for exclusion.
+When we found a relevant video, we also searched for similar content uploaded by 
+the same person/channel. For each YouTube search conducted, we watched all 
+relevant videos until we reached five consecutive videos that did not feature 
+any parrots. At this point, we ended that search and initiated the next search. 
+In line with previous recommendations [@Nelson2013], we planned to exclude any 
+videos that consisted of four or more shots edited together so as to ensure the 
+behaviours being observed were not edited or manipulated, but none of the videos 
+obtained qualified for exclusion.
 
-All videos featuring parrots manipulating objects were investigated for potential tool use or borderline tool use.
-We defined tool use as the manipulation of an unattached object as an extension of the beak or foot to achieve a goal towards another object, individual, or oneself[@Shumaker2011].
-Borderline tool use was similarly defined, except that it involved the use of an object that was still attached to a substrate[@Seed2010].
-For example, if individuals used a fallen feather or stick for self-scratching this was defined as tool use, but using one’s currently attached tail feathers or cage furnishings for the same purpose was defined as borderline tool use.
-Self-scratching had to involve slow and repeated movements of touching an object to one’s body (or, in the case of borderline tool use, rubbing repetitively against an attached object[@Sandor2020]).
+All videos featuring parrots manipulating objects were investigated for 
+potential tool use or borderline tool use. We defined tool use as the 
+manipulation of an unattached object as an extension of the beak or foot to 
+achieve a goal towards another object, individual, or oneself [@Shumaker2011]. 
+Borderline tool use was similarly defined, except that it involved the use of an 
+object that was still attached to a substrate [@Seed2010]. For example, if 
+individuals used a fallen feather or stick for self-scratching this was defined 
+as tool use, but using one’s currently attached tail feathers or cage 
+furnishings for the same purpose was defined as borderline tool use. 
+Self-scratching had to involve slow and repeated movements of touching an object 
+to one’s body (or, in the case of borderline tool use, rubbing repetitively 
+against an attached object [@Sandor2020]).
 
-All relevant videos were coded for video length, species, tool use presence (yes/borderline), tool use type (e.g., scratching, feeding), the object being used (e.g., feather, stick), tool use target, human interference with the action (talking or handing object to parrot, holding parrot), and the number of shots within each video.
-Our complete dataset also includes the name for each video, link, subject name, sex (as declared by owner, as most parrot species are not sexually dimorphic), publishing date, and dates found and coded.
+All relevant videos were coded for video length, species, tool use presence 
+(yes/borderline), tool use type (e.g., scratching, feeding), the object being 
+used (e.g., feather, stick), tool use target, human interaction 
+(talking or handing object to parrot, holding parrot), and the number of shots 
+within each video. Our complete dataset also includes the name for each video, 
+link, subject name, sex (as declared by owner, as most parrot species are not 
+sexually dimorphic), publishing date, and dates found and coded.
 
@@
 
-We collected data for 194 parrot species (Supplementary Figures \@ref(fig:plotPhylo2) - \@ref(fig:plotPhylo4)).
-We gathered feeding strategy data as a dichotomous variable ("generalist" or "specialist") from the EltonTraits ecological database[@Wilman2016].
-As per the database, specialists were defined as species whose diet comprised at least 70% of a single food source.
-To calculate relative brain size, we collated data from the literature for all known body mass (g) and brain mass (g) values across parrots[@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;@Schuck2008;@Silva2017].
-For all species for which we obtained body and brain mass data, we calculated the encephalisation quotient (EQ) using the following formula[@Jerison1973]: $BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))$.
-We found body mass and brain mass data for a total of 194 parrot species.
-This included all tool-using species in our video dataset, with the exception of three species: _Diopsittaca nobilis_, _Psittacara erythrogenys_, and _Coracopsis vasa_.
-For the latter, we used values for the closely related _Coracopsis nigra_.
-The other two species were excluded from the final dataset.
+We collected data for 194 parrot species (figs. 
+\@ref(fig:plotPhylo2) - \@ref(fig:plotPhylo4)). We gathered feeding strategy 
+data as a dichotomous variable ("generalist" or "specialist") from the 
+EltonTraits ecological database [@Wilman2016]. As per the database, specialists 
+were defined as species whose diet comprised at least 70% of a single food 
+source. To calculate relative brain size, we collated data from the literature 
+for all known body mass (g) and brain mass (g) values across 
+parrots [@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;@Schuck2008;
+@Silva2017]. For all species for which we obtained body and brain mass data, we 
+calculated the encephalisation quotient (EQ) using the following 
+formula [@Jerison1973]: $BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))$. We 
+found body mass and brain mass data for a total of 194 parrot species. This 
+included all tool-using species in our video dataset, with the exception of 
+three species: _Diopsittaca nobilis_, _Psittacara erythrogenys_, and _Coracopsis 
+vasa_. For the latter, we used values for the closely related _Coracopsis 
+nigra_. The other two species were excluded from the final dataset.
 
-For modelling purposes, we coded research effort in both the scientific literature and the crowdsourced videos.
-For the scientific literature, we operationalised research effort as the number of papers published for each species' Latin name up to and including the first paper containing tool use for that species.
-If no tool use had been identified in the scientific literature for a species, then we coded the total number of papers published to date.
-We used the scientific database Scopus for coding the number of published papers.
-For the crowdsourced videos, we coded research effort as the number of search hits for each species on YouTube.
-If tool use had been identified on YouTube, we estimated the number of search hits when the first video of tool use was published on YouTube, assuming linear growth of search hits since the inception of YouTube.
-If tool use had not been identified, we used the current number of search hits.
+For modelling purposes, we coded research effort in both the scientific 
+literature and the crowdsourced videos. For the scientific literature, we 
+operationalised research effort as the number of papers published for each 
+species' Latin name up to and including the first paper containing tool use for 
+that species. If no tool use had been identified in the scientific literature 
+for a species, then we coded the total number of papers published to date. We 
+used the scientific database Scopus for coding the number of published papers. 
+For the crowdsourced videos, we coded research effort as the number of search 
+hits for each species on YouTube. If tool use had been identified on YouTube, we 
+estimated the number of search hits when the first video of tool use was 
+published on YouTube, assuming linear growth of search hits since the inception 
+of YouTube. If tool use had not been identified, we used the current number of 
+search hits.
 
-For phylogenetic data, we used the phylogenetic tool at www.birdtree.org[@Jetz2012] to compile 1000 posterior draws of phylogenetic trees for 174 of the 194 parrot species for which both EQ and genomic data exist.
-A single maximum clade credibility tree was generated from these posterior draws for visualisation purposes.
-In our analyses, we iterated over posterior draws of the phylogeny to account for phylogenetic uncertainty.
+For phylogenetic data, we used the phylogenetic tool at www.birdtree.org
+[@Jetz2012] to compile 1000 posterior draws of phylogenetic trees for 174 of the 
+194 parrot species for which both EQ and genomic data exist. A single maximum 
+clade credibility tree was generated from these posterior draws for 
+visualisation purposes. In our analyses, we iterated over posterior draws of the 
+phylogeny to account for phylogenetic uncertainty.
 
@@
 
-We used the _fitDiscrete_ function in the _ape_ R package[@Paradis2019] to calculate phylogenetic signal, for both the pre-survey and post-survey tool use data.
-We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
+We used the _fitDiscrete_ function in the _ape_ R package [@Paradis2019] to 
+calculate phylogenetic signal, for both the pre-survey and post-survey tool use 
+data. We iterated the model over 100 posterior parrot phylogenies to incorporate 
+phylogenetic uncertainty.
 
@@
 
-To infer unobserved probabilities of tool use across parrots, we proposed a causal model of observed tool use (Figure \@ref(fig:plotDAG)).
-We assumed that observed tool use in the scientific literature and in the crowdsourced videos is caused by both the unobserved presence or absence of tool use and research effort, proxied by the number of papers published on a species and the number of videos published on a species.
-Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected.
-In addition, based on theory, we also assumed that unobserved tool use is caused by feeding strategy and relative brain size[@Lefebvre2004;@Lefebvre1997;@Lefebvre2002;@Ducatez2015;@Sol2005;@Overington2011;@HenkeVonDerMalsburg2020].
-Finally, we assumed that shared phylogenetic history causes unobserved confounding and non-independence in unobserved tool use, feeding strategy, and relative brain size across the parrot phylogeny.
+To infer unobserved probabilities of tool use across parrots, we proposed a 
+causal model of observed tool use (Figure \@ref(fig:plotDAG)). We assumed that 
+observed tool use in the scientific literature and in the crowdsourced videos is 
+caused by both the unobserved presence or absence of tool use and research 
+effort, proxied by the number of papers published on a species and the number of 
+videos published on a species. Tool users are more likely to be observed if they 
+are well studied, but understudied tool users may go undetected. In addition, 
+based on theory, we also assumed that unobserved tool use is caused by feeding 
+strategy and relative brain size [@Lefebvre2004;@Lefebvre1997;@Lefebvre2002;
+@Ducatez2015;@Sol2005;@Overington2011;@HenkeVonDerMalsburg2020]. Finally, we 
+assumed that shared phylogenetic history causes unobserved confounding and 
+non-independence in unobserved tool use, feeding strategy, and relative brain 
+size across the parrot phylogeny.
 
@@
 
-Given our proposed causal model, we constructed a statistical model to impute unobserved probabilities of tool use and test existing theories of the evolution of tool use in parrots.
-To understand the model, suppose that we have the following observed variables for parrot species $i$.
-For the scientific literature, we declare $\text{N}_{\text{Lit},i}$ as the number of papers published before and up to tool use identification for species $i$ (or, if tool use has not been identified, the total number of papers published for species $i$) and $\text{T}_{\text{Lit},i}$ as a binary variable stating whether (1) or not (0) tool use has yet been observed in the scientific literature for species $i$.
-For the crowdsourced videos, we declare $\text{N}_{\text{Vid},i}$ as the number of videos published before and up to tool use identification for species $i$ (or, if tool use has not been identified, the total number of videos published for species $i$) and $\text{T}_{\text{Vid},i}$ as a binary variable stating whether (1) or not (0) tool use has yet been observed in the crowdsourced videos for species $i$.
-Additionally, $\text{F}_i$ and $\text{EQ}_i$ are feeding strategy and encephalisation quotient values for species $i$ and we have a phylogenetic distance matrix $D$ that describes the patristic distances between all parrot species.
+Given our proposed causal model, we constructed a statistical model to impute 
+unobserved probabilities of tool use and test existing theories of the evolution 
+of tool use in parrots. To understand the model, suppose that we have the 
+following observed variables for parrot species $i$. For the scientific 
+literature, we declare $\text{N}_{\text{Lit},i}$ as the number of papers 
+published before and up to tool use identification for species $i$ (or, if tool 
+use has not been identified, the total number of papers published for species 
+$i$) and $\text{T}_{\text{Lit},i}$ as a binary variable stating whether (1) or 
+not (0) tool use has yet been observed in the scientific literature for species 
+$i$. For the crowdsourced videos, we declare $\text{N}_{\text{Vid},i}$ as the 
+number of videos published before and up to tool use identification for species 
+$i$ (or, if tool use has not been identified, the total number of videos 
+published for species $i$) and $\text{T}_{\text{Vid},i}$ as a binary variable 
+stating whether (1) or not (0) tool use has yet been observed in the 
+crowdsourced videos for species $i$. Additionally, $\text{F}_i$ and 
+$\text{EQ}_i$ are feeding strategy and encephalisation quotient values for 
+species $i$ and we have a phylogenetic distance matrix $D$ that describes the 
+patristic distances between all parrot species.
 
-We assume that species $i$ is a non-tool-user (i.e.
-"cured") with some probability $p_i$.
-We also assume that tool use is identified in the scientific literature and the crowdsourced videos at constant rates $\lambda_{\text{Lit}}$ and $\lambda_{\text{Vid}}$ following exponential survival functions.
-Given these assumptions, we can then describe the different ways in which variables $\text{N}_\text{Lit}$ and $\text{N}_\text{Vid}$ can be distributed.
-Focusing on the scientific literature, if tool use has been observed ($\text{T}_{\text{Lit},i} = 1$), then the likelihood for $\text{N}_{\text{Lit},i}$ is:
+We assume that species $i$ is a non-tool-user with some 
+probability $p_i$. We also assume that tool use is identified in the scientific 
+literature and the crowdsourced videos at constant rates $\lambda_{\text{Lit}}$ 
+and $\lambda_{\text{Vid}}$ following exponential survival functions. Given these 
+assumptions, we can then describe the different ways in which variables 
+$\text{N}_\text{Lit}$ and $\text{N}_\text{Vid}$ can be distributed. Focusing on 
+the scientific literature, if tool use has been observed 
+($\text{T}_{\text{Lit},i} = 1$), then the likelihood for 
+$\text{N}_{\text{Lit},i}$ is:
 
@@
 
-On the other hand, if tool use has not yet been observed ($\text{T}_{\text{Lit},i} = 0$), there are two ways that the outcome variable could have been realised.
-First, the species could be a non-tool-user with probability $p_i$.
-Second, the species could be a tool-user with probability ($1 - p_i$) that has been censored and has not had its tool use measured yet.
+On the other hand, if tool use has not yet been observed 
+($\text{T}_{\text{Lit},i} = 0$), there are two ways that the outcome variable 
+could have been realised. First, the species could be a non-tool-user with 
+probability $p_i$. Second, the species could be a tool-user with probability 
+($1 - p_i$) that has been censored and has not had its tool use measured yet. 
 Together, then, the likelihood for $\text{N}_{\text{Lit},i}$ is:
@@
 
-The Exponential-CCDF function allows for the censored nature of the data. The same data generating process is assumed to underlie the crowdsourced videos.
+The Exponential-CCDF function allows for the censored nature of the data. The 
+same data generating process is assumed to underlie the crowdsourced videos.
 
-We define the mixture likelihood $\text{SurvivalCure}$ as the distribution above, with parameters $p$ (the probability of being a "cured" non-tool-user) and $\lambda$ (the rate of the exponential distribution).
-We use an Ornstein-Uhlenbeck Gaussian process[@McElreath2020] to model phylogenetic covariance.
-Below, we specify the full model with priors:
+We define the mixture likelihood $\text{SurvivalCure}$ as the distribution 
+above, with parameters $p$ (the probability of being a non-tool-user) 
+and $\lambda$ (the rate of the exponential distribution). We use an 
+Ornstein-Uhlenbeck Gaussian process [@McElreath2020] to model phylogenetic 
+covariance. Below, we specify the full model with priors:
 
@@
 
-The priors for this model produce reasonable prior predictions of the probabilities of tool use for each parrot species (Supplementary Figure \@ref(fig:plotSurvCure7)), but a sensitivity analysis revealed that the ranking and posterior probabilities reported in the main text were robust to modifying these priors (Supplementary Figure \@ref(fig:plotSurvCure8)).
-We estimated the posterior distribution of this model using Hamiltonian Monte Carlo as implemented in Stan version 2.26.1[@Stan2020].
-We ran the model for 4000 samples, with 2000 warmup samples, and iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
-R-hat values and effective sample sizes suggested that the model converged normally.
-Trace plots are reported in Supplementary Figure \@ref(fig:plotTrace).
-We report equal-tailed credible intervals to describe the posterior distribution of this model in the main text.
+The priors for this model produce reasonable prior predictions of the 
+probabilities of tool use for each parrot species (fig.
+\@ref(fig:plotSurvCure7)), but a sensitivity analysis revealed that the ranking 
+and posterior probabilities reported in the main text were robust to modifying 
+these priors (fig. \@ref(fig:plotSurvCure8)). We estimated the 
+posterior distribution of this model using Hamiltonian Monte Carlo as 
+implemented in Stan version 2.26.1 [@Stan2020]. We ran the model for 4000 
+samples, with 2000 warmup samples, and iterated the model over 100 posterior 
+parrot phylogenies to incorporate phylogenetic uncertainty. R-hat values and 
+effective sample sizes suggested that the model converged normally. Trace plots 
+are reported in fig. \@ref(fig:plotTrace). We report 
+equal-tailed credible intervals to describe the posterior distribution of this 
+model in the main text.
 
-To validate our method, we fitted the model to 100 simulated datasets with known parameters.
-The model was able to successfully recover those parameters (Supplementary Figure \@ref(fig:plotSurvCureSim)).
-We also ran a leave-one-species-out exercise to ensure that we could accurately predict known tool users.
-We repeated this approach for each known tool user by setting observed tool use to zero.
-Cross-validation results are reported in the main text.
+To validate our method, we fitted the model to 100 simulated datasets with known 
+parameters. The model was able to successfully recover those parameters 
+(fig. \@ref(fig:plotSurvCureSim)). We also ran a 
+leave-one-species-out exercise to ensure that we could accurately predict known 
+tool users. We repeated this approach for each known tool user by setting 
+observed tool use to zero. Cross-validation results are reported in the main 
+text.
 
@@
 
-To determine whether the identification of novel tool-using species has implications for our understanding of the evolutionary origins of tool use in parrots, we fitted three exploratory ancestral state reconstruction models.
-We used the _ancThresh_ function from the _phytools_ R package[@phytools], iterating the function over 100 posterior parrot phylogenies.
-This function estimates discrete ancestral states by assuming the evolution of a latent continuous variable following an Ornstein-Uhlenbeck process.
-We fitted this model to three different outcome variables: (_i_) presence vs.
-absence of tool use in scientific literature only, (_ii_) presence vs.
-absence of tool use in literature and/or videos, and (_iii_) the median predicted probabilities of tool use from the phylogenetic survival cure model.
+To determine whether the identification of novel tool-using species has 
+implications for our understanding of the evolutionary origins of tool use in 
+parrots, we fitted three exploratory ancestral state reconstruction models. We 
+used the _ancThresh_ function from the _phytools_ R package [@phytools], 
+iterating the function over 100 posterior parrot phylogenies. This function 
+estimates discrete ancestral states by assuming the evolution of a latent 
+continuous variable following an Ornstein-Uhlenbeck process. We fitted this 
+model to three different outcome variables: (_i_) presence vs. absence of tool 
+use in scientific literature only, (_ii_) presence vs. absence of tool use in 
+literature and/or videos, and (_iii_) the median predicted probabilities of tool 
+use from the phylogenetic survival cure model.
 
@@
 
-All analyses were conducted in R v4.2.1.[@RCoreTeam].
-Visualisations were produced using the _ggplot2_[@Wickham2016] and _cowplot_[@Wilke2020] packages.
-The manuscript was reproducibly generated using the _targets_[@Landau2021] and _papaja_[@Aust2022] packages.
-Code to reproduce all analyses and figures can be found here: https://github.com/ScottClaessens/phyloParrot
+All analyses were conducted in R v4.2.1. [@RCoreTeam]. Visualisations were 
+produced using the _ggplot2_ [@Wickham2016] and _cowplot_ [@Wilke2020] packages. 
+The manuscript was reproducibly generated using the _targets_ [@Landau2021] and 
+_papaja_ [@Aust2022] packages. Code to reproduce all analyses and figures can be 
+found here: https://github.com/ScottClaessens/phyloParrot
 
@@
 
-This project was made possible through the support of a grant from the Templeton World Charity Foundation (A.H.T., X.J.N.) and a Prime Minister’s McDiarmid Emerging Scientist Prize (A.H.T.).
-The authors would like to thank Daniel Sol for providing feedback on a previous version of the manuscript.
+This project was made possible through the support of a grant from the Templeton 
+World Charity Foundation (A.H.T., X.J.N.). The authors would like to thank 
+Daniel Sol for providing feedback on a previous version of the manuscript.
 
@@
 
-All authors contributed to the conceptualisation of the paper.
-A.P.M.B., X.J.N., and A.H.T.
-developed the video search methodology.
-S.C., D.W., and Q.A.D.
-developed the statistical models and analysed the data.
-All the authors wrote the manuscript and approved the final version for submission.
+All authors contributed to the conceptualisation of the paper. A.P.M.B., X.J.N., 
+and A.H.T. developed the video search methodology. S.C., D.W., and Q.A.D. 
+developed the statistical models and analysed the data. All the authors wrote 
+the manuscript and approved the final version for submission.
 
@@
 
-All data used in this study are publicly available on GitHub: https://github.com/ScottClaessens/phyloParrot
+All data used in this study are publicly available on GitHub: 
+https://github.com/ScottClaessens/phyloParrot
 
@@
 
-All code to reproduce the analyses in this study are publicly available on GitHub: https://github.com/ScottClaessens/phyloParrot
+All code to reproduce the analyses in this study are publicly available on 
+GitHub: https://github.com/ScottClaessens/phyloParrot
 

### 2023-11-20 manuscript.tex
prepare for submission

@@
 {}{\PatchFailed}
-\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling\newline\indent Word count: 4289 words excluding Methods (Methods: 1821 words)}
+\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling\newline\indent Word count: 6548 words}
 \usepackage{lineno}
@@
 \nolinenumbers
-\note{\raggedright † indicates shared first authorship, ‡ indicates shared senior authorship \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand.
+\note{\raggedright † These authors contributed equally to this work \par ‡ These authors contributed equally to this work \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand.
 \text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}} \par This working paper has not yet been peer-reviewed.}
@@
 \abstract{%
-Studying the prevalence of putatively rare behaviours, such as tool use, is challenging because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort.
-Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to approximate actual rates of a rarely observed behaviour based on limited data, targeting tool use in parrots.
-Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
-Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11\% and 17\% of extant parrot species may be tool users.
-These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait.
-Overall, our findings challenge the assumption that current sampling effort captures the full distribution of putatively rare animal behaviours.
-Combining our sampling and analysis methods offers a fruitful approach for investigating the distribution, drivers, and origins of other rare behaviours.
+Putatively rare behaviours, such as tool use, are challenging to study because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort.
+Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to estimate actual rates of tool use in parrots.
+Crowdsourcing revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
+Phylogenetic models incorporating these data together with measures of research effort and hypothesised predictors of tool use suggest that between 11\% and 17\% of parrot species may be tool users.
+These findings challenge the assumption that current research effort captures the distribution of putatively rare animal behaviours.
 }
@@
 
-\linenumbers
-
-Our understanding of the evolution of animal behaviour is built on the assumption that we have access to sufficient data\textsuperscript{1--3}.
-However, this is not always the case.
-Data on behaviours that are rare, fleeting, or otherwise difficult to observe are likely to be patchy and incomplete\textsuperscript{4,5}.
-Among species for which such behaviours have not been observed, it can be difficult to differentiate between cases in which the species is truly incapable of producing the behaviour and cases in which the species is capable of producing the behaviour but the behaviour has not yet been observed.
-Such a distinction can be critical for drawing conclusions about the rarity and evolution of the behaviour in question.
-
-Comparative work on the evolution of tool use is a paradigmatic example of this issue.
-The initial discoveries of tool use in chimpanzees\textsuperscript{6}, birds\textsuperscript{7}, dolphins\textsuperscript{8}, and octopuses\textsuperscript{9} occurred decades after significant advances on other more easily measurable aspects of their biology.
-Since these initial discoveries, scholars have used the distribution of reported tool use across species to make various claims about the evolutionary drivers of tool use behaviours.
-For example, based on the observation that bird species with reported tool use tended to have larger brains, researchers have identified higher relative brain size as a likely precondition for tool using capabilities\textsuperscript{10--12}.
-These researchers argue that larger brains are better able to integrate visual and somatosensory information when innovating novel behaviours, such as tool use, in changing environments\textsuperscript{13,14}.
-Similarly, researchers have used existing reports of tool use in birds to debate the roles of generalist versus specialist feeding strategies in driving the evolution of tool use, with some arguing that feeding generalists require technical innovations to expand their dietary niche\textsuperscript{13,15,16} and others arguing that feeding specialists require technical innovations for extractive foraging of specific foods\textsuperscript{17,18}.
-
-However, before we can make claims of this kind, we need to know whether current research effort in the literature is sufficient for robust conclusions to be drawn about the evolution of tool use.
-In fact, evidence suggests that research effort is often systematically biased towards particular taxonomic groups, parts of the world that are easy to access, and species with life history traits that make them easier to study, such as larger distribution ranges and population sizes\textsuperscript{19}.
-This is a crucial limitation because insufficient observation may lead researchers to miss true instances of tool behaviours and thus draw premature conclusions about the evolutionary drivers and origins of tool use.
-While researchers have attempted to deal with this problem by controlling for the number of scientific papers published on different species, previous work has not yet attempted to quantify and explicitly model the relationship between actual tool-using behaviour and what is reported in the scientific literature.
-If more tool-using species exist than previously thought, this could have important implications for theories of the evolutionary drivers and origins of tool use and, more generally, for our understanding of how rare this behaviour actually is.
-
-One potentially powerful method for quantifying actual rates of rare animal behaviours is crowdsourcing\textsuperscript{20}.
-In a crowdsourcing study, researchers collect reports from the general public and/or collate and analyse videos posted on social media platforms.
-This citizen science approach has been widely used in ecology to monitor the distributional patterns of species\textsuperscript{21}, but has also recently been used to uncover a variety of rare animal behaviours, including interspecies play in dogs\textsuperscript{20}, novel problem-solving behaviours in horses\textsuperscript{22}, and socially-learned foraging innovations in cockatoos\textsuperscript{23,24}.
-By casting the net wider than the scientific literature, the crowdsourcing method can provide an indication of the tool-using species that the literature might be missing.
-
-Even after using this crowdsourcing approach, some tool-users could \emph{still} remain unobserved.
-An additional approach to identify these unobserved species is to specify a causal model of the process that generates the observed data.
-We propose one such causal model in Figure \ref{fig:plotDAG}.
-In this model, we assume that the presence of tool use in the scientific literature (or in crowdsourced reports) is caused by both unobserved tool use capabilities and the number of published studies (or the number of crowdsourced reports) for any given species.
-Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected.
-Furthermore, based on existing theories of the evolution of tool use\textsuperscript{10--18}, we propose that the unobserved presence or absence of tool use is additionally caused by relative brain size, feeding strategy, and shared phylogenetic ancestry.
-Expressing this causal model as a statistical model can suggest further species which are likely to be unobserved tool-users and, simultaneously, test existing theories of the evolutionary drivers of tool use without incorrectly assuming that absence of evidence is evidence of absence.
+\nolinenumbers
+
+Our understanding of the evolution of animal behaviour is built on the
+assumption that we have access to sufficient data (\emph{1}--\emph{3}). However, this is not always the case. Data on behaviours that are
+rare, fleeting, or otherwise difficult to observe are likely to be patchy and
+incomplete (\emph{4}, \emph{5}). Among species for which such behaviours
+have not been observed, it can be difficult to differentiate between cases in
+which the species is truly incapable of producing the behaviour and cases in
+which the species is capable of producing the behaviour but the behaviour has
+not yet been observed. Such a distinction can be critical for drawing
+conclusions about the rarity and evolution of the behaviour in question.
+
+Comparative work on the evolution of tool use is a paradigmatic example of this
+issue. The initial discoveries of tool use in chimpanzees (\emph{6}),
+birds (\emph{7}), dolphins (\emph{8}), and octopuses (\emph{9}) occurred
+decades after significant advances on other more easily measurable aspects of
+their biology. Since then, scholars have proposed a clear operational
+definition of tool use applicable to all species --- the manipulation of an
+unattached object as an extension of the animal's body to achieve a
+goal (\emph{10}) --- and have used the distribution of species meeting this
+definition to make various claims about the evolutionary drivers of tool use
+behaviours. For example, based on the observation that bird species with
+reported tool use tended to have larger brains, researchers have identified
+higher relative brain size as a likely precondition for tool using
+capabilities (\emph{11}--\emph{13}). These researchers
+argue that larger brains are better able to integrate visual and somatosensory
+information when innovating novel behaviours, such as tool use, in changing
+environments (\emph{14}, \emph{15}). Similarly, researchers have used existing
+reports of tool use in birds to debate the roles of generalist versus
+specialist feeding strategies in driving the evolution of tool use, with some
+arguing that feeding generalists require technical innovations to expand their
+dietary niche (\emph{14}, \emph{16}, \emph{17}) and others arguing that
+feeding specialists require technical innovations for extractive foraging of
+specific foods (\emph{18}, \emph{19}).
+
+However, before we can make claims of this kind, we need to know whether current
+research effort in the literature is sufficient for robust conclusions to be
+drawn about the evolution of tool use. In fact, evidence suggests that research
+effort is often systematically biased towards particular taxonomic groups, parts
+of the world that are easy to access, and species with life history traits that
+make them easier to study, such as larger distribution ranges and population
+sizes (\emph{20}). This is a crucial limitation because insufficient
+observation may lead researchers to miss true instances of tool behaviours and
+thus draw premature conclusions about the evolutionary drivers and origins of
+tool use. While researchers have attempted to deal with this problem by
+controlling for the number of scientific papers published on different species,
+previous work has not yet attempted to quantify and explicitly model the
+relationship between actual tool-using behaviour and what is reported in the
+scientific literature. If more tool-using species exist than previously thought,
+this could have important implications for theories of the evolutionary drivers
+and origins of tool use and for our understanding of how rare this behaviour
+actually is.
+
+One potentially powerful method for quantifying actual rates of rare animal
+behaviours is crowdsourcing (\emph{21}). In a crowdsourcing study, researchers
+collect reports from the general public and/or collate and analyse videos posted
+on social media platforms. This citizen science approach has been widely used in
+ecology to monitor the distributional patterns of species (\emph{22}), but
+has also recently been used to uncover a variety of rare animal behaviours,
+including interspecies play in dogs (\emph{21}), novel problem-solving
+behaviours in horses (\emph{23}), and socially-learned foraging innovations
+in cockatoos (\emph{24}, \emph{25}). By casting the net wider than the
+scientific literature, the crowdsourcing method can provide an indication of the
+tool-using species that the literature might be missing.
+
+Even after using this crowdsourcing approach, some tool-users could \emph{still}
+remain unobserved. One principled framework for identifying these unobserved species
+is to specify a causal model of the process that generates the observed data. We
+propose one such causal model in Figure \ref{fig:plotDAG}. In this model, we
+assume that the presence of tool use in the scientific literature (or in
+crowdsourced reports) is caused by both unobserved tool use capabilities and the
+number of published studies (or the number of crowdsourced reports) for any
+given species. Tool users are more likely to be observed if they are well
+studied, but understudied tool users may go undetected. Furthermore, based on
+existing theories of the evolution of tool use (\emph{11}--\emph{19}), we propose that the
+unobserved tool use capabilities are additionally caused by relative brain size,
+feeding strategy, and shared phylogenetic ancestry. Expressing this causal model
+as a statistical model can suggest further species which are likely to be
+unobserved tool-users and, simultaneously, test existing theories of the
+evolutionary drivers of tool use without incorrectly assuming that absence of
+evidence is evidence of absence.
 
@@
 \includegraphics{manuscript_files/figure-latex/plotDAG-1.pdf}
-\caption{\label{fig:plotDAG}\emph{Causal model of observed tool use.} Directed acyclic graph of the causal relationships between observed tool use and other variables.
-Available scientific data on tool use is caused both by unobserved tool use presence and scientific research effort (i.e., number of publications).
-Available crowdsourced data on tool use is caused both by unobserved tool use presence and crowdsourcing effort (i.e., number of crowdsourced reports).
-According to theory, unobserved tool use presence should be caused by relative brain size (encephalisation quotient) and feeding strategy (generalist vs.~specialist).
-These variables all share unobserved confounds generated by shared phylogenetic history.
-Grey circles indicate unobserved variables.}
+\caption{\label{fig:plotDAG}\emph{Causal model of observed tool use.} Directed acyclic graph
+of the causal relationships between observed tool use and other variables.
+Available scientific data on tool use is caused both by unobserved tool use
+presence and scientific research effort (i.e., number of publications).
+Available crowdsourced data on tool use is caused both by unobserved tool use
+presence and crowdsourcing effort (i.e., number of crowdsourced reports).
+According to theory, unobserved tool use presence should be caused by relative
+brain size (encephalisation quotient) and feeding strategy (generalist vs.~
+specialist). These variables all share unobserved confounds generated by shared
+phylogenetic history. Grey circles indicate unobserved variables.}
 \end{figure}
 
-Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool use in the parrot order.
-We focus on tool use in parrots for a number of reasons.
-First, the scientific literature suggests that only a small proportion of extant parrot species (11 out of 398\textsuperscript{25}; 3\%) use tools\textsuperscript{10,26--38} (note that we do not include in this count species that have been previously shown to use touchscreen devices as these behaviours were explicitly trained\textsuperscript{39}).
-Parrot tool use thus provides an ideal test case for examining how robust sampling is in the scientific literature.
-Second, parrots are highly popular as pets.
-Over 70\% of all extant parrot species are bred in the aviculture industry and kept as pets worldwide\textsuperscript{40--46}, enabling us to leverage the power of crowdsourcing on a social media platform to search for evidence of tool use\textsuperscript{20}.
-Third, detailed data on relative brain sizes\textsuperscript{47--52}, feeding strategies\textsuperscript{53}, and shared ancestry\textsuperscript{54} exist for parrots, allowing us to fit the statistical model implied by Figure \ref{fig:plotDAG} to the entire parrot order.
-
-We first present the results from our crowdsourcing survey, in which we collated videos of tool use in parrots from an online video platform.
-This survey reveals a number of previously unidentified tool-using parrot species, which we map onto the phylogeny of the parrot order.
-We then describe our statistical model in more detail, and use it to (\emph{i}) rank further parrot species that are likely unobserved tool users and (\emph{ii}) re-examine key hypotheses regarding the evolutionary drivers and origins of tool use in parrots.
+Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool
+use in the parrot order. We focus on tool use in parrots for a number of
+reasons. First, the scientific literature suggests that only a small proportion
+of extant parrot species (11 out of 398; 3\%) use tools
+(\emph{11}, \emph{26}--\emph{38}). Parrot tool use
+thus provides an ideal test case for examining how robust sampling is in the
+scientific literature. Second, parrots are highly popular as pets. Over 70\% of
+all extant parrot species are bred in the aviculture industry and kept as pets
+worldwide (\emph{39}--\emph{45}), enabling us to leverage the power of crowdsourcing on a social
+media platform to search for evidence of tool use (\emph{21}). Third, detailed
+data on relative brain sizes (\emph{46}--\emph{51}), feeding strategies (\emph{52}), and
+shared ancestry (\emph{53}) exist for parrots, allowing us to fit the
+statistical model implied by Figure \ref{fig:plotDAG} to the entire parrot
+order.
+
+We first present the results from our crowdsourcing survey, in which we collated
+videos of tool use in parrots from an online video platform. This survey reveals
+a number of previously unidentified tool-using parrot species, which we map onto
+the phylogeny of the parrot order. We then describe our statistical model in
+more detail, and use it to (\emph{i}) rank further parrot species that are likely
+unobserved tool users and (\emph{ii}) re-examine key hypotheses regarding the
+evolutionary drivers and origins of tool use in parrots.
 
@@
 
-\hypertarget{crowdsourcing-video-survey}{%
-\subsection{Crowdsourcing video survey}\label{crowdsourcing-video-survey}}
-
-We surveyed the social media platform YouTube for video evidence of tool use in parrots (see Methods for detailed search criteria).
-In our search, we defined ``true'' tool use behaviour as the manipulation of an unattached object to achieve a goal\textsuperscript{55}, while ``borderline'' tool use involved the use of an object that was still attached to a substrate\textsuperscript{56}.
-
-In total, we found 116 videos of 104 individuals from 25 parrot species performing either true tool use (100 videos of 89 individuals from 22 species) or borderline tool use (16 videos of 16 individuals from 7 species).
-All videos featured pet parrots in captive settings.
-In 68 of these videos, owners did not appear to interfere with the subjects' actions.
-In 43 videos, there was potential interference, either from the owners being in close physical contact with the bird (e.g., bird perching on hand), talking to the bird, or handing it the tool (which occurred in only two videos).
-We could not establish the degree of interference in the remaining 5 videos, as sound had been removed or was substituted by music.
-None of the videos featured owners directly rewarding tool use behaviours with food.
-All borderline tool use cases were excluded from further analyses.
-
-Of the 22 parrot species performing true tool use, 13 were represented in our video survey by two or more individuals over multiple independent observations.
-True tool use always involved the subject using an object for self-scratching (95 videos involved scratching the head and/or neck).
-The most common tool (53 videos) was a moulted feather.
-Human-made objects (e.g., pens, spoons, pieces of wood, cardboard) were also common.
-
-According to YouTube video descriptions and owner comments, 45 of the individuals performing true tool use were males and 18 were females.
-No sex information was provided for the remaining 26 individuals.
-As owners provided no information on whether sex had been established through genetic testing, and sexual dimorphism in parrots is rare\textsuperscript{57,58}, we could not typically ascertain if descriptions were accurate.
-It is unclear if the disproportionately large number of males in the sample is a consequence of owners more readily assuming their parrots are male when they have not been genetically tested, owners being more likely to own or film male parrots, or male parrots exhibiting more true tool use behaviours than female parrots.
-
-Figure \ref{fig:plotPhylo1} maps the findings from the video survey onto a maximum clade credibility phylogeny for the parrot order, plotted alongside species previously identified in the scientific literature.
-Before the video survey, 11 parrot species (3\%) had been identified as tool users in the scientific literature.
-Across our video survey, we observed true tool use in 22 species, 5 of which overlapped with the scientific literature and 17 of which were novel species.
-All of the species identified in the video survey were cockatoos (Cacatuidae), Old World parrots (Psittacinae), or neotropical parrots (Arinae).
-The most common species in our survey, accounting for 41 videos from 37 individuals, was the green-cheeked conure (\emph{Pyrrhura molinae}).
-In accordance with the scientific literature, the video survey found no evidence of tool use in any species of Psittaculidae, despite this family containing some of the most commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet species.
-Combining both the video survey and the scientific literature, we can thus identify 28 tool-using parrot species overall (7\%), compared to the 11 previously reported.
+\hypertarget{crowdsourcing-reveals-tool-use-in-additional-parrot-species}{%
+\subsection{Crowdsourcing reveals tool use in additional parrot species}\label{crowdsourcing-reveals-tool-use-in-additional-parrot-species}}
+
+We surveyed the social media platform YouTube for video evidence of tool use in
+parrots (see Methods for detailed search criteria). In our search, we used the
+standard criteria for identifying tool use in the literature, defining ``true''
+tool use behaviour as the manipulation of an unattached object as an extension
+of the animal's body to achieve a goal (\emph{10}), while ``borderline'' tool
+use involved the use of an object that was still attached to a substrate
+(\emph{54}).
+
+In total, we found 116 videos of
+104 individuals from
+25
+parrot species performing behaviours that met the definition of either true tool
+use (100 videos of
+89
+individuals from
+22
+species) or borderline tool use (16 videos of
+16
+individuals from
+7
+species). All videos featured pet parrots in captive settings. In
+68 of these
+videos, owners did not appear to interact with the subjects. In
+43 videos,
+there was potential human interaction, either from the owners being in close physical
+contact with the bird (e.g., bird perching on hand), talking to the bird, or
+handing it the tool (which occurred in only two videos). We could not establish
+the degree of human interaction in the remaining
+5
+videos, as sound had been removed or was substituted by music. None of the
+videos featured owners directly rewarding tool use behaviours with food. All
+borderline tool use cases were excluded from further analyses.
+
+Of the 22
+parrot species performing true tool use,
+13
+were represented in our video survey by two or more individuals over multiple
+independent observations. True tool use always involved the subject using an
+object for self-scratching (95
+videos involved scratching the head and/or neck). The most common tool (53
+videos) was a moulted feather. Human-made objects (e.g., pens, spoons, pieces of
+wood, cardboard) were also common.
+
+According to YouTube video descriptions and owner comments,
+45
+of the individuals performing true tool use were males and
+18
+were females. No sex information was provided for the remaining
+26
+individuals. As owners provided no information on whether sex had been
+established through genetic testing, and sexual dimorphism in parrots is
+rare (\emph{55}, \emph{56}), we could not typically ascertain if descriptions
+were accurate. It is unclear if the disproportionately large number of males in
+the sample is a consequence of owners more readily assuming their parrots are
+male when they have not been genetically tested, owners being more likely to own
+or film male parrots, or male parrots exhibiting more true tool use behaviours
+than female parrots.
+
+Figure \ref{fig:plotPhylo1} maps the findings from the video survey onto a
+maximum clade credibility phylogeny for the parrot order, plotted alongside
+species previously identified in the scientific literature. Before the video
+survey, 11 parrot species (3\%) had been identified as tool users in the
+scientific literature. Across our video survey, we observed true tool use in
+22
+species, 5 of which overlapped with the scientific literature and
+17
+of which were novel species. All of the species identified in the video survey
+were cockatoos (\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), or neotropical
+parrots (\emph{Arinae}). The most common species in our survey, accounting for
+41 videos from
+37
+individuals, was the green-cheeked conure (\emph{Pyrrhura molinae}). In accordance
+with the scientific literature, the video survey found no evidence of tool use
+in any species of Psittaculidae, despite this family containing some of the most
+commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet
+species. Combining both the video survey and the scientific literature, we can
+thus identify 28 tool-using parrot species overall (7\%), compared to the 11
+previously reported.
 
@@
 \includegraphics{manuscript_files/figure-latex/plotPhylo1-1.pdf}
-\caption{\label{fig:plotPhylo1}\emph{Results of crowdsourcing video survey and phylogenetic survival cure modelling mapped onto a maximum clade credibility phylogeny of the parrot order.} Purple tips indicate species observed in the scientific literature and in the video survey.
-Blue tips indicate species observed only in the scientific literature.
-Orange tips indicate species observed only in the video survey (note that three species observed only in the video survey are not present in the phylogeny due to a lack of genomic data: \emph{Psittacara erythrogenys}, \emph{Psittacus timneh}, and \emph{Aratinga nenday}).
-Yellow tips indicate the top ten most likely tool-using species from our phylogenetic survival cure model which were not observed in the scientific literature or the video survey.
-All other tips are labelled as absent (grey).
+\caption{\label{fig:plotPhylo1}\emph{Results of crowdsourcing video survey and phylogenetic
+survival cure modelling mapped onto a maximum clade credibility phylogeny of the
+parrot order.} Orange points in the inner ring indicate species observed in the
+video survey, with point size scaled by the number of videos for each species
+(note that three species observed only in the video survey are not present in
+the phylogeny due to a lack of genomic data: \emph{Psittacara erythrogenys},
+\emph{Psittacus timneh}, and \emph{Aratinga nenday}). Blue points in the outer ring
+indicate species observed in the scientific literature, with point size scaled
+by the number of papers published on each species. Yellow species names indicate
+the top ten most likely tool-using species from our phylogenetic survival cure
+model which were not observed in the scientific literature or the video survey.
 Total \emph{n} = 174 species.}
@@
 
-The identification of new tool-using species in our video survey increases the extent to which phylogeny can explain the distribution of tool use in the parrot order.
-We estimated phylogenetic signal (Pagel's \(\lambda\)) of tool use using both the pre-video-survey and post-video-survey data.
-Pagel's \(\lambda\) varies between 0 and 1, where 0 implies that the distribution of a trait across species is unexplained by phylogenetic relatedness and 1 implies that the distribution of a trait across species is fully explained by phylogeny.
-Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's \(\lambda\) of 0.60 (95\% credible interval {[}0.00 0.90{]}; total \emph{n} = 174 species).
-This estimate was moderate-to-strong, but highly uncertain.
-In comparison, combining the evidence from both the literature and the video survey (post-video-survey data; 28 tool-using species) resulted in a stronger and more certain estimate of phylogenetic signal.
-With these data, we estimated Pagel's \(\lambda\) = 0.65 (95\% CI {[}0.50 0.77{]}; total \emph{n} = 174 species).
-Thus, the results of our video survey increase the extent to which the distribution of tool use across parrot species can be explained by shared phylogenetic ancestry.
-This suggests that we can potentially use phylogenetic information, along with other variables, to identify further tool-using parrot species that may remain undetected.
-
-\hypertarget{phylogenetic-survival-cure-model}{%
-\subsection{Phylogenetic survival cure model}\label{phylogenetic-survival-cure-model}}
-
-In addition to the 28 tool-using species identified in the literature and our video survey, we fitted a Bayesian phylogenetic survival cure model to rank further species that are likely to be undetected tool-users (i.e., tool-using species with no tool use reported in the literature or in crowdsourced videos).
-
-Survival cure models are often used in the medical sciences to analyse the time to some event, such as cancer relapse, with censored patient data\textsuperscript{59}.
-The data are right-censored because some patients have relapsed when they are measured, and some have not yet relapsed when they are measured (i.e., they are censored).
-The cure aspect of these models comes from an additional assumption that a certain proportion of the population is ``cured'' and can never relapse, no matter how long we measure them for.
-
-Our tool use problem has the same features.
-We are modelling a time-to-event; specifically, the amount of ``time'' (i.e., observation opportunities measured as the number of published papers or crowdsourced videos) until tool use is identified.
-This is right-censored data, because many species will not have had tool use identified when we measure them.
-Moreover, we can assume that a certain proportion of the population is ``cured'' -- that is, they are not tool users, and so we will never identify tool use for them, no matter how long we measure them for.
-
-In our model, we infer the tool-using status of each species by allowing each species to have their own probability of being ``cured'' (i.e., not a tool user).
-Following our causal model (Figure \ref{fig:plotDAG}), we predict these probabilities based on feeding strategy, encephalisation quotient, and phylogenetic history (see Methods for full model).
-The model additionally takes research effort into account by allowing that, among species for which tool use is unobserved, all else being equal those with fewer published papers and fewer video search hits have a higher probability of being undetected tool users (Supplementary Figure \ref{fig:plotSurvCure3}).
-
-We found that this phylogenetic survival cure model was able to adequately distinguish between species with and without evidence for tool use, with an area-under-the-curve classification statistic of 0.95 (Supplementary Figure \ref{fig:plotSurvCure9}).
-To further estimate the accuracy of the model's predictions, we also used a leave-one-species-out approach with known tool users.
-For each of the 25 tool-using species that were represented on the phylogeny and for which we had brain size and genomic data (we lacked data for three tool-using species), we fitted the model to a modified dataset which set tool use to be absent for the target species in both the scientific literature and the video survey.
-Across 25 cross-validation models, 18 models (72\%) continued to predict the target species as having a median posterior probability of tool use that was within the range of all other tool users.
-This classification rate was greater than the baseline classification rate of 26\% for species without evidence of tool use in the full model (38 of 149 species without evidence of tool use had a median posterior probability of tool use that was within the range of the tool-using species).
-Together, the area-under-the-curve statistic and the leave-one-species-out approach suggest that the model is able to adequately classify known tool users, with some error.
-
-Figure \ref{fig:plotSurvCure1} visualises the ranked posterior probabilities of tool use from the phylogenetic survival cure model for all parrot species.
-As expected, the known tool users are ranked towards the top of this list.
-However, several ``tool use absent'' species also rank highly on the list, despite not being identified as tool users in the scientific literature or in our video survey.
-In fact, according to the model, the most likely tool user is a species for which tool use is unobserved in our data: the blue-eyed cockatoo (\emph{Cacatua opthalmica}).
-This species is endemic to Papua New Guinea and is relatively understudied, with only 6 published papers and 596 video search hits, which is fewer than the model expects are necessary to discover tool use when it is present (Figure \ref{fig:plotSurvCure2}).
-This species is also found in the \emph{Cacatua} genus, a clade containing several known tool users.
-This prediction makes sense given the high phylogenetic signal for tool use reported by the model (Supplementary Figures \ref{fig:plotSurvCure5} and \ref{fig:plotSurvCure6}).
-Beyond the blue-eyed cockatoo, other highly ranked species without observed evidence of tool use are the Meyer's parrot (\emph{Poicephalus meyeri}), the golden parakeet (\emph{Guaruba guarouba}), the long-billed corella (\emph{Cacatua tenuirostris}), the Solomons cockatoo (\emph{Cacatua ducorpsii}), the red-fronted parrot (\emph{Poicephalus gulielmi}), the Cape parrot (\emph{Poicephalus robustus}), the yellow-eared parrot (\emph{Ognorhynchus icterotis}), the red-vented cockatoo (\emph{Cacatua haematuropygia}), and the gang-gang cockatoo (\emph{Callocephalon fimbriatum}).
-Figure \ref{fig:plotPhylo1} plots these species on the parrot phylogeny, using the top ten highest ranked species without observed evidence of tool use as an abitrary cutoff for visualisation purposes.
+The identification of new tool-using species in our video survey increases the
+extent to which phylogeny can explain the distribution of tool use in the parrot
+order. We estimated phylogenetic signal (Pagel's \(\lambda\)) of tool use using
+both the pre-video-survey and post-video-survey data. Pagel's \(\lambda\) varies
+between 0 and 1, where 0 implies that the distribution of a trait across species
+is unexplained by phylogenetic relatedness and 1 implies that the distribution
+of a trait across species is fully explained by phylogeny. Using the evidence of
+tool use from the scientific literature alone (pre-video-survey data; 11
+tool-using species), we estimated an average posterior Pagel's \(\lambda\) of
+0.60 (95\% credible interval {[}0.00
+0.90{]}; total \emph{n} =
+174 species). This estimate was moderate-to-strong, but highly
+uncertain. In comparison, combining the evidence from both the literature and
+the video survey (post-video-survey data; 28 tool-using species) resulted in a
+stronger and more certain estimate of phylogenetic signal. With these data, we
+estimated Pagel's \(\lambda\) = 0.65 (95\% CI
+{[}0.50
+0.77{]}; total \emph{n} =
+174 species). Thus, the results of our video survey increase
+the extent to which the distribution of tool use across parrot species can be
+explained by shared phylogenetic ancestry. This suggests that we can potentially
+use phylogenetic information, along with other variables, to identify further
+tool-using parrot species that may remain undetected.
+
+\hypertarget{phylogenetic-survival-cure-modelling-identifies-further-candidate-tool-users}{%
+\subsection{Phylogenetic survival cure modelling identifies further candidate tool users}\label{phylogenetic-survival-cure-modelling-identifies-further-candidate-tool-users}}
+
+In addition to the 28 tool-using species identified in the literature and our
+video survey, we fitted a Bayesian phylogenetic survival cure model to rank
+further species that are likely to be undetected tool-users (i.e., tool-using
+species with no tool use reported in the literature or in crowdsourced videos).
+
+Survival cure models (\emph{57}), also known as split population
+models (\emph{58}), are used to analyse the time to some event of interest
+with the added assumption that a certain proportion of the population will never
+experience the event, no matter how long they are measured for. These models
+have been used to analyse a variety of right-censored outcomes, from cancer
+relapse (\emph{57}) to criminal recidivism (\emph{58}). The data are
+right-censored because some individuals will have experienced the event when
+they are measured (e.g., disease onset, return to prison) while others will have
+not experienced the event. For those who have not experienced the event, this
+may be because (\emph{i}) the event has not happened to them yet or (\emph{ii}) the event
+will \emph{never} happen to them. Survival cure models treat these two processes
+separately.
+
+Our tool use problem has the same features. We are modelling a time-to-event;
+specifically, the amount of ``time'' (i.e., observation opportunities measured as
+the number of published papers or crowdsourced videos) until tool use is
+identified. This is right-censored data because many species will not have had
+tool use identified when we measure them. Moreover, we can assume that a certain
+proportion of the population will never experience the event -- that is, they
+are a non-tool-user and so we will never identify tool use no matter how long we
+measure them for.
+
+In our model, we infer the tool-using status of each species by allowing each
+species to have their own probability of being a non-tool-user. Following our
+causal model (Figure \ref{fig:plotDAG}), we predict these probabilities based
+on feeding strategy, encephalisation quotient, and phylogenetic history (see
+Methods for full model). The model additionally takes research effort into
+account by allowing that, among species for which tool use is unobserved, all
+else being equal those with fewer published papers and fewer video search hits
+have a higher probability of being undetected tool users (fig.~
+\ref{fig:plotSurvCure3}).
+
+We found that this phylogenetic survival cure model was able to adequately
+distinguish between species with and without evidence for tool use, with an
+area-under-the-curve classification statistic of
+0.95 (fig.\\
+\ref{fig:plotSurvCure9}). To further estimate the accuracy of the model's
+predictions, we also used a leave-one-species-out approach with known tool
+users. For each of the 25 tool-using species that were represented on the
+phylogeny and for which we had brain size and genomic data (we lacked data for
+three tool-using species), we fitted the model to a modified dataset which set
+tool use to be absent for the target species in both the scientific literature
+and the video survey. Across 25 cross-validation models,
+18 models (72\%)
+continued to predict the target species as having a median posterior probability
+of tool use that was within the range of all other tool users. This
+classification rate was greater than the baseline classification rate of
+26\%
+for species without evidence of tool use in the full model
+(38
+of 149 species without
+evidence of tool use had a median posterior probability of tool use that was
+within the range of the tool-using species). Together, the area-under-the-curve
+statistic and the leave-one-species-out approach suggest that the model is able
+to adequately classify known tool users, with some error.
+
+Figure \ref{fig:plotSurvCure1} visualises the ranked posterior probabilities of
+tool use from the phylogenetic survival cure model for all parrot species. As
+expected, the known tool users are ranked towards the top of this list. However,
+several ``tool use absent'' species also rank highly on the list, despite not
+being identified as tool users in the scientific literature or in our video
+survey. In fact, according to the model, the most likely tool user is a species
+for which tool use is unobserved in our data: the blue-eyed cockatoo (\emph{Cacatua
+opthalmica}). This species is endemic to Papua New Guinea and is relatively
+understudied, with only 6 published papers
+and 596 video search hits, which is fewer than the
+model expects are necessary to discover tool use when it is present (Figure
+\ref{fig:plotSurvCure2}). This species is also found in the \emph{Cacatua} genus, a
+clade containing several known tool users. This prediction makes sense given the
+high phylogenetic signal for tool use reported by the model (Supplementary
+Figures \ref{fig:plotSurvCure5} and \ref{fig:plotSurvCure6}). Beyond the
+blue-eyed cockatoo, other highly ranked species without observed evidence of
+tool use are the Meyer's parrot (\emph{Poicephalus meyeri}), the golden parakeet
+(\emph{Guaruba guarouba}), the long-billed corella (\emph{Cacatua tenuirostris}), the
+Solomons cockatoo (\emph{Cacatua ducorpsii}), the red-fronted parrot (\emph{Poicephalus
+gulielmi}), the Cape parrot (\emph{Poicephalus robustus}), the yellow-eared parrot
+(\emph{Ognorhynchus icterotis}), the red-vented cockatoo (\emph{Cacatua haematuropygia}),
+and the gang-gang cockatoo (\emph{Callocephalon fimbriatum}). Figure
+\ref{fig:plotPhylo1} plots these species on the parrot phylogeny, using the top
+ten highest ranked species without observed evidence of tool use as an arbitrary
+cutoff for visualisation purposes.
 
@@
 \includegraphics{manuscript_files/figure-latex/plotSurvCure1-1.pdf}
-\caption{\label{fig:plotSurvCure1}\emph{Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model.} Points are posterior medians and lines are 50\% and 95\% credible intervals.
-Total \emph{n} = 174 species.}
+\caption{\label{fig:plotSurvCure1}\emph{Posterior predicted probabilities of tool use for
+each species from our phylogenetic survival cure model.} Points are posterior
+medians and lines are 50\% and 95\% credible intervals. Total \emph{n} =
+174 species.}
 \end{figure}
@@
 \includegraphics{manuscript_files/figure-latex/plotSurvCure2-1.pdf}
-\caption{\label{fig:plotSurvCure2}\emph{Expected number of published papers and videos until tool use discovery, according to the survival component of the phylogenetic survival cure model.} Densities are full posterior distributions, points are posterior medians, and lines are 50\% and 95\% credible intervals.}
+\caption{\label{fig:plotSurvCure2}\emph{Expected number of published papers and videos until
+tool use discovery, according to the survival component of the phylogenetic
+survival cure model.} Densities are full posterior distributions, points are
+posterior medians, and lines are 50\% and 95\% credible intervals.}
 \end{figure}
 
-The posterior probabilities shown in Figure \ref{fig:plotSurvCure1} are estimated with uncertainty, so it is difficult to ``identify'' any particular species as an undetected tool user.
-Nevertheless, taking the sum of all the posterior probabilities for the 149 species without observed evidence of tool use, we can estimate that around 26 of those species are likely to be undetected tool users (median sum of probabilities = 25.68, 95\% CI {[}15.15 41.33{]}).
-When combined with the species known to use tools, this implies that between 11\% and 17\% of extant parrot species may be tool users.
+The posterior probabilities shown in Figure \ref{fig:plotSurvCure1} are
+estimated with uncertainty, so it is difficult to ``identify'' any particular
+species as an undetected tool user. Nevertheless, taking the sum of all the
+posterior probabilities for the
+149 species without
+observed evidence of tool use, we can estimate that around
+26 of those species are likely to be
+undetected tool users (median sum of probabilities =
+25.68, 95\% CI
+{[}15.15
+41.33{]}). When combined with the
+species known to use tools, this implies that between 11\% and 17\% of extant
+parrot species may be tool users.
 
@@
 
-The predicted probabilities from our phylogenetic survival cure model have implications for inferences about the evolutionary drivers and origins of tool use in the parrot order.
-Regarding the drivers of tool use hypothesised in Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = 1.12, 95\% CI {[}0.39 2.00{]}; total \emph{n} = 174 species; Figure \ref{fig:plotSurvCure4}).
-This helps explain the ranking in Figure \ref{fig:plotSurvCure1}: the blue-eyed cockatoo has the largest relative brain size in the dataset.
-We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = 0.33, 95\% CI {[}-1.13 1.76{]}; total \emph{n} = 174 species).
-These results from the survival cure model differed from the results of models fitted to pre-video-survey and post-video-survey data without the survival cure component, which found no effect of relative brain size and no difference between feeding strategies, respectively (Supplementary Figure \ref{fig:plotComparison}).
+The predicted probabilities from our phylogenetic survival cure model have
+implications for inferences about the evolutionary drivers and origins of tool
+use in the parrot order. Regarding the drivers of tool use hypothesised in
+Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that
+encephalisation quotient strongly positively predicted the probability of tool
+use (median posterior log odds slope = 1.12, 95\%
+CI {[}0.39
+2.00{]}; total \emph{n} = 174
+species; Figure \ref{fig:plotSurvCure4}). This helps explain the ranking in
+Figure \ref{fig:plotSurvCure1}: the blue-eyed cockatoo has the largest relative
+brain size in the dataset. We also found that feeding generalist species were
+slightly more likely to be tool users, though the posterior difference between
+generalists and specialists was quite uncertain (median posterior log odds
+difference = 0.33, 95\% CI {[}
+-1.13 1.76{]}; total
+\emph{n} = 174 species). These results from the survival cure model
+differed from the results of models fitted to pre-video-survey and
+post-video-survey data without the survival cure component, which found no
+effect of relative brain size and no difference between feeding strategies,
+respectively (fig.~\ref{fig:plotComparison}).
 
@@
 \includegraphics{manuscript_files/figure-latex/plotSurvCure4-1.pdf}
-\caption{\label{fig:plotSurvCure4}\emph{Posterior predictions for the effects of feeding strategy and encephalisation quotient on the probability of tool use from the phylogenetic survival cure model.} In the left plot, points and lines represent posterior medians and 50\% and 95\% credible intervals, with densities representing full posterior distributions.
-In the right plot, the line and shaded area represents the posterior median regression line with 95\% credible intervals.
-In both plots, individual species are coloured according to the presence / absence of tool use in the video survey and the scientific literature.
-Total \emph{n} = 174 species, generalist \emph{n} = 121 species, specialist \emph{n} = 53 species.}
+\caption{\label{fig:plotSurvCure4}\emph{Posterior predictions for the effects of feeding
+strategy and encephalisation quotient on the probability of tool use from the
+phylogenetic survival cure model.} In the left plot, points and lines represent
+posterior medians and 50\% and 95\% credible intervals, with densities
+representing full posterior distributions. In the right plot, the line and
+shaded areas represent the posterior median regression line with 50\% and 95\%
+credible intervals. In both plots, individual species are coloured according to
+the presence / absence of tool use in the video survey and the scientific
+literature. Total \emph{n} = 174 species, generalist \emph{n} =
+121 species, specialist \emph{n} =
+53 species.}
 \end{figure}
 
-Regarding the origins of tool use, we fitted exploratory ancestral state reconstruction models to the pre-video-survey data, the post-video-survey data, and the predicted probabilities from the phylogenetic survival cure model.
-The discoveries from our video survey and from our phylogenetic modelling increased the likelihood that tool use was present in the most recent common ancestor for several parrot genera.
-These include the amazon parrots native to the Americas (\emph{Amazona}), the true white cockatoos and corellas found in South East Asia and Australasia (\emph{Cacatua}), the kea and the kākā from New Zealand (\emph{Nestor}), and the \emph{Poicephalus} genus native to Africa (Table \ref{tab:tableASR}; Supplementary Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}).
-These findings suggest that species from each of these genera share their tool use capabilities via common descent from their respective common ancestors, rather than via independent evolution within each genus.
+Regarding the origins of tool use, we fitted exploratory ancestral state
+reconstruction models to the pre-video-survey data, the post-video-survey data,
+and the predicted probabilities from the phylogenetic survival cure model. The
+discoveries from our video survey and from our phylogenetic modelling increased
+the likelihood that tool use was present in the most recent common ancestor for
+several parrot genera. These include the amazon parrots native to the Americas
+(\emph{Amazona}), the true white cockatoos and corellas found in South East Asia and
+Australasia (\emph{Cacatua}), the kea and the kākā from New Zealand (\emph{Nestor}), and
+the \emph{Poicephalus} genus native to Africa (Table \ref{tab:tableASR};
+fig.~s \ref{fig:plotASR1} - \ref{fig:plotASR3}). These findings
+suggest that species from each of these genera may share their tool use
+capabilities via common descent from their respective common ancestors, rather
+than via independent evolution within each genus or behavioural innovation
+within species.
 
@@
 
-\caption{\label{tab:tableASR}Estimated probabilities of tool use for most recent common ancestors of several parrot genera.
-\emph{Probabilities estimated using exploratory ancestral state reconstruction models fitted to the pre-video-survey data, post-video-survey data, and predicted probabilities from the phylogenetic survival cure model.
-Total} n \emph{= 174 species.}}
+\caption{\label{tab:tableASR}Estimated probabilities of tool use for most recent common
+ancestors of several parrot genera. \emph{Probabilities estimated using exploratory
+ancestral state reconstruction models fitted to the pre-video-survey data,
+post-video-survey data, and predicted probabilities from the phylogenetic
+survival cure model. Total} n \emph{= 174 species.}}
 
@@
 
-Since the earliest anecdotal reports of parrots using tools in the 1970s\textsuperscript{60}, only 11 parrot species (3\% of all extant parrot species) have been documented as tool users in the scientific literature.
-Our study used crowdsourcing to identify 17 additional tool-using parrot species that are new to science, more than doubling the overall count to 28 species (7\%).
-These species consisted of cockatoos (Cacatuidae), Old World parrots (Psittacinae), and neotropical parrots (Arinae).
-
-We found strong phylogenetic signal in our extended dataset, demonstrating that the distribution of tool use across parrot species is affected by shared phylogenetic ancestry.
-This allowed us to use phylogenetic information, along with other variables, to infer the unobserved probabilities of tool use across the parrot order.
-Our phylogenetic survival cure model incorporated information on phylogenetic history, research effort, relative brain size, and feeding specialisation to rank parrot species that were most likely to be undetected tool users.
-The sum of probabilities from this model implied that between 15 and 41 of the species without observed evidence of tool use are likely to be undetected tool users, suggesting that the true proportion of tool users may be as high as 17\%.
-
-These findings have a number of important implications.
-First, our findings show that current research effort in the scientific literature is insufficient to capture the real world occurrence of parrot tool use.
-If the scientific literature had sampled the natural world sufficiently, we would expect to see close correspondence between those species reported as tool users in the literature and those species the public have filmed performing tool use.
-Instead, we discovered a large discrepancy between these two data sources, both in the prevalence of tool use and the species identified.
-This raises the possibility that insufficient research effort is a general issue across the scientific literature, both for tool use in other groups and for other rare behaviours.
-
-Second, in terms of the evolution of tool use in parrots, our study challenges a key assumption made in the literature to date: that only a minority of parrots are tool users\textsuperscript{30,31,34,37,38}.
-The paucity of evidence for tool use across parrots in the literature initially implied that tool use may have evolved independently in different parrot species.
-Our discovery of the widespread distribution of tool use across the parrot phylogeny, along with the strong phylogenetic signal in this expanded dataset, challenges this and suggests that, at least for some parrot clades, the capacity for tool use might be a homologous trait that has been evolutionarily conserved.
-Our exploratory ancestral state reconstruction analysis provides preliminary support for this hypothesis, revealing an increased probability of tool use among the most recent common ancestors for the \emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera.
-Even at this preliminary stage, our analysis therefore raises an alternative hypothesis for the observed tool use in \emph{Cacatua}\textsuperscript{30,38} and \emph{Nestor}\textsuperscript{26--29,31,34}, namely that tool behaviours have arisen due to the common ancestor being a tool user, rather than from behavioural innovation within a species.
-
-Third, our results support existing theories of the drivers of tool use.
-We found that encephalisation was strongly positively related to the probability of tool use in our phylogenetic model, supporting previous theories linking relative brain size to increased tool innovation in birds\textsuperscript{10--12} and primates\textsuperscript{61}.
-Nevertheless, we recognise that cross-species correlations between brain size and behaviour are challenging to interpret causally\textsuperscript{3,4}, and thus encourage further work on the specific neural correlates of technical intelligence in parrots (see e.g.\textsuperscript{62}).
-In our phylogenetic model, we also found that tool use was somewhat more likely among feeding generalists compared to feeding specialists, although this difference was uncertain.
-This trend supports previous suggestions that increased cognitive abilities and technical innovation rates are required to expand a generalist species' dietary niche\textsuperscript{15,17,63}.
-However, the trend contradicts theories linking tool use to dietary specialisation, whereby species eating specific foods that require extractive foraging have higher cognitive ability and are especially prone to using tools (reviewed in ref\textsuperscript{17}).
-
-We believe that the observations of tool use in our video survey reflect intentional tool use, rather than accidental object manipulations or trained behaviours.
-In the crowdsourcing video survey, individual parrots often used tools slowly and repetitively over long periods of time, even across multiple different videos, suggesting that their behaviour was not accidental\textsuperscript{64}.
-Moreover, for 60\% of the species we report on, we found two or more videos of repetitive and sustained scratching by different individuals in separate households.
-Following the assumption that accidental tool use (e.g., briefly holding an object and attempting to scratch oneself simultaneously) is rare\textsuperscript{65}, the repeated observation of the same tool use behaviours for scratching by multiple animals of the same species across multiple households suggests that these manipulations are intentional and recurring events rather than rare ``accidents'' and likely do not represent unusual stereotypies of a single individual.
-We also found little evidence to suggest that the tool use behaviours were trained or unintentionally cued by the birds' owners.
-Over half of the videos coded contained no evidence of human interference with the parrots' tool use aside from filming the behaviour.
-Humans only handed parrots their tools in two of the videos, and none of the videos featured owners directly rewarding tool use behaviours with food.
-Finally, and perhaps most importantly, the high levels of phylogenetic signal in our data provides strong evidence that the observations from our video survey reflect biologically-endowed capacities for tool use rather than accidents or trained behaviours, which would likely appear uniformly across the phylogeny.
-
-While missing data imputation is becoming more common in phylogenetic analyses\textsuperscript{66}, the important distinction between absence of evidence and evidence of absence has not been given as much attention.
-Our phylogenetic analysis provides one approach to this problem by distinguishing between true absences of tool use and absences of tool use due to a lack of research effort in the scientific literature or in crowdsourced videos.
-To achieve this, we explicitly modelled the measurement of the outcome variable along a research effort time series, such that species with lower research effort in the literature or in videos were likely to be censored.
-In line with our causal model, we also included relative brain size, feeding strategy, and phylogenetic history as predictors of unobserved tool use.
-We encourage researchers to test this model by directing future study efforts towards the parrot species with the highest probabilities of being undetected tool-users.
-Future work should also refine the causal model in Figure \ref{fig:plotDAG} to provide more certain estimates of tool use probabilities, either by including additional predictor variables or modelling further causes of measurement error in the taxonomic record, such as species abundance and geographic accessibility\textsuperscript{19}.
-
-In conclusion, we have shown that the scientific literature has insufficiently captured the full distribution of tool use in the parrot order.
-Our crowdsourcing survey has more than doubled the number of known tool using parrot species from 11 to 28, and our phylogenetic inference suggested that the true proportion of parrot tool users could be as high as 17\%.
-These discoveries have implications for theories of the evolutionary drivers and origins of tool use in parrots.
-Beyond parrot tool use, the crowdsourcing and phylogenetic methods used in this study have the potential to be applied to other rarely observed behaviours, including tool use in other taxa\textsuperscript{67}, rhythmic entrainment in birds\textsuperscript{68--71}, teasing behaviours in primates\textsuperscript{72}, and tactical deception across the animal kingdom\textsuperscript{73--75}.
-We hope that these methods will continue to uncover a diverse array of ephemeral behaviours that have as yet gone undetected in the scientific literature.
+Since the earliest anecdotes of parrots using tools by Wallace in the 1880s
+(\emph{59}) and more systematic anecdotal reports in the 1970s (\emph{60}),
+only 11 parrot species (3\% of all extant parrots) have been documented as tool
+users in the scientific literature. Our study used crowdsourcing to identify 17
+additional tool-using parrot species that are new to science, more than doubling
+the overall count to 28 species (7\%). These species consisted of cockatoos
+(\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), and neotropical parrots
+(\emph{Arinae}).
+
+While parrots in the wild use tools to achieve a variety of
+goals (\emph{34}, \emph{38}), the 17 additional species identified by our
+video survey were exclusively observed using tools for self-scratching. This is
+likely because preening is the only context in which captive parrots regularly
+require tools, unlike wild parrots who may also require tools for extractive
+foraging (\emph{34}, \emph{38}). Despite this difference in the type of tool
+use observed, self-scratching is nonetheless a major category of animal tool
+use and clearly meets the established criteria for tool use in the literature:
+the manipulation of an unattached object as an extension of the animal's body to
+achieve a goal (\emph{10}). It also meets the definition for a more complex
+type of embodied tool use known as `tooling', the deliberate generation of a
+mechanical interface by using an object to manipulate another target or
+surface (\emph{61}). The fact that we found strong phylogenetic clustering
+of self-scratching tool use from the video survey with other examples of tool
+use from the literature supports a common underlying cognitive mechanism. In
+line with this, some of the species of parrots that use tools for
+self-scratching in captivity also use tools for other purposes in the wild
+(\emph{30}, \emph{31}, \emph{34}, \emph{38}).
+
+There was little evidence to suggest that the observations of self-scratching
+tool use in the video survey were merely unintentional accidents or explicitly
+trained behaviours. Individual parrots often used tools slowly and repetitively
+over long periods of time, even across multiple different videos, suggesting
+that their behaviour was not random or accidental (\emph{62}). Parrots
+preferentially employed self-scratching tools on areas of their body that were
+otherwise inaccessible, with 96\% of all instances involving scratching of the
+head or neck, suggesting intentional tool use. For 60\% of the species in the
+video survey, we found two or more videos of repetitive and sustained scratching
+by different individuals of the same species in separate households, suggesting
+that the manipulations were intentional and recurring events that did not
+represent unusual stereotypies of any single individual. Regarding the
+possibility of training or cueing from owners, over half of the videos contained
+no evidence of human interaction aside from filming the behaviour. Humans only
+handed parrots their tools in two of the videos, and none of the videos featured
+owners directly rewarding tool use behaviours with food. Finally, the high
+levels of phylogenetic signal in our data provides strong evidence that the
+observations from our video survey reflect biologically-endowed capacities for
+tool use rather than accidental or trained behaviours, which would likely appear
+uniformly across the phylogeny.
+
+Beyond the video survey, the strong phylogenetic signal in our dataset allowed
+us to use phylogenetic information, along with other variables, to infer the
+unobserved probabilities of tool use across the parrot order. Our phylogenetic
+survival cure model incorporated information on phylogenetic history, research
+effort, relative brain size, and feeding specialisation to rank parrot species
+that were most likely to be undetected tool users. The sum of probabilities from
+this model implied that between 15 and 41 of the species without observed
+evidence of tool use are likely to be undetected tool users, suggesting that the
+true proportion of tool users may be as high as 17\%.
+
+These findings have a number of important implications. First, our findings show
+that current research effort in the scientific literature is insufficient to
+capture the real world occurrence of parrot tool use. If the scientific
+literature had sampled the natural world sufficiently, we would expect to see
+close correspondence between those species reported as tool users in the
+literature and those species the public have filmed performing tool use.
+Instead, we discovered a large discrepancy between these two data sources, both
+in the prevalence of tool use and the species identified. This raises the
+possibility that insufficient research effort is a general issue across the
+scientific literature, both for tool use in other groups and for other rare
+behaviours.
+
+Second, in terms of the evolution of tool use in parrots, our study challenges a
+key assumption made in the literature to date: that only a minority of parrots
+are tool users (\emph{30}, \emph{31}, \emph{34}, \emph{37}, \emph{38}).
+The paucity of evidence for tool use across parrots in the literature initially
+implied that the capacity for tool use may have evolved independently in
+different parrot species. Our discovery of the widespread distribution of tool
+use across the parrot phylogeny, along with the strong phylogenetic signal in
+this expanded dataset, challenges this and suggests that, at least for some
+parrot clades, the capacity for tool use might be a homologous trait that has
+been evolutionarily conserved. Our exploratory ancestral state reconstruction
+analysis provides preliminary support for this hypothesis, revealing an
+increased probability of tool use among the most recent common ancestors for the
+\emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera. Even at this
+preliminary stage, our analysis therefore raises an alternative hypothesis for
+the observed tool use in \emph{Cacatua} (\emph{30}, \emph{38}) and
+\emph{Nestor} (\emph{26}--\emph{29}, \emph{31}, \emph{34}), namely that tool behaviours have arisen due to the
+common ancestor having the capacity to use tools, rather than from independent
+evolution or behavioural innovation within species.
+
+Third, our results support existing theories of the drivers of tool use. We
+found that encephalisation was strongly positively related to the probability of
+tool use in our phylogenetic model, supporting previous theories linking
+relative brain size to increased tool innovation in birds (\emph{11}--\emph{13}) and primates (\emph{63}). We acknowledge that
+encephalisation quotient is not a perfect measure due to measurement error and
+challenges with interpretation (\emph{3}, \emph{4}). However, encephalisation
+quotient has much greater coverage across the parrot phylogeny than more
+fine-grained measures like whole neuron count (\emph{64}) and there is no reason
+to think that measurement error would produce the consistent patterns across our
+study and prior work. To understand the causal mechanisms responsible for these
+relationships, we encourage further work on the specific neural correlates of
+technical intelligence in parrots, e.g., (\emph{65}). In our phylogenetic
+model, we also found that tool use was somewhat more likely among feeding
+generalists compared to feeding specialists, although this difference was
+uncertain. This trend supports previous suggestions that increased cognitive
+abilities and technical innovation rates are required to expand a generalist
+species' dietary niche (\emph{16}, \emph{18}, \emph{66}). However, the trend contradicts theories linking tool use to
+dietary specialisation, whereby species eating specific foods that require
+extractive foraging have higher cognitive ability and are especially prone to
+using tools (\emph{18}).
+
+While missing data imputation is becoming more common in phylogenetic
+analyses (\emph{67}), the important distinction between absence of
+evidence and evidence of absence has not been given as much attention. Our
+phylogenetic analysis provides one approach to this problem by distinguishing
+between true absences of tool use and absences of tool use due to a lack of
+research effort in the scientific literature or in crowdsourced videos. To
+achieve this, we explicitly modelled the measurement of the outcome variable
+along a research effort time series, such that species with lower research
+effort in the literature or in videos were likely to be censored. In line with
+our causal model, we also included relative brain size, feeding strategy, and
+phylogenetic history as predictors of unobserved tool use. We encourage
+researchers to test this model by directing future study efforts towards the
+parrot species with the highest probabilities of being undetected tool-users.
+Future work should also refine the causal model in Figure \ref{fig:plotDAG} to
+provide more certain estimates of tool use probabilities, either by including
+additional predictor variables or modelling further causes of measurement error
+in the taxonomic record, such as species abundance and geographic
+accessibility (\emph{20}).
+
+In conclusion, we have shown that the scientific literature has insufficiently
+captured the full distribution of tool use in the parrot order. Our
+crowdsourcing survey more than doubled the number of known tool using parrot
+species from 11 to 28, and our phylogenetic model suggested that the true
+proportion of parrot tool users could be as high as 17\% of all species in this
+order. These discoveries have implications for theories of the evolutionary
+drivers and origins of tool use in parrots. Beyond parrot tool use, the
+crowdsourcing and phylogenetic methods used in this study have the potential to
+be applied to other rarely observed behaviours, including tool use in other
+taxa (\emph{68}), rhythmic entrainment in birds (\emph{69}--\emph{72}), teasing behaviours in primates (\emph{73}), and
+tactical deception across all animals (\emph{74}--\emph{76}).
+We hope that these methods will continue to uncover a diverse array of ephemeral
+behaviours that have as yet gone undetected in the scientific literature.
 
@@
 
-Our video search was conducted on YouTube in July 2020.
-Search terms included ``parrot using tool'' and variants (e.g., ``macaw using tool'', ``lorikeet using tool'', ``parakeet using tool''), ``tool use in parrot'', ``parrot tool use'', ``parrot scratching itself'' (included after we found several videos demonstrating self-care tool use in previous searches) and equivalent terms (e.g., ``parrot preening itself'', ``parrot grooming itself'', ``parrot scratching'').
-For all species that did not display results including object manipulation or scratching behaviours, we also searched the species' common name(s) + ``tool use'', as well as the species' common name(s) + ``scratching''.
-We also searched for translations of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all countries where bird ownership was reported as \textgreater5\%\textsuperscript{76}, namely, Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, Portuguese, and Mandarin.
-
-When we found a relevant video, we also searched for similar content uploaded by the same person/channel.
-For each YouTube search conducted, we watched all relevant videos until we reached five consecutive videos that did not feature any parrots.
-At this point, we ended that search and initiated the next search.
-In line with previous recommendations\textsuperscript{20}, we planned to exclude any videos that consisted of four or more shots edited together so as to ensure the behaviours being observed were not edited or manipulated, but none of the videos obtained qualified for exclusion.
-
-All videos featuring parrots manipulating objects were investigated for potential tool use or borderline tool use.
-We defined tool use as the manipulation of an unattached object as an extension of the beak or foot to achieve a goal towards another object, individual, or oneself\textsuperscript{55}.
-Borderline tool use was similarly defined, except that it involved the use of an object that was still attached to a substrate\textsuperscript{56}.
-For example, if individuals used a fallen feather or stick for self-scratching this was defined as tool use, but using one's currently attached tail feathers or cage furnishings for the same purpose was defined as borderline tool use.
-Self-scratching had to involve slow and repeated movements of touching an object to one's body (or, in the case of borderline tool use, rubbing repetitively against an attached object\textsuperscript{64}).
-
-All relevant videos were coded for video length, species, tool use presence (yes/borderline), tool use type (e.g., scratching, feeding), the object being used (e.g., feather, stick), tool use target, human interference with the action (talking or handing object to parrot, holding parrot), and the number of shots within each video.
-Our complete dataset also includes the name for each video, link, subject name, sex (as declared by owner, as most parrot species are not sexually dimorphic), publishing date, and dates found and coded.
+Our video search was conducted on YouTube in July 2020. Search terms included
+``parrot using tool'' and variants (e.g., ``macaw using tool'', ``lorikeet using
+tool'', ``parakeet using tool''), ``tool use in parrot'', ``parrot tool use'', ``parrot
+scratching itself'' (included after we found several videos demonstrating
+self-care tool use in previous searches) and equivalent terms (e.g., ``parrot
+preening itself'', ``parrot grooming itself'', ``parrot scratching''). For all
+species that did not display results including object manipulation or scratching
+behaviours, we also searched the species' common name(s) + ``tool use'', as well
+as the species' common name(s) + ``scratching''. We also searched for translations
+of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all
+countries where bird ownership was reported as \textgreater5\% (\emph{77}), namely,
+Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish,
+Portuguese, and Mandarin.
+
+When we found a relevant video, we also searched for similar content uploaded by
+the same person/channel. For each YouTube search conducted, we watched all
+relevant videos until we reached five consecutive videos that did not feature
+any parrots. At this point, we ended that search and initiated the next search.
+In line with previous recommendations (\emph{21}), we planned to exclude any
+videos that consisted of four or more shots edited together so as to ensure the
+behaviours being observed were not edited or manipulated, but none of the videos
+obtained qualified for exclusion.
+
+All videos featuring parrots manipulating objects were investigated for
+potential tool use or borderline tool use. We defined tool use as the
+manipulation of an unattached object as an extension of the beak or foot to
+achieve a goal towards another object, individual, or oneself (\emph{10}).
+Borderline tool use was similarly defined, except that it involved the use of an
+object that was still attached to a substrate (\emph{54}). For example, if
+individuals used a fallen feather or stick for self-scratching this was defined
+as tool use, but using one's currently attached tail feathers or cage
+furnishings for the same purpose was defined as borderline tool use.
+Self-scratching had to involve slow and repeated movements of touching an object
+to one's body (or, in the case of borderline tool use, rubbing repetitively
+against an attached object (\emph{62})).
+
+All relevant videos were coded for video length, species, tool use presence
+(yes/borderline), tool use type (e.g., scratching, feeding), the object being
+used (e.g., feather, stick), tool use target, human interaction
+(talking or handing object to parrot, holding parrot), and the number of shots
+within each video. Our complete dataset also includes the name for each video,
+link, subject name, sex (as declared by owner, as most parrot species are not
+sexually dimorphic), publishing date, and dates found and coded.
 
@@
 
-We collected data for 194 parrot species (Supplementary Figures \ref{fig:plotPhylo2} - \ref{fig:plotPhylo4}).
-We gathered feeding strategy data as a dichotomous variable (``generalist'' or ``specialist'') from the EltonTraits ecological database\textsuperscript{53}.
-As per the database, specialists were defined as species whose diet comprised at least 70\% of a single food source.
-To calculate relative brain size, we collated data from the literature for all known body mass (g) and brain mass (g) values across parrots\textsuperscript{47--52}.
-For all species for which we obtained body and brain mass data, we calculated the encephalisation quotient (EQ) using the following formula\textsuperscript{77}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\).
-We found body mass and brain mass data for a total of 194 parrot species.
-This included all tool-using species in our video dataset, with the exception of three species: \emph{Diopsittaca nobilis}, \emph{Psittacara erythrogenys}, and \emph{Coracopsis vasa}.
-For the latter, we used values for the closely related \emph{Coracopsis nigra}.
-The other two species were excluded from the final dataset.
-
-For modelling purposes, we coded research effort in both the scientific literature and the crowdsourced videos.
-For the scientific literature, we operationalised research effort as the number of papers published for each species' Latin name up to and including the first paper containing tool use for that species.
-If no tool use had been identified in the scientific literature for a species, then we coded the total number of papers published to date.
-We used the scientific database Scopus for coding the number of published papers.
-For the crowdsourced videos, we coded research effort as the number of search hits for each species on YouTube.
-If tool use had been identified on YouTube, we estimated the number of search hits when the first video of tool use was published on YouTube, assuming linear growth of search hits since the inception of YouTube.
-If tool use had not been identified, we used the current number of search hits.
-
-For phylogenetic data, we used the phylogenetic tool at www.birdtree.org\textsuperscript{54} to compile 1000 posterior draws of phylogenetic trees for 174 of the 194 parrot species for which both EQ and genomic data exist.
-A single maximum clade credibility tree was generated from these posterior draws for visualisation purposes.
-In our analyses, we iterated over posterior draws of the phylogeny to account for phylogenetic uncertainty.
+We collected data for 194 parrot species (figs.
+\ref{fig:plotPhylo2} - \ref{fig:plotPhylo4}). We gathered feeding strategy
+data as a dichotomous variable (``generalist'' or ``specialist'') from the
+EltonTraits ecological database (\emph{52}). As per the database, specialists
+were defined as species whose diet comprised at least 70\% of a single food
+source. To calculate relative brain size, we collated data from the literature
+for all known body mass (g) and brain mass (g) values across
+parrots (\emph{46}--\emph{51}). For all species for which we obtained body and brain mass data, we
+calculated the encephalisation quotient (EQ) using the following
+formula (\emph{78}): \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
+found body mass and brain mass data for a total of 194 parrot species. This
+included all tool-using species in our video dataset, with the exception of
+three species: \emph{Diopsittaca nobilis}, \emph{Psittacara erythrogenys}, and \emph{Coracopsis
+vasa}. For the latter, we used values for the closely related \emph{Coracopsis
+nigra}. The other two species were excluded from the final dataset.
+
+For modelling purposes, we coded research effort in both the scientific
+literature and the crowdsourced videos. For the scientific literature, we
+operationalised research effort as the number of papers published for each
+species' Latin name up to and including the first paper containing tool use for
+that species. If no tool use had been identified in the scientific literature
+for a species, then we coded the total number of papers published to date. We
+used the scientific database Scopus for coding the number of published papers.
+For the crowdsourced videos, we coded research effort as the number of search
+hits for each species on YouTube. If tool use had been identified on YouTube, we
+estimated the number of search hits when the first video of tool use was
+published on YouTube, assuming linear growth of search hits since the inception
+of YouTube. If tool use had not been identified, we used the current number of
+search hits.
+
+For phylogenetic data, we used the phylogenetic tool at www.birdtree.org
+(\emph{53}) to compile 1000 posterior draws of phylogenetic trees for 174 of the
+194 parrot species for which both EQ and genomic data exist. A single maximum
+clade credibility tree was generated from these posterior draws for
+visualisation purposes. In our analyses, we iterated over posterior draws of the
+phylogeny to account for phylogenetic uncertainty.
 
@@
 
-We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{78} to calculate phylogenetic signal, for both the pre-survey and post-survey tool use data.
-We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
+We used the \emph{fitDiscrete} function in the \emph{ape} R package (\emph{79}) to
+calculate phylogenetic signal, for both the pre-survey and post-survey tool use
+data. We iterated the model over 100 posterior parrot phylogenies to incorporate
+phylogenetic uncertainty.
 
@@
 
-To infer unobserved probabilities of tool use across parrots, we proposed a causal model of observed tool use (Figure \ref{fig:plotDAG}).
-We assumed that observed tool use in the scientific literature and in the crowdsourced videos is caused by both the unobserved presence or absence of tool use and research effort, proxied by the number of papers published on a species and the number of videos published on a species.
-Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected.
-In addition, based on theory, we also assumed that unobserved tool use is caused by feeding strategy and relative brain size\textsuperscript{10--13,15--17}.
-Finally, we assumed that shared phylogenetic history causes unobserved confounding and non-independence in unobserved tool use, feeding strategy, and relative brain size across the parrot phylogeny.
+To infer unobserved probabilities of tool use across parrots, we proposed a
+causal model of observed tool use (Figure \ref{fig:plotDAG}). We assumed that
+observed tool use in the scientific literature and in the crowdsourced videos is
+caused by both the unobserved presence or absence of tool use and research
+effort, proxied by the number of papers published on a species and the number of
+videos published on a species. Tool users are more likely to be observed if they
+are well studied, but understudied tool users may go undetected. In addition,
+based on theory, we also assumed that unobserved tool use is caused by feeding
+strategy and relative brain size (\emph{11}--\emph{14}, \emph{16}--\emph{18}). Finally, we
+assumed that shared phylogenetic history causes unobserved confounding and
+non-independence in unobserved tool use, feeding strategy, and relative brain
+size across the parrot phylogeny.
 
@@
 
-Given our proposed causal model, we constructed a statistical model to impute unobserved probabilities of tool use and test existing theories of the evolution of tool use in parrots.
-To understand the model, suppose that we have the following observed variables for parrot species \(i\).
-For the scientific literature, we declare \(\text{N}_{\text{Lit},i}\) as the number of papers published before and up to tool use identification for species \(i\) (or, if tool use has not been identified, the total number of papers published for species \(i\)) and \(\text{T}_{\text{Lit},i}\) as a binary variable stating whether (1) or not (0) tool use has yet been observed in the scientific literature for species \(i\).
-For the crowdsourced videos, we declare \(\text{N}_{\text{Vid},i}\) as the number of videos published before and up to tool use identification for species \(i\) (or, if tool use has not been identified, the total number of videos published for species \(i\)) and \(\text{T}_{\text{Vid},i}\) as a binary variable stating whether (1) or not (0) tool use has yet been observed in the crowdsourced videos for species \(i\).
-Additionally, \(\text{F}_i\) and \(\text{EQ}_i\) are feeding strategy and encephalisation quotient values for species \(i\) and we have a phylogenetic distance matrix \(D\) that describes the patristic distances between all parrot species.
-
-We assume that species \(i\) is a non-tool-user (i.e.~``cured'') with some probability \(p_i\).
-We also assume that tool use is identified in the scientific literature and the crowdsourced videos at constant rates \(\lambda_{\text{Lit}}\) and \(\lambda_{\text{Vid}}\) following exponential survival functions.
-Given these assumptions, we can then describe the different ways in which variables \(\text{N}_\text{Lit}\) and \(\text{N}_\text{Vid}\) can be distributed.
-Focusing on the scientific literature, if tool use has been observed (\(\text{T}_{\text{Lit},i} = 1\)), then the likelihood for \(\text{N}_{\text{Lit},i}\) is:
+Given our proposed causal model, we constructed a statistical model to impute
+unobserved probabilities of tool use and test existing theories of the evolution
+of tool use in parrots. To understand the model, suppose that we have the
+following observed variables for parrot species \(i\). For the scientific
+literature, we declare \(\text{N}_{\text{Lit},i}\) as the number of papers
+published before and up to tool use identification for species \(i\) (or, if tool
+use has not been identified, the total number of papers published for species
+\(i\)) and \(\text{T}_{\text{Lit},i}\) as a binary variable stating whether (1) or
+not (0) tool use has yet been observed in the scientific literature for species
+\(i\). For the crowdsourced videos, we declare \(\text{N}_{\text{Vid},i}\) as the
+number of videos published before and up to tool use identification for species
+\(i\) (or, if tool use has not been identified, the total number of videos
+published for species \(i\)) and \(\text{T}_{\text{Vid},i}\) as a binary variable
+stating whether (1) or not (0) tool use has yet been observed in the
+crowdsourced videos for species \(i\). Additionally, \(\text{F}_i\) and
+\(\text{EQ}_i\) are feeding strategy and encephalisation quotient values for
+species \(i\) and we have a phylogenetic distance matrix \(D\) that describes the
+patristic distances between all parrot species.
+
+We assume that species \(i\) is a non-tool-user with some
+probability \(p_i\). We also assume that tool use is identified in the scientific
+literature and the crowdsourced videos at constant rates \(\lambda_{\text{Lit}}\)
+and \(\lambda_{\text{Vid}}\) following exponential survival functions. Given these
+assumptions, we can then describe the different ways in which variables
+\(\text{N}_\text{Lit}\) and \(\text{N}_\text{Vid}\) can be distributed. Focusing on
+the scientific literature, if tool use has been observed
+(\(\text{T}_{\text{Lit},i} = 1\)), then the likelihood for
+\(\text{N}_{\text{Lit},i}\) is:
 
@@
 
-On the other hand, if tool use has not yet been observed (\(\text{T}_{\text{Lit},i} = 0\)), there are two ways that the outcome variable could have been realised.
-First, the species could be a non-tool-user with probability \(p_i\).
-Second, the species could be a tool-user with probability (\(1 - p_i\)) that has been censored and has not had its tool use measured yet.
+On the other hand, if tool use has not yet been observed
+(\(\text{T}_{\text{Lit},i} = 0\)), there are two ways that the outcome variable
+could have been realised. First, the species could be a non-tool-user with
+probability \(p_i\). Second, the species could be a tool-user with probability
+(\(1 - p_i\)) that has been censored and has not had its tool use measured yet.
 Together, then, the likelihood for \(\text{N}_{\text{Lit},i}\) is:
@@
 
-The Exponential-CCDF function allows for the censored nature of the data. The same data generating process is assumed to underlie the crowdsourced videos.
-
-We define the mixture likelihood \(\text{SurvivalCure}\) as the distribution above, with parameters \(p\) (the probability of being a ``cured'' non-tool-user) and \(\lambda\) (the rate of the exponential distribution).
-We use an Ornstein-Uhlenbeck Gaussian process\textsuperscript{79} to model phylogenetic covariance.
-Below, we specify the full model with priors:
+The Exponential-CCDF function allows for the censored nature of the data. The
+same data generating process is assumed to underlie the crowdsourced videos.
+
+We define the mixture likelihood \(\text{SurvivalCure}\) as the distribution
+above, with parameters \(p\) (the probability of being a non-tool-user)
+and \(\lambda\) (the rate of the exponential distribution). We use an
+Ornstein-Uhlenbeck Gaussian process (\emph{80}) to model phylogenetic
+covariance. Below, we specify the full model with priors:
 
@@
 
-The priors for this model produce reasonable prior predictions of the probabilities of tool use for each parrot species (Supplementary Figure \ref{fig:plotSurvCure7}), but a sensitivity analysis revealed that the ranking and posterior probabilities reported in the main text were robust to modifying these priors (Supplementary Figure \ref{fig:plotSurvCure8}).
-We estimated the posterior distribution of this model using Hamiltonian Monte Carlo as implemented in Stan version 2.26.1\textsuperscript{80}.
-We ran the model for 4000 samples, with 2000 warmup samples, and iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
-R-hat values and effective sample sizes suggested that the model converged normally.
-Trace plots are reported in Supplementary Figure \ref{fig:plotTrace}.
-We report equal-tailed credible intervals to describe the posterior distribution of this model in the main text.
-
-To validate our method, we fitted the model to 100 simulated datasets with known parameters.
-The model was able to successfully recover those parameters (Supplementary Figure \ref{fig:plotSurvCureSim}).
-We also ran a leave-one-species-out exercise to ensure that we could accurately predict known tool users.
-We repeated this approach for each known tool user by setting observed tool use to zero.
-Cross-validation results are reported in the main text.
+The priors for this model produce reasonable prior predictions of the
+probabilities of tool use for each parrot species (fig.
+\ref{fig:plotSurvCure7}), but a sensitivity analysis revealed that the ranking
+and posterior probabilities reported in the main text were robust to modifying
+these priors (fig.~\ref{fig:plotSurvCure8}). We estimated the
+posterior distribution of this model using Hamiltonian Monte Carlo as
+implemented in Stan version 2.26.1 (\emph{81}). We ran the model for 4000
+samples, with 2000 warmup samples, and iterated the model over 100 posterior
+parrot phylogenies to incorporate phylogenetic uncertainty. R-hat values and
+effective sample sizes suggested that the model converged normally. Trace plots
+are reported in fig.~\ref{fig:plotTrace}. We report
+equal-tailed credible intervals to describe the posterior distribution of this
+model in the main text.
+
+To validate our method, we fitted the model to 100 simulated datasets with known
+parameters. The model was able to successfully recover those parameters
+(fig.~\ref{fig:plotSurvCureSim}). We also ran a
+leave-one-species-out exercise to ensure that we could accurately predict known
+tool users. We repeated this approach for each known tool user by setting
+observed tool use to zero. Cross-validation results are reported in the main
+text.
 
@@
 
-To determine whether the identification of novel tool-using species has implications for our understanding of the evolutionary origins of tool use in parrots, we fitted three exploratory ancestral state reconstruction models.
-We used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{81}, iterating the function over 100 posterior parrot phylogenies.
-This function estimates discrete ancestral states by assuming the evolution of a latent continuous variable following an Ornstein-Uhlenbeck process.
-We fitted this model to three different outcome variables: (\emph{i}) presence vs.~absence of tool use in scientific literature only, (\emph{ii}) presence vs.~absence of tool use in literature and/or videos, and (\emph{iii}) the median predicted probabilities of tool use from the phylogenetic survival cure model.
+To determine whether the identification of novel tool-using species has
+implications for our understanding of the evolutionary origins of tool use in
+parrots, we fitted three exploratory ancestral state reconstruction models. We
+used the \emph{ancThresh} function from the \emph{phytools} R package (\emph{82}),
+iterating the function over 100 posterior parrot phylogenies. This function
+estimates discrete ancestral states by assuming the evolution of a latent
+continuous variable following an Ornstein-Uhlenbeck process. We fitted this
+model to three different outcome variables: (\emph{i}) presence vs.~absence of tool
+use in scientific literature only, (\emph{ii}) presence vs.~absence of tool use in
+literature and/or videos, and (\emph{iii}) the median predicted probabilities of tool
+use from the phylogenetic survival cure model.
 
@@
 
-All analyses were conducted in R v4.2.1.\textsuperscript{82}.
-Visualisations were produced using the \emph{ggplot2}\textsuperscript{83} and \emph{cowplot}\textsuperscript{84} packages.
-The manuscript was reproducibly generated using the \emph{targets}\textsuperscript{85} and \emph{papaja}\textsuperscript{86} packages.
-Code to reproduce all analyses and figures can be found here: \url{https://github.com/ScottClaessens/phyloParrot}
+All analyses were conducted in R v4.2.1. (\emph{83}). Visualisations were
+produced using the \emph{ggplot2} (\emph{84}) and \emph{cowplot} (\emph{85}) packages.
+The manuscript was reproducibly generated using the \emph{targets} (\emph{86}) and
+\emph{papaja} (\emph{87}) packages. Code to reproduce all analyses and figures can be
+found here: \url{https://github.com/ScottClaessens/phyloParrot}
 
@@
 
-This project was made possible through the support of a grant from the Templeton World Charity Foundation (A.H.T., X.J.N.) and a Prime Minister's McDiarmid Emerging Scientist Prize (A.H.T.).
-The authors would like to thank Daniel Sol for providing feedback on a previous version of the manuscript.
+This project was made possible through the support of a grant from the Templeton
+World Charity Foundation (A.H.T., X.J.N.). The authors would like to thank
+Daniel Sol for providing feedback on a previous version of the manuscript.
 
@@
 
-All authors contributed to the conceptualisation of the paper.
-A.P.M.B., X.J.N., and A.H.T.
-developed the video search methodology.
-S.C., D.W., and Q.A.D.
-developed the statistical models and analysed the data.
-All the authors wrote the manuscript and approved the final version for submission.
+All authors contributed to the conceptualisation of the paper. A.P.M.B., X.J.N.,
+and A.H.T. developed the video search methodology. S.C., D.W., and Q.A.D.
+developed the statistical models and analysed the data. All the authors wrote
+the manuscript and approved the final version for submission.
 
@@
 
-All data used in this study are publicly available on GitHub: \url{https://github.com/ScottClaessens/phyloParrot}
+All data used in this study are publicly available on GitHub:
+\url{https://github.com/ScottClaessens/phyloParrot}
 
@@
 
-All code to reproduce the analyses in this study are publicly available on GitHub: \url{https://github.com/ScottClaessens/phyloParrot}
+All code to reproduce the analyses in this study are publicly available on
+GitHub: \url{https://github.com/ScottClaessens/phyloParrot}
 
@@
 \CSLLeftMargin{1. }%
-\CSLRightInline{MacLean, E.
+\CSLRightInline{E.
 L.
-\emph{et al.} \href{https://doi.org/10.1007/s10071-011-0448-8}{How does cognition evolve?
+MacLean, L.
+J.
+Matthews, B.
+A.
+Hare, C.
+L.
+Nunn, R.
+C.
+Anderson, F.
+Aureli, E.
+M.
+Brannon, J.
+Call, C.
+M.
+Drea, N.
+J.
+Emery, others, \href{https://doi.org/10.1007/s10071-011-0448-8}{How does cognition evolve?
 Phylogenetic comparative psychology}.
@@
 \CSLLeftMargin{2. }%
-\CSLRightInline{Lefebvre, L. \href{https://doi.org/10.1098/rsbl.2010.0556}{Taxonomic counts of cognition in the wild}. \emph{Biology Letters} \textbf{7}, 631--633 (2011).}
+\CSLRightInline{L. Lefebvre, \href{https://doi.org/10.1098/rsbl.2010.0556}{Taxonomic counts of cognition in the wild}. \emph{Biology Letters} \textbf{7}, 631--633 (2011).}
 
@@
 \CSLLeftMargin{3. }%
-\CSLRightInline{Logan, C.
+\CSLRightInline{C.
 J.
-\emph{et al.} \href{https://doi.org/10.3819/CCBR.2018.130008}{Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization}.
+Logan, S.
+Avin, N.
+Boogert, A.
+Buskell, F.
+R.
+Cross, A.
+Currie, S.
+Jelbert, D.
+Lukas, R.
+Mares, A.
+F.
+Navarrete, S.
+Shigeno, S.
+H.
+Montgomery, \href{https://doi.org/10.3819/CCBR.2018.130008}{Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization}.
 \emph{Comparative Cognition \& Behavior Reviews} \textbf{13}, 55--89 (2018).}
@@
 \CSLLeftMargin{4. }%
-\CSLRightInline{Healy, S.
+\CSLRightInline{S.
 D.
-\& Rowe, C.
-\href{https://doi.org/10.1098/rspb.2006.3748}{A critique of comparative studies of brain size}.
+Healy, C.
+Rowe, \href{https://doi.org/10.1098/rspb.2006.3748}{A critique of comparative studies of brain size}.
 \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{274}, 453--464 (2007).}
@@
 \CSLLeftMargin{5. }%
-\CSLRightInline{Powell, L.
-E., Isler, K.
-\& Barton, R.
+\CSLRightInline{L.
+E.
+Powell, K.
+Isler, R.
 A.
-\href{https://doi.org/10.1098/rspb.2017.1765}{Re-evaluating the link between brain size and behavioural ecology in primates}.
+Barton, \href{https://doi.org/10.1098/rspb.2017.1765}{Re-evaluating the link between brain size and behavioural ecology in primates}.
 \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{284}, 20171765 (2017).}
@@
 \CSLLeftMargin{6. }%
-\CSLRightInline{Goodall, J. Tool-using and aimed throwing in a community of free-living chimpanzees. \emph{Nature} \textbf{201}, 1264--1266 (1964).}
+\CSLRightInline{J. Goodall, Tool-using and aimed throwing in a community of free-living chimpanzees. \emph{Nature} \textbf{201}, 1264--1266 (1964).}
 
@@
 \CSLLeftMargin{7. }%
-\CSLRightInline{Hunt, G. R. \href{https://doi.org/10.1038/379249a0}{Manufacture and use of hook-tools by {N}ew {C}aledonian crows}. \emph{Nature} \textbf{379}, 249--251 (1996).}
+\CSLRightInline{G. R. Hunt, \href{https://doi.org/10.1038/379249a0}{Manufacture and use of hook-tools by {N}ew {C}aledonian crows}. \emph{Nature} \textbf{379}, 249--251 (1996).}
 
@@
 \CSLLeftMargin{8. }%
-\CSLRightInline{Smolker, R., Richards, A., Connor, R., Mann, J.
-\& Berggren, P.
-\href{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}{Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?} \emph{Ethology} \textbf{103}, 454--465 (1997).}
+\CSLRightInline{R.
+Smolker, A.
+Richards, R.
+Connor, J.
+Mann, P.
+Berggren, \href{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}{Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?} \emph{Ethology} \textbf{103}, 454--465 (1997).}
 
@@
 \CSLLeftMargin{9. }%
-\CSLRightInline{Finn, J.
-K., Tregenza, T.
-\& Norman, M.
+\CSLRightInline{J.
+K.
+Finn, T.
+Tregenza, M.
 D.
-\href{https://doi.org/10.1016/j.cub.2009.10.052}{Defensive tool use in a coconut-carrying octopus}.
+Norman, \href{https://doi.org/10.1016/j.cub.2009.10.052}{Defensive tool use in a coconut-carrying octopus}.
 \emph{Current Biology} \textbf{19}, R1069--R1070 (2009).}
 
+\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{R.
+W.
+Shumaker, K.
+R.
+Walkup, B.
+B.
+Beck, G.
+M.
+Burghardt, \emph{\href{https://doi.org/10.1353/book.98237}{Animal Tool Behavior: The Use and Manufacture of Tools by Animals}} (Johns Hopkins University Press, Baltimore, MD).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2002}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Lefebvre, L., Nicolakakis, N. \& Boire, D. \href{https://doi.org/10.1163/156853902320387918}{Tools and brains in birds}. \emph{Behaviour} \textbf{139}, 939--973 (2002).}
+\CSLLeftMargin{11. }%
+\CSLRightInline{L. Lefebvre, N. Nicolakakis, D. Boire, \href{https://doi.org/10.1163/156853902320387918}{Tools and brains in birds}. \emph{Behaviour} \textbf{139}, 939--973 (2002).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Lefebvre1997}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E.
-\& Finkelstein, A.
-\href{https://doi.org/10.1006/anbe.1996.0330}{Feeding innovations and forebrain size in birds}.
+\CSLLeftMargin{12. }%
+\CSLRightInline{L.
+Lefebvre, P.
+Whittle, E.
+Lascaris, A.
+Finkelstein, \href{https://doi.org/10.1006/anbe.1996.0330}{Feeding innovations and forebrain size in birds}.
 \emph{Animal Behaviour} \textbf{53}, 549--560 (1997).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2004}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Lefebvre, L., Reader, S.
-M.
-\& Sol, D.
-\href{https://doi.org/10.1159/000076784}{Brains, innovations and evolution in birds and primates}.
+\CSLLeftMargin{13. }%
+\CSLRightInline{L.
+Lefebvre, S.
+M.
+Reader, D.
+Sol, \href{https://doi.org/10.1159/000076784}{Brains, innovations and evolution in birds and primates}.
 \emph{Brain, Behavior and Evolution} \textbf{63}, 233--246 (2004).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sol2005}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Sol, D., Duncan, R.
-P., Blackburn, T.
-M., Cassey, P.
-\& Lefebvre, L.
-\href{https://doi.org/10.1073/pnas.0408145102}{Big brains, enhanced cognition, and response of birds to novel environments}.
+\CSLLeftMargin{14. }%
+\CSLRightInline{D.
+Sol, R.
+P.
+Duncan, T.
+M.
+Blackburn, P.
+Cassey, L.
+Lefebvre, \href{https://doi.org/10.1073/pnas.0408145102}{Big brains, enhanced cognition, and response of birds to novel environments}.
 \emph{Proceedings of the National Academy of Sciences} \textbf{102}, 5460--5465 (2005).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sol2009}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Sol, D.
-\href{https://doi.org/10.1098/rsbl.2008.0621}{Revisiting the cognitive buffer hypothesis for the evolution of large brains}.
+\CSLLeftMargin{15. }%
+\CSLRightInline{D.
+Sol, \href{https://doi.org/10.1098/rsbl.2008.0621}{Revisiting the cognitive buffer hypothesis for the evolution of large brains}.
 \emph{Biology Letters} \textbf{5}, 130--133 (2009).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ducatez2015}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Ducatez, S., Clavel, J.
-\& Lefebvre, L.
-\href{https://doi.org/10.1111/1365-2656.12255}{Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?} \emph{Journal of Animal Ecology} \textbf{84}, 79--89 (2015).}
+\CSLLeftMargin{16. }%
+\CSLRightInline{S.
+Ducatez, J.
+Clavel, L.
+Lefebvre, \href{https://doi.org/10.1111/1365-2656.12255}{Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?} \emph{Journal of Animal Ecology} \textbf{84}, 79--89 (2015).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Overington2011}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Overington, S.
-E., Griffin, A.
-S., Sol, D.
-\& Lefebvre, L.
-\href{https://doi.org/10.1093/beheco/arr130}{Are innovative species ecological generalists?
+\CSLLeftMargin{17. }%
+\CSLRightInline{S.
+E.
+Overington, A.
+S.
+Griffin, D.
+Sol, L.
+Lefebvre, \href{https://doi.org/10.1093/beheco/arr130}{Are innovative species ecological generalists?
 A test in {N}orth {A}merican birds}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2020}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.
-M.
-\& Fichtel, C.
-Linking ecology and cognition: Does ecological specialisation predict cognitive test performance?
+\CSLLeftMargin{18. }%
+\CSLRightInline{J.
+Henke-von der Malsburg, P.
+M.
+Kappeler, C.
+Fichtel, Linking ecology and cognition: Does ecological specialisation predict cognitive test performance?
 \emph{Behavioral Ecology and Sociobiology} \textbf{74}, 154 (2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MettkeHofmann2014}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{Mettke-Hofmann, C.
-\href{https://doi.org/10.1002/wcs.1289}{Cognitive ecology: Ecological factors, life-styles, and cognition}.
+\CSLLeftMargin{19. }%
+\CSLRightInline{C.
+Mettke-Hofmann, \href{https://doi.org/10.1002/wcs.1289}{Cognitive ecology: Ecological factors, life-styles, and cognition}.
 \emph{WIREs Cognitive Science} \textbf{5}, 345--360 (2014).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ducatez2014}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Ducatez, S. \& Lefebvre, L. \href{https://doi.org/10.1371/journal.pone.0089955}{Patterns of research effort in birds}. \emph{PLOS ONE} \textbf{9}, e89955 (2014).}
+\CSLLeftMargin{20. }%
+\CSLRightInline{S. Ducatez, L. Lefebvre, \href{https://doi.org/10.1371/journal.pone.0089955}{Patterns of research effort in birds}. \emph{PLOS ONE} \textbf{9}, e89955 (2014).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Nelson2013}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Nelson, X.
+\CSLLeftMargin{21. }%
+\CSLRightInline{X.
 J.
-\& Fijn, N.
-\href{https://doi.org/10.1016/j.anbehav.2012.12.009}{The use of visual media as a tool for investigating animal behaviour}.
+Nelson, N.
+Fijn, \href{https://doi.org/10.1016/j.anbehav.2012.12.009}{The use of visual media as a tool for investigating animal behaviour}.
 \emph{Animal Behaviour} \textbf{85}, 525--536 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Dickinson2010}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Dickinson, J.
-L., Zuckerberg, B.
-\& Bonter, D.
+\CSLLeftMargin{22. }%
+\CSLRightInline{J.
+L.
+Dickinson, B.
+Zuckerberg, D.
 N.
-\href{https://doi.org/10.1146/annurev-ecolsys-102209-144636}{Citizen science as an ecological research tool: Challenges and benefits}.
+Bonter, \href{https://doi.org/10.1146/annurev-ecolsys-102209-144636}{Citizen science as an ecological research tool: Challenges and benefits}.
 \emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{41}, 149--172 (2010).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{Krueger, K., Esch, L.
-\& Byrne, R.
-\href{https://doi.org/10.1371/journal.pone.0218954}{Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms}.
+\CSLLeftMargin{23. }%
+\CSLRightInline{K.
+Krueger, L.
+Esch, R.
+Byrne, \href{https://doi.org/10.1371/journal.pone.0218954}{Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms}.
 \emph{PLOS ONE} \textbf{14}, 1--20 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Klump2021}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Klump, B.
+\CSLLeftMargin{24. }%
+\CSLRightInline{B.
 C.
-\emph{et al.} \href{https://doi.org/10.1126/science.abe7808}{Innovation and geographic spread of a complex foraging culture in an urban parrot}.
+Klump, J.
+M.
+Martin, S.
+Wild, J.
+K.
+Hörsch, R.
+E.
+Major, L.
+M.
+Aplin, \href{https://doi.org/10.1126/science.abe7808}{Innovation and geographic spread of a complex foraging culture in an urban parrot}.
 \emph{Science} \textbf{373}, 456--460 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Klump2022}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Klump, B.
-C., Major, R.
-E., Farine, D.
-R., Martin, J.
-M.
-\& Aplin, L.
-M.
-Is bin-opening in cockatoos leading to an innovation arms race with humans?
+\CSLLeftMargin{25. }%
+\CSLRightInline{B.
+C.
+Klump, R.
+E.
+Major, D.
+R.
+Farine, J.
+M.
+Martin, L.
+M.
+Aplin, Is bin-opening in cockatoos leading to an innovation arms race with humans?
 \emph{Current Biology} \textbf{32}, R910--R911 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Burgio2019}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Burgio, K.
-R.
-\emph{et al.} \href{https://doi.org/10.1016/j.dib.2019.103882}{Phylogenetic supertree and functional trait database for all extant parrots}.
-\emph{Data in Brief} \textbf{24}, 103882 (2019).}
 
@@
 \CSLLeftMargin{26. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Gajdon, G.
+\CSLRightInline{A.
+M.
+I.
+Auersperg, G.
 K.
-\& Huber, L.
-\href{https://doi.org/10.1098/rsbl.2009.0114}{Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem}.
+Gajdon, L.
+Huber, \href{https://doi.org/10.1098/rsbl.2009.0114}{Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem}.
 \emph{Biology Letters} \textbf{5}, 455--458 (2009).}
@@
 \CSLLeftMargin{27. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Gajdon, G.
+\CSLRightInline{A.
+M.
+I.
+Auersperg, G.
 K.
-\& Huber, L.
-\href{https://doi.org/10.1016/j.anbehav.2010.08.007}{Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task}.
+Gajdon, L.
+Huber, \href{https://doi.org/10.1016/j.anbehav.2010.08.007}{Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task}.
 \emph{Animal Behaviour} \textbf{80}, 783--789 (2010).}
@@
 \CSLLeftMargin{28. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Huber, L.
-\& Gajdon, G.
+\CSLRightInline{A.
+M.
+I.
+Auersperg, L.
+Huber, G.
 K.
-\href{https://doi.org/10.1098/rsbl.2011.0388}{Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis})}.
+Gajdon, \href{https://doi.org/10.1098/rsbl.2011.0388}{Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis})}.
 \emph{Biology Letters} \textbf{7}, 825--828 (2011).}
@@
 \CSLLeftMargin{29. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Bayern, A.
+\CSLRightInline{A.
+M.
+I.
+Auersperg, A.
 M.
 P.
-von, Gajdon, G.
-K., Huber, L.
-\& Kacelnik, A.
-\href{https://doi.org/10.1371/journal.pone.0020231}{Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm}.
+von Bayern, G.
+K.
+Gajdon, L.
+Huber, A.
+Kacelnik, \href{https://doi.org/10.1371/journal.pone.0020231}{Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm}.
 \emph{PLOS ONE} \textbf{6}, 1--8 (2011).}
@@
 \CSLLeftMargin{30. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Szabo, B., von Bayern, A.
+\CSLRightInline{A.
+M.
+I.
+Auersperg, B.
+Szabo, A.
 M.
 P.
-\& Kacelnik, A.
-\href{https://doi.org/10.1016/j.cub.2012.09.002}{Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo}.
+von Bayern, A.
+Kacelnik, \href{https://doi.org/10.1016/j.cub.2012.09.002}{Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo}.
 \emph{Current Biology} \textbf{22}, R903--R904 (2012).}
@@
 \CSLLeftMargin{31. }%
-\CSLRightInline{Bastos, A.
-P., Horváth, K., Webb, J.
-L., Wood, P.
-M.
-\& Taylor, A.
+\CSLRightInline{A.
+P.
+Bastos, K.
+Horváth, J.
+L.
+Webb, P.
+M.
+Wood, A.
 H.
-Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
+Taylor, Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
 \emph{Scientific Reports} \textbf{11}, 18035 (2021).}
@@
 \CSLLeftMargin{32. }%
-\CSLRightInline{Bentley-Condit, V.
-\& Smith, E.
+\CSLRightInline{V.
+Bentley-Condit, E.
 O.
-\href{https://doi.org/10.1163/000579509X12512865686555}{Animal tool use: Current definitions and an updated comprehensive catalog}.
+Smith, \href{https://doi.org/10.1163/000579509X12512865686555}{Animal tool use: Current definitions and an updated comprehensive catalog}.
 \emph{Behaviour} \textbf{147}, 185--32A (2010).}
@@
 \CSLLeftMargin{33. }%
-\CSLRightInline{Borsari, A.
-\& Ottoni, E.
+\CSLRightInline{A.
+Borsari, E.
 B.
-\href{https://doi.org/10.1007/s10071-004-0221-3}{Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus})}.
+Ottoni, \href{https://doi.org/10.1007/s10071-004-0221-3}{Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus})}.
 \emph{Animal Cognition} \textbf{8}, 48--52 (2005).}
@@
 \CSLLeftMargin{34. }%
-\CSLRightInline{Goodman, M., Hayward, T.
-\& Hunt, G.
+\CSLRightInline{M.
+Goodman, T.
+Hayward, G.
 R.
-\href{https://doi.org/10.1038/s41598-018-32363-9}{Habitual tool use innovated by free-living {N}ew {Z}ealand kea}.
+Hunt, \href{https://doi.org/10.1038/s41598-018-32363-9}{Habitual tool use innovated by free-living {N}ew {Z}ealand kea}.
 \emph{Scientific Reports} \textbf{8}, 13935 (2018).}
@@
 \CSLLeftMargin{35. }%
-\CSLRightInline{Heinsohn, R., Zdenek, C.
-N., Cunningham, R.
-B., Endler, J.
+\CSLRightInline{R.
+Heinsohn, C.
+N.
+Zdenek, R.
+B.
+Cunningham, J.
 A.
-\& Langmore, N.
+Endler, N.
 E.
-\href{https://doi.org/10.1126/sciadv.1602399}{Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music}.
+Langmore, \href{https://doi.org/10.1126/sciadv.1602399}{Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music}.
 \emph{Science Advances} \textbf{3}, e1602399 (2017).}
@@
 \CSLLeftMargin{36. }%
-\CSLRightInline{Janzen, M. J., Janzen, D. H. \& Pond, C. M. Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). \emph{Biotropica} \textbf{8}, 70 (1976).}
+\CSLRightInline{M. J. Janzen, D. H. Janzen, C. M. Pond, Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). \emph{Biotropica} \textbf{8}, 70 (1976).}
 
@@
 \CSLLeftMargin{37. }%
-\CSLRightInline{Lambert, M.
-L., Seed, A.
-M.
-\& Slocombe, K.
+\CSLRightInline{M.
+L.
+Lambert, A.
+M.
+Seed, K.
 E.
-\href{https://doi.org/10.1098/rsbl.2015.0861}{A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa})}.
+Slocombe, \href{https://doi.org/10.1098/rsbl.2015.0861}{A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa})}.
 \emph{Biology Letters} \textbf{11}, 20150861 (2015).}
@@
 \CSLLeftMargin{38. }%
-\CSLRightInline{O'Hara, M.
-\emph{et al.} \href{https://doi.org/10.1016/j.cub.2021.08.009}{Wild {G}offin's cockatoos flexibly manufacture and use tool sets}.
+\CSLRightInline{M.
+O'Hara, B.
+Mioduszewska, R.
+Mundry, Yohanna, T.
+Haryoko, R.
+Rachmatika, D.
+M.
+Prawiradilaga, L.
+Huber, A.
+M.
+I.
+Auersperg, \href{https://doi.org/10.1016/j.cub.2021.08.009}{Wild {G}offin's cockatoos flexibly manufacture and use tool sets}.
 \emph{Current Biology} \textbf{31}, 4512--4520.e6 (2021).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kleinberger2023}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
 \CSLLeftMargin{39. }%
-\CSLRightInline{Kleinberger, R., Cunha, J., Vemuri, M.
-M.
-\& Hirskyj-Douglas, I.
-Birds of a feather video-flock together: Design and evaluation of an agency-based parrot-to-parrot video-calling system for interspecies ethical enrichment.
-in \emph{Proceedings of the 2023 CHI conference on human factors in computing systems} (Association for Computing Machinery, 2023).
-doi:\href{https://doi.org/10.1145/3544548.3581166}{10.1145/3544548.3581166}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
+\CSLRightInline{P.
+Anderson, \href{https://doi.org/10.1163/156853003322796109}{A bird in the house: An anthropological perspective on companion parrots}.
+\emph{Society \& Animals} \textbf{11}, 393--418 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
 \CSLLeftMargin{40. }%
-\CSLRightInline{Anderson, P.
-\href{https://doi.org/10.1163/156853003322796109}{A bird in the house: An anthropological perspective on companion parrots}.
-\emph{Society \& Animals} \textbf{11}, 393--418 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
+\CSLRightInline{M.
+Carrete, J.
+Tella, \href{https://doi.org/10.1890/070075}{Wild-bird trade and exotic invasions: A new link of conservation concern?} \emph{Frontiers in Ecology and the Environment} \textbf{6}, 207--211 (2008).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
 \CSLLeftMargin{41. }%
-\CSLRightInline{Carrete, M.
-\& Tella, J.
-\href{https://doi.org/10.1890/070075}{Wild-bird trade and exotic invasions: A new link of conservation concern?} \emph{Frontiers in Ecology and the Environment} \textbf{6}, 207--211 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
+\CSLRightInline{C.
+Drews, \href{https://doi.org/10.1163/156853001753639233}{Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers}.
+\emph{Society \& Animals} \textbf{9}, 107--126 (2001).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
 \CSLLeftMargin{42. }%
-\CSLRightInline{Drews, C.
-\href{https://doi.org/10.1163/156853001753639233}{Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers}.
-\emph{Society \& Animals} \textbf{9}, 107--126 (2001).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
+\CSLRightInline{D.
+Kelly, E.
+McCarthy, K.
+Menzel, M.
+Engebretson, How many captive birds: Are population studies giving us a clear picture?
+(2014).
+\url{https://www.avianwelfare.org/issues/overview.htm}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
 \CSLLeftMargin{43. }%
-\CSLRightInline{Kelly, D., McCarthy, E., Menzel, K.
-\& Engebretson, M.
-\href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?} (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
+\CSLRightInline{L. Li, Z. Jiang, \href{https://doi.org/10.1371/journal.pone.0085012}{International trade of {CITES} listed bird species in {C}hina}. \emph{PLOS ONE} \textbf{9}, 1--8 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
 \CSLLeftMargin{44. }%
-\CSLRightInline{Li, L. \& Jiang, Z. \href{https://doi.org/10.1371/journal.pone.0085012}{International trade of {CITES} listed bird species in {C}hina}. \emph{PLOS ONE} \textbf{9}, 1--8 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
+\CSLRightInline{S.
+Su, P.
+Cassey, M.
+Vall-llosera, T.
+M.
+Blackburn, \href{https://doi.org/10.1371/journal.pone.0127482}{Going cheap: Determinants of bird price in the {T}aiwanese pet market}.
+\emph{PLOS ONE} \textbf{10}, 1--17 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
 \CSLLeftMargin{45. }%
-\CSLRightInline{Su, S., Cassey, P., Vall-llosera, M.
-\& Blackburn, T.
-M.
-\href{https://doi.org/10.1371/journal.pone.0127482}{Going cheap: Determinants of bird price in the {T}aiwanese pet market}.
-\emph{PLOS ONE} \textbf{10}, 1--17 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
+\CSLRightInline{A.
+M.
+Young, E.
+A.
+Hobson, L.
+B.
+Lackey, T.
+F.
+Wright, \href{https://doi.org/10.1111/j.1469-1795.2011.00477.x}{Survival on the ark: Life-history trends in captive parrots}.
+\emph{Animal Conservation} \textbf{15}, 28--43 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
 \CSLLeftMargin{46. }%
-\CSLRightInline{Young, A.
-M., Hobson, E.
-A., Lackey, L.
+\CSLRightInline{K.
+Flammer, D.
+Whitt-Smith, M.
+Papich, \href{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}{Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection}.
+\emph{Journal of Avian Medicine and Surgery} \textbf{15}, 276--282 (2001).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{A.
+N.
+Iwaniuk, K.
+M.
+Dean, J.
+E.
+Nelson, Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
+\emph{Brain, Behavior and Evolution} \textbf{65}, 40--59 (2005).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
+\CSLLeftMargin{48. }%
+\CSLRightInline{P.
+Mazengenya, A.
+Bhagwandin, P.
+R.
+Manger, A.
+O.
+Ihunwo, \href{https://doi.org/10.3389/fnana.2018.00007}{Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh})}.
+\emph{Frontiers in Neuroanatomy} \textbf{12}, 7 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{S.
+Olkowicz, M.
+Kocourek, R.
+K.
+Lučan, M.
+Porteš, W.
+T.
+Fitch, S.
+Herculano-Houzel, P.
+Němec, \href{https://doi.org/10.1073/pnas.1517131113}{Birds have primate-like numbers of neurons in the forebrain}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{113}, 7255--7260 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{C.
+Schuck-Paim, W.
+J.
+Alonso, E.
 B.
-\& Wright, T.
-F.
-\href{https://doi.org/10.1111/j.1469-1795.2011.00477.x}{Survival on the ark: Life-history trends in captive parrots}.
-\emph{Animal Conservation} \textbf{15}, 28--43 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Flammer, K., Whitt-Smith, D.
-\& Papich, M.
-\href{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}{Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection}.
-\emph{Journal of Avian Medicine and Surgery} \textbf{15}, 276--282 (2001).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Iwaniuk, A.
-N., Dean, K.
-M.
-\& Nelson, J.
-E.
-Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
-\emph{Brain, Behavior and Evolution} \textbf{65}, 40--59 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P.
+Ottoni, \href{https://doi.org/10.1159/000119710}{Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots}.
+\emph{Brain, Behavior and Evolution} \textbf{71}, 200--215 (2008).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
+\CSLLeftMargin{51. }%
+\CSLRightInline{T.
+Silva, A.
+Guzmán, A.
+D.
+Urantówka, P.
+Mackiewicz, \href{https://doi.org/10.7717/peerj.3475}{A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny}.
+\emph{PeerJ} \textbf{5}, e3475 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
+\CSLLeftMargin{52. }%
+\CSLRightInline{H.
+Wilman, J.
+Belmaker, J.
+Simpson, C.
+de la Rosa, M.
+M.
+Rivadeneira, W.
+Jetz, EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals (2016).
+\url{https://doi.org/10.6084/m9.figshare.c.3306933.v1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
+\CSLLeftMargin{53. }%
+\CSLRightInline{W. Jetz, G. H. Thomas, J. B. Joy, K. Hartmann, A. O. Mooers, The global diversity of birds in space and time. \emph{Nature} \textbf{491}, 444--448 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
+\CSLLeftMargin{54. }%
+\CSLRightInline{A. Seed, R. Byrne, \href{https://doi.org/10.1016/j.cub.2010.09.042}{Animal tool-use}. \emph{Current Biology} \textbf{20}, R1032--R1039 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
+\CSLLeftMargin{55. }%
+\CSLRightInline{A. B. Bercovitz, {``Avian sex identification techniques''} in \emph{Companion Bird Medicine}, E. W. Burr, Ed. (Iowa State University Press, Ames, IA, 1987).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
+\CSLLeftMargin{56. }%
+\CSLRightInline{J. D. Hoyo, R. Bierregaard, \emph{Handbook of the Birds of the World} (Lynx Edicions, Barcelona, Spain, 2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
+\CSLLeftMargin{57. }%
+\CSLRightInline{M.
+Amico, I.
+Van Keilegom, \href{https://doi.org/10.1146/annurev-statistics-031017-100101}{Cure models in survival analysis}.
+\emph{Annual Review of Statistics and Its Application} \textbf{5}, 311--342 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
+\CSLLeftMargin{58. }%
+\CSLRightInline{P.
+Schmidt, A.
+D.
+Witte, \href{https://doi.org/10.1016/0304-4076(89)90034-1}{Predicting criminal recidivism using {``split population''} survival time models}.
+\emph{Journal of Econometrics} \textbf{40}, 141--159 (1989).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
+\CSLLeftMargin{59. }%
+\CSLRightInline{A.
 R.
-\& Ihunwo, A.
-O.
-\href{https://doi.org/10.3389/fnana.2018.00007}{Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh})}.
-\emph{Frontiers in Neuroanatomy} \textbf{12}, 7 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Olkowicz, S.
-\emph{et al.} \href{https://doi.org/10.1073/pnas.1517131113}{Birds have primate-like numbers of neurons in the forebrain}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{113}, 7255--7260 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Schuck-Paim, C., Alonso, W.
-J.
-\& Ottoni, E.
-B.
-\href{https://doi.org/10.1159/000119710}{Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots}.
-\emph{Brain, Behavior and Evolution} \textbf{71}, 200--215 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Silva, T., Guzmán, A., Urantówka, A.
-D.
-\& Mackiewicz, P.
-\href{https://doi.org/10.7717/peerj.3475}{A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny}.
-\emph{PeerJ} \textbf{5}, e3475 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Wilman, H.
-\emph{et al.} EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals.
-(2016) doi:\href{https://doi.org/10.6084/m9.figshare.c.3306933.v1}{10.6084/m9.figshare.c.3306933.v1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Jetz, W., Thomas, G. H., Joy, J. B., Hartmann, K. \& Mooers, A. O. The global diversity of birds in space and time. \emph{Nature} \textbf{491}, 444--448 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Shumaker, R.
-W., Walkup, K.
-R., Beck, B.
-B.
-\& Burghardt, G.
-M.
-\emph{Animal tool behavior: The use and manufacture of tools by animals}.
-(Johns Hopkins University Press).
-doi:\href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Seed, A. \& Byrne, R. \href{https://doi.org/10.1016/j.cub.2010.09.042}{Animal tool-use}. \emph{Current Biology} \textbf{20}, R1032--R1039 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Bercovitz, A. B. Avian sex identification techniques. in \emph{Companion bird medicine} (ed. Burr, E. W.) (Iowa State University Press, 1987).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Hoyo, J. D. \& Bierregaard, R. \emph{Handbook of the birds of the world}. (Lynx Edicions, 2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Amico, M.
-\& Van Keilegom, I.
-\href{https://doi.org/10.1146/annurev-statistics-031017-100101}{Cure models in survival analysis}.
-\emph{Annual Review of Statistics and Its Application} \textbf{5}, 311--342 (2018).}
+Wallace, \emph{The {M}alay {A}rchipelago: The Land of the Orang-Utan and the Bird of Paradise; a Narrative of Travel, with the Studies of Man and Nature} (MacMillan; Co., London, UK, 1869).}
 
@@
 \CSLLeftMargin{60. }%
-\CSLRightInline{Goodall, J.
-\href{https://doi.org/10.1016/S0065-3454(08)60157-6}{Tool-using in primates and other vertebrates}.
-in (eds.
-Lehrman, D.
-S., Hinde, R.
+\CSLRightInline{J.
+Goodall, {``Tool-using in primates and other vertebrates''} D.
+S.
+Lehrman, R.
 A.
-\& Shaw, E.) vol.
-3 195--249 (Academic Press, 1971).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
+Hinde, E.
+Shaw, Eds.
+(Academic Press, 1971; \url{https://www.sciencedirect.com/science/article/pii/S0065345408601576})vol.
+3 of \emph{Advances in the study of behavior}, pp.
+195--249.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
 \CSLLeftMargin{61. }%
-\CSLRightInline{Reader, S.
-M.
-\& Laland, K.
-N.
-\href{https://doi.org/10.1073/pnas.062041299}{Social intelligence, innovation, and enhanced brain size in primates}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{99}, 4436--4441 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
+\CSLRightInline{D.
+M.
+Fragaszy, M.
+Mangalam, {``Tooling''} M.
+Naguib, L.
+Barrett, S.
+D.
+Healy, J.
+Podos, L.
+W.
+Simmons, M.
+Zuk, Eds.
+(Academic Press, 2018; \url{https://www.sciencedirect.com/science/article/pii/S0065345418300019})vol.
+50 of \emph{Advances in the study of behavior}, pp.
+177--241.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
 \CSLLeftMargin{62. }%
-\CSLRightInline{Cabrera-Álvarez, M.
-J.
-\& Clayton, N.
-S.
-\href{https://doi.org/10.3389/fpsyg.2020.560669}{Neural processes underlying tool use in humans, macaques, and corvids}.
-\emph{Frontiers in Psychology} \textbf{11}, 560669 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.
-M.
-\& Fichtel, C.
-\href{https://doi.org/10.1098/rspb.2021.1728}{Linking cognition to ecology in wild sympatric mouse lemur species}.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{288}, 20211728 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Sándor, K.
-\& Miklósi, Á.
-\href{https://doi.org/10.3389/fpsyg.2020.555487}{How to report anecdotal observations?
+\CSLRightInline{K.
+Sándor, Á.
+Miklósi, \href{https://doi.org/10.3389/fpsyg.2020.555487}{How to report anecdotal observations?
 A new approach based on a lesson from "puffin tool use"}.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2020}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
+\CSLLeftMargin{63. }%
+\CSLRightInline{S.
+M.
+Reader, K.
+N.
+Laland, \href{https://doi.org/10.1073/pnas.062041299}{Social intelligence, innovation, and enhanced brain size in primates}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{99}, 4436--4441 (2002).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{D.
+Sol, S.
+Olkowicz, F.
+Sayol, M.
+Kocourek, Y.
+Zhang, L.
+Marhounová, C.
+Osadnik, E.
+Corssmit, J.
+Garcia-Porta, T.
+E.
+Martin, others, Neuron numbers link innovativeness with both absolute and relative brain size in birds.
+\emph{Nature Ecology \& Evolution} \textbf{6}, 1381--1389 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
 \CSLLeftMargin{65. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Schwing, R., Mioduszewska, B., O'Hara, M.
-\& Huber, L.
-\href{https://doi.org/10.1073/pnas.2001988117}{Do puffins use tools?} \emph{Proceedings of the National Academy of Sciences} \textbf{117}, 11859--11859 (2020).}
+\CSLRightInline{M.
+J.
+Cabrera-Álvarez, N.
+S.
+Clayton, \href{https://doi.org/10.3389/fpsyg.2020.560669}{Neural processes underlying tool use in humans, macaques, and corvids}.
+\emph{Frontiers in Psychology} \textbf{11}, 560669 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
+\CSLLeftMargin{66. }%
+\CSLRightInline{J.
+Henke-von der Malsburg, P.
+M.
+Kappeler, C.
+Fichtel, \href{https://doi.org/10.1098/rspb.2021.1728}{Linking cognition to ecology in wild sympatric mouse lemur species}.
+\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{288}, 20211728 (2021).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
-\CSLLeftMargin{66. }%
-\CSLRightInline{Debastiani, V.
-J., Bastazini, V.
+\CSLLeftMargin{67. }%
+\CSLRightInline{V.
+J.
+Debastiani, V.
 A.
 G.
-\& Pillar, V.
+Bastazini, V.
 D.
-\href{https://doi.org/10.1016/j.ecoinf.2021.101315}{Using phylogenetic information to impute missing functional trait values in ecological databases}.
+Pillar, \href{https://doi.org/10.1016/j.ecoinf.2021.101315}{Using phylogenetic information to impute missing functional trait values in ecological databases}.
 \emph{Ecological Informatics} \textbf{63}, 101315 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
-\CSLLeftMargin{67. }%
-\CSLRightInline{Hunt, G.
-R., Gray, R.
+\CSLLeftMargin{68. }%
+\CSLRightInline{G.
+R.
+Hunt, R.
 D.
-\& Taylor, A.
+Gray, A.
 H.
-Why is tool use rare in animals?
-in \emph{Tool use in animals: Cognition and ecology} (eds.
-Sanz, C.
-M., Call, J.
-\& Boesch, C.) 89--118 (Cambridge University Press, 2013).
-doi:\href{https://doi.org/10.1017/CBO9780511894800.007}{10.1017/CBO9780511894800.007}.}
+Taylor, {``\href{https://doi.org/10.1017/CBO9780511894800.007}{Why is tool use rare in animals?}''} in \emph{Tool Use in Animals: Cognition and Ecology}, C.
+M.
+Sanz, J.
+Call, C.
+Boesch, Eds.
+(Cambridge University Press, 2013), pp.
+89--118.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
-\CSLLeftMargin{68. }%
-\CSLRightInline{Benichov, J.
-I., Globerson, E.
-\& Tchernichovski, O.
-\href{https://doi.org/10.3389/fnhum.2016.00255}{Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans}.
-\emph{Frontiers in Human Neuroscience} \textbf{10}, (2016).}
+\CSLLeftMargin{69. }%
+\CSLRightInline{J.
+I.
+Benichov, E.
+Globerson, O.
+Tchernichovski, \href{https://doi.org/10.3389/fnhum.2016.00255}{Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans}.
+\emph{Frontiers in Human Neuroscience} \textbf{10} (2016).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{Patel, A.
-D., Iversen, J.
-R., Bregman, M.
+\CSLLeftMargin{70. }%
+\CSLRightInline{A.
+D.
+Patel, J.
 R.
-\& Schulz, I.
-\href{https://doi.org/10.1016/j.cub.2009.03.038}{Experimental evidence for synchronization to a musical beat in a nonhuman animal}.
+Iversen, M.
+R.
+Bregman, I.
+Schulz, \href{https://doi.org/10.1016/j.cub.2009.03.038}{Experimental evidence for synchronization to a musical beat in a nonhuman animal}.
 \emph{Current Biology} \textbf{19}, 827--830 (2009).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
-\CSLLeftMargin{70. }%
-\CSLRightInline{ten Cate, C., Spierings, M., Hubert, J.
-\& Honing, H.
-\href{https://doi.org/10.3389/fpsyg.2016.00730}{Can birds perceive rhythmic patterns?
+\CSLLeftMargin{71. }%
+\CSLRightInline{C.
+ten Cate, M.
+Spierings, J.
+Hubert, H.
+Honing, \href{https://doi.org/10.3389/fpsyg.2016.00730}{Can birds perceive rhythmic patterns?
 A review and experiments on a songbird and a parrot species}.
-\emph{Frontiers in Psychology} \textbf{7}, (2016).}
+\emph{Frontiers in Psychology} \textbf{7} (2016).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{Wilson, M.
-\& Cook, P.
+\CSLLeftMargin{72. }%
+\CSLRightInline{M.
+Wilson, P.
 F.
-\href{https://doi.org/10.3758/s13423-016-1013-x}{Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed}.
+Cook, \href{https://doi.org/10.3758/s13423-016-1013-x}{Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed}.
 \emph{Psychonomic Bulletin \& Review} \textbf{23}, 1647--1659 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
-\CSLLeftMargin{72. }%
-\CSLRightInline{Eckert, J., Winkler, S.
+\CSLLeftMargin{73. }%
+\CSLRightInline{J.
+Eckert, S.
 L.
-\& Cartmill, E.
+Winkler, E.
 A.
-\href{https://doi.org/10.1098/rsbl.2020.0370}{Just kidding: The evolutionary roots of playful teasing}.
+Cartmill, \href{https://doi.org/10.1098/rsbl.2020.0370}{Just kidding: The evolutionary roots of playful teasing}.
 \emph{Biology Letters} \textbf{16}, 20200370 (2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
-\CSLLeftMargin{73. }%
-\CSLRightInline{Bro-Jørgensen, J.
-\& Pangle, W.
-M.
-\href{https://doi.org/10.1086/653078}{Male topi antelopes alarm snort deceptively to retain females for mating}.
+\CSLLeftMargin{74. }%
+\CSLRightInline{J.
+Bro-Jørgensen, W.
+M.
+Pangle, \href{https://doi.org/10.1086/653078}{Male topi antelopes alarm snort deceptively to retain females for mating}.
 \emph{The American Naturalist} \textbf{176}, E33--E39 (2010).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
-\CSLLeftMargin{74. }%
-\CSLRightInline{Byrne, R.
+\CSLLeftMargin{75. }%
+\CSLRightInline{R.
 W.
-\& Whiten, A.
-\href{https://doi.org/10.1017/S0140525X00049955}{Toward the next generation in data quality: A new survey of primate tactical deception}.
+Byrne, A.
+Whiten, \href{https://doi.org/10.1017/S0140525X00049955}{Toward the next generation in data quality: A new survey of primate tactical deception}.
 \emph{Behavioral and Brain Sciences} \textbf{11}, 267--273 (1988).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
-\CSLLeftMargin{75. }%
-\CSLRightInline{Byrne, R.
+\CSLLeftMargin{76. }%
+\CSLRightInline{R.
 W.
-\& Whiten, A.
-Computation and mindreading in primate tactical deception.
-in \emph{Natural theories of mind: Evolution, development and simulation of everyday mindreading} (ed.
-Whiten, A.) 127--141 (Basil Blackwell, 1991).}
+Byrne, A.
+Whiten, {``Computation and mindreading in primate tactical deception''} in \emph{Natural Theories of Mind: Evolution, Development and Simulation of Everyday Mindreading}, A.
+Whiten, Ed.
+(Basil Blackwell, 1991), pp.
+127--141.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
-\CSLLeftMargin{76. }%
-\CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership}. (2016).}
+\CSLLeftMargin{77. }%
+\CSLRightInline{Global GfK survey: Pet ownership (2016). \url{http://www.gfk.com/global-studies/global-studies-pet-ownership}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
-\CSLLeftMargin{77. }%
-\CSLRightInline{Jerison, H. J. \emph{Evolution of the brain and intelligence}. (Academic Press, 1973).}
+\CSLLeftMargin{78. }%
+\CSLRightInline{H. J. Jerison, \emph{Evolution of the Brain and Intelligence} (Academic Press, New York, NY, 1973).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
-\CSLLeftMargin{78. }%
-\CSLRightInline{Paradis, E.
-\& Schliep, K.
-\href{https://doi.org/10.1093/bioinformatics/bty633}{{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}}.
+\CSLLeftMargin{79. }%
+\CSLRightInline{E.
+Paradis, K.
+Schliep, \href{https://doi.org/10.1093/bioinformatics/bty633}{{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}}.
 \emph{Bioinformatics} \textbf{35}, 526--528 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
-\CSLLeftMargin{79. }%
-\CSLRightInline{McElreath, R. \emph{\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition}}. (CRC Press, 2020).}
+\CSLLeftMargin{80. }%
+\CSLRightInline{R.
+McElreath, \emph{Statistical Rethinking: A {Bayesian} Course with Examples in {R} and {Stan}, 2nd Edition} (CRC Press, ed.
+2, 2020; \url{http://xcelab.net/rm/statistical-rethinking/}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
-\CSLLeftMargin{80. }%
-\CSLRightInline{Stan Development Team. \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}. (2020).}
+\CSLLeftMargin{81. }%
+\CSLRightInline{Stan Development Team, {RStan}: The {R} interface to {Stan} (2020). \url{http://mc-stan.org/}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
-\CSLLeftMargin{81. }%
-\CSLRightInline{Revell, L.
+\CSLLeftMargin{82. }%
+\CSLRightInline{L.
 J.
-\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{{phytools}: An {R} package for phylogenetic comparative biology (and other things)}.
+Revell, \href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{{phytools}: An {R} package for phylogenetic comparative biology (and other things)}.
 \emph{Methods in Ecology and Evolution} \textbf{3}, 217--223 (2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
-\CSLLeftMargin{82. }%
-\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2022).}
+\CSLLeftMargin{83. }%
+\CSLRightInline{R Core Team, \emph{R: A Language and Environment for Statistical Computing} (R Foundation for Statistical Computing, Vienna, Austria, 2022; \url{https://www.R-project.org/}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-\CSLLeftMargin{83. }%
-\CSLRightInline{Wickham, H. \emph{\href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis}}. (Springer-Verlag New York, 2016).}
+\CSLLeftMargin{84. }%
+\CSLRightInline{H. Wickham, \emph{{ggplot2}: Elegant Graphics for Data Analysis} (Springer-Verlag New York, 2016; \url{https://ggplot2.tidyverse.org}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
-\CSLLeftMargin{84. }%
-\CSLRightInline{Wilke, C. O. \emph{\href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}}. (2020).}
+\CSLLeftMargin{85. }%
+\CSLRightInline{C. O. Wilke, \emph{{cowplot}: Streamlined Plot Theme and Plot Annotations for 'Ggplot2'} (2020; \url{https://CRAN.R-project.org/package=cowplot}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
-\CSLLeftMargin{85. }%
-\CSLRightInline{Landau, W.
-M.
-\href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}.
+\CSLLeftMargin{86. }%
+\CSLRightInline{W.
+M.
+Landau, \href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}.
 \emph{Journal of Open Source Software} \textbf{6}, 2959 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
-\CSLLeftMargin{86. }%
-\CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}}. (2022).}
+\CSLLeftMargin{87. }%
+\CSLRightInline{F. Aust, M. Barth, \emph{{papaja}: {Prepare} Reproducible {APA} Journal Articles with {R Markdown}} (2022; \url{https://github.com/crsh/papaja}).}
 
@@
 
-\renewcommand{\figurename}{Supplementary Figure}
-\renewcommand{\tablename}{Supplementary Table}
-\renewcommand{\thefigure}{\arabic{figure}} \setcounter{figure}{0}
-\renewcommand{\thetable}{\arabic{table}} \setcounter{table}{0}
+\renewcommand{\figurename}{Fig.}
+\renewcommand{\tablename}{Table}
+\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
 \renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}

### 2023-11-20 R/functionsPlotPhylo.R

@@ -12,20 +12,15 @@ plotPhylogeny1 <- function(d, MCCphylogeny) {
   # mutate and rename vars
   d <-
     d %>%
-    mutate(ToolUse = ifelse(d$ToolUse == 0, "Absent",
-                                   ifelse(d$LiteratureExists_Binary == 1 & d$VideosFound == 0, "Present (in literature only)",
-                                          ifelse(d$LiteratureExists_Binary == 0 & d$VideosFound > 0, "Present (in videos only)",
-                                                 "Present (in videos and lit.)")
-                                   ))) %>%
-    # add "candidate" tool users from survival cure model
-    mutate(ToolUse = ifelse(d$Name %in% candidates, "Top 10 candidate species", ToolUse),
-           ToolUse = factor(ToolUse, levels = c("Present (in videos and lit.)",
-                                                "Present (in literature only)",
-                                                "Present (in videos only)",
-                                                "Top 10 candidate species",
-                                                "Absent"))) %>%
-    # rename variables
-    rename(`Tool Use` = ToolUse, `Search Hits` = SearchHits)
+    mutate(
+      # total number of papers/videos
+      ResearchEffort_Lit = log(Current.General.Papers + 1),
+      ResearchEffort_Vid = log(SearchHits + 1),
+      ToolUse_Lit = ifelse(LiteratureExists_Binary == 1, "Present in literature", "Absent"),
+      ToolUse_Vid = ifelse(VideosFound > 0, "Present in videos", "Absent"),
+      # add "candidate" tool users from survival cure model
+      Candidates = ifelse(Name %in% candidates, "Top 10 candidate species", "Non-candidate")
+      )
   # abbreviated species names for labels
   makeLabel <- function(x) paste0(substring(x, 1, 1), ". ", str_split(x, "_")[[1]][2])
   for (i in 1:length(d$Name)) {
@@ -35,24 +30,38 @@ plotPhylogeny1 <- function(d, MCCphylogeny) {
   # plot
   out <- 
     ggtree(MCCphylogeny, layout = "fan") %<+% d +
[…]

### 2023-11-20 _targets.R

@@ -13,9 +13,9 @@ source("R/functionsSurvivalCure.R")
 options(tidyverse.quiet = TRUE)
 tar_option_set(packages = c("tidyverse", "ape", "brms", "cowplot", "dagitty", 
                             "geiger", "ggdag", "ggridges", "ggstance", "ggtree", 
-                            "magick", "papaja", "phangorn", "phytools", 
-                            "readxl", "reshape2", "rethinking", "rstan",
-                            "scales", "sdamr", "tidybayes"))
+                            "ggtreeExtra", "magick", "papaja", "phangorn", 
+                            "phytools", "readxl", "reshape2", "rethinking", 
+                            "rstan", "scales", "sdamr", "tidybayes"))
 options(
   clustermq.scheduler = "slurm", 
   clustermq.template = "slurm_clustermq.tmpl"

### 2024-01-04 manuscript.Rmd
update manuscript

@@
 Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to estimate actual rates of tool use in parrots.
-Crowdsourcing revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%).
-Phylogenetic models incorporating these data together with measures of research effort and hypothesised predictors of tool use suggest that between 11% and 17% of parrot species may be tool users.
-These findings challenge the assumption that current research effort captures the distribution of putatively rare animal behaviours.
+Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%).
+Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11% and 17% of extant parrot species may be tool users.
+These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait.
+Overall, our findings challenge the assumption that current sampling effort captures the full distribution of putatively rare animal behaviours.
+Combining our sampling and analysis methods offers a fruitful approach for investigating the distribution, drivers, and origins of other rare behaviours.
 
 keywords          : "tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling"
-wordcount         : "6548 words"
 bibliography      : ["r-references.bib"]
@@
 appendix          : "appendix.Rmd"
-csl               : science.csl
+csl               : nature.csl
 ---
 
-\nolinenumbers
+\linenumbers
 
@@
 else being equal those with fewer published papers and fewer video search hits 
-have a higher probability of being undetected tool users (fig. 
+have a higher probability of being undetected tool users (Supplementary Figure 
 \@ref(fig:plotSurvCure3)).
@@
 area-under-the-curve classification statistic of 
-`r printnum(tar_read(auc), digits = 2)` (fig.  
+`r printnum(tar_read(auc), digits = 2)` (Supplementary Figure 
 \@ref(fig:plotSurvCure9)). To further estimate the accuracy of the model's 
@@
 effect of relative brain size and no difference between feeding strategies, 
-respectively (fig. \@ref(fig:plotComparison)).
+respectively (Supplementary Figure \@ref(fig:plotComparison)).
 
@@
 the _Poicephalus_ genus native to Africa (Table \@ref(tab:tableASR); 
-fig. s \@ref(fig:plotASR1) - \@ref(fig:plotASR3)). These findings 
+Supplementary Figures \@ref(fig:plotASR1) - \@ref(fig:plotASR3)). These findings 
 suggest that species from each of these genera may share their tool use 
@@
 (_Cacatuidae_), Old World parrots (_Psittacinae_), and neotropical parrots 
-(_Arinae_).
-
-While parrots in the wild use tools to achieve a variety of 
-goals [@Goodman2018;@OHara2021], the 17 additional species identified by our 
-video survey were exclusively observed using tools for self-scratching. This is 
-likely because preening is the only context in which captive parrots regularly 
-require tools, unlike wild parrots who may also require tools for extractive 
-foraging [@Goodman2018;@OHara2021]. Despite this difference in the type of tool 
-use observed, self-scratching is nonetheless a major category of animal tool 
-use and clearly meets the established criteria for tool use in the literature: 
-the manipulation of an unattached object as an extension of the animal's body to 
-achieve a goal [@Shumaker2011]. It also meets the definition for a more complex 
-type of embodied tool use known as 'tooling', the deliberate generation of a 
-mechanical interface by using an object to manipulate another target or 
-surface [@Fragaszy2018]. The fact that we found strong phylogenetic clustering 
-of self-scratching tool use from the video survey with other examples of tool 
-use from the literature supports a common underlying cognitive mechanism. In 
-line with this, some of the species of parrots that use tools for 
-self-scratching in captivity also use tools for other purposes in the wild
-[@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021].
-
-There was little evidence to suggest that the observations of self-scratching
-tool use in the video survey were merely unintentional accidents or explicitly 
-trained behaviours. Individual parrots often used tools slowly and repetitively 
-over long periods of time, even across multiple different videos, suggesting 
-that their behaviour was not random or accidental [@Sandor2020]. Parrots 
-preferentially employed self-scratching tools on areas of their body that were 
-otherwise inaccessible, with 96% of all instances involving scratching of the 
-head or neck, suggesting intentional tool use. For 60% of the species in the 
-video survey, we found two or more videos of repetitive and sustained scratching 
-by different individuals of the same species in separate households, suggesting 
-that the manipulations were intentional and recurring events that did not 
-represent unusual stereotypies of any single individual. Regarding the 
-possibility of training or cueing from owners, over half of the videos contained 
-no evidence of human interaction aside from filming the behaviour. Humans only 
-handed parrots their tools in two of the videos, and none of the videos featured 
-owners directly rewarding tool use behaviours with food. Finally, the high 
-levels of phylogenetic signal in our data provides strong evidence that the 
-observations from our video survey reflect biologically-endowed capacities for 
-tool use rather than accidental or trained behaviours, which would likely appear 
-uniformly across the phylogeny.
-
-Beyond the video survey, the strong phylogenetic signal in our dataset allowed 
-us to use phylogenetic information, along with other variables, to infer the 
-unobserved probabilities of tool use across the parrot order. Our phylogenetic 
-survival cure model incorporated information on phylogenetic history, research 
-effort, relative brain size, and feeding specialisation to rank parrot species 
-that were most likely to be undetected tool users. The sum of probabilities from 
-this model implied that between 15 and 41 of the species without observed 
-evidence of tool use are likely to be undetected tool users, suggesting that the 
-true proportion of tool users may be as high as 17%.
+(_Arinae_). Beyond the crowdsourcing survey, the strong phylogenetic signal in 
+our dataset allowed us to use phylogenetic information, along with other 
+variables, to infer the unobserved probabilities of tool use across the parrot 
+order. Our phylogenetic survival cure model incorporated information on 
+phylogenetic history, research effort, relative brain size, and feeding 
+specialisation to rank parrot species that were most likely to be undetected 
+tool users. The sum of probabilities from this model implied that between 15 
+and 41 of the species without observed evidence of tool use are likely to be 
+undetected tool users, suggesting that the true proportion of tool users may be
+as high as 17%.
 
@@
 using tools [@HenkeVonDerMalsburg2020].
+
+All instances of tool use in our crowdsourcing survey met the established
+criteria for tool use in the literature: the manipulation of an unattached 
+object as an extension of the animal's body to achieve a goal [@Shumaker2011].
+However, a striking feature of the dataset is that the 17 additional species
+identified in the video survey were exclusively observed using tools for
+self-scratching. While parrots in the wild use tools to achieve a variety of 
+goals, including extractive foraging and preening [@Goodman2018;@OHara2021],
+parrots in captivity only require tools to achieve the latter goal. Despite this
+difference in the type of tool use observed, self-scratching is nonetheless a 
+major category of animal tool use. Self-scratching also meets the definition for
+a more complex type of embodied tool use known as 'tooling', the deliberate 
+generation of a mechanical interface by using an object to manipulate another 
+target or surface [@Fragaszy2018]. The fact that we found strong phylogenetic 
+clustering of self-scratching tool use from the video survey with other examples
+of tool use from the literature supports a common underlying cognitive
+mechanism. In line with this, some of the species of parrots that use tools for 
+self-scratching in captivity also use tools for other purposes in the wild
+[@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021].
+
+There was little evidence to suggest that the observations of self-scratching
+tool use in the video survey were merely unintentional accidents or explicitly 
+trained behaviours. Individual parrots often used tools slowly and repetitively 
+over long periods of time, even across multiple different videos, suggesting 
+that their behaviour was not random or accidental [@Sandor2020]. Parrots 
+preferentially employed self-scratching tools on areas of their body that were 
+otherwise inaccessible, with 96% of all instances involving scratching of the 
+head or neck, suggesting intentional tool use. For 60% of the species in the 
+video survey, we found two or more videos of repetitive and sustained scratching 
+by different individuals of the same species in separate households, suggesting 
+that the manipulations were intentional and recurring events that did not 
+represent unusual stereotypies of any single individual. Regarding the 
+possibility of training or cueing from owners, over half of the videos contained 
+no evidence of human interaction aside from filming the behaviour. Humans only 
+handed parrots their tools in two of the videos, and none of the videos featured 
+owners directly rewarding tool use behaviours with food. Finally, the high 
+levels of phylogenetic signal in our data provide strong evidence that the 
+observations from our video survey reflect biologically-endowed capacities for 
+tool use rather than accidental or trained behaviours, which would likely appear 
+uniformly across the phylogeny.
 
@@
 
-We collected data for 194 parrot species (figs. 
+We collected data for 194 parrot species (Supplementary Figures
 \@ref(fig:plotPhylo2) - \@ref(fig:plotPhylo4)). We gathered feeding strategy 
@@
 The priors for this model produce reasonable prior predictions of the 
-probabilities of tool use for each parrot species (fig.
+probabilities of tool use for each parrot species (Supplementary Figure
 \@ref(fig:plotSurvCure7)), but a sensitivity analysis revealed that the ranking 
 and posterior probabilities reported in the main text were robust to modifying 
-these priors (fig. \@ref(fig:plotSurvCure8)). We estimated the 
+these priors (Supplementary Figure \@ref(fig:plotSurvCure8)). We estimated the 
 posterior distribution of this model using Hamiltonian Monte Carlo as 
@@
 effective sample sizes suggested that the model converged normally. Trace plots 
-are reported in fig. \@ref(fig:plotTrace). We report 
+are reported in Supplementary Figure \@ref(fig:plotTrace). We report 
 equal-tailed credible intervals to describe the posterior distribution of this 
@@
 parameters. The model was able to successfully recover those parameters 
-(fig. \@ref(fig:plotSurvCureSim)). We also ran a 
+(Supplementary Figure \@ref(fig:plotSurvCureSim)). We also ran a 
 leave-one-species-out exercise to ensure that we could accurately predict known 
@@
 All analyses were conducted in R v4.2.1. [@RCoreTeam]. Visualisations were 
-produced using the _ggplot2_ [@Wickham2016] and _cowplot_ [@Wilke2020] packages. 
-The manuscript was reproducibly generated using the _targets_ [@Landau2021] and 
-_papaja_ [@Aust2022] packages. Code to reproduce all analyses and figures can be 
-found here: https://github.com/ScottClaessens/phyloParrot
+produced using the _ggtree_[@ggtree], _ggplot2_ [@Wickham2016], and _cowplot_ 
+[@Wilke2020] packages. The manuscript was reproducibly generated using the 
+_targets_ [@Landau2021] and _papaja_ [@Aust2022] packages. Code to reproduce all 
+analyses and figures can be found here: 
+https://github.com/ScottClaessens/phyloParrot
 

### 2024-01-04 manuscript.tex
update manuscript

--- 2023-08-18 manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling\newline\indent Word count: 4289 words excluding Methods (Methods: 1821 words)}
+\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling}
 \usepackage{lineno}
@@
 \abstract{%
-Studying the prevalence of putatively rare behaviours, such as tool use, is challenging because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort.
-Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to approximate actual rates of a rarely observed behaviour based on limited data, targeting tool use in parrots.
+Putatively rare behaviours, such as tool use, are challenging to study because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort.
+Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to estimate actual rates of tool use in parrots.
 Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
@@
 
-Our understanding of the evolution of animal behaviour is built on the assumption that we have access to sufficient data\textsuperscript{1--3}.
-However, this is not always the case.
-Data on behaviours that are rare, fleeting, or otherwise difficult to observe are likely to be patchy and incomplete\textsuperscript{4,5}.
-Among species for which such behaviours have not been observed, it can be difficult to differentiate between cases in which the species is truly incapable of producing the behaviour and cases in which the species is capable of producing the behaviour but the behaviour has not yet been observed.
-Such a distinction can be critical for drawing conclusions about the rarity and evolution of the behaviour in question.
-
-Comparative work on the evolution of tool use is a paradigmatic example of this issue.
-The initial discoveries of tool use in chimpanzees\textsuperscript{6}, birds\textsuperscript{7}, dolphins\textsuperscript{8}, and octopuses\textsuperscript{9} occurred decades after significant advances on other more easily measurable aspects of their biology.
-Since these initial discoveries, scholars have used the distribution of reported tool use across species to make various claims about the evolutionary drivers of tool use behaviours.
-For example, based on the observation that bird species with reported tool use tended to have larger brains, researchers have identified higher relative brain size as a likely precondition for tool using capabilities\textsuperscript{10--12}.
-These researchers argue that larger brains are better able to integrate visual and somatosensory information when innovating novel behaviours, such as tool use, in changing environments\textsuperscript{13,14}.
-Similarly, researchers have used existing reports of tool use in birds to debate the roles of generalist versus specialist feeding strategies in driving the evolution of tool use, with some arguing that feeding generalists require technical innovations to expand their dietary niche\textsuperscript{13,15,16} and others arguing that feeding specialists require technical innovations for extractive foraging of specific foods\textsuperscript{17,18}.
-
-However, before we can make claims of this kind, we need to know whether current research effort in the literature is sufficient for robust conclusions to be drawn about the evolution of tool use.
-In fact, evidence suggests that research effort is often systematically biased towards particular taxonomic groups, parts of the world that are easy to access, and species with life history traits that make them easier to study, such as larger distribution ranges and population sizes\textsuperscript{19}.
-This is a crucial limitation because insufficient observation may lead researchers to miss true instances of tool behaviours and thus draw premature conclusions about the evolutionary drivers and origins of tool use.
-While researchers have attempted to deal with this problem by controlling for the number of scientific papers published on different species, previous work has not yet attempted to quantify and explicitly model the relationship between actual tool-using behaviour and what is reported in the scientific literature.
-If more tool-using species exist than previously thought, this could have important implications for theories of the evolutionary drivers and origins of tool use and, more generally, for our understanding of how rare this behaviour actually is.
-
-One potentially powerful method for quantifying actual rates of rare animal behaviours is crowdsourcing\textsuperscript{20}.
-In a crowdsourcing study, researchers collect reports from the general public and/or collate and analyse videos posted on social media platforms.
-This citizen science approach has been widely used in ecology to monitor the distributional patterns of species\textsuperscript{21}, but has also recently been used to uncover a variety of rare animal behaviours, including interspecies play in dogs\textsuperscript{20}, novel problem-solving behaviours in horses\textsuperscript{22}, and socially-learned foraging innovations in cockatoos\textsuperscript{23,24}.
-By casting the net wider than the scientific literature, the crowdsourcing method can provide an indication of the tool-using species that the literature might be missing.
-
-Even after using this crowdsourcing approach, some tool-users could \emph{still} remain unobserved.
-An additional approach to identify these unobserved species is to specify a causal model of the process that generates the observed data.
-We propose one such causal model in Figure \ref{fig:plotDAG}.
-In this model, we assume that the presence of tool use in the scientific literature (or in crowdsourced reports) is caused by both unobserved tool use capabilities and the number of published studies (or the number of crowdsourced reports) for any given species.
-Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected.
-Furthermore, based on existing theories of the evolution of tool use\textsuperscript{10--18}, we propose that the unobserved presence or absence of tool use is additionally caused by relative brain size, feeding strategy, and shared phylogenetic ancestry.
-Expressing this causal model as a statistical model can suggest further species which are likely to be unobserved tool-users and, simultaneously, test existing theories of the evolutionary drivers of tool use without incorrectly assuming that absence of evidence is evidence of absence.
+Our understanding of the evolution of animal behaviour is built on the
+assumption that we have access to sufficient data\textsuperscript{1--3}. However, this is not always the case. Data on behaviours that are
+rare, fleeting, or otherwise difficult to observe are likely to be patchy and
+incomplete\textsuperscript{4,5}. Among species for which such behaviours
+have not been observed, it can be difficult to differentiate between cases in
+which the species is truly incapable of producing the behaviour and cases in
+which the species is capable of producing the behaviour but the behaviour has
+not yet been observed. Such a distinction can be critical for drawing
+conclusions about the rarity and evolution of the behaviour in question.
+
+Comparative work on the evolution of tool use is a paradigmatic example of this
+issue. The initial discoveries of tool use in chimpanzees\textsuperscript{6},
+birds\textsuperscript{7}, dolphins\textsuperscript{8}, and octopuses\textsuperscript{9} occurred
+decades after significant advances on other more easily measurable aspects of
+their biology. Since then, scholars have proposed a clear operational
+definition of tool use applicable to all species --- the manipulation of an
+unattached object as an extension of the animal's body to achieve a
+goal\textsuperscript{10} --- and have used the distribution of species meeting this
+definition to make various claims about the evolutionary drivers of tool use
+behaviours. For example, based on the observation that bird species with
+reported tool use tended to have larger brains, researchers have identified
+higher relative brain size as a likely precondition for tool using
+capabilities\textsuperscript{11--13}. These researchers
+argue that larger brains are better able to integrate visual and somatosensory
+information when innovating novel behaviours, such as tool use, in changing
+environments\textsuperscript{14,15}. Similarly, researchers have used existing
+reports of tool use in birds to debate the roles of generalist versus
+specialist feeding strategies in driving the evolution of tool use, with some
+arguing that feeding generalists require technical innovations to expand their
+dietary niche\textsuperscript{14,16,17} and others arguing that
+feeding specialists require technical innovations for extractive foraging of
+specific foods\textsuperscript{18,19}.
+
+However, before we can make claims of this kind, we need to know whether current
+research effort in the literature is sufficient for robust conclusions to be
+drawn about the evolution of tool use. In fact, evidence suggests that research
+effort is often systematically biased towards particular taxonomic groups, parts
+of the world that are easy to access, and species with life history traits that
+make them easier to study, such as larger distribution ranges and population
+sizes\textsuperscript{20}. This is a crucial limitation because insufficient
+observation may lead researchers to miss true instances of tool behaviours and
+thus draw premature conclusions about the evolutionary drivers and origins of
+tool use. While researchers have attempted to deal with this problem by
+controlling for the number of scientific papers published on different species,
+previous work has not yet attempted to quantify and explicitly model the
+relationship between actual tool-using behaviour and what is reported in the
+scientific literature. If more tool-using species exist than previously thought,
+this could have important implications for theories of the evolutionary drivers
+and origins of tool use and for our understanding of how rare this behaviour
+actually is.
+
+One potentially powerful method for quantifying actual rates of rare animal
+behaviours is crowdsourcing\textsuperscript{21}. In a crowdsourcing study, researchers
+collect reports from the general public and/or collate and analyse videos posted
+on social media platforms. This citizen science approach has been widely used in
+ecology to monitor the distributional patterns of species\textsuperscript{22}, but
+has also recently been used to uncover a variety of rare animal behaviours,
+including interspecies play in dogs\textsuperscript{21}, novel problem-solving
+behaviours in horses\textsuperscript{23}, and socially-learned foraging innovations
+in cockatoos\textsuperscript{24,25}. By casting the net wider than the
+scientific literature, the crowdsourcing method can provide an indication of the
+tool-using species that the literature might be missing.
+
+Even after using this crowdsourcing approach, some tool-users could \emph{still}
+remain unobserved. One principled framework for identifying these unobserved species
+is to specify a causal model of the process that generates the observed data. We
+propose one such causal model in Figure \ref{fig:plotDAG}. In this model, we
+assume that the presence of tool use in the scientific literature (or in
+crowdsourced reports) is caused by both unobserved tool use capabilities and the
+number of published studies (or the number of crowdsourced reports) for any
+given species. Tool users are more likely to be observed if they are well
+studied, but understudied tool users may go undetected. Furthermore, based on
+existing theories of the evolution of tool use\textsuperscript{11--19}, we propose that the
+unobserved tool use capabilities are additionally caused by relative brain size,
+feeding strategy, and shared phylogenetic ancestry. Expressing this causal model
+as a statistical model can suggest further species which are likely to be
+unobserved tool-users and, simultaneously, test existing theories of the
+evolutionary drivers of tool use without incorrectly assuming that absence of
+evidence is evidence of absence.
 
@@
 \includegraphics{manuscript_files/figure-latex/plotDAG-1.pdf}
-\caption{\label{fig:plotDAG}\emph{Causal model of observed tool use.} Directed acyclic graph of the causal relationships between observed tool use and other variables.
-Available scientific data on tool use is caused both by unobserved tool use presence and scientific research effort (i.e., number of publications).
-Available crowdsourced data on tool use is caused both by unobserved tool use presence and crowdsourcing effort (i.e., number of crowdsourced reports).
-According to theory, unobserved tool use presence should be caused by relative brain size (encephalisation quotient) and feeding strategy (generalist vs.~specialist).
-These variables all share unobserved confounds generated by shared phylogenetic history.
-Grey circles indicate unobserved variables.}
+\caption{\label{fig:plotDAG}\emph{Causal model of observed tool use.} Directed acyclic graph
+of the causal relationships between observed tool use and other variables.
+Available scientific data on tool use is caused both by unobserved tool use
+presence and scientific research effort (i.e., number of publications).
+Available crowdsourced data on tool use is caused both by unobserved tool use
+presence and crowdsourcing effort (i.e., number of crowdsourced reports).
+According to theory, unobserved tool use presence should be caused by relative
+brain size (encephalisation quotient) and feeding strategy (generalist vs.~
+specialist). These variables all share unobserved confounds generated by shared
+phylogenetic history. Grey circles indicate unobserved variables.}
 \end{figure}
 
-Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool use in the parrot order.
-We focus on tool use in parrots for a number of reasons.
-First, the scientific literature suggests that only a small proportion of extant parrot species (11 out of 398\textsuperscript{25}; 3\%) use tools\textsuperscript{10,26--38} (note that we do not include in this count species that have been previously shown to use touchscreen devices as these behaviours were explicitly trained\textsuperscript{39}).
-Parrot tool use thus provides an ideal test case for examining how robust sampling is in the scientific literature.
-Second, parrots are highly popular as pets.
-Over 70\% of all extant parrot species are bred in the aviculture industry and kept as pets worldwide\textsuperscript{40--46}, enabling us to leverage the power of crowdsourcing on a social media platform to search for evidence of tool use\textsuperscript{20}.
-Third, detailed data on relative brain sizes\textsuperscript{47--52}, feeding strategies\textsuperscript{53}, and shared ancestry\textsuperscript{54} exist for parrots, allowing us to fit the statistical model implied by Figure \ref{fig:plotDAG} to the entire parrot order.
-
-We first present the results from our crowdsourcing survey, in which we collated videos of tool use in parrots from an online video platform.
-This survey reveals a number of previously unidentified tool-using parrot species, which we map onto the phylogeny of the parrot order.
-We then describe our statistical model in more detail, and use it to (\emph{i}) rank further parrot species that are likely unobserved tool users and (\emph{ii}) re-examine key hypotheses regarding the evolutionary drivers and origins of tool use in parrots.
+Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool
+use in the parrot order. We focus on tool use in parrots for a number of
+reasons. First, the scientific literature suggests that only a small proportion
+of extant parrot species (11 out of 398; 3\%) use tools\textsuperscript{11,26--38}. Parrot tool use
+thus provides an ideal test case for examining how robust sampling is in the
+scientific literature. Second, parrots are highly popular as pets. Over 70\% of
+all extant parrot species are bred in the aviculture industry and kept as pets
+worldwide\textsuperscript{39--45}, enabling us to leverage the power of crowdsourcing on a social
+media platform to search for evidence of tool use\textsuperscript{21}. Third, detailed
+data on relative brain sizes\textsuperscript{46--51}, feeding strategies\textsuperscript{52}, and
+shared ancestry\textsuperscript{53} exist for parrots, allowing us to fit the
+statistical model implied by Figure \ref{fig:plotDAG} to the entire parrot
+order.
+
+We first present the results from our crowdsourcing survey, in which we collated
+videos of tool use in parrots from an online video platform. This survey reveals
+a number of previously unidentified tool-using parrot species, which we map onto
+the phylogeny of the parrot order. We then describe our statistical model in
+more detail, and use it to (\emph{i}) rank further parrot species that are likely
+unobserved tool users and (\emph{ii}) re-examine key hypotheses regarding the
+evolutionary drivers and origins of tool use in parrots.
 
@@
 
-\hypertarget{crowdsourcing-video-survey}{%
-\subsection{Crowdsourcing video survey}\label{crowdsourcing-video-survey}}
-
-We surveyed the social media platform YouTube for video evidence of tool use in parrots (see Methods for detailed search criteria).
-In our search, we defined ``true'' tool use behaviour as the manipulation of an unattached object to achieve a goal\textsuperscript{55}, while ``borderline'' tool use involved the use of an object that was still attached to a substrate\textsuperscript{56}.
-
-In total, we found 116 videos of 104 individuals from 25 parrot species performing either true tool use (100 videos of 89 individuals from 22 species) or borderline tool use (16 videos of 16 individuals from 7 species).
-All videos featured pet parrots in captive settings.
-In 68 of these videos, owners did not appear to interfere with the subjects' actions.
-In 43 videos, there was potential interference, either from the owners being in close physical contact with the bird (e.g., bird perching on hand), talking to the bird, or handing it the tool (which occurred in only two videos).
-We could not establish the degree of interference in the remaining 5 videos, as sound had been removed or was substituted by music.
-None of the videos featured owners directly rewarding tool use behaviours with food.
-All borderline tool use cases were excluded from further analyses.
-
-Of the 22 parrot species performing true tool use, 13 were represented in our video survey by two or more individuals over multiple independent observations.
-True tool use always involved the subject using an object for self-scratching (95 videos involved scratching the head and/or neck).
-The most common tool (53 videos) was a moulted feather.
-Human-made objects (e.g., pens, spoons, pieces of wood, cardboard) were also common.
-
-According to YouTube video descriptions and owner comments, 45 of the individuals performing true tool use were males and 18 were females.
-No sex information was provided for the remaining 26 individuals.
-As owners provided no information on whether sex had been established through genetic testing, and sexual dimorphism in parrots is rare\textsuperscript{57,58}, we could not typically ascertain if descriptions were accurate.
-It is unclear if the disproportionately large number of males in the sample is a consequence of owners more readily assuming their parrots are male when they have not been genetically tested, owners being more likely to own or film male parrots, or male parrots exhibiting more true tool use behaviours than female parrots.
-
-Figure \ref{fig:plotPhylo1} maps the findings from the video survey onto a maximum clade credibility phylogeny for the parrot order, plotted alongside species previously identified in the scientific literature.
-Before the video survey, 11 parrot species (3\%) had been identified as tool users in the scientific literature.
-Across our video survey, we observed true tool use in 22 species, 5 of which overlapped with the scientific literature and 17 of which were novel species.
-All of the species identified in the video survey were cockatoos (Cacatuidae), Old World parrots (Psittacinae), or neotropical parrots (Arinae).
-The most common species in our survey, accounting for 41 videos from 37 individuals, was the green-cheeked conure (\emph{Pyrrhura molinae}).
-In accordance with the scientific literature, the video survey found no evidence of tool use in any species of Psittaculidae, despite this family containing some of the most commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet species.
-Combining both the video survey and the scientific literature, we can thus identify 28 tool-using parrot species overall (7\%), compared to the 11 previously reported.
+\hypertarget{crowdsourcing-reveals-tool-use-in-additional-parrot-species}{%
+\subsection{Crowdsourcing reveals tool use in additional parrot species}\label{crowdsourcing-reveals-tool-use-in-additional-parrot-species}}
+
+We surveyed the social media platform YouTube for video evidence of tool use in
+parrots (see Methods for detailed search criteria). In our search, we used the
+standard criteria for identifying tool use in the literature, defining ``true''
+tool use behaviour as the manipulation of an unattached object as an extension
+of the animal's body to achieve a goal\textsuperscript{10}, while ``borderline'' tool
+use involved the use of an object that was still attached to a substrate\textsuperscript{54}.
+
+In total, we found 116 videos of
+104 individuals from
+25
+parrot species performing behaviours that met the definition of either true tool
+use (100 videos of
+89
+individuals from
+22
+species) or borderline tool use (16 videos of
+16
+individuals from
+7
+species). All videos featured pet parrots in captive settings. In
+68 of these
+videos, owners did not appear to interact with the subjects. In
+43 videos,
+there was potential human interaction, either from the owners being in close physical
+contact with the bird (e.g., bird perching on hand), talking to the bird, or
+handing it the tool (which occurred in only two videos). We could not establish
+the degree of human interaction in the remaining
+5
+videos, as sound had been removed or was substituted by music. None of the
+videos featured owners directly rewarding tool use behaviours with food. All
+borderline tool use cases were excluded from further analyses.
+
+Of the 22
+parrot species performing true tool use,
+13
+were represented in our video survey by two or more individuals over multiple
+independent observations. True tool use always involved the subject using an
+object for self-scratching (95
+videos involved scratching the head and/or neck). The most common tool (53
+videos) was a moulted feather. Human-made objects (e.g., pens, spoons, pieces of
+wood, cardboard) were also common.
+
+According to YouTube video descriptions and owner comments,
+45
+of the individuals performing true tool use were males and
+18
+were females. No sex information was provided for the remaining
+26
+individuals. As owners provided no information on whether sex had been
+established through genetic testing, and sexual dimorphism in parrots is
+rare\textsuperscript{55,56}, we could not typically ascertain if descriptions
+were accurate. It is unclear if the disproportionately large number of males in
+the sample is a consequence of owners more readily assuming their parrots are
+male when they have not been genetically tested, owners being more likely to own
+or film male parrots, or male parrots exhibiting more true tool use behaviours
+than female parrots.
+
+Figure \ref{fig:plotPhylo1} maps the findings from the video survey onto a
+maximum clade credibility phylogeny for the parrot order, plotted alongside
+species previously identified in the scientific literature. Before the video
+survey, 11 parrot species (3\%) had been identified as tool users in the
+scientific literature. Across our video survey, we observed true tool use in
+22
+species, 5 of which overlapped with the scientific literature and
+17
+of which were novel species. All of the species identified in the video survey
+were cockatoos (\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), or neotropical
+parrots (\emph{Arinae}). The most common species in our survey, accounting for
+41 videos from
+37
+individuals, was the green-cheeked conure (\emph{Pyrrhura molinae}). In accordance
+with the scientific literature, the video survey found no evidence of tool use
+in any species of Psittaculidae, despite this family containing some of the most
+commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet
+species. Combining both the video survey and the scientific literature, we can
+thus identify 28 tool-using parrot species overall (7\%), compared to the 11
+previously reported.
 
@@
 
-The identification of new tool-using species in our video survey increases the extent to which phylogeny can explain the distribution of tool use in the parrot order.
-We estimated phylogenetic signal (Pagel's \(\lambda\)) of tool use using both the pre-video-survey and post-video-survey data.
-Pagel's \(\lambda\) varies between 0 and 1, where 0 implies that the distribution of a trait across species is unexplained by phylogenetic relatedness and 1 implies that the distribution of a trait across species is fully explained by phylogeny.
-Using the evidence of tool use from the scientific literature alone (pre-video-survey data; 11 tool-using species), we estimated an average posterior Pagel's \(\lambda\) of 0.60 (95\% credible interval {[}0.00 0.90{]}; total \emph{n} = 174 species).
-This estimate was moderate-to-strong, but highly uncertain.
-In comparison, combining the evidence from both the literature and the video survey (post-video-survey data; 28 tool-using species) resulted in a stronger and more certain estimate of phylogenetic signal.
-With these data, we estimated Pagel's \(\lambda\) = 0.65 (95\% CI {[}0.50 0.77{]}; total \emph{n} = 174 species).
-Thus, the results of our video survey increase the extent to which the distribution of tool use across parrot species can be explained by shared phylogenetic ancestry.
-This suggests that we can potentially use phylogenetic information, along with other variables, to identify further tool-using parrot species that may remain undetected.
-
-\hypertarget{phylogenetic-survival-cure-model}{%
-\subsection{Phylogenetic survival cure model}\label{phylogenetic-survival-cure-model}}
-
-In addition to the 28 tool-using species identified in the literature and our video survey, we fitted a Bayesian phylogenetic survival cure model to rank further species that are likely to be undetected tool-users (i.e., tool-using species with no tool use reported in the literature or in crowdsourced videos).
-
-Survival cure models are often used in the medical sciences to analyse the time to some event, such as cancer relapse, with censored patient data\textsuperscript{59}.
-The data are right-censored because some patients have relapsed when they are measured, and some have not yet relapsed when they are measured (i.e., they are censored).
-The cure aspect of these models comes from an additional assumption that a certain proportion of the population is ``cured'' and can never relapse, no matter how long we measure them for.
-
-Our tool use problem has the same features.
-We are modelling a time-to-event; specifically, the amount of ``time'' (i.e., observation opportunities measured as the number of published papers or crowdsourced videos) until tool use is identified.
-This is right-censored data, because many species will not have had tool use identified when we measure them.
-Moreover, we can assume that a certain proportion of the population is ``cured'' -- that is, they are not tool users, and so we will never identify tool use for them, no matter how long we measure them for.
-
-In our model, we infer the tool-using status of each species by allowing each species to have their own probability of being ``cured'' (i.e., not a tool user).
-Following our causal model (Figure \ref{fig:plotDAG}), we predict these probabilities based on feeding strategy, encephalisation quotient, and phylogenetic history (see Methods for full model).
-The model additionally takes research effort into account by allowing that, among species for which tool use is unobserved, all else being equal those with fewer published papers and fewer video search hits have a higher probability of being undetected tool users (Supplementary Figure \ref{fig:plotSurvCure3}).
-
-We found that this phylogenetic survival cure model was able to adequately distinguish between species with and without evidence for tool use, with an area-under-the-curve classification statistic of 0.95 (Supplementary Figure \ref{fig:plotSurvCure9}).
-To further estimate the accuracy of the model's predictions, we also used a leave-one-species-out approach with known tool users.
-For each of the 25 tool-using species that were represented on the phylogeny and for which we had brain size and genomic data (we lacked data for three tool-using species), we fitted the model to a modified dataset which set tool use to be absent for the target species in both the scientific literature and the video survey.
-Across 25 cross-validation models, 18 models (72\%) continued to predict the target species as having a median posterior probability of tool use that was within the range of all other tool users.
-This classification rate was greater than the baseline classification rate of 26\% for species without evidence of tool use in the full model (38 of 149 species without evidence of tool use had a median posterior probability of tool use that was within the range of the tool-using species).
-Together, the area-under-the-curve statistic and the leave-one-species-out approach suggest that the model is able to adequately classify known tool users, with some error.
-
-Figure \ref{fig:plotSurvCure1} visualises the ranked posterior probabilities of tool use from the phylogenetic survival cure model for all parrot species.
-As expected, the known tool users are ranked towards the top of this list.
-However, several ``tool use absent'' species also rank highly on the list, despite not being identified as tool users in the scientific literature or in our video survey.
-In fact, according to the model, the most likely tool user is a species for which tool use is unobserved in our data: the blue-eyed cockatoo (\emph{Cacatua opthalmica}).
-This species is endemic to Papua New Guinea and is relatively understudied, with only 6 published papers and 596 video search hits, which is fewer than the model expects are necessary to discover tool use when it is present (Figure \ref{fig:plotSurvCure2}).
-This species is also found in the \emph{Cacatua} genus, a clade containing several known tool users.
-This prediction makes sense given the high phylogenetic signal for tool use reported by the model (Supplementary Figures \ref{fig:plotSurvCure5} and \ref{fig:plotSurvCure6}).
-Beyond the blue-eyed cockatoo, other highly ranked species without observed evidence of tool use are the Meyer's parrot (\emph{Poicephalus meyeri}), the golden parakeet (\emph{Guaruba guarouba}), the long-billed corella (\emph{Cacatua tenuirostris}), the Solomons cockatoo (\emph{Cacatua ducorpsii}), the red-fronted parrot (\emph{Poicephalus gulielmi}), the Cape parrot (\emph{Poicephalus robustus}), the yellow-eared parrot (\emph{Ognorhynchus icterotis}), the red-vented cockatoo (\emph{Cacatua haematuropygia}), and the gang-gang cockatoo (\emph{Callocephalon fimbriatum}).
-Figure \ref{fig:plotPhylo1} plots these species on the parrot phylogeny, using the top ten highest ranked species without observed evidence of tool use as an abitrary cutoff for visualisation purposes.
+The identification of new tool-using species in our video survey increases the
+extent to which phylogeny can explain the distribution of tool use in the parrot
+order. We estimated phylogenetic signal (Pagel's \(\lambda\)) of tool use using
+both the pre-video-survey and post-video-survey data. Pagel's \(\lambda\) varies
+between 0 and 1, where 0 implies that the distribution of a trait across species
+is unexplained by phylogenetic relatedness and 1 implies that the distribution
+of a trait across species is fully explained by phylogeny. Using the evidence of
+tool use from the scientific literature alone (pre-video-survey data; 11
+tool-using species), we estimated an average posterior Pagel's \(\lambda\) of
+0.60 (95\% credible interval {[}0.00
+0.90{]}; total \emph{n} =
+174 species). This estimate was moderate-to-strong, but highly
+uncertain. In comparison, combining the evidence from both the literature and
+the video survey (post-video-survey data; 28 tool-using species) resulted in a
+stronger and more certain estimate of phylogenetic signal. With these data, we
+estimated Pagel's \(\lambda\) = 0.65 (95\% CI
+{[}0.50
+0.77{]}; total \emph{n} =
+174 species). Thus, the results of our video survey increase
+the extent to which the distribution of tool use across parrot species can be
+explained by shared phylogenetic ancestry. This suggests that we can potentially
+use phylogenetic information, along with other variables, to identify further
+tool-using parrot species that may remain undetected.
+
+\hypertarget{phylogenetic-survival-cure-modelling-identifies-further-candidate-tool-users}{%
+\subsection{Phylogenetic survival cure modelling identifies further candidate tool users}\label{phylogenetic-survival-cure-modelling-identifies-further-candidate-tool-users}}
+
+In addition to the 28 tool-using species identified in the literature and our
+video survey, we fitted a Bayesian phylogenetic survival cure model to rank
+further species that are likely to be undetected tool-users (i.e., tool-using
+species with no tool use reported in the literature or in crowdsourced videos).
+
+Survival cure models\textsuperscript{57}, also known as split population
+models\textsuperscript{58}, are used to analyse the time to some event of interest
+with the added assumption that a certain proportion of the population will never
+experience the event, no matter how long they are measured for. These models
+have been used to analyse a variety of right-censored outcomes, from cancer
+relapse\textsuperscript{57} to criminal recidivism\textsuperscript{58}. The data are
+right-censored because some individuals will have experienced the event when
+they are measured (e.g., disease onset, return to prison) while others will have
+not experienced the event. For those who have not experienced the event, this
+may be because (\emph{i}) the event has not happened to them yet or (\emph{ii}) the event
+will \emph{never} happen to them. Survival cure models treat these two processes
+separately.
+
+Our tool use problem has the same features. We are modelling a time-to-event;
+specifically, the amount of ``time'' (i.e., observation opportunities measured as
+the number of published papers or crowdsourced videos) until tool use is
+identified. This is right-censored data because many species will not have had
+tool use identified when we measure them. Moreover, we can assume that a certain
+proportion of the population will never experience the event -- that is, they
+are a non-tool-user and so we will never identify tool use no matter how long we
+measure them for.
+
+In our model, we infer the tool-using status of each species by allowing each
+species to have their own probability of being a non-tool-user. Following our
+causal model (Figure \ref{fig:plotDAG}), we predict these probabilities based
+on feeding strategy, encephalisation quotient, and phylogenetic history (see
+Methods for full model). The model additionally takes research effort into
+account by allowing that, among species for which tool use is unobserved, all
+else being equal those with fewer published papers and fewer video search hits
+have a higher probability of being undetected tool users (Supplementary Figure
+\ref{fig:plotSurvCure3}).
+
+We found that this phylogenetic survival cure model was able to adequately
+distinguish between species with and without evidence for tool use, with an
+area-under-the-curve classification statistic of
+0.95 (Supplementary Figure
+\ref{fig:plotSurvCure9}). To further estimate the accuracy of the model's
+predictions, we also used a leave-one-species-out approach with known tool
+users. For each of the 25 tool-using species that were represented on the
+phylogeny and for which we had brain size and genomic data (we lacked data for
+three tool-using species), we fitted the model to a modified dataset which set
+tool use to be absent for the target species in both the scientific literature
+and the video survey. Across 25 cross-validation models,
+18 models (72\%)
+continued to predict the target species as having a median posterior probability
+of tool use that was within the range of all other tool users. This
+classification rate was greater than the baseline classification rate of
+26\%
+for species without evidence of tool use in the full model
+(38
+of 149 species without
+evidence of tool use had a median posterior probability of tool use that was
+within the range of the tool-using species). Together, the area-under-the-curve
+statistic and the leave-one-species-out approach suggest that the model is able
+to adequately classify known tool users, with some error.
+
+Figure \ref{fig:plotSurvCure1} visualises the ranked posterior probabilities of
+tool use from the phylogenetic survival cure model for all parrot species. As
+expected, the known tool users are ranked towards the top of this list. However,
+several ``tool use absent'' species also rank highly on the list, despite not
+being identified as tool users in the scientific literature or in our video
+survey. In fact, according to the model, the most likely tool user is a species
+for which tool use is unobserved in our data: the blue-eyed cockatoo (\emph{Cacatua
+opthalmica}). This species is endemic to Papua New Guinea and is relatively
+understudied, with only 6 published papers
+and 596 video search hits, which is fewer than the
+model expects are necessary to discover tool use when it is present (Figure
+\ref{fig:plotSurvCure2}). This species is also found in the \emph{Cacatua} genus, a
+clade containing several known tool users. This prediction makes sense given the
+high phylogenetic signal for tool use reported by the model (Supplementary
+Figures \ref{fig:plotSurvCure5} and \ref{fig:plotSurvCure6}). Beyond the
+blue-eyed cockatoo, other highly ranked species without observed evidence of
+tool use are the Meyer's parrot (\emph{Poicephalus meyeri}), the golden parakeet
+(\emph{Guaruba guarouba}), the long-billed corella (\emph{Cacatua tenuirostris}), the
+Solomons cockatoo (\emph{Cacatua ducorpsii}), the red-fronted parrot (\emph{Poicephalus
+gulielmi}), the Cape parrot (\emph{Poicephalus robustus}), the yellow-eared parrot
+(\emph{Ognorhynchus icterotis}), the red-vented cockatoo (\emph{Cacatua haematuropygia}),
+and the gang-gang cockatoo (\emph{Callocephalon fimbriatum}). Figure
+\ref{fig:plotPhylo1} plots these species on the parrot phylogeny, using the top
+ten highest ranked species without observed evidence of tool use as an arbitrary
+cutoff for visualisation purposes.
 
@@
 
-The predicted probabilities from our phylogenetic survival cure model have implications for inferences about the evolutionary drivers and origins of tool use in the parrot order.
-Regarding the drivers of tool use hypothesised in Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that encephalisation quotient strongly positively predicted the probability of tool use (median posterior log odds slope = 1.12, 95\% CI {[}0.39 2.00{]}; total \emph{n} = 174 species; Figure \ref{fig:plotSurvCure4}).
-This helps explain the ranking in Figure \ref{fig:plotSurvCure1}: the blue-eyed cockatoo has the largest relative brain size in the dataset.
-We also found that feeding generalist species were slightly more likely to be tool users, though the posterior difference between generalists and specialists was quite uncertain (median posterior log odds difference = 0.33, 95\% CI {[}-1.13 1.76{]}; total \emph{n} = 174 species).
-These results from the survival cure model differed from the results of models fitted to pre-video-survey and post-video-survey data without the survival cure component, which found no effect of relative brain size and no difference between feeding strategies, respectively (Supplementary Figure \ref{fig:plotComparison}).
+The predicted probabilities from our phylogenetic survival cure model have
+implications for inferences about the evolutionary drivers and origins of tool
+use in the parrot order. Regarding the drivers of tool use hypothesised in
+Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that
+encephalisation quotient strongly positively predicted the probability of tool
+use (median posterior log odds slope = 1.12, 95\%
+CI {[}0.39
+2.00{]}; total \emph{n} = 174
+species; Figure \ref{fig:plotSurvCure4}). This helps explain the ranking in
+Figure \ref{fig:plotSurvCure1}: the blue-eyed cockatoo has the largest relative
+brain size in the dataset. We also found that feeding generalist species were
+slightly more likely to be tool users, though the posterior difference between
+generalists and specialists was quite uncertain (median posterior log odds
+difference = 0.33, 95\% CI {[}
+-1.13 1.76{]}; total
+\emph{n} = 174 species). These results from the survival cure model
+differed from the results of models fitted to pre-video-survey and
+post-video-survey data without the survival cure component, which found no
+effect of relative brain size and no difference between feeding strategies,
+respectively (Supplementary Figure \ref{fig:plotComparison}).
 
@@
 \includegraphics{manuscript_files/figure-latex/plotSurvCure4-1.pdf}
-\caption{\label{fig:plotSurvCure4}\emph{Posterior predictions for the effects of feeding strategy and encephalisation quotient on the probability of tool use from the phylogenetic survival cure model.} In the left plot, points and lines represent posterior medians and 50\% and 95\% credible intervals, with densities representing full posterior distributions.
-In the right plot, the line and shaded area represents the posterior median regression line with 95\% credible intervals.
-In both plots, individual species are coloured according to the presence / absence of tool use in the video survey and the scientific literature.
-Total \emph{n} = 174 species, generalist \emph{n} = 121 species, specialist \emph{n} = 53 species.}
+\caption{\label{fig:plotSurvCure4}\emph{Posterior predictions for the effects of feeding
+strategy and encephalisation quotient on the probability of tool use from the
+phylogenetic survival cure model.} In the left plot, points and lines represent
+posterior medians and 50\% and 95\% credible intervals, with densities
+representing full posterior distributions. In the right plot, the line and
+shaded areas represent the posterior median regression line with 50\% and 95\%
+credible intervals. In both plots, individual species are coloured according to
+the presence / absence of tool use in the video survey and the scientific
+literature. Total \emph{n} = 174 species, generalist \emph{n} =
+121 species, specialist \emph{n} =
+53 species.}
 \end{figure}
 
-Regarding the origins of tool use, we fitted exploratory ancestral state reconstruction models to the pre-video-survey data, the post-video-survey data, and the predicted probabilities from the phylogenetic survival cure model.
-The discoveries from our video survey and from our phylogenetic modelling increased the likelihood that tool use was present in the most recent common ancestor for several parrot genera.
-These include the amazon parrots native to the Americas (\emph{Amazona}), the true white cockatoos and corellas found in South East Asia and Australasia (\emph{Cacatua}), the kea and the kākā from New Zealand (\emph{Nestor}), and the \emph{Poicephalus} genus native to Africa (Table \ref{tab:tableASR}; Supplementary Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}).
-These findings suggest that species from each of these genera share their tool use capabilities via common descent from their respective common ancestors, rather than via independent evolution within each genus.
+Regarding the origins of tool use, we fitted exploratory ancestral state
+reconstruction models to the pre-video-survey data, the post-video-survey data,
+and the predicted probabilities from the phylogenetic survival cure model. The
+discoveries from our video survey and from our phylogenetic modelling increased
+the likelihood that tool use was present in the most recent common ancestor for
+several parrot genera. These include the amazon parrots native to the Americas
+(\emph{Amazona}), the true white cockatoos and corellas found in South East Asia and
+Australasia (\emph{Cacatua}), the kea and the kākā from New Zealand (\emph{Nestor}), and
+the \emph{Poicephalus} genus native to Africa (Table \ref{tab:tableASR};
+Supplementary Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}). These findings
+suggest that species from each of these genera may share their tool use
+capabilities via common descent from their respective common ancestors, rather
+than via independent evolution within each genus or behavioural innovation
+within species.
 
@@
 
-Since the earliest anecdotal reports of parrots using tools in the 1970s\textsuperscript{60}, only 11 parrot species (3\% of all extant parrot species) have been documented as tool users in the scientific literature.
-Our study used crowdsourcing to identify 17 additional tool-using parrot species that are new to science, more than doubling the overall count to 28 species (7\%).
-These species consisted of cockatoos (Cacatuidae), Old World parrots (Psittacinae), and neotropical parrots (Arinae).
-
-We found strong phylogenetic signal in our extended dataset, demonstrating that the distribution of tool use across parrot species is affected by shared phylogenetic ancestry.
-This allowed us to use phylogenetic information, along with other variables, to infer the unobserved probabilities of tool use across the parrot order.
-Our phylogenetic survival cure model incorporated information on phylogenetic history, research effort, relative brain size, and feeding specialisation to rank parrot species that were most likely to be undetected tool users.
-The sum of probabilities from this model implied that between 15 and 41 of the species without observed evidence of tool use are likely to be undetected tool users, suggesting that the true proportion of tool users may be as high as 17\%.
-
-These findings have a number of important implications.
-First, our findings show that current research effort in the scientific literature is insufficient to capture the real world occurrence of parrot tool use.
-If the scientific literature had sampled the natural world sufficiently, we would expect to see close correspondence between those species reported as tool users in the literature and those species the public have filmed performing tool use.
-Instead, we discovered a large discrepancy between these two data sources, both in the prevalence of tool use and the species identified.
-This raises the possibility that insufficient research effort is a general issue across the scientific literature, both for tool use in other groups and for other rare behaviours.
-
-Second, in terms of the evolution of tool use in parrots, our study challenges a key assumption made in the literature to date: that only a minority of parrots are tool users\textsuperscript{30,31,34,37,38}.
-The paucity of evidence for tool use across parrots in the literature initially implied that tool use may have evolved independently in different parrot species.
-Our discovery of the widespread distribution of tool use across the parrot phylogeny, along with the strong phylogenetic signal in this expanded dataset, challenges this and suggests that, at least for some parrot clades, the capacity for tool use might be a homologous trait that has been evolutionarily conserved.
-Our exploratory ancestral state reconstruction analysis provides preliminary support for this hypothesis, revealing an increased probability of tool use among the most recent common ancestors for the \emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera.
-Even at this preliminary stage, our analysis therefore raises an alternative hypothesis for the observed tool use in \emph{Cacatua}\textsuperscript{30,38} and \emph{Nestor}\textsuperscript{26--29,31,34}, namely that tool behaviours have arisen due to the common ancestor being a tool user, rather than from behavioural innovation within a species.
-
-Third, our results support existing theories of the drivers of tool use.
-We found that encephalisation was strongly positively related to the probability of tool use in our phylogenetic model, supporting previous theories linking relative brain size to increased tool innovation in birds\textsuperscript{10--12} and primates\textsuperscript{61}.
-Nevertheless, we recognise that cross-species correlations between brain size and behaviour are challenging to interpret causally\textsuperscript{3,4}, and thus encourage further work on the specific neural correlates of technical intelligence in parrots (see e.g.\textsuperscript{62}).
-In our phylogenetic model, we also found that tool use was somewhat more likely among feeding generalists compared to feeding specialists, although this difference was uncertain.
-This trend supports previous suggestions that increased cognitive abilities and technical innovation rates are required to expand a generalist species' dietary niche\textsuperscript{15,17,63}.
-However, the trend contradicts theories linking tool use to dietary specialisation, whereby species eating specific foods that require extractive foraging have higher cognitive ability and are especially prone to using tools (reviewed in ref\textsuperscript{17}).
-
-We believe that the observations of tool use in our video survey reflect intentional tool use, rather than accidental object manipulations or trained behaviours.
-In the crowdsourcing video survey, individual parrots often used tools slowly and repetitively over long periods of time, even across multiple different videos, suggesting that their behaviour was not accidental\textsuperscript{64}.
-Moreover, for 60\% of the species we report on, we found two or more videos of repetitive and sustained scratching by different individuals in separate households.
-Following the assumption that accidental tool use (e.g., briefly holding an object and attempting to scratch oneself simultaneously) is rare\textsuperscript{65}, the repeated observation of the same tool use behaviours for scratching by multiple animals of the same species across multiple households suggests that these manipulations are intentional and recurring events rather than rare ``accidents'' and likely do not represent unusual stereotypies of a single individual.
-We also found little evidence to suggest that the tool use behaviours were trained or unintentionally cued by the birds' owners.
-Over half of the videos coded contained no evidence of human interference with the parrots' tool use aside from filming the behaviour.
-Humans only handed parrots their tools in two of the videos, and none of the videos featured owners directly rewarding tool use behaviours with food.
-Finally, and perhaps most importantly, the high levels of phylogenetic signal in our data provides strong evidence that the observations from our video survey reflect biologically-endowed capacities for tool use rather than accidents or trained behaviours, which would likely appear uniformly across the phylogeny.
-
-While missing data imputation is becoming more common in phylogenetic analyses\textsuperscript{66}, the important distinction between absence of evidence and evidence of absence has not been given as much attention.
-Our phylogenetic analysis provides one approach to this problem by distinguishing between true absences of tool use and absences of tool use due to a lack of research effort in the scientific literature or in crowdsourced videos.
-To achieve this, we explicitly modelled the measurement of the outcome variable along a research effort time series, such that species with lower research effort in the literature or in videos were likely to be censored.
-In line with our causal model, we also included relative brain size, feeding strategy, and phylogenetic history as predictors of unobserved tool use.
-We encourage researchers to test this model by directing future study efforts towards the parrot species with the highest probabilities of being undetected tool-users.
-Future work should also refine the causal model in Figure \ref{fig:plotDAG} to provide more certain estimates of tool use probabilities, either by including additional predictor variables or modelling further causes of measurement error in the taxonomic record, such as species abundance and geographic accessibility\textsuperscript{19}.
-
-In conclusion, we have shown that the scientific literature has insufficiently captured the full distribution of tool use in the parrot order.
-Our crowdsourcing survey has more than doubled the number of known tool using parrot species from 11 to 28, and our phylogenetic inference suggested that the true proportion of parrot tool users could be as high as 17\%.
-These discoveries have implications for theories of the evolutionary drivers and origins of tool use in parrots.
-Beyond parrot tool use, the crowdsourcing and phylogenetic methods used in this study have the potential to be applied to other rarely observed behaviours, including tool use in other taxa\textsuperscript{67}, rhythmic entrainment in birds\textsuperscript{68--71}, teasing behaviours in primates\textsuperscript{72}, and tactical deception across the animal kingdom\textsuperscript{73--75}.
-We hope that these methods will continue to uncover a diverse array of ephemeral behaviours that have as yet gone undetected in the scientific literature.
+Since the earliest anecdotes of parrots using tools by Wallace in the 1880s\textsuperscript{59} and more systematic anecdotal reports in the 1970s\textsuperscript{60},
+only 11 parrot species (3\% of all extant parrots) have been documented as tool
+users in the scientific literature. Our study used crowdsourcing to identify 17
+additional tool-using parrot species that are new to science, more than doubling
+the overall count to 28 species (7\%). These species consisted of cockatoos
+(\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), and neotropical parrots
+(\emph{Arinae}). Beyond the crowdsourcing survey, the strong phylogenetic signal in
+our dataset allowed us to use phylogenetic information, along with other
+variables, to infer the unobserved probabilities of tool use across the parrot
+order. Our phylogenetic survival cure model incorporated information on
+phylogenetic history, research effort, relative brain size, and feeding
+specialisation to rank parrot species that were most likely to be undetected
+tool users. The sum of probabilities from this model implied that between 15
+and 41 of the species without observed evidence of tool use are likely to be
+undetected tool users, suggesting that the true proportion of tool users may be
+as high as 17\%.
+
+These findings have a number of important implications. First, our findings show
+that current research effort in the scientific literature is insufficient to
+capture the real world occurrence of parrot tool use. If the scientific
+literature had sampled the natural world sufficiently, we would expect to see
+close correspondence between those species reported as tool users in the
+literature and those species the public have filmed performing tool use.
+Instead, we discovered a large discrepancy between these two data sources, both
+in the prevalence of tool use and the species identified. This raises the
+possibility that insufficient research effort is a general issue across the
+scientific literature, both for tool use in other groups and for other rare
+behaviours.
+
+Second, in terms of the evolution of tool use in parrots, our study challenges a
+key assumption made in the literature to date: that only a minority of parrots
+are tool users\textsuperscript{30,31,34,37,38}.
+The paucity of evidence for tool use across parrots in the literature initially
+implied that the capacity for tool use may have evolved independently in
+different parrot species. Our discovery of the widespread distribution of tool
+use across the parrot phylogeny, along with the strong phylogenetic signal in
+this expanded dataset, challenges this and suggests that, at least for some
+parrot clades, the capacity for tool use might be a homologous trait that has
+been evolutionarily conserved. Our exploratory ancestral state reconstruction
+analysis provides preliminary support for this hypothesis, revealing an
+increased probability of tool use among the most recent common ancestors for the
+\emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera. Even at this
+preliminary stage, our analysis therefore raises an alternative hypothesis for
+the observed tool use in \emph{Cacatua}\textsuperscript{30,38} and
+\emph{Nestor}\textsuperscript{26--29,31,34}, namely that tool behaviours have arisen due to the
+common ancestor having the capacity to use tools, rather than from independent
+evolution or behavioural innovation within species.
+
+Third, our results support existing theories of the drivers of tool use. We
+found that encephalisation was strongly positively related to the probability of
+tool use in our phylogenetic model, supporting previous theories linking
+relative brain size to increased tool innovation in birds\textsuperscript{11--13} and primates\textsuperscript{61}. We acknowledge that
+encephalisation quotient is not a perfect measure due to measurement error and
+challenges with interpretation\textsuperscript{3,4}. However, encephalisation
+quotient has much greater coverage across the parrot phylogeny than more
+fine-grained measures like whole neuron count\textsuperscript{62} and there is no reason
+to think that measurement error would produce the consistent patterns across our
+study and prior work. To understand the causal mechanisms responsible for these
+relationships, we encourage further work on the specific neural correlates of
+technical intelligence in parrots, e.g.,\textsuperscript{63}. In our phylogenetic
+model, we also found that tool use was somewhat more likely among feeding
+generalists compared to feeding specialists, although this difference was
+uncertain. This trend supports previous suggestions that increased cognitive
+abilities and technical innovation rates are required to expand a generalist
+species' dietary niche\textsuperscript{16,18,64}. However, the trend contradicts theories linking tool use to
+dietary specialisation, whereby species eating specific foods that require
+extractive foraging have higher cognitive ability and are especially prone to
+using tools\textsuperscript{18}.
+
+All instances of tool use in our crowdsourcing survey met the established
+criteria for tool use in the literature: the manipulation of an unattached
+object as an extension of the animal's body to achieve a goal\textsuperscript{10}.
+However, a striking feature of the dataset is that the 17 additional species
+identified in the video survey were exclusively observed using tools for
+self-scratching. While parrots in the wild use tools to achieve a variety of
+goals, including extractive foraging and preening\textsuperscript{34,38},
+parrots in captivity only require tools to achieve the latter goal. Despite this
+difference in the type of tool use observed, self-scratching is nonetheless a
+major category of animal tool use. Self-scratching also meets the definition for
+a more complex type of embodied tool use known as `tooling', the deliberate
+generation of a mechanical interface by using an object to manipulate another
+target or surface\textsuperscript{65}. The fact that we found strong phylogenetic
+clustering of self-scratching tool use from the video survey with other examples
+of tool use from the literature supports a common underlying cognitive
+mechanism. In line with this, some of the species of parrots that use tools for
+self-scratching in captivity also use tools for other purposes in the wild\textsuperscript{30,31,34,38}.
+
+There was little evidence to suggest that the observations of self-scratching
+tool use in the video survey were merely unintentional accidents or explicitly
+trained behaviours. Individual parrots often used tools slowly and repetitively
+over long periods of time, even across multiple different videos, suggesting
+that their behaviour was not random or accidental\textsuperscript{66}. Parrots
+preferentially employed self-scratching tools on areas of their body that were
+otherwise inaccessible, with 96\% of all instances involving scratching of the
+head or neck, suggesting intentional tool use. For 60\% of the species in the
+video survey, we found two or more videos of repetitive and sustained scratching
+by different individuals of the same species in separate households, suggesting
+that the manipulations were intentional and recurring events that did not
+represent unusual stereotypies of any single individual. Regarding the
+possibility of training or cueing from owners, over half of the videos contained
+no evidence of human interaction aside from filming the behaviour. Humans only
+handed parrots their tools in two of the videos, and none of the videos featured
+owners directly rewarding tool use behaviours with food. Finally, the high
+levels of phylogenetic signal in our data provide strong evidence that the
+observations from our video survey reflect biologically-endowed capacities for
+tool use rather than accidental or trained behaviours, which would likely appear
+uniformly across the phylogeny.
+
+While missing data imputation is becoming more common in phylogenetic
+analyses\textsuperscript{67}, the important distinction between absence of
+evidence and evidence of absence has not been given as much attention. Our
+phylogenetic analysis provides one approach to this problem by distinguishing
+between true absences of tool use and absences of tool use due to a lack of
+research effort in the scientific literature or in crowdsourced videos. To
+achieve this, we explicitly modelled the measurement of the outcome variable
+along a research effort time series, such that species with lower research
+effort in the literature or in videos were likely to be censored. In line with
+our causal model, we also included relative brain size, feeding strategy, and
+phylogenetic history as predictors of unobserved tool use. We encourage
+researchers to test this model by directing future study efforts towards the
+parrot species with the highest probabilities of being undetected tool-users.
+Future work should also refine the causal model in Figure \ref{fig:plotDAG} to
+provide more certain estimates of tool use probabilities, either by including
+additional predictor variables or modelling further causes of measurement error
+in the taxonomic record, such as species abundance and geographic
+accessibility\textsuperscript{20}.
+
+In conclusion, we have shown that the scientific literature has insufficiently
+captured the full distribution of tool use in the parrot order. Our
+crowdsourcing survey more than doubled the number of known tool using parrot
+species from 11 to 28, and our phylogenetic model suggested that the true
+proportion of parrot tool users could be as high as 17\% of all species in this
+order. These discoveries have implications for theories of the evolutionary
+drivers and origins of tool use in parrots. Beyond parrot tool use, the
+crowdsourcing and phylogenetic methods used in this study have the potential to
+be applied to other rarely observed behaviours, including tool use in other
+taxa\textsuperscript{68}, rhythmic entrainment in birds\textsuperscript{69--72}, teasing behaviours in primates\textsuperscript{73}, and
+tactical deception across all animals\textsuperscript{74--76}.
+We hope that these methods will continue to uncover a diverse array of ephemeral
+behaviours that have as yet gone undetected in the scientific literature.
 
@@
 
-Our video search was conducted on YouTube in July 2020.
-Search terms included ``parrot using tool'' and variants (e.g., ``macaw using tool'', ``lorikeet using tool'', ``parakeet using tool''), ``tool use in parrot'', ``parrot tool use'', ``parrot scratching itself'' (included after we found several videos demonstrating self-care tool use in previous searches) and equivalent terms (e.g., ``parrot preening itself'', ``parrot grooming itself'', ``parrot scratching'').
-For all species that did not display results including object manipulation or scratching behaviours, we also searched the species' common name(s) + ``tool use'', as well as the species' common name(s) + ``scratching''.
-We also searched for translations of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all countries where bird ownership was reported as \textgreater5\%\textsuperscript{76}, namely, Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, Portuguese, and Mandarin.
-
-When we found a relevant video, we also searched for similar content uploaded by the same person/channel.
-For each YouTube search conducted, we watched all relevant videos until we reached five consecutive videos that did not feature any parrots.
-At this point, we ended that search and initiated the next search.
-In line with previous recommendations\textsuperscript{20}, we planned to exclude any videos that consisted of four or more shots edited together so as to ensure the behaviours being observed were not edited or manipulated, but none of the videos obtained qualified for exclusion.
-
-All videos featuring parrots manipulating objects were investigated for potential tool use or borderline tool use.
-We defined tool use as the manipulation of an unattached object as an extension of the beak or foot to achieve a goal towards another object, individual, or oneself\textsuperscript{55}.
-Borderline tool use was similarly defined, except that it involved the use of an object that was still attached to a substrate\textsuperscript{56}.
-For example, if individuals used a fallen feather or stick for self-scratching this was defined as tool use, but using one's currently attached tail feathers or cage furnishings for the same purpose was defined as borderline tool use.
-Self-scratching had to involve slow and repeated movements of touching an object to one's body (or, in the case of borderline tool use, rubbing repetitively against an attached object\textsuperscript{64}).
-
-All relevant videos were coded for video length, species, tool use presence (yes/borderline), tool use type (e.g., scratching, feeding), the object being used (e.g., feather, stick), tool use target, human interference with the action (talking or handing object to parrot, holding parrot), and the number of shots within each video.
-Our complete dataset also includes the name for each video, link, subject name, sex (as declared by owner, as most parrot species are not sexually dimorphic), publishing date, and dates found and coded.
+Our video search was conducted on YouTube in July 2020. Search terms included
+``parrot using tool'' and variants (e.g., ``macaw using tool'', ``lorikeet using
+tool'', ``parakeet using tool''), ``tool use in parrot'', ``parrot tool use'', ``parrot
+scratching itself'' (included after we found several videos demonstrating
+self-care tool use in previous searches) and equivalent terms (e.g., ``parrot
+preening itself'', ``parrot grooming itself'', ``parrot scratching''). For all
+species that did not display results including object manipulation or scratching
+behaviours, we also searched the species' common name(s) + ``tool use'', as well
+as the species' common name(s) + ``scratching''. We also searched for translations
+of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all
+countries where bird ownership was reported as \textgreater5\%\textsuperscript{77}, namely,
+Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish,
+Portuguese, and Mandarin.
+
+When we found a relevant video, we also searched for similar content uploaded by
+the same person/channel. For each YouTube search conducted, we watched all
+relevant videos until we reached five consecutive videos that did not feature
+any parrots. At this point, we ended that search and initiated the next search.
+In line with previous recommendations\textsuperscript{21}, we planned to exclude any
+videos that consisted of four or more shots edited together so as to ensure the
+behaviours being observed were not edited or manipulated, but none of the videos
+obtained qualified for exclusion.
+
+All videos featuring parrots manipulating objects were investigated for
+potential tool use or borderline tool use. We defined tool use as the
+manipulation of an unattached object as an extension of the beak or foot to
+achieve a goal towards another object, individual, or oneself\textsuperscript{10}.
+Borderline tool use was similarly defined, except that it involved the use of an
+object that was still attached to a substrate\textsuperscript{54}. For example, if
+individuals used a fallen feather or stick for self-scratching this was defined
+as tool use, but using one's currently attached tail feathers or cage
+furnishings for the same purpose was defined as borderline tool use.
+Self-scratching had to involve slow and repeated movements of touching an object
+to one's body (or, in the case of borderline tool use, rubbing repetitively
+against an attached object\textsuperscript{66}).
+
+All relevant videos were coded for video length, species, tool use presence
+(yes/borderline), tool use type (e.g., scratching, feeding), the object being
+used (e.g., feather, stick), tool use target, human interaction
+(talking or handing object to parrot, holding parrot), and the number of shots
+within each video. Our complete dataset also includes the name for each video,
+link, subject name, sex (as declared by owner, as most parrot species are not
+sexually dimorphic), publishing date, and dates found and coded.
 
@@
 
-We collected data for 194 parrot species (Supplementary Figures \ref{fig:plotPhylo2} - \ref{fig:plotPhylo4}).
-We gathered feeding strategy data as a dichotomous variable (``generalist'' or ``specialist'') from the EltonTraits ecological database\textsuperscript{53}.
-As per the database, specialists were defined as species whose diet comprised at least 70\% of a single food source.
-To calculate relative brain size, we collated data from the literature for all known body mass (g) and brain mass (g) values across parrots\textsuperscript{47--52}.
-For all species for which we obtained body and brain mass data, we calculated the encephalisation quotient (EQ) using the following formula\textsuperscript{77}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\).
-We found body mass and brain mass data for a total of 194 parrot species.
-This included all tool-using species in our video dataset, with the exception of three species: \emph{Diopsittaca nobilis}, \emph{Psittacara erythrogenys}, and \emph{Coracopsis vasa}.
-For the latter, we used values for the closely related \emph{Coracopsis nigra}.
-The other two species were excluded from the final dataset.
-
-For modelling purposes, we coded research effort in both the scientific literature and the crowdsourced videos.
-For the scientific literature, we operationalised research effort as the number of papers published for each species' Latin name up to and including the first paper containing tool use for that species.
-If no tool use had been identified in the scientific literature for a species, then we coded the total number of papers published to date.
-We used the scientific database Scopus for coding the number of published papers.
-For the crowdsourced videos, we coded research effort as the number of search hits for each species on YouTube.
-If tool use had been identified on YouTube, we estimated the number of search hits when the first video of tool use was published on YouTube, assuming linear growth of search hits since the inception of YouTube.
-If tool use had not been identified, we used the current number of search hits.
-
-For phylogenetic data, we used the phylogenetic tool at www.birdtree.org\textsuperscript{54} to compile 1000 posterior draws of phylogenetic trees for 174 of the 194 parrot species for which both EQ and genomic data exist.
-A single maximum clade credibility tree was generated from these posterior draws for visualisation purposes.
-In our analyses, we iterated over posterior draws of the phylogeny to account for phylogenetic uncertainty.
+We collected data for 194 parrot species (Supplementary Figures
+\ref{fig:plotPhylo2} - \ref{fig:plotPhylo4}). We gathered feeding strategy
+data as a dichotomous variable (``generalist'' or ``specialist'') from the
+EltonTraits ecological database\textsuperscript{52}. As per the database, specialists
+were defined as species whose diet comprised at least 70\% of a single food
+source. To calculate relative brain size, we collated data from the literature
+for all known body mass (g) and brain mass (g) values across
+parrots\textsuperscript{46--51}. For all species for which we obtained body and brain mass data, we
+calculated the encephalisation quotient (EQ) using the following
+formula\textsuperscript{78}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
+found body mass and brain mass data for a total of 194 parrot species. This
+included all tool-using species in our video dataset, with the exception of
+three species: \emph{Diopsittaca nobilis}, \emph{Psittacara erythrogenys}, and \emph{Coracopsis
+vasa}. For the latter, we used values for the closely related \emph{Coracopsis
+nigra}. The other two species were excluded from the final dataset.
+
+For modelling purposes, we coded research effort in both the scientific
+literature and the crowdsourced videos. For the scientific literature, we
+operationalised research effort as the number of papers published for each
+species' Latin name up to and including the first paper containing tool use for
+that species. If no tool use had been identified in the scientific literature
+for a species, then we coded the total number of papers published to date. We
+used the scientific database Scopus for coding the number of published papers.
+For the crowdsourced videos, we coded research effort as the number of search
+hits for each species on YouTube. If tool use had been identified on YouTube, we
+estimated the number of search hits when the first video of tool use was
+published on YouTube, assuming linear growth of search hits since the inception
+of YouTube. If tool use had not been identified, we used the current number of
+search hits.
+
+For phylogenetic data, we used the phylogenetic tool at www.birdtree.org\textsuperscript{53} to compile 1000 posterior draws of phylogenetic trees for 174 of the
+194 parrot species for which both EQ and genomic data exist. A single maximum
+clade credibility tree was generated from these posterior draws for
+visualisation purposes. In our analyses, we iterated over posterior draws of the
+phylogeny to account for phylogenetic uncertainty.
 
@@
 
-We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{78} to calculate phylogenetic signal, for both the pre-survey and post-survey tool use data.
-We iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
+We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{79} to
+calculate phylogenetic signal, for both the pre-survey and post-survey tool use
+data. We iterated the model over 100 posterior parrot phylogenies to incorporate
+phylogenetic uncertainty.
 
@@
 
-To infer unobserved probabilities of tool use across parrots, we proposed a causal model of observed tool use (Figure \ref{fig:plotDAG}).
-We assumed that observed tool use in the scientific literature and in the crowdsourced videos is caused by both the unobserved presence or absence of tool use and research effort, proxied by the number of papers published on a species and the number of videos published on a species.
-Tool users are more likely to be observed if they are well studied, but understudied tool users may go undetected.
-In addition, based on theory, we also assumed that unobserved tool use is caused by feeding strategy and relative brain size\textsuperscript{10--13,15--17}.
-Finally, we assumed that shared phylogenetic history causes unobserved confounding and non-independence in unobserved tool use, feeding strategy, and relative brain size across the parrot phylogeny.
+To infer unobserved probabilities of tool use across parrots, we proposed a
+causal model of observed tool use (Figure \ref{fig:plotDAG}). We assumed that
+observed tool use in the scientific literature and in the crowdsourced videos is
+caused by both the unobserved presence or absence of tool use and research
+effort, proxied by the number of papers published on a species and the number of
+videos published on a species. Tool users are more likely to be observed if they
+are well studied, but understudied tool users may go undetected. In addition,
+based on theory, we also assumed that unobserved tool use is caused by feeding
+strategy and relative brain size\textsuperscript{11--14,16--18}. Finally, we
+assumed that shared phylogenetic history causes unobserved confounding and
+non-independence in unobserved tool use, feeding strategy, and relative brain
+size across the parrot phylogeny.
 
@@
 
-The Exponential-CCDF function allows for the censored nature of the data. The same data generating process is assumed to underlie the crowdsourced videos.
-
-We define the mixture likelihood \(\text{SurvivalCure}\) as the distribution above, with parameters \(p\) (the probability of being a ``cured'' non-tool-user) and \(\lambda\) (the rate of the exponential distribution).
-We use an Ornstein-Uhlenbeck Gaussian process\textsuperscript{79} to model phylogenetic covariance.
-Below, we specify the full model with priors:
+The Exponential-CCDF function allows for the censored nature of the data. The
+same data generating process is assumed to underlie the crowdsourced videos.
+
+We define the mixture likelihood \(\text{SurvivalCure}\) as the distribution
+above, with parameters \(p\) (the probability of being a non-tool-user)
+and \(\lambda\) (the rate of the exponential distribution). We use an
+Ornstein-Uhlenbeck Gaussian process\textsuperscript{80} to model phylogenetic
+covariance. Below, we specify the full model with priors:
 
@@
 
-The priors for this model produce reasonable prior predictions of the probabilities of tool use for each parrot species (Supplementary Figure \ref{fig:plotSurvCure7}), but a sensitivity analysis revealed that the ranking and posterior probabilities reported in the main text were robust to modifying these priors (Supplementary Figure \ref{fig:plotSurvCure8}).
-We estimated the posterior distribution of this model using Hamiltonian Monte Carlo as implemented in Stan version 2.26.1\textsuperscript{80}.
-We ran the model for 4000 samples, with 2000 warmup samples, and iterated the model over 100 posterior parrot phylogenies to incorporate phylogenetic uncertainty.
-R-hat values and effective sample sizes suggested that the model converged normally.
-Trace plots are reported in Supplementary Figure \ref{fig:plotTrace}.
-We report equal-tailed credible intervals to describe the posterior distribution of this model in the main text.
-
-To validate our method, we fitted the model to 100 simulated datasets with known parameters.
-The model was able to successfully recover those parameters (Supplementary Figure \ref{fig:plotSurvCureSim}).
-We also ran a leave-one-species-out exercise to ensure that we could accurately predict known tool users.
-We repeated this approach for each known tool user by setting observed tool use to zero.
-Cross-validation results are reported in the main text.
+The priors for this model produce reasonable prior predictions of the
+probabilities of tool use for each parrot species (Supplementary Figure
+\ref{fig:plotSurvCure7}), but a sensitivity analysis revealed that the ranking
+and posterior probabilities reported in the main text were robust to modifying
+these priors (Supplementary Figure \ref{fig:plotSurvCure8}). We estimated the
+posterior distribution of this model using Hamiltonian Monte Carlo as
+implemented in Stan version 2.26.1\textsuperscript{81}. We ran the model for 4000
+samples, with 2000 warmup samples, and iterated the model over 100 posterior
+parrot phylogenies to incorporate phylogenetic uncertainty. R-hat values and
+effective sample sizes suggested that the model converged normally. Trace plots
+are reported in Supplementary Figure \ref{fig:plotTrace}. We report
+equal-tailed credible intervals to describe the posterior distribution of this
+model in the main text.
+
+To validate our method, we fitted the model to 100 simulated datasets with known
+parameters. The model was able to successfully recover those parameters
+(Supplementary Figure \ref{fig:plotSurvCureSim}). We also ran a
+leave-one-species-out exercise to ensure that we could accurately predict known
+tool users. We repeated this approach for each known tool user by setting
+observed tool use to zero. Cross-validation results are reported in the main
+text.
 
@@
 
-To determine whether the identification of novel tool-using species has implications for our understanding of the evolutionary origins of tool use in parrots, we fitted three exploratory ancestral state reconstruction models.
-We used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{81}, iterating the function over 100 posterior parrot phylogenies.
-This function estimates discrete ancestral states by assuming the evolution of a latent continuous variable following an Ornstein-Uhlenbeck process.
-We fitted this model to three different outcome variables: (\emph{i}) presence vs.~absence of tool use in scientific literature only, (\emph{ii}) presence vs.~absence of tool use in literature and/or videos, and (\emph{iii}) the median predicted probabilities of tool use from the phylogenetic survival cure model.
+To determine whether the identification of novel tool-using species has
+implications for our understanding of the evolutionary origins of tool use in
+parrots, we fitted three exploratory ancestral state reconstruction models. We
+used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{82},
+iterating the function over 100 posterior parrot phylogenies. This function
+estimates discrete ancestral states by assuming the evolution of a latent
+continuous variable following an Ornstein-Uhlenbeck process. We fitted this
+model to three different outcome variables: (\emph{i}) presence vs.~absence of tool
+use in scientific literature only, (\emph{ii}) presence vs.~absence of tool use in
+literature and/or videos, and (\emph{iii}) the median predicted probabilities of tool
+use from the phylogenetic survival cure model.
 
@@
 
-All analyses were conducted in R v4.2.1.\textsuperscript{82}.
-Visualisations were produced using the \emph{ggplot2}\textsuperscript{83} and \emph{cowplot}\textsuperscript{84} packages.
-The manuscript was reproducibly generated using the \emph{targets}\textsuperscript{85} and \emph{papaja}\textsuperscript{86} packages.
-Code to reproduce all analyses and figures can be found here: \url{https://github.com/ScottClaessens/phyloParrot}
+All analyses were conducted in R v4.2.1.\textsuperscript{83}. Visualisations were
+produced using the \emph{ggtree}\textsuperscript{84}, \emph{ggplot2}\textsuperscript{85}, and \emph{cowplot}\textsuperscript{86} packages. The manuscript was reproducibly generated using the
+\emph{targets}\textsuperscript{87} and \emph{papaja}\textsuperscript{88} packages. Code to reproduce all
+analyses and figures can be found here:
+\url{https://github.com/ScottClaessens/phyloParrot}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Shumaker, R.
+W., Walkup, K.
+R., Beck, B.
+B.
+\& Burghardt, G.
+M.
+\emph{Animal tool behavior: The use and manufacture of tools by animals}.
+(Johns Hopkins University Press).
+doi:\href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2002}{}}%
-\CSLLeftMargin{10. }%
+\CSLLeftMargin{11. }%
 \CSLRightInline{Lefebvre, L., Nicolakakis, N. \& Boire, D. \href{https://doi.org/10.1163/156853902320387918}{Tools and brains in birds}. \emph{Behaviour} \textbf{139}, 939--973 (2002).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lefebvre1997}{}}%
-\CSLLeftMargin{11. }%
+\CSLLeftMargin{12. }%
 \CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2004}{}}%
-\CSLLeftMargin{12. }%
+\CSLLeftMargin{13. }%
 \CSLRightInline{Lefebvre, L., Reader, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sol2005}{}}%
-\CSLLeftMargin{13. }%
+\CSLLeftMargin{14. }%
 \CSLRightInline{Sol, D., Duncan, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sol2009}{}}%
-\CSLLeftMargin{14. }%
+\CSLLeftMargin{15. }%
 \CSLRightInline{Sol, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ducatez2015}{}}%
-\CSLLeftMargin{15. }%
+\CSLLeftMargin{16. }%
 \CSLRightInline{Ducatez, S., Clavel, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Overington2011}{}}%
-\CSLLeftMargin{16. }%
+\CSLLeftMargin{17. }%
 \CSLRightInline{Overington, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2020}{}}%
-\CSLLeftMargin{17. }%
+\CSLLeftMargin{18. }%
 \CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MettkeHofmann2014}{}}%
-\CSLLeftMargin{18. }%
+\CSLLeftMargin{19. }%
 \CSLRightInline{Mettke-Hofmann, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Ducatez2014}{}}%
-\CSLLeftMargin{19. }%
+\CSLLeftMargin{20. }%
 \CSLRightInline{Ducatez, S. \& Lefebvre, L. \href{https://doi.org/10.1371/journal.pone.0089955}{Patterns of research effort in birds}. \emph{PLOS ONE} \textbf{9}, e89955 (2014).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Nelson2013}{}}%
-\CSLLeftMargin{20. }%
+\CSLLeftMargin{21. }%
 \CSLRightInline{Nelson, X.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Dickinson2010}{}}%
-\CSLLeftMargin{21. }%
+\CSLLeftMargin{22. }%
 \CSLRightInline{Dickinson, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
-\CSLLeftMargin{22. }%
+\CSLLeftMargin{23. }%
 \CSLRightInline{Krueger, K., Esch, L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Klump2021}{}}%
-\CSLLeftMargin{23. }%
+\CSLLeftMargin{24. }%
 \CSLRightInline{Klump, B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Klump2022}{}}%
-\CSLLeftMargin{24. }%
+\CSLLeftMargin{25. }%
 \CSLRightInline{Klump, B.
@@
 \emph{Current Biology} \textbf{32}, R910--R911 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Burgio2019}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Burgio, K.
-R.
-\emph{et al.} \href{https://doi.org/10.1016/j.dib.2019.103882}{Phylogenetic supertree and functional trait database for all extant parrots}.
-\emph{Data in Brief} \textbf{24}, 103882 (2019).}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kleinberger2023}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
 \CSLLeftMargin{39. }%
-\CSLRightInline{Kleinberger, R., Cunha, J., Vemuri, M.
-M.
-\& Hirskyj-Douglas, I.
-Birds of a feather video-flock together: Design and evaluation of an agency-based parrot-to-parrot video-calling system for interspecies ethical enrichment.
-in \emph{Proceedings of the 2023 CHI conference on human factors in computing systems} (Association for Computing Machinery, 2023).
-doi:\href{https://doi.org/10.1145/3544548.3581166}{10.1145/3544548.3581166}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
-\CSLLeftMargin{40. }%
 \CSLRightInline{Anderson, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
-\CSLLeftMargin{41. }%
+\CSLLeftMargin{40. }%
 \CSLRightInline{Carrete, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
-\CSLLeftMargin{42. }%
+\CSLLeftMargin{41. }%
 \CSLRightInline{Drews, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
-\CSLLeftMargin{43. }%
+\CSLLeftMargin{42. }%
 \CSLRightInline{Kelly, D., McCarthy, E., Menzel, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{Li, L. \& Jiang, Z. \href{https://doi.org/10.1371/journal.pone.0085012}{International trade of {CITES} listed bird species in {C}hina}. \emph{PLOS ONE} \textbf{9}, 1--8 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
 \CSLLeftMargin{44. }%
-\CSLRightInline{Li, L. \& Jiang, Z. \href{https://doi.org/10.1371/journal.pone.0085012}{International trade of {CITES} listed bird species in {C}hina}. \emph{PLOS ONE} \textbf{9}, 1--8 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
-\CSLLeftMargin{45. }%
 \CSLRightInline{Su, S., Cassey, P., Vall-llosera, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
-\CSLLeftMargin{46. }%
+\CSLLeftMargin{45. }%
 \CSLRightInline{Young, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
-\CSLLeftMargin{47. }%
+\CSLLeftMargin{46. }%
 \CSLRightInline{Flammer, K., Whitt-Smith, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
-\CSLLeftMargin{48. }%
+\CSLLeftMargin{47. }%
 \CSLRightInline{Iwaniuk, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
-\CSLLeftMargin{49. }%
+\CSLLeftMargin{48. }%
 \CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
-\CSLLeftMargin{50. }%
+\CSLLeftMargin{49. }%
 \CSLRightInline{Olkowicz, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
-\CSLLeftMargin{51. }%
+\CSLLeftMargin{50. }%
 \CSLRightInline{Schuck-Paim, C., Alonso, W.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
-\CSLLeftMargin{52. }%
+\CSLLeftMargin{51. }%
 \CSLRightInline{Silva, T., Guzmán, A., Urantówka, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
-\CSLLeftMargin{53. }%
+\CSLLeftMargin{52. }%
 \CSLRightInline{Wilman, H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
+\CSLLeftMargin{53. }%
+\CSLRightInline{Jetz, W., Thomas, G. H., Joy, J. B., Hartmann, K. \& Mooers, A. O. The global diversity of birds in space and time. \emph{Nature} \textbf{491}, 444--448 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
 \CSLLeftMargin{54. }%
-\CSLRightInline{Jetz, W., Thomas, G. H., Joy, J. B., Hartmann, K. \& Mooers, A. O. The global diversity of birds in space and time. \emph{Nature} \textbf{491}, 444--448 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
+\CSLRightInline{Seed, A. \& Byrne, R. \href{https://doi.org/10.1016/j.cub.2010.09.042}{Animal tool-use}. \emph{Current Biology} \textbf{20}, R1032--R1039 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
 \CSLLeftMargin{55. }%
-\CSLRightInline{Shumaker, R.
-W., Walkup, K.
-R., Beck, B.
-B.
-\& Burghardt, G.
-M.
-\emph{Animal tool behavior: The use and manufacture of tools by animals}.
-(Johns Hopkins University Press).
-doi:\href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
+\CSLRightInline{Bercovitz, A. B. Avian sex identification techniques. in \emph{Companion bird medicine} (ed. Burr, E. W.) (Iowa State University Press, 1987).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
 \CSLLeftMargin{56. }%
-\CSLRightInline{Seed, A. \& Byrne, R. \href{https://doi.org/10.1016/j.cub.2010.09.042}{Animal tool-use}. \emph{Current Biology} \textbf{20}, R1032--R1039 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
+\CSLRightInline{Hoyo, J. D. \& Bierregaard, R. \emph{Handbook of the birds of the world}. (Lynx Edicions, 2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
 \CSLLeftMargin{57. }%
-\CSLRightInline{Bercovitz, A. B. Avian sex identification techniques. in \emph{Companion bird medicine} (ed. Burr, E. W.) (Iowa State University Press, 1987).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Hoyo, J. D. \& Bierregaard, R. \emph{Handbook of the birds of the world}. (Lynx Edicions, 2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
-\CSLLeftMargin{59. }%
 \CSLRightInline{Amico, M.
@@
 \emph{Annual Review of Statistics and Its Application} \textbf{5}, 311--342 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
+\CSLLeftMargin{58. }%
+\CSLRightInline{Schmidt, P.
+\& Witte, A.
+D.
+\href{https://doi.org/10.1016/0304-4076(89)90034-1}{Predicting criminal recidivism using {`split population'} survival time models}.
+\emph{Journal of Econometrics} \textbf{40}, 141--159 (1989).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
+\CSLLeftMargin{59. }%
+\CSLRightInline{Wallace, A.
+R.
+\emph{The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature}.
+(MacMillan; Co., 1869).}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
+\CSLLeftMargin{62. }%
+\CSLRightInline{Sol, D. \emph{et al.} Neuron numbers link innovativeness with both absolute and relative brain size in birds. \emph{Nature Ecology \& Evolution} \textbf{6}, 1381--1389 (2022).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
-\CSLLeftMargin{62. }%
+\CSLLeftMargin{63. }%
 \CSLRightInline{Cabrera-Álvarez, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
-\CSLLeftMargin{63. }%
+\CSLLeftMargin{64. }%
 \CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
+\CSLLeftMargin{65. }%
+\CSLRightInline{Fragaszy, D. M. \& Mangalam, M. \href{https://doi.org/10.1016/bs.asb.2018.01.001}{Tooling}. in (eds. Naguib, M. et al.) vol. 50 177--241 (Academic Press, 2018).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{64. }%
+\CSLLeftMargin{66. }%
 \CSLRightInline{Sándor, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2020}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Schwing, R., Mioduszewska, B., O'Hara, M.
-\& Huber, L.
-\href{https://doi.org/10.1073/pnas.2001988117}{Do puffins use tools?} \emph{Proceedings of the National Academy of Sciences} \textbf{117}, 11859--11859 (2020).}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
-\CSLLeftMargin{66. }%
+\CSLLeftMargin{67. }%
 \CSLRightInline{Debastiani, V.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
-\CSLLeftMargin{67. }%
+\CSLLeftMargin{68. }%
 \CSLRightInline{Hunt, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
-\CSLLeftMargin{68. }%
+\CSLLeftMargin{69. }%
 \CSLRightInline{Benichov, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
-\CSLLeftMargin{69. }%
+\CSLLeftMargin{70. }%
 \CSLRightInline{Patel, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
-\CSLLeftMargin{70. }%
+\CSLLeftMargin{71. }%
 \CSLRightInline{ten Cate, C., Spierings, M., Hubert, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
-\CSLLeftMargin{71. }%
+\CSLLeftMargin{72. }%
 \CSLRightInline{Wilson, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
-\CSLLeftMargin{72. }%
+\CSLLeftMargin{73. }%
 \CSLRightInline{Eckert, J., Winkler, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
-\CSLLeftMargin{73. }%
+\CSLLeftMargin{74. }%
 \CSLRightInline{Bro-Jørgensen, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
-\CSLLeftMargin{74. }%
+\CSLLeftMargin{75. }%
 \CSLRightInline{Byrne, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
-\CSLLeftMargin{75. }%
+\CSLLeftMargin{76. }%
 \CSLRightInline{Byrne, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
-\CSLLeftMargin{76. }%
+\CSLLeftMargin{77. }%
 \CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership}. (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
-\CSLLeftMargin{77. }%
+\CSLLeftMargin{78. }%
 \CSLRightInline{Jerison, H. J. \emph{Evolution of the brain and intelligence}. (Academic Press, 1973).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
-\CSLLeftMargin{78. }%
+\CSLLeftMargin{79. }%
 \CSLRightInline{Paradis, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
-\CSLLeftMargin{79. }%
+\CSLLeftMargin{80. }%
 \CSLRightInline{McElreath, R. \emph{\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition}}. (CRC Press, 2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
-\CSLLeftMargin{80. }%
+\CSLLeftMargin{81. }%
 \CSLRightInline{Stan Development Team. \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}. (2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
-\CSLLeftMargin{81. }%
+\CSLLeftMargin{82. }%
 \CSLRightInline{Revell, L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
-\CSLLeftMargin{82. }%
+\CSLLeftMargin{83. }%
 \CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2022).}
 
+\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
+\CSLLeftMargin{84. }%
+\CSLRightInline{Yu, G., Smith, D., Zhu, H., Guan, Y.
+\& Lam, T.
+T.-Y.
+\href{https://doi.org/10.1111/2041-210X.12628}{{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data}.
+\emph{Methods in Ecology and Evolution} \textbf{8}, 28--36 (2017).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-\CSLLeftMargin{83. }%
+\CSLLeftMargin{85. }%
 \CSLRightInline{Wickham, H. \emph{\href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis}}. (Springer-Verlag New York, 2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
-\CSLLeftMargin{84. }%
+\CSLLeftMargin{86. }%
 \CSLRightInline{Wilke, C. O. \emph{\href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}}. (2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
-\CSLLeftMargin{85. }%
+\CSLLeftMargin{87. }%
 \CSLRightInline{Landau, W.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
-\CSLLeftMargin{86. }%
+\CSLLeftMargin{88. }%
 \CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}}. (2022).}
@@
 
-\renewcommand{\figurename}{Supplementary Figure}
-\renewcommand{\tablename}{Supplementary Table}
-\renewcommand{\thefigure}{\arabic{figure}} \setcounter{figure}{0}
-\renewcommand{\thetable}{\arabic{table}} \setcounter{table}{0}
+\renewcommand{\figurename}{Figure}
+\renewcommand{\tablename}{Table}
+\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
 \renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}
@@
 
-\noindent \hspace*{5mm} \small Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare \newline
+\noindent \hspace*{8mm} \small Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare \newline
 \hspace*{1cm} \small Amalia P. M. Bastos\textsuperscript{1,2}, Scott Claessens\textsuperscript{2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, \newline

### 2024-01-16 manuscript.Rmd
prepare for submission

@@
 generation of a mechanical interface by using an object to manipulate another 
-target or surface [@Fragaszy2018]. The fact that we found strong phylogenetic 
-clustering of self-scratching tool use from the video survey with other examples
-of tool use from the literature supports a common underlying cognitive
-mechanism. In line with this, some of the species of parrots that use tools for 
-self-scratching in captivity also use tools for other purposes in the wild
-[@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021].
+target or surface [@Fragaszy2018]. This makes it difficult to dismiss
+self-scratching as unimportant: to do so would require a redefinition of
+tool-use in non-human animals. Moreover, the fact that we found strong 
+phylogenetic clustering of self-scratching tool use from the video survey with 
+other examples of tool use from the literature supports a common underlying 
+cognitive mechanism. In line with this, some of the species of parrots that use
+tools for self-scratching in captivity also use tools for other purposes in the 
+wild [@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021].
 

### 2024-01-16 manuscript.tex
prepare for submission

@@
 generation of a mechanical interface by using an object to manipulate another
-target or surface\textsuperscript{65}. The fact that we found strong phylogenetic
-clustering of self-scratching tool use from the video survey with other examples
-of tool use from the literature supports a common underlying cognitive
-mechanism. In line with this, some of the species of parrots that use tools for
-self-scratching in captivity also use tools for other purposes in the wild\textsuperscript{30,31,34,38}.
+target or surface\textsuperscript{65}. This makes it difficult to dismiss
+self-scratching as unimportant: to do so would require a redefinition of
+tool-use in non-human animals. Moreover, the fact that we found strong
+phylogenetic clustering of self-scratching tool use from the video survey with
+other examples of tool use from the literature supports a common underlying
+cognitive mechanism. In line with this, some of the species of parrots that use
+tools for self-scratching in captivity also use tools for other purposes in the
+wild\textsuperscript{30,31,34,38}.
 

### 2024-02-04 manuscript.Rmd
update manuscript and prepare for submission

@@
 appendix          : "appendix.Rmd"
-csl               : nature.csl
+csl               : pnas.csl
 ---

### 2024-02-04 manuscript.tex
update manuscript and prepare for submission

--- 2023-11-20 manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling\newline\indent Word count: 6548 words}
+\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling}
 \usepackage{lineno}
@@
 Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to estimate actual rates of tool use in parrots.
-Crowdsourcing revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
-Phylogenetic models incorporating these data together with measures of research effort and hypothesised predictors of tool use suggest that between 11\% and 17\% of parrot species may be tool users.
-These findings challenge the assumption that current research effort captures the distribution of putatively rare animal behaviours.
+Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
+Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11\% and 17\% of extant parrot species may be tool users.
+These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait.
+Overall, our findings challenge the assumption that current sampling effort captures the full distribution of putatively rare animal behaviours.
+Combining our sampling and analysis methods offers a fruitful approach for investigating the distribution, drivers, and origins of other rare behaviours.
 }
@@
 
-\nolinenumbers
+\linenumbers
 
 Our understanding of the evolution of animal behaviour is built on the
-assumption that we have access to sufficient data (\emph{1}--\emph{3}). However, this is not always the case. Data on behaviours that are
+assumption that we have access to sufficient data (1--3). However, this is not always the case. Data on behaviours that are
 rare, fleeting, or otherwise difficult to observe are likely to be patchy and
-incomplete (\emph{4}, \emph{5}). Among species for which such behaviours
+incomplete (4, 5). Among species for which such behaviours
 have not been observed, it can be difficult to differentiate between cases in
@@
 Comparative work on the evolution of tool use is a paradigmatic example of this
-issue. The initial discoveries of tool use in chimpanzees (\emph{6}),
-birds (\emph{7}), dolphins (\emph{8}), and octopuses (\emph{9}) occurred
+issue. The initial discoveries of tool use in chimpanzees (6),
+birds (7), dolphins (8), and octopuses (9) occurred
 decades after significant advances on other more easily measurable aspects of
@@
 unattached object as an extension of the animal's body to achieve a
-goal (\emph{10}) --- and have used the distribution of species meeting this
+goal (10) --- and have used the distribution of species meeting this
 definition to make various claims about the evolutionary drivers of tool use
@@
 higher relative brain size as a likely precondition for tool using
-capabilities (\emph{11}--\emph{13}). These researchers
+capabilities (11--13). These researchers
 argue that larger brains are better able to integrate visual and somatosensory
 information when innovating novel behaviours, such as tool use, in changing
-environments (\emph{14}, \emph{15}). Similarly, researchers have used existing
+environments (14, 15). Similarly, researchers have used existing
 reports of tool use in birds to debate the roles of generalist versus
@@
 arguing that feeding generalists require technical innovations to expand their
-dietary niche (\emph{14}, \emph{16}, \emph{17}) and others arguing that
+dietary niche (14, 16, 17) and others arguing that
 feeding specialists require technical innovations for extractive foraging of
-specific foods (\emph{18}, \emph{19}).
+specific foods (18, 19).
 
@@
 make them easier to study, such as larger distribution ranges and population
-sizes (\emph{20}). This is a crucial limitation because insufficient
+sizes (20). This is a crucial limitation because insufficient
 observation may lead researchers to miss true instances of tool behaviours and
@@
 One potentially powerful method for quantifying actual rates of rare animal
-behaviours is crowdsourcing (\emph{21}). In a crowdsourcing study, researchers
+behaviours is crowdsourcing (21). In a crowdsourcing study, researchers
 collect reports from the general public and/or collate and analyse videos posted
 on social media platforms. This citizen science approach has been widely used in
-ecology to monitor the distributional patterns of species (\emph{22}), but
+ecology to monitor the distributional patterns of species (22), but
 has also recently been used to uncover a variety of rare animal behaviours,
-including interspecies play in dogs (\emph{21}), novel problem-solving
-behaviours in horses (\emph{23}), and socially-learned foraging innovations
-in cockatoos (\emph{24}, \emph{25}). By casting the net wider than the
+including interspecies play in dogs (21), novel problem-solving
+behaviours in horses (23), and socially-learned foraging innovations
+in cockatoos (24, 25). By casting the net wider than the
 scientific literature, the crowdsourcing method can provide an indication of the
@@
 studied, but understudied tool users may go undetected. Furthermore, based on
-existing theories of the evolution of tool use (\emph{11}--\emph{19}), we propose that the
+existing theories of the evolution of tool use (11--19), we propose that the
 unobserved tool use capabilities are additionally caused by relative brain size,
@@
 of extant parrot species (11 out of 398; 3\%) use tools
-(\emph{11}, \emph{26}--\emph{38}). Parrot tool use
+(11, 26--38). Parrot tool use
 thus provides an ideal test case for examining how robust sampling is in the
@@
 all extant parrot species are bred in the aviculture industry and kept as pets
-worldwide (\emph{39}--\emph{45}), enabling us to leverage the power of crowdsourcing on a social
-media platform to search for evidence of tool use (\emph{21}). Third, detailed
-data on relative brain sizes (\emph{46}--\emph{51}), feeding strategies (\emph{52}), and
-shared ancestry (\emph{53}) exist for parrots, allowing us to fit the
+worldwide (39--45), enabling us to leverage the power of crowdsourcing on a social
+media platform to search for evidence of tool use (21). Third, detailed
+data on relative brain sizes (46--51), feeding strategies (52), and
+shared ancestry (53) exist for parrots, allowing us to fit the
 statistical model implied by Figure \ref{fig:plotDAG} to the entire parrot
@@
 tool use behaviour as the manipulation of an unattached object as an extension
-of the animal's body to achieve a goal (\emph{10}), while ``borderline'' tool
+of the animal's body to achieve a goal (10), while ``borderline'' tool
 use involved the use of an object that was still attached to a substrate
-(\emph{54}).
+(54).
 
@@
 established through genetic testing, and sexual dimorphism in parrots is
-rare (\emph{55}, \emph{56}), we could not typically ascertain if descriptions
+rare (55, 56), we could not typically ascertain if descriptions
 were accurate. It is unclear if the disproportionately large number of males in
@@
 
-Survival cure models (\emph{57}), also known as split population
-models (\emph{58}), are used to analyse the time to some event of interest
+Survival cure models (57), also known as split population
+models (58), are used to analyse the time to some event of interest
 with the added assumption that a certain proportion of the population will never
@@
 have been used to analyse a variety of right-censored outcomes, from cancer
-relapse (\emph{57}) to criminal recidivism (\emph{58}). The data are
+relapse (57) to criminal recidivism (58). The data are
 right-censored because some individuals will have experienced the event when
@@
 else being equal those with fewer published papers and fewer video search hits
-have a higher probability of being undetected tool users (fig.~
+have a higher probability of being undetected tool users (Supplementary Figure
 \ref{fig:plotSurvCure3}).
@@
 area-under-the-curve classification statistic of
-0.95 (fig.\\
+0.95 (Supplementary Figure
 \ref{fig:plotSurvCure9}). To further estimate the accuracy of the model's
@@
 effect of relative brain size and no difference between feeding strategies,
-respectively (fig.~\ref{fig:plotComparison}).
+respectively (Supplementary Figure \ref{fig:plotComparison}).
 
@@
 the \emph{Poicephalus} genus native to Africa (Table \ref{tab:tableASR};
-fig.~s \ref{fig:plotASR1} - \ref{fig:plotASR3}). These findings
+Supplementary Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}). These findings
 suggest that species from each of these genera may share their tool use
@@
 Since the earliest anecdotes of parrots using tools by Wallace in the 1880s
-(\emph{59}) and more systematic anecdotal reports in the 1970s (\emph{60}),
+(59) and more systematic anecdotal reports in the 1970s (60),
 only 11 parrot species (3\% of all extant parrots) have been documented as tool
@@
 (\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), and neotropical parrots
-(\emph{Arinae}).
-
-While parrots in the wild use tools to achieve a variety of
-goals (\emph{34}, \emph{38}), the 17 additional species identified by our
-video survey were exclusively observed using tools for self-scratching. This is
-likely because preening is the only context in which captive parrots regularly
-require tools, unlike wild parrots who may also require tools for extractive
-foraging (\emph{34}, \emph{38}). Despite this difference in the type of tool
-use observed, self-scratching is nonetheless a major category of animal tool
-use and clearly meets the established criteria for tool use in the literature:
-the manipulation of an unattached object as an extension of the animal's body to
-achieve a goal (\emph{10}). It also meets the definition for a more complex
-type of embodied tool use known as `tooling', the deliberate generation of a
-mechanical interface by using an object to manipulate another target or
-surface (\emph{61}). The fact that we found strong phylogenetic clustering
-of self-scratching tool use from the video survey with other examples of tool
-use from the literature supports a common underlying cognitive mechanism. In
-line with this, some of the species of parrots that use tools for
-self-scratching in captivity also use tools for other purposes in the wild
-(\emph{30}, \emph{31}, \emph{34}, \emph{38}).
+(\emph{Arinae}). Beyond the crowdsourcing survey, the strong phylogenetic signal in
+our dataset allowed us to use phylogenetic information, along with other
+variables, to infer the unobserved probabilities of tool use across the parrot
+order. Our phylogenetic survival cure model incorporated information on
+phylogenetic history, research effort, relative brain size, and feeding
+specialisation to rank parrot species that were most likely to be undetected
+tool users. The sum of probabilities from this model implied that between 15
+and 41 of the species without observed evidence of tool use are likely to be
+undetected tool users, suggesting that the true proportion of tool users may be
+as high as 17\%.
+
+These findings have a number of important implications. First, our findings show
+that current research effort in the scientific literature is insufficient to
+capture the real world occurrence of parrot tool use. If the scientific
+literature had sampled the natural world sufficiently, we would expect to see
+close correspondence between those species reported as tool users in the
+literature and those species the public have filmed performing tool use.
+Instead, we discovered a large discrepancy between these two data sources, both
+in the prevalence of tool use and the species identified. This raises the
+possibility that insufficient research effort is a general issue across the
+scientific literature, both for tool use in other groups and for other rare
+behaviours.
+
+Second, in terms of the evolution of tool use in parrots, our study challenges a
+key assumption made in the literature to date: that only a minority of parrots
+are tool users (30, 31, 34, 37, 38).
+The paucity of evidence for tool use across parrots in the literature initially
+implied that the capacity for tool use may have evolved independently in
+different parrot species. Our discovery of the widespread distribution of tool
+use across the parrot phylogeny, along with the strong phylogenetic signal in
+this expanded dataset, challenges this and suggests that, at least for some
+parrot clades, the capacity for tool use might be a homologous trait that has
+been evolutionarily conserved. Our exploratory ancestral state reconstruction
+analysis provides preliminary support for this hypothesis, revealing an
+increased probability of tool use among the most recent common ancestors for the
+\emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera. Even at this
+preliminary stage, our analysis therefore raises an alternative hypothesis for
+the observed tool use in \emph{Cacatua} (30, 38) and
+\emph{Nestor} (26--29, 31, 34), namely that tool behaviours have arisen due to the
+common ancestor having the capacity to use tools, rather than from independent
+evolution or behavioural innovation within species.
+
+Third, our results support existing theories of the drivers of tool use. We
+found that encephalisation was strongly positively related to the probability of
+tool use in our phylogenetic model, supporting previous theories linking
+relative brain size to increased tool innovation in birds (11--13) and primates (61). We acknowledge that
+encephalisation quotient is not a perfect measure due to measurement error and
+challenges with interpretation (3, 4). However, encephalisation
+quotient has much greater coverage across the parrot phylogeny than more
+fine-grained measures like whole neuron count (62) and there is no reason
+to think that measurement error would produce the consistent patterns across our
+study and prior work. To understand the causal mechanisms responsible for these
+relationships, we encourage further work on the specific neural correlates of
+technical intelligence in parrots, e.g., (63). In our phylogenetic
+model, we also found that tool use was somewhat more likely among feeding
+generalists compared to feeding specialists, although this difference was
+uncertain. This trend supports previous suggestions that increased cognitive
+abilities and technical innovation rates are required to expand a generalist
+species' dietary niche (16, 18, 64). However, the trend contradicts theories linking tool use to
+dietary specialisation, whereby species eating specific foods that require
+extractive foraging have higher cognitive ability and are especially prone to
+using tools (18).
+
+All instances of tool use in our crowdsourcing survey met the established
+criteria for tool use in the literature: the manipulation of an unattached
+object as an extension of the animal's body to achieve a goal (10).
+However, a striking feature of the dataset is that the 17 additional species
+identified in the video survey were exclusively observed using tools for
+self-scratching. While parrots in the wild use tools to achieve a variety of
+goals, including extractive foraging and preening (34, 38),
+parrots in captivity only require tools to achieve the latter goal. Despite this
+difference in the type of tool use observed, self-scratching is nonetheless a
+major category of animal tool use. Self-scratching also meets the definition for
+a more complex type of embodied tool use known as `tooling', the deliberate
+generation of a mechanical interface by using an object to manipulate another
+target or surface (65). This makes it difficult to dismiss
+self-scratching as unimportant: to do so would require a redefinition of
+tool-use in non-human animals. Moreover, the fact that we found strong
+phylogenetic clustering of self-scratching tool use from the video survey with
+other examples of tool use from the literature supports a common underlying
+cognitive mechanism. In line with this, some of the species of parrots that use
+tools for self-scratching in captivity also use tools for other purposes in the
+wild (30, 31, 34, 38).
 
@@
 over long periods of time, even across multiple different videos, suggesting
-that their behaviour was not random or accidental (\emph{62}). Parrots
+that their behaviour was not random or accidental (66). Parrots
 preferentially employed self-scratching tools on areas of their body that were
@@
 owners directly rewarding tool use behaviours with food. Finally, the high
-levels of phylogenetic signal in our data provides strong evidence that the
+levels of phylogenetic signal in our data provide strong evidence that the
 observations from our video survey reflect biologically-endowed capacities for
@@
 
-Beyond the video survey, the strong phylogenetic signal in our dataset allowed
-us to use phylogenetic information, along with other variables, to infer the
-unobserved probabilities of tool use across the parrot order. Our phylogenetic
-survival cure model incorporated information on phylogenetic history, research
-effort, relative brain size, and feeding specialisation to rank parrot species
-that were most likely to be undetected tool users. The sum of probabilities from
-this model implied that between 15 and 41 of the species without observed
-evidence of tool use are likely to be undetected tool users, suggesting that the
-true proportion of tool users may be as high as 17\%.
-
-These findings have a number of important implications. First, our findings show
-that current research effort in the scientific literature is insufficient to
-capture the real world occurrence of parrot tool use. If the scientific
-literature had sampled the natural world sufficiently, we would expect to see
-close correspondence between those species reported as tool users in the
-literature and those species the public have filmed performing tool use.
-Instead, we discovered a large discrepancy between these two data sources, both
-in the prevalence of tool use and the species identified. This raises the
-possibility that insufficient research effort is a general issue across the
-scientific literature, both for tool use in other groups and for other rare
-behaviours.
-
-Second, in terms of the evolution of tool use in parrots, our study challenges a
-key assumption made in the literature to date: that only a minority of parrots
-are tool users (\emph{30}, \emph{31}, \emph{34}, \emph{37}, \emph{38}).
-The paucity of evidence for tool use across parrots in the literature initially
-implied that the capacity for tool use may have evolved independently in
-different parrot species. Our discovery of the widespread distribution of tool
-use across the parrot phylogeny, along with the strong phylogenetic signal in
-this expanded dataset, challenges this and suggests that, at least for some
-parrot clades, the capacity for tool use might be a homologous trait that has
-been evolutionarily conserved. Our exploratory ancestral state reconstruction
-analysis provides preliminary support for this hypothesis, revealing an
-increased probability of tool use among the most recent common ancestors for the
-\emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera. Even at this
-preliminary stage, our analysis therefore raises an alternative hypothesis for
-the observed tool use in \emph{Cacatua} (\emph{30}, \emph{38}) and
-\emph{Nestor} (\emph{26}--\emph{29}, \emph{31}, \emph{34}), namely that tool behaviours have arisen due to the
-common ancestor having the capacity to use tools, rather than from independent
-evolution or behavioural innovation within species.
-
-Third, our results support existing theories of the drivers of tool use. We
-found that encephalisation was strongly positively related to the probability of
-tool use in our phylogenetic model, supporting previous theories linking
-relative brain size to increased tool innovation in birds (\emph{11}--\emph{13}) and primates (\emph{63}). We acknowledge that
-encephalisation quotient is not a perfect measure due to measurement error and
-challenges with interpretation (\emph{3}, \emph{4}). However, encephalisation
-quotient has much greater coverage across the parrot phylogeny than more
-fine-grained measures like whole neuron count (\emph{64}) and there is no reason
-to think that measurement error would produce the consistent patterns across our
-study and prior work. To understand the causal mechanisms responsible for these
-relationships, we encourage further work on the specific neural correlates of
-technical intelligence in parrots, e.g., (\emph{65}). In our phylogenetic
-model, we also found that tool use was somewhat more likely among feeding
-generalists compared to feeding specialists, although this difference was
-uncertain. This trend supports previous suggestions that increased cognitive
-abilities and technical innovation rates are required to expand a generalist
-species' dietary niche (\emph{16}, \emph{18}, \emph{66}). However, the trend contradicts theories linking tool use to
-dietary specialisation, whereby species eating specific foods that require
-extractive foraging have higher cognitive ability and are especially prone to
-using tools (\emph{18}).
-
 While missing data imputation is becoming more common in phylogenetic
-analyses (\emph{67}), the important distinction between absence of
+analyses (67), the important distinction between absence of
 evidence and evidence of absence has not been given as much attention. Our
@@
 in the taxonomic record, such as species abundance and geographic
-accessibility (\emph{20}).
+accessibility (20).
 
@@
 be applied to other rarely observed behaviours, including tool use in other
-taxa (\emph{68}), rhythmic entrainment in birds (\emph{69}--\emph{72}), teasing behaviours in primates (\emph{73}), and
-tactical deception across all animals (\emph{74}--\emph{76}).
+taxa (68), rhythmic entrainment in birds (69--72), teasing behaviours in primates (73), and
+tactical deception across all animals (74--76).
 We hope that these methods will continue to uncover a diverse array of ephemeral
@@
 of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all
-countries where bird ownership was reported as \textgreater5\% (\emph{77}), namely,
+countries where bird ownership was reported as \textgreater5\% (77), namely,
 Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish,
@@
 any parrots. At this point, we ended that search and initiated the next search.
-In line with previous recommendations (\emph{21}), we planned to exclude any
+In line with previous recommendations (21), we planned to exclude any
 videos that consisted of four or more shots edited together so as to ensure the
@@
 manipulation of an unattached object as an extension of the beak or foot to
-achieve a goal towards another object, individual, or oneself (\emph{10}).
+achieve a goal towards another object, individual, or oneself (10).
 Borderline tool use was similarly defined, except that it involved the use of an
-object that was still attached to a substrate (\emph{54}). For example, if
+object that was still attached to a substrate (54). For example, if
 individuals used a fallen feather or stick for self-scratching this was defined
@@
 to one's body (or, in the case of borderline tool use, rubbing repetitively
-against an attached object (\emph{62})).
+against an attached object (66)).
 
@@
 
-We collected data for 194 parrot species (figs.
+We collected data for 194 parrot species (Supplementary Figures
 \ref{fig:plotPhylo2} - \ref{fig:plotPhylo4}). We gathered feeding strategy
 data as a dichotomous variable (``generalist'' or ``specialist'') from the
-EltonTraits ecological database (\emph{52}). As per the database, specialists
+EltonTraits ecological database (52). As per the database, specialists
 were defined as species whose diet comprised at least 70\% of a single food
@@
 for all known body mass (g) and brain mass (g) values across
-parrots (\emph{46}--\emph{51}). For all species for which we obtained body and brain mass data, we
+parrots (46--51). For all species for which we obtained body and brain mass data, we
 calculated the encephalisation quotient (EQ) using the following
-formula (\emph{78}): \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
+formula (78): \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
 found body mass and brain mass data for a total of 194 parrot species. This
@@
 For phylogenetic data, we used the phylogenetic tool at www.birdtree.org
-(\emph{53}) to compile 1000 posterior draws of phylogenetic trees for 174 of the
+(53) to compile 1000 posterior draws of phylogenetic trees for 174 of the
 194 parrot species for which both EQ and genomic data exist. A single maximum
@@
 
-We used the \emph{fitDiscrete} function in the \emph{ape} R package (\emph{79}) to
+We used the \emph{fitDiscrete} function in the \emph{ape} R package (79) to
 calculate phylogenetic signal, for both the pre-survey and post-survey tool use
@@
 based on theory, we also assumed that unobserved tool use is caused by feeding
-strategy and relative brain size (\emph{11}--\emph{14}, \emph{16}--\emph{18}). Finally, we
+strategy and relative brain size (11--14, 16--18). Finally, we
 assumed that shared phylogenetic history causes unobserved confounding and
@@
 and \(\lambda\) (the rate of the exponential distribution). We use an
-Ornstein-Uhlenbeck Gaussian process (\emph{80}) to model phylogenetic
+Ornstein-Uhlenbeck Gaussian process (80) to model phylogenetic
 covariance. Below, we specify the full model with priors:
@@
 The priors for this model produce reasonable prior predictions of the
-probabilities of tool use for each parrot species (fig.
+probabilities of tool use for each parrot species (Supplementary Figure
 \ref{fig:plotSurvCure7}), but a sensitivity analysis revealed that the ranking
 and posterior probabilities reported in the main text were robust to modifying
-these priors (fig.~\ref{fig:plotSurvCure8}). We estimated the
+these priors (Supplementary Figure \ref{fig:plotSurvCure8}). We estimated the
 posterior distribution of this model using Hamiltonian Monte Carlo as
-implemented in Stan version 2.26.1 (\emph{81}). We ran the model for 4000
+implemented in Stan version 2.26.1 (81). We ran the model for 4000
 samples, with 2000 warmup samples, and iterated the model over 100 posterior
@@
 effective sample sizes suggested that the model converged normally. Trace plots
-are reported in fig.~\ref{fig:plotTrace}. We report
+are reported in Supplementary Figure \ref{fig:plotTrace}. We report
 equal-tailed credible intervals to describe the posterior distribution of this
@@
 parameters. The model was able to successfully recover those parameters
-(fig.~\ref{fig:plotSurvCureSim}). We also ran a
+(Supplementary Figure \ref{fig:plotSurvCureSim}). We also ran a
 leave-one-species-out exercise to ensure that we could accurately predict known
@@
 parrots, we fitted three exploratory ancestral state reconstruction models. We
-used the \emph{ancThresh} function from the \emph{phytools} R package (\emph{82}),
+used the \emph{ancThresh} function from the \emph{phytools} R package (82),
 iterating the function over 100 posterior parrot phylogenies. This function
@@
 
-All analyses were conducted in R v4.2.1. (\emph{83}). Visualisations were
-produced using the \emph{ggplot2} (\emph{84}) and \emph{cowplot} (\emph{85}) packages.
-The manuscript was reproducibly generated using the \emph{targets} (\emph{86}) and
-\emph{papaja} (\emph{87}) packages. Code to reproduce all analyses and figures can be
-found here: \url{https://github.com/ScottClaessens/phyloParrot}
+All analyses were conducted in R v4.2.1. (83). Visualisations were
+produced using the \emph{ggtree}(84), \emph{ggplot2} (85), and \emph{cowplot}
+(86) packages. The manuscript was reproducibly generated using the
+\emph{targets} (87) and \emph{papaja} (88) packages. Code to reproduce all
+analyses and figures can be found here:
+\url{https://github.com/ScottClaessens/phyloParrot}
 
@@
 L.
-MacLean, L.
-J.
-Matthews, B.
-A.
-Hare, C.
-L.
-Nunn, R.
-C.
-Anderson, F.
-Aureli, E.
-M.
-Brannon, J.
-Call, C.
-M.
-Drea, N.
-J.
-Emery, others, \href{https://doi.org/10.1007/s10071-011-0448-8}{How does cognition evolve?
+MacLean, \emph{et al.}, \href{https://doi.org/10.1007/s10071-011-0448-8}{How does cognition evolve?
 Phylogenetic comparative psychology}.
@@
 J.
-Logan, S.
-Avin, N.
-Boogert, A.
-Buskell, F.
-R.
-Cross, A.
-Currie, S.
-Jelbert, D.
-Lukas, R.
-Mares, A.
-F.
-Navarrete, S.
-Shigeno, S.
-H.
-Montgomery, \href{https://doi.org/10.3819/CCBR.2018.130008}{Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization}.
+Logan, \emph{et al.}, \href{https://doi.org/10.3819/CCBR.2018.130008}{Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization}.
 \emph{Comparative Cognition \& Behavior Reviews} \textbf{13}, 55--89 (2018).}
@@
 M.
-Burghardt, \emph{\href{https://doi.org/10.1353/book.98237}{Animal Tool Behavior: The Use and Manufacture of Tools by Animals}} (Johns Hopkins University Press, Baltimore, MD).}
+Burghardt, \emph{Animal tool behavior: The use and manufacture of tools by animals} (Johns Hopkins University Press) https:/doi.org/\href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}
 
@@
 C.
-Klump, J.
-M.
-Martin, S.
-Wild, J.
-K.
-Hörsch, R.
-E.
-Major, L.
-M.
-Aplin, \href{https://doi.org/10.1126/science.abe7808}{Innovation and geographic spread of a complex foraging culture in an urban parrot}.
+Klump, \emph{et al.}, \href{https://doi.org/10.1126/science.abe7808}{Innovation and geographic spread of a complex foraging culture in an urban parrot}.
 \emph{Science} \textbf{373}, 456--460 (2021).}
@@
 \CSLRightInline{M.
-O'Hara, B.
-Mioduszewska, R.
-Mundry, Yohanna, T.
-Haryoko, R.
-Rachmatika, D.
-M.
-Prawiradilaga, L.
-Huber, A.
-M.
-I.
-Auersperg, \href{https://doi.org/10.1016/j.cub.2021.08.009}{Wild {G}offin's cockatoos flexibly manufacture and use tool sets}.
+O'Hara, \emph{et al.}, \href{https://doi.org/10.1016/j.cub.2021.08.009}{Wild {G}offin's cockatoos flexibly manufacture and use tool sets}.
 \emph{Current Biology} \textbf{31}, 4512--4520.e6 (2021).}
@@
 Menzel, M.
-Engebretson, How many captive birds: Are population studies giving us a clear picture?
-(2014).
-\url{https://www.avianwelfare.org/issues/overview.htm}.}
+Engebretson, \href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?} (2014).}
 
@@
 \CSLRightInline{S.
-Olkowicz, M.
-Kocourek, R.
-K.
-Lučan, M.
-Porteš, W.
-T.
-Fitch, S.
-Herculano-Houzel, P.
-Němec, \href{https://doi.org/10.1073/pnas.1517131113}{Birds have primate-like numbers of neurons in the forebrain}.
+Olkowicz, \emph{et al.}, \href{https://doi.org/10.1073/pnas.1517131113}{Birds have primate-like numbers of neurons in the forebrain}.
 \emph{Proceedings of the National Academy of Sciences} \textbf{113}, 7255--7260 (2016).}
@@
 \CSLRightInline{H.
-Wilman, J.
-Belmaker, J.
-Simpson, C.
-de la Rosa, M.
-M.
-Rivadeneira, W.
-Jetz, EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals (2016).
-\url{https://doi.org/10.6084/m9.figshare.c.3306933.v1}.}
+Wilman, \emph{et al.}, EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals (2016) https:/doi.org/\href{https://doi.org/10.6084/m9.figshare.c.3306933.v1}{10.6084/m9.figshare.c.3306933.v1}.}
 
@@
 \CSLLeftMargin{55. }%
-\CSLRightInline{A. B. Bercovitz, {``Avian sex identification techniques''} in \emph{Companion Bird Medicine}, E. W. Burr, Ed. (Iowa State University Press, Ames, IA, 1987).}
+\CSLRightInline{A. B. Bercovitz, {``Avian sex identification techniques''} in \emph{Companion Bird Medicine}, E. W. Burr, Ed. (Iowa State University Press, 1987).}
 
@@
 \CSLLeftMargin{56. }%
-\CSLRightInline{J. D. Hoyo, R. Bierregaard, \emph{Handbook of the Birds of the World} (Lynx Edicions, Barcelona, Spain, 2011).}
+\CSLRightInline{J. D. Hoyo, R. Bierregaard, \emph{Handbook of the birds of the world} (Lynx Edicions, 2011).}
 
@@
 \CSLLeftMargin{59. }%
-\CSLRightInline{A.
-R.
-Wallace, \emph{The {M}alay {A}rchipelago: The Land of the Orang-Utan and the Bird of Paradise; a Narrative of Travel, with the Studies of Man and Nature} (MacMillan; Co., London, UK, 1869).}
+\CSLRightInline{A. R. Wallace, \emph{The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature} (MacMillan; Co., 1869).}
 
@@
 \CSLRightInline{J.
-Goodall, {``Tool-using in primates and other vertebrates''} D.
+Goodall, {``\href{https://doi.org/10.1016/S0065-3454(08)60157-6}{Tool-using in primates and other vertebrates}''} in Advances in the study of behavior., D.
 S.
@@
 Shaw, Eds.
-(Academic Press, 1971; \url{https://www.sciencedirect.com/science/article/pii/S0065345408601576})vol.
-3 of \emph{Advances in the study of behavior}, pp.
+(Academic Press, 1971), pp.
 195--249.}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
 \CSLLeftMargin{61. }%
-\CSLRightInline{D.
-M.
-Fragaszy, M.
-Mangalam, {``Tooling''} M.
-Naguib, L.
-Barrett, S.
-D.
-Healy, J.
-Podos, L.
-W.
-Simmons, M.
-Zuk, Eds.
-(Academic Press, 2018; \url{https://www.sciencedirect.com/science/article/pii/S0065345418300019})vol.
-50 of \emph{Advances in the study of behavior}, pp.
-177--241.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{K.
-Sándor, Á.
-Miklósi, \href{https://doi.org/10.3389/fpsyg.2020.555487}{How to report anecdotal observations?
-A new approach based on a lesson from "puffin tool use"}.
-\emph{Frontiers in Psychology} \textbf{11}, 555487 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
-\CSLLeftMargin{63. }%
 \CSLRightInline{S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{D.
-Sol, S.
-Olkowicz, F.
-Sayol, M.
-Kocourek, Y.
-Zhang, L.
-Marhounová, C.
-Osadnik, E.
-Corssmit, J.
-Garcia-Porta, T.
-E.
-Martin, others, Neuron numbers link innovativeness with both absolute and relative brain size in birds.
-\emph{Nature Ecology \& Evolution} \textbf{6}, 1381--1389 (2022).}
+\CSLLeftMargin{62. }%
+\CSLRightInline{D. Sol, \emph{et al.}, Neuron numbers link innovativeness with both absolute and relative brain size in birds. \emph{Nature Ecology \& Evolution} \textbf{6}, 1381--1389 (2022).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
-\CSLLeftMargin{65. }%
+\CSLLeftMargin{63. }%
 \CSLRightInline{M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
-\CSLLeftMargin{66. }%
+\CSLLeftMargin{64. }%
 \CSLRightInline{J.
@@
 \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{288}, 20211728 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
+\CSLLeftMargin{65. }%
+\CSLRightInline{D.
+M.
+Fragaszy, M.
+Mangalam, {``\href{https://doi.org/10.1016/bs.asb.2018.01.001}{Tooling}''} in Advances in the study of behavior., M.
+Naguib, \emph{et al.}, Eds.
+(Academic Press, 2018), pp.
+177--241.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
+\CSLLeftMargin{66. }%
+\CSLRightInline{K.
+Sándor, Á.
+Miklósi, \href{https://doi.org/10.3389/fpsyg.2020.555487}{How to report anecdotal observations?
+A new approach based on a lesson from "puffin tool use"}.
+\emph{Frontiers in Psychology} \textbf{11}, 555487 (2020).}
 
@@
 \CSLLeftMargin{77. }%
-\CSLRightInline{Global GfK survey: Pet ownership (2016). \url{http://www.gfk.com/global-studies/global-studies-pet-ownership}.}
+\CSLRightInline{, \href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership} (2016).}
 
@@
 \CSLLeftMargin{78. }%
-\CSLRightInline{H. J. Jerison, \emph{Evolution of the Brain and Intelligence} (Academic Press, New York, NY, 1973).}
+\CSLRightInline{H. J. Jerison, \emph{Evolution of the brain and intelligence} (Academic Press, 1973).}
 
@@
 \CSLRightInline{R.
-McElreath, \emph{Statistical Rethinking: A {Bayesian} Course with Examples in {R} and {Stan}, 2nd Edition} (CRC Press, ed.
-2, 2020; \url{http://xcelab.net/rm/statistical-rethinking/}).}
+McElreath, \emph{\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition}}, 2nd Ed.
+(CRC Press, 2020).}
 
@@
 \CSLLeftMargin{81. }%
-\CSLRightInline{Stan Development Team, {RStan}: The {R} interface to {Stan} (2020). \url{http://mc-stan.org/}.}
+\CSLRightInline{Stan Development Team, \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}} (2020).}
 
@@
 \CSLLeftMargin{83. }%
-\CSLRightInline{R Core Team, \emph{R: A Language and Environment for Statistical Computing} (R Foundation for Statistical Computing, Vienna, Austria, 2022; \url{https://www.R-project.org/}).}
+\CSLRightInline{R Core Team, \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}} (R Foundation for Statistical Computing, 2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
+\CSLLeftMargin{84. }%
+\CSLRightInline{G.
+Yu, D.
+Smith, H.
+Zhu, Y.
+Guan, T.
+T.-Y.
+Lam, \href{https://doi.org/10.1111/2041-210X.12628}{{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data}.
+\emph{Methods in Ecology and Evolution} \textbf{8}, 28--36 (2017).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-\CSLLeftMargin{84. }%
-\CSLRightInline{H. Wickham, \emph{{ggplot2}: Elegant Graphics for Data Analysis} (Springer-Verlag New York, 2016; \url{https://ggplot2.tidyverse.org}).}
+\CSLLeftMargin{85. }%
+\CSLRightInline{H. Wickham, \emph{\href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis}} (Springer-Verlag New York, 2016).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
-\CSLLeftMargin{85. }%
-\CSLRightInline{C. O. Wilke, \emph{{cowplot}: Streamlined Plot Theme and Plot Annotations for 'Ggplot2'} (2020; \url{https://CRAN.R-project.org/package=cowplot}).}
+\CSLLeftMargin{86. }%
+\CSLRightInline{C. O. Wilke, \emph{\href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}} (2020).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
-\CSLLeftMargin{86. }%
+\CSLLeftMargin{87. }%
 \CSLRightInline{W.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
-\CSLLeftMargin{87. }%
-\CSLRightInline{F. Aust, M. Barth, \emph{{papaja}: {Prepare} Reproducible {APA} Journal Articles with {R Markdown}} (2022; \url{https://github.com/crsh/papaja}).}
+\CSLLeftMargin{88. }%
+\CSLRightInline{F. Aust, M. Barth, \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}} (2022).}
 
@@
 
-\renewcommand{\figurename}{Fig.}
+\renewcommand{\figurename}{Figure}
 \renewcommand{\tablename}{Table}

### 2024-02-04 manuscript.Rmd
add significance statement

@@
 documentclass     : "apa6"
-classoption       : "man"
+classoption       : "man, donotrepeattitle"
 output            : papaja::apa6_pdf
@@
 
+# Significance Statement
+
+Tool use has been identified in a number of non-human animal species, including
+11 species of parrot. However, it is possible that the number of tool-using 
+parrot species has been underestimated due to insufficient research effort. 
+Here, we combine two approaches – crowdsourcing and phylogenetic modelling – to 
+estimate actual rates of tool use in parrots. Crowdsourcing on a social media 
+platform identified tool use in 17 novel parrot species, more than doubling the 
+confirmed number of tool-using parrot species from 11 to 28. Moreover, 
+phylogenetic modelling ranked additional species that are likely to be 
+unobserved tool users. Our findings have implications for inferences about the 
+evolutionary origins of technical intelligence in parrots.
+
+\newpage
 \linenumbers
+
+# Introduction
 

### 2024-02-04 manuscript.tex
add significance statement

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man, donotrepeattitle,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 
+\hypertarget{significance-statement}{%
+\section{Significance Statement}\label{significance-statement}}
+
+Tool use has been identified in a number of non-human animal species, including
+11 species of parrot. However, it is possible that the number of tool-using
+parrot species has been underestimated due to insufficient research effort.
+Here, we combine two approaches -- crowdsourcing and phylogenetic modelling -- to
+estimate actual rates of tool use in parrots. Crowdsourcing on a social media
+platform identified tool use in 17 novel parrot species, more than doubling the
+confirmed number of tool-using parrot species from 11 to 28. Moreover,
+phylogenetic modelling ranked additional species that are likely to be
+unobserved tool users. Our findings have implications for inferences about the
+evolutionary origins of technical intelligence in parrots.
+
+\newpage
 \linenumbers
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 

### 2024-05-20 manuscript.Rmd
update manuscript and prepare for submission

--- 2024-02-04 manuscript.Rmd
@@
 ---
-title             : "Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare"
+title             : "Digital video platforms and phylogenetic modelling reveal parrot tool use is not rare"
 shorttitle        : "Parrot tool use"
@@
  Putatively rare behaviours, such as tool use, are challenging to study because absence of evidence can arise either from a species’ inability to produce the behaviour or from insufficient research effort.
-Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to estimate actual rates of tool use in parrots.
-Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%).
+Here, we tackle this challenge by combining data from digital platforms and phylogenetic modelling to estimate actual rates of tool use in parrots.
+Videos on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%).
 Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11% and 17% of extant parrot species may be tool users.
@@
 
-keywords          : "tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling"
+keywords          : "tool use; technical intelligence; parrots; digital video platforms; phylogenetic modelling"
 bibliography      : ["r-references.bib"]
@@
 appendix          : "appendix.Rmd"
-csl               : pnas.csl
+csl               : current-biology.csl
 ---
 
-\linenumbers
+\newpage
+\nolinenumbers
+
+# Introduction
 
@@
 One potentially powerful method for quantifying actual rates of rare animal 
-behaviours is crowdsourcing [@Nelson2013]. In a crowdsourcing study, researchers 
-collect reports from the general public and/or collate and analyse videos posted 
-on social media platforms. This citizen science approach has been widely used in 
-ecology to monitor the distributional patterns of species [@Dickinson2010], but 
-has also recently been used to uncover a variety of rare animal behaviours, 
-including interspecies play in dogs [@Nelson2013], novel problem-solving 
-behaviours in horses [@Krueger2019], and socially-learned foraging innovations 
-in cockatoos [@Klump2021;@Klump2022]. By casting the net wider than the 
-scientific literature, the crowdsourcing method can provide an indication of the 
+behaviours is by collating evidence of the behaviours from digital video 
+platforms [@Nelson2013]. With millions of videos posted every day, digital 
+platforms like YouTube offer a valuable source of data on animal behaviour. 
+Digital video platforms have already been successfully used to uncover a variety
+of rare animal behaviours, including interspecies play in dogs [@Nelson2013], 
+novel problem-solving behaviours in horses [@Krueger2019], and death-related 
+behaviours in Asian elephants [@Pokharel2022]. By casting the net wider than the 
+scientific literature, digital video platforms can provide an indication of the 
 tool-using species that the literature might be missing.
 
-Even after using this crowdsourcing approach, some tool-users could _still_ 
-remain unobserved. One principled framework for identifying these unobserved species 
-is to specify a causal model of the process that generates the observed data. We 
-propose one such causal model in Figure \@ref(fig:plotDAG). In this model, we 
-assume that the presence of tool use in the scientific literature (or in 
-crowdsourced reports) is caused by both unobserved tool use capabilities and the 
-number of published studies (or the number of crowdsourced reports) for any 
-given species. Tool users are more likely to be observed if they are well 
-studied, but understudied tool users may go undetected. Furthermore, based on 
-existing theories of the evolution of tool use [@Ducatez2015;
-@HenkeVonDerMalsburg2020;@Lefebvre1997;@Lefebvre2002;@Lefebvre2004;
-@MettkeHofmann2014;@Overington2011;@Sol2005;@Sol2009], we propose that the 
-unobserved tool use capabilities are additionally caused by relative brain size, 
-feeding strategy, and shared phylogenetic ancestry. Expressing this causal model 
-as a statistical model can suggest further species which are likely to be 
-unobserved tool-users and, simultaneously, test existing theories of the 
+Even after collating evidence from digital video platforms, some tool-users 
+could _still_ remain unobserved. One principled framework for identifying these
+unobserved species is to specify a causal model of the process that generates
+the observed data. We propose one such causal model in Figure 
+\@ref(fig:plotDAG). In this model, we assume that the presence of tool use in 
+the scientific literature (or on digital video platforms) is caused by both 
+unobserved tool use capabilities and the number of published studies (or the 
+number of videos) for any given species. Tool users are more likely to be 
+observed if they are well studied, but understudied tool users may go 
+undetected. Furthermore, based on existing theories of the evolution of tool use
+[@Ducatez2015;@HenkeVonDerMalsburg2020;@Lefebvre1997;@Lefebvre2002;
+@Lefebvre2004;@MettkeHofmann2014;@Overington2011;@Sol2005;@Sol2009], we propose
+that the unobserved tool use capabilities are additionally caused by relative 
+brain size, feeding strategy, and shared phylogenetic ancestry. Expressing this
+causal model as a statistical model can suggest further species which are likely
+to be unobserved tool-users and, simultaneously, test existing theories of the 
 evolutionary drivers of tool use without incorrectly assuming that absence of 
@@
 presence and scientific research effort (i.e., number of publications). 
-Available crowdsourced data on tool use is caused both by unobserved tool use 
-presence and crowdsourcing effort (i.e., number of crowdsourced reports). 
-According to theory, unobserved tool use presence should be caused by relative 
-brain size (encephalisation quotient) and feeding strategy (generalist vs. 
-specialist). These variables all share unobserved confounds generated by shared 
-phylogenetic history. Grey circles indicate unobserved variables.
+Available video data on tool use is caused both by unobserved tool use 
+presence and video research effort (i.e., number of videos). According to 
+theory, unobserved tool use presence should be caused by relative brain size 
+(encephalisation quotient) and feeding strategy (generalist vs. specialist). 
+These variables all share unobserved confounds generated by shared phylogenetic
+history. Grey circles indicate unobserved variables.
 
@@
 
-Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool 
-use in the parrot order. We focus on tool use in parrots for a number of 
-reasons. First, the scientific literature suggests that only a small proportion 
-of extant parrot species (11 out of 398; 3%) use tools 
-[@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;@Auersperg2012;
-@Bastos2021;@BentleyCondit2010;@Borsari2005;@Goodman2018;@Heinsohn2017;
-@Janzen1976;@Lambert2015;@Lefebvre2002;@OHara2021]. Parrot tool use 
-thus provides an ideal test case for examining how robust sampling is in the 
+Here, we apply these approaches to tool use in the parrot order. We focus on 
+tool use in parrots for a number of reasons. First, the scientific literature 
+suggests that only a small proportion of extant parrot species (11 out of 398;
+3%) use tools [@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;
+@Auersperg2012;@Bastos2021;@BentleyCondit2010;@Borsari2005;@Goodman2018;
+@Heinsohn2017;@Janzen1976;@Lambert2015;@Lefebvre2002;@OHara2021]. Parrot tool 
+use thus provides an ideal test case for examining how robust sampling is in the 
 scientific literature. Second, parrots are highly popular as pets. Over 70% of 
@@
 worldwide [@Anderson2003;@Carrete2008;@Drews2001;@Kelly2014;@Li2014;@Su2015;
-@Young2012], enabling us to leverage the power of crowdsourcing on a social 
-media platform to search for evidence of tool use [@Nelson2013]. Third, detailed 
-data on relative brain sizes [@Flammer2001;@Iwaniuk2005;@Mazengenya2018;
-@Olkowicz2016;@Schuck2008;@Silva2017], feeding strategies [@Wilman2016], and 
-shared ancestry [@Jetz2012] exist for parrots, allowing us to fit the 
-statistical model implied by Figure \@ref(fig:plotDAG) to the entire parrot 
-order.
+@Young2012], enabling us to leverage the power of digital video platforms to 
+search for evidence of tool use [@Nelson2013]. Third, detailed data on relative
+brain sizes [@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;
+@Schuck2008;@Silva2017], feeding strategies [@Wilman2016], and shared ancestry
+[@Jetz2012] exist for parrots, allowing us to fit the statistical model implied
+by Figure \@ref(fig:plotDAG) to the entire parrot order.
 
-We first present the results from our crowdsourcing survey, in which we collated 
-videos of tool use in parrots from an online video platform. This survey reveals 
-a number of previously unidentified tool-using parrot species, which we map onto 
+We first present the results from our video survey, in which we collated videos
+of tool use in parrots from a digital video platform. This survey reveals a 
+number of previously unidentified tool-using parrot species, which we map onto 
 the phylogeny of the parrot order. We then describe our statistical model in 
@@
 
-## Crowdsourcing reveals tool use in additional parrot species
+## Digital video platform reveals tool use in additional parrot species
 
-We surveyed the social media platform YouTube for video evidence of tool use in 
+We surveyed the digital media platform YouTube for video evidence of tool use in 
 parrots (see Methods for detailed search criteria). In our search, we used the 
@@
 
-(ref:plotPhylo1Caption) _Results of crowdsourcing video survey and phylogenetic 
-survival cure modelling mapped onto a maximum clade credibility phylogeny of the 
-parrot order._ Orange points in the inner ring indicate species observed in the 
-video survey, with point size scaled by the number of videos for each species 
-(note that three species observed only in the video survey are not present in 
-the phylogeny due to a lack of genomic data: _Psittacara erythrogenys_, 
-_Psittacus timneh_, and _Aratinga nenday_). Blue points in the outer ring 
-indicate species observed in the scientific literature, with point size scaled 
-by the number of papers published on each species. Yellow species names indicate 
-the top ten most likely tool-using species from our phylogenetic survival cure 
-model which were not observed in the scientific literature or the video survey. 
-Total _n_ = `r nrow(tar_read(d))` species.
+(ref:plotPhylo1Caption) _Results of video survey and phylogenetic survival cure
+modelling mapped onto a maximum clade credibility phylogeny of the parrot order._
+Orange points in the inner ring indicate species observed in the video survey,
+with point size scaled by the number of videos for each species (note that three
+species observed only in the video survey are not present in the phylogeny due
+to a lack of genomic data: _Psittacara erythrogenys_, _Psittacus timneh_, and 
+_Aratinga nenday_). Blue points in the outer ring indicate species observed in
+the scientific literature, with point size scaled by the number of papers 
+published on each species. Yellow species names indicate the top ten most likely
+tool-using species from our phylogenetic survival cure model which were not 
+observed in the scientific literature or the video survey. Total _n_ = 
+`r nrow(tar_read(d))` species.
 
@@
 further species that are likely to be undetected tool-users (i.e., tool-using 
-species with no tool use reported in the literature or in crowdsourced videos).
+species with no tool use reported in the literature or in videos).
 
@@
 specifically, the amount of "time" (i.e., observation opportunities measured as 
-the number of published papers or crowdsourced videos) until tool use is 
-identified. This is right-censored data because many species will not have had 
-tool use identified when we measure them. Moreover, we can assume that a certain 
-proportion of the population will never experience the event -- that is, they 
-are a non-tool-user and so we will never identify tool use no matter how long we 
-measure them for.
+the number of published papers or videos) until tool use is identified. This is
+right-censored data because many species will not have had tool use identified
+when we measure them. Moreover, we can assume that a certain proportion of the
+population will never experience the event -- that is, they are a non-tool-user
+and so we will never identify tool use no matter how long we measure them for.
 
@@
 only 11 parrot species (3% of all extant parrots) have been documented as tool 
-users in the scientific literature. Our study used crowdsourcing to identify 17 
-additional tool-using parrot species that are new to science, more than doubling 
-the overall count to 28 species (7%). These species consisted of cockatoos 
-(_Cacatuidae_), Old World parrots (_Psittacinae_), and neotropical parrots 
-(_Arinae_). Beyond the crowdsourcing survey, the strong phylogenetic signal in 
-our dataset allowed us to use phylogenetic information, along with other 
-variables, to infer the unobserved probabilities of tool use across the parrot 
-order. Our phylogenetic survival cure model incorporated information on 
-phylogenetic history, research effort, relative brain size, and feeding 
-specialisation to rank parrot species that were most likely to be undetected 
-tool users. The sum of probabilities from this model implied that between 15 
-and 41 of the species without observed evidence of tool use are likely to be 
-undetected tool users, suggesting that the true proportion of tool users may be
-as high as 17%.
+users in the scientific literature. Our study collated data from a digital video
+platform to identify 17 additional tool-using parrot species that are new to 
+science, more than doubling the overall count to 28 species (7%). These species 
+consisted of cockatoos (_Cacatuidae_), Old World parrots (_Psittacinae_), and 
+neotropical parrots (_Arinae_). Beyond the video survey, the strong 
+phylogenetic signal in our dataset allowed us to use phylogenetic information, 
+along with other variables, to infer the unobserved probabilities of tool use 
+across the parrot order. Our phylogenetic survival cure model incorporated
+information on phylogenetic history, research effort, relative brain size, and 
+feeding specialisation to rank parrot species that were most likely to be 
+undetected tool users. The sum of probabilities from this model implied that 
+between 15 and 41 of the species without observed evidence of tool use are 
+likely to be undetected tool users, suggesting that the true proportion of tool
+users may be as high as 17%.
 
@@
 
-All instances of tool use in our crowdsourcing survey met the established
-criteria for tool use in the literature: the manipulation of an unattached 
-object as an extension of the animal's body to achieve a goal [@Shumaker2011].
-However, a striking feature of the dataset is that the 17 additional species
-identified in the video survey were exclusively observed using tools for
-self-scratching. While parrots in the wild use tools to achieve a variety of 
-goals, including extractive foraging and preening [@Goodman2018;@OHara2021],
-parrots in captivity only require tools to achieve the latter goal. Despite this
-difference in the type of tool use observed, self-scratching is nonetheless a 
-major category of animal tool use. Self-scratching also meets the definition for
-a more complex type of embodied tool use known as 'tooling', the deliberate 
-generation of a mechanical interface by using an object to manipulate another 
-target or surface [@Fragaszy2018]. This makes it difficult to dismiss
-self-scratching as unimportant: to do so would require a redefinition of
-tool-use in non-human animals. Moreover, the fact that we found strong 
-phylogenetic clustering of self-scratching tool use from the video survey with 
-other examples of tool use from the literature supports a common underlying 
-cognitive mechanism. In line with this, some of the species of parrots that use
-tools for self-scratching in captivity also use tools for other purposes in the 
-wild [@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021].
+All instances of tool use in our video survey met the established criteria for 
+tool use in the literature: the manipulation of an unattached object as an 
+extension of the animal's body to achieve a goal [@Shumaker2011]. However, a 
+striking feature of the dataset is that the 17 additional species identified in
+the video survey were exclusively observed using tools for self-scratching.
+While parrots in the wild use tools to achieve a variety of goals, including 
+extractive foraging and preening [@Goodman2018;@OHara2021], parrots in captivity
+only require tools to achieve the latter goal. Despite this difference in the
+type of tool use observed, self-scratching is nonetheless a major category of 
+animal tool use. Self-scratching also meets the definition for a more complex 
+type of embodied tool use known as 'tooling', the deliberate generation of a 
+mechanical interface by using an object to manipulate another target or surface
+[@Fragaszy2018]. This makes it difficult to dismiss self-scratching as 
+unimportant: to do so would require a redefinition of tool-use in non-human
+animals. Moreover, the fact that we found strong phylogenetic clustering of 
+self-scratching tool use from the video survey with other examples of tool use
+from the literature supports a common underlying cognitive mechanism. In line 
+with this, some of the species of parrots that use tools for self-scratching in
+captivity also use tools for other purposes in the wild [@Auersperg2012;
+@Bastos2021;@Goodman2018;@OHara2021].
 
@@
 handed parrots their tools in two of the videos, and none of the videos featured 
-owners directly rewarding tool use behaviours with food. Finally, the high 
-levels of phylogenetic signal in our data provide strong evidence that the 
-observations from our video survey reflect biologically-endowed capacities for 
-tool use rather than accidental or trained behaviours, which would likely appear 
-uniformly across the phylogeny.
+owners directly rewarding tool use behaviours with food. It is unlikely that 
+owners would specifically train parrots to scratch themselves with tools. 
+Finally, the high levels of phylogenetic signal in our data provide strong 
+evidence that the observations from our video survey reflect
+biologically-endowed capacities for tool use rather than accidental or trained
+behaviours, which would likely appear uniformly across the phylogeny.
 
@@
 between true absences of tool use and absences of tool use due to a lack of 
-research effort in the scientific literature or in crowdsourced videos. To 
-achieve this, we explicitly modelled the measurement of the outcome variable 
-along a research effort time series, such that species with lower research 
-effort in the literature or in videos were likely to be censored. In line with 
-our causal model, we also included relative brain size, feeding strategy, and 
-phylogenetic history as predictors of unobserved tool use. We encourage 
-researchers to test this model by directing future study efforts towards the 
-parrot species with the highest probabilities of being undetected tool-users. 
-Future work should also refine the causal model in Figure \@ref(fig:plotDAG) to 
-provide more certain estimates of tool use probabilities, either by including 
-additional predictor variables or modelling further causes of measurement error 
-in the taxonomic record, such as species abundance and geographic 
-accessibility [@Ducatez2014].
+research effort in the scientific literature or in videos. To achieve this, we 
+explicitly modelled the measurement of the outcome variable along a research 
+effort time series, such that species with lower research effort in the 
+literature or in videos were likely to be censored. In line with our causal 
+model, we also included relative brain size, feeding strategy, and phylogenetic
+history as predictors of unobserved tool use. We encourage researchers to test
+this model by directing future study efforts towards the parrot species with the
+highest probabilities of being undetected tool-users. Future work should also
+refine the causal model in Figure \@ref(fig:plotDAG) to provide more certain
+estimates of tool use probabilities, either by including additional predictor
+variables or modelling further causes of measurement error in the taxonomic
+record, such as species abundance and geographic accessibility [@Ducatez2014].
 
@@
 captured the full distribution of tool use in the parrot order. Our 
-crowdsourcing survey more than doubled the number of known tool using parrot 
+digital video survey more than doubled the number of known tool using parrot 
 species from 11 to 28, and our phylogenetic model suggested that the true 
@@
 drivers and origins of tool use in parrots. Beyond parrot tool use, the 
-crowdsourcing and phylogenetic methods used in this study have the potential to 
-be applied to other rarely observed behaviours, including tool use in other 
-taxa [@Hunt2013], rhythmic entrainment in birds [@Benichov2016;@Patel2009;
-@tenCate2016;@Wilson2016], teasing behaviours in primates [@Eckert2020], and 
-tactical deception across all animals [@BroJorgensen2010;@Byrne1988;@Byrne1991]. 
-We hope that these methods will continue to uncover a diverse array of ephemeral 
-behaviours that have as yet gone undetected in the scientific literature.
+methods used in this study have the potential to be applied to other rarely 
+observed behaviours, including tool use in other taxa [@Hunt2013], rhythmic 
+entrainment in birds [@Benichov2016;@Patel2009;@tenCate2016;@Wilson2016],
+teasing behaviours in primates [@Eckert2020], and tactical deception across all
+animals [@BroJorgensen2010;@Byrne1988;@Byrne1991]. We hope that these methods
+will continue to uncover a diverse array of ephemeral behaviours that have as
+yet gone undetected in the scientific literature.
 
@@
 
-Our video search was conducted on YouTube in July 2020. Search terms included 
+Our video search was conducted on YouTube in July 2020. Searches were conducted
+manually by the first author over a month-long period, using the same IP address
+and not logged in with a YouTube user account. Search terms included 
 "parrot using tool" and variants (e.g., "macaw using tool", "lorikeet using 
@@
 Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, 
-Portuguese, and Mandarin.
+Portuguese, and Mandarin. Browser search histories were not cleared between
+searches.
 
@@
 
+Since YouTube is constantly growing and evolving in both its uploaded content 
+and its proprietary recommendation algorithms, the same search strategy today 
+would not return exactly the same videos as our search in July 2020. It is 
+possible that some videos have since been deleted or more videos of parrot tool
+use have since been uploaded. However, this does not affect our conclusions
+about the number of parrot species found to use tools in our initial search.
+
 ## Data for parrot species
@@
 For modelling purposes, we coded research effort in both the scientific 
-literature and the crowdsourced videos. For the scientific literature, we 
+literature and the YouTube videos. For the scientific literature, we 
 operationalised research effort as the number of papers published for each 
@@
 used the scientific database Scopus for coding the number of published papers. 
-For the crowdsourced videos, we coded research effort as the number of search 
-hits for each species on YouTube. If tool use had been identified on YouTube, we 
-estimated the number of search hits when the first video of tool use was 
-published on YouTube, assuming linear growth of search hits since the inception 
-of YouTube. If tool use had not been identified, we used the current number of 
-search hits.
+For the videos, we coded research effort as the number of search hits for each
+species on YouTube. If tool use had been identified on YouTube, we estimated the
+number of search hits when the first video of tool use was published on YouTube,
+assuming linear growth of search hits since the inception of YouTube. If tool
+use had not been identified, we used the current number of search hits.
 
@@
 causal model of observed tool use (Figure \@ref(fig:plotDAG)). We assumed that 
-observed tool use in the scientific literature and in the crowdsourced videos is 
-caused by both the unobserved presence or absence of tool use and research 
-effort, proxied by the number of papers published on a species and the number of 
-videos published on a species. Tool users are more likely to be observed if they 
-are well studied, but understudied tool users may go undetected. In addition, 
-based on theory, we also assumed that unobserved tool use is caused by feeding 
+observed tool use in the scientific literature and in the videos is caused by 
+both the unobserved presence or absence of tool use and research effort, proxied
+by the number of papers published on a species and the number of videos
+published on a species. Tool users are more likely to be observed if they are
+well studied, but understudied tool users may go undetected. In addition, based
+on theory, we also assumed that unobserved tool use is caused by feeding 
 strategy and relative brain size [@Lefebvre2004;@Lefebvre1997;@Lefebvre2002;
@@
 not (0) tool use has yet been observed in the scientific literature for species 
-$i$. For the crowdsourced videos, we declare $\text{N}_{\text{Vid},i}$ as the 
+$i$. For the videos, we declare $\text{N}_{\text{Vid},i}$ as the 
 number of videos published before and up to tool use identification for species 
@@
 stating whether (1) or not (0) tool use has yet been observed in the 
-crowdsourced videos for species $i$. Additionally, $\text{F}_i$ and 
+videos for species $i$. Additionally, $\text{F}_i$ and 
 $\text{EQ}_i$ are feeding strategy and encephalisation quotient values for 
@@
 probability $p_i$. We also assume that tool use is identified in the scientific 
-literature and the crowdsourced videos at constant rates $\lambda_{\text{Lit}}$ 
+literature and the videos at constant rates $\lambda_{\text{Lit}}$ 
 and $\lambda_{\text{Vid}}$ following exponential survival functions. Given these 
@@
 The Exponential-CCDF function allows for the censored nature of the data. The 
-same data generating process is assumed to underlie the crowdsourced videos.
+same data generating process is assumed to underlie the videos.
 

### 2024-05-20 manuscript.tex
update manuscript and prepare for submission

--- 2024-01-16 manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling}
+\keywords{tool use; technical intelligence; parrots; digital video platforms; phylogenetic modelling}
 \usepackage{lineno}
@@
 \hypersetup{
-  pdftitle={Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare},
+  pdftitle={Digital video platforms and phylogenetic modelling reveal parrot tool use is not rare},
   pdfauthor={Amalia P. M. Bastos†,1,2, Scott Claessens*†,2, Ximena J. Nelson3, David Welch4, Quentin D. Atkinson‡,2, \& Alex H. Taylor‡,2,3,5,6},
   pdflang={en-EN},
-  pdfkeywords={tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling},
+  pdfkeywords={tool use; technical intelligence; parrots; digital video platforms; phylogenetic modelling},
   hidelinks,
@@
 
-\title{Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare}
+\title{Digital video platforms and phylogenetic modelling reveal parrot tool use is not rare}
 \author{Amalia P.
@@
 Putatively rare behaviours, such as tool use, are challenging to study because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort.
-Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to estimate actual rates of tool use in parrots.
-Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
+Here, we tackle this challenge by combining data from digital platforms and phylogenetic modelling to estimate actual rates of tool use in parrots.
+Videos on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
 Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11\% and 17\% of extant parrot species may be tool users.
@@
 
-\linenumbers
+\newpage
+\nolinenumbers
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 One potentially powerful method for quantifying actual rates of rare animal
-behaviours is crowdsourcing\textsuperscript{21}. In a crowdsourcing study, researchers
-collect reports from the general public and/or collate and analyse videos posted
-on social media platforms. This citizen science approach has been widely used in
-ecology to monitor the distributional patterns of species\textsuperscript{22}, but
-has also recently been used to uncover a variety of rare animal behaviours,
-including interspecies play in dogs\textsuperscript{21}, novel problem-solving
-behaviours in horses\textsuperscript{23}, and socially-learned foraging innovations
-in cockatoos\textsuperscript{24,25}. By casting the net wider than the
-scientific literature, the crowdsourcing method can provide an indication of the
+behaviours is by collating evidence of the behaviours from digital video
+platforms\textsuperscript{21}. With millions of videos posted every day, digital
+platforms like YouTube offer a valuable source of data on animal behaviour.
+Digital video platforms have already been successfully used to uncover a variety
+of rare animal behaviours, including interspecies play in dogs\textsuperscript{21},
+novel problem-solving behaviours in horses\textsuperscript{22}, and death-related
+behaviours in Asian elephants\textsuperscript{23}. By casting the net wider than the
+scientific literature, digital video platforms can provide an indication of the
 tool-using species that the literature might be missing.
 
-Even after using this crowdsourcing approach, some tool-users could \emph{still}
-remain unobserved. One principled framework for identifying these unobserved species
-is to specify a causal model of the process that generates the observed data. We
-propose one such causal model in Figure \ref{fig:plotDAG}. In this model, we
-assume that the presence of tool use in the scientific literature (or in
-crowdsourced reports) is caused by both unobserved tool use capabilities and the
-number of published studies (or the number of crowdsourced reports) for any
-given species. Tool users are more likely to be observed if they are well
-studied, but understudied tool users may go undetected. Furthermore, based on
-existing theories of the evolution of tool use\textsuperscript{11--19}, we propose that the
-unobserved tool use capabilities are additionally caused by relative brain size,
-feeding strategy, and shared phylogenetic ancestry. Expressing this causal model
-as a statistical model can suggest further species which are likely to be
-unobserved tool-users and, simultaneously, test existing theories of the
+Even after collating evidence from digital video platforms, some tool-users
+could \emph{still} remain unobserved. One principled framework for identifying these
+unobserved species is to specify a causal model of the process that generates
+the observed data. We propose one such causal model in Figure
+\ref{fig:plotDAG}. In this model, we assume that the presence of tool use in
+the scientific literature (or on digital video platforms) is caused by both
+unobserved tool use capabilities and the number of published studies (or the
+number of videos) for any given species. Tool users are more likely to be
+observed if they are well studied, but understudied tool users may go
+undetected. Furthermore, based on existing theories of the evolution of tool use\textsuperscript{11--19}, we propose
+that the unobserved tool use capabilities are additionally caused by relative
+brain size, feeding strategy, and shared phylogenetic ancestry. Expressing this
+causal model as a statistical model can suggest further species which are likely
+to be unobserved tool-users and, simultaneously, test existing theories of the
 evolutionary drivers of tool use without incorrectly assuming that absence of
@@
 presence and scientific research effort (i.e., number of publications).
-Available crowdsourced data on tool use is caused both by unobserved tool use
-presence and crowdsourcing effort (i.e., number of crowdsourced reports).
-According to theory, unobserved tool use presence should be caused by relative
-brain size (encephalisation quotient) and feeding strategy (generalist vs.~
-specialist). These variables all share unobserved confounds generated by shared
-phylogenetic history. Grey circles indicate unobserved variables.}
+Available video data on tool use is caused both by unobserved tool use
+presence and video research effort (i.e., number of videos). According to
+theory, unobserved tool use presence should be caused by relative brain size
+(encephalisation quotient) and feeding strategy (generalist vs.~specialist).
+These variables all share unobserved confounds generated by shared phylogenetic
+history. Grey circles indicate unobserved variables.}
 \end{figure}
 
-Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool
-use in the parrot order. We focus on tool use in parrots for a number of
-reasons. First, the scientific literature suggests that only a small proportion
-of extant parrot species (11 out of 398; 3\%) use tools\textsuperscript{11,26--38}. Parrot tool use
-thus provides an ideal test case for examining how robust sampling is in the
+Here, we apply these approaches to tool use in the parrot order. We focus on
+tool use in parrots for a number of reasons. First, the scientific literature
+suggests that only a small proportion of extant parrot species (11 out of 398;
+3\%) use tools\textsuperscript{11,24--36}. Parrot tool
+use thus provides an ideal test case for examining how robust sampling is in the
 scientific literature. Second, parrots are highly popular as pets. Over 70\% of
 all extant parrot species are bred in the aviculture industry and kept as pets
-worldwide\textsuperscript{39--45}, enabling us to leverage the power of crowdsourcing on a social
-media platform to search for evidence of tool use\textsuperscript{21}. Third, detailed
-data on relative brain sizes\textsuperscript{46--51}, feeding strategies\textsuperscript{52}, and
-shared ancestry\textsuperscript{53} exist for parrots, allowing us to fit the
-statistical model implied by Figure \ref{fig:plotDAG} to the entire parrot
-order.
-
-We first present the results from our crowdsourcing survey, in which we collated
-videos of tool use in parrots from an online video platform. This survey reveals
-a number of previously unidentified tool-using parrot species, which we map onto
+worldwide\textsuperscript{37--43}, enabling us to leverage the power of digital video platforms to
+search for evidence of tool use\textsuperscript{21}. Third, detailed data on relative
+brain sizes\textsuperscript{44--49}, feeding strategies\textsuperscript{50}, and shared ancestry\textsuperscript{51} exist for parrots, allowing us to fit the statistical model implied
+by Figure \ref{fig:plotDAG} to the entire parrot order.
+
+We first present the results from our video survey, in which we collated videos
+of tool use in parrots from a digital video platform. This survey reveals a
+number of previously unidentified tool-using parrot species, which we map onto
 the phylogeny of the parrot order. We then describe our statistical model in
@@
 
-\hypertarget{crowdsourcing-reveals-tool-use-in-additional-parrot-species}{%
-\subsection{Crowdsourcing reveals tool use in additional parrot species}\label{crowdsourcing-reveals-tool-use-in-additional-parrot-species}}
-
-We surveyed the social media platform YouTube for video evidence of tool use in
+\hypertarget{digital-video-platform-reveals-tool-use-in-additional-parrot-species}{%
+\subsection{Digital video platform reveals tool use in additional parrot species}\label{digital-video-platform-reveals-tool-use-in-additional-parrot-species}}
+
+We surveyed the digital media platform YouTube for video evidence of tool use in
 parrots (see Methods for detailed search criteria). In our search, we used the
@@
 of the animal's body to achieve a goal\textsuperscript{10}, while ``borderline'' tool
-use involved the use of an object that was still attached to a substrate\textsuperscript{54}.
+use involved the use of an object that was still attached to a substrate\textsuperscript{52}.
 
@@
 established through genetic testing, and sexual dimorphism in parrots is
-rare\textsuperscript{55,56}, we could not typically ascertain if descriptions
+rare\textsuperscript{53,54}, we could not typically ascertain if descriptions
 were accurate. It is unclear if the disproportionately large number of males in
@@
 \includegraphics{manuscript_files/figure-latex/plotPhylo1-1.pdf}
-\caption{\label{fig:plotPhylo1}\emph{Results of crowdsourcing video survey and phylogenetic
-survival cure modelling mapped onto a maximum clade credibility phylogeny of the
-parrot order.} Orange points in the inner ring indicate species observed in the
-video survey, with point size scaled by the number of videos for each species
-(note that three species observed only in the video survey are not present in
-the phylogeny due to a lack of genomic data: \emph{Psittacara erythrogenys},
-\emph{Psittacus timneh}, and \emph{Aratinga nenday}). Blue points in the outer ring
-indicate species observed in the scientific literature, with point size scaled
-by the number of papers published on each species. Yellow species names indicate
-the top ten most likely tool-using species from our phylogenetic survival cure
-model which were not observed in the scientific literature or the video survey.
-Total \emph{n} = 174 species.}
+\caption{\label{fig:plotPhylo1}\emph{Results of video survey and phylogenetic survival cure
+modelling mapped onto a maximum clade credibility phylogeny of the parrot order.}
+Orange points in the inner ring indicate species observed in the video survey,
+with point size scaled by the number of videos for each species (note that three
+species observed only in the video survey are not present in the phylogeny due
+to a lack of genomic data: \emph{Psittacara erythrogenys}, \emph{Psittacus timneh}, and
+\emph{Aratinga nenday}). Blue points in the outer ring indicate species observed in
+the scientific literature, with point size scaled by the number of papers
+published on each species. Yellow species names indicate the top ten most likely
+tool-using species from our phylogenetic survival cure model which were not
+observed in the scientific literature or the video survey. Total \emph{n} =
+174 species.}
 \end{figure}
@@
 further species that are likely to be undetected tool-users (i.e., tool-using
-species with no tool use reported in the literature or in crowdsourced videos).
-
-Survival cure models\textsuperscript{57}, also known as split population
-models\textsuperscript{58}, are used to analyse the time to some event of interest
+species with no tool use reported in the literature or in videos).
+
+Survival cure models\textsuperscript{55}, also known as split population
+models\textsuperscript{56}, are used to analyse the time to some event of interest
 with the added assumption that a certain proportion of the population will never
@@
 have been used to analyse a variety of right-censored outcomes, from cancer
-relapse\textsuperscript{57} to criminal recidivism\textsuperscript{58}. The data are
+relapse\textsuperscript{55} to criminal recidivism\textsuperscript{56}. The data are
 right-censored because some individuals will have experienced the event when
@@
 specifically, the amount of ``time'' (i.e., observation opportunities measured as
-the number of published papers or crowdsourced videos) until tool use is
-identified. This is right-censored data because many species will not have had
-tool use identified when we measure them. Moreover, we can assume that a certain
-proportion of the population will never experience the event -- that is, they
-are a non-tool-user and so we will never identify tool use no matter how long we
-measure them for.
+the number of published papers or videos) until tool use is identified. This is
+right-censored data because many species will not have had tool use identified
+when we measure them. Moreover, we can assume that a certain proportion of the
+population will never experience the event -- that is, they are a non-tool-user
+and so we will never identify tool use no matter how long we measure them for.
 
@@
 
-Since the earliest anecdotes of parrots using tools by Wallace in the 1880s\textsuperscript{59} and more systematic anecdotal reports in the 1970s\textsuperscript{60},
+Since the earliest anecdotes of parrots using tools by Wallace in the 1880s\textsuperscript{57} and more systematic anecdotal reports in the 1970s\textsuperscript{58},
 only 11 parrot species (3\% of all extant parrots) have been documented as tool
-users in the scientific literature. Our study used crowdsourcing to identify 17
-additional tool-using parrot species that are new to science, more than doubling
-the overall count to 28 species (7\%). These species consisted of cockatoos
-(\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), and neotropical parrots
-(\emph{Arinae}). Beyond the crowdsourcing survey, the strong phylogenetic signal in
-our dataset allowed us to use phylogenetic information, along with other
-variables, to infer the unobserved probabilities of tool use across the parrot
-order. Our phylogenetic survival cure model incorporated information on
-phylogenetic history, research effort, relative brain size, and feeding
-specialisation to rank parrot species that were most likely to be undetected
-tool users. The sum of probabilities from this model implied that between 15
-and 41 of the species without observed evidence of tool use are likely to be
-undetected tool users, suggesting that the true proportion of tool users may be
-as high as 17\%.
+users in the scientific literature. Our study collated data from a digital video
+platform to identify 17 additional tool-using parrot species that are new to
+science, more than doubling the overall count to 28 species (7\%). These species
+consisted of cockatoos (\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), and
+neotropical parrots (\emph{Arinae}). Beyond the video survey, the strong
+phylogenetic signal in our dataset allowed us to use phylogenetic information,
+along with other variables, to infer the unobserved probabilities of tool use
+across the parrot order. Our phylogenetic survival cure model incorporated
+information on phylogenetic history, research effort, relative brain size, and
+feeding specialisation to rank parrot species that were most likely to be
+undetected tool users. The sum of probabilities from this model implied that
+between 15 and 41 of the species without observed evidence of tool use are
+likely to be undetected tool users, suggesting that the true proportion of tool
+users may be as high as 17\%.
 
@@
 key assumption made in the literature to date: that only a minority of parrots
-are tool users\textsuperscript{30,31,34,37,38}.
+are tool users\textsuperscript{28,29,32,35,36}.
 The paucity of evidence for tool use across parrots in the literature initially
@@
 preliminary stage, our analysis therefore raises an alternative hypothesis for
-the observed tool use in \emph{Cacatua}\textsuperscript{30,38} and
-\emph{Nestor}\textsuperscript{26--29,31,34}, namely that tool behaviours have arisen due to the
+the observed tool use in \emph{Cacatua}\textsuperscript{28,36} and
+\emph{Nestor}\textsuperscript{24--27,29,32}, namely that tool behaviours have arisen due to the
 common ancestor having the capacity to use tools, rather than from independent
@@
 tool use in our phylogenetic model, supporting previous theories linking
-relative brain size to increased tool innovation in birds\textsuperscript{11--13} and primates\textsuperscript{61}. We acknowledge that
+relative brain size to increased tool innovation in birds\textsuperscript{11--13} and primates\textsuperscript{59}. We acknowledge that
 encephalisation quotient is not a perfect measure due to measurement error and
@@
 quotient has much greater coverage across the parrot phylogeny than more
-fine-grained measures like whole neuron count\textsuperscript{62} and there is no reason
+fine-grained measures like whole neuron count\textsuperscript{60} and there is no reason
 to think that measurement error would produce the consistent patterns across our
@@
 relationships, we encourage further work on the specific neural correlates of
-technical intelligence in parrots, e.g.,\textsuperscript{63}. In our phylogenetic
+technical intelligence in parrots, e.g.,\textsuperscript{61}. In our phylogenetic
 model, we also found that tool use was somewhat more likely among feeding
@@
 abilities and technical innovation rates are required to expand a generalist
-species' dietary niche\textsuperscript{16,18,64}. However, the trend contradicts theories linking tool use to
+species' dietary niche\textsuperscript{16,18,62}. However, the trend contradicts theories linking tool use to
 dietary specialisation, whereby species eating specific foods that require
@@
 
-All instances of tool use in our crowdsourcing survey met the established
-criteria for tool use in the literature: the manipulation of an unattached
-object as an extension of the animal's body to achieve a goal\textsuperscript{10}.
-However, a striking feature of the dataset is that the 17 additional species
-identified in the video survey were exclusively observed using tools for
-self-scratching. While parrots in the wild use tools to achieve a variety of
-goals, including extractive foraging and preening\textsuperscript{34,38},
-parrots in captivity only require tools to achieve the latter goal. Despite this
-difference in the type of tool use observed, self-scratching is nonetheless a
-major category of animal tool use. Self-scratching also meets the definition for
-a more complex type of embodied tool use known as `tooling', the deliberate
-generation of a mechanical interface by using an object to manipulate another
-target or surface\textsuperscript{65}. This makes it difficult to dismiss
-self-scratching as unimportant: to do so would require a redefinition of
-tool-use in non-human animals. Moreover, the fact that we found strong
-phylogenetic clustering of self-scratching tool use from the video survey with
-other examples of tool use from the literature supports a common underlying
-cognitive mechanism. In line with this, some of the species of parrots that use
-tools for self-scratching in captivity also use tools for other purposes in the
-wild\textsuperscript{30,31,34,38}.
+All instances of tool use in our video survey met the established criteria for
+tool use in the literature: the manipulation of an unattached object as an
+extension of the animal's body to achieve a goal\textsuperscript{10}. However, a
+striking feature of the dataset is that the 17 additional species identified in
+the video survey were exclusively observed using tools for self-scratching.
+While parrots in the wild use tools to achieve a variety of goals, including
+extractive foraging and preening\textsuperscript{32,36}, parrots in captivity
+only require tools to achieve the latter goal. Despite this difference in the
+type of tool use observed, self-scratching is nonetheless a major category of
+animal tool use. Self-scratching also meets the definition for a more complex
+type of embodied tool use known as `tooling', the deliberate generation of a
+mechanical interface by using an object to manipulate another target or surface\textsuperscript{63}. This makes it difficult to dismiss self-scratching as
+unimportant: to do so would require a redefinition of tool-use in non-human
+animals. Moreover, the fact that we found strong phylogenetic clustering of
+self-scratching tool use from the video survey with other examples of tool use
+from the literature supports a common underlying cognitive mechanism. In line
+with this, some of the species of parrots that use tools for self-scratching in
+captivity also use tools for other purposes in the wild\textsuperscript{28,29,32,36}.
 
@@
 over long periods of time, even across multiple different videos, suggesting
-that their behaviour was not random or accidental\textsuperscript{66}. Parrots
+that their behaviour was not random or accidental\textsuperscript{64}. Parrots
 preferentially employed self-scratching tools on areas of their body that were
@@
 handed parrots their tools in two of the videos, and none of the videos featured
-owners directly rewarding tool use behaviours with food. Finally, the high
-levels of phylogenetic signal in our data provide strong evidence that the
-observations from our video survey reflect biologically-endowed capacities for
-tool use rather than accidental or trained behaviours, which would likely appear
-uniformly across the phylogeny.
+owners directly rewarding tool use behaviours with food. It is unlikely that
+owners would specifically train parrots to scratch themselves with tools.
+Finally, the high levels of phylogenetic signal in our data provide strong
+evidence that the observations from our video survey reflect
+biologically-endowed capacities for tool use rather than accidental or trained
+behaviours, which would likely appear uniformly across the phylogeny.
 
 While missing data imputation is becoming more common in phylogenetic
-analyses\textsuperscript{67}, the important distinction between absence of
+analyses\textsuperscript{65}, the important distinction between absence of
 evidence and evidence of absence has not been given as much attention. Our
@@
 between true absences of tool use and absences of tool use due to a lack of
-research effort in the scientific literature or in crowdsourced videos. To
-achieve this, we explicitly modelled the measurement of the outcome variable
-along a research effort time series, such that species with lower research
-effort in the literature or in videos were likely to be censored. In line with
-our causal model, we also included relative brain size, feeding strategy, and
-phylogenetic history as predictors of unobserved tool use. We encourage
-researchers to test this model by directing future study efforts towards the
-parrot species with the highest probabilities of being undetected tool-users.
-Future work should also refine the causal model in Figure \ref{fig:plotDAG} to
-provide more certain estimates of tool use probabilities, either by including
-additional predictor variables or modelling further causes of measurement error
-in the taxonomic record, such as species abundance and geographic
-accessibility\textsuperscript{20}.
+research effort in the scientific literature or in videos. To achieve this, we
+explicitly modelled the measurement of the outcome variable along a research
+effort time series, such that species with lower research effort in the
+literature or in videos were likely to be censored. In line with our causal
+model, we also included relative brain size, feeding strategy, and phylogenetic
+history as predictors of unobserved tool use. We encourage researchers to test
+this model by directing future study efforts towards the parrot species with the
+highest probabilities of being undetected tool-users. Future work should also
+refine the causal model in Figure \ref{fig:plotDAG} to provide more certain
+estimates of tool use probabilities, either by including additional predictor
+variables or modelling further causes of measurement error in the taxonomic
+record, such as species abundance and geographic accessibility\textsuperscript{20}.
 
@@
 captured the full distribution of tool use in the parrot order. Our
-crowdsourcing survey more than doubled the number of known tool using parrot
+digital video survey more than doubled the number of known tool using parrot
 species from 11 to 28, and our phylogenetic model suggested that the true
@@
 drivers and origins of tool use in parrots. Beyond parrot tool use, the
-crowdsourcing and phylogenetic methods used in this study have the potential to
-be applied to other rarely observed behaviours, including tool use in other
-taxa\textsuperscript{68}, rhythmic entrainment in birds\textsuperscript{69--72}, teasing behaviours in primates\textsuperscript{73}, and
-tactical deception across all animals\textsuperscript{74--76}.
-We hope that these methods will continue to uncover a diverse array of ephemeral
-behaviours that have as yet gone undetected in the scientific literature.
+methods used in this study have the potential to be applied to other rarely
+observed behaviours, including tool use in other taxa\textsuperscript{66}, rhythmic
+entrainment in birds\textsuperscript{67--70},
+teasing behaviours in primates\textsuperscript{71}, and tactical deception across all
+animals\textsuperscript{72--74}. We hope that these methods
+will continue to uncover a diverse array of ephemeral behaviours that have as
+yet gone undetected in the scientific literature.
 
@@
 
-Our video search was conducted on YouTube in July 2020. Search terms included
+Our video search was conducted on YouTube in July 2020. Searches were conducted
+manually by the first author over a month-long period, using the same IP address
+and not logged in with a YouTube user account. Search terms included
 ``parrot using tool'' and variants (e.g., ``macaw using tool'', ``lorikeet using
@@
 of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all
-countries where bird ownership was reported as \textgreater5\%\textsuperscript{77}, namely,
+countries where bird ownership was reported as \textgreater5\%\textsuperscript{75}, namely,
 Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish,
-Portuguese, and Mandarin.
+Portuguese, and Mandarin. Browser search histories were not cleared between
+searches.
 
@@
 Borderline tool use was similarly defined, except that it involved the use of an
-object that was still attached to a substrate\textsuperscript{54}. For example, if
+object that was still attached to a substrate\textsuperscript{52}. For example, if
 individuals used a fallen feather or stick for self-scratching this was defined
@@
 to one's body (or, in the case of borderline tool use, rubbing repetitively
-against an attached object\textsuperscript{66}).
+against an attached object\textsuperscript{64}).
 
@@
 
+Since YouTube is constantly growing and evolving in both its uploaded content
+and its proprietary recommendation algorithms, the same search strategy today
+would not return exactly the same videos as our search in July 2020. It is
+possible that some videos have since been deleted or more videos of parrot tool
+use have since been uploaded. However, this does not affect our conclusions
+about the number of parrot species found to use tools in our initial search.
+
 \hypertarget{data-for-parrot-species}{%
@@
 data as a dichotomous variable (``generalist'' or ``specialist'') from the
-EltonTraits ecological database\textsuperscript{52}. As per the database, specialists
+EltonTraits ecological database\textsuperscript{50}. As per the database, specialists
 were defined as species whose diet comprised at least 70\% of a single food
@@
 for all known body mass (g) and brain mass (g) values across
-parrots\textsuperscript{46--51}. For all species for which we obtained body and brain mass data, we
+parrots\textsuperscript{44--49}. For all species for which we obtained body and brain mass data, we
 calculated the encephalisation quotient (EQ) using the following
-formula\textsuperscript{78}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
+formula\textsuperscript{76}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
 found body mass and brain mass data for a total of 194 parrot species. This
@@
 For modelling purposes, we coded research effort in both the scientific
-literature and the crowdsourced videos. For the scientific literature, we
+literature and the YouTube videos. For the scientific literature, we
 operationalised research effort as the number of papers published for each
@@
 used the scientific database Scopus for coding the number of published papers.
-For the crowdsourced videos, we coded research effort as the number of search
-hits for each species on YouTube. If tool use had been identified on YouTube, we
-estimated the number of search hits when the first video of tool use was
-published on YouTube, assuming linear growth of search hits since the inception
-of YouTube. If tool use had not been identified, we used the current number of
-search hits.
-
-For phylogenetic data, we used the phylogenetic tool at www.birdtree.org\textsuperscript{53} to compile 1000 posterior draws of phylogenetic trees for 174 of the
+For the videos, we coded research effort as the number of search hits for each
+species on YouTube. If tool use had been identified on YouTube, we estimated the
+number of search hits when the first video of tool use was published on YouTube,
+assuming linear growth of search hits since the inception of YouTube. If tool
+use had not been identified, we used the current number of search hits.
+
+For phylogenetic data, we used the phylogenetic tool at www.birdtree.org\textsuperscript{51} to compile 1000 posterior draws of phylogenetic trees for 174 of the
 194 parrot species for which both EQ and genomic data exist. A single maximum
@@
 
-We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{79} to
+We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{77} to
 calculate phylogenetic signal, for both the pre-survey and post-survey tool use
@@
 causal model of observed tool use (Figure \ref{fig:plotDAG}). We assumed that
-observed tool use in the scientific literature and in the crowdsourced videos is
-caused by both the unobserved presence or absence of tool use and research
-effort, proxied by the number of papers published on a species and the number of
-videos published on a species. Tool users are more likely to be observed if they
-are well studied, but understudied tool users may go undetected. In addition,
-based on theory, we also assumed that unobserved tool use is caused by feeding
+observed tool use in the scientific literature and in the videos is caused by
+both the unobserved presence or absence of tool use and research effort, proxied
+by the number of papers published on a species and the number of videos
+published on a species. Tool users are more likely to be observed if they are
+well studied, but understudied tool users may go undetected. In addition, based
+on theory, we also assumed that unobserved tool use is caused by feeding
 strategy and relative brain size\textsuperscript{11--14,16--18}. Finally, we
@@
 not (0) tool use has yet been observed in the scientific literature for species
-\(i\). For the crowdsourced videos, we declare \(\text{N}_{\text{Vid},i}\) as the
+\(i\). For the videos, we declare \(\text{N}_{\text{Vid},i}\) as the
 number of videos published before and up to tool use identification for species
@@
 stating whether (1) or not (0) tool use has yet been observed in the
-crowdsourced videos for species \(i\). Additionally, \(\text{F}_i\) and
+videos for species \(i\). Additionally, \(\text{F}_i\) and
 \(\text{EQ}_i\) are feeding strategy and encephalisation quotient values for
@@
 probability \(p_i\). We also assume that tool use is identified in the scientific
-literature and the crowdsourced videos at constant rates \(\lambda_{\text{Lit}}\)
+literature and the videos at constant rates \(\lambda_{\text{Lit}}\)
 and \(\lambda_{\text{Vid}}\) following exponential survival functions. Given these
@@
 The Exponential-CCDF function allows for the censored nature of the data. The
-same data generating process is assumed to underlie the crowdsourced videos.
+same data generating process is assumed to underlie the videos.
 
@@
 and \(\lambda\) (the rate of the exponential distribution). We use an
-Ornstein-Uhlenbeck Gaussian process\textsuperscript{80} to model phylogenetic
+Ornstein-Uhlenbeck Gaussian process\textsuperscript{78} to model phylogenetic
 covariance. Below, we specify the full model with priors:
@@
 posterior distribution of this model using Hamiltonian Monte Carlo as
-implemented in Stan version 2.26.1\textsuperscript{81}. We ran the model for 4000
+implemented in Stan version 2.26.1\textsuperscript{79}. We ran the model for 4000
 samples, with 2000 warmup samples, and iterated the model over 100 posterior
@@
 parrots, we fitted three exploratory ancestral state reconstruction models. We
-used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{82},
+used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{80},
 iterating the function over 100 posterior parrot phylogenies. This function
@@
 
-All analyses were conducted in R v4.2.1.\textsuperscript{83}. Visualisations were
-produced using the \emph{ggtree}\textsuperscript{84}, \emph{ggplot2}\textsuperscript{85}, and \emph{cowplot}\textsuperscript{86} packages. The manuscript was reproducibly generated using the
-\emph{targets}\textsuperscript{87} and \emph{papaja}\textsuperscript{88} packages. Code to reproduce all
+All analyses were conducted in R v4.2.1.\textsuperscript{81}. Visualisations were
+produced using the \emph{ggtree}\textsuperscript{82}, \emph{ggplot2}\textsuperscript{83}, and \emph{cowplot}\textsuperscript{84} packages. The manuscript was reproducibly generated using the
+\emph{targets}\textsuperscript{85} and \emph{papaja}\textsuperscript{86} packages. Code to reproduce all
 analyses and figures can be found here:
@@
 \CSLLeftMargin{1. }%
-\CSLRightInline{MacLean, E.
-L.
-\emph{et al.} \href{https://doi.org/10.1007/s10071-011-0448-8}{How does cognition evolve?
-Phylogenetic comparative psychology}.
-\emph{Animal Cognition} \textbf{15}, 223--238 (2012).}
+\CSLRightInline{MacLean, E.L., Matthews, L.J., Hare, B.A., Nunn, C.L., Anderson, R.C., Aureli, F., Brannon, E.M., Call, J., Drea, C.M., Emery, N.J., et al.
+(2012).
+How does cognition evolve?
+Phylogenetic comparative psychology.
+Animal Cognition \emph{15}, 223--238.
+\href{https://doi.org/10.1007/s10071-011-0448-8}{10.1007/s10071-011-0448-8}.}
 
@@
 \CSLLeftMargin{2. }%
-\CSLRightInline{Lefebvre, L. \href{https://doi.org/10.1098/rsbl.2010.0556}{Taxonomic counts of cognition in the wild}. \emph{Biology Letters} \textbf{7}, 631--633 (2011).}
+\CSLRightInline{Lefebvre, L. (2011). Taxonomic counts of cognition in the wild. Biology Letters \emph{7}, 631--633. \href{https://doi.org/10.1098/rsbl.2010.0556}{10.1098/rsbl.2010.0556}.}
 
@@
 \CSLLeftMargin{3. }%
-\CSLRightInline{Logan, C.
-J.
-\emph{et al.} \href{https://doi.org/10.3819/CCBR.2018.130008}{Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization}.
-\emph{Comparative Cognition \& Behavior Reviews} \textbf{13}, 55--89 (2018).}
+\CSLRightInline{Logan, C.J., Avin, S., Boogert, N., Buskell, A., Cross, F.R., Currie, A., Jelbert, S., Lukas, D., Mares, R., Navarrete, A.F., et al.
+(2018).
+Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization.
+Comparative Cognition \& Behavior Reviews \emph{13}, 55--89.
+\href{https://doi.org/10.3819/CCBR.2018.130008}{10.3819/CCBR.2018.130008}.}
 
@@
 \CSLLeftMargin{4. }%
-\CSLRightInline{Healy, S.
-D.
-\& Rowe, C.
-\href{https://doi.org/10.1098/rspb.2006.3748}{A critique of comparative studies of brain size}.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{274}, 453--464 (2007).}
+\CSLRightInline{Healy, S.D., and Rowe, C.
+(2007).
+A critique of comparative studies of brain size.
+Proceedings of the Royal Society B: Biological Sciences \emph{274}, 453--464.
+\href{https://doi.org/10.1098/rspb.2006.3748}{10.1098/rspb.2006.3748}.}
 
@@
 \CSLLeftMargin{5. }%
-\CSLRightInline{Powell, L.
-E., Isler, K.
-\& Barton, R.
-A.
-\href{https://doi.org/10.1098/rspb.2017.1765}{Re-evaluating the link between brain size and behavioural ecology in primates}.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{284}, 20171765 (2017).}
+\CSLRightInline{Powell, L.E., Isler, K., and Barton, R.A.
+(2017).
+Re-evaluating the link between brain size and behavioural ecology in primates.
+Proceedings of the Royal Society B: Biological Sciences \emph{284}, 20171765.
+\href{https://doi.org/10.1098/rspb.2017.1765}{10.1098/rspb.2017.1765}.}
 
@@
 \CSLLeftMargin{6. }%
-\CSLRightInline{Goodall, J. Tool-using and aimed throwing in a community of free-living chimpanzees. \emph{Nature} \textbf{201}, 1264--1266 (1964).}
+\CSLRightInline{Goodall, J. (1964). Tool-using and aimed throwing in a community of free-living chimpanzees. Nature \emph{201}, 1264--1266.}
 
@@
 \CSLLeftMargin{7. }%
-\CSLRightInline{Hunt, G. R. \href{https://doi.org/10.1038/379249a0}{Manufacture and use of hook-tools by {N}ew {C}aledonian crows}. \emph{Nature} \textbf{379}, 249--251 (1996).}
+\CSLRightInline{Hunt, G.R. (1996). Manufacture and use of hook-tools by {N}ew {C}aledonian crows. Nature \emph{379}, 249--251. \href{https://doi.org/10.1038/379249a0}{10.1038/379249a0}.}
 
@@
 \CSLLeftMargin{8. }%
-\CSLRightInline{Smolker, R., Richards, A., Connor, R., Mann, J.
-\& Berggren, P.
-\href{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}{Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?} \emph{Ethology} \textbf{103}, 454--465 (1997).}
+\CSLRightInline{Smolker, R., Richards, A., Connor, R., Mann, J., and Berggren, P.
+(1997).
+Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?
+Ethology \emph{103}, 454--465.
+\href{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}{10.1111/j.1439-0310.1997.tb00160.x}.}
 
@@
 \CSLLeftMargin{9. }%
-\CSLRightInline{Finn, J.
-K., Tregenza, T.
-\& Norman, M.
-D.
-\href{https://doi.org/10.1016/j.cub.2009.10.052}{Defensive tool use in a coconut-carrying octopus}.
-\emph{Current Biology} \textbf{19}, R1069--R1070 (2009).}
+\CSLRightInline{Finn, J.K., Tregenza, T., and Norman, M.D.
+(2009).
+Defensive tool use in a coconut-carrying octopus.
+Current Biology \emph{19}, R1069--R1070.
+\href{https://doi.org/10.1016/j.cub.2009.10.052}{10.1016/j.cub.2009.10.052}.}
 
@@
 \CSLLeftMargin{10. }%
-\CSLRightInline{Shumaker, R.
-W., Walkup, K.
-R., Beck, B.
-B.
-\& Burghardt, G.
-M.
-\emph{Animal tool behavior: The use and manufacture of tools by animals}.
-(Johns Hopkins University Press).
-doi:\href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}
+\CSLRightInline{Shumaker, R.W., Walkup, K.R., Beck, B.B., and Burghardt, G.M.
+Animal tool behavior: The use and manufacture of tools by animals (Johns Hopkins University Press) \href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}
 
@@
 \CSLLeftMargin{11. }%
-\CSLRightInline{Lefebvre, L., Nicolakakis, N. \& Boire, D. \href{https://doi.org/10.1163/156853902320387918}{Tools and brains in birds}. \emph{Behaviour} \textbf{139}, 939--973 (2002).}
+\CSLRightInline{Lefebvre, L., Nicolakakis, N., and Boire, D.
+(2002).
+Tools and brains in birds.
+Behaviour \emph{139}, 939--973.
+\href{https://doi.org/10.1163/156853902320387918}{10.1163/156853902320387918}.}
 
@@
 \CSLLeftMargin{12. }%
-\CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E.
-\& Finkelstein, A.
-\href{https://doi.org/10.1006/anbe.1996.0330}{Feeding innovations and forebrain size in birds}.
-\emph{Animal Behaviour} \textbf{53}, 549--560 (1997).}
+\CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E., and Finkelstein, A.
+(1997).
+Feeding innovations and forebrain size in birds.
+Animal Behaviour \emph{53}, 549--560.
+\href{https://doi.org/10.1006/anbe.1996.0330}{10.1006/anbe.1996.0330}.}
 
@@
 \CSLLeftMargin{13. }%
-\CSLRightInline{Lefebvre, L., Reader, S.
-M.
-\& Sol, D.
-\href{https://doi.org/10.1159/000076784}{Brains, innovations and evolution in birds and primates}.
-\emph{Brain, Behavior and Evolution} \textbf{63}, 233--246 (2004).}
+\CSLRightInline{Lefebvre, L., Reader, S.M., and Sol, D.
+(2004).
+Brains, innovations and evolution in birds and primates.
+Brain, Behavior and Evolution \emph{63}, 233--246.
+\href{https://doi.org/10.1159/000076784}{10.1159/000076784}.}
 
@@
 \CSLLeftMargin{14. }%
-\CSLRightInline{Sol, D., Duncan, R.
-P., Blackburn, T.
-M., Cassey, P.
-\& Lefebvre, L.
-\href{https://doi.org/10.1073/pnas.0408145102}{Big brains, enhanced cognition, and response of birds to novel environments}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{102}, 5460--5465 (2005).}
+\CSLRightInline{Sol, D., Duncan, R.P., Blackburn, T.M., Cassey, P., and Lefebvre, L.
+(2005).
+Big brains, enhanced cognition, and response of birds to novel environments.
+Proceedings of the National Academy of Sciences \emph{102}, 5460--5465.
+\href{https://doi.org/10.1073/pnas.0408145102}{10.1073/pnas.0408145102}.}
 
@@
 \CSLRightInline{Sol, D.
-\href{https://doi.org/10.1098/rsbl.2008.0621}{Revisiting the cognitive buffer hypothesis for the evolution of large brains}.
-\emph{Biology Letters} \textbf{5}, 130--133 (2009).}
+(2009).
+Revisiting the cognitive buffer hypothesis for the evolution of large brains.
+Biology Letters \emph{5}, 130--133.
+\href{https://doi.org/10.1098/rsbl.2008.0621}{10.1098/rsbl.2008.0621}.}
 
@@
 \CSLLeftMargin{16. }%
-\CSLRightInline{Ducatez, S., Clavel, J.
-\& Lefebvre, L.
-\href{https://doi.org/10.1111/1365-2656.12255}{Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?} \emph{Journal of Animal Ecology} \textbf{84}, 79--89 (2015).}
+\CSLRightInline{Ducatez, S., Clavel, J., and Lefebvre, L.
+(2015).
+Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?
+Journal of Animal Ecology \emph{84}, 79--89.
+\href{https://doi.org/10.1111/1365-2656.12255}{10.1111/1365-2656.12255}.}
 
@@
 \CSLLeftMargin{17. }%
-\CSLRightInline{Overington, S.
-E., Griffin, A.
-S., Sol, D.
-\& Lefebvre, L.
-\href{https://doi.org/10.1093/beheco/arr130}{Are innovative species ecological generalists?
-A test in {N}orth {A}merican birds}.
-\emph{Behavioral Ecology} \textbf{22}, 1286--1293 (2011).}
+\CSLRightInline{Overington, S.E., Griffin, A.S., Sol, D., and Lefebvre, L.
+(2011).
+Are innovative species ecological generalists?
+A test in {N}orth {A}merican birds.
+Behavioral Ecology \emph{22}, 1286--1293.
+\href{https://doi.org/10.1093/beheco/arr130}{10.1093/beheco/arr130}.}
 
@@
 \CSLLeftMargin{18. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.
-M.
-\& Fichtel, C.
+\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
+(2020).
 Linking ecology and cognition: Does ecological specialisation predict cognitive test performance?
-\emph{Behavioral Ecology and Sociobiology} \textbf{74}, 154 (2020).}
+Behavioral Ecology and Sociobiology \emph{74}, 154.}
 
@@
 \CSLRightInline{Mettke-Hofmann, C.
-\href{https://doi.org/10.1002/wcs.1289}{Cognitive ecology: Ecological factors, life-styles, and cognition}.
-\emph{WIREs Cognitive Science} \textbf{5}, 345--360 (2014).}
+(2014).
+Cognitive ecology: Ecological factors, life-styles, and cognition.
+WIREs Cognitive Science \emph{5}, 345--360.
+\href{https://doi.org/10.1002/wcs.1289}{10.1002/wcs.1289}.}
 
@@
 \CSLLeftMargin{20. }%
-\CSLRightInline{Ducatez, S. \& Lefebvre, L. \href{https://doi.org/10.1371/journal.pone.0089955}{Patterns of research effort in birds}. \emph{PLOS ONE} \textbf{9}, e89955 (2014).}
+\CSLRightInline{Ducatez, S., and Lefebvre, L.
+(2014).
+Patterns of research effort in birds.
+PLOS ONE \emph{9}, e89955.
+\href{https://doi.org/10.1371/journal.pone.0089955}{10.1371/journal.pone.0089955}.}
 
@@
 \CSLLeftMargin{21. }%
-\CSLRightInline{Nelson, X.
-J.
-\& Fijn, N.
-\href{https://doi.org/10.1016/j.anbehav.2012.12.009}{The use of visual media as a tool for investigating animal behaviour}.
-\emph{Animal Behaviour} \textbf{85}, 525--536 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dickinson2010}{}}%
+\CSLRightInline{Nelson, X.J., and Fijn, N.
+(2013).
+The use of visual media as a tool for investigating animal behaviour.
+Animal Behaviour \emph{85}, 525--536.
+\href{https://doi.org/10.1016/j.anbehav.2012.12.009}{10.1016/j.anbehav.2012.12.009}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
 \CSLLeftMargin{22. }%
-\CSLRightInline{Dickinson, J.
-L., Zuckerberg, B.
-\& Bonter, D.
-N.
-\href{https://doi.org/10.1146/annurev-ecolsys-102209-144636}{Citizen science as an ecological research tool: Challenges and benefits}.
-\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{41}, 149--172 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
+\CSLRightInline{Krueger, K., Esch, L., and Byrne, R.
+(2019).
+Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms.
+PLOS ONE \emph{14}, 1--20.
+\href{https://doi.org/10.1371/journal.pone.0218954}{10.1371/journal.pone.0218954}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pokharel2022}{}}%
 \CSLLeftMargin{23. }%
-\CSLRightInline{Krueger, K., Esch, L.
-\& Byrne, R.
-\href{https://doi.org/10.1371/journal.pone.0218954}{Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms}.
-\emph{PLOS ONE} \textbf{14}, 1--20 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Klump2021}{}}%
+\CSLRightInline{Pokharel, S.S., Sharma, N., and Sukumar, R.
+(2022).
+Viewing the rare through public lenses: Insights into dead calf carrying and other thanatological responses in asian elephants using YouTube videos.
+Royal Society Open Science \emph{9}, 211740.
+\href{https://doi.org/10.1098/rsos.211740}{10.1098/rsos.211740}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2009}{}}%
 \CSLLeftMargin{24. }%
-\CSLRightInline{Klump, B.
-C.
-\emph{et al.} \href{https://doi.org/10.1126/science.abe7808}{Innovation and geographic spread of a complex foraging culture in an urban parrot}.
-\emph{Science} \textbf{373}, 456--460 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Klump2022}{}}%
+\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
+(2009).
+Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem.
+Biology Letters \emph{5}, 455--458.
+\href{https://doi.org/10.1098/rsbl.2009.0114}{10.1098/rsbl.2009.0114}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2010}{}}%
 \CSLLeftMargin{25. }%
-\CSLRightInline{Klump, B.
-C., Major, R.
-E., Farine, D.
-R., Martin, J.
+\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
+(2010).
+Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task.
+Animal Behaviour \emph{80}, 783--789.
+\href{https://doi.org/10.1016/j.anbehav.2010.08.007}{10.1016/j.anbehav.2010.08.007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011a}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Auersperg, A.M.I., Huber, L., and Gajdon, G.K.
+(2011).
+Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis}).
+Biology Letters \emph{7}, 825--828.
+\href{https://doi.org/10.1098/rsbl.2011.0388}{10.1098/rsbl.2011.0388}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011b}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{Auersperg, A.M.I., Bayern, A.M.P.
+von, Gajdon, G.K., Huber, L., and Kacelnik, A.
+(2011).
+Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm.
+PLOS ONE \emph{6}, 1--8.
+\href{https://doi.org/10.1371/journal.pone.0020231}{10.1371/journal.pone.0020231}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2012}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Auersperg, A.M.I., Szabo, B., von Bayern, A.M.P., and Kacelnik, A.
+(2012).
+Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo.
+Current Biology \emph{22}, R903--R904.
+\href{https://doi.org/10.1016/j.cub.2012.09.002}{10.1016/j.cub.2012.09.002}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bastos2021}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Bastos, A.P., Horváth, K., Webb, J.L., Wood, P.M., and Taylor, A.H.
+(2021).
+Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
+Scientific Reports \emph{11}, 18035.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-BentleyCondit2010}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Bentley-Condit, V., and Smith, E.O.
+(2010).
+Animal tool use: Current definitions and an updated comprehensive catalog.
+Behaviour \emph{147}, 185--32A.
+\href{https://doi.org/10.1163/000579509X12512865686555}{10.1163/000579509X12512865686555}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Borsari2005}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Borsari, A., and Ottoni, E.B.
+(2005).
+Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus}).
+Animal Cognition \emph{8}, 48--52.
+\href{https://doi.org/10.1007/s10071-004-0221-3}{10.1007/s10071-004-0221-3}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodman2018}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{Goodman, M., Hayward, T., and Hunt, G.R.
+(2018).
+Habitual tool use innovated by free-living {N}ew {Z}ealand kea.
+Scientific Reports \emph{8}, 13935.
+\href{https://doi.org/10.1038/s41598-018-32363-9}{10.1038/s41598-018-32363-9}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Heinsohn2017}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Heinsohn, R., Zdenek, C.N., Cunningham, R.B., Endler, J.A., and Langmore, N.E.
+(2017).
+Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music.
+Science Advances \emph{3}, e1602399.
+\href{https://doi.org/10.1126/sciadv.1602399}{10.1126/sciadv.1602399}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Janzen1976}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{Janzen, M.J., Janzen, D.H., and Pond, C.M. (1976). Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). Biotropica \emph{8}, 70.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lambert2015}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{Lambert, M.L., Seed, A.M., and Slocombe, K.E.
+(2015).
+A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa}).
+Biology Letters \emph{11}, 20150861.
+\href{https://doi.org/10.1098/rsbl.2015.0861}{10.1098/rsbl.2015.0861}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-OHara2021}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{O'Hara, M., Mioduszewska, B., Mundry, R., Yohanna, Haryoko, T., Rachmatika, R., Prawiradilaga, D.M., Huber, L., and Auersperg, A.M.I.
+(2021).
+Wild {G}offin's cockatoos flexibly manufacture and use tool sets.
+Current Biology \emph{31}, 4512--4520.e6.
+\href{https://doi.org/10.1016/j.cub.2021.08.009}{10.1016/j.cub.2021.08.009}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Anderson, P.
+(2003).
+A bird in the house: An anthropological perspective on companion parrots.
+Society \& Animals \emph{11}, 393--418.
+\href{https://doi.org/10.1163/156853003322796109}{10.1163/156853003322796109}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{Carrete, M., and Tella, J.
+(2008).
+Wild-bird trade and exotic invasions: A new link of conservation concern?
+Frontiers in Ecology and the Environment \emph{6}, 207--211.
+\href{https://doi.org/10.1890/070075}{10.1890/070075}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{Drews, C.
+(2001).
+Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers.
+Society \& Animals \emph{9}, 107--126.
+\href{https://doi.org/10.1163/156853001753639233}{10.1163/156853001753639233}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{Kelly, D., McCarthy, E., Menzel, K., and Engebretson, M.
+(2014).
+\href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{Li, L., and Jiang, Z.
+(2014).
+International trade of {CITES} listed bird species in {C}hina.
+PLOS ONE \emph{9}, 1--8.
+\href{https://doi.org/10.1371/journal.pone.0085012}{10.1371/journal.pone.0085012}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
+\CSLLeftMargin{42. }%
+\CSLRightInline{Su, S., Cassey, P., Vall-llosera, M., and Blackburn, T.M.
+(2015).
+Going cheap: Determinants of bird price in the {T}aiwanese pet market.
+PLOS ONE \emph{10}, 1--17.
+\href{https://doi.org/10.1371/journal.pone.0127482}{10.1371/journal.pone.0127482}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{Young, A.M., Hobson, E.A., Lackey, L.B., and Wright, T.F.
+(2012).
+Survival on the ark: Life-history trends in captive parrots.
+Animal Conservation \emph{15}, 28--43.
+\href{https://doi.org/10.1111/j.1469-1795.2011.00477.x}{10.1111/j.1469-1795.2011.00477.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{Flammer, K., Whitt-Smith, D., and Papich, M.
+(2001).
+Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection.
+Journal of Avian Medicine and Surgery \emph{15}, 276--282.
+\href{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}{10.1647/1082-6742(2001)015{[}0276:PCODIS{]}2.0.CO;2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{Iwaniuk, A.N., Dean, K.M., and Nelson, J.E.
+(2005).
+Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
+Brain, Behavior and Evolution \emph{65}, 40--59.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P.R., and Ihunwo, A.O.
+(2018).
+Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh}).
+Frontiers in Neuroanatomy \emph{12}, 7.
+\href{https://doi.org/10.3389/fnana.2018.00007}{10.3389/fnana.2018.00007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{Olkowicz, S., Kocourek, M., Lučan, R.K., Porteš, M., Fitch, W.T., Herculano-Houzel, S., and Němec, P.
+(2016).
+Birds have primate-like numbers of neurons in the forebrain.
+Proceedings of the National Academy of Sciences \emph{113}, 7255--7260.
+\href{https://doi.org/10.1073/pnas.1517131113}{10.1073/pnas.1517131113}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
+\CSLLeftMargin{48. }%
+\CSLRightInline{Schuck-Paim, C., Alonso, W.J., and Ottoni, E.B.
+(2008).
+Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots.
+Brain, Behavior and Evolution \emph{71}, 200--215.
+\href{https://doi.org/10.1159/000119710}{10.1159/000119710}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{Silva, T., Guzmán, A., Urantówka, A.D., and Mackiewicz, P.
+(2017).
+A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny.
+PeerJ \emph{5}, e3475.
+\href{https://doi.org/10.7717/peerj.3475}{10.7717/peerj.3475}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{Wilman, H., Belmaker, J., Simpson, J., Rosa, C.
+de la, Rivadeneira, M.M., and Jetz, W.
+(2016).
+EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals.
+\href{https://doi.org/10.6084/m9.figshare.c.3306933.v1}{10.6084/m9.figshare.c.3306933.v1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
+\CSLLeftMargin{51. }%
+\CSLRightInline{Jetz, W., Thomas, G.H., Joy, J.B., Hartmann, K., and Mooers, A.O. (2012). The global diversity of birds in space and time. Nature \emph{491}, 444--448.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
+\CSLLeftMargin{52. }%
+\CSLRightInline{Seed, A., and Byrne, R. (2010). Animal tool-use. Current Biology \emph{20}, R1032--R1039. \href{https://doi.org/10.1016/j.cub.2010.09.042}{10.1016/j.cub.2010.09.042}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
+\CSLLeftMargin{53. }%
+\CSLRightInline{Bercovitz, A.B. (1987). Avian sex identification techniques. In Companion bird medicine, E. W. Burr, ed. (Iowa State University Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
+\CSLLeftMargin{54. }%
+\CSLRightInline{Hoyo, J.D., and Bierregaard, R. (2011). Handbook of the birds of the world (Lynx Edicions).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
+\CSLLeftMargin{55. }%
+\CSLRightInline{Amico, M., and Van Keilegom, I.
+(2018).
+Cure models in survival analysis.
+Annual Review of Statistics and Its Application \emph{5}, 311--342.
+\href{https://doi.org/10.1146/annurev-statistics-031017-100101}{10.1146/annurev-statistics-031017-100101}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
+\CSLLeftMargin{56. }%
+\CSLRightInline{Schmidt, P., and Witte, A.D.
+(1989).
+Predicting criminal recidivism using {``split population''} survival time models.
+Journal of Econometrics \emph{40}, 141--159.
+\href{https://doi.org/10.1016/0304-4076(89)90034-1}{10.1016/0304-4076(89)90034-1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
+\CSLLeftMargin{57. }%
+\CSLRightInline{Wallace, A.R. (1869). The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature (MacMillan; Co.).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodall1971}{}}%
+\CSLLeftMargin{58. }%
+\CSLRightInline{Goodall, J.
+(1971).
+Tool-using in primates and other vertebrates.
+In Advances in the study of behavior., D.
+S.
+Lehrman, R.
+A.
+Hinde, and E.
+Shaw, eds.
+(Academic Press), pp.
+195--249.
+\href{https://doi.org/10.1016/S0065-3454(08)60157-6}{10.1016/S0065-3454(08)60157-6}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
+\CSLLeftMargin{59. }%
+\CSLRightInline{Reader, S.M., and Laland, K.N.
+(2002).
+Social intelligence, innovation, and enhanced brain size in primates.
+Proceedings of the National Academy of Sciences \emph{99}, 4436--4441.
+\href{https://doi.org/10.1073/pnas.062041299}{10.1073/pnas.062041299}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
+\CSLLeftMargin{60. }%
+\CSLRightInline{Sol, D., Olkowicz, S., Sayol, F., Kocourek, M., Zhang, Y., Marhounová, L., Osadnik, C., Corssmit, E., Garcia-Porta, J., Martin, T.E., et al.
+(2022).
+Neuron numbers link innovativeness with both absolute and relative brain size in birds.
+Nature Ecology \& Evolution \emph{6}, 1381--1389.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
+\CSLLeftMargin{61. }%
+\CSLRightInline{Cabrera-Álvarez, M.J., and Clayton, N.S.
+(2020).
+Neural processes underlying tool use in humans, macaques, and corvids.
+Frontiers in Psychology \emph{11}, 560669.
+\href{https://doi.org/10.3389/fpsyg.2020.560669}{10.3389/fpsyg.2020.560669}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
+\CSLLeftMargin{62. }%
+\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
+(2021).
+Linking cognition to ecology in wild sympatric mouse lemur species.
+Proceedings of the Royal Society B: Biological Sciences \emph{288}, 20211728.
+\href{https://doi.org/10.1098/rspb.2021.1728}{10.1098/rspb.2021.1728}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
+\CSLLeftMargin{63. }%
+\CSLRightInline{Fragaszy, D.M., and Mangalam, M.
+(2018).
+Tooling.
+In Advances in the study of behavior., M.
+Naguib, L.
+Barrett, S.
+D.
+Healy, J.
+Podos, L.
+W.
+Simmons, and M.
+Zuk, eds.
+(Academic Press), pp.
+177--241.
+\href{https://doi.org/10.1016/bs.asb.2018.01.001}{10.1016/bs.asb.2018.01.001}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{Sándor, K., and Miklósi, Á.
+(2020).
+How to report anecdotal observations?
+A new approach based on a lesson from "puffin tool use".
+Frontiers in Psychology \emph{11}, 555487.
+\href{https://doi.org/10.3389/fpsyg.2020.555487}{10.3389/fpsyg.2020.555487}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
+\CSLLeftMargin{65. }%
+\CSLRightInline{Debastiani, V.J., Bastazini, V.A.G., and Pillar, V.D.
+(2021).
+Using phylogenetic information to impute missing functional trait values in ecological databases.
+Ecological Informatics \emph{63}, 101315.
+\href{https://doi.org/10.1016/j.ecoinf.2021.101315}{10.1016/j.ecoinf.2021.101315}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
+\CSLLeftMargin{66. }%
+\CSLRightInline{Hunt, G.R., Gray, R.D., and Taylor, A.H.
+(2013).
+Why is tool use rare in animals?
+In Tool use in animals: Cognition and ecology, C.
 M.
-\& Aplin, L.
-M.
-Is bin-opening in cockatoos leading to an innovation arms race with humans?
-\emph{Current Biology} \textbf{32}, R910--R911 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2009}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Gajdon, G.
-K.
-\& Huber, L.
-\href{https://doi.org/10.1098/rsbl.2009.0114}{Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem}.
-\emph{Biology Letters} \textbf{5}, 455--458 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2010}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Gajdon, G.
-K.
-\& Huber, L.
-\href{https://doi.org/10.1016/j.anbehav.2010.08.007}{Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task}.
-\emph{Animal Behaviour} \textbf{80}, 783--789 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011a}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Huber, L.
-\& Gajdon, G.
-K.
-\href{https://doi.org/10.1098/rsbl.2011.0388}{Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis})}.
-\emph{Biology Letters} \textbf{7}, 825--828 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011b}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Bayern, A.
-M.
-P.
-von, Gajdon, G.
-K., Huber, L.
-\& Kacelnik, A.
-\href{https://doi.org/10.1371/journal.pone.0020231}{Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm}.
-\emph{PLOS ONE} \textbf{6}, 1--8 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2012}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Auersperg, A.
-M.
-I., Szabo, B., von Bayern, A.
-M.
-P.
-\& Kacelnik, A.
-\href{https://doi.org/10.1016/j.cub.2012.09.002}{Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo}.
-\emph{Current Biology} \textbf{22}, R903--R904 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bastos2021}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Bastos, A.
-P., Horváth, K., Webb, J.
-L., Wood, P.
-M.
-\& Taylor, A.
-H.
-Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
-\emph{Scientific Reports} \textbf{11}, 18035 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BentleyCondit2010}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Bentley-Condit, V.
-\& Smith, E.
-O.
-\href{https://doi.org/10.1163/000579509X12512865686555}{Animal tool use: Current definitions and an updated comprehensive catalog}.
-\emph{Behaviour} \textbf{147}, 185--32A (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Borsari2005}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Borsari, A.
-\& Ottoni, E.
-B.
-\href{https://doi.org/10.1007/s10071-004-0221-3}{Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus})}.
-\emph{Animal Cognition} \textbf{8}, 48--52 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodman2018}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Goodman, M., Hayward, T.
-\& Hunt, G.
-R.
-\href{https://doi.org/10.1038/s41598-018-32363-9}{Habitual tool use innovated by free-living {N}ew {Z}ealand kea}.
-\emph{Scientific Reports} \textbf{8}, 13935 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Heinsohn2017}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{Heinsohn, R., Zdenek, C.
-N., Cunningham, R.
-B., Endler, J.
-A.
-\& Langmore, N.
-E.
-\href{https://doi.org/10.1126/sciadv.1602399}{Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music}.
-\emph{Science Advances} \textbf{3}, e1602399 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Janzen1976}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Janzen, M. J., Janzen, D. H. \& Pond, C. M. Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). \emph{Biotropica} \textbf{8}, 70 (1976).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lambert2015}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Lambert, M.
-L., Seed, A.
-M.
-\& Slocombe, K.
-E.
-\href{https://doi.org/10.1098/rsbl.2015.0861}{A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa})}.
-\emph{Biology Letters} \textbf{11}, 20150861 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-OHara2021}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{O'Hara, M.
-\emph{et al.} \href{https://doi.org/10.1016/j.cub.2021.08.009}{Wild {G}offin's cockatoos flexibly manufacture and use tool sets}.
-\emph{Current Biology} \textbf{31}, 4512--4520.e6 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Anderson, P.
-\href{https://doi.org/10.1163/156853003322796109}{A bird in the house: An anthropological perspective on companion parrots}.
-\emph{Society \& Animals} \textbf{11}, 393--418 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Carrete, M.
-\& Tella, J.
-\href{https://doi.org/10.1890/070075}{Wild-bird trade and exotic invasions: A new link of conservation concern?} \emph{Frontiers in Ecology and the Environment} \textbf{6}, 207--211 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Drews, C.
-\href{https://doi.org/10.1163/156853001753639233}{Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers}.
-\emph{Society \& Animals} \textbf{9}, 107--126 (2001).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Kelly, D., McCarthy, E., Menzel, K.
-\& Engebretson, M.
-\href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?} (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Li, L. \& Jiang, Z. \href{https://doi.org/10.1371/journal.pone.0085012}{International trade of {CITES} listed bird species in {C}hina}. \emph{PLOS ONE} \textbf{9}, 1--8 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Su, S., Cassey, P., Vall-llosera, M.
-\& Blackburn, T.
-M.
-\href{https://doi.org/10.1371/journal.pone.0127482}{Going cheap: Determinants of bird price in the {T}aiwanese pet market}.
-\emph{PLOS ONE} \textbf{10}, 1--17 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Young, A.
-M., Hobson, E.
-A., Lackey, L.
-B.
-\& Wright, T.
-F.
-\href{https://doi.org/10.1111/j.1469-1795.2011.00477.x}{Survival on the ark: Life-history trends in captive parrots}.
-\emph{Animal Conservation} \textbf{15}, 28--43 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Flammer, K., Whitt-Smith, D.
-\& Papich, M.
-\href{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}{Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection}.
-\emph{Journal of Avian Medicine and Surgery} \textbf{15}, 276--282 (2001).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Iwaniuk, A.
-N., Dean, K.
-M.
-\& Nelson, J.
-E.
-Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
-\emph{Brain, Behavior and Evolution} \textbf{65}, 40--59 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P.
-R.
-\& Ihunwo, A.
-O.
-\href{https://doi.org/10.3389/fnana.2018.00007}{Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh})}.
-\emph{Frontiers in Neuroanatomy} \textbf{12}, 7 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Olkowicz, S.
-\emph{et al.} \href{https://doi.org/10.1073/pnas.1517131113}{Birds have primate-like numbers of neurons in the forebrain}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{113}, 7255--7260 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Schuck-Paim, C., Alonso, W.
-J.
-\& Ottoni, E.
-B.
-\href{https://doi.org/10.1159/000119710}{Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots}.
-\emph{Brain, Behavior and Evolution} \textbf{71}, 200--215 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Silva, T., Guzmán, A., Urantówka, A.
-D.
-\& Mackiewicz, P.
-\href{https://doi.org/10.7717/peerj.3475}{A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny}.
-\emph{PeerJ} \textbf{5}, e3475 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Wilman, H.
-\emph{et al.} EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals.
-(2016) doi:\href{https://doi.org/10.6084/m9.figshare.c.3306933.v1}{10.6084/m9.figshare.c.3306933.v1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Jetz, W., Thomas, G. H., Joy, J. B., Hartmann, K. \& Mooers, A. O. The global diversity of birds in space and time. \emph{Nature} \textbf{491}, 444--448 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Seed, A. \& Byrne, R. \href{https://doi.org/10.1016/j.cub.2010.09.042}{Animal tool-use}. \emph{Current Biology} \textbf{20}, R1032--R1039 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Bercovitz, A. B. Avian sex identification techniques. in \emph{Companion bird medicine} (ed. Burr, E. W.) (Iowa State University Press, 1987).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Hoyo, J. D. \& Bierregaard, R. \emph{Handbook of the birds of the world}. (Lynx Edicions, 2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Amico, M.
-\& Van Keilegom, I.
-\href{https://doi.org/10.1146/annurev-statistics-031017-100101}{Cure models in survival analysis}.
-\emph{Annual Review of Statistics and Its Application} \textbf{5}, 311--342 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Schmidt, P.
-\& Witte, A.
-D.
-\href{https://doi.org/10.1016/0304-4076(89)90034-1}{Predicting criminal recidivism using {`split population'} survival time models}.
-\emph{Journal of Econometrics} \textbf{40}, 141--159 (1989).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Wallace, A.
-R.
-\emph{The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature}.
-(MacMillan; Co., 1869).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodall1971}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{Goodall, J.
-\href{https://doi.org/10.1016/S0065-3454(08)60157-6}{Tool-using in primates and other vertebrates}.
-in (eds.
-Lehrman, D.
-S., Hinde, R.
-A.
-\& Shaw, E.) vol.
-3 195--249 (Academic Press, 1971).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Reader, S.
-M.
-\& Laland, K.
-N.
-\href{https://doi.org/10.1073/pnas.062041299}{Social intelligence, innovation, and enhanced brain size in primates}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{99}, 4436--4441 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{Sol, D. \emph{et al.} Neuron numbers link innovativeness with both absolute and relative brain size in birds. \emph{Nature Ecology \& Evolution} \textbf{6}, 1381--1389 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Cabrera-Álvarez, M.
-J.
-\& Clayton, N.
-S.
-\href{https://doi.org/10.3389/fpsyg.2020.560669}{Neural processes underlying tool use in humans, macaques, and corvids}.
-\emph{Frontiers in Psychology} \textbf{11}, 560669 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.
-M.
-\& Fichtel, C.
-\href{https://doi.org/10.1098/rspb.2021.1728}{Linking cognition to ecology in wild sympatric mouse lemur species}.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{288}, 20211728 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Fragaszy, D. M. \& Mangalam, M. \href{https://doi.org/10.1016/bs.asb.2018.01.001}{Tooling}. in (eds. Naguib, M. et al.) vol. 50 177--241 (Academic Press, 2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{66. }%
-\CSLRightInline{Sándor, K.
-\& Miklósi, Á.
-\href{https://doi.org/10.3389/fpsyg.2020.555487}{How to report anecdotal observations?
-A new approach based on a lesson from "puffin tool use"}.
-\emph{Frontiers in Psychology} \textbf{11}, 555487 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
+Sanz, J.
+Call, and C.
+Boesch, eds.
+(Cambridge University Press), pp.
+89--118.
+\href{https://doi.org/10.1017/CBO9780511894800.007}{10.1017/CBO9780511894800.007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
 \CSLLeftMargin{67. }%
-\CSLRightInline{Debastiani, V.
-J., Bastazini, V.
-A.
-G.
-\& Pillar, V.
-D.
-\href{https://doi.org/10.1016/j.ecoinf.2021.101315}{Using phylogenetic information to impute missing functional trait values in ecological databases}.
-\emph{Ecological Informatics} \textbf{63}, 101315 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
+\CSLRightInline{Benichov, J.I., Globerson, E., and Tchernichovski, O.
+(2016).
+Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans.
+Frontiers in Human Neuroscience \emph{10}.
+\href{https://doi.org/10.3389/fnhum.2016.00255}{10.3389/fnhum.2016.00255}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
 \CSLLeftMargin{68. }%
-\CSLRightInline{Hunt, G.
-R., Gray, R.
-D.
-\& Taylor, A.
-H.
-Why is tool use rare in animals?
-in \emph{Tool use in animals: Cognition and ecology} (eds.
-Sanz, C.
-M., Call, J.
-\& Boesch, C.) 89--118 (Cambridge University Press, 2013).
-doi:\href{https://doi.org/10.1017/CBO9780511894800.007}{10.1017/CBO9780511894800.007}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
+\CSLRightInline{Patel, A.D., Iversen, J.R., Bregman, M.R., and Schulz, I.
+(2009).
+Experimental evidence for synchronization to a musical beat in a nonhuman animal.
+Current Biology \emph{19}, 827--830.
+\href{https://doi.org/10.1016/j.cub.2009.03.038}{10.1016/j.cub.2009.03.038}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
 \CSLLeftMargin{69. }%
-\CSLRightInline{Benichov, J.
-I., Globerson, E.
-\& Tchernichovski, O.
-\href{https://doi.org/10.3389/fnhum.2016.00255}{Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans}.
-\emph{Frontiers in Human Neuroscience} \textbf{10}, (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
+\CSLRightInline{ten Cate, C., Spierings, M., Hubert, J., and Honing, H.
+(2016).
+Can birds perceive rhythmic patterns?
+A review and experiments on a songbird and a parrot species.
+Frontiers in Psychology \emph{7}.
+\href{https://doi.org/10.3389/fpsyg.2016.00730}{10.3389/fpsyg.2016.00730}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
 \CSLLeftMargin{70. }%
-\CSLRightInline{Patel, A.
-D., Iversen, J.
-R., Bregman, M.
-R.
-\& Schulz, I.
-\href{https://doi.org/10.1016/j.cub.2009.03.038}{Experimental evidence for synchronization to a musical beat in a nonhuman animal}.
-\emph{Current Biology} \textbf{19}, 827--830 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
+\CSLRightInline{Wilson, M., and Cook, P.F.
+(2016).
+Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed.
+Psychonomic Bulletin \& Review \emph{23}, 1647--1659.
+\href{https://doi.org/10.3758/s13423-016-1013-x}{10.3758/s13423-016-1013-x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
 \CSLLeftMargin{71. }%
-\CSLRightInline{ten Cate, C., Spierings, M., Hubert, J.
-\& Honing, H.
-\href{https://doi.org/10.3389/fpsyg.2016.00730}{Can birds perceive rhythmic patterns?
-A review and experiments on a songbird and a parrot species}.
-\emph{Frontiers in Psychology} \textbf{7}, (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
+\CSLRightInline{Eckert, J., Winkler, S.L., and Cartmill, E.A.
+(2020).
+Just kidding: The evolutionary roots of playful teasing.
+Biology Letters \emph{16}, 20200370.
+\href{https://doi.org/10.1098/rsbl.2020.0370}{10.1098/rsbl.2020.0370}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
 \CSLLeftMargin{72. }%
-\CSLRightInline{Wilson, M.
-\& Cook, P.
-F.
-\href{https://doi.org/10.3758/s13423-016-1013-x}{Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed}.
-\emph{Psychonomic Bulletin \& Review} \textbf{23}, 1647--1659 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
+\CSLRightInline{Bro-Jørgensen, J., and Pangle, W.M.
+(2010).
+Male topi antelopes alarm snort deceptively to retain females for mating.
+The American Naturalist \emph{176}, E33--E39.
+\href{https://doi.org/10.1086/653078}{10.1086/653078}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
 \CSLLeftMargin{73. }%
-\CSLRightInline{Eckert, J., Winkler, S.
-L.
-\& Cartmill, E.
-A.
-\href{https://doi.org/10.1098/rsbl.2020.0370}{Just kidding: The evolutionary roots of playful teasing}.
-\emph{Biology Letters} \textbf{16}, 20200370 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
+\CSLRightInline{Byrne, R.W., and Whiten, A.
+(1988).
+Toward the next generation in data quality: A new survey of primate tactical deception.
+Behavioral and Brain Sciences \emph{11}, 267--273.
+\href{https://doi.org/10.1017/S0140525X00049955}{10.1017/S0140525X00049955}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
 \CSLLeftMargin{74. }%
-\CSLRightInline{Bro-Jørgensen, J.
-\& Pangle, W.
-M.
-\href{https://doi.org/10.1086/653078}{Male topi antelopes alarm snort deceptively to retain females for mating}.
-\emph{The American Naturalist} \textbf{176}, E33--E39 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
+\CSLRightInline{Byrne, R.W., and Whiten, A.
+(1991).
+Computation and mindreading in primate tactical deception.
+In Natural theories of mind: Evolution, development and simulation of everyday mindreading, A.
+Whiten, ed.
+(Basil Blackwell), pp.
+127--141.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
 \CSLLeftMargin{75. }%
-\CSLRightInline{Byrne, R.
-W.
-\& Whiten, A.
-\href{https://doi.org/10.1017/S0140525X00049955}{Toward the next generation in data quality: A new survey of primate tactical deception}.
-\emph{Behavioral and Brain Sciences} \textbf{11}, 267--273 (1988).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
+\CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership} (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
 \CSLLeftMargin{76. }%
-\CSLRightInline{Byrne, R.
-W.
-\& Whiten, A.
-Computation and mindreading in primate tactical deception.
-in \emph{Natural theories of mind: Evolution, development and simulation of everyday mindreading} (ed.
-Whiten, A.) 127--141 (Basil Blackwell, 1991).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
+\CSLRightInline{Jerison, H.J. (1973). Evolution of the brain and intelligence (Academic Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
 \CSLLeftMargin{77. }%
-\CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership}. (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
+\CSLRightInline{Paradis, E., and Schliep, K.
+(2019).
+{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}.
+Bioinformatics \emph{35}, 526--528.
+\href{https://doi.org/10.1093/bioinformatics/bty633}{10.1093/bioinformatics/bty633}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
 \CSLLeftMargin{78. }%
-\CSLRightInline{Jerison, H. J. \emph{Evolution of the brain and intelligence}. (Academic Press, 1973).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
+\CSLRightInline{McElreath, R.
+(2020).
+\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition} 2nd ed.
+(CRC Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
 \CSLLeftMargin{79. }%
-\CSLRightInline{Paradis, E.
-\& Schliep, K.
-\href{https://doi.org/10.1093/bioinformatics/bty633}{{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}}.
-\emph{Bioinformatics} \textbf{35}, 526--528 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
+\CSLRightInline{Stan Development Team (2020). \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
 \CSLLeftMargin{80. }%
-\CSLRightInline{McElreath, R. \emph{\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition}}. (CRC Press, 2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
+\CSLRightInline{Revell, L.J.
+(2012).
+{phytools}: An {R} package for phylogenetic comparative biology (and other things).
+Methods in Ecology and Evolution \emph{3}, 217--223.
+\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{10.1111/j.2041-210X.2011.00169.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
 \CSLLeftMargin{81. }%
-\CSLRightInline{Stan Development Team. \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}. (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
+\CSLRightInline{R Core Team (2022). \href{https://www.R-project.org/}{R: A language and environment for statistical computing} (R Foundation for Statistical Computing).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
 \CSLLeftMargin{82. }%
-\CSLRightInline{Revell, L.
-J.
-\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{{phytools}: An {R} package for phylogenetic comparative biology (and other things)}.
-\emph{Methods in Ecology and Evolution} \textbf{3}, 217--223 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
+\CSLRightInline{Yu, G., Smith, D., Zhu, H., Guan, Y., and Lam, T.T.-Y.
+(2017).
+{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data.
+Methods in Ecology and Evolution \emph{8}, 28--36.
+\href{https://doi.org/10.1111/2041-210X.12628}{10.1111/2041-210X.12628}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
 \CSLLeftMargin{83. }%
-\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
+\CSLRightInline{Wickham, H. (2016). \href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis} (Springer-Verlag New York).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
 \CSLLeftMargin{84. }%
-\CSLRightInline{Yu, G., Smith, D., Zhu, H., Guan, Y.
-\& Lam, T.
-T.-Y.
-\href{https://doi.org/10.1111/2041-210X.12628}{{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data}.
-\emph{Methods in Ecology and Evolution} \textbf{8}, 28--36 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
+\CSLRightInline{Wilke, C.O. (2020). \href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
 \CSLLeftMargin{85. }%
-\CSLRightInline{Wickham, H. \emph{\href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis}}. (Springer-Verlag New York, 2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
+\CSLRightInline{Landau, W.M.
+(2021).
+The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing.
+Journal of Open Source Software \emph{6}, 2959.
+\href{https://doi.org/10.21105/joss.02959}{10.21105/joss.02959}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
 \CSLLeftMargin{86. }%
-\CSLRightInline{Wilke, C. O. \emph{\href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}}. (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
-\CSLLeftMargin{87. }%
-\CSLRightInline{Landau, W.
-M.
-\href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}.
-\emph{Journal of Open Source Software} \textbf{6}, 2959 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
-\CSLLeftMargin{88. }%
-\CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}}. (2022).}
+\CSLRightInline{Aust, F., and Barth, M. (2022). \href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}.}
 
@@
 
-\noindent \hspace*{8mm} \small Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare \newline
+\noindent \hspace*{5mm} \small Digital video platforms and phylogenetic modelling reveal parrot tool use is not rare \newline
 \hspace*{1cm} \small Amalia P. M. Bastos\textsuperscript{1,2}, Scott Claessens\textsuperscript{2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, \newline

### 2024-05-20 R/functionsDAG.R

@@ -21,10 +21,10 @@ drawDAG <- function() {
     ggplot(aes(x = x, y = y, xend = xend, yend = yend))
   # modify labels
   labels <- c("TUu"    = "Tool use\n(unobserved)",
-              "TUoLit" = "Tool use\nobserved in\nliterature",
-              "TUoVid" = "Tool use\nobserved in\ncrowdsourcing",
+              "TUoLit" = "Tool use\nobserved in\nscientific literature",
+              "TUoVid" = "Tool use\nobserved on\ndigital video platform",
               "numLit" = "Number of\nscientific papers\npublished",
-              "numVid" = "Number of\ncrowdsourced\nreports",
+              "numVid" = "Number of\nvideos on\ndigital platform",
               "EQ"     = "Relative\nbrain size",
               "F"      = "Feeding\nstrategy",
               "U"      = "Unobserved\nconfounds",

### 2024-07-12 manuscript.Rmd
revise and resubmit

@@
 \newpage
-\nolinenumbers
+\linenumbers
+
+```{r include=FALSE, message=FALSE, warning=FALSE}
+library(papaja)
+library(targets)
+library(tidyverse)
+```
 
@@
 behaviours. For example, based on the observation that bird species with 
-reported tool use tended to have larger brains, researchers have identified 
+reported tool use tend to have larger brains, researchers have identified 
 higher relative brain size as a likely precondition for tool using 
-capabilities [@Lefebvre2002;@Lefebvre1997;@Lefebvre2004]. These researchers 
-argue that larger brains are better able to integrate visual and somatosensory 
-information when innovating novel behaviours, such as tool use, in changing 
-environments [@Sol2005;@Sol2009]. Similarly, researchers have used existing 
-reports of tool use in birds to debate the roles of generalist versus 
-specialist feeding strategies in driving the evolution of tool use, with some 
-arguing that feeding generalists require technical innovations to expand their 
-dietary niche [@Ducatez2015;@Overington2011;@Sol2005] and others arguing that 
-feeding specialists require technical innovations for extractive foraging of 
-specific foods [@HenkeVonDerMalsburg2020;@MettkeHofmann2014].
+capabilities [@Audet2024;@Lefebvre2002;@Lefebvre1997;@Lefebvre2004]. These 
+researchers argue that larger brains are better able to integrate visual and 
+somatosensory information when innovating novel behaviours, such as tool use, 
+in changing environments [@Sol2005;@Sol2009] (but see ref [@Kaplan2020]). 
+Similarly, researchers have used existing reports of tool use in birds to debate
+the roles of generalist versus specialist feeding strategies in driving the 
+evolution of tool use, with some arguing that feeding generalists require 
+technical innovations to expand their dietary niche 
+[@Ducatez2015;@Overington2011;@Sol2005] and others arguing that feeding 
+specialists require technical innovations for extractive foraging of specific 
+foods [@HenkeVonDerMalsburg2020;@MettkeHofmann2014].
 
@@
 thus draw premature conclusions about the evolutionary drivers and origins of 
-tool use. While researchers have attempted to deal with this problem by 
-controlling for the number of scientific papers published on different species, 
-previous work has not yet attempted to quantify and explicitly model the 
-relationship between actual tool-using behaviour and what is reported in the 
-scientific literature. If more tool-using species exist than previously thought, 
-this could have important implications for theories of the evolutionary drivers 
-and origins of tool use and for our understanding of how rare this behaviour 
-actually is.
+tool use. Researchers are keenly aware of this problem and have attempted to 
+deal with it in different ways, such as controlling for the number of scientific 
+papers published on different species. But previous work has not yet attempted 
+to quantify and explicitly model the relationship between actual tool-using 
+behaviour and what is reported in the scientific literature. If more tool-using 
+species exist than previously thought, this could have important implications 
+for theories of the evolutionary drivers and origins of tool use and for our 
+understanding of how rare this behaviour actually is.
 
@@
 tar_load(crowdData)
-trueCrowdData <- filter(crowdData, ToolUse == "Y")
-bordCrowdData <- filter(crowdData, ToolUse == "B")
+trueCrowdData <- dplyr::filter(crowdData, ToolUse == "Y")
+bordCrowdData <- dplyr::filter(crowdData, ToolUse == "B")
 ```
@@
 videos) was a moulted feather. Human-made objects (e.g., pens, spoons, pieces of 
-wood, cardboard) were also common.
+wood, cardboard) were also common. In `r sum(readxl::read_xlsx(tar_read(crowdsourcing_file))$Directionality == "Tool to body", na.rm = TRUE)` 
+videos, parrots manipulated the tool while keeping their body still, rather than 
+holding the tool still and moving towards it.
 
@@
 else being equal those with fewer published papers and fewer video search hits 
-have a higher probability of being undetected tool users (Supplementary Figure 
+have a higher probability of being undetected tool users (Figure 
 \@ref(fig:plotSurvCure3)).
@@
 area-under-the-curve classification statistic of 
-`r printnum(tar_read(auc), digits = 2)` (Supplementary Figure 
+`r printnum(tar_read(auc), digits = 2)` (Figure 
 \@ref(fig:plotSurvCure9)). To further estimate the accuracy of the model's 
@@
 for which tool use is unobserved in our data: the blue-eyed cockatoo (_Cacatua 
-opthalmica_). This species is endemic to Papua New Guinea and is relatively 
+ophthalmica_). This species is endemic to Papua New Guinea and is relatively 
 understudied, with only `r tar_read(d)$EX.Pre.Tool.Papers[165]` published papers 
@@
 clade containing several known tool users. This prediction makes sense given the 
-high phylogenetic signal for tool use reported by the model (Supplementary 
+high phylogenetic signal for tool use reported by the model (
 Figures \@ref(fig:plotSurvCure5) and \@ref(fig:plotSurvCure6)). Beyond the 
@@
 effect of relative brain size and no difference between feeding strategies, 
-respectively (Supplementary Figure \@ref(fig:plotComparison)).
+respectively (Figure \@ref(fig:plotComparison)).
 
@@
 discoveries from our video survey and from our phylogenetic modelling increased 
-the likelihood that tool use was present in the most recent common ancestor for 
-several parrot genera. These include the amazon parrots native to the Americas 
-(_Amazona_), the true white cockatoos and corellas found in South East Asia and 
-Australasia (_Cacatua_), the kea and the kākā from New Zealand (_Nestor_), and 
+the likelihood that the capacity for tool use was present in the most recent 
+common ancestors for several parrot genera. These include the most recent common 
+ancestor of amazon parrots native to the Americas (_Amazona_), the most recent 
+common ancestor of the true white cockatoos and corellas found in South East 
+Asia and Australasia (_Cacatua_), the most recent common ancestor of the kea and 
+the kākā from New Zealand (_Nestor_), and the most recent common ancestor for
 the _Poicephalus_ genus native to Africa (Table \@ref(tab:tableASR); 
-Supplementary Figures \@ref(fig:plotASR1) - \@ref(fig:plotASR3)). These findings 
-suggest that species from each of these genera may share their tool use 
-capabilities via common descent from their respective common ancestors, rather 
-than via independent evolution within each genus or behavioural innovation
-within species.
+Figures \@ref(fig:plotASR1) - \@ref(fig:plotASR3)).
 
@@
 Instead, we discovered a large discrepancy between these two data sources, both 
-in the prevalence of tool use and the species identified. This raises the 
-possibility that insufficient research effort is a general issue across the 
-scientific literature, both for tool use in other groups and for other rare 
-behaviours.
+in the prevalence of tool use and the species identified, likely due to the 
+numerous difficulties inherent to conducting observations in the wild. This 
+raises the possibility that other rare behaviours remain yet to be discovered in 
+the scientific literature.
 
@@
 analysis provides preliminary support for this hypothesis, revealing an 
-increased probability of tool use among the most recent common ancestors for the 
-_Amazona_, _Cacatua_, _Nestor_, and _Poicephalus_ genera. Even at this 
-preliminary stage, our analysis therefore raises an alternative hypothesis for 
-the observed tool use in _Cacatua_ [@Auersperg2012;@OHara2021] and 
-_Nestor_ [@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;
+increased probability of the capacity for tool use among the most recent common 
+ancestors for the _Amazona_, _Cacatua_, _Nestor_, and _Poicephalus_ genera. The 
+complexity of tool use behaviour that such a basic capacity might afford, and 
+the conditions under which it emerges in the wild, are yet to be established. 
+However, even at this preliminary stage, our analysis raises an alternative 
+hypothesis for the observed tool use in _Cacatua_ [@Auersperg2012;@OHara2021] 
+and _Nestor_ [@Auersperg2009;@Auersperg2010;@Auersperg2011a;@Auersperg2011b;
 @Bastos2021;@Goodman2018], namely that tool behaviours have arisen due to the 
@@
 extractive foraging and preening [@Goodman2018;@OHara2021], parrots in captivity
-only require tools to achieve the latter goal. Despite this difference in the
-type of tool use observed, self-scratching is nonetheless a major category of 
-animal tool use. Self-scratching also meets the definition for a more complex 
-type of embodied tool use known as 'tooling', the deliberate generation of a 
-mechanical interface by using an object to manipulate another target or surface
-[@Fragaszy2018]. This makes it difficult to dismiss self-scratching as 
-unimportant: to do so would require a redefinition of tool-use in non-human
-animals. Moreover, the fact that we found strong phylogenetic clustering of 
-self-scratching tool use from the video survey with other examples of tool use
-from the literature supports a common underlying cognitive mechanism. In line 
-with this, some of the species of parrots that use tools for self-scratching in
-captivity also use tools for other purposes in the wild [@Auersperg2012;
-@Bastos2021;@Goodman2018;@OHara2021].
+only require tools to achieve the latter goal. It could be argued that 
+self-scratching is a more cognitively simplistic form of tool use than 
+extractive foraging as it is egocentric, meaning that the tool is directed 
+towards oneself rather than an external object. Nevertheless, self-scratching 
+meets the definition for a more complex type of embodied tool use known as 
+'tooling', the deliberate generation of a mechanical interface by using an 
+object to manipulate another target or surface [@Fragaszy2018]. In our dataset, 
+most self-scratching tooling instances involved manipulating the tool while 
+keeping the body still, suggesting that these were goal-directed, deliberate 
+movements by individuals. This makes it difficult to dismiss self-scratching as 
+unimportant: to do so would require a redefinition of tool-use and tooling in 
+non-human animals. Moreover, the fact that we found strong phylogenetic 
+clustering of self-scratching tool use from the video survey with other examples 
+of tool use from the literature supports a common underlying cognitive 
+mechanism. In line with this, some of the species of parrots that use tools for 
+self-scratching in captivity also use tools for other purposes in the wild 
+[@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021].
 
-There was little evidence to suggest that the observations of self-scratching
-tool use in the video survey were merely unintentional accidents or explicitly 
-trained behaviours. Individual parrots often used tools slowly and repetitively 
-over long periods of time, even across multiple different videos, suggesting 
-that their behaviour was not random or accidental [@Sandor2020]. Parrots 
-preferentially employed self-scratching tools on areas of their body that were 
-otherwise inaccessible, with 96% of all instances involving scratching of the 
-head or neck, suggesting intentional tool use. For 60% of the species in the 
-video survey, we found two or more videos of repetitive and sustained scratching 
-by different individuals of the same species in separate households, suggesting 
-that the manipulations were intentional and recurring events that did not 
-represent unusual stereotypies of any single individual. Regarding the 
+A potential concern with data originating from digital video platforms is its 
+reliability [@Auersperg2020;@DechaumeMoncharmont2020;@Farrar2020;@Nelson2013;@Sandor2020;@vonBayern2020]. 
+In particular, the self-care tool use instances detected in our video survey 
+might be attributable to training or unintentional cueing by the birds' owners.
+However, there was little evidence to suggest that the observations of 
+self-scratching tool use in the video survey were merely unintentional accidents 
+or explicitly trained behaviours. Individual parrots often used tools slowly and 
+repetitively over long periods of time, even across multiple different videos, 
+suggesting that their behaviour was not random or accidental [@Sandor2020]. 
+Parrots preferentially employed self-scratching tools on areas of their body 
+that were otherwise inaccessible, with 96% of all instances involving scratching 
+of the head or neck, suggesting intentional tool use. For 60% of the species in 
+the video survey, we found two or more videos of repetitive and sustained 
+scratching by different individuals of the same species in separate households, 
+suggesting that the manipulations were intentional and recurring events that did 
+not represent unusual stereotypies of any single individual. Regarding the 
 possibility of training or cueing from owners, over half of the videos contained 
@@
 behaviours, which would likely appear uniformly across the phylogeny. 
+Nevertheless, future work using data such as this should choose target 
+behaviours carefully and examine videos for evidence of training or cueing.
+
+Our data reveals that a wide range of parrot species exhibit self-scratching 
+tool use behaviours in captive environments. It is possible that these self-care 
+behaviours emerge more often in captivity because pet parrots are kept with few 
+or no conspecifics, and therefore must innovate tool use to preen inaccessible 
+body areas, such as their heads and necks, which would have been otherwise 
+preened by flock members. This may indicate that human interaction and 
+allopreening in the absence of a conspecific is insufficient for pet parrots, as 
+suggested by studies on welfare and chronic stress in lone captive parrots 
+[@Aydinonat2014;@Engebretson2006;@Mason2010;@Meehan2003]. Beyond social 
+isolation in captivity, other factors that reduce preening efficacy by an 
+individual might also lead to the innovation of self-care tooling: for example,
+a captive kea housed with conspecifics in a naturalistic environment was shown
+to have innovated the use of a pebble tool for self-care likely as a consequence 
+of a missing upper mandible [@Bastos2021]. These behaviours might therefore be 
+innovated by individuals when ecologically necessary. Critically, however, a 
+cognitive capacity to innovate a behaviour such as tool use must exist in a 
+species in order to manifest in any environment, whether that be captive or in 
+the wild. As such, despite differences in individuals' life experiences in 
+captive and wild settings, such behaviour emerging in a captive setting at the 
+very least indicates an underlying cognitive capacity to innovate that same 
+behaviour in the wild.
 
@@
 
-# Methods
-
-## Video searches and coding
-
-Our video search was conducted on YouTube in July 2020. Searches were conducted
-manually by the first author over a month-long period, using the same IP address
-and not logged in with a YouTube user account. Search terms included 
-"parrot using tool" and variants (e.g., "macaw using tool", "lorikeet using 
-tool", "parakeet using tool"), "tool use in parrot", "parrot tool use", "parrot 
-scratching itself" (included after we found several videos demonstrating 
-self-care tool use in previous searches) and equivalent terms (e.g., "parrot 
-preening itself", "parrot grooming itself", "parrot scratching"). For all 
-species that did not display results including object manipulation or scratching 
-behaviours, we also searched the species’ common name(s) + "tool use", as well 
-as the species’ common name(s) + "scratching". We also searched for translations 
-of the terms "parrot tool use" and "parrot scratching" in languages for all 
-countries where bird ownership was reported as >5% [@GlobalGfkSurvey], namely, 
-Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, 
-Portuguese, and Mandarin. Browser search histories were not cleared between
-searches.
-
-When we found a relevant video, we also searched for similar content uploaded by 
-the same person/channel. For each YouTube search conducted, we watched all 
-relevant videos until we reached five consecutive videos that did not feature 
-any parrots. At this point, we ended that search and initiated the next search. 
-In line with previous recommendations [@Nelson2013], we planned to exclude any 
-videos that consisted of four or more shots edited together so as to ensure the 
-behaviours being observed were not edited or manipulated, but none of the videos 
-obtained qualified for exclusion.
-
-All videos featuring parrots manipulating objects were investigated for 
-potential tool use or borderline tool use. We defined tool use as the 
-manipulation of an unattached object as an extension of the beak or foot to 
-achieve a goal towards another object, individual, or oneself [@Shumaker2011]. 
-Borderline tool use was similarly defined, except that it involved the use of an 
-object that was still attached to a substrate [@Seed2010]. For example, if 
-individuals used a fallen feather or stick for self-scratching this was defined 
-as tool use, but using one’s currently attached tail feathers or cage 
-furnishings for the same purpose was defined as borderline tool use. 
-Self-scratching had to involve slow and repeated movements of touching an object 
-to one’s body (or, in the case of borderline tool use, rubbing repetitively 
-against an attached object [@Sandor2020]).
-
-All relevant videos were coded for video length, species, tool use presence 
-(yes/borderline), tool use type (e.g., scratching, feeding), the object being 
-used (e.g., feather, stick), tool use target, human interaction 
-(talking or handing object to parrot, holding parrot), and the number of shots 
-within each video. Our complete dataset also includes the name for each video, 
-link, subject name, sex (as declared by owner, as most parrot species are not 
-sexually dimorphic), publishing date, and dates found and coded.
-
-Since YouTube is constantly growing and evolving in both its uploaded content 
-and its proprietary recommendation algorithms, the same search strategy today 
-would not return exactly the same videos as our search in July 2020. It is 
-possible that some videos have since been deleted or more videos of parrot tool
-use have since been uploaded. However, this does not affect our conclusions
-about the number of parrot species found to use tools in our initial search.
-
-## Data for parrot species
-
-We collected data for 194 parrot species (Supplementary Figures
-\@ref(fig:plotPhylo2) - \@ref(fig:plotPhylo4)). We gathered feeding strategy 
-data as a dichotomous variable ("generalist" or "specialist") from the 
-EltonTraits ecological database [@Wilman2016]. As per the database, specialists 
-were defined as species whose diet comprised at least 70% of a single food 
-source. To calculate relative brain size, we collated data from the literature 
-for all known body mass (g) and brain mass (g) values across 
-parrots [@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;@Schuck2008;
-@Silva2017]. For all species for which we obtained body and brain mass data, we 
-calculated the encephalisation quotient (EQ) using the following 
-formula [@Jerison1973]: $BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))$. We 
-found body mass and brain mass data for a total of 194 parrot species. This 
-included all tool-using species in our video dataset, with the exception of 
-three species: _Diopsittaca nobilis_, _Psittacara erythrogenys_, and _Coracopsis 
-vasa_. For the latter, we used values for the closely related _Coracopsis 
-nigra_. The other two species were excluded from the final dataset.
-
-For modelling purposes, we coded research effort in both the scientific 
-literature and the YouTube videos. For the scientific literature, we 
-operationalised research effort as the number of papers published for each 
-species' Latin name up to and including the first paper containing tool use for 
-that species. If no tool use had been identified in the scientific literature 
-for a species, then we coded the total number of papers published to date. We 
-used the scientific database Scopus for coding the number of published papers. 
-For the videos, we coded research effort as the number of search hits for each
-species on YouTube. If tool use had been identified on YouTube, we estimated the
-number of search hits when the first video of tool use was published on YouTube,
-assuming linear growth of search hits since the inception of YouTube. If tool
-use had not been identified, we used the current number of search hits.
-
-For phylogenetic data, we used the phylogenetic tool at www.birdtree.org
-[@Jetz2012] to compile 1000 posterior draws of phylogenetic trees for 174 of the 
-194 parrot species for which both EQ and genomic data exist. A single maximum 
-clade credibility tree was generated from these posterior draws for 
-visualisation purposes. In our analyses, we iterated over posterior draws of the 
-phylogeny to account for phylogenetic uncertainty.
-
-## Phylogenetic signal
-
-We used the _fitDiscrete_ function in the _ape_ R package [@Paradis2019] to 
-calculate phylogenetic signal, for both the pre-survey and post-survey tool use 
-data. We iterated the model over 100 posterior parrot phylogenies to incorporate 
-phylogenetic uncertainty.
-
-## Causal model of tool use
-
-To infer unobserved probabilities of tool use across parrots, we proposed a 
-causal model of observed tool use (Figure \@ref(fig:plotDAG)). We assumed that 
-observed tool use in the scientific literature and in the videos is caused by 
-both the unobserved presence or absence of tool use and research effort, proxied
-by the number of papers published on a species and the number of videos
-published on a species. Tool users are more likely to be observed if they are
-well studied, but understudied tool users may go undetected. In addition, based
-on theory, we also assumed that unobserved tool use is caused by feeding 
-strategy and relative brain size [@Lefebvre2004;@Lefebvre1997;@Lefebvre2002;
-@Ducatez2015;@Sol2005;@Overington2011;@HenkeVonDerMalsburg2020]. Finally, we 
-assumed that shared phylogenetic history causes unobserved confounding and 
-non-independence in unobserved tool use, feeding strategy, and relative brain 
-size across the parrot phylogeny.
-
-## Bayesian phylogenetic survival cure model
-
-Given our proposed causal model, we constructed a statistical model to impute 
-unobserved probabilities of tool use and test existing theories of the evolution 
-of tool use in parrots. To understand the model, suppose that we have the 
-following observed variables for parrot species $i$. For the scientific 
-literature, we declare $\text{N}_{\text{Lit},i}$ as the number of papers 
-published before and up to tool use identification for species $i$ (or, if tool 
-use has not been identified, the total number of papers published for species 
-$i$) and $\text{T}_{\text{Lit},i}$ as a binary variable stating whether (1) or 
-not (0) tool use has yet been observed in the scientific literature for species 
-$i$. For the videos, we declare $\text{N}_{\text{Vid},i}$ as the 
-number of videos published before and up to tool use identification for species 
-$i$ (or, if tool use has not been identified, the total number of videos 
-published for species $i$) and $\text{T}_{\text{Vid},i}$ as a binary variable 
-stating whether (1) or not (0) tool use has yet been observed in the 
-videos for species $i$. Additionally, $\text{F}_i$ and 
-$\text{EQ}_i$ are feeding strategy and encephalisation quotient values for 
-species $i$ and we have a phylogenetic distance matrix $D$ that describes the 
-patristic distances between all parrot species.
-
-We assume that species $i$ is a non-tool-user with some 
-probability $p_i$. We also assume that tool use is identified in the scientific 
-literature and the videos at constant rates $\lambda_{\text{Lit}}$ 
-and $\lambda_{\text{Vid}}$ following exponential survival functions. Given these 
-assumptions, we can then describe the different ways in which variables 
-$\text{N}_\text{Lit}$ and $\text{N}_\text{Vid}$ can be distributed. Focusing on 
-the scientific literature, if tool use has been observed 
-($\text{T}_{\text{Lit},i} = 1$), then the likelihood for 
-$\text{N}_{\text{Lit},i}$ is:
-
-\begin{align}
-\text{Pr}(\text{N}_{\text{Lit},i}|\text{T}_{\text{Lit},i} = 1,p_i,\lambda_\text{Lit}) = (1-p_i)\cdot\text{Exponential}(\text{N}_{\text{Lit},i}|\lambda_\text{Lit})
-\end{align}
-
-On the other hand, if tool use has not yet been observed 
-($\text{T}_{\text{Lit},i} = 0$), there are two ways that the outcome variable 
-could have been realised. First, the species could be a non-tool-user with 
-probability $p_i$. Second, the species could be a tool-user with probability 
-($1 - p_i$) that has been censored and has not had its tool use measured yet. 
-Together, then, the likelihood for $\text{N}_{\text{Lit},i}$ is:
-
-\begin{align}
-\text{Pr}(\text{N}_{\text{Lit},i}|\text{T}_{\text{Lit},i} = 0,p_i,\lambda_\text{Lit}) = p_i + ((1-p_i)\cdot\text{Exponential-CCDF}(\text{N}_{\text{Lit},i}|\lambda_\text{Lit}))
-\end{align}
-
-The Exponential-CCDF function allows for the censored nature of the data. The 
-same data generating process is assumed to underlie the videos.
-
-We define the mixture likelihood $\text{SurvivalCure}$ as the distribution 
-above, with parameters $p$ (the probability of being a non-tool-user) 
-and $\lambda$ (the rate of the exponential distribution). We use an 
-Ornstein-Uhlenbeck Gaussian process [@McElreath2020] to model phylogenetic 
-covariance. Below, we specify the full model with priors:
-
-\begin{align}
-N_{\text{Lit},i} &\sim \text{SurvivalCure}(\lambda_{\text{Lit},i}, p_{i}) \\
-N_{\text{Vid},i} &\sim \text{SurvivalCure}(\lambda_{\text{Vid},i}, p_{i}) \nonumber \\
-\lambda_{\text{Lit},i} &= 1 / \text{exp}(\gamma_\text{Lit}) \nonumber \\
-\lambda_{\text{Vid},i} &= 1 / \text{exp}(\gamma_\text{Vid}) \nonumber \\
-\text{logit}(p_{i}) &= \alpha_{\text{FEEDING}[i]} + \beta\text{EQ}_{i} +  k_{\text{SPECIES}[i]} \nonumber \\
-\begin{pmatrix}k_{1}\\k_{2}\\...\\k_{n}\\\end{pmatrix}
-&\sim \text{MVNormal}
-\begin{pmatrix}\begin{pmatrix}0\\0\\...\\0\\\end{pmatrix},\bf{K}\end{pmatrix} \nonumber \\
-\bf{K}_{ij} &= \eta^2\text{exp}(-\rho^2D_{ij}) \nonumber \\
-\gamma_\text{Lit}, \gamma_\text{Vid}, \alpha_{1,2}, \beta &\sim \text{Normal(0, 1)} \nonumber \\
-\eta^2, \rho^2 &\sim \text{Exponential(0.5)} \nonumber
-\end{align}
-
-The priors for this model produce reasonable prior predictions of the 
-probabilities of tool use for each parrot species (Supplementary Figure
-\@ref(fig:plotSurvCure7)), but a sensitivity analysis revealed that the ranking 
-and posterior probabilities reported in the main text were robust to modifying 
-these priors (Supplementary Figure \@ref(fig:plotSurvCure8)). We estimated the 
-posterior distribution of this model using Hamiltonian Monte Carlo as 
-implemented in Stan version 2.26.1 [@Stan2020]. We ran the model for 4000 
-samples, with 2000 warmup samples, and iterated the model over 100 posterior 
-parrot phylogenies to incorporate phylogenetic uncertainty. R-hat values and 
-effective sample sizes suggested that the model converged normally. Trace plots 
-are reported in Supplementary Figure \@ref(fig:plotTrace). We report 
-equal-tailed credible intervals to describe the posterior distribution of this 
-model in the main text.
-
-To validate our method, we fitted the model to 100 simulated datasets with known 
-parameters. The model was able to successfully recover those parameters 
-(Supplementary Figure \@ref(fig:plotSurvCureSim)). We also ran a 
-leave-one-species-out exercise to ensure that we could accurately predict known 
-tool users. We repeated this approach for each known tool user by setting 
-observed tool use to zero. Cross-validation results are reported in the main 
-text.
-
-## Ancestral state reconstruction
-
-To determine whether the identification of novel tool-using species has 
-implications for our understanding of the evolutionary origins of tool use in 
-parrots, we fitted three exploratory ancestral state reconstruction models. We 
-used the _ancThresh_ function from the _phytools_ R package [@phytools], 
-iterating the function over 100 posterior parrot phylogenies. This function 
-estimates discrete ancestral states by assuming the evolution of a latent 
-continuous variable following an Ornstein-Uhlenbeck process. We fitted this 
-model to three different outcome variables: (_i_) presence vs. absence of tool 
-use in scientific literature only, (_ii_) presence vs. absence of tool use in 
-literature and/or videos, and (_iii_) the median predicted probabilities of tool 
-use from the phylogenetic survival cure model.
-
-## Reproducibility
-
-All analyses were conducted in R v4.2.1. [@RCoreTeam]. Visualisations were 
-produced using the _ggtree_[@ggtree], _ggplot2_ [@Wickham2016], and _cowplot_ 
-[@Wilke2020] packages. The manuscript was reproducibly generated using the 
-_targets_ [@Landau2021] and _papaja_ [@Aust2022] packages. Code to reproduce all 
-analyses and figures can be found here: 
-https://github.com/ScottClaessens/phyloParrot
-
 \newpage
@@
 
-# Competing Interests
+# Declaration of Interests
 
 The authors declare no competing interests.
-
-# Data Availability
-
-All data used in this study are publicly available on GitHub: 
-https://github.com/ScottClaessens/phyloParrot
-
-# Code Availability
-
-All code to reproduce the analyses in this study are publicly available on 
-GitHub: https://github.com/ScottClaessens/phyloParrot
 
@@
 \newpage
+\linenumbers
+
+```{r child = "methods.Rmd"}
+```
+
+\newpage
+\nolinenumbers
 \vspace*{60mm}

### 2024-07-12 manuscript.tex
revise and resubmit

@@
 \newpage
-\nolinenumbers
+\linenumbers
 
@@
 behaviours. For example, based on the observation that bird species with
-reported tool use tended to have larger brains, researchers have identified
+reported tool use tend to have larger brains, researchers have identified
 higher relative brain size as a likely precondition for tool using
-capabilities\textsuperscript{11--13}. These researchers
-argue that larger brains are better able to integrate visual and somatosensory
-information when innovating novel behaviours, such as tool use, in changing
-environments\textsuperscript{14,15}. Similarly, researchers have used existing
-reports of tool use in birds to debate the roles of generalist versus
-specialist feeding strategies in driving the evolution of tool use, with some
-arguing that feeding generalists require technical innovations to expand their
-dietary niche\textsuperscript{14,16,17} and others arguing that
-feeding specialists require technical innovations for extractive foraging of
-specific foods\textsuperscript{18,19}.
+capabilities\textsuperscript{11--14}. These
+researchers argue that larger brains are better able to integrate visual and
+somatosensory information when innovating novel behaviours, such as tool use,
+in changing environments\textsuperscript{15,16} (but see ref\textsuperscript{17}).
+Similarly, researchers have used existing reports of tool use in birds to debate
+the roles of generalist versus specialist feeding strategies in driving the
+evolution of tool use, with some arguing that feeding generalists require
+technical innovations to expand their dietary niche\textsuperscript{15,18,19} and others arguing that feeding
+specialists require technical innovations for extractive foraging of specific
+foods\textsuperscript{20,21}.
 
@@
 make them easier to study, such as larger distribution ranges and population
-sizes\textsuperscript{20}. This is a crucial limitation because insufficient
+sizes\textsuperscript{22}. This is a crucial limitation because insufficient
 observation may lead researchers to miss true instances of tool behaviours and
 thus draw premature conclusions about the evolutionary drivers and origins of
-tool use. While researchers have attempted to deal with this problem by
-controlling for the number of scientific papers published on different species,
-previous work has not yet attempted to quantify and explicitly model the
-relationship between actual tool-using behaviour and what is reported in the
-scientific literature. If more tool-using species exist than previously thought,
-this could have important implications for theories of the evolutionary drivers
-and origins of tool use and for our understanding of how rare this behaviour
-actually is.
+tool use. Researchers are keenly aware of this problem and have attempted to
+deal with it in different ways, such as controlling for the number of scientific
+papers published on different species. But previous work has not yet attempted
+to quantify and explicitly model the relationship between actual tool-using
+behaviour and what is reported in the scientific literature. If more tool-using
+species exist than previously thought, this could have important implications
+for theories of the evolutionary drivers and origins of tool use and for our
+understanding of how rare this behaviour actually is.
 
@@
 behaviours is by collating evidence of the behaviours from digital video
-platforms\textsuperscript{21}. With millions of videos posted every day, digital
+platforms\textsuperscript{23}. With millions of videos posted every day, digital
 platforms like YouTube offer a valuable source of data on animal behaviour.
 Digital video platforms have already been successfully used to uncover a variety
-of rare animal behaviours, including interspecies play in dogs\textsuperscript{21},
-novel problem-solving behaviours in horses\textsuperscript{22}, and death-related
-behaviours in Asian elephants\textsuperscript{23}. By casting the net wider than the
+of rare animal behaviours, including interspecies play in dogs\textsuperscript{23},
+novel problem-solving behaviours in horses\textsuperscript{24}, and death-related
+behaviours in Asian elephants\textsuperscript{25}. By casting the net wider than the
 scientific literature, digital video platforms can provide an indication of the
@@
 observed if they are well studied, but understudied tool users may go
-undetected. Furthermore, based on existing theories of the evolution of tool use\textsuperscript{11--19}, we propose
+undetected. Furthermore, based on existing theories of the evolution of tool use\textsuperscript{12--16,18--21}, we propose
 that the unobserved tool use capabilities are additionally caused by relative
@@
 suggests that only a small proportion of extant parrot species (11 out of 398;
-3\%) use tools\textsuperscript{11,24--36}. Parrot tool
+3\%) use tools\textsuperscript{12,26--38}. Parrot tool
 use thus provides an ideal test case for examining how robust sampling is in the
@@
 all extant parrot species are bred in the aviculture industry and kept as pets
-worldwide\textsuperscript{37--43}, enabling us to leverage the power of digital video platforms to
-search for evidence of tool use\textsuperscript{21}. Third, detailed data on relative
-brain sizes\textsuperscript{44--49}, feeding strategies\textsuperscript{50}, and shared ancestry\textsuperscript{51} exist for parrots, allowing us to fit the statistical model implied
+worldwide\textsuperscript{39--45}, enabling us to leverage the power of digital video platforms to
+search for evidence of tool use\textsuperscript{23}. Third, detailed data on relative
+brain sizes\textsuperscript{46--51}, feeding strategies\textsuperscript{52}, and shared ancestry\textsuperscript{53} exist for parrots, allowing us to fit the statistical model implied
 by Figure \ref{fig:plotDAG} to the entire parrot order.
@@
 of the animal's body to achieve a goal\textsuperscript{10}, while ``borderline'' tool
-use involved the use of an object that was still attached to a substrate\textsuperscript{52}.
+use involved the use of an object that was still attached to a substrate\textsuperscript{54}.
 
@@
 videos) was a moulted feather. Human-made objects (e.g., pens, spoons, pieces of
-wood, cardboard) were also common.
+wood, cardboard) were also common. In 66
+videos, parrots manipulated the tool while keeping their body still, rather than
+holding the tool still and moving towards it.
 
@@
 established through genetic testing, and sexual dimorphism in parrots is
-rare\textsuperscript{53,54}, we could not typically ascertain if descriptions
+rare\textsuperscript{55,56}, we could not typically ascertain if descriptions
 were accurate. It is unclear if the disproportionately large number of males in
@@
 
-Survival cure models\textsuperscript{55}, also known as split population
-models\textsuperscript{56}, are used to analyse the time to some event of interest
+Survival cure models\textsuperscript{57}, also known as split population
+models\textsuperscript{58}, are used to analyse the time to some event of interest
 with the added assumption that a certain proportion of the population will never
@@
 have been used to analyse a variety of right-censored outcomes, from cancer
-relapse\textsuperscript{55} to criminal recidivism\textsuperscript{56}. The data are
+relapse\textsuperscript{57} to criminal recidivism\textsuperscript{58}. The data are
 right-censored because some individuals will have experienced the event when
@@
 else being equal those with fewer published papers and fewer video search hits
-have a higher probability of being undetected tool users (Supplementary Figure
+have a higher probability of being undetected tool users (Figure
 \ref{fig:plotSurvCure3}).
@@
 area-under-the-curve classification statistic of
-0.95 (Supplementary Figure
+0.95 (Figure
 \ref{fig:plotSurvCure9}). To further estimate the accuracy of the model's
@@
 for which tool use is unobserved in our data: the blue-eyed cockatoo (\emph{Cacatua
-opthalmica}). This species is endemic to Papua New Guinea and is relatively
+ophthalmica}). This species is endemic to Papua New Guinea and is relatively
 understudied, with only 6 published papers
@@
 clade containing several known tool users. This prediction makes sense given the
-high phylogenetic signal for tool use reported by the model (Supplementary
+high phylogenetic signal for tool use reported by the model (
 Figures \ref{fig:plotSurvCure5} and \ref{fig:plotSurvCure6}). Beyond the
@@
 effect of relative brain size and no difference between feeding strategies,
-respectively (Supplementary Figure \ref{fig:plotComparison}).
+respectively (Figure \ref{fig:plotComparison}).
 
@@
 discoveries from our video survey and from our phylogenetic modelling increased
-the likelihood that tool use was present in the most recent common ancestor for
-several parrot genera. These include the amazon parrots native to the Americas
-(\emph{Amazona}), the true white cockatoos and corellas found in South East Asia and
-Australasia (\emph{Cacatua}), the kea and the kākā from New Zealand (\emph{Nestor}), and
+the likelihood that the capacity for tool use was present in the most recent
+common ancestors for several parrot genera. These include the most recent common
+ancestor of amazon parrots native to the Americas (\emph{Amazona}), the most recent
+common ancestor of the true white cockatoos and corellas found in South East
+Asia and Australasia (\emph{Cacatua}), the most recent common ancestor of the kea and
+the kākā from New Zealand (\emph{Nestor}), and the most recent common ancestor for
 the \emph{Poicephalus} genus native to Africa (Table \ref{tab:tableASR};
-Supplementary Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}). These findings
-suggest that species from each of these genera may share their tool use
-capabilities via common descent from their respective common ancestors, rather
-than via independent evolution within each genus or behavioural innovation
-within species.
+Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}).
 
@@
 
-Since the earliest anecdotes of parrots using tools by Wallace in the 1880s\textsuperscript{57} and more systematic anecdotal reports in the 1970s\textsuperscript{58},
+Since the earliest anecdotes of parrots using tools by Wallace in the 1880s\textsuperscript{59} and more systematic anecdotal reports in the 1970s\textsuperscript{60},
 only 11 parrot species (3\% of all extant parrots) have been documented as tool
@@
 Instead, we discovered a large discrepancy between these two data sources, both
-in the prevalence of tool use and the species identified. This raises the
-possibility that insufficient research effort is a general issue across the
-scientific literature, both for tool use in other groups and for other rare
-behaviours.
+in the prevalence of tool use and the species identified, likely due to the
+numerous difficulties inherent to conducting observations in the wild. This
+raises the possibility that other rare behaviours remain yet to be discovered in
+the scientific literature.
 
@@
 key assumption made in the literature to date: that only a minority of parrots
-are tool users\textsuperscript{28,29,32,35,36}.
+are tool users\textsuperscript{30,31,34,37,38}.
 The paucity of evidence for tool use across parrots in the literature initially
@@
 analysis provides preliminary support for this hypothesis, revealing an
-increased probability of tool use among the most recent common ancestors for the
-\emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera. Even at this
-preliminary stage, our analysis therefore raises an alternative hypothesis for
-the observed tool use in \emph{Cacatua}\textsuperscript{28,36} and
-\emph{Nestor}\textsuperscript{24--27,29,32}, namely that tool behaviours have arisen due to the
+increased probability of the capacity for tool use among the most recent common
+ancestors for the \emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera. The
+complexity of tool use behaviour that such a basic capacity might afford, and
+the conditions under which it emerges in the wild, are yet to be established.
+However, even at this preliminary stage, our analysis raises an alternative
+hypothesis for the observed tool use in \emph{Cacatua}\textsuperscript{30,38}
+and \emph{Nestor}\textsuperscript{26--29,31,34}, namely that tool behaviours have arisen due to the
 common ancestor having the capacity to use tools, rather than from independent
@@
 tool use in our phylogenetic model, supporting previous theories linking
-relative brain size to increased tool innovation in birds\textsuperscript{11--13} and primates\textsuperscript{59}. We acknowledge that
+relative brain size to increased tool innovation in birds\textsuperscript{12--14} and primates\textsuperscript{61}. We acknowledge that
 encephalisation quotient is not a perfect measure due to measurement error and
@@
 quotient has much greater coverage across the parrot phylogeny than more
-fine-grained measures like whole neuron count\textsuperscript{60} and there is no reason
+fine-grained measures like whole neuron count\textsuperscript{62} and there is no reason
 to think that measurement error would produce the consistent patterns across our
@@
 relationships, we encourage further work on the specific neural correlates of
-technical intelligence in parrots, e.g.,\textsuperscript{61}. In our phylogenetic
+technical intelligence in parrots, e.g.,\textsuperscript{63}. In our phylogenetic
 model, we also found that tool use was somewhat more likely among feeding
@@
 abilities and technical innovation rates are required to expand a generalist
-species' dietary niche\textsuperscript{16,18,62}. However, the trend contradicts theories linking tool use to
+species' dietary niche\textsuperscript{18,20,64}. However, the trend contradicts theories linking tool use to
 dietary specialisation, whereby species eating specific foods that require
 extractive foraging have higher cognitive ability and are especially prone to
-using tools\textsuperscript{18}.
+using tools\textsuperscript{20}.
 
@@
 While parrots in the wild use tools to achieve a variety of goals, including
-extractive foraging and preening\textsuperscript{32,36}, parrots in captivity
-only require tools to achieve the latter goal. Despite this difference in the
-type of tool use observed, self-scratching is nonetheless a major category of
-animal tool use. Self-scratching also meets the definition for a more complex
-type of embodied tool use known as `tooling', the deliberate generation of a
-mechanical interface by using an object to manipulate another target or surface\textsuperscript{63}. This makes it difficult to dismiss self-scratching as
-unimportant: to do so would require a redefinition of tool-use in non-human
-animals. Moreover, the fact that we found strong phylogenetic clustering of
-self-scratching tool use from the video survey with other examples of tool use
-from the literature supports a common underlying cognitive mechanism. In line
-with this, some of the species of parrots that use tools for self-scratching in
-captivity also use tools for other purposes in the wild\textsuperscript{28,29,32,36}.
-
-There was little evidence to suggest that the observations of self-scratching
-tool use in the video survey were merely unintentional accidents or explicitly
-trained behaviours. Individual parrots often used tools slowly and repetitively
-over long periods of time, even across multiple different videos, suggesting
-that their behaviour was not random or accidental\textsuperscript{64}. Parrots
-preferentially employed self-scratching tools on areas of their body that were
-otherwise inaccessible, with 96\% of all instances involving scratching of the
-head or neck, suggesting intentional tool use. For 60\% of the species in the
-video survey, we found two or more videos of repetitive and sustained scratching
-by different individuals of the same species in separate households, suggesting
-that the manipulations were intentional and recurring events that did not
-represent unusual stereotypies of any single individual. Regarding the
+extractive foraging and preening\textsuperscript{34,38}, parrots in captivity
+only require tools to achieve the latter goal. It could be argued that
+self-scratching is a more cognitively simplistic form of tool use than
+extractive foraging as it is egocentric, meaning that the tool is directed
+towards oneself rather than an external object. Nevertheless, self-scratching
+meets the definition for a more complex type of embodied tool use known as
+`tooling', the deliberate generation of a mechanical interface by using an
+object to manipulate another target or surface\textsuperscript{65}. In our dataset,
+most self-scratching tooling instances involved manipulating the tool while
+keeping the body still, suggesting that these were goal-directed, deliberate
+movements by individuals. This makes it difficult to dismiss self-scratching as
+unimportant: to do so would require a redefinition of tool-use and tooling in
+non-human animals. Moreover, the fact that we found strong phylogenetic
+clustering of self-scratching tool use from the video survey with other examples
+of tool use from the literature supports a common underlying cognitive
+mechanism. In line with this, some of the species of parrots that use tools for
+self-scratching in captivity also use tools for other purposes in the wild\textsuperscript{30,31,34,38}.
+
+A potential concern with data originating from digital video platforms is its
+reliability\textsuperscript{23,66--70}.
+In particular, the self-care tool use instances detected in our video survey
+might be attributable to training or unintentional cueing by the birds' owners.
+However, there was little evidence to suggest that the observations of
+self-scratching tool use in the video survey were merely unintentional accidents
+or explicitly trained behaviours. Individual parrots often used tools slowly and
+repetitively over long periods of time, even across multiple different videos,
+suggesting that their behaviour was not random or accidental\textsuperscript{69}.
+Parrots preferentially employed self-scratching tools on areas of their body
+that were otherwise inaccessible, with 96\% of all instances involving scratching
+of the head or neck, suggesting intentional tool use. For 60\% of the species in
+the video survey, we found two or more videos of repetitive and sustained
+scratching by different individuals of the same species in separate households,
+suggesting that the manipulations were intentional and recurring events that did
+not represent unusual stereotypies of any single individual. Regarding the
 possibility of training or cueing from owners, over half of the videos contained
@@
 behaviours, which would likely appear uniformly across the phylogeny.
+Nevertheless, future work using data such as this should choose target
+behaviours carefully and examine videos for evidence of training or cueing.
+
+Our data reveals that a wide range of parrot species exhibit self-scratching
+tool use behaviours in captive environments. It is possible that these self-care
+behaviours emerge more often in captivity because pet parrots are kept with few
+or no conspecifics, and therefore must innovate tool use to preen inaccessible
+body areas, such as their heads and necks, which would have been otherwise
+preened by flock members. This may indicate that human interaction and
+allopreening in the absence of a conspecific is insufficient for pet parrots, as
+suggested by studies on welfare and chronic stress in lone captive parrots\textsuperscript{71--74}. Beyond social
+isolation in captivity, other factors that reduce preening efficacy by an
+individual might also lead to the innovation of self-care tooling: for example,
+a captive kea housed with conspecifics in a naturalistic environment was shown
+to have innovated the use of a pebble tool for self-care likely as a consequence
+of a missing upper mandible\textsuperscript{31}. These behaviours might therefore be
+innovated by individuals when ecologically necessary. Critically, however, a
+cognitive capacity to innovate a behaviour such as tool use must exist in a
+species in order to manifest in any environment, whether that be captive or in
+the wild. As such, despite differences in individuals' life experiences in
+captive and wild settings, such behaviour emerging in a captive setting at the
+very least indicates an underlying cognitive capacity to innovate that same
+behaviour in the wild.
 
 While missing data imputation is becoming more common in phylogenetic
-analyses\textsuperscript{65}, the important distinction between absence of
+analyses\textsuperscript{75}, the important distinction between absence of
 evidence and evidence of absence has not been given as much attention. Our
@@
 variables or modelling further causes of measurement error in the taxonomic
-record, such as species abundance and geographic accessibility\textsuperscript{20}.
+record, such as species abundance and geographic accessibility\textsuperscript{22}.
 
@@
 methods used in this study have the potential to be applied to other rarely
-observed behaviours, including tool use in other taxa\textsuperscript{66}, rhythmic
-entrainment in birds\textsuperscript{67--70},
-teasing behaviours in primates\textsuperscript{71}, and tactical deception across all
-animals\textsuperscript{72--74}. We hope that these methods
+observed behaviours, including tool use in other taxa\textsuperscript{76}, rhythmic
+entrainment in birds\textsuperscript{77--80},
+teasing behaviours in primates\textsuperscript{81}, and tactical deception across all
+animals\textsuperscript{82--84}. We hope that these methods
 will continue to uncover a diverse array of ephemeral behaviours that have as
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\newpage
+\nolinenumbers
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+This project was made possible through the support of a grant from the Templeton
+World Charity Foundation (A.H.T., X.J.N.). The authors would like to thank
+Daniel Sol for providing feedback on a previous version of the manuscript.
+
+\hypertarget{author-contributions}{%
+\section{Author Contributions}\label{author-contributions}}
+
+All authors contributed to the conceptualisation of the paper. A.P.M.B., X.J.N.,
+and A.H.T. developed the video search methodology. S.C., D.W., and Q.A.D.
+developed the statistical models and analysed the data. All the authors wrote
+the manuscript and approved the final version for submission.
+
+\hypertarget{declaration-of-interests}{%
+\section{Declaration of Interests}\label{declaration-of-interests}}
+
+The authors declare no competing interests.
+
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-MacLean2012}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{MacLean, E.L., Matthews, L.J., Hare, B.A., Nunn, C.L., Anderson, R.C., Aureli, F., Brannon, E.M., Call, J., Drea, C.M., Emery, N.J., et al.
+(2012).
+How does cognition evolve?
+Phylogenetic comparative psychology.
+Animal Cognition \emph{15}, 223--238.
+\url{https://doi.org/10.1007/s10071-011-0448-8}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2011}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Lefebvre, L. (2011). Taxonomic counts of cognition in the wild. Biology Letters \emph{7}, 631--633. \url{https://doi.org/10.1098/rsbl.2010.0556}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Logan2018}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{Logan, C.J., Avin, S., Boogert, N., Buskell, A., Cross, F.R., Currie, A., Jelbert, S., Lukas, D., Mares, R., Navarrete, A.F., et al.
+(2018).
+Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization.
+Comparative Cognition \& Behavior Reviews \emph{13}, 55--89.
+\url{https://doi.org/10.3819/CCBR.2018.130008}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Healy2007}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Healy, S.D., and Rowe, C.
+(2007).
+A critique of comparative studies of brain size.
+Proceedings of the Royal Society B: Biological Sciences \emph{274}, 453--464.
+\url{https://doi.org/10.1098/rspb.2006.3748}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Powell2017}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Powell, L.E., Isler, K., and Barton, R.A.
+(2017).
+Re-evaluating the link between brain size and behavioural ecology in primates.
+Proceedings of the Royal Society B: Biological Sciences \emph{284}, 20171765.
+\url{https://doi.org/10.1098/rspb.2017.1765}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodall1964}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Goodall, J. (1964). Tool-using and aimed throwing in a community of free-living chimpanzees. Nature \emph{201}, 1264--1266.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hunt1996}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Hunt, G.R. (1996). Manufacture and use of hook-tools by {N}ew {C}aledonian crows. Nature \emph{379}, 249--251. \url{https://doi.org/10.1038/379249a0}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Smolker1997}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Smolker, R., Richards, A., Connor, R., Mann, J., and Berggren, P.
+(1997).
+Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?
+Ethology \emph{103}, 454--465.
+\url{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Finn2009}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Finn, J.K., Tregenza, T., and Norman, M.D.
+(2009).
+Defensive tool use in a coconut-carrying octopus.
+Current Biology \emph{19}, R1069--R1070.
+\url{https://doi.org/10.1016/j.cub.2009.10.052}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Shumaker, R.W., Walkup, K.R., Beck, B.B., and Burghardt, G.M.
+(2011).
+Animal tool behavior: The use and manufacture of tools by animals (Johns Hopkins University Press) \url{https://doi.org/10.1353/book.98237}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Audet2024}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Audet, J.-N., Couture, M., Lefebvre, L., and Jarvis, E.D.
+(2024).
+Problem-solving skills are predicted by technical innovations in the wild and brain size in passerines.
+Nature Ecology \& Evolution \emph{8}, 806--816.
+\url{https://doi.org/10.1038/s41559-024-02342-7}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2002}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Lefebvre, L., Nicolakakis, N., and Boire, D. (2002). Tools and brains in birds. Behaviour \emph{139}, 939--973. \url{https://doi.org/10.1163/156853902320387918}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre1997}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E., and Finkelstein, A.
+(1997).
+Feeding innovations and forebrain size in birds.
+Animal Behaviour \emph{53}, 549--560.
+\url{https://doi.org/10.1006/anbe.1996.0330}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2004}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Lefebvre, L., Reader, S.M., and Sol, D.
+(2004).
+Brains, innovations and evolution in birds and primates.
+Brain, Behavior and Evolution \emph{63}, 233--246.
+\url{https://doi.org/10.1159/000076784}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2005}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Sol, D., Duncan, R.P., Blackburn, T.M., Cassey, P., and Lefebvre, L.
+(2005).
+Big brains, enhanced cognition, and response of birds to novel environments.
+Proceedings of the National Academy of Sciences \emph{102}, 5460--5465.
+\url{https://doi.org/10.1073/pnas.0408145102}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2009}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Sol, D. (2009). Revisiting the cognitive buffer hypothesis for the evolution of large brains. Biology Letters \emph{5}, 130--133. \url{https://doi.org/10.1098/rsbl.2008.0621}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kaplan2020}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Kaplan, G. (2020). Play behaviour, not tool using, relates to brain mass in a sample of birds. Scientific Reports \emph{10}, 20437. \url{https://doi.org/10.1038/s41598-020-76572-7}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2015}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{Ducatez, S., Clavel, J., and Lefebvre, L.
+(2015).
+Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?
+Journal of Animal Ecology \emph{84}, 79--89.
+\url{https://doi.org/10.1111/1365-2656.12255}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Overington2011}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{Overington, S.E., Griffin, A.S., Sol, D., and Lefebvre, L.
+(2011).
+Are innovative species ecological generalists?
+A test in {N}orth {A}merican birds.
+Behavioral Ecology \emph{22}, 1286--1293.
+\url{https://doi.org/10.1093/beheco/arr130}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2020}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
+(2020).
+Linking ecology and cognition: Does ecological specialisation predict cognitive test performance?
+Behavioral Ecology and Sociobiology \emph{74}, 154.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MettkeHofmann2014}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Mettke-Hofmann, C. (2014). Cognitive ecology: Ecological factors, life-styles, and cognition. WIREs Cognitive Science \emph{5}, 345--360. \url{https://doi.org/10.1002/wcs.1289}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2014}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{Ducatez, S., and Lefebvre, L. (2014). Patterns of research effort in birds. PLOS ONE \emph{9}, e89955. \url{https://doi.org/10.1371/journal.pone.0089955}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Nelson2013}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{Nelson, X.J., and Fijn, N.
+(2013).
+The use of visual media as a tool for investigating animal behaviour.
+Animal Behaviour \emph{85}, 525--536.
+\url{https://doi.org/10.1016/j.anbehav.2012.12.009}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{Krueger, K., Esch, L., and Byrne, R.
+(2019).
+Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms.
+PLOS ONE \emph{14}, 1--20.
+\url{https://doi.org/10.1371/journal.pone.0218954}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pokharel2022}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{Pokharel, S.S., Sharma, N., and Sukumar, R.
+(2022).
+Viewing the rare through public lenses: Insights into dead calf carrying and other thanatological responses in {A}sian elephants using YouTube videos.
+Royal Society Open Science \emph{9}, 211740.
+\url{https://doi.org/10.1098/rsos.211740}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2009}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
+(2009).
+Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem.
+Biology Letters \emph{5}, 455--458.
+\url{https://doi.org/10.1098/rsbl.2009.0114}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2010}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
+(2010).
+Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task.
+Animal Behaviour \emph{80}, 783--789.
+\url{https://doi.org/10.1016/j.anbehav.2010.08.007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011a}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Auersperg, A.M.I., Huber, L., and Gajdon, G.K.
+(2011).
+Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis}).
+Biology Letters \emph{7}, 825--828.
+\url{https://doi.org/10.1098/rsbl.2011.0388}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011b}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Auersperg, A.M.I., Bayern, A.M.P.
+von, Gajdon, G.K., Huber, L., and Kacelnik, A.
+(2011).
+Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm.
+PLOS ONE \emph{6}, 1--8.
+\url{https://doi.org/10.1371/journal.pone.0020231}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2012}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Auersperg, A.M.I., Szabo, B., von Bayern, A.M.P., and Kacelnik, A.
+(2012).
+Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo.
+Current Biology \emph{22}, R903--R904.
+\url{https://doi.org/10.1016/j.cub.2012.09.002}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bastos2021}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Bastos, A.P., Horváth, K., Webb, J.L., Wood, P.M., and Taylor, A.H.
+(2021).
+Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
+Scientific Reports \emph{11}, 18035.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-BentleyCondit2010}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{Bentley-Condit, V., and Smith, E.O.
+(2010).
+Animal tool use: Current definitions and an updated comprehensive catalog.
+Behaviour \emph{147}, 185--32A.
+\url{https://doi.org/10.1163/000579509X12512865686555}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Borsari2005}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Borsari, A., and Ottoni, E.B.
+(2005).
+Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus}).
+Animal Cognition \emph{8}, 48--52.
+\url{https://doi.org/10.1007/s10071-004-0221-3}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodman2018}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{Goodman, M., Hayward, T., and Hunt, G.R.
+(2018).
+Habitual tool use innovated by free-living {N}ew {Z}ealand kea.
+Scientific Reports \emph{8}, 13935.
+\url{https://doi.org/10.1038/s41598-018-32363-9}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Heinsohn2017}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{Heinsohn, R., Zdenek, C.N., Cunningham, R.B., Endler, J.A., and Langmore, N.E.
+(2017).
+Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music.
+Science Advances \emph{3}, e1602399.
+\url{https://doi.org/10.1126/sciadv.1602399}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Janzen1976}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Janzen, M.J., Janzen, D.H., and Pond, C.M. (1976). Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). Biotropica \emph{8}, 70.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lambert2015}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Lambert, M.L., Seed, A.M., and Slocombe, K.E.
+(2015).
+A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa}).
+Biology Letters \emph{11}, 20150861.
+\url{https://doi.org/10.1098/rsbl.2015.0861}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-OHara2021}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{O'Hara, M., Mioduszewska, B., Mundry, R., Yohanna, Haryoko, T., Rachmatika, R., Prawiradilaga, D.M., Huber, L., and Auersperg, A.M.I.
+(2021).
+Wild {G}offin's cockatoos flexibly manufacture and use tool sets.
+Current Biology \emph{31}, 4512--4520.e6.
+\url{https://doi.org/10.1016/j.cub.2021.08.009}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{Anderson, P.
+(2003).
+A bird in the house: An anthropological perspective on companion parrots.
+Society \& Animals \emph{11}, 393--418.
+\url{https://doi.org/10.1163/156853003322796109}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{Carrete, M., and Tella, J.
+(2008).
+Wild-bird trade and exotic invasions: A new link of conservation concern?
+Frontiers in Ecology and the Environment \emph{6}, 207--211.
+\url{https://doi.org/10.1890/070075}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{Drews, C.
+(2001).
+Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers.
+Society \& Animals \emph{9}, 107--126.
+\url{https://doi.org/10.1163/156853001753639233}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
+\CSLLeftMargin{42. }%
+\CSLRightInline{Kelly, D., McCarthy, E., Menzel, K., and Engebretson, M.
+(2014).
+\href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{Li, L., and Jiang, Z. (2014). International trade of {CITES} listed bird species in {C}hina. PLOS ONE \emph{9}, 1--8. \url{https://doi.org/10.1371/journal.pone.0085012}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{Su, S., Cassey, P., Vall-llosera, M., and Blackburn, T.M.
+(2015).
+Going cheap: Determinants of bird price in the {T}aiwanese pet market.
+PLOS ONE \emph{10}, 1--17.
+\url{https://doi.org/10.1371/journal.pone.0127482}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{Young, A.M., Hobson, E.A., Lackey, L.B., and Wright, T.F.
+(2012).
+Survival on the ark: Life-history trends in captive parrots.
+Animal Conservation \emph{15}, 28--43.
+\url{https://doi.org/10.1111/j.1469-1795.2011.00477.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{Flammer, K., Whitt-Smith, D., and Papich, M.
+(2001).
+Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection.
+Journal of Avian Medicine and Surgery \emph{15}, 276--282.
+\url{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{Iwaniuk, A.N., Dean, K.M., and Nelson, J.E.
+(2005).
+Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
+Brain, Behavior and Evolution \emph{65}, 40--59.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
+\CSLLeftMargin{48. }%
+\CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P.R., and Ihunwo, A.O.
+(2018).
+Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh}).
+Frontiers in Neuroanatomy \emph{12}, 7.
+\url{https://doi.org/10.3389/fnana.2018.00007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{Olkowicz, S., Kocourek, M., Lučan, R.K., Porteš, M., Fitch, W.T., Herculano-Houzel, S., and Němec, P.
+(2016).
+Birds have primate-like numbers of neurons in the forebrain.
+Proceedings of the National Academy of Sciences \emph{113}, 7255--7260.
+\url{https://doi.org/10.1073/pnas.1517131113}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{Schuck-Paim, C., Alonso, W.J., and Ottoni, E.B.
+(2008).
+Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots.
+Brain, Behavior and Evolution \emph{71}, 200--215.
+\url{https://doi.org/10.1159/000119710}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
+\CSLLeftMargin{51. }%
+\CSLRightInline{Silva, T., Guzmán, A., Urantówka, A.D., and Mackiewicz, P.
+(2017).
+A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny.
+PeerJ \emph{5}, e3475.
+\url{https://doi.org/10.7717/peerj.3475}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
+\CSLLeftMargin{52. }%
+\CSLRightInline{Wilman, H., Belmaker, J., Simpson, J., Rosa, C.
+de la, Rivadeneira, M.M., and Jetz, W.
+(2016).
+EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals.
+\url{https://doi.org/10.6084/m9.figshare.c.3306933.v1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
+\CSLLeftMargin{53. }%
+\CSLRightInline{Jetz, W., Thomas, G.H., Joy, J.B., Hartmann, K., and Mooers, A.O. (2012). The global diversity of birds in space and time. Nature \emph{491}, 444--448.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
+\CSLLeftMargin{54. }%
+\CSLRightInline{Seed, A., and Byrne, R. (2010). Animal tool-use. Current Biology \emph{20}, R1032--R1039. \url{https://doi.org/10.1016/j.cub.2010.09.042}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
+\CSLLeftMargin{55. }%
+\CSLRightInline{Bercovitz, A.B. (1987). Avian sex identification techniques. In Companion bird medicine, E. W. Burr, ed. (Iowa State University Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
+\CSLLeftMargin{56. }%
+\CSLRightInline{Hoyo, J.D., and Bierregaard, R. (2011). Handbook of the birds of the world (Lynx Edicions).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
+\CSLLeftMargin{57. }%
+\CSLRightInline{Amico, M., and Van Keilegom, I.
+(2018).
+Cure models in survival analysis.
+Annual Review of Statistics and Its Application \emph{5}, 311--342.
+\url{https://doi.org/10.1146/annurev-statistics-031017-100101}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
+\CSLLeftMargin{58. }%
+\CSLRightInline{Schmidt, P., and Witte, A.D.
+(1989).
+Predicting criminal recidivism using {``split population''} survival time models.
+Journal of Econometrics \emph{40}, 141--159.
+\url{https://doi.org/10.1016/0304-4076(89)90034-1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
+\CSLLeftMargin{59. }%
+\CSLRightInline{Wallace, A.R. (1869). The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature (MacMillan; Co.).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodall1971}{}}%
+\CSLLeftMargin{60. }%
+\CSLRightInline{Goodall, J.
+(1971).
+Tool-using in primates and other vertebrates.
+In Advances in the study of behavior., D.
+S.
+Lehrman, R.
+A.
+Hinde, and E.
+Shaw, eds.
+(Academic Press), pp.
+195--249.
+\url{https://doi.org/10.1016/S0065-3454(08)60157-6}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
+\CSLLeftMargin{61. }%
+\CSLRightInline{Reader, S.M., and Laland, K.N.
+(2002).
+Social intelligence, innovation, and enhanced brain size in primates.
+Proceedings of the National Academy of Sciences \emph{99}, 4436--4441.
+\url{https://doi.org/10.1073/pnas.062041299}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
+\CSLLeftMargin{62. }%
+\CSLRightInline{Sol, D., Olkowicz, S., Sayol, F., Kocourek, M., Zhang, Y., Marhounová, L., Osadnik, C., Corssmit, E., Garcia-Porta, J., Martin, T.E., et al.
+(2022).
+Neuron numbers link innovativeness with both absolute and relative brain size in birds.
+Nature Ecology \& Evolution \emph{6}, 1381--1389.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
+\CSLLeftMargin{63. }%
+\CSLRightInline{Cabrera-Álvarez, M.J., and Clayton, N.S.
+(2020).
+Neural processes underlying tool use in humans, macaques, and corvids.
+Frontiers in Psychology \emph{11}, 560669.
+\url{https://doi.org/10.3389/fpsyg.2020.560669}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
+(2021).
+Linking cognition to ecology in wild sympatric mouse lemur species.
+Proceedings of the Royal Society B: Biological Sciences \emph{288}, 20211728.
+\url{https://doi.org/10.1098/rspb.2021.1728}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
+\CSLLeftMargin{65. }%
+\CSLRightInline{Fragaszy, D.M., and Mangalam, M.
+(2018).
+Tooling.
+In Advances in the study of behavior., M.
+Naguib, L.
+Barrett, S.
+D.
+Healy, J.
+Podos, L.
+W.
+Simmons, and M.
+Zuk, eds.
+(Academic Press), pp.
+177--241.
+\url{https://doi.org/10.1016/bs.asb.2018.01.001}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2020}{}}%
+\CSLLeftMargin{66. }%
+\CSLRightInline{Auersperg, A.M.I., Schwing, R., Mioduszewska, B., O'Hara, M., and Huber, L.
+(2020).
+Do puffins use tools?
+Proceedings of the National Academy of Sciences \emph{117}, 11859--11859.
+\url{https://doi.org/10.1073/pnas.2001988117}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-DechaumeMoncharmont2020}{}}%
+\CSLLeftMargin{67. }%
+\CSLRightInline{Dechaume-Moncharmont, F.-X.
+(2020).
+Touchy matter: The delicate balance between {M}organ's canon and open-minded description of advanced cognitive skills in the animal.
+Peer Community in Ecology, 100042.
+\url{https://doi.org/10.24072/pci.ecology.100042}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Farrar2020}{}}%
+\CSLLeftMargin{68. }%
+\CSLRightInline{Farrar, B.G. (2020). Evidence of tool use in a seabird? PsyArXiv. \url{https://doi.org/10.31234/osf.io/463hk}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
+\CSLLeftMargin{69. }%
+\CSLRightInline{Sándor, K., and Miklósi, Á.
+(2020).
+How to report anecdotal observations?
+A new approach based on a lesson from "puffin tool use".
+Frontiers in Psychology \emph{11}, 555487.
+\url{https://doi.org/10.3389/fpsyg.2020.555487}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vonBayern2020}{}}%
+\CSLLeftMargin{70. }%
+\CSLRightInline{von Bayern, A.M., Jacobs, I., and Osvath, M.
+(2020).
+Tool-using puffins prickle the puzzle of cognitive evolution.
+Proceedings of the National Academy of Sciences \emph{117}, 2737--2739.
+\url{https://doi.org/10.1073/pnas.1922117117}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Aydinonat2014}{}}%
+\CSLLeftMargin{71. }%
+\CSLRightInline{Aydinonat, D., Penn, D.J., Smith, S., Moodley, Y., Hoelzl, F., Knauer, F., and Schwarzenberger, F.
+(2014).
+Social isolation shortens telomeres in {A}frican {G}rey parrots (\emph{{P}sittacus erithacus erithacus}).
+PLOS ONE \emph{9}, e93839.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Engebretson2006}{}}%
+\CSLLeftMargin{72. }%
+\CSLRightInline{Engebretson, M. (2006). The welfare and suitability of parrots as companion animals: A review. Animal Welfare \emph{15}, 263--276. \url{https://doi.org/10.1017/S0962728600030475}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mason2010}{}}%
+\CSLLeftMargin{73. }%
+\CSLRightInline{Mason, G.J.
+(2010).
+Species differences in responses to captivity: Stress, welfare and the comparative method.
+Trends in Ecology \& Evolution \emph{25}, 713--721.
+\url{https://doi.org/10.1016/j.tree.2010.08.011}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Meehan2003}{}}%
+\CSLLeftMargin{74. }%
+\CSLRightInline{Meehan, C., Garner, J., and Mench, J.
+(2003).
+Isosexual pair housing improves the welfare of young amazon parrots.
+Applied Animal Behaviour Science \emph{81}, 73--88.
+\url{https://doi.org/10.1016/S0168-1591(02)00238-1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
+\CSLLeftMargin{75. }%
+\CSLRightInline{Debastiani, V.J., Bastazini, V.A.G., and Pillar, V.D.
+(2021).
+Using phylogenetic information to impute missing functional trait values in ecological databases.
+Ecological Informatics \emph{63}, 101315.
+\url{https://doi.org/10.1016/j.ecoinf.2021.101315}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
+\CSLLeftMargin{76. }%
+\CSLRightInline{Hunt, G.R., Gray, R.D., and Taylor, A.H.
+(2013).
+Why is tool use rare in animals?
+In Tool use in animals: Cognition and ecology, C.
+M.
+Sanz, J.
+Call, and C.
+Boesch, eds.
+(Cambridge University Press), pp.
+89--118.
+\url{https://doi.org/10.1017/CBO9780511894800.007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
+\CSLLeftMargin{77. }%
+\CSLRightInline{Benichov, J.I., Globerson, E., and Tchernichovski, O.
+(2016).
+Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans.
+Frontiers in Human Neuroscience \emph{10}.
+\url{https://doi.org/10.3389/fnhum.2016.00255}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
+\CSLLeftMargin{78. }%
+\CSLRightInline{Patel, A.D., Iversen, J.R., Bregman, M.R., and Schulz, I.
+(2009).
+Experimental evidence for synchronization to a musical beat in a nonhuman animal.
+Current Biology \emph{19}, 827--830.
+\url{https://doi.org/10.1016/j.cub.2009.03.038}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
+\CSLLeftMargin{79. }%
+\CSLRightInline{ten Cate, C., Spierings, M., Hubert, J., and Honing, H.
+(2016).
+Can birds perceive rhythmic patterns?
+A review and experiments on a songbird and a parrot species.
+Frontiers in Psychology \emph{7}.
+\url{https://doi.org/10.3389/fpsyg.2016.00730}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
+\CSLLeftMargin{80. }%
+\CSLRightInline{Wilson, M., and Cook, P.F.
+(2016).
+Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed.
+Psychonomic Bulletin \& Review \emph{23}, 1647--1659.
+\url{https://doi.org/10.3758/s13423-016-1013-x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
+\CSLLeftMargin{81. }%
+\CSLRightInline{Eckert, J., Winkler, S.L., and Cartmill, E.A.
+(2020).
+Just kidding: The evolutionary roots of playful teasing.
+Biology Letters \emph{16}, 20200370.
+\url{https://doi.org/10.1098/rsbl.2020.0370}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
+\CSLLeftMargin{82. }%
+\CSLRightInline{Bro-Jørgensen, J., and Pangle, W.M.
+(2010).
+Male topi antelopes alarm snort deceptively to retain females for mating.
+The American Naturalist \emph{176}, E33--E39.
+\url{https://doi.org/10.1086/653078}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
+\CSLLeftMargin{83. }%
+\CSLRightInline{Byrne, R.W., and Whiten, A.
+(1988).
+Toward the next generation in data quality: A new survey of primate tactical deception.
+Behavioral and Brain Sciences \emph{11}, 267--273.
+\url{https://doi.org/10.1017/S0140525X00049955}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
+\CSLLeftMargin{84. }%
+\CSLRightInline{Byrne, R.W., and Whiten, A.
+(1991).
+Computation and mindreading in primate tactical deception.
+In Natural theories of mind: Evolution, development and simulation of everyday mindreading, A.
+Whiten, ed.
+(Basil Blackwell), pp.
+127--141.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
+\CSLLeftMargin{85. }%
+\CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership} (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
+\CSLLeftMargin{86. }%
+\CSLRightInline{Jerison, H.J. (1973). Evolution of the brain and intelligence (Academic Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
+\CSLLeftMargin{87. }%
+\CSLRightInline{Paradis, E., and Schliep, K.
+(2019).
+{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}.
+Bioinformatics \emph{35}, 526--528.
+\url{https://doi.org/10.1093/bioinformatics/bty633}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
+\CSLLeftMargin{88. }%
+\CSLRightInline{McElreath, R.
+(2020).
+\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition} 2nd ed.
+(CRC Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
+\CSLLeftMargin{89. }%
+\CSLRightInline{Stan Development Team (2020). \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
+\CSLLeftMargin{90. }%
+\CSLRightInline{Revell, L.J.
+(2012).
+{phytools}: An {R} package for phylogenetic comparative biology (and other things).
+Methods in Ecology and Evolution \emph{3}, 217--223.
+\url{https://doi.org/10.1111/j.2041-210X.2011.00169.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
+\CSLLeftMargin{91. }%
+\CSLRightInline{R Core Team (2022). \href{https://www.R-project.org/}{R: A language and environment for statistical computing} (R Foundation for Statistical Computing).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
+\CSLLeftMargin{92. }%
+\CSLRightInline{Yu, G., Smith, D., Zhu, H., Guan, Y., and Lam, T.T.-Y.
+(2017).
+{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data.
+Methods in Ecology and Evolution \emph{8}, 28--36.
+\url{https://doi.org/10.1111/2041-210X.12628}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
+\CSLLeftMargin{93. }%
+\CSLRightInline{Wickham, H. (2016). \href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis} (Springer-Verlag New York).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
+\CSLLeftMargin{94. }%
+\CSLRightInline{Wilke, C.O. (2020). \href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
+\CSLLeftMargin{95. }%
+\CSLRightInline{Landau, W.M.
+(2021).
+The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing.
+Journal of Open Source Software \emph{6}, 2959.
+\url{https://doi.org/10.21105/joss.02959}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
+\CSLLeftMargin{96. }%
+\CSLRightInline{Aust, F., and Barth, M. (2022). \href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}.}
+
+\end{CSLReferences}
+
+\endgroup
+
+\newpage
+\linenumbers
+
+\hypertarget{star-methods}{%
+\section{STAR Methods}\label{star-methods}}
+
+\hypertarget{resource-availability}{%
+\subsection{Resource Availability}\label{resource-availability}}
+
+\hypertarget{lead-contact}{%
+\subsubsection{Lead contact}\label{lead-contact}}
+
+Further information about resources should be directed to Scott Claessens
+(\href{mailto:scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}}).
+
+\hypertarget{materials-availability}{%
+\subsubsection{Materials availability}\label{materials-availability}}
+
+This study did not generate new unique materials.
+
+\hypertarget{data-and-code-availability}{%
+\subsubsection{Data and code availability}\label{data-and-code-availability}}
+
+All data have been deposited on GitHub and are publicly available as of the date
+of publication. DOIs are listed in the key resources table.
+
+All original code has been deposited on GitHub and is publicly available as of
+the date of publication. DOIs are listed in the key resources table.
+
+\hypertarget{method-details}{%
+\subsection{Method Details}\label{method-details}}
 
 \hypertarget{video-searches-and-coding}{%
-\subsection{Video searches and coding}\label{video-searches-and-coding}}
+\subsubsection{Video searches and coding}\label{video-searches-and-coding}}
 
@@
 of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all
-countries where bird ownership was reported as \textgreater5\%\textsuperscript{75}, namely,
+countries where bird ownership was reported as \textgreater5\%\textsuperscript{85}, namely,
 Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish,
@@
 any parrots. At this point, we ended that search and initiated the next search.
-In line with previous recommendations\textsuperscript{21}, we planned to exclude any
+In line with previous recommendations\textsuperscript{23}, we planned to exclude any
 videos that consisted of four or more shots edited together so as to ensure the
@@
 Borderline tool use was similarly defined, except that it involved the use of an
-object that was still attached to a substrate\textsuperscript{52}. For example, if
+object that was still attached to a substrate\textsuperscript{54}. For example, if
 individuals used a fallen feather or stick for self-scratching this was defined
@@
 to one's body (or, in the case of borderline tool use, rubbing repetitively
-against an attached object\textsuperscript{64}).
+against an attached object\textsuperscript{69}).
 
@@
 \hypertarget{data-for-parrot-species}{%
-\subsection{Data for parrot species}\label{data-for-parrot-species}}
-
-We collected data for 194 parrot species (Supplementary Figures
+\subsubsection{Data for parrot species}\label{data-for-parrot-species}}
+
+We collected data for 194 parrot species (Figures
 \ref{fig:plotPhylo2} - \ref{fig:plotPhylo4}). We gathered feeding strategy
 data as a dichotomous variable (``generalist'' or ``specialist'') from the
-EltonTraits ecological database\textsuperscript{50}. As per the database, specialists
+EltonTraits ecological database\textsuperscript{52}. As per the database, specialists
 were defined as species whose diet comprised at least 70\% of a single food
@@
 for all known body mass (g) and brain mass (g) values across
-parrots\textsuperscript{44--49}. For all species for which we obtained body and brain mass data, we
+parrots\textsuperscript{46--51}. For all species for which we obtained body and brain mass data, we
 calculated the encephalisation quotient (EQ) using the following
-formula\textsuperscript{76}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
+formula\textsuperscript{86}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
 found body mass and brain mass data for a total of 194 parrot species. This
@@
 
-For phylogenetic data, we used the phylogenetic tool at www.birdtree.org\textsuperscript{51} to compile 1000 posterior draws of phylogenetic trees for 174 of the
+For phylogenetic data, we used the phylogenetic tool at www.birdtree.org\textsuperscript{53} to compile 1000 posterior draws of phylogenetic trees for 174 of the
 194 parrot species for which both EQ and genomic data exist. A single maximum
@@
 
+\hypertarget{quantification-and-statistical-analysis}{%
+\subsection{Quantification and Statistical Analysis}\label{quantification-and-statistical-analysis}}
+
 \hypertarget{phylogenetic-signal}{%
-\subsection{Phylogenetic signal}\label{phylogenetic-signal}}
-
-We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{77} to
+\subsubsection{Phylogenetic signal}\label{phylogenetic-signal}}
+
+We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{87} to
 calculate phylogenetic signal, for both the pre-survey and post-survey tool use
@@
 \hypertarget{causal-model-of-tool-use}{%
-\subsection{Causal model of tool use}\label{causal-model-of-tool-use}}
+\subsubsection{Causal model of tool use}\label{causal-model-of-tool-use}}
 
@@
 on theory, we also assumed that unobserved tool use is caused by feeding
-strategy and relative brain size\textsuperscript{11--14,16--18}. Finally, we
+strategy and relative brain size\textsuperscript{12--15,18--20}. Finally, we
 assumed that shared phylogenetic history causes unobserved confounding and
@@
 \hypertarget{bayesian-phylogenetic-survival-cure-model}{%
-\subsection{Bayesian phylogenetic survival cure model}\label{bayesian-phylogenetic-survival-cure-model}}
+\subsubsection{Bayesian phylogenetic survival cure model}\label{bayesian-phylogenetic-survival-cure-model}}
 
@@
 and \(\lambda\) (the rate of the exponential distribution). We use an
-Ornstein-Uhlenbeck Gaussian process\textsuperscript{78} to model phylogenetic
+Ornstein-Uhlenbeck Gaussian process\textsuperscript{88} to model phylogenetic
 covariance. Below, we specify the full model with priors:
@@
 The priors for this model produce reasonable prior predictions of the
-probabilities of tool use for each parrot species (Supplementary Figure
+probabilities of tool use for each parrot species (Figure
 \ref{fig:plotSurvCure7}), but a sensitivity analysis revealed that the ranking
 and posterior probabilities reported in the main text were robust to modifying
-these priors (Supplementary Figure \ref{fig:plotSurvCure8}). We estimated the
+these priors (Figure \ref{fig:plotSurvCure8}). We estimated the
 posterior distribution of this model using Hamiltonian Monte Carlo as
-implemented in Stan version 2.26.1\textsuperscript{79}. We ran the model for 4000
+implemented in Stan version 2.26.1\textsuperscript{89}. We ran the model for 4000
 samples, with 2000 warmup samples, and iterated the model over 100 posterior
@@
 effective sample sizes suggested that the model converged normally. Trace plots
-are reported in Supplementary Figure \ref{fig:plotTrace}. We report
+are reported in Figure \ref{fig:plotTrace}. We report
 equal-tailed credible intervals to describe the posterior distribution of this
@@
 parameters. The model was able to successfully recover those parameters
-(Supplementary Figure \ref{fig:plotSurvCureSim}). We also ran a
+(Figure \ref{fig:plotSurvCureSim}). We also ran a
 leave-one-species-out exercise to ensure that we could accurately predict known
@@
 \hypertarget{ancestral-state-reconstruction}{%
-\subsection{Ancestral state reconstruction}\label{ancestral-state-reconstruction}}
+\subsubsection{Ancestral state reconstruction}\label{ancestral-state-reconstruction}}
 
@@
 parrots, we fitted three exploratory ancestral state reconstruction models. We
-used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{80},
+used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{90},
 iterating the function over 100 posterior parrot phylogenies. This function
@@
 \hypertarget{reproducibility}{%
-\subsection{Reproducibility}\label{reproducibility}}
-
-All analyses were conducted in R v4.2.1.\textsuperscript{81}. Visualisations were
-produced using the \emph{ggtree}\textsuperscript{82}, \emph{ggplot2}\textsuperscript{83}, and \emph{cowplot}\textsuperscript{84} packages. The manuscript was reproducibly generated using the
-\emph{targets}\textsuperscript{85} and \emph{papaja}\textsuperscript{86} packages. Code to reproduce all
+\subsubsection{Reproducibility}\label{reproducibility}}
+
+All analyses were conducted in R v4.2.1.\textsuperscript{91}. Visualisations were
+produced using the \emph{ggtree}\textsuperscript{92}, \emph{ggplot2}\textsuperscript{93}, and \emph{cowplot}\textsuperscript{94} packages. The manuscript was reproducibly generated using the
+\emph{targets}\textsuperscript{95} and \emph{papaja}\textsuperscript{96} packages. Code to reproduce all
 analyses and figures can be found here:
@@
 \nolinenumbers
-
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-This project was made possible through the support of a grant from the Templeton
-World Charity Foundation (A.H.T., X.J.N.). The authors would like to thank
-Daniel Sol for providing feedback on a previous version of the manuscript.
-
-\hypertarget{author-contributions}{%
-\section{Author Contributions}\label{author-contributions}}
-
-All authors contributed to the conceptualisation of the paper. A.P.M.B., X.J.N.,
-and A.H.T. developed the video search methodology. S.C., D.W., and Q.A.D.
-developed the statistical models and analysed the data. All the authors wrote
-the manuscript and approved the final version for submission.
-
-\hypertarget{competing-interests}{%
-\section{Competing Interests}\label{competing-interests}}
-
-The authors declare no competing interests.
-
-\hypertarget{data-availability}{%
-\section{Data Availability}\label{data-availability}}
-
-All data used in this study are publicly available on GitHub:
-\url{https://github.com/ScottClaessens/phyloParrot}
-
-\hypertarget{code-availability}{%
-\section{Code Availability}\label{code-availability}}
-
-All code to reproduce the analyses in this study are publicly available on
-GitHub: \url{https://github.com/ScottClaessens/phyloParrot}
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-MacLean2012}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{MacLean, E.L., Matthews, L.J., Hare, B.A., Nunn, C.L., Anderson, R.C., Aureli, F., Brannon, E.M., Call, J., Drea, C.M., Emery, N.J., et al.
-(2012).
-How does cognition evolve?
-Phylogenetic comparative psychology.
-Animal Cognition \emph{15}, 223--238.
-\href{https://doi.org/10.1007/s10071-011-0448-8}{10.1007/s10071-011-0448-8}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2011}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Lefebvre, L. (2011). Taxonomic counts of cognition in the wild. Biology Letters \emph{7}, 631--633. \href{https://doi.org/10.1098/rsbl.2010.0556}{10.1098/rsbl.2010.0556}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Logan2018}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{Logan, C.J., Avin, S., Boogert, N., Buskell, A., Cross, F.R., Currie, A., Jelbert, S., Lukas, D., Mares, R., Navarrete, A.F., et al.
-(2018).
-Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization.
-Comparative Cognition \& Behavior Reviews \emph{13}, 55--89.
-\href{https://doi.org/10.3819/CCBR.2018.130008}{10.3819/CCBR.2018.130008}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Healy2007}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{Healy, S.D., and Rowe, C.
-(2007).
-A critique of comparative studies of brain size.
-Proceedings of the Royal Society B: Biological Sciences \emph{274}, 453--464.
-\href{https://doi.org/10.1098/rspb.2006.3748}{10.1098/rspb.2006.3748}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Powell2017}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{Powell, L.E., Isler, K., and Barton, R.A.
-(2017).
-Re-evaluating the link between brain size and behavioural ecology in primates.
-Proceedings of the Royal Society B: Biological Sciences \emph{284}, 20171765.
-\href{https://doi.org/10.1098/rspb.2017.1765}{10.1098/rspb.2017.1765}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodall1964}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{Goodall, J. (1964). Tool-using and aimed throwing in a community of free-living chimpanzees. Nature \emph{201}, 1264--1266.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hunt1996}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Hunt, G.R. (1996). Manufacture and use of hook-tools by {N}ew {C}aledonian crows. Nature \emph{379}, 249--251. \href{https://doi.org/10.1038/379249a0}{10.1038/379249a0}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Smolker1997}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Smolker, R., Richards, A., Connor, R., Mann, J., and Berggren, P.
-(1997).
-Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?
-Ethology \emph{103}, 454--465.
-\href{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}{10.1111/j.1439-0310.1997.tb00160.x}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Finn2009}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Finn, J.K., Tregenza, T., and Norman, M.D.
-(2009).
-Defensive tool use in a coconut-carrying octopus.
-Current Biology \emph{19}, R1069--R1070.
-\href{https://doi.org/10.1016/j.cub.2009.10.052}{10.1016/j.cub.2009.10.052}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Shumaker, R.W., Walkup, K.R., Beck, B.B., and Burghardt, G.M.
-Animal tool behavior: The use and manufacture of tools by animals (Johns Hopkins University Press) \href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2002}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Lefebvre, L., Nicolakakis, N., and Boire, D.
-(2002).
-Tools and brains in birds.
-Behaviour \emph{139}, 939--973.
-\href{https://doi.org/10.1163/156853902320387918}{10.1163/156853902320387918}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre1997}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E., and Finkelstein, A.
-(1997).
-Feeding innovations and forebrain size in birds.
-Animal Behaviour \emph{53}, 549--560.
-\href{https://doi.org/10.1006/anbe.1996.0330}{10.1006/anbe.1996.0330}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2004}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Lefebvre, L., Reader, S.M., and Sol, D.
-(2004).
-Brains, innovations and evolution in birds and primates.
-Brain, Behavior and Evolution \emph{63}, 233--246.
-\href{https://doi.org/10.1159/000076784}{10.1159/000076784}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2005}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Sol, D., Duncan, R.P., Blackburn, T.M., Cassey, P., and Lefebvre, L.
-(2005).
-Big brains, enhanced cognition, and response of birds to novel environments.
-Proceedings of the National Academy of Sciences \emph{102}, 5460--5465.
-\href{https://doi.org/10.1073/pnas.0408145102}{10.1073/pnas.0408145102}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2009}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Sol, D.
-(2009).
-Revisiting the cognitive buffer hypothesis for the evolution of large brains.
-Biology Letters \emph{5}, 130--133.
-\href{https://doi.org/10.1098/rsbl.2008.0621}{10.1098/rsbl.2008.0621}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2015}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Ducatez, S., Clavel, J., and Lefebvre, L.
-(2015).
-Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?
-Journal of Animal Ecology \emph{84}, 79--89.
-\href{https://doi.org/10.1111/1365-2656.12255}{10.1111/1365-2656.12255}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Overington2011}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Overington, S.E., Griffin, A.S., Sol, D., and Lefebvre, L.
-(2011).
-Are innovative species ecological generalists?
-A test in {N}orth {A}merican birds.
-Behavioral Ecology \emph{22}, 1286--1293.
-\href{https://doi.org/10.1093/beheco/arr130}{10.1093/beheco/arr130}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2020}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
-(2020).
-Linking ecology and cognition: Does ecological specialisation predict cognitive test performance?
-Behavioral Ecology and Sociobiology \emph{74}, 154.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MettkeHofmann2014}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Mettke-Hofmann, C.
-(2014).
-Cognitive ecology: Ecological factors, life-styles, and cognition.
-WIREs Cognitive Science \emph{5}, 345--360.
-\href{https://doi.org/10.1002/wcs.1289}{10.1002/wcs.1289}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2014}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Ducatez, S., and Lefebvre, L.
-(2014).
-Patterns of research effort in birds.
-PLOS ONE \emph{9}, e89955.
-\href{https://doi.org/10.1371/journal.pone.0089955}{10.1371/journal.pone.0089955}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Nelson2013}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Nelson, X.J., and Fijn, N.
-(2013).
-The use of visual media as a tool for investigating animal behaviour.
-Animal Behaviour \emph{85}, 525--536.
-\href{https://doi.org/10.1016/j.anbehav.2012.12.009}{10.1016/j.anbehav.2012.12.009}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{Krueger, K., Esch, L., and Byrne, R.
-(2019).
-Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms.
-PLOS ONE \emph{14}, 1--20.
-\href{https://doi.org/10.1371/journal.pone.0218954}{10.1371/journal.pone.0218954}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pokharel2022}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Pokharel, S.S., Sharma, N., and Sukumar, R.
-(2022).
-Viewing the rare through public lenses: Insights into dead calf carrying and other thanatological responses in asian elephants using YouTube videos.
-Royal Society Open Science \emph{9}, 211740.
-\href{https://doi.org/10.1098/rsos.211740}{10.1098/rsos.211740}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2009}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
-(2009).
-Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem.
-Biology Letters \emph{5}, 455--458.
-\href{https://doi.org/10.1098/rsbl.2009.0114}{10.1098/rsbl.2009.0114}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2010}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
-(2010).
-Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task.
-Animal Behaviour \emph{80}, 783--789.
-\href{https://doi.org/10.1016/j.anbehav.2010.08.007}{10.1016/j.anbehav.2010.08.007}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011a}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Auersperg, A.M.I., Huber, L., and Gajdon, G.K.
-(2011).
-Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis}).
-Biology Letters \emph{7}, 825--828.
-\href{https://doi.org/10.1098/rsbl.2011.0388}{10.1098/rsbl.2011.0388}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011b}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Auersperg, A.M.I., Bayern, A.M.P.
-von, Gajdon, G.K., Huber, L., and Kacelnik, A.
-(2011).
-Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm.
-PLOS ONE \emph{6}, 1--8.
-\href{https://doi.org/10.1371/journal.pone.0020231}{10.1371/journal.pone.0020231}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2012}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Auersperg, A.M.I., Szabo, B., von Bayern, A.M.P., and Kacelnik, A.
-(2012).
-Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo.
-Current Biology \emph{22}, R903--R904.
-\href{https://doi.org/10.1016/j.cub.2012.09.002}{10.1016/j.cub.2012.09.002}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bastos2021}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Bastos, A.P., Horváth, K., Webb, J.L., Wood, P.M., and Taylor, A.H.
-(2021).
-Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
-Scientific Reports \emph{11}, 18035.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BentleyCondit2010}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Bentley-Condit, V., and Smith, E.O.
-(2010).
-Animal tool use: Current definitions and an updated comprehensive catalog.
-Behaviour \emph{147}, 185--32A.
-\href{https://doi.org/10.1163/000579509X12512865686555}{10.1163/000579509X12512865686555}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Borsari2005}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Borsari, A., and Ottoni, E.B.
-(2005).
-Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus}).
-Animal Cognition \emph{8}, 48--52.
-\href{https://doi.org/10.1007/s10071-004-0221-3}{10.1007/s10071-004-0221-3}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodman2018}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Goodman, M., Hayward, T., and Hunt, G.R.
-(2018).
-Habitual tool use innovated by free-living {N}ew {Z}ealand kea.
-Scientific Reports \emph{8}, 13935.
-\href{https://doi.org/10.1038/s41598-018-32363-9}{10.1038/s41598-018-32363-9}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Heinsohn2017}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Heinsohn, R., Zdenek, C.N., Cunningham, R.B., Endler, J.A., and Langmore, N.E.
-(2017).
-Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music.
-Science Advances \emph{3}, e1602399.
-\href{https://doi.org/10.1126/sciadv.1602399}{10.1126/sciadv.1602399}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Janzen1976}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Janzen, M.J., Janzen, D.H., and Pond, C.M. (1976). Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). Biotropica \emph{8}, 70.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lambert2015}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{Lambert, M.L., Seed, A.M., and Slocombe, K.E.
-(2015).
-A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa}).
-Biology Letters \emph{11}, 20150861.
-\href{https://doi.org/10.1098/rsbl.2015.0861}{10.1098/rsbl.2015.0861}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-OHara2021}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{O'Hara, M., Mioduszewska, B., Mundry, R., Yohanna, Haryoko, T., Rachmatika, R., Prawiradilaga, D.M., Huber, L., and Auersperg, A.M.I.
-(2021).
-Wild {G}offin's cockatoos flexibly manufacture and use tool sets.
-Current Biology \emph{31}, 4512--4520.e6.
-\href{https://doi.org/10.1016/j.cub.2021.08.009}{10.1016/j.cub.2021.08.009}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Anderson, P.
-(2003).
-A bird in the house: An anthropological perspective on companion parrots.
-Society \& Animals \emph{11}, 393--418.
-\href{https://doi.org/10.1163/156853003322796109}{10.1163/156853003322796109}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{Carrete, M., and Tella, J.
-(2008).
-Wild-bird trade and exotic invasions: A new link of conservation concern?
-Frontiers in Ecology and the Environment \emph{6}, 207--211.
-\href{https://doi.org/10.1890/070075}{10.1890/070075}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Drews, C.
-(2001).
-Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers.
-Society \& Animals \emph{9}, 107--126.
-\href{https://doi.org/10.1163/156853001753639233}{10.1163/156853001753639233}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Kelly, D., McCarthy, E., Menzel, K., and Engebretson, M.
-(2014).
-\href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Li, L., and Jiang, Z.
-(2014).
-International trade of {CITES} listed bird species in {C}hina.
-PLOS ONE \emph{9}, 1--8.
-\href{https://doi.org/10.1371/journal.pone.0085012}{10.1371/journal.pone.0085012}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Su, S., Cassey, P., Vall-llosera, M., and Blackburn, T.M.
-(2015).
-Going cheap: Determinants of bird price in the {T}aiwanese pet market.
-PLOS ONE \emph{10}, 1--17.
-\href{https://doi.org/10.1371/journal.pone.0127482}{10.1371/journal.pone.0127482}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Young, A.M., Hobson, E.A., Lackey, L.B., and Wright, T.F.
-(2012).
-Survival on the ark: Life-history trends in captive parrots.
-Animal Conservation \emph{15}, 28--43.
-\href{https://doi.org/10.1111/j.1469-1795.2011.00477.x}{10.1111/j.1469-1795.2011.00477.x}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Flammer, K., Whitt-Smith, D., and Papich, M.
-(2001).
-Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection.
-Journal of Avian Medicine and Surgery \emph{15}, 276--282.
-\href{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}{10.1647/1082-6742(2001)015{[}0276:PCODIS{]}2.0.CO;2}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Iwaniuk, A.N., Dean, K.M., and Nelson, J.E.
-(2005).
-Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
-Brain, Behavior and Evolution \emph{65}, 40--59.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P.R., and Ihunwo, A.O.
-(2018).
-Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh}).
-Frontiers in Neuroanatomy \emph{12}, 7.
-\href{https://doi.org/10.3389/fnana.2018.00007}{10.3389/fnana.2018.00007}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Olkowicz, S., Kocourek, M., Lučan, R.K., Porteš, M., Fitch, W.T., Herculano-Houzel, S., and Němec, P.
-(2016).
-Birds have primate-like numbers of neurons in the forebrain.
-Proceedings of the National Academy of Sciences \emph{113}, 7255--7260.
-\href{https://doi.org/10.1073/pnas.1517131113}{10.1073/pnas.1517131113}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Schuck-Paim, C., Alonso, W.J., and Ottoni, E.B.
-(2008).
-Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots.
-Brain, Behavior and Evolution \emph{71}, 200--215.
-\href{https://doi.org/10.1159/000119710}{10.1159/000119710}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Silva, T., Guzmán, A., Urantówka, A.D., and Mackiewicz, P.
-(2017).
-A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny.
-PeerJ \emph{5}, e3475.
-\href{https://doi.org/10.7717/peerj.3475}{10.7717/peerj.3475}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Wilman, H., Belmaker, J., Simpson, J., Rosa, C.
-de la, Rivadeneira, M.M., and Jetz, W.
-(2016).
-EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals.
-\href{https://doi.org/10.6084/m9.figshare.c.3306933.v1}{10.6084/m9.figshare.c.3306933.v1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Jetz, W., Thomas, G.H., Joy, J.B., Hartmann, K., and Mooers, A.O. (2012). The global diversity of birds in space and time. Nature \emph{491}, 444--448.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Seed, A., and Byrne, R. (2010). Animal tool-use. Current Biology \emph{20}, R1032--R1039. \href{https://doi.org/10.1016/j.cub.2010.09.042}{10.1016/j.cub.2010.09.042}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Bercovitz, A.B. (1987). Avian sex identification techniques. In Companion bird medicine, E. W. Burr, ed. (Iowa State University Press).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Hoyo, J.D., and Bierregaard, R. (2011). Handbook of the birds of the world (Lynx Edicions).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Amico, M., and Van Keilegom, I.
-(2018).
-Cure models in survival analysis.
-Annual Review of Statistics and Its Application \emph{5}, 311--342.
-\href{https://doi.org/10.1146/annurev-statistics-031017-100101}{10.1146/annurev-statistics-031017-100101}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Schmidt, P., and Witte, A.D.
-(1989).
-Predicting criminal recidivism using {``split population''} survival time models.
-Journal of Econometrics \emph{40}, 141--159.
-\href{https://doi.org/10.1016/0304-4076(89)90034-1}{10.1016/0304-4076(89)90034-1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Wallace, A.R. (1869). The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature (MacMillan; Co.).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodall1971}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Goodall, J.
-(1971).
-Tool-using in primates and other vertebrates.
-In Advances in the study of behavior., D.
-S.
-Lehrman, R.
-A.
-Hinde, and E.
-Shaw, eds.
-(Academic Press), pp.
-195--249.
-\href{https://doi.org/10.1016/S0065-3454(08)60157-6}{10.1016/S0065-3454(08)60157-6}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Reader, S.M., and Laland, K.N.
-(2002).
-Social intelligence, innovation, and enhanced brain size in primates.
-Proceedings of the National Academy of Sciences \emph{99}, 4436--4441.
-\href{https://doi.org/10.1073/pnas.062041299}{10.1073/pnas.062041299}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{Sol, D., Olkowicz, S., Sayol, F., Kocourek, M., Zhang, Y., Marhounová, L., Osadnik, C., Corssmit, E., Garcia-Porta, J., Martin, T.E., et al.
-(2022).
-Neuron numbers link innovativeness with both absolute and relative brain size in birds.
-Nature Ecology \& Evolution \emph{6}, 1381--1389.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Cabrera-Álvarez, M.J., and Clayton, N.S.
-(2020).
-Neural processes underlying tool use in humans, macaques, and corvids.
-Frontiers in Psychology \emph{11}, 560669.
-\href{https://doi.org/10.3389/fpsyg.2020.560669}{10.3389/fpsyg.2020.560669}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
-(2021).
-Linking cognition to ecology in wild sympatric mouse lemur species.
-Proceedings of the Royal Society B: Biological Sciences \emph{288}, 20211728.
-\href{https://doi.org/10.1098/rspb.2021.1728}{10.1098/rspb.2021.1728}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Fragaszy, D.M., and Mangalam, M.
-(2018).
-Tooling.
-In Advances in the study of behavior., M.
-Naguib, L.
-Barrett, S.
-D.
-Healy, J.
-Podos, L.
-W.
-Simmons, and M.
-Zuk, eds.
-(Academic Press), pp.
-177--241.
-\href{https://doi.org/10.1016/bs.asb.2018.01.001}{10.1016/bs.asb.2018.01.001}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Sándor, K., and Miklósi, Á.
-(2020).
-How to report anecdotal observations?
-A new approach based on a lesson from "puffin tool use".
-Frontiers in Psychology \emph{11}, 555487.
-\href{https://doi.org/10.3389/fpsyg.2020.555487}{10.3389/fpsyg.2020.555487}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Debastiani, V.J., Bastazini, V.A.G., and Pillar, V.D.
-(2021).
-Using phylogenetic information to impute missing functional trait values in ecological databases.
-Ecological Informatics \emph{63}, 101315.
-\href{https://doi.org/10.1016/j.ecoinf.2021.101315}{10.1016/j.ecoinf.2021.101315}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
-\CSLLeftMargin{66. }%
-\CSLRightInline{Hunt, G.R., Gray, R.D., and Taylor, A.H.
-(2013).
-Why is tool use rare in animals?
-In Tool use in animals: Cognition and ecology, C.
-M.
-Sanz, J.
-Call, and C.
-Boesch, eds.
-(Cambridge University Press), pp.
-89--118.
-\href{https://doi.org/10.1017/CBO9780511894800.007}{10.1017/CBO9780511894800.007}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
-\CSLLeftMargin{67. }%
-\CSLRightInline{Benichov, J.I., Globerson, E., and Tchernichovski, O.
-(2016).
-Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans.
-Frontiers in Human Neuroscience \emph{10}.
-\href{https://doi.org/10.3389/fnhum.2016.00255}{10.3389/fnhum.2016.00255}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
-\CSLLeftMargin{68. }%
-\CSLRightInline{Patel, A.D., Iversen, J.R., Bregman, M.R., and Schulz, I.
-(2009).
-Experimental evidence for synchronization to a musical beat in a nonhuman animal.
-Current Biology \emph{19}, 827--830.
-\href{https://doi.org/10.1016/j.cub.2009.03.038}{10.1016/j.cub.2009.03.038}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{ten Cate, C., Spierings, M., Hubert, J., and Honing, H.
-(2016).
-Can birds perceive rhythmic patterns?
-A review and experiments on a songbird and a parrot species.
-Frontiers in Psychology \emph{7}.
-\href{https://doi.org/10.3389/fpsyg.2016.00730}{10.3389/fpsyg.2016.00730}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
-\CSLLeftMargin{70. }%
-\CSLRightInline{Wilson, M., and Cook, P.F.
-(2016).
-Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed.
-Psychonomic Bulletin \& Review \emph{23}, 1647--1659.
-\href{https://doi.org/10.3758/s13423-016-1013-x}{10.3758/s13423-016-1013-x}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{Eckert, J., Winkler, S.L., and Cartmill, E.A.
-(2020).
-Just kidding: The evolutionary roots of playful teasing.
-Biology Letters \emph{16}, 20200370.
-\href{https://doi.org/10.1098/rsbl.2020.0370}{10.1098/rsbl.2020.0370}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
-\CSLLeftMargin{72. }%
-\CSLRightInline{Bro-Jørgensen, J., and Pangle, W.M.
-(2010).
-Male topi antelopes alarm snort deceptively to retain females for mating.
-The American Naturalist \emph{176}, E33--E39.
-\href{https://doi.org/10.1086/653078}{10.1086/653078}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
-\CSLLeftMargin{73. }%
-\CSLRightInline{Byrne, R.W., and Whiten, A.
-(1988).
-Toward the next generation in data quality: A new survey of primate tactical deception.
-Behavioral and Brain Sciences \emph{11}, 267--273.
-\href{https://doi.org/10.1017/S0140525X00049955}{10.1017/S0140525X00049955}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
-\CSLLeftMargin{74. }%
-\CSLRightInline{Byrne, R.W., and Whiten, A.
-(1991).
-Computation and mindreading in primate tactical deception.
-In Natural theories of mind: Evolution, development and simulation of everyday mindreading, A.
-Whiten, ed.
-(Basil Blackwell), pp.
-127--141.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
-\CSLLeftMargin{75. }%
-\CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership} (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
-\CSLLeftMargin{76. }%
-\CSLRightInline{Jerison, H.J. (1973). Evolution of the brain and intelligence (Academic Press).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
-\CSLLeftMargin{77. }%
-\CSLRightInline{Paradis, E., and Schliep, K.
-(2019).
-{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}.
-Bioinformatics \emph{35}, 526--528.
-\href{https://doi.org/10.1093/bioinformatics/bty633}{10.1093/bioinformatics/bty633}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
-\CSLLeftMargin{78. }%
-\CSLRightInline{McElreath, R.
-(2020).
-\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition} 2nd ed.
-(CRC Press).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
-\CSLLeftMargin{79. }%
-\CSLRightInline{Stan Development Team (2020). \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
-\CSLLeftMargin{80. }%
-\CSLRightInline{Revell, L.J.
-(2012).
-{phytools}: An {R} package for phylogenetic comparative biology (and other things).
-Methods in Ecology and Evolution \emph{3}, 217--223.
-\href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{10.1111/j.2041-210X.2011.00169.x}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
-\CSLLeftMargin{81. }%
-\CSLRightInline{R Core Team (2022). \href{https://www.R-project.org/}{R: A language and environment for statistical computing} (R Foundation for Statistical Computing).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
-\CSLLeftMargin{82. }%
-\CSLRightInline{Yu, G., Smith, D., Zhu, H., Guan, Y., and Lam, T.T.-Y.
-(2017).
-{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data.
-Methods in Ecology and Evolution \emph{8}, 28--36.
-\href{https://doi.org/10.1111/2041-210X.12628}{10.1111/2041-210X.12628}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-\CSLLeftMargin{83. }%
-\CSLRightInline{Wickham, H. (2016). \href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis} (Springer-Verlag New York).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
-\CSLLeftMargin{84. }%
-\CSLRightInline{Wilke, C.O. (2020). \href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
-\CSLLeftMargin{85. }%
-\CSLRightInline{Landau, W.M.
-(2021).
-The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing.
-Journal of Open Source Software \emph{6}, 2959.
-\href{https://doi.org/10.21105/joss.02959}{10.21105/joss.02959}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
-\CSLLeftMargin{86. }%
-\CSLRightInline{Aust, F., and Barth, M. (2022). \href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}.}
-
-\end{CSLReferences}
-
-\endgroup
-
-\newpage
 \vspace*{60mm}
@@
 
-\hypertarget{supplementary-information}{%
-\section{\texorpdfstring{\textbf{Supplementary Information}}{Supplementary Information}}\label{supplementary-information}}
+\hypertarget{supplemental-information}{%
+\section{\texorpdfstring{\textbf{Supplemental Information}}{Supplemental Information}}\label{supplemental-information}}
 
@@
 
-\hypertarget{supplementary-figures}{%
-\subsection{Supplementary Figures}\label{supplementary-figures}}
+\hypertarget{supplemental-figures}{%
+\subsection{Supplemental Figures}\label{supplemental-figures}}
 

### 2024-07-12 methods.Rmd
revise and resubmit

--- 2024-02-04 manuscript.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  man, donotrepeattitle,floatsintext]{apa6}
-\usepackage{amsmath,amssymb}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-\usepackage[bidi=basic]{babel}
-\else
-\usepackage[bidi=default]{babel}
-\fi
-\babelprovide[main,import]{english}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
+# STAR Methods
 
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+## Resource Availability
 
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+### Lead contact
 
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+Further information about resources should be directed to Scott Claessens 
+(scott.claessens@gmail.com).
 
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+### Materials availability
 
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+This study did not generate new unique materials.
 
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
+### Data and code availability
 
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
+All data have been deposited on GitHub and are publicly available as of the date
+of publication. DOIs are listed in the key resources table.
 
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
-\keywords{tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling}
-\usepackage{lineno}
+All original code has been deposited on GitHub and is publicly available as of 
+the date of publication. DOIs are listed in the key resources table.
 
-\linenumbers
-\usepackage{csquotes}
-\usepackage{array}
-\usepackage{caption}
-\usepackage{graphicx}
-\usepackage{siunitx}
-\usepackage[normalem]{ulem}
-\usepackage{colortbl}
-\usepackage{multirow}
-\usepackage{hhline}
-\usepackage{calc}
-\usepackage{tabularx}
-\usepackage{threeparttable}
-\usepackage{wrapfig}
-\usepackage{adjustbox}
-\usepackage{hyperref}
-\usepackage{setspace}
-\raggedbottom
-\AtBeginEnvironment{tabular}{\singlespacing}
-\AtBeginEnvironment{lltable}{\singlespacing}
-\AtBeginEnvironment{tablenotes}{\doublespacing}
-\captionsetup[table]{font={stretch=1,small}}
-\captionsetup[figure]{font={stretch=1,small}}
-\nolinenumbers
-\note{\raggedright † These authors contributed equally to this work \par ‡ These authors contributed equally to this work \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand.
-\text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}} \par This working paper has not yet been peer-reviewed.}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare},
-  pdfauthor={Amalia P. M. Bastos†,1,2, Scott Claessens*†,2, Ximena J. Nelson3, David Welch4, Quentin D. Atkinson‡,2, \& Alex H. Taylor‡,2,3,5,6},
-  pdflang={en-EN},
-  pdfkeywords={tool use; technical intelligence; parrots; crowdsourcing; phylogenetic modelling},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
+## Method Details
 
-\title{Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare}
-\author{Amalia P.
-M.
-Bastos\textsuperscript{†,1,2}, Scott Claessens\textsuperscript{*†,2}, Ximena J.
-Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, Quentin D.
-Atkinson\textsuperscript{‡,2}, \& Alex H.
-Taylor\textsuperscript{‡,2,3,5,6}}
-\date{}
+### Video searches and coding
 
-\shorttitle{Parrot tool use}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} \footnotesize Department of Psychological \& Brain Sciences, Johns Hopkins University, Baltimore, MD, United States\\\textsuperscript{2} \footnotesize School of Psychology, University of Auckland, Auckland, New Zealand\\\textsuperscript{3} \footnotesize School of Biological Sciences, University of Canterbury, Christchurch, New Zealand\\\textsuperscript{4} \footnotesize School of Computer Science, University of Auckland, Auckland, New Zealand\\\textsuperscript{5} \footnotesize ICREA, Pg.
-Lluís Companys 23, Barcelona, Spain\\\textsuperscript{6} \footnotesize Institute of Neuroscience, Universitat Autònoma de Barcelona, Barcelona, Spain}
-
-\abstract{%
-Putatively rare behaviours, such as tool use, are challenging to study because absence of evidence can arise either from a species' inability to produce the behaviour or from insufficient research effort.
-Here, we tackle this challenge by combining crowdsourcing and phylogenetic modelling to estimate actual rates of tool use in parrots.
-Crowdsourcing on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
-Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11\% and 17\% of extant parrot species may be tool users.
-These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait.
-Overall, our findings challenge the assumption that current sampling effort captures the full distribution of putatively rare animal behaviours.
-Combining our sampling and analysis methods offers a fruitful approach for investigating the distribution, drivers, and origins of other rare behaviours.
-}
-
-\begin{document}
-\maketitle
-
-\hypertarget{significance-statement}{%
-\section{Significance Statement}\label{significance-statement}}
-
-Tool use has been identified in a number of non-human animal species, including
-11 species of parrot. However, it is possible that the number of tool-using
-parrot species has been underestimated due to insufficient research effort.
-Here, we combine two approaches -- crowdsourcing and phylogenetic modelling -- to
-estimate actual rates of tool use in parrots. Crowdsourcing on a social media
-platform identified tool use in 17 novel parrot species, more than doubling the
-confirmed number of tool-using parrot species from 11 to 28. Moreover,
-phylogenetic modelling ranked additional species that are likely to be
-unobserved tool users. Our findings have implications for inferences about the
-evolutionary origins of technical intelligence in parrots.
-
-\newpage
-\linenumbers
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Our understanding of the evolution of animal behaviour is built on the
-assumption that we have access to sufficient data (1--3). However, this is not always the case. Data on behaviours that are
-rare, fleeting, or otherwise difficult to observe are likely to be patchy and
-incomplete (4, 5). Among species for which such behaviours
-have not been observed, it can be difficult to differentiate between cases in
-which the species is truly incapable of producing the behaviour and cases in
-which the species is capable of producing the behaviour but the behaviour has
-not yet been observed. Such a distinction can be critical for drawing
-conclusions about the rarity and evolution of the behaviour in question.
-
-Comparative work on the evolution of tool use is a paradigmatic example of this
-issue. The initial discoveries of tool use in chimpanzees (6),
-birds (7), dolphins (8), and octopuses (9) occurred
-decades after significant advances on other more easily measurable aspects of
-their biology. Since then, scholars have proposed a clear operational
-definition of tool use applicable to all species --- the manipulation of an
-unattached object as an extension of the animal's body to achieve a
-goal (10) --- and have used the distribution of species meeting this
-definition to make various claims about the evolutionary drivers of tool use
-behaviours. For example, based on the observation that bird species with
-reported tool use tended to have larger brains, researchers have identified
-higher relative brain size as a likely precondition for tool using
-capabilities (11--13). These researchers
-argue that larger brains are better able to integrate visual and somatosensory
-information when innovating novel behaviours, such as tool use, in changing
-environments (14, 15). Similarly, researchers have used existing
-reports of tool use in birds to debate the roles of generalist versus
-specialist feeding strategies in driving the evolution of tool use, with some
-arguing that feeding generalists require technical innovations to expand their
-dietary niche (14, 16, 17) and others arguing that
-feeding specialists require technical innovations for extractive foraging of
-specific foods (18, 19).
-
-However, before we can make claims of this kind, we need to know whether current
-research effort in the literature is sufficient for robust conclusions to be
-drawn about the evolution of tool use. In fact, evidence suggests that research
-effort is often systematically biased towards particular taxonomic groups, parts
-of the world that are easy to access, and species with life history traits that
-make them easier to study, such as larger distribution ranges and population
-sizes (20). This is a crucial limitation because insufficient
-observation may lead researchers to miss true instances of tool behaviours and
-thus draw premature conclusions about the evolutionary drivers and origins of
-tool use. While researchers have attempted to deal with this problem by
-controlling for the number of scientific papers published on different species,
-previous work has not yet attempted to quantify and explicitly model the
-relationship between actual tool-using behaviour and what is reported in the
-scientific literature. If more tool-using species exist than previously thought,
-this could have important implications for theories of the evolutionary drivers
-and origins of tool use and for our understanding of how rare this behaviour
-actually is.
-
-One potentially powerful method for quantifying actual rates of rare animal
-behaviours is crowdsourcing (21). In a crowdsourcing study, researchers
-collect reports from the general public and/or collate and analyse videos posted
-on social media platforms. This citizen science approach has been widely used in
-ecology to monitor the distributional patterns of species (22), but
-has also recently been used to uncover a variety of rare animal behaviours,
-including interspecies play in dogs (21), novel problem-solving
-behaviours in horses (23), and socially-learned foraging innovations
-in cockatoos (24, 25). By casting the net wider than the
-scientific literature, the crowdsourcing method can provide an indication of the
-tool-using species that the literature might be missing.
-
-Even after using this crowdsourcing approach, some tool-users could \emph{still}
-remain unobserved. One principled framework for identifying these unobserved species
-is to specify a causal model of the process that generates the observed data. We
-propose one such causal model in Figure \ref{fig:plotDAG}. In this model, we
-assume that the presence of tool use in the scientific literature (or in
-crowdsourced reports) is caused by both unobserved tool use capabilities and the
-number of published studies (or the number of crowdsourced reports) for any
-given species. Tool users are more likely to be observed if they are well
-studied, but understudied tool users may go undetected. Furthermore, based on
-existing theories of the evolution of tool use (11--19), we propose that the
-unobserved tool use capabilities are additionally caused by relative brain size,
-feeding strategy, and shared phylogenetic ancestry. Expressing this causal model
-as a statistical model can suggest further species which are likely to be
-unobserved tool-users and, simultaneously, test existing theories of the
-evolutionary drivers of tool use without incorrectly assuming that absence of
-evidence is evidence of absence.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotDAG-1.pdf}
-\caption{\label{fig:plotDAG}\emph{Causal model of observed tool use.} Directed acyclic graph
-of the causal relationships between observed tool use and other variables.
-Available scientific data on tool use is caused both by unobserved tool use
-presence and scientific research effort (i.e., number of publications).
-Available crowdsourced data on tool use is caused both by unobserved tool use
-presence and crowdsourcing effort (i.e., number of crowdsourced reports).
-According to theory, unobserved tool use presence should be caused by relative
-brain size (encephalisation quotient) and feeding strategy (generalist vs.~
-specialist). These variables all share unobserved confounds generated by shared
-phylogenetic history. Grey circles indicate unobserved variables.}
-\end{figure}
-
-Here, we apply these crowdsourcing and phylogenetic modelling approaches to tool
-use in the parrot order. We focus on tool use in parrots for a number of
-reasons. First, the scientific literature suggests that only a small proportion
-of extant parrot species (11 out of 398; 3\%) use tools
-(11, 26--38). Parrot tool use
-thus provides an ideal test case for examining how robust sampling is in the
-scientific literature. Second, parrots are highly popular as pets. Over 70\% of
-all extant parrot species are bred in the aviculture industry and kept as pets
-worldwide (39--45), enabling us to leverage the power of crowdsourcing on a social
-media platform to search for evidence of tool use (21). Third, detailed
-data on relative brain sizes (46--51), feeding strategies (52), and
-shared ancestry (53) exist for parrots, allowing us to fit the
-statistical model implied by Figure \ref{fig:plotDAG} to the entire parrot
-order.
-
-We first present the results from our crowdsourcing survey, in which we collated
-videos of tool use in parrots from an online video platform. This survey reveals
-a number of previously unidentified tool-using parrot species, which we map onto
-the phylogeny of the parrot order. We then describe our statistical model in
-more detail, and use it to (\emph{i}) rank further parrot species that are likely
-unobserved tool users and (\emph{ii}) re-examine key hypotheses regarding the
-evolutionary drivers and origins of tool use in parrots.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{crowdsourcing-reveals-tool-use-in-additional-parrot-species}{%
-\subsection{Crowdsourcing reveals tool use in additional parrot species}\label{crowdsourcing-reveals-tool-use-in-additional-parrot-species}}
-
-We surveyed the social media platform YouTube for video evidence of tool use in
-parrots (see Methods for detailed search criteria). In our search, we used the
-standard criteria for identifying tool use in the literature, defining ``true''
-tool use behaviour as the manipulation of an unattached object as an extension
-of the animal's body to achieve a goal (10), while ``borderline'' tool
-use involved the use of an object that was still attached to a substrate
-(54).
-
-In total, we found 116 videos of
-104 individuals from
-25
-parrot species performing behaviours that met the definition of either true tool
-use (100 videos of
-89
-individuals from
-22
-species) or borderline tool use (16 videos of
-16
-individuals from
-7
-species). All videos featured pet parrots in captive settings. In
-68 of these
-videos, owners did not appear to interact with the subjects. In
-43 videos,
-there was potential human interaction, either from the owners being in close physical
-contact with the bird (e.g., bird perching on hand), talking to the bird, or
-handing it the tool (which occurred in only two videos). We could not establish
-the degree of human interaction in the remaining
-5
-videos, as sound had been removed or was substituted by music. None of the
-videos featured owners directly rewarding tool use behaviours with food. All
-borderline tool use cases were excluded from further analyses.
-
-Of the 22
-parrot species performing true tool use,
-13
-were represented in our video survey by two or more individuals over multiple
-independent observations. True tool use always involved the subject using an
-object for self-scratching (95
-videos involved scratching the head and/or neck). The most common tool (53
-videos) was a moulted feather. Human-made objects (e.g., pens, spoons, pieces of
-wood, cardboard) were also common.
-
-According to YouTube video descriptions and owner comments,
-45
-of the individuals performing true tool use were males and
-18
-were females. No sex information was provided for the remaining
-26
-individuals. As owners provided no information on whether sex had been
-established through genetic testing, and sexual dimorphism in parrots is
-rare (55, 56), we could not typically ascertain if descriptions
-were accurate. It is unclear if the disproportionately large number of males in
-the sample is a consequence of owners more readily assuming their parrots are
-male when they have not been genetically tested, owners being more likely to own
-or film male parrots, or male parrots exhibiting more true tool use behaviours
-than female parrots.
-
-Figure \ref{fig:plotPhylo1} maps the findings from the video survey onto a
-maximum clade credibility phylogeny for the parrot order, plotted alongside
-species previously identified in the scientific literature. Before the video
-survey, 11 parrot species (3\%) had been identified as tool users in the
-scientific literature. Across our video survey, we observed true tool use in
-22
-species, 5 of which overlapped with the scientific literature and
-17
-of which were novel species. All of the species identified in the video survey
-were cockatoos (\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), or neotropical
-parrots (\emph{Arinae}). The most common species in our survey, accounting for
-41 videos from
-37
-individuals, was the green-cheeked conure (\emph{Pyrrhura molinae}). In accordance
-with the scientific literature, the video survey found no evidence of tool use
-in any species of Psittaculidae, despite this family containing some of the most
-commonly kept pet species, including lovebirds, lorikeets, and Asian parakeet
-species. Combining both the video survey and the scientific literature, we can
-thus identify 28 tool-using parrot species overall (7\%), compared to the 11
-previously reported.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotPhylo1-1.pdf}
-\caption{\label{fig:plotPhylo1}\emph{Results of crowdsourcing video survey and phylogenetic
-survival cure modelling mapped onto a maximum clade credibility phylogeny of the
-parrot order.} Orange points in the inner ring indicate species observed in the
-video survey, with point size scaled by the number of videos for each species
-(note that three species observed only in the video survey are not present in
-the phylogeny due to a lack of genomic data: \emph{Psittacara erythrogenys},
-\emph{Psittacus timneh}, and \emph{Aratinga nenday}). Blue points in the outer ring
-indicate species observed in the scientific literature, with point size scaled
-by the number of papers published on each species. Yellow species names indicate
-the top ten most likely tool-using species from our phylogenetic survival cure
-model which were not observed in the scientific literature or the video survey.
-Total \emph{n} = 174 species.}
-\end{figure}
-
-The identification of new tool-using species in our video survey increases the
-extent to which phylogeny can explain the distribution of tool use in the parrot
-order. We estimated phylogenetic signal (Pagel's \(\lambda\)) of tool use using
-both the pre-video-survey and post-video-survey data. Pagel's \(\lambda\) varies
-between 0 and 1, where 0 implies that the distribution of a trait across species
-is unexplained by phylogenetic relatedness and 1 implies that the distribution
-of a trait across species is fully explained by phylogeny. Using the evidence of
-tool use from the scientific literature alone (pre-video-survey data; 11
-tool-using species), we estimated an average posterior Pagel's \(\lambda\) of
-0.60 (95\% credible interval {[}0.00
-0.90{]}; total \emph{n} =
-174 species). This estimate was moderate-to-strong, but highly
-uncertain. In comparison, combining the evidence from both the literature and
-the video survey (post-video-survey data; 28 tool-using species) resulted in a
-stronger and more certain estimate of phylogenetic signal. With these data, we
-estimated Pagel's \(\lambda\) = 0.65 (95\% CI
-{[}0.50
-0.77{]}; total \emph{n} =
-174 species). Thus, the results of our video survey increase
-the extent to which the distribution of tool use across parrot species can be
-explained by shared phylogenetic ancestry. This suggests that we can potentially
-use phylogenetic information, along with other variables, to identify further
-tool-using parrot species that may remain undetected.
-
-\hypertarget{phylogenetic-survival-cure-modelling-identifies-further-candidate-tool-users}{%
-\subsection{Phylogenetic survival cure modelling identifies further candidate tool users}\label{phylogenetic-survival-cure-modelling-identifies-further-candidate-tool-users}}
-
-In addition to the 28 tool-using species identified in the literature and our
-video survey, we fitted a Bayesian phylogenetic survival cure model to rank
-further species that are likely to be undetected tool-users (i.e., tool-using
-species with no tool use reported in the literature or in crowdsourced videos).
-
-Survival cure models (57), also known as split population
-models (58), are used to analyse the time to some event of interest
-with the added assumption that a certain proportion of the population will never
-experience the event, no matter how long they are measured for. These models
-have been used to analyse a variety of right-censored outcomes, from cancer
-relapse (57) to criminal recidivism (58). The data are
-right-censored because some individuals will have experienced the event when
-they are measured (e.g., disease onset, return to prison) while others will have
-not experienced the event. For those who have not experienced the event, this
-may be because (\emph{i}) the event has not happened to them yet or (\emph{ii}) the event
-will \emph{never} happen to them. Survival cure models treat these two processes
-separately.
-
-Our tool use problem has the same features. We are modelling a time-to-event;
-specifically, the amount of ``time'' (i.e., observation opportunities measured as
-the number of published papers or crowdsourced videos) until tool use is
-identified. This is right-censored data because many species will not have had
-tool use identified when we measure them. Moreover, we can assume that a certain
-proportion of the population will never experience the event -- that is, they
-are a non-tool-user and so we will never identify tool use no matter how long we
-measure them for.
-
-In our model, we infer the tool-using status of each species by allowing each
-species to have their own probability of being a non-tool-user. Following our
-causal model (Figure \ref{fig:plotDAG}), we predict these probabilities based
-on feeding strategy, encephalisation quotient, and phylogenetic history (see
-Methods for full model). The model additionally takes research effort into
-account by allowing that, among species for which tool use is unobserved, all
-else being equal those with fewer published papers and fewer video search hits
-have a higher probability of being undetected tool users (Supplementary Figure
-\ref{fig:plotSurvCure3}).
-
-We found that this phylogenetic survival cure model was able to adequately
-distinguish between species with and without evidence for tool use, with an
-area-under-the-curve classification statistic of
-0.95 (Supplementary Figure
-\ref{fig:plotSurvCure9}). To further estimate the accuracy of the model's
-predictions, we also used a leave-one-species-out approach with known tool
-users. For each of the 25 tool-using species that were represented on the
-phylogeny and for which we had brain size and genomic data (we lacked data for
-three tool-using species), we fitted the model to a modified dataset which set
-tool use to be absent for the target species in both the scientific literature
-and the video survey. Across 25 cross-validation models,
-18 models (72\%)
-continued to predict the target species as having a median posterior probability
-of tool use that was within the range of all other tool users. This
-classification rate was greater than the baseline classification rate of
-26\%
-for species without evidence of tool use in the full model
-(38
-of 149 species without
-evidence of tool use had a median posterior probability of tool use that was
-within the range of the tool-using species). Together, the area-under-the-curve
-statistic and the leave-one-species-out approach suggest that the model is able
-to adequately classify known tool users, with some error.
-
-Figure \ref{fig:plotSurvCure1} visualises the ranked posterior probabilities of
-tool use from the phylogenetic survival cure model for all parrot species. As
-expected, the known tool users are ranked towards the top of this list. However,
-several ``tool use absent'' species also rank highly on the list, despite not
-being identified as tool users in the scientific literature or in our video
-survey. In fact, according to the model, the most likely tool user is a species
-for which tool use is unobserved in our data: the blue-eyed cockatoo (\emph{Cacatua
-opthalmica}). This species is endemic to Papua New Guinea and is relatively
-understudied, with only 6 published papers
-and 596 video search hits, which is fewer than the
-model expects are necessary to discover tool use when it is present (Figure
-\ref{fig:plotSurvCure2}). This species is also found in the \emph{Cacatua} genus, a
-clade containing several known tool users. This prediction makes sense given the
-high phylogenetic signal for tool use reported by the model (Supplementary
-Figures \ref{fig:plotSurvCure5} and \ref{fig:plotSurvCure6}). Beyond the
-blue-eyed cockatoo, other highly ranked species without observed evidence of
-tool use are the Meyer's parrot (\emph{Poicephalus meyeri}), the golden parakeet
-(\emph{Guaruba guarouba}), the long-billed corella (\emph{Cacatua tenuirostris}), the
-Solomons cockatoo (\emph{Cacatua ducorpsii}), the red-fronted parrot (\emph{Poicephalus
-gulielmi}), the Cape parrot (\emph{Poicephalus robustus}), the yellow-eared parrot
-(\emph{Ognorhynchus icterotis}), the red-vented cockatoo (\emph{Cacatua haematuropygia}),
-and the gang-gang cockatoo (\emph{Callocephalon fimbriatum}). Figure
-\ref{fig:plotPhylo1} plots these species on the parrot phylogeny, using the top
-ten highest ranked species without observed evidence of tool use as an arbitrary
-cutoff for visualisation purposes.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure1-1.pdf}
-\caption{\label{fig:plotSurvCure1}\emph{Posterior predicted probabilities of tool use for
-each species from our phylogenetic survival cure model.} Points are posterior
-medians and lines are 50\% and 95\% credible intervals. Total \emph{n} =
-174 species.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure2-1.pdf}
-\caption{\label{fig:plotSurvCure2}\emph{Expected number of published papers and videos until
-tool use discovery, according to the survival component of the phylogenetic
-survival cure model.} Densities are full posterior distributions, points are
-posterior medians, and lines are 50\% and 95\% credible intervals.}
-\end{figure}
-
-The posterior probabilities shown in Figure \ref{fig:plotSurvCure1} are
-estimated with uncertainty, so it is difficult to ``identify'' any particular
-species as an undetected tool user. Nevertheless, taking the sum of all the
-posterior probabilities for the
-149 species without
-observed evidence of tool use, we can estimate that around
-26 of those species are likely to be
-undetected tool users (median sum of probabilities =
-25.68, 95\% CI
-{[}15.15
-41.33{]}). When combined with the
-species known to use tools, this implies that between 11\% and 17\% of extant
-parrot species may be tool users.
-
-\hypertarget{implications-for-the-evolutionary-drivers-and-origins-of-tool-use}{%
-\subsection{Implications for the evolutionary drivers and origins of tool use}\label{implications-for-the-evolutionary-drivers-and-origins-of-tool-use}}
-
-The predicted probabilities from our phylogenetic survival cure model have
-implications for inferences about the evolutionary drivers and origins of tool
-use in the parrot order. Regarding the drivers of tool use hypothesised in
-Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that
-encephalisation quotient strongly positively predicted the probability of tool
-use (median posterior log odds slope = 1.12, 95\%
-CI {[}0.39
-2.00{]}; total \emph{n} = 174
-species; Figure \ref{fig:plotSurvCure4}). This helps explain the ranking in
-Figure \ref{fig:plotSurvCure1}: the blue-eyed cockatoo has the largest relative
-brain size in the dataset. We also found that feeding generalist species were
-slightly more likely to be tool users, though the posterior difference between
-generalists and specialists was quite uncertain (median posterior log odds
-difference = 0.33, 95\% CI {[}
--1.13 1.76{]}; total
-\emph{n} = 174 species). These results from the survival cure model
-differed from the results of models fitted to pre-video-survey and
-post-video-survey data without the survival cure component, which found no
-effect of relative brain size and no difference between feeding strategies,
-respectively (Supplementary Figure \ref{fig:plotComparison}).
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure4-1.pdf}
-\caption{\label{fig:plotSurvCure4}\emph{Posterior predictions for the effects of feeding
-strategy and encephalisation quotient on the probability of tool use from the
-phylogenetic survival cure model.} In the left plot, points and lines represent
-posterior medians and 50\% and 95\% credible intervals, with densities
-representing full posterior distributions. In the right plot, the line and
-shaded areas represent the posterior median regression line with 50\% and 95\%
-credible intervals. In both plots, individual species are coloured according to
-the presence / absence of tool use in the video survey and the scientific
-literature. Total \emph{n} = 174 species, generalist \emph{n} =
-121 species, specialist \emph{n} =
-53 species.}
-\end{figure}
-
-Regarding the origins of tool use, we fitted exploratory ancestral state
-reconstruction models to the pre-video-survey data, the post-video-survey data,
-and the predicted probabilities from the phylogenetic survival cure model. The
-discoveries from our video survey and from our phylogenetic modelling increased
-the likelihood that tool use was present in the most recent common ancestor for
-several parrot genera. These include the amazon parrots native to the Americas
-(\emph{Amazona}), the true white cockatoos and corellas found in South East Asia and
-Australasia (\emph{Cacatua}), the kea and the kākā from New Zealand (\emph{Nestor}), and
-the \emph{Poicephalus} genus native to Africa (Table \ref{tab:tableASR};
-Supplementary Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}). These findings
-suggest that species from each of these genera may share their tool use
-capabilities via common descent from their respective common ancestors, rather
-than via independent evolution within each genus or behavioural innovation
-within species.
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tableASR}Estimated probabilities of tool use for most recent common
-ancestors of several parrot genera. \emph{Probabilities estimated using exploratory
-ancestral state reconstruction models fitted to the pre-video-survey data,
-post-video-survey data, and predicted probabilities from the phylogenetic
-survival cure model. Total} n \emph{= 174 species.}}
-
-\begin{tabular}{llll}
-\toprule
-Genus & \multicolumn{1}{c}{Pre-video-survey} & \multicolumn{1}{c}{Post-video-survey} & \multicolumn{1}{c}{Survival cure probabilities}\\
-\midrule
-\textit{Amazona} & 0.06, 95\% CI [0.01 0.17] & 0.21, 95\% CI [0.04 0.66] & 0.48, 95\% CI [0.05 0.84]\\
-\textit{Cacatua} & 0.08, 95\% CI [0.03 0.20] & 0.17, 95\% CI [0.03 0.45] & 0.81, 95\% CI [0.23 0.99]\\
-\textit{Nestor} & 0.11, 95\% CI [0.05 0.29] & 0.21, 95\% CI [0.12 0.37] & 0.53, 95\% CI [0.29 0.66]\\
-\textit{Poicephalus} & 0.06, 95\% CI [0.02 0.11] & 0.19, 95\% CI [0.12 0.41] & 0.72, 95\% CI [0.16 0.90]\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Since the earliest anecdotes of parrots using tools by Wallace in the 1880s
-(59) and more systematic anecdotal reports in the 1970s (60),
-only 11 parrot species (3\% of all extant parrots) have been documented as tool
-users in the scientific literature. Our study used crowdsourcing to identify 17
-additional tool-using parrot species that are new to science, more than doubling
-the overall count to 28 species (7\%). These species consisted of cockatoos
-(\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), and neotropical parrots
-(\emph{Arinae}). Beyond the crowdsourcing survey, the strong phylogenetic signal in
-our dataset allowed us to use phylogenetic information, along with other
-variables, to infer the unobserved probabilities of tool use across the parrot
-order. Our phylogenetic survival cure model incorporated information on
-phylogenetic history, research effort, relative brain size, and feeding
-specialisation to rank parrot species that were most likely to be undetected
-tool users. The sum of probabilities from this model implied that between 15
-and 41 of the species without observed evidence of tool use are likely to be
-undetected tool users, suggesting that the true proportion of tool users may be
-as high as 17\%.
-
-These findings have a number of important implications. First, our findings show
-that current research effort in the scientific literature is insufficient to
-capture the real world occurrence of parrot tool use. If the scientific
-literature had sampled the natural world sufficiently, we would expect to see
-close correspondence between those species reported as tool users in the
-literature and those species the public have filmed performing tool use.
-Instead, we discovered a large discrepancy between these two data sources, both
-in the prevalence of tool use and the species identified. This raises the
-possibility that insufficient research effort is a general issue across the
-scientific literature, both for tool use in other groups and for other rare
-behaviours.
-
-Second, in terms of the evolution of tool use in parrots, our study challenges a
-key assumption made in the literature to date: that only a minority of parrots
-are tool users (30, 31, 34, 37, 38).
-The paucity of evidence for tool use across parrots in the literature initially
-implied that the capacity for tool use may have evolved independently in
-different parrot species. Our discovery of the widespread distribution of tool
-use across the parrot phylogeny, along with the strong phylogenetic signal in
-this expanded dataset, challenges this and suggests that, at least for some
-parrot clades, the capacity for tool use might be a homologous trait that has
-been evolutionarily conserved. Our exploratory ancestral state reconstruction
-analysis provides preliminary support for this hypothesis, revealing an
-increased probability of tool use among the most recent common ancestors for the
-\emph{Amazona}, \emph{Cacatua}, \emph{Nestor}, and \emph{Poicephalus} genera. Even at this
-preliminary stage, our analysis therefore raises an alternative hypothesis for
-the observed tool use in \emph{Cacatua} (30, 38) and
-\emph{Nestor} (26--29, 31, 34), namely that tool behaviours have arisen due to the
-common ancestor having the capacity to use tools, rather than from independent
-evolution or behavioural innovation within species.
-
-Third, our results support existing theories of the drivers of tool use. We
-found that encephalisation was strongly positively related to the probability of
-tool use in our phylogenetic model, supporting previous theories linking
-relative brain size to increased tool innovation in birds (11--13) and primates (61). We acknowledge that
-encephalisation quotient is not a perfect measure due to measurement error and
-challenges with interpretation (3, 4). However, encephalisation
-quotient has much greater coverage across the parrot phylogeny than more
-fine-grained measures like whole neuron count (62) and there is no reason
-to think that measurement error would produce the consistent patterns across our
-study and prior work. To understand the causal mechanisms responsible for these
-relationships, we encourage further work on the specific neural correlates of
-technical intelligence in parrots, e.g., (63). In our phylogenetic
-model, we also found that tool use was somewhat more likely among feeding
-generalists compared to feeding specialists, although this difference was
-uncertain. This trend supports previous suggestions that increased cognitive
-abilities and technical innovation rates are required to expand a generalist
-species' dietary niche (16, 18, 64). However, the trend contradicts theories linking tool use to
-dietary specialisation, whereby species eating specific foods that require
-extractive foraging have higher cognitive ability and are especially prone to
-using tools (18).
-
-All instances of tool use in our crowdsourcing survey met the established
-criteria for tool use in the literature: the manipulation of an unattached
-object as an extension of the animal's body to achieve a goal (10).
-However, a striking feature of the dataset is that the 17 additional species
-identified in the video survey were exclusively observed using tools for
-self-scratching. While parrots in the wild use tools to achieve a variety of
-goals, including extractive foraging and preening (34, 38),
-parrots in captivity only require tools to achieve the latter goal. Despite this
-difference in the type of tool use observed, self-scratching is nonetheless a
-major category of animal tool use. Self-scratching also meets the definition for
-a more complex type of embodied tool use known as `tooling', the deliberate
-generation of a mechanical interface by using an object to manipulate another
-target or surface (65). This makes it difficult to dismiss
-self-scratching as unimportant: to do so would require a redefinition of
-tool-use in non-human animals. Moreover, the fact that we found strong
-phylogenetic clustering of self-scratching tool use from the video survey with
-other examples of tool use from the literature supports a common underlying
-cognitive mechanism. In line with this, some of the species of parrots that use
-tools for self-scratching in captivity also use tools for other purposes in the
-wild (30, 31, 34, 38).
-
-There was little evidence to suggest that the observations of self-scratching
-tool use in the video survey were merely unintentional accidents or explicitly
-trained behaviours. Individual parrots often used tools slowly and repetitively
-over long periods of time, even across multiple different videos, suggesting
-that their behaviour was not random or accidental (66). Parrots
-preferentially employed self-scratching tools on areas of their body that were
-otherwise inaccessible, with 96\% of all instances involving scratching of the
-head or neck, suggesting intentional tool use. For 60\% of the species in the
-video survey, we found two or more videos of repetitive and sustained scratching
-by different individuals of the same species in separate households, suggesting
-that the manipulations were intentional and recurring events that did not
-represent unusual stereotypies of any single individual. Regarding the
-possibility of training or cueing from owners, over half of the videos contained
-no evidence of human interaction aside from filming the behaviour. Humans only
-handed parrots their tools in two of the videos, and none of the videos featured
-owners directly rewarding tool use behaviours with food. Finally, the high
-levels of phylogenetic signal in our data provide strong evidence that the
-observations from our video survey reflect biologically-endowed capacities for
-tool use rather than accidental or trained behaviours, which would likely appear
-uniformly across the phylogeny.
-
-While missing data imputation is becoming more common in phylogenetic
-analyses (67), the important distinction between absence of
-evidence and evidence of absence has not been given as much attention. Our
-phylogenetic analysis provides one approach to this problem by distinguishing
-between true absences of tool use and absences of tool use due to a lack of
-research effort in the scientific literature or in crowdsourced videos. To
-achieve this, we explicitly modelled the measurement of the outcome variable
-along a research effort time series, such that species with lower research
-effort in the literature or in videos were likely to be censored. In line with
-our causal model, we also included relative brain size, feeding strategy, and
-phylogenetic history as predictors of unobserved tool use. We encourage
-researchers to test this model by directing future study efforts towards the
-parrot species with the highest probabilities of being undetected tool-users.
-Future work should also refine the causal model in Figure \ref{fig:plotDAG} to
-provide more certain estimates of tool use probabilities, either by including
-additional predictor variables or modelling further causes of measurement error
-in the taxonomic record, such as species abundance and geographic
-accessibility (20).
-
-In conclusion, we have shown that the scientific literature has insufficiently
-captured the full distribution of tool use in the parrot order. Our
-crowdsourcing survey more than doubled the number of known tool using parrot
-species from 11 to 28, and our phylogenetic model suggested that the true
-proportion of parrot tool users could be as high as 17\% of all species in this
-order. These discoveries have implications for theories of the evolutionary
-drivers and origins of tool use in parrots. Beyond parrot tool use, the
-crowdsourcing and phylogenetic methods used in this study have the potential to
-be applied to other rarely observed behaviours, including tool use in other
-taxa (68), rhythmic entrainment in birds (69--72), teasing behaviours in primates (73), and
-tactical deception across all animals (74--76).
-We hope that these methods will continue to uncover a diverse array of ephemeral
-behaviours that have as yet gone undetected in the scientific literature.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{video-searches-and-coding}{%
-\subsection{Video searches and coding}\label{video-searches-and-coding}}
-
-Our video search was conducted on YouTube in July 2020. Search terms included
-``parrot using tool'' and variants (e.g., ``macaw using tool'', ``lorikeet using
-tool'', ``parakeet using tool''), ``tool use in parrot'', ``parrot tool use'', ``parrot
-scratching itself'' (included after we found several videos demonstrating
-self-care tool use in previous searches) and equivalent terms (e.g., ``parrot
-preening itself'', ``parrot grooming itself'', ``parrot scratching''). For all
+Our video search was conducted on YouTube in July 2020. Searches were conducted
+manually by the first author over a month-long period, using the same IP address
+and not logged in with a YouTube user account. Search terms included 
+"parrot using tool" and variants (e.g., "macaw using tool", "lorikeet using 
+tool", "parakeet using tool"), "tool use in parrot", "parrot tool use", "parrot 
+scratching itself" (included after we found several videos demonstrating 
+self-care tool use in previous searches) and equivalent terms (e.g., "parrot 
+preening itself", "parrot grooming itself", "parrot scratching"). For all 
 species that did not display results including object manipulation or scratching 
-behaviours, we also searched the species' common name(s) + ``tool use'', as well
-as the species' common name(s) + ``scratching''. We also searched for translations
-of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all
-countries where bird ownership was reported as \textgreater5\% (77), namely,
+behaviours, we also searched the species’ common name(s) + "tool use", as well 
+as the species’ common name(s) + "scratching". We also searched for translations 
+of the terms "parrot tool use" and "parrot scratching" in languages for all 
+countries where bird ownership was reported as >5% [@GlobalGfkSurvey], namely, 
 Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, 
-Portuguese, and Mandarin.
+Portuguese, and Mandarin. Browser search histories were not cleared between
+searches.
 
@@
 any parrots. At this point, we ended that search and initiated the next search. 
-In line with previous recommendations (21), we planned to exclude any
+In line with previous recommendations [@Nelson2013], we planned to exclude any 
 videos that consisted of four or more shots edited together so as to ensure the 
@@
 manipulation of an unattached object as an extension of the beak or foot to 
-achieve a goal towards another object, individual, or oneself (10).
+achieve a goal towards another object, individual, or oneself [@Shumaker2011]. 
 Borderline tool use was similarly defined, except that it involved the use of an 
-object that was still attached to a substrate (54). For example, if
+object that was still attached to a substrate [@Seed2010]. For example, if 
 individuals used a fallen feather or stick for self-scratching this was defined 
-as tool use, but using one's currently attached tail feathers or cage
+as tool use, but using one’s currently attached tail feathers or cage 
 furnishings for the same purpose was defined as borderline tool use. 
 Self-scratching had to involve slow and repeated movements of touching an object 
-to one's body (or, in the case of borderline tool use, rubbing repetitively
-against an attached object (66)).
+to one’s body (or, in the case of borderline tool use, rubbing repetitively 
+against an attached object [@Sandor2020]).
 
@@
 
-\hypertarget{data-for-parrot-species}{%
-\subsection{Data for parrot species}\label{data-for-parrot-species}}
+Since YouTube is constantly growing and evolving in both its uploaded content 
+and its proprietary recommendation algorithms, the same search strategy today 
+would not return exactly the same videos as our search in July 2020. It is 
+possible that some videos have since been deleted or more videos of parrot tool
+use have since been uploaded. However, this does not affect our conclusions
+about the number of parrot species found to use tools in our initial search.
 
-We collected data for 194 parrot species (Supplementary Figures
-\ref{fig:plotPhylo2} - \ref{fig:plotPhylo4}). We gathered feeding strategy
-data as a dichotomous variable (``generalist'' or ``specialist'') from the
-EltonTraits ecological database (52). As per the database, specialists
-were defined as species whose diet comprised at least 70\% of a single food
+### Data for parrot species
+
+We collected data for 194 parrot species (Figures
+\@ref(fig:plotPhylo2) - \@ref(fig:plotPhylo4)). We gathered feeding strategy 
+data as a dichotomous variable ("generalist" or "specialist") from the 
+EltonTraits ecological database [@Wilman2016]. As per the database, specialists 
+were defined as species whose diet comprised at least 70% of a single food 
 source. To calculate relative brain size, we collated data from the literature 
 for all known body mass (g) and brain mass (g) values across 
-parrots (46--51). For all species for which we obtained body and brain mass data, we
+parrots [@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;@Schuck2008;
+@Silva2017]. For all species for which we obtained body and brain mass data, we 
 calculated the encephalisation quotient (EQ) using the following 
-formula (78): \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
+formula [@Jerison1973]: $BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))$. We 
 found body mass and brain mass data for a total of 194 parrot species. This 
 included all tool-using species in our video dataset, with the exception of 
-three species: \emph{Diopsittaca nobilis}, \emph{Psittacara erythrogenys}, and \emph{Coracopsis
-vasa}. For the latter, we used values for the closely related \emph{Coracopsis
-nigra}. The other two species were excluded from the final dataset.
+three species: _Diopsittaca nobilis_, _Psittacara erythrogenys_, and _Coracopsis 
+vasa_. For the latter, we used values for the closely related _Coracopsis 
+nigra_. The other two species were excluded from the final dataset.
 
 For modelling purposes, we coded research effort in both the scientific 
-literature and the crowdsourced videos. For the scientific literature, we
+literature and the YouTube videos. For the scientific literature, we 
 operationalised research effort as the number of papers published for each 
@@
 used the scientific database Scopus for coding the number of published papers. 
-For the crowdsourced videos, we coded research effort as the number of search
-hits for each species on YouTube. If tool use had been identified on YouTube, we
-estimated the number of search hits when the first video of tool use was
-published on YouTube, assuming linear growth of search hits since the inception
-of YouTube. If tool use had not been identified, we used the current number of
-search hits.
+For the videos, we coded research effort as the number of search hits for each
+species on YouTube. If tool use had been identified on YouTube, we estimated the
+number of search hits when the first video of tool use was published on YouTube,
+assuming linear growth of search hits since the inception of YouTube. If tool
+use had not been identified, we used the current number of search hits.
 
 For phylogenetic data, we used the phylogenetic tool at www.birdtree.org
-(53) to compile 1000 posterior draws of phylogenetic trees for 174 of the
+[@Jetz2012] to compile 1000 posterior draws of phylogenetic trees for 174 of the 
 194 parrot species for which both EQ and genomic data exist. A single maximum 
@@
 
-\hypertarget{phylogenetic-signal}{%
-\subsection{Phylogenetic signal}\label{phylogenetic-signal}}
+## Quantification and Statistical Analysis
 
-We used the \emph{fitDiscrete} function in the \emph{ape} R package (79) to
+### Phylogenetic signal
+
+We used the _fitDiscrete_ function in the _ape_ R package [@Paradis2019] to 
 calculate phylogenetic signal, for both the pre-survey and post-survey tool use 
@@
 
-\hypertarget{causal-model-of-tool-use}{%
-\subsection{Causal model of tool use}\label{causal-model-of-tool-use}}
+### Causal model of tool use
 
 To infer unobserved probabilities of tool use across parrots, we proposed a 
-causal model of observed tool use (Figure \ref{fig:plotDAG}). We assumed that
-observed tool use in the scientific literature and in the crowdsourced videos is
-caused by both the unobserved presence or absence of tool use and research
-effort, proxied by the number of papers published on a species and the number of
-videos published on a species. Tool users are more likely to be observed if they
-are well studied, but understudied tool users may go undetected. In addition,
-based on theory, we also assumed that unobserved tool use is caused by feeding
-strategy and relative brain size (11--14, 16--18). Finally, we
+causal model of observed tool use (Figure \@ref(fig:plotDAG)). We assumed that 
+observed tool use in the scientific literature and in the videos is caused by 
+both the unobserved presence or absence of tool use and research effort, proxied
+by the number of papers published on a species and the number of videos
+published on a species. Tool users are more likely to be observed if they are
+well studied, but understudied tool users may go undetected. In addition, based
+on theory, we also assumed that unobserved tool use is caused by feeding 
+strategy and relative brain size [@Lefebvre2004;@Lefebvre1997;@Lefebvre2002;
+@Ducatez2015;@Sol2005;@Overington2011;@HenkeVonDerMalsburg2020]. Finally, we 
 assumed that shared phylogenetic history causes unobserved confounding and 
@@
 
-\hypertarget{bayesian-phylogenetic-survival-cure-model}{%
-\subsection{Bayesian phylogenetic survival cure model}\label{bayesian-phylogenetic-survival-cure-model}}
+### Bayesian phylogenetic survival cure model
 
@@
 of tool use in parrots. To understand the model, suppose that we have the 
-following observed variables for parrot species \(i\). For the scientific
-literature, we declare \(\text{N}_{\text{Lit},i}\) as the number of papers
-published before and up to tool use identification for species \(i\) (or, if tool
+following observed variables for parrot species $i$. For the scientific 
+literature, we declare $\text{N}_{\text{Lit},i}$ as the number of papers 
+published before and up to tool use identification for species $i$ (or, if tool 
 use has not been identified, the total number of papers published for species 
-\(i\)) and \(\text{T}_{\text{Lit},i}\) as a binary variable stating whether (1) or
+$i$) and $\text{T}_{\text{Lit},i}$ as a binary variable stating whether (1) or 
 not (0) tool use has yet been observed in the scientific literature for species 
-\(i\). For the crowdsourced videos, we declare \(\text{N}_{\text{Vid},i}\) as the
+$i$. For the videos, we declare $\text{N}_{\text{Vid},i}$ as the 
 number of videos published before and up to tool use identification for species 
-\(i\) (or, if tool use has not been identified, the total number of videos
-published for species \(i\)) and \(\text{T}_{\text{Vid},i}\) as a binary variable
+$i$ (or, if tool use has not been identified, the total number of videos 
+published for species $i$) and $\text{T}_{\text{Vid},i}$ as a binary variable 
 stating whether (1) or not (0) tool use has yet been observed in the 
-crowdsourced videos for species \(i\). Additionally, \(\text{F}_i\) and
-\(\text{EQ}_i\) are feeding strategy and encephalisation quotient values for
-species \(i\) and we have a phylogenetic distance matrix \(D\) that describes the
+videos for species $i$. Additionally, $\text{F}_i$ and 
+$\text{EQ}_i$ are feeding strategy and encephalisation quotient values for 
+species $i$ and we have a phylogenetic distance matrix $D$ that describes the 
 patristic distances between all parrot species.
 
-We assume that species \(i\) is a non-tool-user with some
-probability \(p_i\). We also assume that tool use is identified in the scientific
-literature and the crowdsourced videos at constant rates \(\lambda_{\text{Lit}}\)
-and \(\lambda_{\text{Vid}}\) following exponential survival functions. Given these
+We assume that species $i$ is a non-tool-user with some 
+probability $p_i$. We also assume that tool use is identified in the scientific 
+literature and the videos at constant rates $\lambda_{\text{Lit}}$ 
+and $\lambda_{\text{Vid}}$ following exponential survival functions. Given these 
 assumptions, we can then describe the different ways in which variables 
-\(\text{N}_\text{Lit}\) and \(\text{N}_\text{Vid}\) can be distributed. Focusing on
+$\text{N}_\text{Lit}$ and $\text{N}_\text{Vid}$ can be distributed. Focusing on 
 the scientific literature, if tool use has been observed 
-(\(\text{T}_{\text{Lit},i} = 1\)), then the likelihood for
-\(\text{N}_{\text{Lit},i}\) is:
+($\text{T}_{\text{Lit},i} = 1$), then the likelihood for 
+$\text{N}_{\text{Lit},i}$ is:
 
@@
 On the other hand, if tool use has not yet been observed 
-(\(\text{T}_{\text{Lit},i} = 0\)), there are two ways that the outcome variable
+($\text{T}_{\text{Lit},i} = 0$), there are two ways that the outcome variable 
 could have been realised. First, the species could be a non-tool-user with 
-probability \(p_i\). Second, the species could be a tool-user with probability
-(\(1 - p_i\)) that has been censored and has not had its tool use measured yet.
-Together, then, the likelihood for \(\text{N}_{\text{Lit},i}\) is:
+probability $p_i$. Second, the species could be a tool-user with probability 
+($1 - p_i$) that has been censored and has not had its tool use measured yet. 
+Together, then, the likelihood for $\text{N}_{\text{Lit},i}$ is:
 
@@
 The Exponential-CCDF function allows for the censored nature of the data. The 
-same data generating process is assumed to underlie the crowdsourced videos.
+same data generating process is assumed to underlie the videos.
 
-We define the mixture likelihood \(\text{SurvivalCure}\) as the distribution
-above, with parameters \(p\) (the probability of being a non-tool-user)
-and \(\lambda\) (the rate of the exponential distribution). We use an
-Ornstein-Uhlenbeck Gaussian process (80) to model phylogenetic
+We define the mixture likelihood $\text{SurvivalCure}$ as the distribution 
+above, with parameters $p$ (the probability of being a non-tool-user) 
+and $\lambda$ (the rate of the exponential distribution). We use an 
+Ornstein-Uhlenbeck Gaussian process [@McElreath2020] to model phylogenetic 
 covariance. Below, we specify the full model with priors:
@@
 The priors for this model produce reasonable prior predictions of the 
-probabilities of tool use for each parrot species (Supplementary Figure
-\ref{fig:plotSurvCure7}), but a sensitivity analysis revealed that the ranking
+probabilities of tool use for each parrot species (Figure
+\@ref(fig:plotSurvCure7)), but a sensitivity analysis revealed that the ranking 
 and posterior probabilities reported in the main text were robust to modifying 
-these priors (Supplementary Figure \ref{fig:plotSurvCure8}). We estimated the
+these priors (Figure \@ref(fig:plotSurvCure8)). We estimated the 
 posterior distribution of this model using Hamiltonian Monte Carlo as 
-implemented in Stan version 2.26.1 (81). We ran the model for 4000
+implemented in Stan version 2.26.1 [@Stan2020]. We ran the model for 4000 
 samples, with 2000 warmup samples, and iterated the model over 100 posterior 
@@
 effective sample sizes suggested that the model converged normally. Trace plots 
-are reported in Supplementary Figure \ref{fig:plotTrace}. We report
+are reported in Figure \@ref(fig:plotTrace). We report 
 equal-tailed credible intervals to describe the posterior distribution of this 
@@
 parameters. The model was able to successfully recover those parameters 
-(Supplementary Figure \ref{fig:plotSurvCureSim}). We also ran a
+(Figure \@ref(fig:plotSurvCureSim)). We also ran a 
 leave-one-species-out exercise to ensure that we could accurately predict known 
@@
 
-\hypertarget{ancestral-state-reconstruction}{%
-\subsection{Ancestral state reconstruction}\label{ancestral-state-reconstruction}}
+### Ancestral state reconstruction
 
@@
 parrots, we fitted three exploratory ancestral state reconstruction models. We 
-used the \emph{ancThresh} function from the \emph{phytools} R package (82),
+used the _ancThresh_ function from the _phytools_ R package [@phytools], 
 iterating the function over 100 posterior parrot phylogenies. This function 
@@
 continuous variable following an Ornstein-Uhlenbeck process. We fitted this 
-model to three different outcome variables: (\emph{i}) presence vs.~absence of tool
-use in scientific literature only, (\emph{ii}) presence vs.~absence of tool use in
-literature and/or videos, and (\emph{iii}) the median predicted probabilities of tool
+model to three different outcome variables: (_i_) presence vs. absence of tool 
+use in scientific literature only, (_ii_) presence vs. absence of tool use in 
+literature and/or videos, and (_iii_) the median predicted probabilities of tool 
 use from the phylogenetic survival cure model.
 
-\hypertarget{reproducibility}{%
-\subsection{Reproducibility}\label{reproducibility}}
+### Reproducibility
 
-All analyses were conducted in R v4.2.1. (83). Visualisations were
-produced using the \emph{ggtree}(84), \emph{ggplot2} (85), and \emph{cowplot}
-(86) packages. The manuscript was reproducibly generated using the
-\emph{targets} (87) and \emph{papaja} (88) packages. Code to reproduce all
+All analyses were conducted in R v4.2.1. [@RCoreTeam]. Visualisations were 
+produced using the _ggtree_[@ggtree], _ggplot2_ [@Wickham2016], and _cowplot_ 
+[@Wilke2020] packages. The manuscript was reproducibly generated using the 
+_targets_ [@Landau2021] and _papaja_ [@Aust2022] packages. Code to reproduce all 
 analyses and figures can be found here: 
-\url{https://github.com/ScottClaessens/phyloParrot}
-
-\newpage
-\nolinenumbers
-
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-This project was made possible through the support of a grant from the Templeton
-World Charity Foundation (A.H.T., X.J.N.). The authors would like to thank
-Daniel Sol for providing feedback on a previous version of the manuscript.
-
-\hypertarget{author-contributions}{%
-\section{Author Contributions}\label{author-contributions}}
-
-All authors contributed to the conceptualisation of the paper. A.P.M.B., X.J.N.,
-and A.H.T. developed the video search methodology. S.C., D.W., and Q.A.D.
-developed the statistical models and analysed the data. All the authors wrote
-the manuscript and approved the final version for submission.
-
-\hypertarget{competing-interests}{%
-\section{Competing Interests}\label{competing-interests}}
-
-The authors declare no competing interests.
-
-\hypertarget{data-availability}{%
-\section{Data Availability}\label{data-availability}}
-
-All data used in this study are publicly available on GitHub:
-\url{https://github.com/ScottClaessens/phyloParrot}
-
-\hypertarget{code-availability}{%
-\section{Code Availability}\label{code-availability}}
-
-All code to reproduce the analyses in this study are publicly available on
-GitHub: \url{https://github.com/ScottClaessens/phyloParrot}
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-MacLean2012}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{E.
-L.
-MacLean, \emph{et al.}, \href{https://doi.org/10.1007/s10071-011-0448-8}{How does cognition evolve?
-Phylogenetic comparative psychology}.
-\emph{Animal Cognition} \textbf{15}, 223--238 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2011}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{L. Lefebvre, \href{https://doi.org/10.1098/rsbl.2010.0556}{Taxonomic counts of cognition in the wild}. \emph{Biology Letters} \textbf{7}, 631--633 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Logan2018}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{C.
-J.
-Logan, \emph{et al.}, \href{https://doi.org/10.3819/CCBR.2018.130008}{Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization}.
-\emph{Comparative Cognition \& Behavior Reviews} \textbf{13}, 55--89 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Healy2007}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{S.
-D.
-Healy, C.
-Rowe, \href{https://doi.org/10.1098/rspb.2006.3748}{A critique of comparative studies of brain size}.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{274}, 453--464 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Powell2017}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{L.
-E.
-Powell, K.
-Isler, R.
-A.
-Barton, \href{https://doi.org/10.1098/rspb.2017.1765}{Re-evaluating the link between brain size and behavioural ecology in primates}.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{284}, 20171765 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodall1964}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{J. Goodall, Tool-using and aimed throwing in a community of free-living chimpanzees. \emph{Nature} \textbf{201}, 1264--1266 (1964).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hunt1996}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{G. R. Hunt, \href{https://doi.org/10.1038/379249a0}{Manufacture and use of hook-tools by {N}ew {C}aledonian crows}. \emph{Nature} \textbf{379}, 249--251 (1996).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Smolker1997}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{R.
-Smolker, A.
-Richards, R.
-Connor, J.
-Mann, P.
-Berggren, \href{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}{Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?} \emph{Ethology} \textbf{103}, 454--465 (1997).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Finn2009}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{J.
-K.
-Finn, T.
-Tregenza, M.
-D.
-Norman, \href{https://doi.org/10.1016/j.cub.2009.10.052}{Defensive tool use in a coconut-carrying octopus}.
-\emph{Current Biology} \textbf{19}, R1069--R1070 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{R.
-W.
-Shumaker, K.
-R.
-Walkup, B.
-B.
-Beck, G.
-M.
-Burghardt, \emph{Animal tool behavior: The use and manufacture of tools by animals} (Johns Hopkins University Press) https:/doi.org/\href{https://doi.org/10.1353/book.98237}{10.1353/book.98237}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2002}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{L. Lefebvre, N. Nicolakakis, D. Boire, \href{https://doi.org/10.1163/156853902320387918}{Tools and brains in birds}. \emph{Behaviour} \textbf{139}, 939--973 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre1997}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{L.
-Lefebvre, P.
-Whittle, E.
-Lascaris, A.
-Finkelstein, \href{https://doi.org/10.1006/anbe.1996.0330}{Feeding innovations and forebrain size in birds}.
-\emph{Animal Behaviour} \textbf{53}, 549--560 (1997).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2004}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{L.
-Lefebvre, S.
-M.
-Reader, D.
-Sol, \href{https://doi.org/10.1159/000076784}{Brains, innovations and evolution in birds and primates}.
-\emph{Brain, Behavior and Evolution} \textbf{63}, 233--246 (2004).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2005}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{D.
-Sol, R.
-P.
-Duncan, T.
-M.
-Blackburn, P.
-Cassey, L.
-Lefebvre, \href{https://doi.org/10.1073/pnas.0408145102}{Big brains, enhanced cognition, and response of birds to novel environments}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{102}, 5460--5465 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2009}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{D.
-Sol, \href{https://doi.org/10.1098/rsbl.2008.0621}{Revisiting the cognitive buffer hypothesis for the evolution of large brains}.
-\emph{Biology Letters} \textbf{5}, 130--133 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2015}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{S.
-Ducatez, J.
-Clavel, L.
-Lefebvre, \href{https://doi.org/10.1111/1365-2656.12255}{Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?} \emph{Journal of Animal Ecology} \textbf{84}, 79--89 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Overington2011}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{S.
-E.
-Overington, A.
-S.
-Griffin, D.
-Sol, L.
-Lefebvre, \href{https://doi.org/10.1093/beheco/arr130}{Are innovative species ecological generalists?
-A test in {N}orth {A}merican birds}.
-\emph{Behavioral Ecology} \textbf{22}, 1286--1293 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2020}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{J.
-Henke-von der Malsburg, P.
-M.
-Kappeler, C.
-Fichtel, Linking ecology and cognition: Does ecological specialisation predict cognitive test performance?
-\emph{Behavioral Ecology and Sociobiology} \textbf{74}, 154 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MettkeHofmann2014}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{C.
-Mettke-Hofmann, \href{https://doi.org/10.1002/wcs.1289}{Cognitive ecology: Ecological factors, life-styles, and cognition}.
-\emph{WIREs Cognitive Science} \textbf{5}, 345--360 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2014}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{S. Ducatez, L. Lefebvre, \href{https://doi.org/10.1371/journal.pone.0089955}{Patterns of research effort in birds}. \emph{PLOS ONE} \textbf{9}, e89955 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Nelson2013}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{X.
-J.
-Nelson, N.
-Fijn, \href{https://doi.org/10.1016/j.anbehav.2012.12.009}{The use of visual media as a tool for investigating animal behaviour}.
-\emph{Animal Behaviour} \textbf{85}, 525--536 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dickinson2010}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{J.
-L.
-Dickinson, B.
-Zuckerberg, D.
-N.
-Bonter, \href{https://doi.org/10.1146/annurev-ecolsys-102209-144636}{Citizen science as an ecological research tool: Challenges and benefits}.
-\emph{Annual Review of Ecology, Evolution, and Systematics} \textbf{41}, 149--172 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{K.
-Krueger, L.
-Esch, R.
-Byrne, \href{https://doi.org/10.1371/journal.pone.0218954}{Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms}.
-\emph{PLOS ONE} \textbf{14}, 1--20 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Klump2021}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{B.
-C.
-Klump, \emph{et al.}, \href{https://doi.org/10.1126/science.abe7808}{Innovation and geographic spread of a complex foraging culture in an urban parrot}.
-\emph{Science} \textbf{373}, 456--460 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Klump2022}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{B.
-C.
-Klump, R.
-E.
-Major, D.
-R.
-Farine, J.
-M.
-Martin, L.
-M.
-Aplin, Is bin-opening in cockatoos leading to an innovation arms race with humans?
-\emph{Current Biology} \textbf{32}, R910--R911 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2009}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{A.
-M.
-I.
-Auersperg, G.
-K.
-Gajdon, L.
-Huber, \href{https://doi.org/10.1098/rsbl.2009.0114}{Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem}.
-\emph{Biology Letters} \textbf{5}, 455--458 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2010}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{A.
-M.
-I.
-Auersperg, G.
-K.
-Gajdon, L.
-Huber, \href{https://doi.org/10.1016/j.anbehav.2010.08.007}{Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task}.
-\emph{Animal Behaviour} \textbf{80}, 783--789 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011a}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{A.
-M.
-I.
-Auersperg, L.
-Huber, G.
-K.
-Gajdon, \href{https://doi.org/10.1098/rsbl.2011.0388}{Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis})}.
-\emph{Biology Letters} \textbf{7}, 825--828 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011b}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{A.
-M.
-I.
-Auersperg, A.
-M.
-P.
-von Bayern, G.
-K.
-Gajdon, L.
-Huber, A.
-Kacelnik, \href{https://doi.org/10.1371/journal.pone.0020231}{Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm}.
-\emph{PLOS ONE} \textbf{6}, 1--8 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2012}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{A.
-M.
-I.
-Auersperg, B.
-Szabo, A.
-M.
-P.
-von Bayern, A.
-Kacelnik, \href{https://doi.org/10.1016/j.cub.2012.09.002}{Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo}.
-\emph{Current Biology} \textbf{22}, R903--R904 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bastos2021}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{A.
-P.
-Bastos, K.
-Horváth, J.
-L.
-Webb, P.
-M.
-Wood, A.
-H.
-Taylor, Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
-\emph{Scientific Reports} \textbf{11}, 18035 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BentleyCondit2010}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{V.
-Bentley-Condit, E.
-O.
-Smith, \href{https://doi.org/10.1163/000579509X12512865686555}{Animal tool use: Current definitions and an updated comprehensive catalog}.
-\emph{Behaviour} \textbf{147}, 185--32A (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Borsari2005}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{A.
-Borsari, E.
-B.
-Ottoni, \href{https://doi.org/10.1007/s10071-004-0221-3}{Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus})}.
-\emph{Animal Cognition} \textbf{8}, 48--52 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodman2018}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{M.
-Goodman, T.
-Hayward, G.
-R.
-Hunt, \href{https://doi.org/10.1038/s41598-018-32363-9}{Habitual tool use innovated by free-living {N}ew {Z}ealand kea}.
-\emph{Scientific Reports} \textbf{8}, 13935 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Heinsohn2017}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{R.
-Heinsohn, C.
-N.
-Zdenek, R.
-B.
-Cunningham, J.
-A.
-Endler, N.
-E.
-Langmore, \href{https://doi.org/10.1126/sciadv.1602399}{Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music}.
-\emph{Science Advances} \textbf{3}, e1602399 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Janzen1976}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{M. J. Janzen, D. H. Janzen, C. M. Pond, Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). \emph{Biotropica} \textbf{8}, 70 (1976).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lambert2015}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{M.
-L.
-Lambert, A.
-M.
-Seed, K.
-E.
-Slocombe, \href{https://doi.org/10.1098/rsbl.2015.0861}{A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa})}.
-\emph{Biology Letters} \textbf{11}, 20150861 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-OHara2021}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{M.
-O'Hara, \emph{et al.}, \href{https://doi.org/10.1016/j.cub.2021.08.009}{Wild {G}offin's cockatoos flexibly manufacture and use tool sets}.
-\emph{Current Biology} \textbf{31}, 4512--4520.e6 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{P.
-Anderson, \href{https://doi.org/10.1163/156853003322796109}{A bird in the house: An anthropological perspective on companion parrots}.
-\emph{Society \& Animals} \textbf{11}, 393--418 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{M.
-Carrete, J.
-Tella, \href{https://doi.org/10.1890/070075}{Wild-bird trade and exotic invasions: A new link of conservation concern?} \emph{Frontiers in Ecology and the Environment} \textbf{6}, 207--211 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{C.
-Drews, \href{https://doi.org/10.1163/156853001753639233}{Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers}.
-\emph{Society \& Animals} \textbf{9}, 107--126 (2001).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{D.
-Kelly, E.
-McCarthy, K.
-Menzel, M.
-Engebretson, \href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?} (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{L. Li, Z. Jiang, \href{https://doi.org/10.1371/journal.pone.0085012}{International trade of {CITES} listed bird species in {C}hina}. \emph{PLOS ONE} \textbf{9}, 1--8 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{S.
-Su, P.
-Cassey, M.
-Vall-llosera, T.
-M.
-Blackburn, \href{https://doi.org/10.1371/journal.pone.0127482}{Going cheap: Determinants of bird price in the {T}aiwanese pet market}.
-\emph{PLOS ONE} \textbf{10}, 1--17 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{A.
-M.
-Young, E.
-A.
-Hobson, L.
-B.
-Lackey, T.
-F.
-Wright, \href{https://doi.org/10.1111/j.1469-1795.2011.00477.x}{Survival on the ark: Life-history trends in captive parrots}.
-\emph{Animal Conservation} \textbf{15}, 28--43 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{K.
-Flammer, D.
-Whitt-Smith, M.
-Papich, \href{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}{Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection}.
-\emph{Journal of Avian Medicine and Surgery} \textbf{15}, 276--282 (2001).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{A.
-N.
-Iwaniuk, K.
-M.
-Dean, J.
-E.
-Nelson, Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
-\emph{Brain, Behavior and Evolution} \textbf{65}, 40--59 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{P.
-Mazengenya, A.
-Bhagwandin, P.
-R.
-Manger, A.
-O.
-Ihunwo, \href{https://doi.org/10.3389/fnana.2018.00007}{Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh})}.
-\emph{Frontiers in Neuroanatomy} \textbf{12}, 7 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{S.
-Olkowicz, \emph{et al.}, \href{https://doi.org/10.1073/pnas.1517131113}{Birds have primate-like numbers of neurons in the forebrain}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{113}, 7255--7260 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{C.
-Schuck-Paim, W.
-J.
-Alonso, E.
-B.
-Ottoni, \href{https://doi.org/10.1159/000119710}{Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots}.
-\emph{Brain, Behavior and Evolution} \textbf{71}, 200--215 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{T.
-Silva, A.
-Guzmán, A.
-D.
-Urantówka, P.
-Mackiewicz, \href{https://doi.org/10.7717/peerj.3475}{A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny}.
-\emph{PeerJ} \textbf{5}, e3475 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{H.
-Wilman, \emph{et al.}, EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals (2016) https:/doi.org/\href{https://doi.org/10.6084/m9.figshare.c.3306933.v1}{10.6084/m9.figshare.c.3306933.v1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{W. Jetz, G. H. Thomas, J. B. Joy, K. Hartmann, A. O. Mooers, The global diversity of birds in space and time. \emph{Nature} \textbf{491}, 444--448 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{A. Seed, R. Byrne, \href{https://doi.org/10.1016/j.cub.2010.09.042}{Animal tool-use}. \emph{Current Biology} \textbf{20}, R1032--R1039 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{A. B. Bercovitz, {``Avian sex identification techniques''} in \emph{Companion Bird Medicine}, E. W. Burr, Ed. (Iowa State University Press, 1987).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{J. D. Hoyo, R. Bierregaard, \emph{Handbook of the birds of the world} (Lynx Edicions, 2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{M.
-Amico, I.
-Van Keilegom, \href{https://doi.org/10.1146/annurev-statistics-031017-100101}{Cure models in survival analysis}.
-\emph{Annual Review of Statistics and Its Application} \textbf{5}, 311--342 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{P.
-Schmidt, A.
-D.
-Witte, \href{https://doi.org/10.1016/0304-4076(89)90034-1}{Predicting criminal recidivism using {``split population''} survival time models}.
-\emph{Journal of Econometrics} \textbf{40}, 141--159 (1989).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{A. R. Wallace, \emph{The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature} (MacMillan; Co., 1869).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodall1971}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{J.
-Goodall, {``\href{https://doi.org/10.1016/S0065-3454(08)60157-6}{Tool-using in primates and other vertebrates}''} in Advances in the study of behavior., D.
-S.
-Lehrman, R.
-A.
-Hinde, E.
-Shaw, Eds.
-(Academic Press, 1971), pp.
-195--249.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{S.
-M.
-Reader, K.
-N.
-Laland, \href{https://doi.org/10.1073/pnas.062041299}{Social intelligence, innovation, and enhanced brain size in primates}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{99}, 4436--4441 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{D. Sol, \emph{et al.}, Neuron numbers link innovativeness with both absolute and relative brain size in birds. \emph{Nature Ecology \& Evolution} \textbf{6}, 1381--1389 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{M.
-J.
-Cabrera-Álvarez, N.
-S.
-Clayton, \href{https://doi.org/10.3389/fpsyg.2020.560669}{Neural processes underlying tool use in humans, macaques, and corvids}.
-\emph{Frontiers in Psychology} \textbf{11}, 560669 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{J.
-Henke-von der Malsburg, P.
-M.
-Kappeler, C.
-Fichtel, \href{https://doi.org/10.1098/rspb.2021.1728}{Linking cognition to ecology in wild sympatric mouse lemur species}.
-\emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{288}, 20211728 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{D.
-M.
-Fragaszy, M.
-Mangalam, {``\href{https://doi.org/10.1016/bs.asb.2018.01.001}{Tooling}''} in Advances in the study of behavior., M.
-Naguib, \emph{et al.}, Eds.
-(Academic Press, 2018), pp.
-177--241.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{66. }%
-\CSLRightInline{K.
-Sándor, Á.
-Miklósi, \href{https://doi.org/10.3389/fpsyg.2020.555487}{How to report anecdotal observations?
-A new approach based on a lesson from "puffin tool use"}.
-\emph{Frontiers in Psychology} \textbf{11}, 555487 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
-\CSLLeftMargin{67. }%
-\CSLRightInline{V.
-J.
-Debastiani, V.
-A.
-G.
-Bastazini, V.
-D.
-Pillar, \href{https://doi.org/10.1016/j.ecoinf.2021.101315}{Using phylogenetic information to impute missing functional trait values in ecological databases}.
-\emph{Ecological Informatics} \textbf{63}, 101315 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
-\CSLLeftMargin{68. }%
-\CSLRightInline{G.
-R.
-Hunt, R.
-D.
-Gray, A.
-H.
-Taylor, {``\href{https://doi.org/10.1017/CBO9780511894800.007}{Why is tool use rare in animals?}''} in \emph{Tool Use in Animals: Cognition and Ecology}, C.
-M.
-Sanz, J.
-Call, C.
-Boesch, Eds.
-(Cambridge University Press, 2013), pp.
-89--118.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{J.
-I.
-Benichov, E.
-Globerson, O.
-Tchernichovski, \href{https://doi.org/10.3389/fnhum.2016.00255}{Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans}.
-\emph{Frontiers in Human Neuroscience} \textbf{10} (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
-\CSLLeftMargin{70. }%
-\CSLRightInline{A.
-D.
-Patel, J.
-R.
-Iversen, M.
-R.
-Bregman, I.
-Schulz, \href{https://doi.org/10.1016/j.cub.2009.03.038}{Experimental evidence for synchronization to a musical beat in a nonhuman animal}.
-\emph{Current Biology} \textbf{19}, 827--830 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{C.
-ten Cate, M.
-Spierings, J.
-Hubert, H.
-Honing, \href{https://doi.org/10.3389/fpsyg.2016.00730}{Can birds perceive rhythmic patterns?
-A review and experiments on a songbird and a parrot species}.
-\emph{Frontiers in Psychology} \textbf{7} (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
-\CSLLeftMargin{72. }%
-\CSLRightInline{M.
-Wilson, P.
-F.
-Cook, \href{https://doi.org/10.3758/s13423-016-1013-x}{Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed}.
-\emph{Psychonomic Bulletin \& Review} \textbf{23}, 1647--1659 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
-\CSLLeftMargin{73. }%
-\CSLRightInline{J.
-Eckert, S.
-L.
-Winkler, E.
-A.
-Cartmill, \href{https://doi.org/10.1098/rsbl.2020.0370}{Just kidding: The evolutionary roots of playful teasing}.
-\emph{Biology Letters} \textbf{16}, 20200370 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
-\CSLLeftMargin{74. }%
-\CSLRightInline{J.
-Bro-Jørgensen, W.
-M.
-Pangle, \href{https://doi.org/10.1086/653078}{Male topi antelopes alarm snort deceptively to retain females for mating}.
-\emph{The American Naturalist} \textbf{176}, E33--E39 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
-\CSLLeftMargin{75. }%
-\CSLRightInline{R.
-W.
-Byrne, A.
-Whiten, \href{https://doi.org/10.1017/S0140525X00049955}{Toward the next generation in data quality: A new survey of primate tactical deception}.
-\emph{Behavioral and Brain Sciences} \textbf{11}, 267--273 (1988).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
-\CSLLeftMargin{76. }%
-\CSLRightInline{R.
-W.
-Byrne, A.
-Whiten, {``Computation and mindreading in primate tactical deception''} in \emph{Natural Theories of Mind: Evolution, Development and Simulation of Everyday Mindreading}, A.
-Whiten, Ed.
-(Basil Blackwell, 1991), pp.
-127--141.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
-\CSLLeftMargin{77. }%
-\CSLRightInline{, \href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership} (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
-\CSLLeftMargin{78. }%
-\CSLRightInline{H. J. Jerison, \emph{Evolution of the brain and intelligence} (Academic Press, 1973).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
-\CSLLeftMargin{79. }%
-\CSLRightInline{E.
-Paradis, K.
-Schliep, \href{https://doi.org/10.1093/bioinformatics/bty633}{{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}}.
-\emph{Bioinformatics} \textbf{35}, 526--528 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
-\CSLLeftMargin{80. }%
-\CSLRightInline{R.
-McElreath, \emph{\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition}}, 2nd Ed.
-(CRC Press, 2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
-\CSLLeftMargin{81. }%
-\CSLRightInline{Stan Development Team, \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}} (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
-\CSLLeftMargin{82. }%
-\CSLRightInline{L.
-J.
-Revell, \href{https://doi.org/10.1111/j.2041-210X.2011.00169.x}{{phytools}: An {R} package for phylogenetic comparative biology (and other things)}.
-\emph{Methods in Ecology and Evolution} \textbf{3}, 217--223 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
-\CSLLeftMargin{83. }%
-\CSLRightInline{R Core Team, \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}} (R Foundation for Statistical Computing, 2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
-\CSLLeftMargin{84. }%
-\CSLRightInline{G.
-Yu, D.
-Smith, H.
-Zhu, Y.
-Guan, T.
-T.-Y.
-Lam, \href{https://doi.org/10.1111/2041-210X.12628}{{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data}.
-\emph{Methods in Ecology and Evolution} \textbf{8}, 28--36 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-\CSLLeftMargin{85. }%
-\CSLRightInline{H. Wickham, \emph{\href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis}} (Springer-Verlag New York, 2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
-\CSLLeftMargin{86. }%
-\CSLRightInline{C. O. Wilke, \emph{\href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}} (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
-\CSLLeftMargin{87. }%
-\CSLRightInline{W.
-M.
-Landau, \href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}.
-\emph{Journal of Open Source Software} \textbf{6}, 2959 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
-\CSLLeftMargin{88. }%
-\CSLRightInline{F. Aust, M. Barth, \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}} (2022).}
-
-\end{CSLReferences}
-
-\endgroup
-
-\newpage
-\vspace*{60mm}
-
-\renewcommand{\figurename}{Figure}
-\renewcommand{\tablename}{Table}
-\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
-\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
-\renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}
-
-\hypertarget{supplementary-information}{%
-\section{\texorpdfstring{\textbf{Supplementary Information}}{Supplementary Information}}\label{supplementary-information}}
-
-\setcounter{page}{1}
-\centering
-
-\noindent \hspace*{8mm} \small Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare \newline
-\hspace*{1cm} \small Amalia P. M. Bastos\textsuperscript{1,2}, Scott Claessens\textsuperscript{2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, \newline
-\hspace*{25mm} Quentin D. Atkinson\textsuperscript{2}, Alex H. Taylor\textsuperscript{2,3,5,6} \newline
-
-\raggedright
-
-\noindent \footnotesize \textsuperscript{1} Department of Psychological \& Brain Sciences, Johns Hopkins University, Baltimore, MD, United States \newline
-\noindent \footnotesize \textsuperscript{2} School of Psychology, University of Auckland, Auckland, New Zealand \newline
-\noindent \footnotesize \textsuperscript{3} School of Biological Sciences, University of Canterbury, Christchurch, New Zealand \newline
-\noindent \footnotesize \textsuperscript{4} School of Computer Science, University of Auckland, Auckland, New Zealand \newline
-\noindent \footnotesize \textsuperscript{5} ICREA, Pg. Lluís Companys 23, Barcelona, Spain \newline
-\noindent \footnotesize \textsuperscript{6} Institute of Neuroscience, Universitat Autònoma de Barcelona, Barcelona, Spain \newline
-\normalsize
-\newpage
-
-\hypertarget{supplementary-figures}{%
-\subsection{Supplementary Figures}\label{supplementary-figures}}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure3-1.pdf}
-\caption{\label{fig:plotSurvCure3}\emph{Median posterior probabilities of undetected tool use for each parrot species without observed evidence of tool use from reduced model.} This reduced version of the phylogenetic survival cure model does not contain relative brain size or feeding strategy as predictors, nor does it contain any phylogenetic covariance.
-The only information included in the model is the number of papers published and the number of YouTube search hits for each species.
-Each point is a parrot species without observed evidence of tool use, and the colour of the points scales with the probability of undetected tool use.
-All else being equal, those species with fewer published papers and fewer YouTube search hits have a higher probability of being undetected tool users.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure9-1.pdf}
-\caption{\label{fig:plotSurvCure9}\emph{Receiver operating characteristic (ROC) curve for the phylogenetic survival cure model.} The area-under-the-curve in this plot is 0.95, suggesting that the model is able to adequately classify observed tool users and non-tool users.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure5-1.pdf}
-\caption{\label{fig:plotSurvCure5}\emph{Prior and posterior phylogenetic covariance functions from the Bayesian survival cure model fitted to the full dataset.} Lines are median posterior functions and shaded areas are 50\% and 95\% credible intervals.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure6-1.pdf}
-\caption{\label{fig:plotSurvCure6}\emph{Between-species correlation matrix implied by the posterior phylogenetic covariance function from the Bayesian survival cure model.} Correlations are median posterior estimates.
-Individual species names omitted for space reasons.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotComparison-1.pdf}
-\caption{\label{fig:plotComparison}\emph{Comparing results between the survival cure model and models fitted to the pre-survey and post-survey data without any survival cure component.} Densities are full posterior distributions from three separate models iterated over 100 posterior parrot phylogenies.
-Points represent posterior medians, and lines represent 50\% and 95\% credible intervals.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotASR1-1.pdf}
-\caption{\label{fig:plotASR1}\emph{Results of exploratory ancestral state reconstruction analysis fitted to pre-video-survey data, represented on a maximum clade credibility tree.} Tip nodes represent the presence (red) or absence (grey) of observed tool use in the scientific literature.
-Pie charts represent the posterior probability of tool use presence at each ancestral node.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotASR2-1.pdf}
-\caption{\label{fig:plotASR2}\emph{Results of exploratory ancestral state reconstruction analysis fitted to post-video-survey data, represented on a maximum clade credibility tree.} Tip nodes represent the presence (red) or absence (grey) of observed tool use in the scientific literature and the video survey.
-Pie charts represent the posterior probability of tool use presence at each ancestral node.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotASR3-1.pdf}
-\caption{\label{fig:plotASR3}\emph{Results of exploratory ancestral state reconstruction analysis fitted to predicted probabilities from the phylogenetic survival cure model, represented on a maximum clade credibility tree.} Tip nodes represent the median posterior predicted probabilities of tool use from the phylogenetic survival cure model, with more red indicating an increasing probability of tool use presence and more grey indicating a decreasing probability of tool use presence.
-Pie charts represent the posterior probability of tool use presence at each ancestral node.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotPhylo2-1.pdf}
-\caption{\label{fig:plotPhylo2}\emph{Data on encephalisation quotient and feeding strategy for all parrots, presented on a maximum clade credibility tree.} Tip points are coloured according to feeding generalism (orange) and specialism (blue), and scaled according to encephalisation quotient (EQ).}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotPhylo3-1.pdf}
-\caption{\label{fig:plotPhylo3}\emph{Data on number of scientific publications until tool use discovery for all parrots, presented on a maximum clade credibility tree.} Tip points are scaled according to the number of published papers up until tool use discovery (or, if tool use has not been observed, the current number of published papers).}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotPhylo4-1.pdf}
-\caption{\label{fig:plotPhylo4}\emph{Data on number of video search hits until tool use discovery for all parrots, presented on a maximum clade credibility tree.} Tip points are scaled according to the estimated number of video search hits up until tool use discovery (or, if tool use has not been observed, the current number of video search hits).}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure7-1.pdf}
-\caption{\label{fig:plotSurvCure7}\emph{Prior predicted probabilities of tool use for each species from our phylogenetic survival cure model.} Points are prior medians and lines are 50\% and 95\% credible intervals.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure8-1.pdf}
-\caption{\label{fig:plotSurvCure8}\emph{Results of sensitivity analysis.} The phylogenetic survival cure model was fitted with either a standard Normal(0, 1) prior on the intercept or an alternative Normal(1.78507, 2) prior on the intercept.
-This latter prior is wider on the logit scale and roughly converts to a 0.86 prior probability of non-tool-use (or a 0.14 prior probability of tool-use, which is the proportion of tool users in the dataset).
-The sensitivity analysis showed that changing this intercept prior did not have a marked impact on (a) the posterior rankings of parrot species from 1st to 174th or (b) the median posterior probabilities of tool use for parrot species.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotTrace-1.pdf}
-\caption{\label{fig:plotTrace}\emph{Trace plots for the Bayesian phylogenetic survival cure model.} Only four chains are shown for ease of presentation.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCureSim-1.pdf}
-\caption{\label{fig:plotSurvCureSim}\emph{Posterior estimates from Bayesian survival cure models fitted to 100 datasets simulated with known parameters.} Each dataset consisted of 100 species.
-Known parameters are presented as solid vertical lines, whereas points and horizontal lines represent posterior medians and 95\% credible intervals.
-The models were successfully able to recapture the parameters from the simulated datasets.}
-\end{figure}
-
-\end{document}
+https://github.com/ScottClaessens/phyloParrot

### 2024-07-12 R/functionsDAG.R

@@ -35,7 +35,7 @@ drawDAG <- function() {
   out <-
     out +
     geom_dag_point(
-      data = function(x) filter(x, name %in% c("Tool use\n(unobserved)", "Unobserved\nconfounds")),
+      data = function(x) dplyr::filter(x, name %in% c("Tool use\n(unobserved)", "Unobserved\nconfounds")),
       alpha = 0.5, size = 35, show.legend = FALSE, colour = "lightgrey"
     ) +
     geom_dag_text(colour = "black") +

### 2024-07-12 _targets.R

@@ -53,7 +53,7 @@ list(
   tar_target(MCCphylogeny, mcc(phylogeny)),
   # load crowdsourcing data
   tar_target(crowdsourcing_file, "data/parrotToolUseYoutubeSurveyData.xlsx"),
-  tar_target(crowdData, read_xlsx(crowdsourcing_file, sheet = 1)),
+  tar_target(crowdData, read_xlsx(crowdsourcing_file, sheet = 1, range = "A1:O117")),
   # load data
   tar_target(data_file, "data/parrotData.csv", format = "file"),
   tar_target(litCount_file, "data/parrotLiteratureSearch.csv", format = "file"),

### 2024-08-19 manuscript.Rmd
revise manuscript

@@
 ---
-title             : "Digital video platforms and phylogenetic modelling reveal parrot tool use is not rare"
+title             : "Evidence of self-care tooling on digital video platforms and phylogenetic modelling reveal parrot tool use is not rare"
 shorttitle        : "Parrot tool use"
@@
 Here, we tackle this challenge by combining data from digital platforms and phylogenetic modelling to estimate actual rates of tool use in parrots.
-Videos on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%).
-Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11% and 17% of extant parrot species may be tool users.
+Videos on a social media platform revealed novel instances of self-care tooling in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3%) to 28 (7%).
+Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11% and 17% of extant parrot species may be capable of tool use.
 These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait.
@@
 use thus provides an ideal test case for examining how robust sampling is in the 
-scientific literature. Second, parrots are highly popular as pets. Over 70% of 
-all extant parrot species are bred in the aviculture industry and kept as pets 
+scientific literature. Second, parrots are popular as pets. Over 70% of all 
+extant parrot species are bred in the aviculture industry and kept as pets 
 worldwide [@Anderson2003;@Carrete2008;@Drews2001;@Kelly2014;@Li2014;@Su2015;
@@
 We first present the results from our video survey, in which we collated videos
-of tool use in parrots from a digital video platform. This survey reveals a 
-number of previously unidentified tool-using parrot species, which we map onto 
-the phylogeny of the parrot order. We then describe our statistical model in 
-more detail, and use it to (_i_) rank further parrot species that are likely 
-unobserved tool users and (_ii_) re-examine key hypotheses regarding the 
-evolutionary drivers and origins of tool use in parrots.
+of tool use in parrots from a digital video platform. This survey reveals that a
+number of parrots not previously known to use tools are capable of self-care 
+tooling. We then map these previously unidentified tool-using species onto the
+phylogeny of the parrot order and use a phylogenetic survival cure model to 
+(_i_) rank further parrot species that are likely unobserved tool users and 
+(_ii_) re-examine key hypotheses regarding the evolutionary drivers and origins
+of tool use in parrots.
 
@@
 
-## Digital video platform reveals tool use in additional parrot species
+## Digital video platform reveals self-care tool use in additional parrot species
 
@@
 `r bordCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` 
-species). All videos featured pet parrots in captive settings. In 
+species). All videos featured pet parrots in captive settings performing
+self-care tool use, specifically self-scratching. In 
 `r crowdData %>% pull(HumanInfluence) %>% str_starts("No") %>% sum()` of these 
@@
 Of the `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` 
-parrot species performing true tool use, 
+parrot species performing true tool use for self-care, 
 `r trueCrowdData %>% filter(Species != "Unknown") %>% group_by(Species, IndividualID) %>% summarise(n = n(), .groups = "drop") %>% group_by(Species) %>% summarise(check = n() > 1, .groups = "drop") %>% pull(check) %>% sum()`
@@
 `r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Male"))` 
-of the individuals performing true tool use were males and 
+of the individuals performing true tool use for self-care were males and 
 `r trueCrowdData %>% group_by(IndividualID, Sex) %>% summarise(.groups = "drop") %>% pull(Sex) %>% (function(x) sum(x == "Female"))` 
@@
 male when they have not been genetically tested, owners being more likely to own 
-or film male parrots, or male parrots exhibiting more true tool use behaviours 
+or film male parrots, or male parrots exhibiting more self-scratching behaviours 
 than female parrots.
@@
 survey, 11 parrot species (3%) had been identified as tool users in the 
-scientific literature. Across our video survey, we observed true tool use in 
+scientific literature. Across our video survey, we observed true tool use for self-care in 
 `r trueCrowdData %>% filter(Species != "Unknown") %>% pull(Species) %>% unique() %>% length()` 
@@
 species. Combining both the video survey and the scientific literature, we can 
-thus identify 28 tool-using parrot species overall (7%), compared to the 11 
-previously reported.
+thus identify 28 total parrot species (7%) capable of true tool use as defined 
+by ref [@Shumaker2011], compared to the 11 previously reported.
 
@@
 
-The identification of new tool-using species in our video survey increases the 
-extent to which phylogeny can explain the distribution of tool use in the parrot 
-order. We estimated phylogenetic signal (Pagel's $\lambda$) of tool use using 
-both the pre-video-survey and post-video-survey data. Pagel's $\lambda$ varies 
-between 0 and 1, where 0 implies that the distribution of a trait across species 
-is unexplained by phylogenetic relatedness and 1 implies that the distribution 
-of a trait across species is fully explained by phylogeny. Using the evidence of 
-tool use from the scientific literature alone (pre-video-survey data; 11 
-tool-using species), we estimated an average posterior Pagel's $\lambda$ of 
+The identification of self-care tooling behaviours in several new parrot species
+in our video survey increases the extent to which phylogeny can explain the 
+distribution of a cognitive capacity for tool use in the parrot order. We 
+estimated the phylogenetic signal (Pagel's $\lambda$) of tool use using both the
+pre-video-survey and post-video-survey data. Pagel's $\lambda$ varies between 0 
+and 1, where 0 implies that the distribution of a trait across species is 
+unexplained by phylogenetic relatedness and 1 implies that the distribution of a 
+trait across species is fully explained by phylogeny. Using the evidence of tool
+use from the scientific literature alone (pre-video-survey data; 11 tool-using 
+species), we estimated an average posterior Pagel's $\lambda$ of 
 `r printnum(mean(tar_read(phySignal1)))` (95% credible interval [`r printnum(quantile(tar_read(phySignal1), 0.025))` 
@@
 `r nrow(tar_read(d))` species). Thus, the results of our video survey increase 
-the extent to which the distribution of tool use across parrot species can be 
-explained by shared phylogenetic ancestry. This suggests that we can potentially 
-use phylogenetic information, along with other variables, to identify further 
-tool-using parrot species that may remain undetected.
+the extent to which the distribution of tool use capabilities across parrot 
+species can be explained by shared phylogenetic ancestry. This suggests that we
+can potentially use phylogenetic information, along with other variables, to 
+identify further parrot species that are capable of tool use but have remained 
+undetected.
 
@@
 
-In addition to the 28 tool-using species identified in the literature and our 
-video survey, we fitted a Bayesian phylogenetic survival cure model to rank 
-further species that are likely to be undetected tool-users (i.e., tool-using 
-species with no tool use reported in the literature or in videos).
+If we combine evidence from both the literature and our video survey, 28 parrot
+species in total have demonstrated a capacity for some form of tool use, whether
+that be self-care tool use in captivity, tool use in a wild foraging context, or
+other tool behaviours that fit the criteria for true tool use [@Shumaker2011].
+By analysing these observations alongside data on relative brain size, feeding
+strategy, and phylogenetic ancestry, we can (_i_) identify which parrot species
+without recorded evidence of tool use are most likely to have a capacity for 
+tool use that has as yet gone unobserved, and (_ii_) test theories about the 
+evolutionary drivers and origins of technical intelligence in the parrot order.
+To this end, we fitted a Bayesian phylogenetic survival cure model to the data
+on parrot tool use from both the literature and our video survey.
 
@@
 specifically, the amount of "time" (i.e., observation opportunities measured as 
-the number of published papers or videos) until tool use is identified. This is
-right-censored data because many species will not have had tool use identified
-when we measure them. Moreover, we can assume that a certain proportion of the
-population will never experience the event -- that is, they are a non-tool-user
-and so we will never identify tool use no matter how long we measure them for.
+the number of published papers or videos) until the capacity for tool use is 
+identified in some form of tool use behaviour. This is right-censored data 
+because many species will not have had tool use identified when we measure them.
+Moreover, we can assume that a certain proportion of the population will never
+experience the event -- that is, they do not have the capacity for tool use and
+so we will never observe tool use behaviour no matter how long we measure them
+for.
 
@@
 estimated with uncertainty, so it is difficult to "identify" any particular 
-species as an undetected tool user. Nevertheless, taking the sum of all the 
-posterior probabilities for the 
+species as having an undetected capacity for tool use. Nevertheless, taking the
+sum of all the posterior probabilities for the 
 `r nrow(plotSurvCure1$data %>% filter(ToolUse == "Absent"))` species without 
@@
 users in the scientific literature. Our study collated data from a digital video
-platform to identify 17 additional tool-using parrot species that are new to 
-science, more than doubling the overall count to 28 species (7%). These species 
-consisted of cockatoos (_Cacatuidae_), Old World parrots (_Psittacinae_), and 
-neotropical parrots (_Arinae_). Beyond the video survey, the strong 
-phylogenetic signal in our dataset allowed us to use phylogenetic information, 
-along with other variables, to infer the unobserved probabilities of tool use 
-across the parrot order. Our phylogenetic survival cure model incorporated
-information on phylogenetic history, research effort, relative brain size, and 
-feeding specialisation to rank parrot species that were most likely to be 
-undetected tool users. The sum of probabilities from this model implied that 
-between 15 and 41 of the species without observed evidence of tool use are 
-likely to be undetected tool users, suggesting that the true proportion of tool
-users may be as high as 17%.
+platform and revealed capabilities for self-care tool use in 17 additional 
+parrot species, more than doubling the overall count of tool-using parrots to 
+28 species (7%). These species consisted of cockatoos (_Cacatuidae_), Old World
+parrots (_Psittacinae_), and neotropical parrots (_Arinae_). Beyond the video 
+survey, the strong phylogenetic signal in our dataset allowed us to use 
+phylogenetic information, along with other variables, to infer the unobserved
+probabilities of tool use across the parrot order. Our phylogenetic survival
+cure model incorporated information on phylogenetic history, research effort, 
+relative brain size, and feeding specialisation to rank parrot species that were
+most likely to be undetected tool users. The sum of probabilities from this 
+model implied that between 15 and 41 of the species without evidence of tool use
+are likely to have an unobserved capacity for tool use, suggesting that the true
+proportion of tool users in the parrot order may be as high as 17%.
 
-These findings have a number of important implications. First, our findings show 
+All instances of tool use in our video survey met the established criteria for 
+tool use in the literature: the manipulation of an unattached object as an 
+extension of the animal's body to achieve a goal [@Shumaker2011]. However, a 
+striking feature of the dataset is that the 17 additional species identified in
+the video survey were exclusively observed using tools for self-scratching.
+While parrots in the wild use tools to achieve a variety of goals, including 
+extractive foraging and courtship [@Goodman2018;@Heinsohn2017;@OHara2021;
+@Wood1984], parrots in captivity rarely ever require tools in an environment 
+where food is readily available and there is little or no competition for mates.
+Instead, the most commonly observed form of tool use in captive parrots is 
+self-scratching. It could be argued that self-scratching is a more cognitively 
+simple form of tool use than extractive foraging as it is egocentric, meaning 
+that the tool is directed towards oneself rather than an external object. 
+Nevertheless, self-scratching meets the definition for a more complex type of 
+embodied tool use known as 'tooling', the deliberate generation of a mechanical 
+interface by using an object to manipulate another target or surface 
+[@Fragaszy2018]. In our dataset, most self-scratching tooling instances involved 
+manipulating the tool while keeping the body still, suggesting that these were 
+goal-directed, deliberate movements by individuals. Moreover, the fact that we 
+found strong phylogenetic clustering of self-scratching tool use from the video 
+survey with other examples of tool use from the literature supports a common 
+underlying cognitive mechanism. In line with this, some of the species of 
+parrots that use tools for self-scratching in captivity also use tools for other 
+purposes in the wild [@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021]. For 
+these reasons, we believe that self-care tool use in captivity is no less 
+indicative of a cognitive capacity for tool use than other tool behaviours in 
+the wild or in captivity. Indeed, if this is not the case, then the field will 
+need to re-evaluate current working definitions of true tool use and their 
+implications for animal cognition. This justifies our use of self-scratching, 
+alongside other wild observations of tool use, to make claims about the 
+evolutionary drivers and origins of technical intelligence in the parrot order.
+
+Our data raise the question of why such a wide range of parrot species exhibit 
+self-scratching tool use behaviours in captive environments. It is possible that 
+these self-care behaviours emerge more often in captivity because pet parrots 
+are kept with few or no conspecifics, and therefore must innovate tool use to 
+preen inaccessible body areas, such as their heads and necks, which would have 
+been otherwise preened by flock members. This may indicate that human 
+interaction and allopreening in the absence of a conspecific is insufficient for
+pet parrots, as suggested by studies on welfare and chronic stress in lone 
+captive parrots [@Aydinonat2014;@Engebretson2006;@Mason2010;@Meehan2003]. Beyond 
+social isolation in captivity, other factors that reduce preening efficacy by an 
+individual might also lead to the innovation of self-care tooling: for example,
+a captive kea housed with conspecifics in a naturalistic environment was shown
+to have innovated the use of a pebble tool for self-care likely as a consequence 
+of a missing upper mandible [@Bastos2021]. These behaviours might therefore be 
+innovated by individuals when ecologically necessary. Critically, however, a 
+capacity to innovate a behaviour such as tool use must exist in a species in 
+order to manifest in any environment, whether that be captive or in the wild. 
+The fact that only a subset of parrot species are innovating self-care tooling 
+in response to their captive setting and that self-care tooling is predicted by 
+phylogenetic history and encephalisation strongly suggests that self-scratching 
+indicates a capacity to produce tool use, which is expressed in different ways 
+in captive and wild settings.
+
+Our findings have a number of important implications. First, our findings show 
 that current research effort in the scientific literature is insufficient to 
@@
 
-All instances of tool use in our video survey met the established criteria for 
-tool use in the literature: the manipulation of an unattached object as an 
-extension of the animal's body to achieve a goal [@Shumaker2011]. However, a 
-striking feature of the dataset is that the 17 additional species identified in
-the video survey were exclusively observed using tools for self-scratching.
-While parrots in the wild use tools to achieve a variety of goals, including 
-extractive foraging and preening [@Goodman2018;@OHara2021], parrots in captivity
-only require tools to achieve the latter goal. It could be argued that 
-self-scratching is a more cognitively simplistic form of tool use than 
-extractive foraging as it is egocentric, meaning that the tool is directed 
-towards oneself rather than an external object. Nevertheless, self-scratching 
-meets the definition for a more complex type of embodied tool use known as 
-'tooling', the deliberate generation of a mechanical interface by using an 
-object to manipulate another target or surface [@Fragaszy2018]. In our dataset, 
-most self-scratching tooling instances involved manipulating the tool while 
-keeping the body still, suggesting that these were goal-directed, deliberate 
-movements by individuals. This makes it difficult to dismiss self-scratching as 
-unimportant: to do so would require a redefinition of tool-use and tooling in 
-non-human animals. Moreover, the fact that we found strong phylogenetic 
-clustering of self-scratching tool use from the video survey with other examples 
-of tool use from the literature supports a common underlying cognitive 
-mechanism. In line with this, some of the species of parrots that use tools for 
-self-scratching in captivity also use tools for other purposes in the wild 
-[@Auersperg2012;@Bastos2021;@Goodman2018;@OHara2021].
-
 A potential concern with data originating from digital video platforms is its 
@@
 
-Our data reveals that a wide range of parrot species exhibit self-scratching 
-tool use behaviours in captive environments. It is possible that these self-care 
-behaviours emerge more often in captivity because pet parrots are kept with few 
-or no conspecifics, and therefore must innovate tool use to preen inaccessible 
-body areas, such as their heads and necks, which would have been otherwise 
-preened by flock members. This may indicate that human interaction and 
-allopreening in the absence of a conspecific is insufficient for pet parrots, as 
-suggested by studies on welfare and chronic stress in lone captive parrots 
-[@Aydinonat2014;@Engebretson2006;@Mason2010;@Meehan2003]. Beyond social 
-isolation in captivity, other factors that reduce preening efficacy by an 
-individual might also lead to the innovation of self-care tooling: for example,
-a captive kea housed with conspecifics in a naturalistic environment was shown
-to have innovated the use of a pebble tool for self-care likely as a consequence 
-of a missing upper mandible [@Bastos2021]. These behaviours might therefore be 
-innovated by individuals when ecologically necessary. Critically, however, a 
-cognitive capacity to innovate a behaviour such as tool use must exist in a 
-species in order to manifest in any environment, whether that be captive or in 
-the wild. As such, despite differences in individuals' life experiences in 
-captive and wild settings, such behaviour emerging in a captive setting at the 
-very least indicates an underlying cognitive capacity to innovate that same 
-behaviour in the wild.
-
 While missing data imputation is becoming more common in phylogenetic 
@@
 captured the full distribution of tool use in the parrot order. Our 
-digital video survey more than doubled the number of known tool using parrot 
-species from 11 to 28, and our phylogenetic model suggested that the true 
+digital video survey identified novel observations of self-care tool use in 
+several parrot species, more than doubling the number of known tool using parrot 
+species from 11 to 28. Our phylogenetic model suggested that the true 
 proportion of parrot tool users could be as high as 17% of all species in this 

### 2024-08-19 manuscript.tex
revise manuscript

@@
 \usepackage{amsmath,amssymb}
+\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
+\urlstyle{same} % disable monospaced font for URLs
 \hypersetup{
-  pdftitle={Digital video platforms and phylogenetic modelling reveal parrot tool use is not rare},
+  pdftitle={Evidence of self-care tooling on digital video platforms and phylogenetic modelling reveal parrot tool use is not rare},
   pdfauthor={Amalia P. M. Bastos†,1,2, Scott Claessens*†,2, Ximena J. Nelson3, David Welch4, Quentin D. Atkinson‡,2, \& Alex H. Taylor‡,2,3,5,6},
@@
 
-\title{Digital video platforms and phylogenetic modelling reveal parrot tool use is not rare}
+\title{Evidence of self-care tooling on digital video platforms and phylogenetic modelling reveal parrot tool use is not rare}
 \author{Amalia P.
@@
 Here, we tackle this challenge by combining data from digital platforms and phylogenetic modelling to estimate actual rates of tool use in parrots.
-Videos on a social media platform revealed novel instances of tool use in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
-Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11\% and 17\% of extant parrot species may be tool users.
+Videos on a social media platform revealed novel instances of self-care tooling in 17 parrot species, more than doubling the confirmed number of tool-using parrot species from 11 (3\%) to 28 (7\%).
+Phylogenetic modelling ranked additional species that are most likely to be unobserved tool users, suggesting that between 11\% and 17\% of extant parrot species may be capable of tool use.
 These discoveries have implications for inferences about the evolutionary drivers and origins of tool use in parrots, revealing associations with relative brain size and feeding generalism and indicating several genera where tool use was likely an ancestral trait.
@@
 use thus provides an ideal test case for examining how robust sampling is in the
-scientific literature. Second, parrots are highly popular as pets. Over 70\% of
-all extant parrot species are bred in the aviculture industry and kept as pets
+scientific literature. Second, parrots are popular as pets. Over 70\% of all
+extant parrot species are bred in the aviculture industry and kept as pets
 worldwide\textsuperscript{39--45}, enabling us to leverage the power of digital video platforms to
@@
 We first present the results from our video survey, in which we collated videos
-of tool use in parrots from a digital video platform. This survey reveals a
-number of previously unidentified tool-using parrot species, which we map onto
-the phylogeny of the parrot order. We then describe our statistical model in
-more detail, and use it to (\emph{i}) rank further parrot species that are likely
-unobserved tool users and (\emph{ii}) re-examine key hypotheses regarding the
-evolutionary drivers and origins of tool use in parrots.
+of tool use in parrots from a digital video platform. This survey reveals that a
+number of parrots not previously known to use tools are capable of self-care
+tooling. We then map these previously unidentified tool-using species onto the
+phylogeny of the parrot order and use a phylogenetic survival cure model to
+(\emph{i}) rank further parrot species that are likely unobserved tool users and
+(\emph{ii}) re-examine key hypotheses regarding the evolutionary drivers and origins
+of tool use in parrots.
 
@@
 
-\hypertarget{digital-video-platform-reveals-tool-use-in-additional-parrot-species}{%
-\subsection{Digital video platform reveals tool use in additional parrot species}\label{digital-video-platform-reveals-tool-use-in-additional-parrot-species}}
+\hypertarget{digital-video-platform-reveals-self-care-tool-use-in-additional-parrot-species}{%
+\subsection{Digital video platform reveals self-care tool use in additional parrot species}\label{digital-video-platform-reveals-self-care-tool-use-in-additional-parrot-species}}
 
@@
 7
-species). All videos featured pet parrots in captive settings. In
+species). All videos featured pet parrots in captive settings performing
+self-care tool use, specifically self-scratching. In
 68 of these
@@
 Of the 22
-parrot species performing true tool use,
+parrot species performing true tool use for self-care,
 13
@@
 45
-of the individuals performing true tool use were males and
+of the individuals performing true tool use for self-care were males and
 18
@@
 male when they have not been genetically tested, owners being more likely to own
-or film male parrots, or male parrots exhibiting more true tool use behaviours
+or film male parrots, or male parrots exhibiting more self-scratching behaviours
 than female parrots.
@@
 survey, 11 parrot species (3\%) had been identified as tool users in the
-scientific literature. Across our video survey, we observed true tool use in
+scientific literature. Across our video survey, we observed true tool use for self-care in
 22
@@
 species. Combining both the video survey and the scientific literature, we can
-thus identify 28 tool-using parrot species overall (7\%), compared to the 11
-previously reported.
+thus identify 28 total parrot species (7\%) capable of true tool use as defined
+by ref\textsuperscript{10}, compared to the 11 previously reported.
 
@@
 
-The identification of new tool-using species in our video survey increases the
-extent to which phylogeny can explain the distribution of tool use in the parrot
-order. We estimated phylogenetic signal (Pagel's \(\lambda\)) of tool use using
-both the pre-video-survey and post-video-survey data. Pagel's \(\lambda\) varies
-between 0 and 1, where 0 implies that the distribution of a trait across species
-is unexplained by phylogenetic relatedness and 1 implies that the distribution
-of a trait across species is fully explained by phylogeny. Using the evidence of
-tool use from the scientific literature alone (pre-video-survey data; 11
-tool-using species), we estimated an average posterior Pagel's \(\lambda\) of
+The identification of self-care tooling behaviours in several new parrot species
+in our video survey increases the extent to which phylogeny can explain the
+distribution of a cognitive capacity for tool use in the parrot order. We
+estimated the phylogenetic signal (Pagel's \(\lambda\)) of tool use using both the
+pre-video-survey and post-video-survey data. Pagel's \(\lambda\) varies between 0
+and 1, where 0 implies that the distribution of a trait across species is
+unexplained by phylogenetic relatedness and 1 implies that the distribution of a
+trait across species is fully explained by phylogeny. Using the evidence of tool
+use from the scientific literature alone (pre-video-survey data; 11 tool-using
+species), we estimated an average posterior Pagel's \(\lambda\) of
 0.60 (95\% credible interval {[}0.00
@@
 174 species). Thus, the results of our video survey increase
-the extent to which the distribution of tool use across parrot species can be
-explained by shared phylogenetic ancestry. This suggests that we can potentially
-use phylogenetic information, along with other variables, to identify further
-tool-using parrot species that may remain undetected.
+the extent to which the distribution of tool use capabilities across parrot
+species can be explained by shared phylogenetic ancestry. This suggests that we
+can potentially use phylogenetic information, along with other variables, to
+identify further parrot species that are capable of tool use but have remained
+undetected.
 
@@
 
-In addition to the 28 tool-using species identified in the literature and our
-video survey, we fitted a Bayesian phylogenetic survival cure model to rank
-further species that are likely to be undetected tool-users (i.e., tool-using
-species with no tool use reported in the literature or in videos).
+If we combine evidence from both the literature and our video survey, 28 parrot
+species in total have demonstrated a capacity for some form of tool use, whether
+that be self-care tool use in captivity, tool use in a wild foraging context, or
+other tool behaviours that fit the criteria for true tool use\textsuperscript{10}.
+By analysing these observations alongside data on relative brain size, feeding
+strategy, and phylogenetic ancestry, we can (\emph{i}) identify which parrot species
+without recorded evidence of tool use are most likely to have a capacity for
+tool use that has as yet gone unobserved, and (\emph{ii}) test theories about the
+evolutionary drivers and origins of technical intelligence in the parrot order.
+To this end, we fitted a Bayesian phylogenetic survival cure model to the data
+on parrot tool use from both the literature and our video survey.
 
@@
 specifically, the amount of ``time'' (i.e., observation opportunities measured as
-the number of published papers or videos) until tool use is identified. This is
-right-censored data because many species will not have had tool use identified
-when we measure them. Moreover, we can assume that a certain proportion of the
-population will never experience the event -- that is, they are a non-tool-user
-and so we will never identify tool use no matter how long we measure them for.
+the number of published papers or videos) until the capacity for tool use is
+identified in some form of tool use behaviour. This is right-censored data
+because many species will not have had tool use identified when we measure them.
+Moreover, we can assume that a certain proportion of the population will never
+experience the event -- that is, they do not have the capacity for tool use and
+so we will never observe tool use behaviour no matter how long we measure them
+for.
 
@@
 estimated with uncertainty, so it is difficult to ``identify'' any particular
-species as an undetected tool user. Nevertheless, taking the sum of all the
-posterior probabilities for the
+species as having an undetected capacity for tool use. Nevertheless, taking the
+sum of all the posterior probabilities for the
 149 species without
@@
 users in the scientific literature. Our study collated data from a digital video
-platform to identify 17 additional tool-using parrot species that are new to
-science, more than doubling the overall count to 28 species (7\%). These species
-consisted of cockatoos (\emph{Cacatuidae}), Old World parrots (\emph{Psittacinae}), and
-neotropical parrots (\emph{Arinae}). Beyond the video survey, the strong
-phylogenetic signal in our dataset allowed us to use phylogenetic information,
-along with other variables, to infer the unobserved probabilities of tool use
-across the parrot order. Our phylogenetic survival cure model incorporated
-information on phylogenetic history, research effort, relative brain size, and
-feeding specialisation to rank parrot species that were most likely to be
-undetected tool users. The sum of probabilities from this model implied that
-between 15 and 41 of the species without observed evidence of tool use are
-likely to be undetected tool users, suggesting that the true proportion of tool
-users may be as high as 17\%.
-
-These findings have a number of important implications. First, our findings show
+platform and revealed capabilities for self-care tool use in 17 additional
+parrot species, more than doubling the overall count of tool-using parrots to
+28 species (7\%). These species consisted of cockatoos (\emph{Cacatuidae}), Old World
+parrots (\emph{Psittacinae}), and neotropical parrots (\emph{Arinae}). Beyond the video
+survey, the strong phylogenetic signal in our dataset allowed us to use
+phylogenetic information, along with other variables, to infer the unobserved
+probabilities of tool use across the parrot order. Our phylogenetic survival
+cure model incorporated information on phylogenetic history, research effort,
+relative brain size, and feeding specialisation to rank parrot species that were
+most likely to be undetected tool users. The sum of probabilities from this
+model implied that between 15 and 41 of the species without evidence of tool use
+are likely to have an unobserved capacity for tool use, suggesting that the true
+proportion of tool users in the parrot order may be as high as 17\%.
+
+All instances of tool use in our video survey met the established criteria for
+tool use in the literature: the manipulation of an unattached object as an
+extension of the animal's body to achieve a goal\textsuperscript{10}. However, a
+striking feature of the dataset is that the 17 additional species identified in
+the video survey were exclusively observed using tools for self-scratching.
+While parrots in the wild use tools to achieve a variety of goals, including
+extractive foraging and courtship\textsuperscript{34,35,38,61}, parrots in captivity rarely ever require tools in an environment
+where food is readily available and there is little or no competition for mates.
+Instead, the most commonly observed form of tool use in captive parrots is
+self-scratching. It could be argued that self-scratching is a more cognitively
+simple form of tool use than extractive foraging as it is egocentric, meaning
+that the tool is directed towards oneself rather than an external object.
+Nevertheless, self-scratching meets the definition for a more complex type of
+embodied tool use known as `tooling', the deliberate generation of a mechanical
+interface by using an object to manipulate another target or surface\textsuperscript{62}. In our dataset, most self-scratching tooling instances involved
+manipulating the tool while keeping the body still, suggesting that these were
+goal-directed, deliberate movements by individuals. Moreover, the fact that we
+found strong phylogenetic clustering of self-scratching tool use from the video
+survey with other examples of tool use from the literature supports a common
+underlying cognitive mechanism. In line with this, some of the species of
+parrots that use tools for self-scratching in captivity also use tools for other
+purposes in the wild\textsuperscript{30,31,34,38}. For
+these reasons, we believe that self-care tool use in captivity is no less
+indicative of a cognitive capacity for tool use than other tool behaviours in
+the wild or in captivity. Indeed, if this is not the case, then the field will
+need to re-evaluate current working definitions of true tool use and their
+implications for animal cognition. This justifies our use of self-scratching,
+alongside other wild observations of tool use, to make claims about the
+evolutionary drivers and origins of technical intelligence in the parrot order.
+
+Our data raise the question of why such a wide range of parrot species exhibit
+self-scratching tool use behaviours in captive environments. It is possible that
+these self-care behaviours emerge more often in captivity because pet parrots
+are kept with few or no conspecifics, and therefore must innovate tool use to
+preen inaccessible body areas, such as their heads and necks, which would have
+been otherwise preened by flock members. This may indicate that human
+interaction and allopreening in the absence of a conspecific is insufficient for
+pet parrots, as suggested by studies on welfare and chronic stress in lone
+captive parrots\textsuperscript{63--66}. Beyond
+social isolation in captivity, other factors that reduce preening efficacy by an
+individual might also lead to the innovation of self-care tooling: for example,
+a captive kea housed with conspecifics in a naturalistic environment was shown
+to have innovated the use of a pebble tool for self-care likely as a consequence
+of a missing upper mandible\textsuperscript{31}. These behaviours might therefore be
+innovated by individuals when ecologically necessary. Critically, however, a
+capacity to innovate a behaviour such as tool use must exist in a species in
+order to manifest in any environment, whether that be captive or in the wild.
+The fact that only a subset of parrot species are innovating self-care tooling
+in response to their captive setting and that self-care tooling is predicted by
+phylogenetic history and encephalisation strongly suggests that self-scratching
+indicates a capacity to produce tool use, which is expressed in different ways
+in captive and wild settings.
+
+Our findings have a number of important implications. First, our findings show
 that current research effort in the scientific literature is insufficient to
@@
 tool use in our phylogenetic model, supporting previous theories linking
-relative brain size to increased tool innovation in birds\textsuperscript{12--14} and primates\textsuperscript{61}. We acknowledge that
+relative brain size to increased tool innovation in birds\textsuperscript{12--14} and primates\textsuperscript{67}. We acknowledge that
 encephalisation quotient is not a perfect measure due to measurement error and
@@
 quotient has much greater coverage across the parrot phylogeny than more
-fine-grained measures like whole neuron count\textsuperscript{62} and there is no reason
+fine-grained measures like whole neuron count\textsuperscript{68} and there is no reason
 to think that measurement error would produce the consistent patterns across our
@@
 relationships, we encourage further work on the specific neural correlates of
-technical intelligence in parrots, e.g.,\textsuperscript{63}. In our phylogenetic
+technical intelligence in parrots, e.g.,\textsuperscript{69}. In our phylogenetic
 model, we also found that tool use was somewhat more likely among feeding
@@
 abilities and technical innovation rates are required to expand a generalist
-species' dietary niche\textsuperscript{18,20,64}. However, the trend contradicts theories linking tool use to
+species' dietary niche\textsuperscript{18,20,70}. However, the trend contradicts theories linking tool use to
 dietary specialisation, whereby species eating specific foods that require
@@
 
-All instances of tool use in our video survey met the established criteria for
-tool use in the literature: the manipulation of an unattached object as an
-extension of the animal's body to achieve a goal\textsuperscript{10}. However, a
-striking feature of the dataset is that the 17 additional species identified in
-the video survey were exclusively observed using tools for self-scratching.
-While parrots in the wild use tools to achieve a variety of goals, including
-extractive foraging and preening\textsuperscript{34,38}, parrots in captivity
-only require tools to achieve the latter goal. It could be argued that
-self-scratching is a more cognitively simplistic form of tool use than
-extractive foraging as it is egocentric, meaning that the tool is directed
-towards oneself rather than an external object. Nevertheless, self-scratching
-meets the definition for a more complex type of embodied tool use known as
-`tooling', the deliberate generation of a mechanical interface by using an
-object to manipulate another target or surface\textsuperscript{65}. In our dataset,
-most self-scratching tooling instances involved manipulating the tool while
-keeping the body still, suggesting that these were goal-directed, deliberate
-movements by individuals. This makes it difficult to dismiss self-scratching as
-unimportant: to do so would require a redefinition of tool-use and tooling in
-non-human animals. Moreover, the fact that we found strong phylogenetic
-clustering of self-scratching tool use from the video survey with other examples
-of tool use from the literature supports a common underlying cognitive
-mechanism. In line with this, some of the species of parrots that use tools for
-self-scratching in captivity also use tools for other purposes in the wild\textsuperscript{30,31,34,38}.
-
 A potential concern with data originating from digital video platforms is its
-reliability\textsuperscript{23,66--70}.
+reliability\textsuperscript{23,71--75}.
 In particular, the self-care tool use instances detected in our video survey
@@
 repetitively over long periods of time, even across multiple different videos,
-suggesting that their behaviour was not random or accidental\textsuperscript{69}.
+suggesting that their behaviour was not random or accidental\textsuperscript{74}.
 Parrots preferentially employed self-scratching tools on areas of their body
@@
 
-Our data reveals that a wide range of parrot species exhibit self-scratching
-tool use behaviours in captive environments. It is possible that these self-care
-behaviours emerge more often in captivity because pet parrots are kept with few
-or no conspecifics, and therefore must innovate tool use to preen inaccessible
-body areas, such as their heads and necks, which would have been otherwise
-preened by flock members. This may indicate that human interaction and
-allopreening in the absence of a conspecific is insufficient for pet parrots, as
-suggested by studies on welfare and chronic stress in lone captive parrots\textsuperscript{71--74}. Beyond social
-isolation in captivity, other factors that reduce preening efficacy by an
-individual might also lead to the innovation of self-care tooling: for example,
-a captive kea housed with conspecifics in a naturalistic environment was shown
-to have innovated the use of a pebble tool for self-care likely as a consequence
-of a missing upper mandible\textsuperscript{31}. These behaviours might therefore be
-innovated by individuals when ecologically necessary. Critically, however, a
-cognitive capacity to innovate a behaviour such as tool use must exist in a
-species in order to manifest in any environment, whether that be captive or in
-the wild. As such, despite differences in individuals' life experiences in
-captive and wild settings, such behaviour emerging in a captive setting at the
-very least indicates an underlying cognitive capacity to innovate that same
-behaviour in the wild.
-
 While missing data imputation is becoming more common in phylogenetic
-analyses\textsuperscript{75}, the important distinction between absence of
+analyses\textsuperscript{76}, the important distinction between absence of
 evidence and evidence of absence has not been given as much attention. Our
@@
 captured the full distribution of tool use in the parrot order. Our
-digital video survey more than doubled the number of known tool using parrot
-species from 11 to 28, and our phylogenetic model suggested that the true
+digital video survey identified novel observations of self-care tool use in
+several parrot species, more than doubling the number of known tool using parrot
+species from 11 to 28. Our phylogenetic model suggested that the true
 proportion of parrot tool users could be as high as 17\% of all species in this
@@
 methods used in this study have the potential to be applied to other rarely
-observed behaviours, including tool use in other taxa\textsuperscript{76}, rhythmic
-entrainment in birds\textsuperscript{77--80},
-teasing behaviours in primates\textsuperscript{81}, and tactical deception across all
-animals\textsuperscript{82--84}. We hope that these methods
+observed behaviours, including tool use in other taxa\textsuperscript{77}, rhythmic
+entrainment in birds\textsuperscript{78--81},
+teasing behaviours in primates\textsuperscript{82}, and tactical deception across all
+animals\textsuperscript{83--85}. We hope that these methods
 will continue to uncover a diverse array of ephemeral behaviours that have as
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wood1984}{}}%
 \CSLLeftMargin{61. }%
-\CSLRightInline{Reader, S.M., and Laland, K.N.
-(2002).
-Social intelligence, innovation, and enhanced brain size in primates.
-Proceedings of the National Academy of Sciences \emph{99}, 4436--4441.
-\url{https://doi.org/10.1073/pnas.062041299}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
+\CSLRightInline{Wood, G.A. (1984). Tool use by the palm cockatoo \emph{{P}robosciger aterrimus} during display. Corella \emph{8}, 94--95.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
 \CSLLeftMargin{62. }%
-\CSLRightInline{Sol, D., Olkowicz, S., Sayol, F., Kocourek, M., Zhang, Y., Marhounová, L., Osadnik, C., Corssmit, E., Garcia-Porta, J., Martin, T.E., et al.
-(2022).
-Neuron numbers link innovativeness with both absolute and relative brain size in birds.
-Nature Ecology \& Evolution \emph{6}, 1381--1389.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Cabrera-Álvarez, M.J., and Clayton, N.S.
-(2020).
-Neural processes underlying tool use in humans, macaques, and corvids.
-Frontiers in Psychology \emph{11}, 560669.
-\url{https://doi.org/10.3389/fpsyg.2020.560669}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
-(2021).
-Linking cognition to ecology in wild sympatric mouse lemur species.
-Proceedings of the Royal Society B: Biological Sciences \emph{288}, 20211728.
-\url{https://doi.org/10.1098/rspb.2021.1728}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
-\CSLLeftMargin{65. }%
 \CSLRightInline{Fragaszy, D.M., and Mangalam, M.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Aydinonat2014}{}}%
+\CSLLeftMargin{63. }%
+\CSLRightInline{Aydinonat, D., Penn, D.J., Smith, S., Moodley, Y., Hoelzl, F., Knauer, F., and Schwarzenberger, F.
+(2014).
+Social isolation shortens telomeres in {A}frican {G}rey parrots (\emph{{P}sittacus erithacus erithacus}).
+PLOS ONE \emph{9}, e93839.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Engebretson2006}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{Engebretson, M. (2006). The welfare and suitability of parrots as companion animals: A review. Animal Welfare \emph{15}, 263--276. \url{https://doi.org/10.1017/S0962728600030475}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mason2010}{}}%
+\CSLLeftMargin{65. }%
+\CSLRightInline{Mason, G.J.
+(2010).
+Species differences in responses to captivity: Stress, welfare and the comparative method.
+Trends in Ecology \& Evolution \emph{25}, 713--721.
+\url{https://doi.org/10.1016/j.tree.2010.08.011}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Meehan2003}{}}%
+\CSLLeftMargin{66. }%
+\CSLRightInline{Meehan, C., Garner, J., and Mench, J.
+(2003).
+Isosexual pair housing improves the welfare of young amazon parrots.
+Applied Animal Behaviour Science \emph{81}, 73--88.
+\url{https://doi.org/10.1016/S0168-1591(02)00238-1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
+\CSLLeftMargin{67. }%
+\CSLRightInline{Reader, S.M., and Laland, K.N.
+(2002).
+Social intelligence, innovation, and enhanced brain size in primates.
+Proceedings of the National Academy of Sciences \emph{99}, 4436--4441.
+\url{https://doi.org/10.1073/pnas.062041299}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
+\CSLLeftMargin{68. }%
+\CSLRightInline{Sol, D., Olkowicz, S., Sayol, F., Kocourek, M., Zhang, Y., Marhounová, L., Osadnik, C., Corssmit, E., Garcia-Porta, J., Martin, T.E., et al.
+(2022).
+Neuron numbers link innovativeness with both absolute and relative brain size in birds.
+Nature Ecology \& Evolution \emph{6}, 1381--1389.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
+\CSLLeftMargin{69. }%
+\CSLRightInline{Cabrera-Álvarez, M.J., and Clayton, N.S.
+(2020).
+Neural processes underlying tool use in humans, macaques, and corvids.
+Frontiers in Psychology \emph{11}, 560669.
+\url{https://doi.org/10.3389/fpsyg.2020.560669}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
+\CSLLeftMargin{70. }%
+\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
+(2021).
+Linking cognition to ecology in wild sympatric mouse lemur species.
+Proceedings of the Royal Society B: Biological Sciences \emph{288}, 20211728.
+\url{https://doi.org/10.1098/rspb.2021.1728}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Auersperg2020}{}}%
-\CSLLeftMargin{66. }%
+\CSLLeftMargin{71. }%
 \CSLRightInline{Auersperg, A.M.I., Schwing, R., Mioduszewska, B., O'Hara, M., and Huber, L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-DechaumeMoncharmont2020}{}}%
-\CSLLeftMargin{67. }%
+\CSLLeftMargin{72. }%
 \CSLRightInline{Dechaume-Moncharmont, F.-X.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Farrar2020}{}}%
-\CSLLeftMargin{68. }%
+\CSLLeftMargin{73. }%
 \CSLRightInline{Farrar, B.G. (2020). Evidence of tool use in a seabird? PsyArXiv. \url{https://doi.org/10.31234/osf.io/463hk}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{69. }%
+\CSLLeftMargin{74. }%
 \CSLRightInline{Sándor, K., and Miklósi, Á.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vonBayern2020}{}}%
-\CSLLeftMargin{70. }%
+\CSLLeftMargin{75. }%
 \CSLRightInline{von Bayern, A.M., Jacobs, I., and Osvath, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Aydinonat2014}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{Aydinonat, D., Penn, D.J., Smith, S., Moodley, Y., Hoelzl, F., Knauer, F., and Schwarzenberger, F.
-(2014).
-Social isolation shortens telomeres in {A}frican {G}rey parrots (\emph{{P}sittacus erithacus erithacus}).
-PLOS ONE \emph{9}, e93839.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Engebretson2006}{}}%
-\CSLLeftMargin{72. }%
-\CSLRightInline{Engebretson, M. (2006). The welfare and suitability of parrots as companion animals: A review. Animal Welfare \emph{15}, 263--276. \url{https://doi.org/10.1017/S0962728600030475}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mason2010}{}}%
-\CSLLeftMargin{73. }%
-\CSLRightInline{Mason, G.J.
-(2010).
-Species differences in responses to captivity: Stress, welfare and the comparative method.
-Trends in Ecology \& Evolution \emph{25}, 713--721.
-\url{https://doi.org/10.1016/j.tree.2010.08.011}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Meehan2003}{}}%
-\CSLLeftMargin{74. }%
-\CSLRightInline{Meehan, C., Garner, J., and Mench, J.
-(2003).
-Isosexual pair housing improves the welfare of young amazon parrots.
-Applied Animal Behaviour Science \emph{81}, 73--88.
-\url{https://doi.org/10.1016/S0168-1591(02)00238-1}.}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
-\CSLLeftMargin{75. }%
+\CSLLeftMargin{76. }%
 \CSLRightInline{Debastiani, V.J., Bastazini, V.A.G., and Pillar, V.D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
-\CSLLeftMargin{76. }%
+\CSLLeftMargin{77. }%
 \CSLRightInline{Hunt, G.R., Gray, R.D., and Taylor, A.H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
-\CSLLeftMargin{77. }%
+\CSLLeftMargin{78. }%
 \CSLRightInline{Benichov, J.I., Globerson, E., and Tchernichovski, O.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
-\CSLLeftMargin{78. }%
+\CSLLeftMargin{79. }%
 \CSLRightInline{Patel, A.D., Iversen, J.R., Bregman, M.R., and Schulz, I.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
-\CSLLeftMargin{79. }%
+\CSLLeftMargin{80. }%
 \CSLRightInline{ten Cate, C., Spierings, M., Hubert, J., and Honing, H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
-\CSLLeftMargin{80. }%
+\CSLLeftMargin{81. }%
 \CSLRightInline{Wilson, M., and Cook, P.F.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
-\CSLLeftMargin{81. }%
+\CSLLeftMargin{82. }%
 \CSLRightInline{Eckert, J., Winkler, S.L., and Cartmill, E.A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
-\CSLLeftMargin{82. }%
+\CSLLeftMargin{83. }%
 \CSLRightInline{Bro-Jørgensen, J., and Pangle, W.M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
-\CSLLeftMargin{83. }%
+\CSLLeftMargin{84. }%
 \CSLRightInline{Byrne, R.W., and Whiten, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
-\CSLLeftMargin{84. }%
+\CSLLeftMargin{85. }%
 \CSLRightInline{Byrne, R.W., and Whiten, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
-\CSLLeftMargin{85. }%
+\CSLLeftMargin{86. }%
 \CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership} (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
-\CSLLeftMargin{86. }%
+\CSLLeftMargin{87. }%
 \CSLRightInline{Jerison, H.J. (1973). Evolution of the brain and intelligence (Academic Press).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
-\CSLLeftMargin{87. }%
+\CSLLeftMargin{88. }%
 \CSLRightInline{Paradis, E., and Schliep, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
-\CSLLeftMargin{88. }%
+\CSLLeftMargin{89. }%
 \CSLRightInline{McElreath, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
-\CSLLeftMargin{89. }%
+\CSLLeftMargin{90. }%
 \CSLRightInline{Stan Development Team (2020). \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
-\CSLLeftMargin{90. }%
+\CSLLeftMargin{91. }%
 \CSLRightInline{Revell, L.J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
-\CSLLeftMargin{91. }%
+\CSLLeftMargin{92. }%
 \CSLRightInline{R Core Team (2022). \href{https://www.R-project.org/}{R: A language and environment for statistical computing} (R Foundation for Statistical Computing).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
-\CSLLeftMargin{92. }%
+\CSLLeftMargin{93. }%
 \CSLRightInline{Yu, G., Smith, D., Zhu, H., Guan, Y., and Lam, T.T.-Y.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-\CSLLeftMargin{93. }%
+\CSLLeftMargin{94. }%
 \CSLRightInline{Wickham, H. (2016). \href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis} (Springer-Verlag New York).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
-\CSLLeftMargin{94. }%
+\CSLLeftMargin{95. }%
 \CSLRightInline{Wilke, C.O. (2020). \href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
-\CSLLeftMargin{95. }%
+\CSLLeftMargin{96. }%
 \CSLRightInline{Landau, W.M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
-\CSLLeftMargin{96. }%
+\CSLLeftMargin{97. }%
 \CSLRightInline{Aust, F., and Barth, M. (2022). \href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}.}
@@
 of the terms ``parrot tool use'' and ``parrot scratching'' in languages for all
-countries where bird ownership was reported as \textgreater5\%\textsuperscript{85}, namely,
+countries where bird ownership was reported as \textgreater5\%\textsuperscript{86}, namely,
 Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish,
@@
 to one's body (or, in the case of borderline tool use, rubbing repetitively
-against an attached object\textsuperscript{69}).
+against an attached object\textsuperscript{74}).
 
@@
 calculated the encephalisation quotient (EQ) using the following
-formula\textsuperscript{86}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
+formula\textsuperscript{87}: \(BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))\). We
 found body mass and brain mass data for a total of 194 parrot species. This
@@
 
-We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{87} to
+We used the \emph{fitDiscrete} function in the \emph{ape} R package\textsuperscript{88} to
 calculate phylogenetic signal, for both the pre-survey and post-survey tool use
@@
 and \(\lambda\) (the rate of the exponential distribution). We use an
-Ornstein-Uhlenbeck Gaussian process\textsuperscript{88} to model phylogenetic
+Ornstein-Uhlenbeck Gaussian process\textsuperscript{89} to model phylogenetic
 covariance. Below, we specify the full model with priors:
@@
 \begin{align}
-N_{\text{Lit},i} &\sim \text{SurvivalCure}(\lambda_{\text{Lit},i}, p_{i}) \\
-N_{\text{Vid},i} &\sim \text{SurvivalCure}(\lambda_{\text{Vid},i}, p_{i}) \nonumber \\
+\text{T}_{\text{Lit},i}, \text{N}_{\text{Lit},i} &\sim \text{SurvivalCure}(\lambda_{\text{Lit},i}, p_{i}) \\
+\text{T}_{\text{Vid},i}, \text{N}_{\text{Vid},i} &\sim \text{SurvivalCure}(\lambda_{\text{Vid},i}, p_{i}) \nonumber \\
 \lambda_{\text{Lit},i} &= 1 / \text{exp}(\gamma_\text{Lit}) \nonumber \\
@@
 posterior distribution of this model using Hamiltonian Monte Carlo as
-implemented in Stan version 2.26.1\textsuperscript{89}. We ran the model for 4000
+implemented in Stan version 2.26.1\textsuperscript{90}. We ran the model for 4000
 samples, with 2000 warmup samples, and iterated the model over 100 posterior
@@
 parrots, we fitted three exploratory ancestral state reconstruction models. We
-used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{90},
+used the \emph{ancThresh} function from the \emph{phytools} R package\textsuperscript{91},
 iterating the function over 100 posterior parrot phylogenies. This function
@@
 
-All analyses were conducted in R v4.2.1.\textsuperscript{91}. Visualisations were
-produced using the \emph{ggtree}\textsuperscript{92}, \emph{ggplot2}\textsuperscript{93}, and \emph{cowplot}\textsuperscript{94} packages. The manuscript was reproducibly generated using the
-\emph{targets}\textsuperscript{95} and \emph{papaja}\textsuperscript{96} packages. Code to reproduce all
+All analyses were conducted in R v4.2.1.\textsuperscript{92}. Visualisations were
+produced using the \emph{ggtree}\textsuperscript{93}, \emph{ggplot2}\textsuperscript{94}, and \emph{cowplot}\textsuperscript{95} packages. The manuscript was reproducibly generated using the
+\emph{targets}\textsuperscript{96} and \emph{papaja}\textsuperscript{97} packages. Code to reproduce all
 analyses and figures can be found here:

### 2024-11-25 manuscript.Rmd
Update manuscript title

@@
 ---
-title             : "Evidence of self-care tooling on digital video platforms and phylogenetic modelling reveal parrot tool use is not rare"
+title             : "New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare"
 shorttitle        : "Parrot tool use"

### 2025-02-05 appendix.Rmd
prepare for submission
update manuscript
update manuscript and prepare for submission
revise and resubmit

@@
-\renewcommand{\figurename}{Supplementary Figure}
-\renewcommand{\tablename}{Supplementary Table}
-\renewcommand{\thefigure}{\arabic{figure}} \setcounter{figure}{0}
-\renewcommand{\thetable}{\arabic{table}} \setcounter{table}{0}
+\renewcommand{\figurename}{Figure}
+\renewcommand{\tablename}{Table}
+\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
 \renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}
 
-# **Supplementary Information**
+# **Supplemental Information**
 
@@
 \centering
-\noindent \hspace*{5mm} \small Crowdsourcing and phylogenetic modelling reveal parrot tool use is not rare \newline
+\noindent \hspace*{5mm} \small New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare \newline
 \hspace*{1cm} \small Amalia P. M. Bastos\textsuperscript{1,2}, Scott Claessens\textsuperscript{2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, \newline
@@
 
-## Supplementary Figures
+## Supplemental Figures
 
@@
 ```{r plotComparison, echo=FALSE, warning=FALSE, fig.width=8, fig.height=4, fig.cap="(ref:plotComparisonCaption)"}
-tar_read(plotComparison)
+#tar_read(plotComparison)
+knitr::include_graphics("figures/comparison.pdf")
 ```
@@
 ```{r plotASR1, echo=FALSE, warning=FALSE, fig.width=10, fig.height=13, fig.cap="(ref:plotASR1Caption)"}
-tar_read(plotASR1)
+#tar_read(plotASR1)
+knitr::include_graphics("figures/asr1.pdf")
 ```
@@
 ```{r plotASR2, echo=FALSE, warning=FALSE, fig.width=10, fig.height=13, fig.cap="(ref:plotASR2Caption)"}
-tar_read(plotASR2)
+#tar_read(plotASR2)
+knitr::include_graphics("figures/asr2.pdf")
 ```
@@
 ```{r plotASR3, echo=FALSE, warning=FALSE, fig.width=10, fig.height=13, fig.cap="(ref:plotASR3Caption)"}
-tar_read(plotASR3)
+#tar_read(plotASR3)
+knitr::include_graphics("figures/asr3.pdf")
 ```

### 2025-02-05 manuscript.Rmd
revise and resubmit

@@
 somatosensory information when innovating novel behaviours, such as tool use, 
-in changing environments [@Sol2005;@Sol2009] (but see ref [@Kaplan2020]). 
+in changing environments [@Sol2005;@Sol2009] (but see Kaplan[@Kaplan2020]). 
 Similarly, researchers have used existing reports of tool use in birds to debate
@@
 deal with it in different ways, such as controlling for the number of scientific 
-papers published on different species. But previous work has not yet attempted 
-to quantify and explicitly model the relationship between actual tool-using 
-behaviour and what is reported in the scientific literature. If more tool-using 
-species exist than previously thought, this could have important implications 
-for theories of the evolutionary drivers and origins of tool use and for our 
-understanding of how rare this behaviour actually is.
+papers published on different species. However, previous work has not yet 
+attempted to quantify and explicitly model the relationship between actual
+tool-using behaviour and what is reported in the scientific literature. If more
+tool-using species exist than previously thought, this could have important
+implications for theories of the evolutionary drivers and origins of tool use
+and for our understanding of how rare this behaviour actually is.
 
@@
 thus identify 28 total parrot species (7%) capable of true tool use as defined 
-by ref [@Shumaker2011], compared to the 11 previously reported.
+by Shumaker et al.[@Shumaker2011], compared to the 11 previously reported.
 
@@
 self-scratching tool use behaviours in captive environments. It is possible that 
-these self-care behaviours emerge more often in captivity because pet parrots 
-are kept with few or no conspecifics, and therefore must innovate tool use to 
-preen inaccessible body areas, such as their heads and necks, which would have 
-been otherwise preened by flock members. This may indicate that human 
-interaction and allopreening in the absence of a conspecific is insufficient for
-pet parrots, as suggested by studies on welfare and chronic stress in lone 
-captive parrots [@Aydinonat2014;@Engebretson2006;@Mason2010;@Meehan2003]. Beyond 
-social isolation in captivity, other factors that reduce preening efficacy by an 
+these self-care behaviours emerge in captivity because pet parrots are kept with
+few or no conspecifics, and therefore must innovate tool use to preen
+inaccessible body areas, such as their heads and necks, which would have been
+otherwise preened by flock members. This may indicate that human interaction and
+allopreening in the absence of a conspecific is insufficient for pet parrots, as
+suggested by studies on welfare and chronic stress in lone captive parrots 
+[@Aydinonat2014;@Engebretson2006;@Mason2010;@Meehan2003]. Beyond social
+isolation in captivity, other factors that reduce preening efficacy by an 
 individual might also lead to the innovation of self-care tooling: for example,
@@
 phylogenetic history and encephalisation strongly suggests that self-scratching 
-indicates a capacity to produce tool use, which is expressed in different ways 
-in captive and wild settings.
+indicates a capacity to produce tool use, which may be expressed in different 
+ways in captive and wild settings. Interestingly, at present there is no
+evidence to suggest that parrots exhibit self-scratching tool use in the wild.
+This could reflect a true absence of this behaviour in wild parrots, which may
+not experience the same environmental pressures that lead to the emergence of
+self-scratching in captivity. On the other hand, it could also reflect a false
+negative, with self-scratching occurring sufficiently infrequently or
+inconspicuously in wild populations that it remains unobserved or unreported.
 
-Our findings have a number of important implications. First, our findings show 
-that current research effort in the scientific literature is insufficient to 
-capture the real world occurrence of parrot tool use. If the scientific 
-literature had sampled the natural world sufficiently, we would expect to see 
-close correspondence between those species reported as tool users in the 
-literature and those species the public have filmed performing tool use. 
+Our findings have a number of important implications. First, our findings
+suggest that current research effort in the scientific literature is
+insufficient to capture the real world occurrence of parrot tool use. If the
+scientific literature had sampled the natural world sufficiently, we would
+expect to see close correspondence between those species reported as tool users
+in the literature and those species the public have filmed performing tool use. 
 Instead, we discovered a large discrepancy between these two data sources, both 
@@
 relationships, we encourage further work on the specific neural correlates of 
-technical intelligence in parrots, e.g., [@Alvarez2020]. In our phylogenetic 
-model, we also found that tool use was somewhat more likely among feeding 
-generalists compared to feeding specialists, although this difference was 
-uncertain. This trend supports previous suggestions that increased cognitive 
-abilities and technical innovation rates are required to expand a generalist 
-species' dietary niche [@HenkeVonDerMalsburg2020;@HenkeVonDerMalsburg2021;
-@Ducatez2015]. However, the trend contradicts theories linking tool use to 
-dietary specialisation, whereby species eating specific foods that require 
-extractive foraging have higher cognitive ability and are especially prone to 
-using tools [@HenkeVonDerMalsburg2020].
+technical intelligence in parrots, e.g., Cabrera-Álvarez and Clayton
+[@Alvarez2020]. In our phylogenetic model, we also found that tool use was 
+somewhat more likely among feeding generalists compared to feeding specialists, 
+although this difference was uncertain. This trend supports previous suggestions
+that increased cognitive abilities and technical innovation rates are required
+to expand a generalist species' dietary niche [@HenkeVonDerMalsburg2020;
+@HenkeVonDerMalsburg2021;@Ducatez2015]. However, the trend contradicts theories
+linking tool use to dietary specialisation, whereby species eating specific
+foods that require extractive foraging have higher cognitive ability and are
+especially prone to using tools [@HenkeVonDerMalsburg2020].
+
+While missing data imputation is becoming more common in phylogenetic 
+analyses [@Debastiani2021], the important distinction between absence of 
+evidence and evidence of absence has not been given as much attention. Our 
+phylogenetic analysis provides one approach to this problem by distinguishing 
+between true absences of tool use and absences of tool use due to a lack of 
+research effort in the scientific literature or in videos. To achieve this, we 
+explicitly modelled the measurement of the outcome variable along a research 
+effort time series, such that species with lower research effort in the 
+literature or in videos were likely to be censored. In line with our causal 
+model, we also included relative brain size, feeding strategy, and phylogenetic
+history as predictors of unobserved tool use. We encourage researchers to test
+this model by directing future study efforts towards the parrot species with the
+highest probabilities of being undetected tool-users. Future work should also
+refine the causal model in Figure \@ref(fig:plotDAG) to provide more certain
+estimates of tool use probabilities, either by including additional predictor
+variables or modelling further causes of measurement error in the taxonomic
+record, such as species abundance and geographic accessibility [@Ducatez2014].
+
+## Limitations of study
 
@@
 owners directly rewarding tool use behaviours with food. It is unlikely that 
-owners would specifically train parrots to scratch themselves with tools. 
-Finally, the high levels of phylogenetic signal in our data provide strong 
-evidence that the observations from our video survey reflect
+a range of owners would independently train parrots to scratch themselves with
+tools. Finally, the high levels of phylogenetic signal in our data provide
+strong evidence that the observations from our video survey reflect
 biologically-endowed capacities for tool use rather than accidental or trained
@@
 
-While missing data imputation is becoming more common in phylogenetic 
-analyses [@Debastiani2021], the important distinction between absence of 
-evidence and evidence of absence has not been given as much attention. Our 
-phylogenetic analysis provides one approach to this problem by distinguishing 
-between true absences of tool use and absences of tool use due to a lack of 
-research effort in the scientific literature or in videos. To achieve this, we 
-explicitly modelled the measurement of the outcome variable along a research 
-effort time series, such that species with lower research effort in the 
-literature or in videos were likely to be censored. In line with our causal 
-model, we also included relative brain size, feeding strategy, and phylogenetic
-history as predictors of unobserved tool use. We encourage researchers to test
-this model by directing future study efforts towards the parrot species with the
-highest probabilities of being undetected tool-users. Future work should also
-refine the causal model in Figure \@ref(fig:plotDAG) to provide more certain
-estimates of tool use probabilities, either by including additional predictor
-variables or modelling further causes of measurement error in the taxonomic
-record, such as species abundance and geographic accessibility [@Ducatez2014].
+## Conclusion
 
@@
 
-This project was made possible through the support of a grant from the Templeton 
-World Charity Foundation (A.H.T., X.J.N.). The authors would like to thank 
-Daniel Sol for providing feedback on a previous version of the manuscript.
+This project was made possible through the support of grants from the Templeton 
+World Charity Foundation (A.H.T., X.J.N., TWCF-2018-0310, TWCF-2024-33225). The
+authors would like to thank Daniel Sol for providing feedback on a previous
+version of the manuscript.
 

### 2025-02-05 manuscript.tex
revise and resubmit

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
   {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
     {}{\InnerPatchFailed}%
@@
 {}{\PatchFailed}
+\makeatother
 \keywords{tool use; technical intelligence; parrots; digital video platforms; phylogenetic modelling}
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
-  pdftitle={Evidence of self-care tooling on digital video platforms and phylogenetic modelling reveal parrot tool use is not rare},
+  pdftitle={New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare},
   pdfauthor={Amalia P. M. Bastos†,1,2, Scott Claessens*†,2, Ximena J. Nelson3, David Welch4, Quentin D. Atkinson‡,2, \& Alex H. Taylor‡,2,3,5,6},
@@
 
-\title{Evidence of self-care tooling on digital video platforms and phylogenetic modelling reveal parrot tool use is not rare}
+\title{New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare}
 \author{Amalia P.
@@
 somatosensory information when innovating novel behaviours, such as tool use,
-in changing environments\textsuperscript{15,16} (but see ref\textsuperscript{17}).
+in changing environments\textsuperscript{15,16} (but see Kaplan\textsuperscript{17}).
 Similarly, researchers have used existing reports of tool use in birds to debate
@@
 deal with it in different ways, such as controlling for the number of scientific
-papers published on different species. But previous work has not yet attempted
-to quantify and explicitly model the relationship between actual tool-using
-behaviour and what is reported in the scientific literature. If more tool-using
-species exist than previously thought, this could have important implications
-for theories of the evolutionary drivers and origins of tool use and for our
-understanding of how rare this behaviour actually is.
+papers published on different species. However, previous work has not yet
+attempted to quantify and explicitly model the relationship between actual
+tool-using behaviour and what is reported in the scientific literature. If more
+tool-using species exist than previously thought, this could have important
+implications for theories of the evolutionary drivers and origins of tool use
+and for our understanding of how rare this behaviour actually is.
 
@@
 thus identify 28 total parrot species (7\%) capable of true tool use as defined
-by ref\textsuperscript{10}, compared to the 11 previously reported.
+by Shumaker et al.\textsuperscript{10}, compared to the 11 previously reported.
 
@@
 self-scratching tool use behaviours in captive environments. It is possible that
-these self-care behaviours emerge more often in captivity because pet parrots
-are kept with few or no conspecifics, and therefore must innovate tool use to
-preen inaccessible body areas, such as their heads and necks, which would have
-been otherwise preened by flock members. This may indicate that human
-interaction and allopreening in the absence of a conspecific is insufficient for
-pet parrots, as suggested by studies on welfare and chronic stress in lone
-captive parrots\textsuperscript{63--66}. Beyond
-social isolation in captivity, other factors that reduce preening efficacy by an
+these self-care behaviours emerge in captivity because pet parrots are kept with
+few or no conspecifics, and therefore must innovate tool use to preen
+inaccessible body areas, such as their heads and necks, which would have been
+otherwise preened by flock members. This may indicate that human interaction and
+allopreening in the absence of a conspecific is insufficient for pet parrots, as
+suggested by studies on welfare and chronic stress in lone captive parrots\textsuperscript{63--66}. Beyond social
+isolation in captivity, other factors that reduce preening efficacy by an
 individual might also lead to the innovation of self-care tooling: for example,
@@
 phylogenetic history and encephalisation strongly suggests that self-scratching
-indicates a capacity to produce tool use, which is expressed in different ways
-in captive and wild settings.
-
-Our findings have a number of important implications. First, our findings show
-that current research effort in the scientific literature is insufficient to
-capture the real world occurrence of parrot tool use. If the scientific
-literature had sampled the natural world sufficiently, we would expect to see
-close correspondence between those species reported as tool users in the
-literature and those species the public have filmed performing tool use.
+indicates a capacity to produce tool use, which may be expressed in different
+ways in captive and wild settings. Interestingly, at present there is no
+evidence to suggest that parrots exhibit self-scratching tool use in the wild.
+This could reflect a true absence of this behaviour in wild parrots, which may
+not experience the same environmental pressures that lead to the emergence of
+self-scratching in captivity. On the other hand, it could also reflect a false
+negative, with self-scratching occurring sufficiently infrequently or
+inconspicuously in wild populations that it remains unobserved or unreported.
+
+Our findings have a number of important implications. First, our findings
+suggest that current research effort in the scientific literature is
+insufficient to capture the real world occurrence of parrot tool use. If the
+scientific literature had sampled the natural world sufficiently, we would
+expect to see close correspondence between those species reported as tool users
+in the literature and those species the public have filmed performing tool use.
 Instead, we discovered a large discrepancy between these two data sources, both
@@
 relationships, we encourage further work on the specific neural correlates of
-technical intelligence in parrots, e.g.,\textsuperscript{69}. In our phylogenetic
-model, we also found that tool use was somewhat more likely among feeding
-generalists compared to feeding specialists, although this difference was
-uncertain. This trend supports previous suggestions that increased cognitive
-abilities and technical innovation rates are required to expand a generalist
-species' dietary niche\textsuperscript{18,20,70}. However, the trend contradicts theories linking tool use to
-dietary specialisation, whereby species eating specific foods that require
-extractive foraging have higher cognitive ability and are especially prone to
-using tools\textsuperscript{20}.
-
-A potential concern with data originating from digital video platforms is its
-reliability\textsuperscript{23,71--75}.
-In particular, the self-care tool use instances detected in our video survey
-might be attributable to training or unintentional cueing by the birds' owners.
-However, there was little evidence to suggest that the observations of
-self-scratching tool use in the video survey were merely unintentional accidents
-or explicitly trained behaviours. Individual parrots often used tools slowly and
-repetitively over long periods of time, even across multiple different videos,
-suggesting that their behaviour was not random or accidental\textsuperscript{74}.
-Parrots preferentially employed self-scratching tools on areas of their body
-that were otherwise inaccessible, with 96\% of all instances involving scratching
-of the head or neck, suggesting intentional tool use. For 60\% of the species in
-the video survey, we found two or more videos of repetitive and sustained
-scratching by different individuals of the same species in separate households,
-suggesting that the manipulations were intentional and recurring events that did
-not represent unusual stereotypies of any single individual. Regarding the
-possibility of training or cueing from owners, over half of the videos contained
-no evidence of human interaction aside from filming the behaviour. Humans only
-handed parrots their tools in two of the videos, and none of the videos featured
-owners directly rewarding tool use behaviours with food. It is unlikely that
-owners would specifically train parrots to scratch themselves with tools.
-Finally, the high levels of phylogenetic signal in our data provide strong
-evidence that the observations from our video survey reflect
-biologically-endowed capacities for tool use rather than accidental or trained
-behaviours, which would likely appear uniformly across the phylogeny.
-Nevertheless, future work using data such as this should choose target
-behaviours carefully and examine videos for evidence of training or cueing.
+technical intelligence in parrots, e.g., Cabrera-Álvarez and Clayton\textsuperscript{69}. In our phylogenetic model, we also found that tool use was
+somewhat more likely among feeding generalists compared to feeding specialists,
+although this difference was uncertain. This trend supports previous suggestions
+that increased cognitive abilities and technical innovation rates are required
+to expand a generalist species' dietary niche\textsuperscript{18,20,70}. However, the trend contradicts theories
+linking tool use to dietary specialisation, whereby species eating specific
+foods that require extractive foraging have higher cognitive ability and are
+especially prone to using tools\textsuperscript{20}.
 
 While missing data imputation is becoming more common in phylogenetic
-analyses\textsuperscript{76}, the important distinction between absence of
+analyses\textsuperscript{71}, the important distinction between absence of
 evidence and evidence of absence has not been given as much attention. Our
@@
 
+\hypertarget{limitations-of-study}{%
+\subsection{Limitations of study}\label{limitations-of-study}}
+
+A potential concern with data originating from digital video platforms is its
+reliability\textsuperscript{23,72--76}.
+In particular, the self-care tool use instances detected in our video survey
+might be attributable to training or unintentional cueing by the birds' owners.
+However, there was little evidence to suggest that the observations of
+self-scratching tool use in the video survey were merely unintentional accidents
+or explicitly trained behaviours. Individual parrots often used tools slowly and
+repetitively over long periods of time, even across multiple different videos,
+suggesting that their behaviour was not random or accidental\textsuperscript{75}.
+Parrots preferentially employed self-scratching tools on areas of their body
+that were otherwise inaccessible, with 96\% of all instances involving scratching
+of the head or neck, suggesting intentional tool use. For 60\% of the species in
+the video survey, we found two or more videos of repetitive and sustained
+scratching by different individuals of the same species in separate households,
+suggesting that the manipulations were intentional and recurring events that did
+not represent unusual stereotypies of any single individual. Regarding the
+possibility of training or cueing from owners, over half of the videos contained
+no evidence of human interaction aside from filming the behaviour. Humans only
+handed parrots their tools in two of the videos, and none of the videos featured
+owners directly rewarding tool use behaviours with food. It is unlikely that
+a range of owners would independently train parrots to scratch themselves with
+tools. Finally, the high levels of phylogenetic signal in our data provide
+strong evidence that the observations from our video survey reflect
+biologically-endowed capacities for tool use rather than accidental or trained
+behaviours, which would likely appear uniformly across the phylogeny.
+Nevertheless, future work using data such as this should choose target
+behaviours carefully and examine videos for evidence of training or cueing.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
+
 In conclusion, we have shown that the scientific literature has insufficiently
@@
 
-This project was made possible through the support of a grant from the Templeton
-World Charity Foundation (A.H.T., X.J.N.). The authors would like to thank
-Daniel Sol for providing feedback on a previous version of the manuscript.
+This project was made possible through the support of grants from the Templeton
+World Charity Foundation (A.H.T., X.J.N., TWCF-2018-0310, TWCF-2024-33225). The
+authors would like to thank Daniel Sol for providing feedback on a previous
+version of the manuscript.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
+\CSLLeftMargin{71. }%
+\CSLRightInline{Debastiani, V.J., Bastazini, V.A.G., and Pillar, V.D.
+(2021).
+Using phylogenetic information to impute missing functional trait values in ecological databases.
+Ecological Informatics \emph{63}, 101315.
+\url{https://doi.org/10.1016/j.ecoinf.2021.101315}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Auersperg2020}{}}%
-\CSLLeftMargin{71. }%
+\CSLLeftMargin{72. }%
 \CSLRightInline{Auersperg, A.M.I., Schwing, R., Mioduszewska, B., O'Hara, M., and Huber, L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-DechaumeMoncharmont2020}{}}%
-\CSLLeftMargin{72. }%
+\CSLLeftMargin{73. }%
 \CSLRightInline{Dechaume-Moncharmont, F.-X.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Farrar2020}{}}%
-\CSLLeftMargin{73. }%
+\CSLLeftMargin{74. }%
 \CSLRightInline{Farrar, B.G. (2020). Evidence of tool use in a seabird? PsyArXiv. \url{https://doi.org/10.31234/osf.io/463hk}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{74. }%
+\CSLLeftMargin{75. }%
 \CSLRightInline{Sándor, K., and Miklósi, Á.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vonBayern2020}{}}%
-\CSLLeftMargin{75. }%
+\CSLLeftMargin{76. }%
 \CSLRightInline{von Bayern, A.M., Jacobs, I., and Osvath, M.
@@
 \url{https://doi.org/10.1073/pnas.1922117117}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
-\CSLLeftMargin{76. }%
-\CSLRightInline{Debastiani, V.J., Bastazini, V.A.G., and Pillar, V.D.
-(2021).
-Using phylogenetic information to impute missing functional trait values in ecological databases.
-Ecological Informatics \emph{63}, 101315.
-\url{https://doi.org/10.1016/j.ecoinf.2021.101315}.}
 
@@
 to one's body (or, in the case of borderline tool use, rubbing repetitively
-against an attached object\textsuperscript{74}).
+against an attached object\textsuperscript{75}).
 
@@
 
-\noindent \hspace*{5mm} \small Digital video platforms and phylogenetic modelling reveal parrot tool use is not rare \newline
+\noindent \hspace*{5mm} \small New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare \newline
 \hspace*{1cm} \small Amalia P. M. Bastos\textsuperscript{1,2}, Scott Claessens\textsuperscript{2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, \newline
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/plotComparison-1.pdf}
+\includegraphics{figures/comparison.pdf}
 \caption{\label{fig:plotComparison}\emph{Comparing results between the survival cure model and models fitted to the pre-survey and post-survey data without any survival cure component.} Densities are full posterior distributions from three separate models iterated over 100 posterior parrot phylogenies.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/plotASR1-1.pdf}
+\includegraphics{figures/asr1.pdf}
 \caption{\label{fig:plotASR1}\emph{Results of exploratory ancestral state reconstruction analysis fitted to pre-video-survey data, represented on a maximum clade credibility tree.} Tip nodes represent the presence (red) or absence (grey) of observed tool use in the scientific literature.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/plotASR2-1.pdf}
+\includegraphics{figures/asr2.pdf}
 \caption{\label{fig:plotASR2}\emph{Results of exploratory ancestral state reconstruction analysis fitted to post-video-survey data, represented on a maximum clade credibility tree.} Tip nodes represent the presence (red) or absence (grey) of observed tool use in the scientific literature and the video survey.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/plotASR3-1.pdf}
+\includegraphics{figures/asr3.pdf}
 \caption{\label{fig:plotASR3}\emph{Results of exploratory ancestral state reconstruction analysis fitted to predicted probabilities from the phylogenetic survival cure model, represented on a maximum clade credibility tree.} Tip nodes represent the median posterior predicted probabilities of tool use from the phylogenetic survival cure model, with more red indicating an increasing probability of tool use presence and more grey indicating a decreasing probability of tool use presence.

### 2025-02-05 run.R

@@ -1,1 +1,0 @@
-targets::tar_make_clustermq(workers = 250L)

### 2025-02-13 manuscript.Rmd
Changes for in-principle acceptance

@@
 ---
-title             : "New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare"
+title             : "Evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare"
 shorttitle        : "Parrot tool use"
@@
 
-keywords          : "tool use; technical intelligence; parrots; digital video platforms; phylogenetic modelling"
 bibliography      : ["r-references.bib"]
@@
   - \note{\raggedright † These authors contributed equally to this work \par ‡ These authors contributed equally to this work \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand.
-\text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}} \par This working paper has not yet been peer-reviewed.}
+\text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}}}
 appendix          : "appendix.Rmd"
@@
 \newpage
-\linenumbers
 
@@
 unobserved species is to specify a causal model of the process that generates
-the observed data. We propose one such causal model in Figure 
-\@ref(fig:plotDAG). In this model, we assume that the presence of tool use in 
+the observed data. We propose one such causal model in Figure 1. 
+In this model, we assume that the presence of tool use in 
 the scientific literature (or on digital video platforms) is caused by both 
@@
 evidence is evidence of absence.
-
-(ref:plotDAGCaption) _Causal model of observed tool use._ Directed acyclic graph 
-of the causal relationships between observed tool use and other variables. 
-Available scientific data on tool use is caused both by unobserved tool use 
-presence and scientific research effort (i.e., number of publications). 
-Available video data on tool use is caused both by unobserved tool use 
-presence and video research effort (i.e., number of videos). According to 
-theory, unobserved tool use presence should be caused by relative brain size 
-(encephalisation quotient) and feeding strategy (generalist vs. specialist). 
-These variables all share unobserved confounds generated by shared phylogenetic
-history. Grey circles indicate unobserved variables.
-
-```{r plotDAG, echo=F, fig.width=6, fig.height=3.6, fig.cap="(ref:plotDAGCaption)"}
-tar_read(plotDAG)
-```
 
@@
 [@Jetz2012] exist for parrots, allowing us to fit the statistical model implied
-by Figure \@ref(fig:plotDAG) to the entire parrot order.
+by Figure 1 to the entire parrot order.
 
@@
 
-Figure \@ref(fig:plotPhylo1) maps the findings from the video survey onto a 
+Figure 2 maps the findings from the video survey onto a 
 maximum clade credibility phylogeny for the parrot order, plotted alongside 
@@
 by Shumaker et al.[@Shumaker2011], compared to the 11 previously reported.
-
-(ref:plotPhylo1Caption) _Results of video survey and phylogenetic survival cure
-modelling mapped onto a maximum clade credibility phylogeny of the parrot order._
-Orange points in the inner ring indicate species observed in the video survey,
-with point size scaled by the number of videos for each species (note that three
-species observed only in the video survey are not present in the phylogeny due
-to a lack of genomic data: _Psittacara erythrogenys_, _Psittacus timneh_, and 
-_Aratinga nenday_). Blue points in the outer ring indicate species observed in
-the scientific literature, with point size scaled by the number of papers 
-published on each species. Yellow species names indicate the top ten most likely
-tool-using species from our phylogenetic survival cure model which were not 
-observed in the scientific literature or the video survey. Total _n_ = 
-`r nrow(tar_read(d))` species.
-
-```{r plotPhylo1, echo=F, fig.width=17, fig.height=15, fig.cap="(ref:plotPhylo1Caption)"}
-tar_read(plotPhylo1)
-```
 
@@
 species to have their own probability of being a non-tool-user. Following our 
-causal model (Figure \@ref(fig:plotDAG)), we predict these probabilities based 
+causal model (Figure 1), we predict these probabilities based 
 on feeding strategy, encephalisation quotient, and phylogenetic history (see 
@@
 
-Figure \@ref(fig:plotSurvCure1) visualises the ranked posterior probabilities of 
+Figure 3 visualises the ranked posterior probabilities of 
 tool use from the phylogenetic survival cure model for all parrot species. As 
@@
 and `r tar_read(d)$SearchHits[165]` video search hits, which is fewer than the 
-model expects are necessary to discover tool use when it is present (Figure 
-\@ref(fig:plotSurvCure2)). This species is also found in the _Cacatua_ genus, a 
+model expects are necessary to discover tool use when it is present (Figure 4). 
+This species is also found in the _Cacatua_ genus, a 
 clade containing several known tool users. This prediction makes sense given the 
@@
 (_Ognorhynchus icterotis_), the red-vented cockatoo (_Cacatua haematuropygia_), 
-and the gang-gang cockatoo (_Callocephalon fimbriatum_). Figure 
-\@ref(fig:plotPhylo1) plots these species on the parrot phylogeny, using the top 
+and the gang-gang cockatoo (_Callocephalon fimbriatum_). Figure 2 
+plots these species on the parrot phylogeny, using the top 
 ten highest ranked species without observed evidence of tool use as an arbitrary 
 cutoff for visualisation purposes.
-
-(ref:plotSurvCure1Caption) _Posterior predicted probabilities of tool use for 
-each species from our phylogenetic survival cure model._ Points are posterior 
-medians and lines are 50% and 95% credible intervals. Total _n_ = 
-`r nrow(tar_read(d))` species.
-
-```{r plotSurvCure1, echo=F, fig.width=7, fig.height=10, fig.cap="(ref:plotSurvCure1Caption)"}
-tar_read(plotSurvCure1)
-```
-
-(ref:plotSurvCure2Caption) _Expected number of published papers and videos until 
-tool use discovery, according to the survival component of the phylogenetic 
-survival cure model._ Densities are full posterior distributions, points are 
-posterior medians, and lines are 50% and 95% credible intervals.
-
-```{r plotSurvCure2, echo=F, fig.width=7, fig.height=3, fig.cap="(ref:plotSurvCure2Caption)"}
-tar_read(plotSurvCure2)
-```
 
@@
 
-The posterior probabilities shown in Figure \@ref(fig:plotSurvCure1) are 
+The posterior probabilities shown in Figure 3 are 
 estimated with uncertainty, so it is difficult to "identify" any particular 
@@
 use in the parrot order. Regarding the drivers of tool use hypothesised in 
-Figure \@ref(fig:plotDAG), the phylogenetic survival cure model revealed that 
+Figure 1, the phylogenetic survival cure model revealed that 
 encephalisation quotient strongly positively predicted the probability of tool 
@@
 `r printnum(quantile(-postFull$bEQ, 0.975))`]; total _n_ = `r nrow(tar_read(d))` 
-species; Figure \@ref(fig:plotSurvCure4)). This helps explain the ranking in 
-Figure \@ref(fig:plotSurvCure1): the blue-eyed cockatoo has the largest relative 
+species; Figure 5). This helps explain the ranking in 
+Figure 3: the blue-eyed cockatoo has the largest relative 
 brain size in the dataset. We also found that feeding generalist species were 
@@
 respectively (Figure \@ref(fig:plotComparison)).
-
-(ref:plotSurvCure4Caption) _Posterior predictions for the effects of feeding 
-strategy and encephalisation quotient on the probability of tool use from the 
-phylogenetic survival cure model._ In the left plot, points and lines represent 
-posterior medians and 50% and 95% credible intervals, with densities 
-representing full posterior distributions. In the right plot, the line and 
-shaded areas represent the posterior median regression line with 50% and 95% 
-credible intervals. In both plots, individual species are coloured according to 
-the presence / absence of tool use in the video survey and the scientific 
-literature. Total _n_ = `r nrow(tar_read(d))` species, generalist _n_ = 
-`r sum(tar_read(d)$Feeding == "Generalist")` species, specialist _n_ = 
-`r sum(tar_read(d)$Feeding == "Specialist")` species.
-
-```{r plotSurvCure4, echo=F, fig.width=8, fig.height=4, fig.cap="(ref:plotSurvCure4Caption)"}
-tar_read(plotSurvCure4)
-```
 
@@
 Figures \@ref(fig:plotASR1) - \@ref(fig:plotASR3)).
-
-(ref:tableASRCaption) Estimated probabilities of tool use for most recent common 
-ancestors of several parrot genera. _Probabilities estimated using exploratory 
-ancestral state reconstruction models fitted to the pre-video-survey data, 
-post-video-survey data, and predicted probabilities from the phylogenetic 
-survival cure model. Total_ n _= `r nrow(tar_read(d))` species._
-
-```{r tableASR, echo=F, warning=F, message=F}
-apa_table(
-  tar_read(tableASR),
-  caption = "(ref:tableASRCaption)",
-  escape = FALSE
-)
-```
 
@@
 highest probabilities of being undetected tool-users. Future work should also
-refine the causal model in Figure \@ref(fig:plotDAG) to provide more certain
+refine the causal model in Figure 1 to provide more certain
 estimates of tool use probabilities, either by including additional predictor
@@
 record, such as species abundance and geographic accessibility [@Ducatez2014].
+
+In conclusion, we have shown that the scientific literature has insufficiently 
+captured the full distribution of tool use in the parrot order. Our 
+digital video survey identified novel observations of self-care tool use in 
+several parrot species, more than doubling the number of known tool using parrot 
+species from 11 to 28. Our phylogenetic model suggested that the true 
+proportion of parrot tool users could be as high as 17% of all species in this 
+order. These discoveries have implications for theories of the evolutionary 
+drivers and origins of tool use in parrots. Beyond parrot tool use, the 
+methods used in this study have the potential to be applied to other rarely 
+observed behaviours, including tool use in other taxa [@Hunt2013], rhythmic 
+entrainment in birds [@Benichov2016;@Patel2009;@tenCate2016;@Wilson2016],
+teasing behaviours in primates [@Eckert2020], and tactical deception across all
+animals [@BroJorgensen2010;@Byrne1988;@Byrne1991]. We hope that these methods
+will continue to uncover a diverse array of ephemeral behaviours that have as
+yet gone undetected in the scientific literature.
 
@@
 
-## Conclusion
+\newpage
 
-In conclusion, we have shown that the scientific literature has insufficiently 
-captured the full distribution of tool use in the parrot order. Our 
-digital video survey identified novel observations of self-care tool use in 
-several parrot species, more than doubling the number of known tool using parrot 
-species from 11 to 28. Our phylogenetic model suggested that the true 
-proportion of parrot tool users could be as high as 17% of all species in this 
-order. These discoveries have implications for theories of the evolutionary 
-drivers and origins of tool use in parrots. Beyond parrot tool use, the 
-methods used in this study have the potential to be applied to other rarely 
-observed behaviours, including tool use in other taxa [@Hunt2013], rhythmic 
-entrainment in birds [@Benichov2016;@Patel2009;@tenCate2016;@Wilson2016],
-teasing behaviours in primates [@Eckert2020], and tactical deception across all
-animals [@BroJorgensen2010;@Byrne1988;@Byrne1991]. We hope that these methods
-will continue to uncover a diverse array of ephemeral behaviours that have as
-yet gone undetected in the scientific literature.
+# Resource Availability
 
-\newpage
-\nolinenumbers
+## Lead contact
+
+Further information about resources should be directed to Scott Claessens 
+(scott.claessens@gmail.com).
+
+## Materials availability
+
+This study did not generate new unique materials.
+
+## Data and code availability
+
+All data and original code have been deposited on GitHub and are publicly
+available as of the date of publication. DOIs are listed in the key resources
+table (see STAR Methods).
 
@@
 
+# Main figures
+
+_Figure 1. Causal model of observed tool use._ Directed acyclic graph 
+of the causal relationships between observed tool use and other variables. 
+Available scientific data on tool use is caused both by unobserved tool use 
+presence and scientific research effort (i.e., number of publications). 
+Available video data on tool use is caused both by unobserved tool use 
+presence and video research effort (i.e., number of videos). According to 
+theory, unobserved tool use presence should be caused by relative brain size 
+(encephalisation quotient) and feeding strategy (generalist vs. specialist). 
+These variables all share unobserved confounds generated by shared phylogenetic
+history. Grey circles indicate unobserved variables.
+
+_Figure 2. Results of video survey and phylogenetic survival cure modelling mapped onto a maximum clade credibility phylogeny of the parrot order._
+Orange points in the inner ring indicate species observed in the video survey,
+with point size scaled by the number of videos for each species (note that three
+species observed only in the video survey are not present in the phylogeny due
+to a lack of genomic data: _Psittacara erythrogenys_, _Psittacus timneh_, and 
+_Aratinga nenday_). Blue points in the outer ring indicate species observed in
+the scientific literature, with point size scaled by the number of papers 
+published on each species. Yellow species names indicate the top ten most likely
+tool-using species from our phylogenetic survival cure model which were not 
+observed in the scientific literature or the video survey. Total _n_ = 
+`r nrow(tar_read(d))` species.
+
+_Figure 3. Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model._ 
+Points are posterior medians and lines are 50% and 95% credible intervals. 
+Total _n_ = `r nrow(tar_read(d))` species.
+
+_Figure 4. Expected number of published papers and videos until tool use discovery, according to the survival component of the phylogenetic survival cure model._ 
+Densities are full posterior distributions, points are 
+posterior medians, and lines are 50% and 95% credible intervals.
+
+_Figure 5. Posterior predictions for the effects of feeding strategy and encephalisation quotient on the probability of tool use from the phylogenetic survival cure model._ 
+In the left plot, points and lines represent 
+posterior medians and 50% and 95% credible intervals, with densities 
+representing full posterior distributions. In the right plot, the line and 
+shaded areas represent the posterior median regression line with 50% and 95% 
+credible intervals. In both plots, individual species are coloured according to 
+the presence / absence of tool use in the video survey and the scientific 
+literature. Total _n_ = `r nrow(tar_read(d))` species, generalist _n_ = 
+`r sum(tar_read(d)$Feeding == "Generalist")` species, specialist _n_ = 
+`r sum(tar_read(d)$Feeding == "Specialist")` species.
+
+(ref:tableASRCaption) Estimated probabilities of tool use for most recent common 
+ancestors of several parrot genera. _Probabilities estimated using exploratory 
+ancestral state reconstruction models fitted to the pre-video-survey data, 
+post-video-survey data, and predicted probabilities from the phylogenetic 
+survival cure model. Total_ n _= `r nrow(tar_read(d))` species._
+
+\newpage
+
+# Main tables
+
+```{r tableASR, echo=F, warning=F, message=F}
+apa_table(
+  tar_read(tableASR),
+  caption = "(ref:tableASRCaption)",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+\newpage
+
+# STAR Methods
+
+## Method Details
+
+### Video searches and coding
+
+Our video search was conducted on YouTube in July 2020. Searches were conducted
+manually by the first author over a month-long period, using the same IP address
+and not logged in with a YouTube user account. Search terms included 
+"parrot using tool" and variants (e.g., "macaw using tool", "lorikeet using 
+tool", "parakeet using tool"), "tool use in parrot", "parrot tool use", "parrot 
+scratching itself" (included after we found several videos demonstrating 
+self-care tool use in previous searches) and equivalent terms (e.g., "parrot 
+preening itself", "parrot grooming itself", "parrot scratching"). For all 
+species that did not display results including object manipulation or scratching 
+behaviours, we also searched the species’ common name(s) + "tool use", as well 
+as the species’ common name(s) + "scratching". We also searched for translations 
+of the terms "parrot tool use" and "parrot scratching" in languages for all 
+countries where bird ownership was reported as >5% [@GlobalGfkSurvey], namely, 
+Turkish, Czech, Polish, French, Italian, Dutch, German, Russian, Spanish, 
+Portuguese, and Mandarin. Browser search histories were not cleared between
+searches.
+
+When we found a relevant video, we also searched for similar content uploaded by 
+the same person/channel. For each YouTube search conducted, we watched all 
+relevant videos until we reached five consecutive videos that did not feature 
+any parrots. At this point, we ended that search and initiated the next search. 
+In line with previous recommendations [@Nelson2013], we planned to exclude any 
+videos that consisted of four or more shots edited together so as to ensure the 
+behaviours being observed were not edited or manipulated, but none of the videos 
+obtained qualified for exclusion.
+
+All videos featuring parrots manipulating objects were investigated for 
+potential tool use or borderline tool use. We defined tool use as the 
+manipulation of an unattached object as an extension of the beak or foot to 
+achieve a goal towards another object, individual, or oneself [@Shumaker2011]. 
+Borderline tool use was similarly defined, except that it involved the use of an 
+object that was still attached to a substrate [@Seed2010]. For example, if 
+individuals used a fallen feather or stick for self-scratching this was defined 
+as tool use, but using one’s currently attached tail feathers or cage 
+furnishings for the same purpose was defined as borderline tool use. 
+Self-scratching had to involve slow and repeated movements of touching an object 
+to one’s body (or, in the case of borderline tool use, rubbing repetitively 
+against an attached object [@Sandor2020]).
+
+All relevant videos were coded for video length, species, tool use presence 
+(yes/borderline), tool use type (e.g., scratching, feeding), the object being 
+used (e.g., feather, stick), tool use target, human interaction 
+(talking or handing object to parrot, holding parrot), and the number of shots 
+within each video. Our complete dataset also includes the name for each video, 
+link, subject name, sex (as declared by owner, as most parrot species are not 
+sexually dimorphic), publishing date, and dates found and coded.
+
+Since YouTube is constantly growing and evolving in both its uploaded content 
+and its proprietary recommendation algorithms, the same search strategy today 
+would not return exactly the same videos as our search in July 2020. It is 
+possible that some videos have since been deleted or more videos of parrot tool
+use have since been uploaded. However, this does not affect our conclusions
+about the number of parrot species found to use tools in our initial search.
+
+### Data for parrot species
+
+We collected data for 194 parrot species (Figures
+\@ref(fig:plotPhylo2) - \@ref(fig:plotPhylo4)). We gathered feeding strategy 
+data as a dichotomous variable ("generalist" or "specialist") from the 
+EltonTraits ecological database [@Wilman2016]. As per the database, specialists 
+were defined as species whose diet comprised at least 70% of a single food 
+source. To calculate relative brain size, we collated data from the literature 
+for all known body mass (g) and brain mass (g) values across 
+parrots [@Flammer2001;@Iwaniuk2005;@Mazengenya2018;@Olkowicz2016;@Schuck2008;
+@Silva2017]. For all species for which we obtained body and brain mass data, we 
+calculated the encephalisation quotient (EQ) using the following 
+formula [@Jerison1973]: $BrainWeight / (0.12 * BodyWeight(\frac{2}{3}))$. We 
+found body mass and brain mass data for a total of 194 parrot species. This 
+included all tool-using species in our video dataset, with the exception of 
+three species: _Diopsittaca nobilis_, _Psittacara erythrogenys_, and _Coracopsis 
+vasa_. For the latter, we used values for the closely related _Coracopsis 
+nigra_. The other two species were excluded from the final dataset.
+
+For modelling purposes, we coded research effort in both the scientific 
+literature and the YouTube videos. For the scientific literature, we 
+operationalised research effort as the number of papers published for each 
+species' Latin name up to and including the first paper containing tool use for 
+that species. If no tool use had been identified in the scientific literature 
+for a species, then we coded the total number of papers published to date. We 
+used the scientific database Scopus for coding the number of published papers. 
+For the videos, we coded research effort as the number of search hits for each
+species on YouTube. If tool use had been identified on YouTube, we estimated the
+number of search hits when the first video of tool use was published on YouTube,
+assuming linear growth of search hits since the inception of YouTube. If tool
+use had not been identified, we used the current number of search hits.
+
+For phylogenetic data, we used the phylogenetic tool at www.birdtree.org
+[@Jetz2012] to compile 1000 posterior draws of phylogenetic trees for 174 of the 
+194 parrot species for which both EQ and genomic data exist. A single maximum 
+clade credibility tree was generated from these posterior draws for 
+visualisation purposes. In our analyses, we iterated over posterior draws of the 
+phylogeny to account for phylogenetic uncertainty.
+
+## Quantification and Statistical Analysis
+
+### Phylogenetic signal
+
+We used the _fitDiscrete_ function in the _ape_ R package [@Paradis2019] to 
+calculate phylogenetic signal, for both the pre-survey and post-survey tool use 
+data. We iterated the model over 100 posterior parrot phylogenies to incorporate 
+phylogenetic uncertainty.
+
+### Causal model of tool use
+
+To infer unobserved probabilities of tool use across parrots, we proposed a 
+causal model of observed tool use (Figure 1). We assumed that 
+observed tool use in the scientific literature and in the videos is caused by 
+both the unobserved presence or absence of tool use and research effort, proxied
+by the number of papers published on a species and the number of videos
+published on a species. Tool users are more likely to be observed if they are
+well studied, but understudied tool users may go undetected. In addition, based
+on theory, we also assumed that unobserved tool use is caused by feeding 
+strategy and relative brain size [@Lefebvre2004;@Lefebvre1997;@Lefebvre2002;
+@Ducatez2015;@Sol2005;@Overington2011;@HenkeVonDerMalsburg2020]. Finally, we 
+assumed that shared phylogenetic history causes unobserved confounding and 
+non-independence in unobserved tool use, feeding strategy, and relative brain 
+size across the parrot phylogeny.
+
+### Bayesian phylogenetic survival cure model
+
+Given our proposed causal model, we constructed a statistical model to impute 
+unobserved probabilities of tool use and test existing theories of the evolution 
+of tool use in parrots. To understand the model, suppose that we have the 
+following observed variables for parrot species $i$. For the scientific 
+literature, we declare $\text{N}_{\text{Lit},i}$ as the number of papers 
+published before and up to tool use identification for species $i$ (or, if tool 
+use has not been identified, the total number of papers published for species 
+$i$) and $\text{T}_{\text{Lit},i}$ as a binary variable stating whether (1) or 
+not (0) tool use has yet been observed in the scientific literature for species 
+$i$. For the videos, we declare $\text{N}_{\text{Vid},i}$ as the 
+number of videos published before and up to tool use identification for species 
+$i$ (or, if tool use has not been identified, the total number of videos 
+published for species $i$) and $\text{T}_{\text{Vid},i}$ as a binary variable 
+stating whether (1) or not (0) tool use has yet been observed in the 
+videos for species $i$. Additionally, $\text{F}_i$ and 
+$\text{EQ}_i$ are feeding strategy and encephalisation quotient values for 
+species $i$ and we have a phylogenetic distance matrix $D$ that describes the 
+patristic distances between all parrot species.
+
+We assume that species $i$ is a non-tool-user with some 
+probability $p_i$. We also assume that tool use is identified in the scientific 
+literature and the videos at constant rates $\lambda_{\text{Lit}}$ 
+and $\lambda_{\text{Vid}}$ following exponential survival functions. Given these 
+assumptions, we can then describe the different ways in which variables 
+$\text{N}_\text{Lit}$ and $\text{N}_\text{Vid}$ can be distributed. Focusing on 
+the scientific literature, if tool use has been observed 
+($\text{T}_{\text{Lit},i} = 1$), then the likelihood for 
+$\text{N}_{\text{Lit},i}$ is:
+
+\begin{align}
+\text{Pr}(\text{N}_{\text{Lit},i}|\text{T}_{\text{Lit},i} = 1,p_i,\lambda_\text{Lit}) = (1-p_i)\cdot\text{Exponential}(\text{N}_{\text{Lit},i}|\lambda_\text{Lit})
+\end{align}
+
+On the other hand, if tool use has not yet been observed 
+($\text{T}_{\text{Lit},i} = 0$), there are two ways that the outcome variable 
+could have been realised. First, the species could be a non-tool-user with 
+probability $p_i$. Second, the species could be a tool-user with probability 
+($1 - p_i$) that has been censored and has not had its tool use measured yet. 
+Together, then, the likelihood for $\text{N}_{\text{Lit},i}$ is:
+
+\begin{align}
+\text{Pr}(\text{N}_{\text{Lit},i}|\text{T}_{\text{Lit},i} = 0,p_i,\lambda_\text{Lit}) = p_i + ((1-p_i)\cdot\text{Exponential-CCDF}(\text{N}_{\text{Lit},i}|\lambda_\text{Lit}))
+\end{align}
+
+The Exponential-CCDF function allows for the censored nature of the data. The 
+same data generating process is assumed to underlie the videos.
+
+We define the mixture likelihood $\text{SurvivalCure}$ as the distribution 
+above, with parameters $p$ (the probability of being a non-tool-user) 
+and $\lambda$ (the rate of the exponential distribution). We use an 
+Ornstein-Uhlenbeck Gaussian process [@McElreath2020] to model phylogenetic 
+covariance. Below, we specify the full model with priors:
+
+\begin{align}
+\text{T}_{\text{Lit},i}, \text{N}_{\text{Lit},i} &\sim \text{SurvivalCure}(\lambda_{\text{Lit},i}, p_{i}) \\
+\text{T}_{\text{Vid},i}, \text{N}_{\text{Vid},i} &\sim \text{SurvivalCure}(\lambda_{\text{Vid},i}, p_{i}) \nonumber \\
+\lambda_{\text{Lit},i} &= 1 / \text{exp}(\gamma_\text{Lit}) \nonumber \\
+\lambda_{\text{Vid},i} &= 1 / \text{exp}(\gamma_\text{Vid}) \nonumber \\
+\text{logit}(p_{i}) &= \alpha_{\text{FEEDING}[i]} + \beta\text{EQ}_{i} +  k_{\text{SPECIES}[i]} \nonumber \\
+\begin{pmatrix}k_{1}\\k_{2}\\...\\k_{n}\\\end{pmatrix}
+&\sim \text{MVNormal}
+\begin{pmatrix}\begin{pmatrix}0\\0\\...\\0\\\end{pmatrix},\bf{K}\end{pmatrix} \nonumber \\
+\bf{K}_{ij} &= \eta^2\text{exp}(-\rho^2D_{ij}) \nonumber \\
+\gamma_\text{Lit}, \gamma_\text{Vid}, \alpha_{1,2}, \beta &\sim \text{Normal(0, 1)} \nonumber \\
+\eta^2, \rho^2 &\sim \text{Exponential(0.5)} \nonumber
+\end{align}
+
+The priors for this model produce reasonable prior predictions of the 
+probabilities of tool use for each parrot species (Figure
+\@ref(fig:plotSurvCure7)), but a sensitivity analysis revealed that the ranking 
+and posterior probabilities reported in the main text were robust to modifying 
+these priors (Figure \@ref(fig:plotSurvCure8)). We estimated the 
+posterior distribution of this model using Hamiltonian Monte Carlo as 
+implemented in Stan version 2.26.1 [@Stan2020]. We ran the model for 4000 
+samples, with 2000 warmup samples, and iterated the model over 100 posterior 
+parrot phylogenies to incorporate phylogenetic uncertainty. R-hat values and 
+effective sample sizes suggested that the model converged normally. Trace plots 
+are reported in Figure \@ref(fig:plotTrace). We report 
+equal-tailed credible intervals to describe the posterior distribution of this 
+model in the main text.
+
+To validate our method, we fitted the model to 100 simulated datasets with known 
+parameters. The model was able to successfully recover those parameters 
+(Figure \@ref(fig:plotSurvCureSim)). We also ran a 
+leave-one-species-out exercise to ensure that we could accurately predict known 
+tool users. We repeated this approach for each known tool user by setting 
+observed tool use to zero. Cross-validation results are reported in the main 
+text.
+
+### Ancestral state reconstruction
+
+To determine whether the identification of novel tool-using species has 
+implications for our understanding of the evolutionary origins of tool use in 
+parrots, we fitted three exploratory ancestral state reconstruction models. We 
+used the _ancThresh_ function from the _phytools_ R package [@phytools], 
+iterating the function over 100 posterior parrot phylogenies. This function 
+estimates discrete ancestral states by assuming the evolution of a latent 
+continuous variable following an Ornstein-Uhlenbeck process. We fitted this 
+model to three different outcome variables: (_i_) presence vs. absence of tool 
+use in scientific literature only, (_ii_) presence vs. absence of tool use in 
+literature and/or videos, and (_iii_) the median predicted probabilities of tool 
+use from the phylogenetic survival cure model.
+
+### Reproducibility
+
+All analyses were conducted in R v4.2.1. [@RCoreTeam]. Visualisations were 
+produced using the _ggtree_[@ggtree], _ggplot2_ [@Wickham2016], and _cowplot_ 
+[@Wilke2020] packages. The manuscript was reproducibly generated using the 
+_targets_ [@Landau2021] and _papaja_ [@Aust2022] packages. Code to reproduce all 
+analyses and figures can be found here: 
+https://github.com/ScottClaessens/phyloParrot
+
+\newpage
+
 # References
@@
 \newpage
-\linenumbers
-
-```{r child = "methods.Rmd"}
-```
-
-\newpage
-\nolinenumbers
 \vspace*{60mm}

### 2025-02-13 manuscript.tex
Changes for in-principle acceptance

@@
 \makeatother
-\keywords{tool use; technical intelligence; parrots; digital video platforms; phylogenetic modelling}
 \usepackage{lineno}
@@
 \note{\raggedright † These authors contributed equally to this work \par ‡ These authors contributed equally to this work \par * Correspondence concerning this article should be addressed to Scott Claessens, Level 2, Building 302, 23 Symonds Street, Auckland, New Zealand.
-\text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}} \par This working paper has not yet been peer-reviewed.}
+\text{E-mail:} \href{scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}}}
 \ifLuaTeX
@@
 \hypersetup{
-  pdftitle={New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare},
+  pdftitle={Evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare},
   pdfauthor={Amalia P. M. Bastos†,1,2, Scott Claessens*†,2, Ximena J. Nelson3, David Welch4, Quentin D. Atkinson‡,2, \& Alex H. Taylor‡,2,3,5,6},
   pdflang={en-EN},
-  pdfkeywords={tool use; technical intelligence; parrots; digital video platforms; phylogenetic modelling},
   hidelinks,
@@
 
-\title{New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare}
+\title{Evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare}
 \author{Amalia P.
@@
 unobserved species is to specify a causal model of the process that generates
-the observed data. We propose one such causal model in Figure
-\ref{fig:plotDAG}. In this model, we assume that the presence of tool use in
+the observed data. We propose one such causal model in Figure 1.
+In this model, we assume that the presence of tool use in
 the scientific literature (or on digital video platforms) is caused by both
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotDAG-1.pdf}
-\caption{\label{fig:plotDAG}\emph{Causal model of observed tool use.} Directed acyclic graph
-of the causal relationships between observed tool use and other variables.
-Available scientific data on tool use is caused both by unobserved tool use
-presence and scientific research effort (i.e., number of publications).
-Available video data on tool use is caused both by unobserved tool use
-presence and video research effort (i.e., number of videos). According to
-theory, unobserved tool use presence should be caused by relative brain size
-(encephalisation quotient) and feeding strategy (generalist vs.~specialist).
-These variables all share unobserved confounds generated by shared phylogenetic
-history. Grey circles indicate unobserved variables.}
-\end{figure}
-
 Here, we apply these approaches to tool use in the parrot order. We focus on
@@
 brain sizes\textsuperscript{46--51}, feeding strategies\textsuperscript{52}, and shared ancestry\textsuperscript{53} exist for parrots, allowing us to fit the statistical model implied
-by Figure \ref{fig:plotDAG} to the entire parrot order.
+by Figure 1 to the entire parrot order.
 
@@
 
-Figure \ref{fig:plotPhylo1} maps the findings from the video survey onto a
+Figure 2 maps the findings from the video survey onto a
 maximum clade credibility phylogeny for the parrot order, plotted alongside
@@
 by Shumaker et al.\textsuperscript{10}, compared to the 11 previously reported.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotPhylo1-1.pdf}
-\caption{\label{fig:plotPhylo1}\emph{Results of video survey and phylogenetic survival cure
-modelling mapped onto a maximum clade credibility phylogeny of the parrot order.}
-Orange points in the inner ring indicate species observed in the video survey,
-with point size scaled by the number of videos for each species (note that three
-species observed only in the video survey are not present in the phylogeny due
-to a lack of genomic data: \emph{Psittacara erythrogenys}, \emph{Psittacus timneh}, and
-\emph{Aratinga nenday}). Blue points in the outer ring indicate species observed in
-the scientific literature, with point size scaled by the number of papers
-published on each species. Yellow species names indicate the top ten most likely
-tool-using species from our phylogenetic survival cure model which were not
-observed in the scientific literature or the video survey. Total \emph{n} =
-174 species.}
-\end{figure}
 
@@
 species to have their own probability of being a non-tool-user. Following our
-causal model (Figure \ref{fig:plotDAG}), we predict these probabilities based
+causal model (Figure 1), we predict these probabilities based
 on feeding strategy, encephalisation quotient, and phylogenetic history (see
@@
 
-Figure \ref{fig:plotSurvCure1} visualises the ranked posterior probabilities of
+Figure 3 visualises the ranked posterior probabilities of
 tool use from the phylogenetic survival cure model for all parrot species. As
@@
 and 596 video search hits, which is fewer than the
-model expects are necessary to discover tool use when it is present (Figure
-\ref{fig:plotSurvCure2}). This species is also found in the \emph{Cacatua} genus, a
+model expects are necessary to discover tool use when it is present (Figure 4).
+This species is also found in the \emph{Cacatua} genus, a
 clade containing several known tool users. This prediction makes sense given the
@@
 (\emph{Ognorhynchus icterotis}), the red-vented cockatoo (\emph{Cacatua haematuropygia}),
-and the gang-gang cockatoo (\emph{Callocephalon fimbriatum}). Figure
-\ref{fig:plotPhylo1} plots these species on the parrot phylogeny, using the top
+and the gang-gang cockatoo (\emph{Callocephalon fimbriatum}). Figure 2
+plots these species on the parrot phylogeny, using the top
 ten highest ranked species without observed evidence of tool use as an arbitrary
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure1-1.pdf}
-\caption{\label{fig:plotSurvCure1}\emph{Posterior predicted probabilities of tool use for
-each species from our phylogenetic survival cure model.} Points are posterior
-medians and lines are 50\% and 95\% credible intervals. Total \emph{n} =
-174 species.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure2-1.pdf}
-\caption{\label{fig:plotSurvCure2}\emph{Expected number of published papers and videos until
-tool use discovery, according to the survival component of the phylogenetic
-survival cure model.} Densities are full posterior distributions, points are
-posterior medians, and lines are 50\% and 95\% credible intervals.}
-\end{figure}
-
-The posterior probabilities shown in Figure \ref{fig:plotSurvCure1} are
+The posterior probabilities shown in Figure 3 are
 estimated with uncertainty, so it is difficult to ``identify'' any particular
@@
 use in the parrot order. Regarding the drivers of tool use hypothesised in
-Figure \ref{fig:plotDAG}, the phylogenetic survival cure model revealed that
+Figure 1, the phylogenetic survival cure model revealed that
 encephalisation quotient strongly positively predicted the probability of tool
@@
 2.00{]}; total \emph{n} = 174
-species; Figure \ref{fig:plotSurvCure4}). This helps explain the ranking in
-Figure \ref{fig:plotSurvCure1}: the blue-eyed cockatoo has the largest relative
+species; Figure 5). This helps explain the ranking in
+Figure 3: the blue-eyed cockatoo has the largest relative
 brain size in the dataset. We also found that feeding generalist species were
@@
 respectively (Figure \ref{fig:plotComparison}).
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/plotSurvCure4-1.pdf}
-\caption{\label{fig:plotSurvCure4}\emph{Posterior predictions for the effects of feeding
-strategy and encephalisation quotient on the probability of tool use from the
-phylogenetic survival cure model.} In the left plot, points and lines represent
-posterior medians and 50\% and 95\% credible intervals, with densities
-representing full posterior distributions. In the right plot, the line and
-shaded areas represent the posterior median regression line with 50\% and 95\%
-credible intervals. In both plots, individual species are coloured according to
-the presence / absence of tool use in the video survey and the scientific
-literature. Total \emph{n} = 174 species, generalist \emph{n} =
-121 species, specialist \emph{n} =
-53 species.}
-\end{figure}
 
@@
 Figures \ref{fig:plotASR1} - \ref{fig:plotASR3}).
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tableASR}Estimated probabilities of tool use for most recent common
-ancestors of several parrot genera. \emph{Probabilities estimated using exploratory
-ancestral state reconstruction models fitted to the pre-video-survey data,
-post-video-survey data, and predicted probabilities from the phylogenetic
-survival cure model. Total} n \emph{= 174 species.}}
-
-\begin{tabular}{llll}
-\toprule
-Genus & \multicolumn{1}{c}{Pre-video-survey} & \multicolumn{1}{c}{Post-video-survey} & \multicolumn{1}{c}{Survival cure probabilities}\\
-\midrule
-\textit{Amazona} & 0.06, 95\% CI [0.01 0.17] & 0.21, 95\% CI [0.04 0.66] & 0.48, 95\% CI [0.05 0.84]\\
-\textit{Cacatua} & 0.08, 95\% CI [0.03 0.20] & 0.17, 95\% CI [0.03 0.45] & 0.81, 95\% CI [0.23 0.99]\\
-\textit{Nestor} & 0.11, 95\% CI [0.05 0.29] & 0.21, 95\% CI [0.12 0.37] & 0.53, 95\% CI [0.29 0.66]\\
-\textit{Poicephalus} & 0.06, 95\% CI [0.02 0.11] & 0.19, 95\% CI [0.12 0.41] & 0.72, 95\% CI [0.16 0.90]\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
 
@@
 highest probabilities of being undetected tool-users. Future work should also
-refine the causal model in Figure \ref{fig:plotDAG} to provide more certain
+refine the causal model in Figure 1 to provide more certain
 estimates of tool use probabilities, either by including additional predictor
@@
 
+In conclusion, we have shown that the scientific literature has insufficiently
+captured the full distribution of tool use in the parrot order. Our
+digital video survey identified novel observations of self-care tool use in
+several parrot species, more than doubling the number of known tool using parrot
+species from 11 to 28. Our phylogenetic model suggested that the true
+proportion of parrot tool users could be as high as 17\% of all species in this
+order. These discoveries have implications for theories of the evolutionary
+drivers and origins of tool use in parrots. Beyond parrot tool use, the
+methods used in this study have the potential to be applied to other rarely
+observed behaviours, including tool use in other taxa\textsuperscript{72}, rhythmic
+entrainment in birds\textsuperscript{73--76},
+teasing behaviours in primates\textsuperscript{77}, and tactical deception across all
+animals\textsuperscript{78--80}. We hope that these methods
+will continue to uncover a diverse array of ephemeral behaviours that have as
+yet gone undetected in the scientific literature.
+
 \hypertarget{limitations-of-study}{%
@@
 A potential concern with data originating from digital video platforms is its
-reliability\textsuperscript{23,72--76}.
+reliability\textsuperscript{23,81--85}.
 In particular, the self-care tool use instances detected in our video survey
@@
 repetitively over long periods of time, even across multiple different videos,
-suggesting that their behaviour was not random or accidental\textsuperscript{75}.
+suggesting that their behaviour was not random or accidental\textsuperscript{84}.
 Parrots preferentially employed self-scratching tools on areas of their body
@@
 
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
-
-In conclusion, we have shown that the scientific literature has insufficiently
-captured the full distribution of tool use in the parrot order. Our
-digital video survey identified novel observations of self-care tool use in
-several parrot species, more than doubling the number of known tool using parrot
-species from 11 to 28. Our phylogenetic model suggested that the true
-proportion of parrot tool users could be as high as 17\% of all species in this
-order. These discoveries have implications for theories of the evolutionary
-drivers and origins of tool use in parrots. Beyond parrot tool use, the
-methods used in this study have the potential to be applied to other rarely
-observed behaviours, including tool use in other taxa\textsuperscript{77}, rhythmic
-entrainment in birds\textsuperscript{78--81},
-teasing behaviours in primates\textsuperscript{82}, and tactical deception across all
-animals\textsuperscript{83--85}. We hope that these methods
-will continue to uncover a diverse array of ephemeral behaviours that have as
-yet gone undetected in the scientific literature.
-
-\newpage
-\nolinenumbers
+\newpage
+
+\hypertarget{resource-availability}{%
+\section{Resource Availability}\label{resource-availability}}
+
+\hypertarget{lead-contact}{%
+\subsection{Lead contact}\label{lead-contact}}
+
+Further information about resources should be directed to Scott Claessens
+(\href{mailto:scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}}).
+
+\hypertarget{materials-availability}{%
+\subsection{Materials availability}\label{materials-availability}}
+
+This study did not generate new unique materials.
+
+\hypertarget{data-and-code-availability}{%
+\subsection{Data and code availability}\label{data-and-code-availability}}
+
+All data and original code have been deposited on GitHub and are publicly
+available as of the date of publication. DOIs are listed in the key resources
+table (see STAR Methods).
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-MacLean2012}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{MacLean, E.L., Matthews, L.J., Hare, B.A., Nunn, C.L., Anderson, R.C., Aureli, F., Brannon, E.M., Call, J., Drea, C.M., Emery, N.J., et al.
-(2012).
-How does cognition evolve?
-Phylogenetic comparative psychology.
-Animal Cognition \emph{15}, 223--238.
-\url{https://doi.org/10.1007/s10071-011-0448-8}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2011}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Lefebvre, L. (2011). Taxonomic counts of cognition in the wild. Biology Letters \emph{7}, 631--633. \url{https://doi.org/10.1098/rsbl.2010.0556}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Logan2018}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{Logan, C.J., Avin, S., Boogert, N., Buskell, A., Cross, F.R., Currie, A., Jelbert, S., Lukas, D., Mares, R., Navarrete, A.F., et al.
-(2018).
-Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization.
-Comparative Cognition \& Behavior Reviews \emph{13}, 55--89.
-\url{https://doi.org/10.3819/CCBR.2018.130008}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Healy2007}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{Healy, S.D., and Rowe, C.
-(2007).
-A critique of comparative studies of brain size.
-Proceedings of the Royal Society B: Biological Sciences \emph{274}, 453--464.
-\url{https://doi.org/10.1098/rspb.2006.3748}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Powell2017}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{Powell, L.E., Isler, K., and Barton, R.A.
-(2017).
-Re-evaluating the link between brain size and behavioural ecology in primates.
-Proceedings of the Royal Society B: Biological Sciences \emph{284}, 20171765.
-\url{https://doi.org/10.1098/rspb.2017.1765}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodall1964}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{Goodall, J. (1964). Tool-using and aimed throwing in a community of free-living chimpanzees. Nature \emph{201}, 1264--1266.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hunt1996}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Hunt, G.R. (1996). Manufacture and use of hook-tools by {N}ew {C}aledonian crows. Nature \emph{379}, 249--251. \url{https://doi.org/10.1038/379249a0}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Smolker1997}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Smolker, R., Richards, A., Connor, R., Mann, J., and Berggren, P.
-(1997).
-Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?
-Ethology \emph{103}, 454--465.
-\url{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Finn2009}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Finn, J.K., Tregenza, T., and Norman, M.D.
-(2009).
-Defensive tool use in a coconut-carrying octopus.
-Current Biology \emph{19}, R1069--R1070.
-\url{https://doi.org/10.1016/j.cub.2009.10.052}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Shumaker, R.W., Walkup, K.R., Beck, B.B., and Burghardt, G.M.
-(2011).
-Animal tool behavior: The use and manufacture of tools by animals (Johns Hopkins University Press) \url{https://doi.org/10.1353/book.98237}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Audet2024}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Audet, J.-N., Couture, M., Lefebvre, L., and Jarvis, E.D.
-(2024).
-Problem-solving skills are predicted by technical innovations in the wild and brain size in passerines.
-Nature Ecology \& Evolution \emph{8}, 806--816.
-\url{https://doi.org/10.1038/s41559-024-02342-7}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2002}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Lefebvre, L., Nicolakakis, N., and Boire, D. (2002). Tools and brains in birds. Behaviour \emph{139}, 939--973. \url{https://doi.org/10.1163/156853902320387918}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre1997}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E., and Finkelstein, A.
-(1997).
-Feeding innovations and forebrain size in birds.
-Animal Behaviour \emph{53}, 549--560.
-\url{https://doi.org/10.1006/anbe.1996.0330}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2004}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Lefebvre, L., Reader, S.M., and Sol, D.
-(2004).
-Brains, innovations and evolution in birds and primates.
-Brain, Behavior and Evolution \emph{63}, 233--246.
-\url{https://doi.org/10.1159/000076784}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2005}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Sol, D., Duncan, R.P., Blackburn, T.M., Cassey, P., and Lefebvre, L.
-(2005).
-Big brains, enhanced cognition, and response of birds to novel environments.
-Proceedings of the National Academy of Sciences \emph{102}, 5460--5465.
-\url{https://doi.org/10.1073/pnas.0408145102}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2009}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Sol, D. (2009). Revisiting the cognitive buffer hypothesis for the evolution of large brains. Biology Letters \emph{5}, 130--133. \url{https://doi.org/10.1098/rsbl.2008.0621}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kaplan2020}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Kaplan, G. (2020). Play behaviour, not tool using, relates to brain mass in a sample of birds. Scientific Reports \emph{10}, 20437. \url{https://doi.org/10.1038/s41598-020-76572-7}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2015}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{Ducatez, S., Clavel, J., and Lefebvre, L.
-(2015).
-Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?
-Journal of Animal Ecology \emph{84}, 79--89.
-\url{https://doi.org/10.1111/1365-2656.12255}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Overington2011}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Overington, S.E., Griffin, A.S., Sol, D., and Lefebvre, L.
-(2011).
-Are innovative species ecological generalists?
-A test in {N}orth {A}merican birds.
-Behavioral Ecology \emph{22}, 1286--1293.
-\url{https://doi.org/10.1093/beheco/arr130}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2020}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
-(2020).
-Linking ecology and cognition: Does ecological specialisation predict cognitive test performance?
-Behavioral Ecology and Sociobiology \emph{74}, 154.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MettkeHofmann2014}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Mettke-Hofmann, C. (2014). Cognitive ecology: Ecological factors, life-styles, and cognition. WIREs Cognitive Science \emph{5}, 345--360. \url{https://doi.org/10.1002/wcs.1289}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2014}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{Ducatez, S., and Lefebvre, L. (2014). Patterns of research effort in birds. PLOS ONE \emph{9}, e89955. \url{https://doi.org/10.1371/journal.pone.0089955}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Nelson2013}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Nelson, X.J., and Fijn, N.
-(2013).
-The use of visual media as a tool for investigating animal behaviour.
-Animal Behaviour \emph{85}, 525--536.
-\url{https://doi.org/10.1016/j.anbehav.2012.12.009}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Krueger, K., Esch, L., and Byrne, R.
-(2019).
-Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms.
-PLOS ONE \emph{14}, 1--20.
-\url{https://doi.org/10.1371/journal.pone.0218954}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pokharel2022}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Pokharel, S.S., Sharma, N., and Sukumar, R.
-(2022).
-Viewing the rare through public lenses: Insights into dead calf carrying and other thanatological responses in {A}sian elephants using YouTube videos.
-Royal Society Open Science \emph{9}, 211740.
-\url{https://doi.org/10.1098/rsos.211740}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2009}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
-(2009).
-Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem.
-Biology Letters \emph{5}, 455--458.
-\url{https://doi.org/10.1098/rsbl.2009.0114}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2010}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
-(2010).
-Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task.
-Animal Behaviour \emph{80}, 783--789.
-\url{https://doi.org/10.1016/j.anbehav.2010.08.007}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011a}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Auersperg, A.M.I., Huber, L., and Gajdon, G.K.
-(2011).
-Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis}).
-Biology Letters \emph{7}, 825--828.
-\url{https://doi.org/10.1098/rsbl.2011.0388}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011b}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Auersperg, A.M.I., Bayern, A.M.P.
-von, Gajdon, G.K., Huber, L., and Kacelnik, A.
-(2011).
-Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm.
-PLOS ONE \emph{6}, 1--8.
-\url{https://doi.org/10.1371/journal.pone.0020231}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2012}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Auersperg, A.M.I., Szabo, B., von Bayern, A.M.P., and Kacelnik, A.
-(2012).
-Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo.
-Current Biology \emph{22}, R903--R904.
-\url{https://doi.org/10.1016/j.cub.2012.09.002}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bastos2021}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Bastos, A.P., Horváth, K., Webb, J.L., Wood, P.M., and Taylor, A.H.
-(2021).
-Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
-Scientific Reports \emph{11}, 18035.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BentleyCondit2010}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Bentley-Condit, V., and Smith, E.O.
-(2010).
-Animal tool use: Current definitions and an updated comprehensive catalog.
-Behaviour \emph{147}, 185--32A.
-\url{https://doi.org/10.1163/000579509X12512865686555}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Borsari2005}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Borsari, A., and Ottoni, E.B.
-(2005).
-Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus}).
-Animal Cognition \emph{8}, 48--52.
-\url{https://doi.org/10.1007/s10071-004-0221-3}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodman2018}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Goodman, M., Hayward, T., and Hunt, G.R.
-(2018).
-Habitual tool use innovated by free-living {N}ew {Z}ealand kea.
-Scientific Reports \emph{8}, 13935.
-\url{https://doi.org/10.1038/s41598-018-32363-9}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Heinsohn2017}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{Heinsohn, R., Zdenek, C.N., Cunningham, R.B., Endler, J.A., and Langmore, N.E.
-(2017).
-Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music.
-Science Advances \emph{3}, e1602399.
-\url{https://doi.org/10.1126/sciadv.1602399}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Janzen1976}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Janzen, M.J., Janzen, D.H., and Pond, C.M. (1976). Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). Biotropica \emph{8}, 70.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lambert2015}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Lambert, M.L., Seed, A.M., and Slocombe, K.E.
-(2015).
-A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa}).
-Biology Letters \emph{11}, 20150861.
-\url{https://doi.org/10.1098/rsbl.2015.0861}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-OHara2021}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{O'Hara, M., Mioduszewska, B., Mundry, R., Yohanna, Haryoko, T., Rachmatika, R., Prawiradilaga, D.M., Huber, L., and Auersperg, A.M.I.
-(2021).
-Wild {G}offin's cockatoos flexibly manufacture and use tool sets.
-Current Biology \emph{31}, 4512--4520.e6.
-\url{https://doi.org/10.1016/j.cub.2021.08.009}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Anderson, P.
-(2003).
-A bird in the house: An anthropological perspective on companion parrots.
-Society \& Animals \emph{11}, 393--418.
-\url{https://doi.org/10.1163/156853003322796109}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Carrete, M., and Tella, J.
-(2008).
-Wild-bird trade and exotic invasions: A new link of conservation concern?
-Frontiers in Ecology and the Environment \emph{6}, 207--211.
-\url{https://doi.org/10.1890/070075}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Drews, C.
-(2001).
-Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers.
-Society \& Animals \emph{9}, 107--126.
-\url{https://doi.org/10.1163/156853001753639233}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Kelly, D., McCarthy, E., Menzel, K., and Engebretson, M.
-(2014).
-\href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Li, L., and Jiang, Z. (2014). International trade of {CITES} listed bird species in {C}hina. PLOS ONE \emph{9}, 1--8. \url{https://doi.org/10.1371/journal.pone.0085012}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Su, S., Cassey, P., Vall-llosera, M., and Blackburn, T.M.
-(2015).
-Going cheap: Determinants of bird price in the {T}aiwanese pet market.
-PLOS ONE \emph{10}, 1--17.
-\url{https://doi.org/10.1371/journal.pone.0127482}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Young, A.M., Hobson, E.A., Lackey, L.B., and Wright, T.F.
-(2012).
-Survival on the ark: Life-history trends in captive parrots.
-Animal Conservation \emph{15}, 28--43.
-\url{https://doi.org/10.1111/j.1469-1795.2011.00477.x}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Flammer, K., Whitt-Smith, D., and Papich, M.
-(2001).
-Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection.
-Journal of Avian Medicine and Surgery \emph{15}, 276--282.
-\url{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Iwaniuk, A.N., Dean, K.M., and Nelson, J.E.
-(2005).
-Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
-Brain, Behavior and Evolution \emph{65}, 40--59.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P.R., and Ihunwo, A.O.
-(2018).
-Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh}).
-Frontiers in Neuroanatomy \emph{12}, 7.
-\url{https://doi.org/10.3389/fnana.2018.00007}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Olkowicz, S., Kocourek, M., Lučan, R.K., Porteš, M., Fitch, W.T., Herculano-Houzel, S., and Němec, P.
-(2016).
-Birds have primate-like numbers of neurons in the forebrain.
-Proceedings of the National Academy of Sciences \emph{113}, 7255--7260.
-\url{https://doi.org/10.1073/pnas.1517131113}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Schuck-Paim, C., Alonso, W.J., and Ottoni, E.B.
-(2008).
-Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots.
-Brain, Behavior and Evolution \emph{71}, 200--215.
-\url{https://doi.org/10.1159/000119710}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Silva, T., Guzmán, A., Urantówka, A.D., and Mackiewicz, P.
-(2017).
-A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny.
-PeerJ \emph{5}, e3475.
-\url{https://doi.org/10.7717/peerj.3475}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Wilman, H., Belmaker, J., Simpson, J., Rosa, C.
-de la, Rivadeneira, M.M., and Jetz, W.
-(2016).
-EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals.
-\url{https://doi.org/10.6084/m9.figshare.c.3306933.v1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Jetz, W., Thomas, G.H., Joy, J.B., Hartmann, K., and Mooers, A.O. (2012). The global diversity of birds in space and time. Nature \emph{491}, 444--448.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Seed, A., and Byrne, R. (2010). Animal tool-use. Current Biology \emph{20}, R1032--R1039. \url{https://doi.org/10.1016/j.cub.2010.09.042}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Bercovitz, A.B. (1987). Avian sex identification techniques. In Companion bird medicine, E. W. Burr, ed. (Iowa State University Press).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Hoyo, J.D., and Bierregaard, R. (2011). Handbook of the birds of the world (Lynx Edicions).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Amico, M., and Van Keilegom, I.
-(2018).
-Cure models in survival analysis.
-Annual Review of Statistics and Its Application \emph{5}, 311--342.
-\url{https://doi.org/10.1146/annurev-statistics-031017-100101}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Schmidt, P., and Witte, A.D.
-(1989).
-Predicting criminal recidivism using {``split population''} survival time models.
-Journal of Econometrics \emph{40}, 141--159.
-\url{https://doi.org/10.1016/0304-4076(89)90034-1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Wallace, A.R. (1869). The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature (MacMillan; Co.).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Goodall1971}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{Goodall, J.
-(1971).
-Tool-using in primates and other vertebrates.
-In Advances in the study of behavior., D.
-S.
-Lehrman, R.
-A.
-Hinde, and E.
-Shaw, eds.
-(Academic Press), pp.
-195--249.
-\url{https://doi.org/10.1016/S0065-3454(08)60157-6}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wood1984}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Wood, G.A. (1984). Tool use by the palm cockatoo \emph{{P}robosciger aterrimus} during display. Corella \emph{8}, 94--95.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{Fragaszy, D.M., and Mangalam, M.
-(2018).
-Tooling.
-In Advances in the study of behavior., M.
-Naguib, L.
-Barrett, S.
-D.
-Healy, J.
-Podos, L.
-W.
-Simmons, and M.
-Zuk, eds.
-(Academic Press), pp.
-177--241.
-\url{https://doi.org/10.1016/bs.asb.2018.01.001}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Aydinonat2014}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Aydinonat, D., Penn, D.J., Smith, S., Moodley, Y., Hoelzl, F., Knauer, F., and Schwarzenberger, F.
-(2014).
-Social isolation shortens telomeres in {A}frican {G}rey parrots (\emph{{P}sittacus erithacus erithacus}).
-PLOS ONE \emph{9}, e93839.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Engebretson2006}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Engebretson, M. (2006). The welfare and suitability of parrots as companion animals: A review. Animal Welfare \emph{15}, 263--276. \url{https://doi.org/10.1017/S0962728600030475}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mason2010}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Mason, G.J.
-(2010).
-Species differences in responses to captivity: Stress, welfare and the comparative method.
-Trends in Ecology \& Evolution \emph{25}, 713--721.
-\url{https://doi.org/10.1016/j.tree.2010.08.011}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Meehan2003}{}}%
-\CSLLeftMargin{66. }%
-\CSLRightInline{Meehan, C., Garner, J., and Mench, J.
-(2003).
-Isosexual pair housing improves the welfare of young amazon parrots.
-Applied Animal Behaviour Science \emph{81}, 73--88.
-\url{https://doi.org/10.1016/S0168-1591(02)00238-1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
-\CSLLeftMargin{67. }%
-\CSLRightInline{Reader, S.M., and Laland, K.N.
-(2002).
-Social intelligence, innovation, and enhanced brain size in primates.
-Proceedings of the National Academy of Sciences \emph{99}, 4436--4441.
-\url{https://doi.org/10.1073/pnas.062041299}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
-\CSLLeftMargin{68. }%
-\CSLRightInline{Sol, D., Olkowicz, S., Sayol, F., Kocourek, M., Zhang, Y., Marhounová, L., Osadnik, C., Corssmit, E., Garcia-Porta, J., Martin, T.E., et al.
-(2022).
-Neuron numbers link innovativeness with both absolute and relative brain size in birds.
-Nature Ecology \& Evolution \emph{6}, 1381--1389.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{Cabrera-Álvarez, M.J., and Clayton, N.S.
-(2020).
-Neural processes underlying tool use in humans, macaques, and corvids.
-Frontiers in Psychology \emph{11}, 560669.
-\url{https://doi.org/10.3389/fpsyg.2020.560669}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
-\CSLLeftMargin{70. }%
-\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
-(2021).
-Linking cognition to ecology in wild sympatric mouse lemur species.
-Proceedings of the Royal Society B: Biological Sciences \emph{288}, 20211728.
-\url{https://doi.org/10.1098/rspb.2021.1728}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{Debastiani, V.J., Bastazini, V.A.G., and Pillar, V.D.
-(2021).
-Using phylogenetic information to impute missing functional trait values in ecological databases.
-Ecological Informatics \emph{63}, 101315.
-\url{https://doi.org/10.1016/j.ecoinf.2021.101315}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2020}{}}%
-\CSLLeftMargin{72. }%
-\CSLRightInline{Auersperg, A.M.I., Schwing, R., Mioduszewska, B., O'Hara, M., and Huber, L.
-(2020).
-Do puffins use tools?
-Proceedings of the National Academy of Sciences \emph{117}, 11859--11859.
-\url{https://doi.org/10.1073/pnas.2001988117}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DechaumeMoncharmont2020}{}}%
-\CSLLeftMargin{73. }%
-\CSLRightInline{Dechaume-Moncharmont, F.-X.
-(2020).
-Touchy matter: The delicate balance between {M}organ's canon and open-minded description of advanced cognitive skills in the animal.
-Peer Community in Ecology, 100042.
-\url{https://doi.org/10.24072/pci.ecology.100042}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Farrar2020}{}}%
-\CSLLeftMargin{74. }%
-\CSLRightInline{Farrar, B.G. (2020). Evidence of tool use in a seabird? PsyArXiv. \url{https://doi.org/10.31234/osf.io/463hk}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
-\CSLLeftMargin{75. }%
-\CSLRightInline{Sándor, K., and Miklósi, Á.
-(2020).
-How to report anecdotal observations?
-A new approach based on a lesson from "puffin tool use".
-Frontiers in Psychology \emph{11}, 555487.
-\url{https://doi.org/10.3389/fpsyg.2020.555487}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vonBayern2020}{}}%
-\CSLLeftMargin{76. }%
-\CSLRightInline{von Bayern, A.M., Jacobs, I., and Osvath, M.
-(2020).
-Tool-using puffins prickle the puzzle of cognitive evolution.
-Proceedings of the National Academy of Sciences \emph{117}, 2737--2739.
-\url{https://doi.org/10.1073/pnas.1922117117}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
-\CSLLeftMargin{77. }%
-\CSLRightInline{Hunt, G.R., Gray, R.D., and Taylor, A.H.
-(2013).
-Why is tool use rare in animals?
-In Tool use in animals: Cognition and ecology, C.
-M.
-Sanz, J.
-Call, and C.
-Boesch, eds.
-(Cambridge University Press), pp.
-89--118.
-\url{https://doi.org/10.1017/CBO9780511894800.007}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
-\CSLLeftMargin{78. }%
-\CSLRightInline{Benichov, J.I., Globerson, E., and Tchernichovski, O.
-(2016).
-Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans.
-Frontiers in Human Neuroscience \emph{10}.
-\url{https://doi.org/10.3389/fnhum.2016.00255}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
-\CSLLeftMargin{79. }%
-\CSLRightInline{Patel, A.D., Iversen, J.R., Bregman, M.R., and Schulz, I.
-(2009).
-Experimental evidence for synchronization to a musical beat in a nonhuman animal.
-Current Biology \emph{19}, 827--830.
-\url{https://doi.org/10.1016/j.cub.2009.03.038}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
-\CSLLeftMargin{80. }%
-\CSLRightInline{ten Cate, C., Spierings, M., Hubert, J., and Honing, H.
-(2016).
-Can birds perceive rhythmic patterns?
-A review and experiments on a songbird and a parrot species.
-Frontiers in Psychology \emph{7}.
-\url{https://doi.org/10.3389/fpsyg.2016.00730}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
-\CSLLeftMargin{81. }%
-\CSLRightInline{Wilson, M., and Cook, P.F.
-(2016).
-Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed.
-Psychonomic Bulletin \& Review \emph{23}, 1647--1659.
-\url{https://doi.org/10.3758/s13423-016-1013-x}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
-\CSLLeftMargin{82. }%
-\CSLRightInline{Eckert, J., Winkler, S.L., and Cartmill, E.A.
-(2020).
-Just kidding: The evolutionary roots of playful teasing.
-Biology Letters \emph{16}, 20200370.
-\url{https://doi.org/10.1098/rsbl.2020.0370}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
-\CSLLeftMargin{83. }%
-\CSLRightInline{Bro-Jørgensen, J., and Pangle, W.M.
-(2010).
-Male topi antelopes alarm snort deceptively to retain females for mating.
-The American Naturalist \emph{176}, E33--E39.
-\url{https://doi.org/10.1086/653078}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
-\CSLLeftMargin{84. }%
-\CSLRightInline{Byrne, R.W., and Whiten, A.
-(1988).
-Toward the next generation in data quality: A new survey of primate tactical deception.
-Behavioral and Brain Sciences \emph{11}, 267--273.
-\url{https://doi.org/10.1017/S0140525X00049955}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
-\CSLLeftMargin{85. }%
-\CSLRightInline{Byrne, R.W., and Whiten, A.
-(1991).
-Computation and mindreading in primate tactical deception.
-In Natural theories of mind: Evolution, development and simulation of everyday mindreading, A.
-Whiten, ed.
-(Basil Blackwell), pp.
-127--141.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
-\CSLLeftMargin{86. }%
-\CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership} (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
-\CSLLeftMargin{87. }%
-\CSLRightInline{Jerison, H.J. (1973). Evolution of the brain and intelligence (Academic Press).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
-\CSLLeftMargin{88. }%
-\CSLRightInline{Paradis, E., and Schliep, K.
-(2019).
-{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}.
-Bioinformatics \emph{35}, 526--528.
-\url{https://doi.org/10.1093/bioinformatics/bty633}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
-\CSLLeftMargin{89. }%
-\CSLRightInline{McElreath, R.
-(2020).
-\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition} 2nd ed.
-(CRC Press).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
-\CSLLeftMargin{90. }%
-\CSLRightInline{Stan Development Team (2020). \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
-\CSLLeftMargin{91. }%
-\CSLRightInline{Revell, L.J.
-(2012).
-{phytools}: An {R} package for phylogenetic comparative biology (and other things).
-Methods in Ecology and Evolution \emph{3}, 217--223.
-\url{https://doi.org/10.1111/j.2041-210X.2011.00169.x}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
-\CSLLeftMargin{92. }%
-\CSLRightInline{R Core Team (2022). \href{https://www.R-project.org/}{R: A language and environment for statistical computing} (R Foundation for Statistical Computing).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
-\CSLLeftMargin{93. }%
-\CSLRightInline{Yu, G., Smith, D., Zhu, H., Guan, Y., and Lam, T.T.-Y.
-(2017).
-{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data.
-Methods in Ecology and Evolution \emph{8}, 28--36.
-\url{https://doi.org/10.1111/2041-210X.12628}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-\CSLLeftMargin{94. }%
-\CSLRightInline{Wickham, H. (2016). \href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis} (Springer-Verlag New York).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
-\CSLLeftMargin{95. }%
-\CSLRightInline{Wilke, C.O. (2020). \href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
-\CSLLeftMargin{96. }%
-\CSLRightInline{Landau, W.M.
-(2021).
-The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing.
-Journal of Open Source Software \emph{6}, 2959.
-\url{https://doi.org/10.21105/joss.02959}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
-\CSLLeftMargin{97. }%
-\CSLRightInline{Aust, F., and Barth, M. (2022). \href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}.}
-
-\end{CSLReferences}
-
-\endgroup
-
-\newpage
-\linenumbers
+\hypertarget{main-figures}{%
+\section{Main figures}\label{main-figures}}
+
+\emph{Figure 1. Causal model of observed tool use.} Directed acyclic graph
+of the causal relationships between observed tool use and other variables.
+Available scientific data on tool use is caused both by unobserved tool use
+presence and scientific research effort (i.e., number of publications).
+Available video data on tool use is caused both by unobserved tool use
+presence and video research effort (i.e., number of videos). According to
+theory, unobserved tool use presence should be caused by relative brain size
+(encephalisation quotient) and feeding strategy (generalist vs.~specialist).
+These variables all share unobserved confounds generated by shared phylogenetic
+history. Grey circles indicate unobserved variables.
+
+\emph{Figure 2. Results of video survey and phylogenetic survival cure modelling mapped onto a maximum clade credibility phylogeny of the parrot order.}
+Orange points in the inner ring indicate species observed in the video survey,
+with point size scaled by the number of videos for each species (note that three
+species observed only in the video survey are not present in the phylogeny due
+to a lack of genomic data: \emph{Psittacara erythrogenys}, \emph{Psittacus timneh}, and
+\emph{Aratinga nenday}). Blue points in the outer ring indicate species observed in
+the scientific literature, with point size scaled by the number of papers
+published on each species. Yellow species names indicate the top ten most likely
+tool-using species from our phylogenetic survival cure model which were not
+observed in the scientific literature or the video survey. Total \emph{n} =
+174 species.
+
+\emph{Figure 3. Posterior predicted probabilities of tool use for each species from our phylogenetic survival cure model.}
+Points are posterior medians and lines are 50\% and 95\% credible intervals.
+Total \emph{n} = 174 species.
+
+\emph{Figure 4. Expected number of published papers and videos until tool use discovery, according to the survival component of the phylogenetic survival cure model.}
+Densities are full posterior distributions, points are
+posterior medians, and lines are 50\% and 95\% credible intervals.
+
+\emph{Figure 5. Posterior predictions for the effects of feeding strategy and encephalisation quotient on the probability of tool use from the phylogenetic survival cure model.}
+In the left plot, points and lines represent
+posterior medians and 50\% and 95\% credible intervals, with densities
+representing full posterior distributions. In the right plot, the line and
+shaded areas represent the posterior median regression line with 50\% and 95\%
+credible intervals. In both plots, individual species are coloured according to
+the presence / absence of tool use in the video survey and the scientific
+literature. Total \emph{n} = 174 species, generalist \emph{n} =
+121 species, specialist \emph{n} =
+53 species.
+
+\newpage
+
+\hypertarget{main-tables}{%
+\section{Main tables}\label{main-tables}}
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tableASR}Estimated probabilities of tool use for most recent common
+ancestors of several parrot genera. \emph{Probabilities estimated using exploratory
+ancestral state reconstruction models fitted to the pre-video-survey data,
+post-video-survey data, and predicted probabilities from the phylogenetic
+survival cure model. Total} n \emph{= 174 species.}}
+
+\begin{tabular}{llll}
+\toprule
+Genus & \multicolumn{1}{c}{Pre-video-survey} & \multicolumn{1}{c}{Post-video-survey} & \multicolumn{1}{c}{Survival cure probabilities}\\
+\midrule
+\textit{Amazona} & 0.06, 95\% CI [0.01 0.17] & 0.21, 95\% CI [0.04 0.66] & 0.48, 95\% CI [0.05 0.84]\\
+\textit{Cacatua} & 0.08, 95\% CI [0.03 0.20] & 0.17, 95\% CI [0.03 0.45] & 0.81, 95\% CI [0.23 0.99]\\
+\textit{Nestor} & 0.11, 95\% CI [0.05 0.29] & 0.21, 95\% CI [0.12 0.37] & 0.53, 95\% CI [0.29 0.66]\\
+\textit{Poicephalus} & 0.06, 95\% CI [0.02 0.11] & 0.19, 95\% CI [0.12 0.41] & 0.72, 95\% CI [0.16 0.90]\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
 
@@
 \section{STAR Methods}\label{star-methods}}
-
-\hypertarget{resource-availability}{%
-\subsection{Resource Availability}\label{resource-availability}}
-
-\hypertarget{lead-contact}{%
-\subsubsection{Lead contact}\label{lead-contact}}
-
-Further information about resources should be directed to Scott Claessens
-(\href{mailto:scott.claessens@gmail.com}{\nolinkurl{scott.claessens@gmail.com}}).
-
-\hypertarget{materials-availability}{%
-\subsubsection{Materials availability}\label{materials-availability}}
-
-This study did not generate new unique materials.
-
-\hypertarget{data-and-code-availability}{%
-\subsubsection{Data and code availability}\label{data-and-code-availability}}
-
-All data have been deposited on GitHub and are publicly available as of the date
-of publication. DOIs are listed in the key resources table.
-
-All original code has been deposited on GitHub and is publicly available as of
-the date of publication. DOIs are listed in the key resources table.
 
@@
 to one's body (or, in the case of borderline tool use, rubbing repetitively
-against an attached object\textsuperscript{75}).
+against an attached object\textsuperscript{84}).
 
@@
 To infer unobserved probabilities of tool use across parrots, we proposed a
-causal model of observed tool use (Figure \ref{fig:plotDAG}). We assumed that
+causal model of observed tool use (Figure 1). We assumed that
 observed tool use in the scientific literature and in the videos is caused by
@@
 \newpage
-\nolinenumbers
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-MacLean2012}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{MacLean, E.L., Matthews, L.J., Hare, B.A., Nunn, C.L., Anderson, R.C., Aureli, F., Brannon, E.M., Call, J., Drea, C.M., Emery, N.J., et al.
+(2012).
+How does cognition evolve?
+Phylogenetic comparative psychology.
+Animal Cognition \emph{15}, 223--238.
+\url{https://doi.org/10.1007/s10071-011-0448-8}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2011}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Lefebvre, L. (2011). Taxonomic counts of cognition in the wild. Biology Letters \emph{7}, 631--633. \url{https://doi.org/10.1098/rsbl.2010.0556}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Logan2018}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{Logan, C.J., Avin, S., Boogert, N., Buskell, A., Cross, F.R., Currie, A., Jelbert, S., Lukas, D., Mares, R., Navarrete, A.F., et al.
+(2018).
+Beyond brain size: Uncovering the neural correlates of behavioral and cognitive specialization.
+Comparative Cognition \& Behavior Reviews \emph{13}, 55--89.
+\url{https://doi.org/10.3819/CCBR.2018.130008}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Healy2007}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Healy, S.D., and Rowe, C.
+(2007).
+A critique of comparative studies of brain size.
+Proceedings of the Royal Society B: Biological Sciences \emph{274}, 453--464.
+\url{https://doi.org/10.1098/rspb.2006.3748}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Powell2017}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Powell, L.E., Isler, K., and Barton, R.A.
+(2017).
+Re-evaluating the link between brain size and behavioural ecology in primates.
+Proceedings of the Royal Society B: Biological Sciences \emph{284}, 20171765.
+\url{https://doi.org/10.1098/rspb.2017.1765}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodall1964}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Goodall, J. (1964). Tool-using and aimed throwing in a community of free-living chimpanzees. Nature \emph{201}, 1264--1266.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hunt1996}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Hunt, G.R. (1996). Manufacture and use of hook-tools by {N}ew {C}aledonian crows. Nature \emph{379}, 249--251. \url{https://doi.org/10.1038/379249a0}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Smolker1997}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Smolker, R., Richards, A., Connor, R., Mann, J., and Berggren, P.
+(1997).
+Sponge carrying by dolphins ({D}elphinidae, \emph{{T}ursiops} sp.): A foraging specialization involving tool use?
+Ethology \emph{103}, 454--465.
+\url{https://doi.org/10.1111/j.1439-0310.1997.tb00160.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Finn2009}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Finn, J.K., Tregenza, T., and Norman, M.D.
+(2009).
+Defensive tool use in a coconut-carrying octopus.
+Current Biology \emph{19}, R1069--R1070.
+\url{https://doi.org/10.1016/j.cub.2009.10.052}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Shumaker2011}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Shumaker, R.W., Walkup, K.R., Beck, B.B., and Burghardt, G.M.
+(2011).
+Animal tool behavior: The use and manufacture of tools by animals (Johns Hopkins University Press) \url{https://doi.org/10.1353/book.98237}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Audet2024}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Audet, J.-N., Couture, M., Lefebvre, L., and Jarvis, E.D.
+(2024).
+Problem-solving skills are predicted by technical innovations in the wild and brain size in passerines.
+Nature Ecology \& Evolution \emph{8}, 806--816.
+\url{https://doi.org/10.1038/s41559-024-02342-7}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2002}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Lefebvre, L., Nicolakakis, N., and Boire, D. (2002). Tools and brains in birds. Behaviour \emph{139}, 939--973. \url{https://doi.org/10.1163/156853902320387918}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre1997}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Lefebvre, L., Whittle, P., Lascaris, E., and Finkelstein, A.
+(1997).
+Feeding innovations and forebrain size in birds.
+Animal Behaviour \emph{53}, 549--560.
+\url{https://doi.org/10.1006/anbe.1996.0330}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lefebvre2004}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Lefebvre, L., Reader, S.M., and Sol, D.
+(2004).
+Brains, innovations and evolution in birds and primates.
+Brain, Behavior and Evolution \emph{63}, 233--246.
+\url{https://doi.org/10.1159/000076784}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2005}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Sol, D., Duncan, R.P., Blackburn, T.M., Cassey, P., and Lefebvre, L.
+(2005).
+Big brains, enhanced cognition, and response of birds to novel environments.
+Proceedings of the National Academy of Sciences \emph{102}, 5460--5465.
+\url{https://doi.org/10.1073/pnas.0408145102}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2009}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Sol, D. (2009). Revisiting the cognitive buffer hypothesis for the evolution of large brains. Biology Letters \emph{5}, 130--133. \url{https://doi.org/10.1098/rsbl.2008.0621}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kaplan2020}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Kaplan, G. (2020). Play behaviour, not tool using, relates to brain mass in a sample of birds. Scientific Reports \emph{10}, 20437. \url{https://doi.org/10.1038/s41598-020-76572-7}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2015}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{Ducatez, S., Clavel, J., and Lefebvre, L.
+(2015).
+Ecological generalism and behavioural innovation in birds: Technical intelligence or the simple incorporation of new foods?
+Journal of Animal Ecology \emph{84}, 79--89.
+\url{https://doi.org/10.1111/1365-2656.12255}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Overington2011}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{Overington, S.E., Griffin, A.S., Sol, D., and Lefebvre, L.
+(2011).
+Are innovative species ecological generalists?
+A test in {N}orth {A}merican birds.
+Behavioral Ecology \emph{22}, 1286--1293.
+\url{https://doi.org/10.1093/beheco/arr130}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2020}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
+(2020).
+Linking ecology and cognition: Does ecological specialisation predict cognitive test performance?
+Behavioral Ecology and Sociobiology \emph{74}, 154.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MettkeHofmann2014}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Mettke-Hofmann, C. (2014). Cognitive ecology: Ecological factors, life-styles, and cognition. WIREs Cognitive Science \emph{5}, 345--360. \url{https://doi.org/10.1002/wcs.1289}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ducatez2014}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{Ducatez, S., and Lefebvre, L. (2014). Patterns of research effort in birds. PLOS ONE \emph{9}, e89955. \url{https://doi.org/10.1371/journal.pone.0089955}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Nelson2013}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{Nelson, X.J., and Fijn, N.
+(2013).
+The use of visual media as a tool for investigating animal behaviour.
+Animal Behaviour \emph{85}, 525--536.
+\url{https://doi.org/10.1016/j.anbehav.2012.12.009}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Krueger2019}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{Krueger, K., Esch, L., and Byrne, R.
+(2019).
+Animal behaviour in a human world: A crowdsourcing study on horses that open door and gate mechanisms.
+PLOS ONE \emph{14}, 1--20.
+\url{https://doi.org/10.1371/journal.pone.0218954}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pokharel2022}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{Pokharel, S.S., Sharma, N., and Sukumar, R.
+(2022).
+Viewing the rare through public lenses: Insights into dead calf carrying and other thanatological responses in {A}sian elephants using YouTube videos.
+Royal Society Open Science \emph{9}, 211740.
+\url{https://doi.org/10.1098/rsos.211740}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2009}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
+(2009).
+Kea (\emph{{N}estor notabilis}) consider spatial relationships between objects in the support problem.
+Biology Letters \emph{5}, 455--458.
+\url{https://doi.org/10.1098/rsbl.2009.0114}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2010}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{Auersperg, A.M.I., Gajdon, G.K., and Huber, L.
+(2010).
+Kea, \emph{{N}estor notabilis}, produce dynamic relationships between objects in a second-order tool use task.
+Animal Behaviour \emph{80}, 783--789.
+\url{https://doi.org/10.1016/j.anbehav.2010.08.007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011a}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Auersperg, A.M.I., Huber, L., and Gajdon, G.K.
+(2011).
+Navigating a tool end in a specific direction: Stick-tool use in kea (\emph{{N}estor notabilis}).
+Biology Letters \emph{7}, 825--828.
+\url{https://doi.org/10.1098/rsbl.2011.0388}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2011b}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Auersperg, A.M.I., Bayern, A.M.P.
+von, Gajdon, G.K., Huber, L., and Kacelnik, A.
+(2011).
+Flexibility in problem solving and tool use of kea and {N}ew {C}aledonian crows in a multi access box paradigm.
+PLOS ONE \emph{6}, 1--8.
+\url{https://doi.org/10.1371/journal.pone.0020231}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2012}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Auersperg, A.M.I., Szabo, B., von Bayern, A.M.P., and Kacelnik, A.
+(2012).
+Spontaneous innovation in tool manufacture and use in a {G}offin's cockatoo.
+Current Biology \emph{22}, R903--R904.
+\url{https://doi.org/10.1016/j.cub.2012.09.002}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bastos2021}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Bastos, A.P., Horváth, K., Webb, J.L., Wood, P.M., and Taylor, A.H.
+(2021).
+Self-care tooling innovation in a disabled kea (\emph{{N}estor notabilis}).
+Scientific Reports \emph{11}, 18035.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-BentleyCondit2010}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{Bentley-Condit, V., and Smith, E.O.
+(2010).
+Animal tool use: Current definitions and an updated comprehensive catalog.
+Behaviour \emph{147}, 185--32A.
+\url{https://doi.org/10.1163/000579509X12512865686555}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Borsari2005}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Borsari, A., and Ottoni, E.B.
+(2005).
+Preliminary observations of tool use in captive hyacinth macaws (\emph{{A}nodorhynchus hyacinthinus}).
+Animal Cognition \emph{8}, 48--52.
+\url{https://doi.org/10.1007/s10071-004-0221-3}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodman2018}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{Goodman, M., Hayward, T., and Hunt, G.R.
+(2018).
+Habitual tool use innovated by free-living {N}ew {Z}ealand kea.
+Scientific Reports \emph{8}, 13935.
+\url{https://doi.org/10.1038/s41598-018-32363-9}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Heinsohn2017}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{Heinsohn, R., Zdenek, C.N., Cunningham, R.B., Endler, J.A., and Langmore, N.E.
+(2017).
+Tool-assisted rhythmic drumming in palm cockatoos shares key elements of human instrumental music.
+Science Advances \emph{3}, e1602399.
+\url{https://doi.org/10.1126/sciadv.1602399}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Janzen1976}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Janzen, M.J., Janzen, D.H., and Pond, C.M. (1976). Tool-using by the {A}frican grey parrot (\emph{{P}sittacus erithacus}). Biotropica \emph{8}, 70.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lambert2015}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Lambert, M.L., Seed, A.M., and Slocombe, K.E.
+(2015).
+A novel form of spontaneous tool use displayed by several captive greater vasa parrots (\emph{{C}oracopsis vasa}).
+Biology Letters \emph{11}, 20150861.
+\url{https://doi.org/10.1098/rsbl.2015.0861}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-OHara2021}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{O'Hara, M., Mioduszewska, B., Mundry, R., Yohanna, Haryoko, T., Rachmatika, R., Prawiradilaga, D.M., Huber, L., and Auersperg, A.M.I.
+(2021).
+Wild {G}offin's cockatoos flexibly manufacture and use tool sets.
+Current Biology \emph{31}, 4512--4520.e6.
+\url{https://doi.org/10.1016/j.cub.2021.08.009}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Anderson2003}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{Anderson, P.
+(2003).
+A bird in the house: An anthropological perspective on companion parrots.
+Society \& Animals \emph{11}, 393--418.
+\url{https://doi.org/10.1163/156853003322796109}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Carrete2008}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{Carrete, M., and Tella, J.
+(2008).
+Wild-bird trade and exotic invasions: A new link of conservation concern?
+Frontiers in Ecology and the Environment \emph{6}, 207--211.
+\url{https://doi.org/10.1890/070075}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Drews2001}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{Drews, C.
+(2001).
+Wild animals and other pets kept in {C}osta {R}ican households: Incidence, species and numbers.
+Society \& Animals \emph{9}, 107--126.
+\url{https://doi.org/10.1163/156853001753639233}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kelly2014}{}}%
+\CSLLeftMargin{42. }%
+\CSLRightInline{Kelly, D., McCarthy, E., Menzel, K., and Engebretson, M.
+(2014).
+\href{https://www.avianwelfare.org/issues/overview.htm}{How many captive birds: Are population studies giving us a clear picture?}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Li2014}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{Li, L., and Jiang, Z. (2014). International trade of {CITES} listed bird species in {C}hina. PLOS ONE \emph{9}, 1--8. \url{https://doi.org/10.1371/journal.pone.0085012}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Su2015}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{Su, S., Cassey, P., Vall-llosera, M., and Blackburn, T.M.
+(2015).
+Going cheap: Determinants of bird price in the {T}aiwanese pet market.
+PLOS ONE \emph{10}, 1--17.
+\url{https://doi.org/10.1371/journal.pone.0127482}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Young2012}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{Young, A.M., Hobson, E.A., Lackey, L.B., and Wright, T.F.
+(2012).
+Survival on the ark: Life-history trends in captive parrots.
+Animal Conservation \emph{15}, 28--43.
+\url{https://doi.org/10.1111/j.1469-1795.2011.00477.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Flammer2001}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{Flammer, K., Whitt-Smith, D., and Papich, M.
+(2001).
+Plasma concentrations of doxycycline in selected psittacine birds when administered in water for potential treatment of \emph{{C}hlamydophila psittaci} infection.
+Journal of Avian Medicine and Surgery \emph{15}, 276--282.
+\url{https://doi.org/10.1647/1082-6742(2001)015\%5B0276:PCODIS\%5D2.0.CO;2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Iwaniuk2005}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{Iwaniuk, A.N., Dean, K.M., and Nelson, J.E.
+(2005).
+Interspecific allometry of the brain and brain regions in parrots ({P}sittaciformes): Comparisons with other birds and primates.
+Brain, Behavior and Evolution \emph{65}, 40--59.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mazengenya2018}{}}%
+\CSLLeftMargin{48. }%
+\CSLRightInline{Mazengenya, P., Bhagwandin, A., Manger, P.R., and Ihunwo, A.O.
+(2018).
+Putative adult neurogenesis in {O}ld {W}orld parrots: The {C}ongo {A}frican grey parrot (\emph{{P}sittacus erithacus}) and {T}imneh grey parrot (\emph{{P}sittacus timneh}).
+Frontiers in Neuroanatomy \emph{12}, 7.
+\url{https://doi.org/10.3389/fnana.2018.00007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Olkowicz2016}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{Olkowicz, S., Kocourek, M., Lučan, R.K., Porteš, M., Fitch, W.T., Herculano-Houzel, S., and Němec, P.
+(2016).
+Birds have primate-like numbers of neurons in the forebrain.
+Proceedings of the National Academy of Sciences \emph{113}, 7255--7260.
+\url{https://doi.org/10.1073/pnas.1517131113}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schuck2008}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{Schuck-Paim, C., Alonso, W.J., and Ottoni, E.B.
+(2008).
+Cognition in an ever-changing world: Climatic variability is associated with brain size in neotropical parrots.
+Brain, Behavior and Evolution \emph{71}, 200--215.
+\url{https://doi.org/10.1159/000119710}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Silva2017}{}}%
+\CSLLeftMargin{51. }%
+\CSLRightInline{Silva, T., Guzmán, A., Urantówka, A.D., and Mackiewicz, P.
+(2017).
+A new parrot taxon from the {Y}ucat{á}n {P}eninsula, {M}exico---its position within genus \emph{{A}mazona} based on morphology and molecular phylogeny.
+PeerJ \emph{5}, e3475.
+\url{https://doi.org/10.7717/peerj.3475}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilman2016}{}}%
+\CSLLeftMargin{52. }%
+\CSLRightInline{Wilman, H., Belmaker, J., Simpson, J., Rosa, C.
+de la, Rivadeneira, M.M., and Jetz, W.
+(2016).
+EltonTraits 1.0: Species-level foraging attributes of the world's birds and mammals.
+\url{https://doi.org/10.6084/m9.figshare.c.3306933.v1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jetz2012}{}}%
+\CSLLeftMargin{53. }%
+\CSLRightInline{Jetz, W., Thomas, G.H., Joy, J.B., Hartmann, K., and Mooers, A.O. (2012). The global diversity of birds in space and time. Nature \emph{491}, 444--448.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Seed2010}{}}%
+\CSLLeftMargin{54. }%
+\CSLRightInline{Seed, A., and Byrne, R. (2010). Animal tool-use. Current Biology \emph{20}, R1032--R1039. \url{https://doi.org/10.1016/j.cub.2010.09.042}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bercovitz1987}{}}%
+\CSLLeftMargin{55. }%
+\CSLRightInline{Bercovitz, A.B. (1987). Avian sex identification techniques. In Companion bird medicine, E. W. Burr, ed. (Iowa State University Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hoyo2011}{}}%
+\CSLLeftMargin{56. }%
+\CSLRightInline{Hoyo, J.D., and Bierregaard, R. (2011). Handbook of the birds of the world (Lynx Edicions).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Amico2018}{}}%
+\CSLLeftMargin{57. }%
+\CSLRightInline{Amico, M., and Van Keilegom, I.
+(2018).
+Cure models in survival analysis.
+Annual Review of Statistics and Its Application \emph{5}, 311--342.
+\url{https://doi.org/10.1146/annurev-statistics-031017-100101}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt1989}{}}%
+\CSLLeftMargin{58. }%
+\CSLRightInline{Schmidt, P., and Witte, A.D.
+(1989).
+Predicting criminal recidivism using {``split population''} survival time models.
+Journal of Econometrics \emph{40}, 141--159.
+\url{https://doi.org/10.1016/0304-4076(89)90034-1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wallace1869}{}}%
+\CSLLeftMargin{59. }%
+\CSLRightInline{Wallace, A.R. (1869). The {M}alay {A}rchipelago: The land of the orang-utan and the bird of paradise; a narrative of travel, with the studies of man and nature (MacMillan; Co.).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Goodall1971}{}}%
+\CSLLeftMargin{60. }%
+\CSLRightInline{Goodall, J.
+(1971).
+Tool-using in primates and other vertebrates.
+In Advances in the study of behavior., D.
+S.
+Lehrman, R.
+A.
+Hinde, and E.
+Shaw, eds.
+(Academic Press), pp.
+195--249.
+\url{https://doi.org/10.1016/S0065-3454(08)60157-6}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wood1984}{}}%
+\CSLLeftMargin{61. }%
+\CSLRightInline{Wood, G.A. (1984). Tool use by the palm cockatoo \emph{{P}robosciger aterrimus} during display. Corella \emph{8}, 94--95.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fragaszy2018}{}}%
+\CSLLeftMargin{62. }%
+\CSLRightInline{Fragaszy, D.M., and Mangalam, M.
+(2018).
+Tooling.
+In Advances in the study of behavior., M.
+Naguib, L.
+Barrett, S.
+D.
+Healy, J.
+Podos, L.
+W.
+Simmons, and M.
+Zuk, eds.
+(Academic Press), pp.
+177--241.
+\url{https://doi.org/10.1016/bs.asb.2018.01.001}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Aydinonat2014}{}}%
+\CSLLeftMargin{63. }%
+\CSLRightInline{Aydinonat, D., Penn, D.J., Smith, S., Moodley, Y., Hoelzl, F., Knauer, F., and Schwarzenberger, F.
+(2014).
+Social isolation shortens telomeres in {A}frican {G}rey parrots (\emph{{P}sittacus erithacus erithacus}).
+PLOS ONE \emph{9}, e93839.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Engebretson2006}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{Engebretson, M. (2006). The welfare and suitability of parrots as companion animals: A review. Animal Welfare \emph{15}, 263--276. \url{https://doi.org/10.1017/S0962728600030475}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mason2010}{}}%
+\CSLLeftMargin{65. }%
+\CSLRightInline{Mason, G.J.
+(2010).
+Species differences in responses to captivity: Stress, welfare and the comparative method.
+Trends in Ecology \& Evolution \emph{25}, 713--721.
+\url{https://doi.org/10.1016/j.tree.2010.08.011}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Meehan2003}{}}%
+\CSLLeftMargin{66. }%
+\CSLRightInline{Meehan, C., Garner, J., and Mench, J.
+(2003).
+Isosexual pair housing improves the welfare of young amazon parrots.
+Applied Animal Behaviour Science \emph{81}, 73--88.
+\url{https://doi.org/10.1016/S0168-1591(02)00238-1}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Reader2002}{}}%
+\CSLLeftMargin{67. }%
+\CSLRightInline{Reader, S.M., and Laland, K.N.
+(2002).
+Social intelligence, innovation, and enhanced brain size in primates.
+Proceedings of the National Academy of Sciences \emph{99}, 4436--4441.
+\url{https://doi.org/10.1073/pnas.062041299}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sol2022}{}}%
+\CSLLeftMargin{68. }%
+\CSLRightInline{Sol, D., Olkowicz, S., Sayol, F., Kocourek, M., Zhang, Y., Marhounová, L., Osadnik, C., Corssmit, E., Garcia-Porta, J., Martin, T.E., et al.
+(2022).
+Neuron numbers link innovativeness with both absolute and relative brain size in birds.
+Nature Ecology \& Evolution \emph{6}, 1381--1389.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Alvarez2020}{}}%
+\CSLLeftMargin{69. }%
+\CSLRightInline{Cabrera-Álvarez, M.J., and Clayton, N.S.
+(2020).
+Neural processes underlying tool use in humans, macaques, and corvids.
+Frontiers in Psychology \emph{11}, 560669.
+\url{https://doi.org/10.3389/fpsyg.2020.560669}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HenkeVonDerMalsburg2021}{}}%
+\CSLLeftMargin{70. }%
+\CSLRightInline{Henke-von der Malsburg, J., Kappeler, P.M., and Fichtel, C.
+(2021).
+Linking cognition to ecology in wild sympatric mouse lemur species.
+Proceedings of the Royal Society B: Biological Sciences \emph{288}, 20211728.
+\url{https://doi.org/10.1098/rspb.2021.1728}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Debastiani2021}{}}%
+\CSLLeftMargin{71. }%
+\CSLRightInline{Debastiani, V.J., Bastazini, V.A.G., and Pillar, V.D.
+(2021).
+Using phylogenetic information to impute missing functional trait values in ecological databases.
+Ecological Informatics \emph{63}, 101315.
+\url{https://doi.org/10.1016/j.ecoinf.2021.101315}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hunt2013}{}}%
+\CSLLeftMargin{72. }%
+\CSLRightInline{Hunt, G.R., Gray, R.D., and Taylor, A.H.
+(2013).
+Why is tool use rare in animals?
+In Tool use in animals: Cognition and ecology, C.
+M.
+Sanz, J.
+Call, and C.
+Boesch, eds.
+(Cambridge University Press), pp.
+89--118.
+\url{https://doi.org/10.1017/CBO9780511894800.007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Benichov2016}{}}%
+\CSLLeftMargin{73. }%
+\CSLRightInline{Benichov, J.I., Globerson, E., and Tchernichovski, O.
+(2016).
+Finding the beat: From socially coordinated vocalizations in songbirds to rhythmic entrainment in humans.
+Frontiers in Human Neuroscience \emph{10}.
+\url{https://doi.org/10.3389/fnhum.2016.00255}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Patel2009}{}}%
+\CSLLeftMargin{74. }%
+\CSLRightInline{Patel, A.D., Iversen, J.R., Bregman, M.R., and Schulz, I.
+(2009).
+Experimental evidence for synchronization to a musical beat in a nonhuman animal.
+Current Biology \emph{19}, 827--830.
+\url{https://doi.org/10.1016/j.cub.2009.03.038}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tenCate2016}{}}%
+\CSLLeftMargin{75. }%
+\CSLRightInline{ten Cate, C., Spierings, M., Hubert, J., and Honing, H.
+(2016).
+Can birds perceive rhythmic patterns?
+A review and experiments on a songbird and a parrot species.
+Frontiers in Psychology \emph{7}.
+\url{https://doi.org/10.3389/fpsyg.2016.00730}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilson2016}{}}%
+\CSLLeftMargin{76. }%
+\CSLRightInline{Wilson, M., and Cook, P.F.
+(2016).
+Rhythmic entrainment: Why humans want to, fireflies can't help it, pet birds try, and sea lions have to be bribed.
+Psychonomic Bulletin \& Review \emph{23}, 1647--1659.
+\url{https://doi.org/10.3758/s13423-016-1013-x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Eckert2020}{}}%
+\CSLLeftMargin{77. }%
+\CSLRightInline{Eckert, J., Winkler, S.L., and Cartmill, E.A.
+(2020).
+Just kidding: The evolutionary roots of playful teasing.
+Biology Letters \emph{16}, 20200370.
+\url{https://doi.org/10.1098/rsbl.2020.0370}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-BroJorgensen2010}{}}%
+\CSLLeftMargin{78. }%
+\CSLRightInline{Bro-Jørgensen, J., and Pangle, W.M.
+(2010).
+Male topi antelopes alarm snort deceptively to retain females for mating.
+The American Naturalist \emph{176}, E33--E39.
+\url{https://doi.org/10.1086/653078}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Byrne1988}{}}%
+\CSLLeftMargin{79. }%
+\CSLRightInline{Byrne, R.W., and Whiten, A.
+(1988).
+Toward the next generation in data quality: A new survey of primate tactical deception.
+Behavioral and Brain Sciences \emph{11}, 267--273.
+\url{https://doi.org/10.1017/S0140525X00049955}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Byrne1991}{}}%
+\CSLLeftMargin{80. }%
+\CSLRightInline{Byrne, R.W., and Whiten, A.
+(1991).
+Computation and mindreading in primate tactical deception.
+In Natural theories of mind: Evolution, development and simulation of everyday mindreading, A.
+Whiten, ed.
+(Basil Blackwell), pp.
+127--141.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Auersperg2020}{}}%
+\CSLLeftMargin{81. }%
+\CSLRightInline{Auersperg, A.M.I., Schwing, R., Mioduszewska, B., O'Hara, M., and Huber, L.
+(2020).
+Do puffins use tools?
+Proceedings of the National Academy of Sciences \emph{117}, 11859--11859.
+\url{https://doi.org/10.1073/pnas.2001988117}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-DechaumeMoncharmont2020}{}}%
+\CSLLeftMargin{82. }%
+\CSLRightInline{Dechaume-Moncharmont, F.-X.
+(2020).
+Touchy matter: The delicate balance between {M}organ's canon and open-minded description of advanced cognitive skills in the animal.
+Peer Community in Ecology, 100042.
+\url{https://doi.org/10.24072/pci.ecology.100042}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Farrar2020}{}}%
+\CSLLeftMargin{83. }%
+\CSLRightInline{Farrar, B.G. (2020). Evidence of tool use in a seabird? PsyArXiv. \url{https://doi.org/10.31234/osf.io/463hk}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sandor2020}{}}%
+\CSLLeftMargin{84. }%
+\CSLRightInline{Sándor, K., and Miklósi, Á.
+(2020).
+How to report anecdotal observations?
+A new approach based on a lesson from "puffin tool use".
+Frontiers in Psychology \emph{11}, 555487.
+\url{https://doi.org/10.3389/fpsyg.2020.555487}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vonBayern2020}{}}%
+\CSLLeftMargin{85. }%
+\CSLRightInline{von Bayern, A.M., Jacobs, I., and Osvath, M.
+(2020).
+Tool-using puffins prickle the puzzle of cognitive evolution.
+Proceedings of the National Academy of Sciences \emph{117}, 2737--2739.
+\url{https://doi.org/10.1073/pnas.1922117117}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GlobalGfkSurvey}{}}%
+\CSLLeftMargin{86. }%
+\CSLRightInline{\href{http://www.gfk.com/global-studies/global-studies-pet-ownership}{Global GfK survey: Pet ownership} (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jerison1973}{}}%
+\CSLLeftMargin{87. }%
+\CSLRightInline{Jerison, H.J. (1973). Evolution of the brain and intelligence (Academic Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Paradis2019}{}}%
+\CSLLeftMargin{88. }%
+\CSLRightInline{Paradis, E., and Schliep, K.
+(2019).
+{ape} 5.0: An environment for modern phylogenetics and evolutionary analyses in {R}.
+Bioinformatics \emph{35}, 526--528.
+\url{https://doi.org/10.1093/bioinformatics/bty633}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-McElreath2020}{}}%
+\CSLLeftMargin{89. }%
+\CSLRightInline{McElreath, R.
+(2020).
+\href{http://xcelab.net/rm/statistical-rethinking/}{Statistical rethinking: A {Bayesian} course with examples in {R} and {Stan}, 2nd edition} 2nd ed.
+(CRC Press).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stan2020}{}}%
+\CSLLeftMargin{90. }%
+\CSLRightInline{Stan Development Team (2020). \href{http://mc-stan.org/}{{RStan}: The {R} interface to {Stan}}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-phytools}{}}%
+\CSLLeftMargin{91. }%
+\CSLRightInline{Revell, L.J.
+(2012).
+{phytools}: An {R} package for phylogenetic comparative biology (and other things).
+Methods in Ecology and Evolution \emph{3}, 217--223.
+\url{https://doi.org/10.1111/j.2041-210X.2011.00169.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam}{}}%
+\CSLLeftMargin{92. }%
+\CSLRightInline{R Core Team (2022). \href{https://www.R-project.org/}{R: A language and environment for statistical computing} (R Foundation for Statistical Computing).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ggtree}{}}%
+\CSLLeftMargin{93. }%
+\CSLRightInline{Yu, G., Smith, D., Zhu, H., Guan, Y., and Lam, T.T.-Y.
+(2017).
+{ggtree}: An {R} package for visualization and annotation of phylogenetic trees with their covariates and other associated data.
+Methods in Ecology and Evolution \emph{8}, 28--36.
+\url{https://doi.org/10.1111/2041-210X.12628}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
+\CSLLeftMargin{94. }%
+\CSLRightInline{Wickham, H. (2016). \href{https://ggplot2.tidyverse.org}{{ggplot2}: Elegant graphics for data analysis} (Springer-Verlag New York).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilke2020}{}}%
+\CSLLeftMargin{95. }%
+\CSLRightInline{Wilke, C.O. (2020). \href{https://CRAN.R-project.org/package=cowplot}{{cowplot}: Streamlined plot theme and plot annotations for 'ggplot2'}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
+\CSLLeftMargin{96. }%
+\CSLRightInline{Landau, W.M.
+(2021).
+The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing.
+Journal of Open Source Software \emph{6}, 2959.
+\url{https://doi.org/10.21105/joss.02959}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Aust2022}{}}%
+\CSLLeftMargin{97. }%
+\CSLRightInline{Aust, F., and Barth, M. (2022). \href{https://github.com/crsh/papaja}{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}.}
+
+\end{CSLReferences}
+
+\endgroup
+
+\newpage
 \vspace*{60mm}
@@
 
-\noindent \hspace*{5mm} \small New evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare \newline
+\noindent \hspace*{5mm} \small Evidence of self-care tooling and phylogenetic modelling reveal parrot tool use is not rare \newline
 \hspace*{1cm} \small Amalia P. M. Bastos\textsuperscript{1,2}, Scott Claessens\textsuperscript{2}, Ximena J. Nelson\textsuperscript{3}, David Welch\textsuperscript{4}, \newline
